### 2023-01-11 02. Design/MSG-P2312-Analysis Plan.rmd
Initial commit

---
title: "Analysis plan"
# date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Sara Guenther and Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(skimr)
library(DataExplorer)
library(readr)
library(oescolorrrs)
library(oesrrr)
```

# Analysis Plan

Project Name: `r params$project_name`

Project Code: `r params$project_number`

Date Finalized: `r nice_date(Sys.Date())`

<!-- How this document is to be used:  -->

<!-- This document serves as a basis for distinguishing between planned confirmatory analyses and any exploratory analyses that might be conducted on project data. This is crucial to ensuring that results of statistical tests are properly interpreted and reported. For the Analysis Plan to fulfill this purpose, it is essential that it be finalized and date-stamped before we take possession of outcome data. Once this plan is finalized, a date is entered above, and the document is posted publicly on our team website.  -->

<!-- If any analyses are described that will not be included in the MSG abstract or reported to the agency partner, then explicitly identify these in order to streamline reanalysis. -->

### Project Description

<!-- [Brief description of the project, including the challenge, the intervention(s) to be tested, and the questions to be answered. This should be brief, but should provide context sufficient for the analysis plan that follows.] -->

Insert text here, and delete the gray prompt above when the document is final

### Pre Registration Details

This Analysis Plan will be posted on the GSA Evaluation Division website at [TBD] before outcome data are analyzed. In addition, this project will be pre registered in the [registry name] at [link to the registry, either main page or project-specific page].

### Research Question(s)

<!-- [Briefly state the primary and any secondary hypotheses to be tested. Aim for plain language. Statistical models and details of hypothesis tests will be covered later; the purpose here is to set the stage for the sections that follow.] -->

Insert text here, and delete the gray prompt above when the document is final

## Data and Data Structure

We will use Daily Check-In data obtained from Management Science and Innovation (MSI), a firm contracted to collect and maintain these data. We will merge in additional variables from the GSA Roster obtained from D2D. The GSA roster is updated monthly at the end of each month. *[We currently have Nov 2022 and Dec 2022 updates; I will try to track down past months. Ideally, we will merge in each monthly check-in file with the preceding month's roster file.]*

### Table 1. GSA Daily Check-In Data Variables Available Feb 2022-Dec 2022. Try bolded variables for merging.

### Data Source(s):

Additional administrative data that may be useful for exploratory analysis includes:

### Outcomes to Be Analyzed:

<!-- [List all outcome variables for which analysis is planned. If specific variable names are unavailable, describe the outcomes in sufficient detail to appropriately guide or constrain their calculation. Specify which outcomes will be submitted to confirmatory versus exploratory analysis (or do this later in the ‘Statistical Models & Hypothesis Tests’ section if it is more appropriate there).] -->

Insert text here, and delete the gray prompt above when the document is final

### Transformations of Data Structure:

<!-- [Describe variables that will be added to the raw data. These may be variables used in the experimental design (e.g., blocking variables) or covariates merged in from a different dataset.]  -->

<!-- [Describe new variables that will be created by transforming or combining variables in the raw data. If you plan on transforming, centering, or recoding the data, or will apply a coding scheme for categorical variables, please describe that process.  If any measurements are  going to be combined into an index (or even a mean), what measures will you use and how will they be combined? Include either a formula or a precise description of your method.] -->

<!-- [Describe any plans to transform the structure of your data (e.g., from cross-sectional to panel).] -->

Insert text here, and delete the gray prompt above when the document is final

### Data Exclusion and Treatment of Missing Data:

<!-- [Describe criteria you will use to determine whether any observations should be excluded from analysis (e.g., values that are likely data-recording errors, outliers, etc.).] -->

<!-- [Describe your plan to handle missing data.  How will you deal with incomplete or missing data (e.g., pairwise or listwise deletion, imputation, interpolation)?] -->

Insert text here, and delete the gray prompt above when the document is final

## Study Design and Analytic Methods

This section describes the statistical models and hypothesis tests that will make up the analysis --- including any follow-ups on effects in the main statistical model and any exploratory analyses that can be anticipated prior to analysis.

### Study Design

<!-- [prompt] -->

Insert text here, and delete the gray prompt above when the document is final

### Statistical Models & Hypothesis Tests

<!-- [What criteria will you use to make inferences? Please describe the information you will use (e.g., specify the p-values), as well as cut-off criteria, where appropriate. Will you be using one- or two-tailed tests for each of your analyses? If you are comparing multiple conditions or testing multiple hypotheses, what method will you use to correct for multiple tests? If you are taking into account practical significance, please specify a minimum effect size of interest.] -->

Insert text here, and delete the gray prompt above when the document is final

### Descriptive Statistics, Tables, & Graphs

<!-- [What descriptive statistics, tables, and graphs will be needed for reporting? If possible, provide table shells and/or mock graphs. If any statistics, tables, or graphs  are listed that will not be included in the MSG abstract or reported to the agency partner, then explicitly identify these in order to streamline reanalysis.] -->

Insert text here, and delete the gray prompt above when the document is final

### Confirmatory Analyses:

<!-- [Specify the hypothesis test(s) that will be reported as confirmatory. Which outcome and which of the above statistical models will you use to test each hypothesis? If you plan to test null hypotheses other than equality (zero effect), please specify the type of test and the margin. Remember that any test not included here must be noted as an exploratory test in any report of this research. Keep in mind that you can specify contingent or follow-up analyses that are still confirmatory. For example, if you find a main effect of the treatment, will you test for heterogeneous treatment effects? Will you look for specific pairwise differences between treatment arms if you find an overall effect of the pooled treatment? Exploratory analyses can be recorded in the next section. If any analyses are described that will not be included in the MSG abstract or reported to the agency partner, then explicitly identify these in order to streamline reanalysis.] -->

Insert text here, and delete the gray prompt above when the document is final

### Exploratory Analysis:

<!-- [OPTIONAL: If you plan to explore your data set to look for unexpected differences or relationships, you may describe those tests here. An exploratory test is any test where a prediction is not made up front, or where there are multiple possible tests that you are going to use. A statistically significant finding in an exploratory test is a great way to form a new confirmatory hypothesis, which could then be tested using a pre-specified analysis at a later time. Note that exploratory analyses will not, by default, be included in reanalysis.] -->

Insert text here, and delete the gray prompt above when the document is final

### Inference Criteria, Including Any Adjustments for Multiple Comparisons:

<!-- [What criteria will you use to make inferences? Please describe the information you will use (e.g., specify the p-values), as well as cut-off criteria, where appropriate. Will you be using one- or two-tailed tests for each of your analyses? If you are comparing multiple conditions or testing multiple hypotheses, what method will you use to correct for multiple tests? If you are taking into account practical significance, please specify a minimum effect size of interest.] -->

Insert text here, and delete the gray prompt above when the document is final

### Limitations:

<!-- [Describe any anticipated limitations associated with this analysis, if not previously identified in the Project Design document.] -->

Insert text here, and delete the gray prompt above when the document is final

### 2023-01-11 04. Analysis/scripts/01_data_preparation.Rmd
Initial commit

---
title: "Data preparation"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  data_folder_1: "Occupancy Data Pull"
  unique_identifier_1: !r c("employee_name")
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(janitor)
library(skimr)
library(DataExplorer)
library(readr)
```

# Data preparation {.tabset .tabset-pills}

**Project number**: `r params$project_number`

**Project name**: `r params$project_name`

**Author**: `r params$author`

**Data folder 1**: `r params$data_folder_`'

**Unique identifier for data folder 1**: `r params$unique_identifier_1`

## Load data {.tabset .tabset-pills}

### Data from `r params$data_folder_1`

Find the list of .csv files in the `r params$data_folder_1` data folder.

```{r}
files <- 
  list.files(here::here("03. Data Collection",params$data_folder_1), pattern = ".csv", full.names = TRUE)
files
```

Load all data files in the `r params$data_folder_1` data folder.

```{r}
prep_01 <- files %>% 
  map_dfr(~read_csv(., 
    col_types = cols(Date = col_date(format = "%m_%d_%Y")))) %>% 
  clean_names()
```

Review data.

```{r}
prep_01 %>% skim()
```

Create function to drop rows with null unique identifiers.

```{r}
filter_unique <- function(in_data, ...)
{
  in_data %>% 
  filter(if_all(c(...),~!is.na(.)))
}
```

Drop rows with null unique identifiers.

```{r}
prep_01 <- 
  prep_01 %>% 
  filter_unique(params$unique_identifier_1)
```

Review data.

```{r}
prep_01 %>% skim()
```

Identify columns with amounts unique values less than 30.

```{r}
low_unique_value_cols <- 
  prep_01 %>% 
  summarise(across(.fns = ~n_distinct(.))) %>% 
  rownames_to_column() %>% 
  pivot_longer(-rowname) %>% 
  filter(value < 30) %>% 
  pull(name)
```

**Unique low value columns**: `r low_unique_value_cols`

Convert low unique value variables to factors.

```{r}
prep_01 <- 
  prep_01 %>% 
  mutate(across(all_of(low_unique_value_cols),as.factor))
```

Review data.

```{r}
prep_01 %>% skim()
```

## Join/bind data {.tabset .tabset-pills}

No data to join or bind so far.

```{r}
d <- prep_01
```

Review data.

```{r}
d %>% skim()
```

## Save data {.tabset .tabset-pills}

```{r}
save(d, file = here::here("03. Data Collection",params$data_folder_1,"prepared_data.rdata"))
```

### 2023-01-11 04. Analysis/scripts/01_data_preparation.R

@@ -1,0 +1,48 @@
+
+# Start timer -------------------------------------------------------------
+
+tictoc::tic()
+
+# Libraries ---------------------------------------------------------------
+
+library(tidyverse)
+library(lubridate)
+library(purrr)
+
+# Parameters --------------------------------------------------------------
+
+author <- "Ben Jaques-Leslie"
+project_number <- 2312
+project_name <- "Occupancy Patterns"
+data_folder_1 <- "Occupancy Data Pull"
+unique_identifier_1 <- c("employee_name")
+
+# Determine file name -----------------------------------------------------
+
+file_name <- glue::glue("01-data-preparation-{project_number}-{str_replace_all(str_to_lower(project_name),' ','-')}-{today()}.html")
+
+file_name
+
+# Render data extraction --------------------------------------------------
+
+rmarkdown::render(input = here::here("04. Analysis",
+                                     "scripts",
+                                     "01_data_preparation.Rmd"),
+                  params = list(
+                    author = author,
+                    project_number = project_number,
+                    project_name = project_name,
+                    data_folder_1 = data_folder_1,
+                    unique_identifier_1 = unique_identifier_1
+                  ),
+                  output_file =
+                    here::here("04. Analysis",
+                               "output",
+                               'html',
+                               file_name))
+
+
+# End timer ---------------------------------------------------------------
+
+tictoc::toc()
+

### 2023-01-11 04. Analysis/scripts/import_roster.R

@@ -1,0 +1,5 @@
+#import_roster.R
+#skg 1/6/2023
+
+r <- read.csv("G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Occupancy Patterns/03. Data Collection/GSA Roster from D2D 20221130.csv",
+              stringsAsFactors = FALSE, na.strings = "NA", row.names=NULL)

### 2023-01-20 02. Design/MSG-P2312-Analysis Plan.rmd
Update MSG-P2312-Analysis Plan.rmd

@@
 
+This section describes variables that will be analyzed, as well as changes that will be made to the raw data with respect to data structure and variables.
+
+### Data Source(s):
+
 We will use Daily Check-In data obtained from Management Science and Innovation (MSI), a firm contracted to collect and maintain these data.
@@
 The GSA roster is updated monthly at the end of each month.
-*[We currently have Nov 2022 and Dec 2022 updates; I will try to track down past months.
-Ideally, we will merge in each monthly check-in file with the preceding month's roster file.]*
+[We currently have Nov 2022 and Dec 2022 updates; I will try to track down past months.
+Ideally, we will merge in each monthly check-in file with the preceding month’s roster file.]
 
-### Table 1. GSA Daily Check-In Data Variables Available Feb 2022-Dec 2022. Try bolded variables for merging.
+### Table 1. GSA Daily Check-In Data Variables Available Feb 2022-Dec 2022.
 
-### Data Source(s):
+### Table 2. GSA Roster Variables.
 

### 2023-01-23 02. Design/MSG-P2312-Analysis Plan.rmd

@@
 
-Insert text here, and delete the gray prompt above when the document is final
+The U.S.
+General Services Administration’s FY 2022 Annual Evaluation Plan includes evaluation goals that involve The Future of Work projects and objectives.
+This initiative is part of an effort to right-size the federal real estate footprint.
+Specifically, this project will examine the effects of distributed, virtual, and asynchronous work with the goal of informing future changes to interior space planning and building operations.
+We will join GSA telework rates and facility occupancy patterns with GSA roster data and describe rates of telework and on site work across employment and personal demographics.
+We will also determine the rates at which teams work together onsite, remotely, or in a hybrid environment.
 
@@
 
-<!-- [Briefly state the primary and any secondary hypotheses to be tested.
-Aim for plain language.
-Statistical models and details of hypothesis tests will be covered later; the purpose here is to set the stage for the sections that follow.] -->
+This work will address the following research questions:
+1. What are the rates of telework since the federal return-to-office transition?
+2. Do telework behaviors match position category (e.g., onsite, offsite, etc.) in the roster?
+3. At what rates to teams work together onsite vs. remotely?
+4. Do the telework patterns of supervisors match the telework patterns of supervisees?
 
-Insert text here, and delete the gray prompt above when the document is final
+At this stage, our research questions are aimed at describing patterns of telework and federal building occupancy rather than estimating the impacts of telework.
 
@@
 
-Insert text here, and delete the gray prompt above when the document is final
-
 ### Transformations of Data Structure:
@@
 
-Insert text here, and delete the gray prompt above when the document is final
-
 ### Data Exclusion and Treatment of Missing Data:
@@
 <!-- [Describe your plan to handle missing data.  How will you deal with incomplete or missing data (e.g., pairwise or listwise deletion, imputation, interpolation)?] -->
-
-Insert text here, and delete the gray prompt above when the document is final
 
@@
 
-Insert text here, and delete the gray prompt above when the document is final
-
 ### Statistical Models & Hypothesis Tests
@@
 
-Insert text here, and delete the gray prompt above when the document is final
-
 ### Descriptive Statistics, Tables, & Graphs
@@
 If any statistics, tables, or graphs  are listed that will not be included in the MSG abstract or reported to the agency partner, then explicitly identify these in order to streamline reanalysis.] -->
-
-Insert text here, and delete the gray prompt above when the document is final
 
@@
 
-Insert text here, and delete the gray prompt above when the document is final
-
 ### Exploratory Analysis:
@@
 Note that exploratory analyses will not, by default, be included in reanalysis.] -->
-
-Insert text here, and delete the gray prompt above when the document is final
 
@@
 
-Insert text here, and delete the gray prompt above when the document is final
-
 ### Limitations:
@@
 <!-- [Describe any anticipated limitations associated with this analysis, if not previously identified in the Project Design document.] -->
-
-Insert text here, and delete the gray prompt above when the document is final

### 2023-01-23 02. Design/MSG-P2312-Analysis Plan.rmd
Update MSG-P2312-Analysis Plan.rmd
Adding some more details to data structure

@@
   project_name: "Occupancy Patterns"
+editor_options: 
+  markdown: 
+    wrap: 72
 ---
@@
 library(oesrrr)
+library(flextable)
 ```
@@
 
-The U.S.
-General Services Administration’s FY 2022 Annual Evaluation Plan includes evaluation goals that involve The Future of Work projects and objectives.
-This initiative is part of an effort to right-size the federal real estate footprint.
-Specifically, this project will examine the effects of distributed, virtual, and asynchronous work with the goal of informing future changes to interior space planning and building operations.
-We will join GSA telework rates and facility occupancy patterns with GSA roster data and describe rates of telework and on site work across employment and personal demographics.
-We will also determine the rates at which teams work together onsite, remotely, or in a hybrid environment.
+The U.S. General Services Administration's FY 2022 Annual Evaluation
+Plan includes evaluation goals that involve The Future of Work projects
+and objectives. This initiative is part of an effort to right-size the
+federal real estate footprint. Specifically, this project will examine
+the effects of distributed, virtual, and asynchronous work with the goal
+of informing future changes to interior space planning and building
+operations. We will join GSA telework rates and facility occupancy
+patterns with GSA roster data and describe rates of telework and on site
+work across employment and personal demographics. We will also determine
+the rates at which teams work together onsite, remotely, or in a hybrid
+environment.
 
@@
 
-This Analysis Plan will be posted on the GSA Evaluation Division website at [TBD] before outcome data are analyzed.
-In addition, this project will be pre registered in the [registry name] at [link to the registry, either main page or project-specific page].
+This Analysis Plan will be posted on the GSA Evaluation Division website
+at [TBD] before outcome data are analyzed. In addition, this project
+will be pre registered in the [registry name] at [link to the registry,
+either main page or project-specific page].
 
@@
 
-This work will address the following research questions:
-1. What are the rates of telework since the federal return-to-office transition?
-2. Do telework behaviors match position category (e.g., onsite, offsite, etc.) in the roster?
-3. At what rates to teams work together onsite vs. remotely?
-4. Do the telework patterns of supervisors match the telework patterns of supervisees?
+This work will address the following research questions: 1. What are the
+rates of telework since the federal return-to-office transition? 2. Do
+telework behaviors match position category (e.g., onsite, offsite, etc.)
+in the roster? 3. At what rates to teams work together onsite vs.
+remotely? 4. Do the telework patterns of supervisors match the telework
+patterns of supervisees?
 
-At this stage, our research questions are aimed at describing patterns of telework and federal building occupancy rather than estimating the impacts of telework.
+At this stage, our research questions are aimed at describing patterns
+of telework and federal building occupancy rather than estimating the
+impacts of telework.
 
@@
 
-This section describes variables that will be analyzed, as well as changes that will be made to the raw data with respect to data structure and variables.
+This section describes variables that will be analyzed, as well as
+changes that will be made to the raw data with respect to data structure
+and variables.
 
@@
 
-We will use Daily Check-In data obtained from Management Science and Innovation (MSI), a firm contracted to collect and maintain these data.
-We will merge in additional variables from the GSA Roster obtained from D2D.
-The GSA roster is updated monthly at the end of each month.
-[We currently have Nov 2022 and Dec 2022 updates; I will try to track down past months.
-Ideally, we will merge in each monthly check-in file with the preceding month’s roster file.]
+We will use Daily Check-In data obtained from Management Science and
+Innovation (MSI), a firm contracted to collect and maintain these data.
+We will merge in additional variables from the GSA Roster obtained from
+D2D. The GSA roster is updated monthly at the end of each month. [We
+currently have Nov 2022 and Dec 2022 updates; I will try to track down
+past months. Ideally, we will merge in each monthly check-in file with
+the preceding month's roster file.]
 
@@
 
-Additional administrative data that may be useful for exploratory analysis includes:
+Additional administrative data that may be useful for exploratory
+analysis includes:
 
@@
 Specify which outcomes will be submitted to confirmatory versus exploratory analysis (or do this later in the ‘Statistical Models & Hypothesis Tests’ section if it is more appropriate there).] -->
+
+For much of this study, no particular outcome will be analyzed. For
+cluster and categorization, we will use various measures of staff work
+location and frequency, for example, proportion of time teleworking or
+frequency of teleworking on particular days. For sequence analysis, we
+will use work status on particular days for staff or in combination with
+team members.
 
@@
 
+For all analysis, we will used a defined cohort of staff to examine work
+status over period of time. A cohort of staff employed in the month of
+March 2022 will be followed over six months. Teams will be defined by
+the supervisors of groups of staff in the beginning of March 2022. Any
+analysis will conduct may be reproduced on a separate cohort or may be
+combined with multiple cohorts depending on the data availability.
+
+The analysis can be thought of as a two-by-two box.
+
+```{r, echo=FALSE}
+tbl <- 
+  tibble::tibble(level = rep("Level of analysis",2),
+                      Group = c("Staff", "Team"),
+                      Cluster = c("Person level aggregation of work status", "Team level aggregation of work status"),
+                      Sequence = c("Daily person work status", "Daily team work status")
+                       )
+```
+
+```{r}
+tbl %>% 
+  flextable() %>% 
+  add_header_row(values = c("","","Type of analysis", "Type of analysis")) %>% 
+  set_header_labels(level = "") %>% 
+  merge_h(part = "header") %>% 
+  merge_v(j = 1) %>% 
+  theme_vanilla() %>% 
+  autofit()
+```
+
+For cluster analysis of staff work status, the data will be transformed
+so that each row is one staff person. From the raw data, the following
+variables will be defined:
+
+-   Proportion of days working onsite
+
+-   Proportion of days working remote
+
+-   Proportion of days working remote by the day of the week
+
+-   Correlation of work status between days of the week
+
+-   Indicator for an exit form employment
+
+-   Indicator for a switch in supervisor
+
+-   Size of team over observation window
+
+For cluster analysis of team work status, the data will be transformed
+so that each row is one team as defined by the supervisor. Supervisors
+may be in multiple teams as supervisor and subordinate. From the raw
+data, the following variables will be defined:
+
+-   Size of team over observation window
+
+-   Proportion of staff days working onsite
+
+-   Proportion of staff days working remote
+
+-   Proportion of staff days working remote by the day of the week
+
+-   Proportion of days of staff concurrent remote status
+
+-   Proportion of days of staff concurrent onsite status
+
+-   Proportion of staff exiting team
+
 ### Data Exclusion and Treatment of Missing Data:
@@
 
-This section describes the statistical models and hypothesis tests that will make up the analysis --- including any follow-ups on effects in the main statistical model and any exploratory analyses that can be anticipated prior to analysis.
+This section describes the statistical models and hypothesis tests that
+will make up the analysis --- including any follow-ups on effects in the
+main statistical model and any exploratory analyses that can be
+anticipated prior to analysis.
 
@@
 If any statistics, tables, or graphs  are listed that will not be included in the MSG abstract or reported to the agency partner, then explicitly identify these in order to streamline reanalysis.] -->
+
+Proportion in staff time telework
+
+Proportion in staff time telework by the day of the week
+
+Proportion in staff time onsite
+
+Proportion in staff time onsite by the day of the week
+
+Correlations of by staff time between the days of the week
+
+Size of teams
 

### 2023-01-30 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Create MSG-P2312-Analysis Plan-1-clusters.rmd
Added new tables for the data, removed references to sequence, built out the analysis section more, added more the descriptive stats and tables

--- 2023-01-23 02. Design/MSG-P2312-Analysis Plan.rmd
@@
   project_name: "Occupancy Patterns"
+  analysis_plan_title: "Phase 2 - Clusters"
 editor_options: 
@@
 Project Code: `r params$project_number`
+
+Analysis plan title: `r params$analysis_plan_title`
 
@@
 
+```{r}
+tbl <- tibble("Variable Name" = c(
+  "date",
+"SSO",
+"short_id",
+"dept_id",
+"employee_name",
+"supervisor_name",
+"location",
+"daily_status",
+"supervisor_correction"
+),
+"Description" = c(
+  "Date of check-in",
+  # Is SSO single sign on? What did we decide?
+"",
+"2-digit department id",
+"Full department id code",
+"Employee name (Last,First Middle)",
+"Supervisor name (Last,First Middle)",
+"State abbreviation-City-Site (e.g., home or address); could string split and match state with roster, possibly city too.",
+"E.g., Teleworking, Leave, Supervisor Corrected, No Response, Reporting to Job Site, Other",
+# I think that this is an indicator for whether the supervisor corrected the record
+""
+)
+)
+```
+
+```{r}
+tbl %>% 
+  flextable() %>% 
+  # add_header_row(values = c("","","Type of analysis", "Type of analysis")) %>% 
+  # set_header_labels(Group = "Level of analysis") %>% 
+  merge_h(part = "header") %>% 
+  merge_v(j = 1) %>% 
+  theme_vanilla() %>% 
+  autofit()
+```
+
 ### Table 2. GSA Roster Variables.
@@
 analysis includes:
+
+```{r}
+tbl <- tibble("Variable Name" = c(
+"Snapshot.Date",
+"Department.ID",
+"Employee.Job.Business.Unit.Description",
+"Full.Name",
+"Employee.E.Mail.Address",
+"Position.Title",
+"Pay.Plan",
+"Occupational.Series",
+"Grade",
+"EOD.Date",
+"Supervisor.Level",
+"Supervisor.Level.Description",
+"Supervisor.Display.Name",
+"Supervisor.E.Mail.Address",
+"Business.Line.2.Letter.Department.ID.",
+"GSA.SSO",
+"Agency.Subelement.Code.Description",
+"GSA.Region",
+"GSA.Duty.Station.Region",
+"Location.City",
+"Location.State",
+"Duty.Station.Code",
+"Employee.Job.Bargaining.Unit.Description",
+"Employee.Summary.Bargaining.Unit",
+"Payroll.Accounting.Code",
+"Position.Number",
+"Position.Category.Code",
+"Position.Category.Description"
+),
+"Description" = c(
+ "Date of data export",
+"Should align with check-in’s 'dept_id'",
+"",
+"Last,First Middle; should align with check-in’s 'employee_name'",
+"",
+"",
+"",
+"",
+"",
+"",
+"",
+"",
+"First, Last",
+"",
+"",
+"",
+"",
+"",
+"",
+"",
+"",
+"",
+"",
+"",
+"",
+"",
+"",
+"E.g., Onsite flexible, Offsite, Onsite required, Not specified, Position has changed"
+)
+)
+```
+
+```{r}
+tbl %>% 
+  flextable() %>% 
+  # add_header_row(values = c("","","Type of analysis", "Type of analysis")) %>% 
+  # set_header_labels(Group = "Level of analysis") %>% 
+  merge_h(part = "header") %>% 
+  merge_v(j = 1) %>% 
+  theme_vanilla() %>% 
+  autofit()
+```
 
@@
 location and frequency, for example, proportion of time teleworking or
-frequency of teleworking on particular days. For sequence analysis, we
-will use work status on particular days for staff or in combination with
-team members.
+frequency of teleworking on particular days.
 
@@
 
-The analysis can be thought of as a two-by-two box.
+The analysis will be done for staff and teams separately
 
@@
 tbl <- 
-  tibble::tibble(level = rep("Level of analysis",2),
+  tibble::tibble(
+    # level = rep("Level of analysis",2),
                       Group = c("Staff", "Team"),
                       Cluster = c("Person level aggregation of work status", "Team level aggregation of work status"),
-                      Sequence = c("Daily person work status", "Daily team work status")
+                      # Sequence = c("Daily person work status", "Daily team work status")
                        )
@@
   flextable() %>% 
-  add_header_row(values = c("","","Type of analysis", "Type of analysis")) %>% 
-  set_header_labels(level = "") %>% 
+  # add_header_row(values = c("","","Type of analysis", "Type of analysis")) %>% 
+  set_header_labels(Group = "Level of analysis") %>% 
   merge_h(part = "header") %>% 
@@
 ```
+
+We will approach grouping staff and teams in two ways.
+First, rules-based groups will be formed.
+For these, definitions of different types of work will be defined.
+Second, groups will be formed using k-means clustering.
+This unsupervised machine learning method produces a defined number of groups (or clusters) minimizing the distance between the members.
+
+<!-- https://www.r-bloggers.com/2021/04/cluster-analysis-in-r/ -->
+<!-- https://www.guru99.com/r-k-means-clustering.html -->
 
@@
 
+Three broad parts of descriptive work are part of this analysis.
+First, the overall description of work patterns in the data.
+Then, differences in work patterns by rules-based group, and differences in descriptive data by those groups.
+Lastly, difference in k-means cluster by work patterns and descriptive data.
+
 Proportion in staff time telework

### 2023-01-30 02. Design/MSG-P2312-Analysis Plan-2-sequence.rmd
Create MSG-P2312-Analysis Plan-2-sequence.rmd
Removed references to clusters.

--- 2023-01-23 02. Design/MSG-P2312-Analysis Plan.rmd
@@
   project_name: "Occupancy Patterns"
+  analysis_plan_title: "Phase 2 - Sequences"
 editor_options: 
@@
 
-# Analysis Plan
-
 Project Name: `r params$project_name`
@@
 tbl <- 
-  tibble::tibble(level = rep("Level of analysis",2),
+  tibble::tibble(
+    # level = rep("Level of analysis",2),
                       Group = c("Staff", "Team"),
-                      Cluster = c("Person level aggregation of work status", "Team level aggregation of work status"),
+                      # Cluster = c("Person level aggregation of work status", "Team level aggregation of work status"),
                       Sequence = c("Daily person work status", "Daily team work status")

### 2023-02-01 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd

@@
 location and frequency, for example, proportion of time teleworking or
-frequency of teleworking on particular days.
+frequency of teleworking on particular days. We will investigate the
+relationships between these and other factors.
 
@@
 combined with multiple cohorts depending on the data availability.
+
+Both data sources will be checked for duplication and deduplicated.
+The unique identifiers of the daily check-in data are `employee_name` and `date`.
+For the roster data the unique identifier is `Full.Name` and `Snapshot.Date`.
+The general approach to deduplication will be that categorical variables will be restructured as indicator variables taking on a one for each category associated with the duplicate.
+From the roster data, if the duplication is based off of `EOD.Date`, the later date will be selected along with the other variables associated with that date.
+There appear to be no numeric variables.
 
@@
 
-We will approach grouping staff and teams in two ways.
-First, rules-based groups will be formed.
-For these, definitions of different types of work will be defined.
-Second, groups will be formed using k-means clustering.
-This unsupervised machine learning method produces a defined number of groups (or clusters) minimizing the distance between the members.
+We will approach grouping staff and teams in two ways. First,
+rules-based groups will be formed. For these, definitions of different
+types of work will be defined. Second, groups will be formed using
+k-means clustering. This unsupervised machine learning method produces a
+defined number of groups (or clusters) minimizing the distance between
+the members.
 
-<!-- https://www.r-bloggers.com/2021/04/cluster-analysis-in-r/ -->
-<!-- https://www.guru99.com/r-k-means-clustering.html -->
-
-For cluster analysis of staff work status, the data will be transformed
-so that each row is one staff person. From the raw data, the following
-variables will be defined:
+For both rules-based and cluster classification of individual staff, the
+daily check-in data will be transformed so that each row is one staff person. From the
+raw data, the following variables will be defined:
 
@@
 
-For cluster analysis of team work status, the data will be transformed
-so that each row is one team as defined by the supervisor. Supervisors
-may be in multiple teams as supervisor and subordinate. From the raw
-data, the following variables will be defined:
+For both rules-based and cluster classification of teams, the daily check-in data will
+be transformed so that each row is one team as defined by the
+supervisor. Supervisors may be in multiple teams as supervisor and
+subordinate. From the raw data, the following variables will be defined:
 
@@
 
+Missing data from daily check in will be treated as follows:
+
+```{r}
+tbl <- tibble("Variable Name" = c(
+  "date",
+"SSO",
+"short_id",
+"dept_id",
+"employee_name",
+"supervisor_name",
+"location",
+"daily_status",
+"supervisor_correction"
+),
+"Treatment if missing" = c(
+  "Drop observation",
+  "",
+  "Impute from other observations of same staff",
+  "Impute from other observations of same staff",
+  "Drop observation",
+  "Impute from other observations of same staff",
+  "Label as missing",
+  "Label as missing",
+  "Label as missing"
+)
+)
+```
+
+```{r}
+tbl %>% 
+  flextable() %>% 
+  # add_header_row(values = c("","","Type of analysis", "Type of analysis")) %>% 
+  # set_header_labels(Group = "Level of analysis") %>% 
+  merge_h(part = "header") %>% 
+  merge_v(j = 1) %>% 
+  theme_vanilla() %>% 
+  autofit()
+```
+
+Missing data from the roster will be treated as follows:
+
+```{r}
+tbl <- tibble("Variable Name" = c(
+"Snapshot.Date",
+"Department.ID",
+"Employee.Job.Business.Unit.Description",
+"Full.Name",
+"Employee.E.Mail.Address",
+"Position.Title",
+"Pay.Plan",
+"Occupational.Series",
+"Grade",
+"EOD.Date",
+"Supervisor.Level",
+"Supervisor.Level.Description",
+"Supervisor.Display.Name",
+"Supervisor.E.Mail.Address",
+"Business.Line.2.Letter.Department.ID.",
+"GSA.SSO",
+"Agency.Subelement.Code.Description",
+"GSA.Region",
+"GSA.Duty.Station.Region",
+"Location.City",
+"Location.State",
+"Duty.Station.Code",
+"Employee.Job.Bargaining.Unit.Description",
+"Employee.Summary.Bargaining.Unit",
+"Payroll.Accounting.Code",
+"Position.Number",
+"Position.Category.Code",
+"Position.Category.Description"
+),
+"Treatment if missing" = c(
+  "Label as missing",
+  "Label as missing",
+  "Label as missing",
+  "Drop observation",
+  "Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing",
+"Label as missing"
+)
+)
+```
+
+```{r}
+tbl %>% 
+  flextable() %>% 
+  # add_header_row(values = c("","","Type of analysis", "Type of analysis")) %>% 
+  # set_header_labels(Group = "Level of analysis") %>% 
+  merge_h(part = "header") %>% 
+  merge_v(j = 1) %>% 
+  theme_vanilla() %>% 
+  autofit()
+```
 <!-- [Describe your plan to handle missing data.  How will you deal with incomplete or missing data (e.g., pairwise or listwise deletion, imputation, interpolation)?] -->
@@
 <!-- [prompt] -->
+
+<!-- https://www.r-bloggers.com/2021/04/cluster-analysis-in-r/ -->
+
+<!-- https://www.guru99.com/r-k-means-clustering.html -->
 
@@
 
-Three broad parts of descriptive work are part of this analysis.
-First, the overall description of work patterns in the data.
-Then, differences in work patterns by rules-based group, and differences in descriptive data by those groups.
-Lastly, difference in k-means cluster by work patterns and descriptive data.
+Three broad parts of descriptive work are part of this analysis. First,
+the overall description of work patterns in the data. Then, differences
+in work patterns by rules-based group, and differences in descriptive
+data by those groups. Lastly, difference in k-means cluster by work
+patterns and descriptive data.
 

### 2023-02-06 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Continued work on the analysis plan

@@
 
-Both data sources will be checked for duplication and deduplicated.
-The unique identifiers of the daily check-in data are `employee_name` and `date`.
-For the roster data the unique identifier is `Full.Name` and `Snapshot.Date`.
-The general approach to deduplication will be that categorical variables will be restructured as indicator variables taking on a one for each category associated with the duplicate.
-From the roster data, if the duplication is based off of `EOD.Date`, the later date will be selected along with the other variables associated with that date.
-There appear to be no numeric variables.
+Both data sources will be checked for duplication and deduplicated. The
+unique identifiers of the daily check-in data are `employee_name` and
+`date`. For the roster data the unique identifier is `Full.Name` and
+`Snapshot.Date`. The general approach to deduplication will be that
+categorical variables will be restructured as indicator variables taking
+on a one for each category associated with the duplicate. From the
+roster data, if the duplication is based off of `EOD.Date`, the later
+date will be selected along with the other variables associated with
+that date. There appear to be no numeric variables.
 
@@
 For both rules-based and cluster classification of individual staff, the
-daily check-in data will be transformed so that each row is one staff person. From the
-raw data, the following variables will be defined:
+daily check-in data will be transformed so that each row is one staff
+person. From the raw data, the following variables will be defined:
 
--   Proportion of days working onsite
+-   Proportion of days onsite
 
--   Proportion of days working remote
+-   Proportion of days remote
 
--   Proportion of days working remote by the day of the week
+-   Proportion of days remote by the day of the week
 
@@
 
--   Indicator for an exit form employment
+-   Number of working days
+
+-   Indicator for an exit from employment
 
@@
 
-For both rules-based and cluster classification of teams, the daily check-in data will
-be transformed so that each row is one team as defined by the
-supervisor. Supervisors may be in multiple teams as supervisor and
-subordinate. From the raw data, the following variables will be defined:
+For both rules-based and cluster classification of teams, the daily
+check-in data will be transformed so that each row is one team as
+defined by the supervisor. Supervisors may be in multiple teams as
+supervisor and subordinate. From the raw data, the following variables
+will be defined:
 
@@
 
--   Proportion of staff days working onsite
+-   Proportion of staff working days onsite
 
--   Proportion of staff days working remote
+-   Proportion of staff working days remote
 
--   Proportion of staff days working remote by the day of the week
+-   Proportion of staff working days remote by the day of the week
 
@@
 
+-   Number of staff working days
+
 ### Data Exclusion and Treatment of Missing Data:
@@
 <!-- [Describe criteria you will use to determine whether any observations should be excluded from analysis (e.g., values that are likely data-recording errors, outliers, etc.).] -->
+
+We have no plans to exclude any date.
 
@@
 ```
+
 <!-- [Describe your plan to handle missing data.  How will you deal with incomplete or missing data (e.g., pairwise or listwise deletion, imputation, interpolation)?] -->
@@
 
-<!-- https://www.r-bloggers.com/2021/04/cluster-analysis-in-r/ -->
+This is a descriptive study attempting to characterize the work patterns
+of GSA staff as individuals and as teams. Work patterns will be
+categorized by a rules-based approach and a supervised machine learning
+approach called k-means clustering.
 
-<!-- https://www.guru99.com/r-k-means-clustering.html -->
+For the rules based approach, the portion of working days remote will be
+the key variable to determine what category a staff or team will be in.
+Staff will be grouped as follows:
+
+1.  **All remote** - Staff who work remotely above the 95th percentile
+    <!-- could be 75th -->
+2.  **Mostly remote** - Staff who work remotely between the median and
+    the 95th percentile <!-- could be 75th -->
+3.  **Mostly onsite** - Staff who work remotely between 5th percentile
+    and the median <!-- could be 25th -->
+4.  **All onsite** - Staff who work remotely below the 5th percentile
+    <!-- could be 75th -->
+
+Teams will be categorized similarly:
+
+1.  **All remote** - Teams that work remotely above the 95th percentile
+    <!-- could be 75th -->
+2.  **Mostly remote** - Teams that work remotely between the median and
+    the 95th percentile <!-- could be 75th -->
+3.  **Mostly onsite** - Teams that work remotely between 5th percentile
+    and the median <!-- could be 25th -->
+4.  **All onsite** - Teams that work remotely below the 5th percentile
+    <!-- could be 75th -->
+
+For the second categorization, a k-means clustering algorithm will be
+used. We follow the methods layed out in:
+
+-   [Cluster Analysis in
+    R](https://www.r-bloggers.com/2021/04/cluster-analysis-in-r/)
+
+-   [K-means Clustering in R with
+    Example](https://www.guru99.com/r-k-means-clustering.html)
+
+-   [K-means clustering with tidy data
+    principles](https://www.tidymodels.org/learn/statistics/k-means/)
+
+For staff clusters, the following variables will be used to define the
+clusters:
+
+-   Proportion of days onsite
+
+-   Proportion of days remote
+
+-   Proportion of days remote by the day of the week
+
+-   Correlation of work status between days of the week
+
+-   Number of working days
+
+-   Average size of team over observation window
+
+For team clusters, the following variables will be used:
+
+-   Averages size of team over observation window
+
+-   Proportion of staff working days onsite
+
+-   Proportion of staff working days remote
+
+-   Proportion of staff working days remote by the day of the week
+
+-   Proportion of days of staff concurrent remote status
+
+-   Proportion of days of staff concurrent onsite status
+
+-   Proportion of staff exiting team
+
+-   Number of staff working days
+
+All of the these variables will be scaled to reduce the effects of
+outliers should they be present.
+
+To determine the number appropriate number of clusters, several methods
+exist. A rule of thumb to identify the correct number us to use
+
+$$
+\frac{\sqrt{NumberOfObservations}}{2}
+$$
 

### 2023-02-06 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Adding more details to the study design and descriptive statistics

@@
 library(flextable)
+library(tidymodels)
+library(ggthemes)
 ```
@@
 
-### Table 1. GSA Daily Check-In Data Variables Available Feb 2022-Dec 2022.
+#### Table 1. GSA Daily Check-In Data Variables Available Feb 2022-Dec 2022.
 
@@
 
-### Table 2. GSA Roster Variables.
+#### Table 2. GSA Roster Variables.
 
@@
 
-We have no plans to exclude any date.
+We have no plans to exclude any data.
 
@@
 To determine the number appropriate number of clusters, several methods
-exist. A rule of thumb to identify the correct number us to use
+exist. A rule of thumb to identify the correct number is to use the
+number calculated from:
 
@@
 $$
+
+However, for this work, the *elbow method* will be used. To do this, the
+k-means algorithm will be executed for different numbers of clusters
+from 1 to 20. For each number of clusters, a total within sum of squares
+will be calculated. As the number of number of clusters increases the
+total within sum of squares will decrease. The optimal number of
+clusters is when the decrease in total within sum of squares starts
+tapering off.
+
+The figure below shows an example of the this. The total within sum of
+squares decreases with the number of clusters. In this example, three
+clusters appears to be the point where the returns to more cluster
+diminishes.
+
+#### Figure 1. Elbow method example
+
+```{r}
+set.seed(27)
+
+centers <- tibble(
+  cluster = factor(1:3), 
+  num_points = c(100, 150, 50),  # number points in each cluster
+  x1 = c(5, 0, -3),              # x1 coordinate of cluster center
+  x2 = c(-1, 1, -2)              # x2 coordinate of cluster center
+)
+
+labelled_points <- 
+  centers %>%
+  mutate(
+    x1 = map2(num_points, x1, rnorm),
+    x2 = map2(num_points, x2, rnorm)
+  ) %>% 
+  select(-num_points) %>% 
+  unnest(cols = c(x1, x2))
+
+points <- 
+  labelled_points %>% 
+  select(-cluster)
+
+kclusts <- 
+  tibble(k = 1:20) %>%
+  mutate(
+    kclust = map(k, ~kmeans(points, .x)),
+    tidied = map(kclust, tidy),
+    glanced = map(kclust, glance),
+    augmented = map(kclust, augment, points)
+  )
+
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+ggplot(clusterings, aes(k, tot.withinss)) +
+  geom_line() +
+  geom_point() +
+  theme_minimal()
+
+```
+
+After the optimal number of clusters is determine, the clusters from
+that iteration will be used to categorized the staff and team occupancy.
+
+The work pattern statistics described below will be used to
+characterized the clusters defined by the k-means algorithm.
 
@@
 If you are taking into account practical significance, please specify a minimum effect size of interest.] -->
+
+This is descriptive work and we will not be making any causal claims.
 
@@
 
-Proportion in staff time telework
+The principle work pattern statistics are as follows:
 
-Proportion in staff time telework by the day of the week
+-   Staff work pattern statistics:
 
-Proportion in staff time onsite
+    -   Proportion in staff time telework
 
-Proportion in staff time onsite by the day of the week
+    -   Proportion in staff time telework by the day of the week
 
-Correlations of by staff time between the days of the week
+    -   Proportion in staff time onsite
 
-Size of teams
+    -   Proportion in staff time onsite by the day of the week
+
+    -   Correlations of by staff time between the days of the week
+
+    -   Size of teams
+
+    -   Number of working days
+
+    -   Number exiting employment
+
+    -   Number changing supervisors
+
+-   Team work pattern statistics:
+
+    -   Proportion in staff time telework
+
+    -   Proportion in staff time onsite
+
+    -   Proportion of concurrent remote days for team members
+
+    -   Proportion of concurrent onsite days for team members
+
+    -   Size of teams
+
+    -   Number of staff working days
+
+The descriptive statistics are:
+
+-   Staff descriptive statistics
+
+    -   Number and proportion of staff by grade
+
+    -   Number and proportion of staff by occupational series
+
+    -   Number and proportion of staff by position category
+
+    -   Number and proportion of staff by GSA region
+
+    -   Number and proportion of staff by SSO
+
+    -   Number and proportion of staff by state
+
+    -   Number and proportion of staff by city
+
+    -   Number and proportion of staff by supervisor level
+
+-   Team descriptive statistics
+
+    -   Number and proportion of staff by most frequent grade
+
+    -   Number and proportion of staff by most frequent occupational series
+
+    -   Number and proportion of staff by most frequent position category
+
+    -   Number and proportion of staff by most frequent GSA region
+
+    -   Number and proportion of staff by most frequent SSO
+
+    -   Number and proportion of staff by most frequent state
+
+    -   Number and proportion of staff by most frequent city
+
+    -   Number and proportion of staff by most frequent supervisor level
 

### 2023-02-08 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Adding more detail to the study design, and last few sections, added table names and numbers throughout document

@@
 
-# Analysis Plan
+```{r}
+table_n <- 0
+```
 
@@
 We will merge in additional variables from the GSA Roster obtained from
-D2D. The GSA roster is updated monthly at the end of each month. [We
-currently have Nov 2022 and Dec 2022 updates; I will try to track down
-past months. Ideally, we will merge in each monthly check-in file with
-the preceding month's roster file.]
+D2D. The GSA roster is updated monthly at the end of each month. 
+<!-- [We currently have Nov 2022 and Dec 2022 updates; I will try to track down -->
+<!-- past months. Ideally, we will merge in each monthly check-in file with -->
+<!-- the preceding month's roster file.] -->
 
-#### Table 1. GSA Daily Check-In Data Variables Available Feb 2022-Dec 2022.
+```{r}
+table_n <- table_n + 1
+```
+
+#### Table `r table_n`. GSA Daily Check-In Data Variables Available Feb 2022-Dec 2022.
 
@@
 
-#### Table 2. GSA Roster Variables.
+```{r}
+table_n <- table_n + 1
+```
+
+#### Table `r table_n`. GSA Roster Variables.
 
@@
 the supervisors of groups of staff in the beginning of March 2022. Any
-analysis will conduct may be reproduced on a separate cohort or may be
+analysis we conduct may be reproduced on a separate cohort or may be
 combined with multiple cohorts depending on the data availability.
@@
 
-The analysis will be done for staff and teams separately
+The analysis will be done for staff and teams separately and aggregated independently. The table below defines how we plan to aggregate for staff and teams.
+
+```{r}
+table_n <- table_n + 1
+```
+
+#### Table `r table_n`. Level of analysis and aggregation
 
@@
                       Group = c("Staff", "Team"),
-                      Cluster = c("Person level aggregation of work status", "Team level aggregation of work status"),
+                      Aggregation = c("Person level aggregation of work status", "Team level aggregation of work status"),
                       # Sequence = c("Daily person work status", "Daily team work status")
@@
 
-Missing data from daily check in will be treated as follows:
+Missing data from daily check in will be treated as defined in the table below.
+
+```{r}
+table_n <- table_n + 1
+```
+
+#### Table `r table_n`. Treatment of missing data from daily check in
 
@@
 
-Missing data from the roster will be treated as follows:
+Missing data from the roster will be treated as show in the table below.
+
+```{r}
+table_n <- table_n + 1
+```
+
+#### Table `r table_n`. Treatment of missing data from roster
 
@@
 clusters appears to be the point where the returns to more cluster
-diminishes.
+diminishes. We will also construct silhouette charts to confirm the number of clusters.
 
@@
 If any statistics, tables, or graphs  are listed that will not be included in the MSG abstract or reported to the agency partner, then explicitly identify these in order to streamline reanalysis.] -->
+
+This work will address the following research questions: 1. What are the
+rates of telework since the federal return-to-office transition? 2. Do
+telework behaviors match position category (e.g., onsite, offsite, etc.)
+in the roster? 3. At what rates to teams work together onsite vs.
+remotely? 4. Do the telework patterns of supervisors match the telework
+patterns of supervisees?
 
@@
 
+The staff statistics will be calculated for the following groups:
+
+1.    Whole cohort of staff
+2.    By rule-based categories of work pattern
+3.    By cluster defined categories of work pattern
+
+The team statistics will be calculated for the following groups:
+
+1.    Whole cohort of teams
+2.    By rule-based categories of work pattern
+3.    By cluster defined categories of work pattern
+
+Another set of statistics will be designed to understand the relationship between staff work patterns and their supervisor.
+We will calculate  the proportion of the staff that fall into the same rule-based and clusters as their supervisors overall as well as by those categories.
+
+These statistics will be presented in tables.
+Visualizations will be created for a subset to help communicated results.
+Charts of the work pattern data will be created to confirm and characterize the groupings.
+In addition, charts showing difference by stated telework position category.
+
 ### Confirmatory Analyses:
@@
 
+We plan no confirmatory analyses.
+
 ### Exploratory Analysis:
@@
 Note that exploratory analyses will not, by default, be included in reanalysis.] -->
+
+We plan no exploratory analyses. Though, all this work may be considered exploratory.
 
@@
 
+We will not be making any inference.
+
 ### Limitations:
@@
 <!-- [Describe any anticipated limitations associated with this analysis, if not previously identified in the Project Design document.] -->
+
+This is non causal research.
+The work will not demonstrate if changes or attributes caused differences, only if there are relationships.
+K-means clustering can be sensetive to the random locations of the first points selected to calculate differences and define clusters.

### 2023-02-09 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd

@@
 
-Another set of statistics will be designed to understand the relationship between staff work patterns and their supervisor.
-We will calculate  the proportion of the staff that fall into the same rule-based and clusters as their supervisors overall as well as by those categories.
+To understand the relationship between staff work patterns and their supervisor, we will calculate the proportion of the staff that fall into the same rule-based and clusters as their supervisors overall, as well as by the above categories.
 
-These statistics will be presented in tables.
-Visualizations will be created for a subset to help communicated results.
-Charts of the work pattern data will be created to confirm and characterize the groupings.
-In addition, charts showing difference by stated telework position category.
+The results will be presented in tables, and we will generate visualizations for a subset of the results for streamlined communication.
+We will use visualizations to validate the work pattern groupings and demonstrate any deviation between clusters, rules-based categories, and stated telework position.
 

### 2023-02-09 02. Design/MSG-P2312-Analysis Plan-2-sequence.rmd
Update MSG-P2312-Analysis Plan-2-sequence.rmd

@@
 We will merge in additional variables from the GSA Roster obtained from
-D2D. The GSA roster is updated monthly at the end of each month. [We
-currently have Nov 2022 and Dec 2022 updates; I will try to track down
-past months. Ideally, we will merge in each monthly check-in file with
-the preceding month's roster file.]
+D2D. The GSA roster is updated monthly at the end of each month.
 
@@
 For cluster analysis of staff work status, the data will be transformed
-so that each row is one staff person. From the raw data, the following
+so that each row is one employee. From the raw data, the following
 variables will be defined:

### 2023-02-09 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd

@@
 D2D. The GSA roster is updated monthly at the end of each month.
-<!-- [We currently have Nov 2022 and Dec 2022 updates; I will try to track down -->
-<!-- past months. Ideally, we will merge in each monthly check-in file with -->
-<!-- the preceding month's roster file.] -->
 
@@
 
+<!-- [I might be more discerning about using "staff" vs. "employees" vs. "teams" vs. "groups" vs. "clusters" -- we are grouping employees into teams, but also categorizing them.]  -->
 We will approach grouping staff and teams in two ways. First,

### 2023-02-13 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd

@@
   project_name: "Occupancy Patterns"
-  analysis_plan_title: "Phase 2 - Clusters"
+  analysis_plan_title: "Phase 1 - Clusters"
 editor_options: 

### 2023-02-15 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Add definition of SSO

@@
   # Is SSO single sign on? What did we decide?
-"",
+"GSA offices",
 "2-digit department id",

### 2023-02-15 04. Analysis/scripts/01-data-preparation-joas.Rmd
Adding other examples

---
title: "Data preparation - JOAs"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: readable
    highlight: tango
    code_folding: hide
params:
  author: "Sam Kim and Ben Jaques-Leslie"
  project_number: "001"
  project_name: "Remote Work"
  data_folder_1: "03. Data Collection/Original data files from Melissa/JOAs"
  unique_identifier_1: !r c("usajobs_control_number")
  date_earliest_open: '2022-01-01'
  data_latest_close: '2022-12-01'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
tictoc::tic()
library(Hmisc)
library(tidyverse)
library(janitor)
library(skimr)
library(DataExplorer)
library(readr)
library(data.table)
library(lubridate)
library(arsenal)
```

# {.tabset .tabset-pills}

**Project number**: `r params$project_number`

**Project name**: `r params$project_name`

**Author**: `r params$author`

**Data folder 1**: `r params$data_folder`

**Unique identifier for data folder 1**: `r params$unique_identifier_1`

## Load data {.tabset .tabset-pills}

### Data files

The file names below represent all original candidate data files from Melissa.

```{r}
files <- 
  tibble(files = list.files(here::here(params$data_folder_1))
)

files
```

### Function to identify the encoding of the data files.

```{r}
encoding_data_frame <- function(in_file_name)
{
  readr::guess_encoding(here::here(params$data_folder_1,in_file_name)) %>% 
        mutate(file = in_file_name) %>% 
        select(file, everything())
}
```

### Identifying file encoding

Identify the encoding the candidates data files.

```{r}
files <- 
  files %>% 
  pull() %>% 
  map_dfr(~encoding_data_frame(.))

files
```

Filter candidate files to those with greatest confidence in the encoding.

```{r}
files <- 
  files %>% 
  group_by(file) %>% 
  filter(confidence == max(confidence))

files
```

### Functions

#### Function to load UTF-8 candidate files

```{r}
load_utf8 <- function(in_file_name, in_col_names)
{
  prep_01 <-
    fread(
      here::here(params$data_folder_1,in_file_name)
    ) %>% 
      distinct()

  return(prep_01)
}
```

#### Function to load UTF-16 candidate files

```{r}
load_utf16 <- function(in_file_name)
{
  prep_01 <- read.csv(
    file = here::here(params$data_folder_1,in_file_name),
    fileEncoding = "UTF-16",
    sep = "\t"
    )

  return(prep_01)
}
```

#### Function to prepare JOA info data.

```{r}
prepare_joa <- function(in_data)
{
prep_02 <- 
  in_data %>% 
  clean_names()

prep_03 <-
  prep_02 %>%
  select(everything())

if("announcement_closing_type" %in% names(prep_03))
{
  prep_04 <-
  prep_03 %>%
  mutate(
    across(
      .cols = c(position_open_date,position_close_date),
      .fns = ~ymd(.)
    )
  ) %>% 
  mutate(
    across(
      .cols = c(usajobs_control_number,announcement_closing_type,agency_level,hiring_department_code,series),
      .fns = ~as.character(.)
    )
  ) %>% 
  mutate(
    across(
      .cols = c(hiring_agency_code,total_openings),
      .fns = ~str_trim(.)
    )
  ) %>% 
  mutate(
    across(
      .cols = c(total_openings),
      .fns = ~as.numeric(.)
    )
  )
}

if(!("announcement_closing_type" %in% names(prep_03)) &
   !("agency_level" %in% names(prep_03)) &
   !("hiring_department_code" %in% names(prep_03)) &
   !("hiring_agency_code" %in% names(prep_03)) 
     )
{
  prep_04 <-
  prep_03 %>%
  mutate(
    across(
      .cols = c(position_open_date,position_close_date),
      .fns = ~ymd(.)
    )
  ) %>% 
  mutate(
    across(
      .cols = c(usajobs_control_number,
                # announcement_closing_type,
                # agency_level,
                # hiring_department_code,
                series),
      .fns = ~as.character(.)
    )
  ) %>% 
  mutate(
    across(
      .cols = c(
        # hiring_agency_code,
        total_openings),
      .fns = ~str_trim(.)
    )
  ) %>% 
  mutate(
    across(
      .cols = c(total_openings),
      .fns = ~as.numeric(.)
    )
  )
}

  #   position_open_date = ymd(position_open_date),
  #   position_close_date = ymd(position_close_date),
  #   usajobs_control_number = as.character(usajobs_control_number),
  #   race = str_remove(race, " - .*"),
  #   race = case_when(race == "" ~ "Did not disclose race",
  #                    is.na(race) ~ "Did not disclose race",
  #                    TRUE ~ race),
  #   degree_level = str_remove(degree_level, " \\(.*"),
  #   degree_level = case_when(degree_level == "" ~ "Did not disclose degree",
  #                    TRUE ~ degree_level),
  #   federal_employment_status =
  #     case_when(
  #       str_detect(
  #         federal_employment_status,"former") ~ "Former",
  #       str_detect(
  #         federal_employment_status,"currently") ~ "Current",
  #       str_detect(
  #         federal_employment_status,"never") ~ "Non-Federal employee"
  #       )
  # )
# 
# prep_05 <- 
#   prep_04 %>% 
#   select(candidate_id,race) %>% 
#   distinct() %>%
#   mutate(ind = 1) %>% 
#   pivot_wider(names_from = race, values_from = ind) %>% 
#   clean_names() %>% 
#   mutate(
#     across(
#       .cols = where(is.numeric),
#       .fns = ~replace_na(.,0)
#     )
#   )
# 
# prep_06 <-
#   prep_04 %>% 
#   select(candidate_id,degree_level) %>% 
#   distinct() %>% 
#   mutate(ind = 1) %>% 
#   pivot_wider(names_from = degree_level, values_from = ind) %>% 
#   clean_names() %>% 
#   mutate(
#     across(
#       .cols = where(is.numeric),
#       .fns = ~replace_na(.,0)
#     )
#   )
# 
# prep_07 <- 
#   prep_04 %>% 
#   select(-race,-degree_level) %>% 
#   distinct()
# 
# prep_08 <- 
#   prep_05 %>% 
#   left_join(prep_06) %>% 
#   left_join(prep_07)

return(prep_04)
}
```

#### Function to prepare JOA info data.

```{r}
prepare_joa_telework <- function(in_data)
{
prep_02 <- 
  in_data %>% 
  clean_names()

prep_03 <-
  prep_02 %>%
  select(everything())

if("is_tele_work_eligible" %in% names(prep_03))
{
  prep_04 <-
  prep_03 %>%
    rename(telework_eligible = is_tele_work_eligible)
}

if(!("is_tele_work_eligible" %in% names(prep_03)))
{
  prep_04 <-
  prep_03
}

prep_05 <- 
  prep_04 %>% 
  select(usajobs_control_number,telework_eligible) %>% 
  mutate(
    across(
      .cols = c(usajobs_control_number,
               ),
      .fns = ~as.character(.)
    )
  ) %>%
  mutate(
    across(
      .cols = c(telework_eligible),
      .fns = ~as.numeric(.)
    )
  )
# 
# if(!("announcement_closing_type" %in% names(prep_03)) &
#    !("agency_level" %in% names(prep_03)) &
#    !("hiring_department_code" %in% names(prep_03)) &
#    !("hiring_agency_code" %in% names(prep_03)) 
#      )
# {
#   prep_04 <-
#   prep_03 %>%
#   mutate(
#     across(
#       .cols = c(position_open_date,position_close_date),
#       .fns = ~ymd(.)
#     )
#   ) %>% 
#   mutate(
#     across(
#       .cols = c(usajobs_control_number,
#                 # announcement_closing_type,
#                 # agency_level,
#                 # hiring_department_code,
#                 series),
#       .fns = ~as.character(.)
#     )
#   ) %>% 
#   mutate(
#     across(
#       .cols = c(
#         # hiring_agency_code,
#         total_openings),
#       .fns = ~str_trim(.)
#     )
#   ) %>% 
#   mutate(
#     across(
#       .cols = c(total_openings),
#       .fns = ~as.numeric(.)
#     )
#   )
# }

  #   position_open_date = ymd(position_open_date),
  #   position_close_date = ymd(position_close_date),
  #   usajobs_control_number = as.character(usajobs_control_number),
  #   race = str_remove(race, " - .*"),
  #   race = case_when(race == "" ~ "Did not disclose race",
  #                    is.na(race) ~ "Did not disclose race",
  #                    TRUE ~ race),
  #   degree_level = str_remove(degree_level, " \\(.*"),
  #   degree_level = case_when(degree_level == "" ~ "Did not disclose degree",
  #                    TRUE ~ degree_level),
  #   federal_employment_status =
  #     case_when(
  #       str_detect(
  #         federal_employment_status,"former") ~ "Former",
  #       str_detect(
  #         federal_employment_status,"currently") ~ "Current",
  #       str_detect(
  #         federal_employment_status,"never") ~ "Non-Federal employee"
  #       )
  # )
# 
# prep_05 <- 
#   prep_04 %>% 
#   select(candidate_id,race) %>% 
#   distinct() %>%
#   mutate(ind = 1) %>% 
#   pivot_wider(names_from = race, values_from = ind) %>% 
#   clean_names() %>% 
#   mutate(
#     across(
#       .cols = where(is.numeric),
#       .fns = ~replace_na(.,0)
#     )
#   )
# 
# prep_06 <-
#   prep_04 %>% 
#   select(candidate_id,degree_level) %>% 
#   distinct() %>% 
#   mutate(ind = 1) %>% 
#   pivot_wider(names_from = degree_level, values_from = ind) %>% 
#   clean_names() %>% 
#   mutate(
#     across(
#       .cols = where(is.numeric),
#       .fns = ~replace_na(.,0)
#     )
#   )
# 
# prep_07 <- 
#   prep_04 %>% 
#   select(-race,-degree_level) %>% 
#   distinct()
# 
# prep_08 <- 
#   prep_05 %>% 
#   left_join(prep_06) %>% 
#   left_join(prep_07)

return(prep_05)
}
```

#### Function to load and prepare JOA information

```{r}
load_prepare_joa <- function(in_file_name,in_encoding)
{
  if(in_encoding == 'ASCII')
  {
    prep_01 <- in_file_name %>% 
  load_utf8()
  }

  if(in_encoding == 'UTF-16LE')
  {
    prep_01 <- in_file_name %>% 
  load_utf16()
  }

  out <- prep_01 %>% 
  prepare_joa()

  return(out)

}
```

#### Function to load and prepare JOA telework information

```{r}
load_prepare_joa_telework <- function(in_file_name,in_encoding)
{
  if(in_encoding == 'ASCII')
  {
    prep_01 <- in_file_name %>% 
  load_utf8()
  }

  if(in_encoding == 'UTF-16LE')
  {
    prep_01 <- in_file_name %>% 
  load_utf16()
  }

  out <- prep_01 %>% 
  prepare_joa_telework()

  return(out)

}
```

#### Function to convert character to indicator

```{r}
character_to_indicator <- function(in_data,in_unique_identifier,in_variable,in_prefix)
{
  in_data %>% 
  select(all_of(in_unique_identifier),{{in_variable}}) %>% 
    distinct() %>% 
    mutate(ind = 1) %>% 
    mutate(across(
      .cols = {{in_variable}},
      .fns = ~case_when(. == "" ~ "missing",
                       TRUE ~ .)
    )) %>% 
    pivot_wider(names_from = {{in_variable}},
                values_from = ind) %>% 
    rename_with(
      .fn = ~glue::glue("{in_prefix} {.}"),
  .cols = -in_unique_identifier
  ) %>% 
    clean_names() %>% 
    mutate(
      across(
        .cols = where(is.numeric),
        .fns = ~replace_na(.,0)
      )
    )
}
```

### JOA data

#### Identify files with "full" in title or "Positions_Updated_Dec2022"

```{r}
files_full <- 
  files %>% 
  filter(str_detect(file,"_full_") | str_detect(file,"Positions_Updated_Dec2022")) %>%
  select(file,encoding)

files_full
```

#### Load 'full' files

```{r}
prep_base <- 
  map2_dfr(
    .x = files_full$file,
    .y = files_full$encoding,
    .f = ~load_prepare_joa(in_file_name = .x, in_encoding = .y)
  ) %>% 
  distinct()
```

#### Identify files with "remote_telework_positions" in title or "telework_eligible_from_09092022"

```{r}
files_telework <- 
  files %>% 
  filter(str_detect(file,"remote_telework_positions") | str_detect(file,"telework_eligible_from_09092022")) %>%
  select(file,encoding)

files_telework
```

#### Load 'telework' files

```{r}
prep_telework <- 
  map2_dfr(
    .x = files_telework$file,
    .y = files_telework$encoding,
    .f = ~load_prepare_joa_telework(in_file_name = .x, in_encoding = .y)
  ) %>% 
  distinct()
```

```{r}
prep_telework %>% 
  skim()
```

## Filter to correct dates

```{r}
prep_base <- 
  prep_base %>% 
  filter(position_open_date >= ymd(params$date_earliest_open) &
           position_close_date <= ymd(params$data_latest_close))

```

#### Review data

```{r}
prep_base %>%
  skim()
```

## Addressing duplication

Melissa recommended using `r params$unique_identifier_1` as the unique identifier.

To review specific cases you to https://www.usajobs.gov/job/ and put the USAJobs control number at the end.

### Check for duplication

```{r}
dupe_01 <- 
  prep_base %>%
  get_dupes(params$unique_identifier_1)
```

#### Data review

```{r}
dupe_01 %>% 
  skim()
```

### Dataframe of the unique identifier

```{r}
prep_uniq <- 
  prep_base %>% 
  select(params$unique_identifier_1) %>% 
  distinct()

prep_uniq %>% 
  count()
```

### Identifying and categorizing columns

Created a dataframe of variable metadata

```{r}
column_meta_data <- 
  prep_base %>% 
  contents()

column_meta_data <- 
  column_meta_data$contents %>% 
  as.data.frame()

column_meta_data <-
  column_meta_data %>% 
  rownames_to_column(var = "variable")

column_meta_data
```

Function that checks whether there are duplicates for different variables

```{r}
dupe_check <- function(in_data,in_variable_name)
{
  check_01 <- 
  in_data %>% 
  select(params$unique_identifier_1,all_of(in_variable_name)) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)

out <- nrow(check_01) > 0

return(out)
}
```

Checking duplicates for each variable in the dataframe.

```{r}
duplicates_by_variable <- 
  column_meta_data %>% 
  pull(variable) %>% 
  map_lgl(~dupe_check(in_data = dupe_01, .))

duplicates_by_variable
```

Add this to the column_meta_data dataframe.

```{r}
column_meta_data <- 
  column_meta_data %>% 
  add_column(
    duplicates_by_variable = duplicates_by_variable
  )

column_meta_data
```

Create dataframe of only variables that cause duplicates.

```{r}
duplicating_variables <- 
  column_meta_data %>% 
  filter(duplicates_by_variable)

duplicating_variables
```

Grouping variables.

```{r}
duplicating_variables <- 
  duplicating_variables %>% 
  mutate(group = 
           case_when(variable == "position_open_date" ~ "dates",
                     variable == "position_close_date" ~ "dates",
                     variable == "announcement_closing_type" ~ "announcement_closing_type",
                     variable == "announcement_closing_type_description" ~ "announcement_closing_type",
                     variable == "application_limit" ~ "application_limit",
                     variable == "application_limit_set" ~ "application_limit",
                     variable == "agency_level" ~ "agency_level",
                     variable == "agency_level_sort" ~ "agency_level",
                     variable == "hiring_agency_code" ~ "agency_level",
                     variable == "hiring_agency_name" ~ "agency_level",
                     variable == "hiring_department_code" ~ "agency_level",
                     variable == "hiring_department_name" ~ "agency_level",
                     variable == "maximum_salary" ~ "maximum_salary",
                     variable == "minimum_salary" ~ "maximum_salary",
                     variable == "maximum_grade" ~ "maximum_salary",
                     variable == "minimum_grade" ~ "maximum_salary",
                     variable == "series" ~ "series",
                     variable == "series_title" ~ "series",
                     TRUE ~ variable
                     ))

duplicating_variables
```

Create list of groups.

```{r}
duplicating_groups <- 
  duplicating_variables %>% 
  select(group) %>% 
  distinct() %>% 
  pull()

duplicating_groups
```

### Duplication removal

```{r}
step_n <- 0
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

Reviewing duplicates.

```{r}
dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)
```

Some of these duplicates may be due to small typos. Transforming the string to upper case.

```{r}
dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  mutate(
    announcement_number = str_to_upper(announcement_number)
  ) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)
```

This fixes some, but not all.

Without better information, we will take the lower of the two values for the remainder.

```{r}
dedupe <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  mutate(
    announcement_number = str_to_upper(announcement_number)
  ) %>% 
  distinct() %>% 
  arrange(params$unique_identifier_1,announcement_number) %>% 
  group_by_at(params$unique_identifier_1) %>% 
  summarise(announcement_number = first(announcement_number))

dedupe %>% 
  get_dupes(params$unique_identifier_1)
```

Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.

First create a dataframe of distinct rows of the variables from the original data.

```{r}
working_01 <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct()

working_01 %>% 
  glimpse()

working_01 %>% 
  skim()
```

Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.

```{r}
working_02 <- 
  working_01 %>% 
  anti_join(dedupe %>% select(params$unique_identifier_1))

working_02 %>% 
  glimpse()

working_02 %>% 
  skim()
```

Last bind this dataframe to the deduplicated set above.

```{r}
prep_xx <- 
  working_02 %>% 
  bind_rows(dedupe)

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Rename dataframe and count rows.

```{r}
prep_01 <- prep_xx

prep_01 %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_01 %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

Reviewing duplicates.

```{r}
dupe_02 <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)

dupe_02
```

Duplication appear to be because of difference in open and close dates. After messaging with Melissa, we decide to retain the later dates as determined by the close date.

```{r}
dedupe <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>%
  arrange(params$unique_identifier_1, position_close_date) %>% 
  group_by(usajobs_control_number) %>% 
  summarise(
    across(
      .cols = all_of(duplicating_group %>% pull(variable)),
      .fns = last
    )
  )

dedupe %>% 
  get_dupes(params$unique_identifier_1)
```

Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.

First create a dataframe of distinct rows of the variables from the original data.

```{r}
working_01 <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct()

working_01 %>% 
  glimpse()

working_01 %>% 
  skim()
```

Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.

```{r}
working_02 <- 
  working_01 %>% 
  anti_join(dedupe %>% select(params$unique_identifier_1))

working_02 %>% 
  glimpse()

working_02 %>% 
  skim()
```

Last bind this dataframe to the deduplicated set above.

```{r}
prep_xx <- 
  working_02 %>% 
  bind_rows(dedupe)

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe

```{r}
prep_02 <- prep_xx
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

Reviewing duplicates.

```{r}
dupe_02 <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)

dupe_02
```

Duplication appear to be because `r duplicating_group %>% pull(variable)` is empty in one row. Transform the empties into 'N'.

We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.

```{r}
prep_xx <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  mutate(
    is_remote_work_eligible = case_when(is_remote_work_eligible == "" ~ "N",
                                        TRUE ~ is_remote_work_eligible)
  ) %>% 
  distinct() %>% 
  character_to_indicator(in_unique_identifier = params$unique_identifier_1,
                         in_variable = is_remote_work_eligible,
                         in_prefix = "is_remote_work_eligible") %>% 
  # Drop the "n" indicatoris_remote_work_eligible
  select(-is_remote_work_eligible_n)

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe

```{r}
prep_03 <- prep_xx
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

Reviewing duplicates.

```{r}
dupe_02 <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)

dupe_02
```

Check to see if the type codes are consistent to the description.

```{r}
prep_base %>% 
  count(announcement_closing_type,announcement_closing_type_description)
```

Codes are consistent to description, but the code adds no new information. We will drop the code and transform the description into columns of indicators.

We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.

```{r}
prep_xx <- 
  prep_base %>% 
  character_to_indicator(params$unique_identifier_1,announcement_closing_type_description,"closing_type")

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Rename dataframe and count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe

```{r}
prep_04 <- prep_xx

```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

Reviewing duplicates.

```{r}
dupe_02 <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)

dupe_02
```

Announcements have multiple open statuses.

First count the statuses across the original data.

```{r}
prep_base %>% count(position_opening_status)
```

Not too many of them. Like above, we will transform these into indicator columns.

We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.

```{r}
prep_xx <- 
  prep_base %>% 
  character_to_indicator(params$unique_identifier_1,position_opening_status,"position_opening_status")

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```
Rename dataframe

```{r}
prep_05 <- prep_xx

```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

Reviewing duplicates.

```{r}
dupe_02 <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)

dupe_02
```

Not too many. It appears that `application_limit_set` is "N" when `application_limit` is "Applicant Cut-Off".

First count the statuses across the original data.

```{r}
prep_base %>% count(application_limit,application_limit_set)
```

All NA `application_limit` are "N" `application_limit_set`.

We will consider "Y" the correct response for all and we will change this into an indicator.

We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.

```{r}
prep_xx <- 
  prep_base %>% 
  character_to_indicator(params$unique_identifier_1,application_limit_set,"application_limit_set") %>% 
  # Drop the "N" column
  select(-application_limit_set_n)

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe

```{r}
prep_06 <- prep_xx
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

Reviewing duplicates.

```{r}
dupe_02 <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)

dupe_02
```

Not too many. It appears that `work_schedule` might have different.

First count the statuses across the original data.

```{r}
prep_base %>% count(work_schedule)
```

There are just a few, but we'll want to transform these into indicators.

We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.

```{r}
prep_xx <- 
  prep_base %>% 
  character_to_indicator(params$unique_identifier_1,work_schedule,"work_schedule")

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe

```{r}
prep_07 <- prep_xx
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

Reviewing duplicates.

```{r}
dupe_02 <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)

dupe_02
```

Not too many. It appears that `disable_apply_online` might have different.

First count the statuses across the original data.

```{r}
prep_base %>% count(disable_apply_online)
```

There are just a few, but we'll want to transform these into indicators.

We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.

Since there is only one instance of this type of duplication, we will still drop the no column.

```{r}
prep_xx <- 
  prep_base %>% 
  character_to_indicator(params$unique_identifier_1,disable_apply_online,"disable_apply_online") %>% 
  # Drop the "N" column
  select(-disable_apply_online_n)

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe

```{r}
prep_08 <- prep_xx
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

Reviewing duplicates.

```{r}
dupe_02 <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)

dupe_02
```

Not too many.

First count the statuses across the original data.

```{r}
prep_base %>% count(appointment_type)
```

There are just a few, but we'll want to transform these into indicators.

We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.

Since there is only one instance of this type of duplication, we will still drop the no column.

```{r}
prep_xx <- 
  prep_base %>% 
  character_to_indicator(params$unique_identifier_1,appointment_type,"appointment_type")

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe

```{r}
prep_09 <- prep_xx
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

Reviewing duplicates.

```{r}
dupe_02 <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)

dupe_02
```

A few things going on here:

1.    Department of Defense agencies are duplicated because sometimes sub-departments (e.i. Department of Navy) are considered the *Department*
2.    Many duplicates are caused by blank values in hiring agency code

First let's remove duplicates because of department. To do this, we'll use the maximum agency level to limit to just the entries with the most levels.

```{r}
dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  group_by(usajobs_control_number) %>% 
  filter(agency_level == max(agency_level)) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)
```

We can still see the duplications from blank hiring agency codes. We'll drop those.

```{r}
dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  group_by(usajobs_control_number) %>% 
  filter(agency_level == max(agency_level)) %>% 
  filter(!is.na(hiring_department_code)) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)
```

We still have one duplicate remaining. For this we'll, select the entry with the later position closing date.

```{r}
dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>% 
  group_by(usajobs_control_number) %>% 
  filter(agency_level == max(agency_level)) %>% 
  filter(!is.na(hiring_department_code)) %>% 
  filter(position_close_date == max(position_close_date)) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)
```

Now we will apply all of these to the duplicated rows.

```{r}
dedupe <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>% 
  group_by(usajobs_control_number) %>% 
  filter(agency_level == max(agency_level)) %>% 
  filter(!is.na(hiring_department_code)) %>% 
  filter(position_close_date == max(position_close_date)) %>% 
  distinct() %>% 
  ungroup() %>% 
  select(-position_close_date)

dedupe %>% 
  get_dupes(params$unique_identifier_1)
```

Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.

First create a dataframe of distinct rows of the variables from the original data.

```{r}
working_01 <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct()

working_01 %>% 
  glimpse()

working_01 %>% 
  skim()
```

Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.

```{r}
working_02 <- 
  working_01 %>% 
  anti_join(dedupe %>% select(params$unique_identifier_1))

working_02 %>% 
  glimpse()

working_02 %>% 
  skim()
```

Last bind this dataframe to the deduplicated set above.

```{r}
prep_xx <- 
  working_02 %>% 
  bind_rows(dedupe)

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe

```{r}
prep_10 <- prep_xx
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

Reviewing duplicates.

```{r}
dupe_02 <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)

dupe_02
```

Count types.

```{r}
prep_base %>% 
  count(hiring_subelement_name)
```

Many blank entries and a level of detail we don't need. We will drop this column.

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

Reviewing duplicates.

```{r}
dupe_02 <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)

dupe_02
```

Appears like this comes from posting the job again with revised salary information.

Like above we decide to retain the later dates as determined by the close date.

```{r}
dedupe <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
  arrange(params$unique_identifier_1, position_close_date) %>% 
  group_by(usajobs_control_number) %>% 
  summarise(
    across(
      .cols = all_of(duplicating_group %>% pull(variable)),
      .fns = last
    )
  )

dedupe %>% 
  get_dupes(params$unique_identifier_1)
```

Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.

First create a dataframe of distinct rows of the variables from the original data.

```{r}
working_01 <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct()

working_01 %>% 
  glimpse()

working_01 %>% 
  skim()
```

Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.

```{r}
working_02 <- 
  working_01 %>% 
  anti_join(dedupe %>% select(params$unique_identifier_1))

working_02 %>% 
  glimpse()

working_02 %>% 
  skim()
```

Last bind this dataframe to the deduplicated set above.

```{r}
prep_xx <- 
  working_02 %>% 
  bind_rows(dedupe)

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe

```{r}
prep_11 <- prep_xx
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

Reviewing duplicates.

```{r}
dupe_02 <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)

dupe_02
```
Count types.

```{r}
prep_base %>% 
  count(series, series_title)
```

Many different titles and series.

Check if the series numbers are duplicated.

```{r}
prep_base %>% 
  count(series, series_title) %>% 
  ungroup() %>% 
  get_dupes(series)
```

None.

Now the titles.

```{r}
prep_base %>% 
  count(series, series_title) %>% 
  ungroup() %>% 
  get_dupes(series_title)
```

None.

Since the `series` adds no information and is uniquely matched to the titles, we will drop `series`.

There are too many series to want indicators, we'll use the last closing date to select the appropriate series.

Like above we decide to retain the later dates as determined by the close date.

```{r}
dedupe <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
  arrange(params$unique_identifier_1, position_close_date) %>% 
  group_by(usajobs_control_number) %>% 
  summarise(
    across(
      .cols = all_of(duplicating_group %>% pull(variable)),
      .fns = last
    )
  )

dedupe %>% 
  get_dupes(params$unique_identifier_1)
```

Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.

First create a dataframe of distinct rows of the variables from the original data.

```{r}
working_01 <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct()

working_01 %>% 
  glimpse()

working_01 %>% 
  skim()
```

Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.

```{r}
working_02 <- 
  working_01 %>% 
  anti_join(dedupe %>% select(params$unique_identifier_1))

working_02 %>% 
  glimpse()

working_02 %>% 
  skim()
```

Last bind this dataframe to the deduplicated set above.

```{r}
prep_xx <- 
  working_02 %>% 
  bind_rows(dedupe) %>% 
  select(-series)

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe

```{r}
prep_12 <- prep_xx
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

Reviewing duplicates.

```{r}
dupe_02 <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)

dupe_02
```

Not too many duplicates. We'll follow the same procedure, taking the number from the row wiht the later closing date.

Like above we decide to retain the later dates as determined by the close date.

```{r}
dedupe <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
  arrange(params$unique_identifier_1, position_close_date) %>% 
  group_by(usajobs_control_number) %>% 
  summarise(
    across(
      .cols = all_of(duplicating_group %>% pull(variable)),
      .fns = last
    )
  )

dedupe %>% 
  get_dupes(params$unique_identifier_1)
```

Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.

First create a dataframe of distinct rows of the variables from the original data.

```{r}
working_01 <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct()

working_01 %>% 
  glimpse()

working_01 %>% 
  skim()
```

Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.

```{r}
working_02 <- 
  working_01 %>% 
  anti_join(dedupe %>% select(params$unique_identifier_1))

working_02 %>% 
  glimpse()

working_02 %>% 
  skim()
```

Last bind this dataframe to the deduplicated set above.

```{r}
prep_xx <- 
  working_02 %>% 
  bind_rows(dedupe)

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe

```{r}
prep_13 <- prep_xx
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

Reviewing duplicates.

```{r}
dupe_02 <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct() %>% 
  get_dupes(params$unique_identifier_1)

dupe_02
```

Not too many duplicates.

Like above we decide to retain the later dates as determined by the close date.

```{r}
dedupe <- 
  dupe_01 %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
  arrange(params$unique_identifier_1, position_close_date) %>% 
  group_by(usajobs_control_number) %>% 
  summarise(
    across(
      .cols = all_of(duplicating_group %>% pull(variable)),
      .fns = last
    )
  )

dedupe %>% 
  get_dupes(params$unique_identifier_1)
```

Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.

First create a dataframe of distinct rows of the variables from the original data.

```{r}
working_01 <- 
  prep_base %>% 
  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
  distinct()

working_01 %>% 
  glimpse()

working_01 %>% 
  skim()
```

Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.

```{r}
working_02 <- 
  working_01 %>% 
  anti_join(dedupe %>% select(params$unique_identifier_1))

working_02 %>% 
  glimpse()

working_02 %>% 
  skim()
```

Last bind this dataframe to the deduplicated set above.

```{r}
prep_xx <- 
  working_02 %>% 
  bind_rows(dedupe)

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe

```{r}
prep_14 <- prep_xx
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing duplicates produced by:

```{r}
duplicating_group <- 
  duplicating_variables %>% 
  filter(group == duplicating_groups[step_n])
duplicating_group
```

No more deplicated columns!!

### Combinding deduplicated data

#### Created dataframe on non-duplicating columns

Collect column names of variables not creating duplicates.

```{r}
non_duplicating_variables <- 
  column_meta_data %>% 
  filter(!duplicates_by_variable) %>% 
  pull(variable)

non_duplicating_variables
```

Create dataframe of only these variables.

```{r}
prep_xx <- 
  prep_base %>% 
  select(any_of(non_duplicating_variables)) %>% 
  distinct()

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe.

```{r}
prep_11 <- prep_xx
```

#### Join all deduplicated dataframes

```{r}
prep_xx <- 
  ls(envir=.GlobalEnv) %>% 
  as_tibble() %>% 
  filter(str_detect(value, "prep_[0-9]")) %>% 
  pull() %>% 
  mget(envir=.GlobalEnv) %>% 
  reduce(full_join)

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe.

```{r}
prep_dedup <- prep_xx
```

### Checking duplicating columns have been fixed

Created a dataframe of variable metadata

```{r}
column_meta_data_dedupe <- 
  prep_dedup %>% 
  contents()

column_meta_data_dedupe <- 
  column_meta_data_dedupe$contents %>% 
  as.data.frame()

column_meta_data_dedupe <-
  column_meta_data_dedupe %>% 
  rownames_to_column(var = "variable")

column_meta_data_dedupe
```

Checking duplicates for each variable in the dataframe.

```{r}
duplicates_by_variable <- 
  column_meta_data_dedupe %>% 
  pull(variable) %>% 
  map_lgl(~dupe_check(in_data = prep_dedup, .))

duplicates_by_variable
```

Add this to the column_meta_data dataframe.

```{r}
column_meta_data_dedupe <- 
  column_meta_data_dedupe %>% 
  add_column(
    duplicates_by_variable = duplicates_by_variable
  )

column_meta_data_dedupe
```

Create dataframe of only variables that cause duplicates.

```{r}
duplicating_variables <- 
  column_meta_data_dedupe %>% 
  filter(duplicates_by_variable)

duplicating_variables
```

## Addressing blanks

Created a dataframe of variable metadata for deduplicated data

```{r}
column_meta_data_dedupe <- 
  prep_dedup %>% 
  contents()

column_meta_data_dedupe <- 
  column_meta_data_dedupe$contents %>% 
  as.data.frame()

column_meta_data_dedupe <-
  column_meta_data_dedupe %>% 
  rownames_to_column(var = "variable")

column_meta_data_dedupe
```

Function that checks whether there are duplicates for different variables

```{r}
blank_check <- function(in_data,in_variable_name)
{
  check_01 <- 
  in_data %>% 
    filter(!!sym(in_variable_name) == "") %>% 
  distinct()

out <- nrow(check_01) > 0

return(out)
}
```

Checking duplicates for each variable in the dataframe.

```{r}
blanks_by_variable <- 
  column_meta_data_dedupe %>% 
  pull(variable) %>% 
  map_lgl(~blank_check(in_data = prep_dedup,.))

blanks_by_variable
```

Add this to the `column_meta_data_dedupe` dataframe.

```{r}
column_meta_data_dedupe <- 
  column_meta_data_dedupe %>% 
  add_column(
    blanks_by_variable = blanks_by_variable
  )

column_meta_data_dedupe
```

Create dataframe of only variables that have blanks.

```{r}
blanking_variables <- 
  column_meta_data_dedupe %>% 
  filter(blanks_by_variable)

blanking_variables
```

Grouping variables.

```{r}
blanking_variables <- 
  blanking_variables %>% 
  mutate(group = 
           case_when(variable == "position_open_date" ~ "dates",
                     variable == "position_close_date" ~ "dates",
                     variable == "announcement_closing_type" ~ "announcement_closing_type",
                     variable == "announcement_closing_type_description" ~ "announcement_closing_type",
                     variable == "application_limit" ~ "application_limit",
                     variable == "application_limit_set" ~ "application_limit",
                     variable == "agency_level" ~ "agency_level",
                     variable == "agency_level_sort" ~ "agency_level",
                     variable == "hiring_agency_code" ~ "agency_level",
                     variable == "hiring_agency_name" ~ "agency_level",
                     variable == "hiring_department_code" ~ "agency_level",
                     variable == "hiring_department_name" ~ "agency_level",
                     variable == "maximum_salary" ~ "maximum_salary",
                     variable == "minimum_salary" ~ "maximum_salary",
                     variable == "maximum_grade" ~ "maximum_salary",
                     variable == "minimum_grade" ~ "maximum_salary",
                     variable == "series" ~ "series",
                     variable == "series_title" ~ "series",
                     TRUE ~ variable
                     ))

blanking_variables
```

Create list of groups.

```{r}
blanking_groups <- 
  blanking_variables %>% 
  select(group) %>% 
  distinct() %>% 
  pull()

blanking_groups
```

### Blanks removal

```{r}
step_n <- 0
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing blanks produced by:

```{r}
blanking_variable <- 
  blanking_variables %>% 
  filter(group == blanking_groups[step_n])

blanking_variable
```

Reviewing blanks.

```{r}
blanks_01 <- 
  prep_dedup %>% 
  filter(if_any(all_of(blanking_variable %>% pull(variable)),  ~.x == "")) %>% 
  select(all_of(blanking_variable %>% pull(variable)),everything())

blanks_01
```

Blanks appear to be caused by a few columns:

1.    `hiring_agency_code` appears to be blank for agencies that don't fall into departments
2.    `hiring_agency_name` appears to be blank for the Air Force

Let's count the extent of the issues.

```{r}
blanking_variable %>% 
  pull(variable) %>% 
  map(
    ~blanks_01 %>% 
  count(!!sym(.x)) %>% 
  arrange(desc(n)) %>% 
    filter(!!sym(.x) == "")
  )
```

A lot of blanks in `hiring_agency_code`, some in `hiring_agency_name`, and very few in `hiring_department_name`.

Let's test filling blanks in `hiring_agency_name` with `hiring_department_name`.

```{r}
blanks_02 <- 
  blanks_01 %>% 
    select(starts_with("hiring_agency_"),starts_with("hiring_department_name"),everything()) %>%
  mutate(
    hiring_agency_name = case_when(
      hiring_agency_name == "" & !is.na(hiring_department_name) ~ hiring_department_name,
      TRUE ~ hiring_agency_name
      ),
    ) 
```

Reviewing blanks.

```{r}
  blanks_02 %>% 
  filter(if_any(all_of(blanking_variable %>% pull(variable)),  ~.x == "")) %>% 
  select(all_of(blanking_variable %>% pull(variable)),everything())
```

Reduced a lot.

Let's count the extent of the issues.

```{r}
blanking_variable %>% 
  pull(variable) %>% 
  map(
    ~blanks_02 %>% 
  count(!!sym(.x)) %>% 
  arrange(desc(n)) %>% 
    filter(!!sym(.x) == "")
  )
```

All the `hiring_agency_name` are gone.

Let's look into the issues with `hiring_department_name`.

```{r}
blanks_02 %>%
  filter(hiring_department_name == "")
```

Let's check what `hiring_department_name` this `hiring_agency_name` has in the larger data.

```{r}
prep_dedup %>% 
  filter(hiring_agency_name == "Public Defender Service for the District of Columbia") %>% 
  count(hiring_agency_name,hiring_department_name)
```

This suggests we should replace `hiring_department_name` this `hiring_agency_name`.

Let's do both steps.

```{r}
blanks_03 <- 
  blanks_01 %>% 
    select(starts_with("hiring_agency_"),starts_with("hiring_department_name"),everything()) %>%
  mutate(
    hiring_agency_name = case_when(
      hiring_agency_name == "" & !is.na(hiring_department_name) ~ hiring_department_name,
      TRUE ~ hiring_agency_name
      ),
    hiring_department_name = case_when(
      hiring_department_name == "" & !is.na(hiring_agency_name) ~ hiring_agency_name,
      TRUE ~ hiring_department_name
      ),
    ) 
```

Reviewing blanks.

```{r}
  blanks_03 %>% 
  filter(if_any(all_of(blanking_variable %>% pull(variable)),  ~.x == "")) %>% 
  select(all_of(blanking_variable %>% pull(variable)),everything())
```

Reduced a lot.

Let's count the extent of the issues.

```{r}
blanking_variable %>% 
  pull(variable) %>% 
  map(
    ~blanks_03 %>% 
  count(!!sym(.x)) %>% 
  arrange(desc(n)) %>% 
    filter(!!sym(.x) == "")
  )
```

Still have many issues with the `hiring_agency_code`. `hiring_agency_name` appears to have all of the important information and is more complete. So we will drop `hiring_agency_code`.

Now apply the steps above to the larger dataframe.

```{r}
prep_xx <- 
  prep_dedup %>% 
  mutate(
    hiring_agency_name = case_when(
      hiring_agency_name == "" & !is.na(hiring_department_name) ~ hiring_department_name,
      TRUE ~ hiring_agency_name
      ),
    hiring_department_name = case_when(
      hiring_department_name == "" & !is.na(hiring_agency_name) ~ hiring_agency_name,
      TRUE ~ hiring_department_name
      ),
    ) %>% 
  select(-hiring_agency_code)
```

Check for blanks.

```{r}
prep_xx %>% 
  filter(if_any(all_of(blanking_variable %>% filter(variable != 'hiring_agency_code') %>%  pull(variable)),  ~.x == ""))
```

Rename dataframe

```{r}
prep_blank <- prep_xx
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing blanks produced by:

```{r}
blanking_variable <- 
  blanking_variables %>% 
  filter(group == blanking_groups[step_n])

blanking_variable
```

Reviewing blanks.

```{r}
blanks_01 <- 
  prep_dedup %>% 
  filter(if_any(all_of(blanking_variable %>% pull(variable)),  ~.x == "")) %>% 
  select(all_of(blanking_variable %>% pull(variable)),everything())

blanks_01
```

Looks like `who_may_apply` is just blank.

Let's count the extent of the issues.

```{r}
blanking_variable %>% 
  pull(variable) %>% 
  map(
    ~blanks_01 %>% 
  count(!!sym(.x)) %>% 
  arrange(desc(n)) %>% 
    filter(!!sym(.x) == "")
  )
```

They are all blank. We will drop the `who_may_apply` column.

```{r}
prep_xx <- 
  prep_blank %>% 
  select(-who_may_apply)
```

Rename dataframe

```{r}
prep_blank <- prep_xx
```

```{r}
step_n <- step_n + 1
```

### Check that blanks are removed

Created a dataframe of variable metadata for deduplicated data

```{r}
column_meta_data_blank <- 
  prep_blank %>% 
  contents()

column_meta_data_blank <- 
  column_meta_data_blank$contents %>% 
  as.data.frame()

column_meta_data_blank <-
  column_meta_data_blank %>% 
  rownames_to_column(var = "variable")

column_meta_data_blank
```

Checking duplicates for each variable in the dataframe.

```{r}
blanks_by_variable <- 
  column_meta_data_blank %>% 
  pull(variable) %>% 
  map_lgl(~blank_check(in_data = prep_blank,.))

blanks_by_variable
```

Add this to the `column_meta_data_dedupe` dataframe.

```{r}
column_meta_data_blank <- 
  column_meta_data_blank %>% 
  add_column(
    blanks_by_variable = blanks_by_variable
  )

column_meta_data_blank
```

Create dataframe of only variables that have blanks.

```{r}
blanking_variables <- 
  column_meta_data_blank %>% 
  filter(blanks_by_variable)

blanking_variables
```

## Addressing nulls

Created a dataframe of variable metadata for blanks data

```{r}
column_meta_data_null <- 
  prep_blank %>% 
  contents()

column_meta_data_null <- 
  column_meta_data_null$contents %>% 
  as.data.frame()

column_meta_data_null <-
  column_meta_data_null %>% 
  rownames_to_column(var = "variable")

column_meta_data_null
```

Function that checks whether there are duplicates for different variables

```{r}
null_check <- function(in_data,in_variable_name)
{
  check_01 <- 
  in_data %>% 
    filter(is.na(!!sym(in_variable_name))) %>% 
  distinct()

out <- nrow(check_01) > 0

return(out)
}
```

Checking duplicates for each variable in the dataframe.

```{r}
nulls_by_variable <- 
  column_meta_data_null %>% 
  pull(variable) %>% 
  map_lgl(~null_check(in_data = prep_dedup,.))

nulls_by_variable
```

Add this to the `column_meta_data_null` dataframe.

```{r}
column_meta_data_null <- 
  column_meta_data_null %>% 
  add_column(
    nulls_by_variable = nulls_by_variable
  )

column_meta_data_null
```

Create dataframe of only variables that have blanks.

```{r}
null_variables <- 
  column_meta_data_null %>% 
  filter(nulls_by_variable)

null_variables
```

Grouping variables.

```{r}
null_variables <- 
  null_variables %>% 
  mutate(group = 
           case_when(variable == "position_open_date" ~ "dates",
                     variable == "position_close_date" ~ "dates",
                     variable == "announcement_closing_type" ~ "announcement_closing_type",
                     variable == "announcement_closing_type_description" ~ "announcement_closing_type",
                     variable == "application_limit" ~ "application_limit",
                     variable == "application_limit_set" ~ "application_limit",
                     variable == "agency_level" ~ "agency_level",
                     variable == "agency_level_sort" ~ "agency_level",
                     variable == "hiring_agency_code" ~ "agency_level",
                     variable == "hiring_agency_name" ~ "agency_level",
                     variable == "hiring_department_code" ~ "agency_level",
                     variable == "hiring_department_name" ~ "agency_level",
                     variable == "maximum_salary" ~ "maximum_salary",
                     variable == "minimum_salary" ~ "maximum_salary",
                     variable == "maximum_grade" ~ "maximum_salary",
                     variable == "minimum_grade" ~ "maximum_salary",
                     variable == "series" ~ "series",
                     variable == "series_title" ~ "series",
                     TRUE ~ variable
                     ))

null_variables
```

Create list of groups.

```{r}
null_groups <- 
  null_variables %>% 
  select(group) %>% 
  distinct() %>% 
  pull()

null_groups
```

### Nulls removal

```{r}
step_n <- 0
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing nulls produced by:

```{r}
null_variable <- 
  null_variables %>% 
  filter(group == null_groups[step_n])

null_variable
```

Reviewing blanks.

```{r}
null_01 <- 
  prep_blank %>% 
  filter(if_any(all_of(null_variable %>% pull(variable)),  ~is.na(.x))) %>% 
  select(all_of(null_variable %>% pull(variable)),everything())

null_01
```

Looks like the `hiring_department_code` is null for some rows.

Let's count the extent of the issues.

```{r}
null_variable %>% 
  pull(variable) %>% 
  map(
    ~null_01 %>% 
  count(!!sym(.x)) %>% 
  arrange(desc(n)) %>% 
    filter(is.na(!!sym(.x)))
  )
```

Let's see how the hiring codes look in comparison to the department names.

```{r}
prep_blank %>% 
  count(hiring_department_code,hiring_department_name)
```

There are a lot of nulls, and 0s.

Check for any duplications in the codes.

```{r}
prep_blank %>% 
  count(hiring_department_code,hiring_department_name) %>% 
  get_dupes(hiring_department_code)
```

Lots of 0, nulls, and 5s.

The department name appears more complete. We will drop `hiring_department_code`.

```{r}
prep_xx <- 
  prep_blank %>% 
  select(-hiring_department_code)
```

Rename dataframe

```{r}
prep_null <- prep_xx
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing nulls produced by:

```{r}
null_variable <- 
  null_variables %>% 
  filter(group == null_groups[step_n])

null_variable
```

Reviewing blanks.

```{r}
null_01 <- 
  prep_blank %>% 
  filter(if_any(all_of(null_variable %>% pull(variable)),  ~is.na(.x))) %>% 
  select(all_of(null_variable %>% pull(variable)),everything())

null_01
```

Looks like the `telework_eligibility_description` is null.

Let's count the extent of the issues.

```{r}
null_variable %>% 
  pull(variable) %>% 
  map(
    ~null_01 %>% 
  count(!!sym(.x)) %>% 
  arrange(desc(n)) %>% 
    filter(is.na(!!sym(.x)))
  )
```

The whole column is null. We should drop.

```{r}
prep_xx <- 
  prep_null %>% 
  select(-telework_eligibility_description)
```

Rename dataframe

```{r}
prep_null <- prep_xx
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing nulls produced by:

```{r}
null_variable <- 
  null_variables %>% 
  filter(group == null_groups[step_n])

null_variable
```

Reviewing blanks.

```{r}
null_01 <- 
  prep_blank %>% 
  filter(if_any(all_of(null_variable %>% pull(variable)),  ~is.na(.x))) %>% 
  select(all_of(null_variable %>% pull(variable)),everything())

null_01
```

Looks like the `second_announcement` is null.

Let's count the extent of the issues.

```{r}
null_variable %>% 
  pull(variable) %>% 
  map(
    ~null_01 %>% 
  count(!!sym(.x)) %>% 
  arrange(desc(n)) %>% 
    filter(is.na(!!sym(.x)))
  )
```

The whole column is null. We should drop.

```{r}
prep_xx <- 
  prep_null %>% 
  select(-second_announcement)
```

Rename dataframe

```{r}
prep_null <- prep_xx
```

```{r}
step_n <- step_n + 1
```

#### Step `r step_n`

Removing nulls produced by:

```{r}
null_variable <- 
  null_variables %>% 
  filter(group == null_groups[step_n])

null_variable
```

Reviewing blanks.

```{r}
null_01 <- 
  prep_blank %>% 
  filter(if_any(all_of(null_variable %>% pull(variable)),  ~is.na(.x))) %>% 
  select(all_of(null_variable %>% pull(variable)),everything())

null_01
```

Looks like the `pay_scale` is null.

Let's count the extent of the issues.

```{r}
null_variable %>% 
  pull(variable) %>% 
  map(
    ~null_01 %>% 
  count(!!sym(.x)) %>% 
  arrange(desc(n)) %>% 
    filter(is.na(!!sym(.x)))
  )
```

Let's see how the `pay_scale` look in comparison to the `pay_scale_description`.

```{r}
prep_blank %>% 
  count(pay_scale,pay_scale_description)
```

Looks like the NAs in `pay_scale` are "Nonappropriated Funds--Nonsupervisory And Nonleader--Federal Wage System." We'll retain `pay_scale_description`and drop `pay_scale`.

```{r}
prep_xx <- 
  prep_null %>% 
  select(-pay_scale)
```

Rename dataframe

```{r}
prep_null <- prep_xx
```

```{r}
step_n <- step_n + 1
```

### Check that nulls are removed

Created a dataframe of variable metadata for blanks data

```{r}
column_meta_data_null <- 
  prep_null %>% 
  contents()

column_meta_data_null <- 
  column_meta_data_null$contents %>% 
  as.data.frame()

column_meta_data_null <-
  column_meta_data_null %>% 
  rownames_to_column(var = "variable")

column_meta_data_null
```

Checking duplicates for each variable in the dataframe.

```{r}
nulls_by_variable <- 
  column_meta_data_null %>% 
  pull(variable) %>% 
  map_lgl(~null_check(in_data = prep_null,.))

nulls_by_variable
```

Add this to the `column_meta_data_null` dataframe.

```{r}
column_meta_data_null <- 
  column_meta_data_null %>% 
  add_column(
    nulls_by_variable = nulls_by_variable
  )

column_meta_data_null
```

Create dataframe of only variables that have blanks.

```{r}
null_variables <- 
  column_meta_data_null %>% 
  filter(nulls_by_variable)

null_variables
```

## Other data cleaning

Review the data.

```{r}
prep_null %>% 
  skim()
```

Only two variables stand out: `telework_eligible` and `supervisory_status`.

First count them.

```{r}
prep_null %>% 
  count(telework_eligible,supervisory_status)
```

No positions appear to be telework eligible, which is wrong.

<!-- Talk to Melissa about this. -->

For supervisory status, it's preferable to transform this into an indicator.

```{r}
prep_xx <- 
  prep_null %>% 
  character_to_indicator(params$unique_identifier_1,supervisory_status,"supervisory_status") %>% 
  select(-supervisory_status_n)

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe.

```{r}
prep_12 <- prep_xx
```

## Creating final data set

Remove `supervisory_status` and attach `supervisory_status_y` the new data

```{r}
prep_xx <- 
  prep_null %>% 
  select(-supervisory_status) %>% 
  left_join(prep_12)

prep_xx %>% 
  glimpse()

prep_xx %>% 
  skim()
```

Count rows.

```{r}
prep_xx %>% 
  count()
```

Do the number of in this dataframe match the number of unique identifiers?

```{r}
prep_xx %>% 
  count() %>% 
  pull() ==
  prep_uniq %>% 
  count() %>% 
  pull()
```

Rename dataframe.

```{r}
joas <- prep_xx
```

## Save data {.tabset .tabset-pills}

```{r}
save(joas, 
     file = here::here("03. Data Collection",
                       "prepared-data",
                       glue::glue("joas-{today()}.rdata")))
```

## Extraction time {.tabset .tabset-pills}

```{r}
tictoc::toc()
```

### 2023-02-15 04. Analysis/scripts/01-data-preparation-joas.R

@@ -1,0 +1,51 @@
+
+# Start timer -------------------------------------------------------------
+
+tictoc::tic()
+
+# Libraries ---------------------------------------------------------------
+
+library(tidyverse)
+library(lubridate)
+library(purrr)
+
+# Parameters --------------------------------------------------------------
+
+author <- "Sam Kim and Ben Jaques-Leslie"
+project_number <- "001"
+project_name <- "Remote Work"
+data_folder_1 <- "03. Data Collection/Original data files from Melissa/JOAs"
+unique_identifier_1 <- c("usajobs_control_number")
+date_earliest_open <- '2022-01-01'
+data_latest_close <- '2022-12-01'
+
+# Determine file name -----------------------------------------------------
+
+file_name <- 
+  glue::glue("01-data-preparation-joas-{project_number}-{str_replace_all(str_to_lower(project_name),' ','-')}-{today()}.html")
+
+file_name
+
+# Render data extraction --------------------------------------------------
+
+rmarkdown::render(input = here::here("scripts",
+                                     "01-data-preparation-joas.Rmd"),
+                  params = list(
+                    author = author,
+                    project_number = project_number,
+                    project_name = project_name,
+                    data_folder_1 = data_folder_1,
+                    unique_identifier_1 = unique_identifier_1,
+                    date_earliest_open = date_earliest_open,
+                    data_latest_close = data_latest_close
+                  ),
+                  output_file =
+                    here::here("output",
+                               'html',
+                               file_name))
+
+
+# End timer ---------------------------------------------------------------
+
+tictoc::toc()
+

### 2023-02-15 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd
Starting deduplication process

@@
   project_name: "Occupancy Patterns"
+  google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Occupancy Patterns"
   data_folder_1: "Occupancy Data Pull"
-  unique_identifier_1: !r c("employee_name")
+  unique_identifier_1: !r c("employee_name","date")
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
+install.packages("arsenal")
+devtools::install_github(repo = "GSA/oesrrr")
+library(oesrrr)
 library(tidyverse)
@@
 library(readr)
+library(arsenal)
+library(Hmisc)
 ```
@@
 files <- 
-  list.files(here::here("03. Data Collection",params$data_folder_1), pattern = ".csv", full.names = TRUE)
+  list.files(file.path(params$google_drive_home,"03. Data Collection",params$data_folder_1), pattern = ".csv", full.names = TRUE)
 files
@@
 ```{r}
-prep_01 <- files %>% 
-  map_dfr(~read_csv(., 
-    col_types = cols(Date = col_date(format = "%m_%d_%Y")))) %>% 
-  clean_names()
+prep_base <- files %>% 
+  map_dfr(~mutate(.data = read_csv(., 
+    col_types = cols(Date = col_date(format = "%m_%d_%Y"))), 
+        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
+      )) %>% 
+  clean_names() %>% 
+  distinct()
 ```
 
-Review data.
+### Review data
 
 ```{r}
-prep_01 %>% skim()
+prep_base %>% skim()
+```
+
+## Addressing duplication
+
+We are using `r params$unique_identifier_1` as the unique identifier.
+
+### Check for duplication
+
+```{r}
+dupe_01 <- 
+  prep_base %>%
+  get_dupes(params$unique_identifier_1)
+```
+
+#### Data review
+
+```{r}
+dupe_01 %>% 
+  skim()
+```
+
+### Dataframe of the unique identifier
+
+```{r}
+prep_uniq <- 
+  prep_base %>% 
+  select(params$unique_identifier_1) %>% 
+  distinct()
+
+prep_uniq %>% 
+  count()
+```
+
+### Identifying and categorizing columns
+
+Created a dataframe of variable metadata
+
+```{r}
+column_meta_data <- 
+  prep_base %>% 
+  contents()
+
+column_meta_data <- 
+  column_meta_data$contents %>% 
+  as.data.frame()
+
+column_meta_data <-
+  column_meta_data %>% 
+  rownames_to_column(var = "variable")
+
+column_meta_data
+```
+
+Function that checks whether there are duplicates for different variables
+
+```{r}
+dupe_check <- function(in_data,in_variable_name)
+{
+  check_01 <- 
+  in_data %>% 
+  select(params$unique_identifier_1,all_of(in_variable_name)) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+out <- nrow(check_01) > 0
+
+return(out)
+}
+```
+
+Checking duplicates for each variable in the dataframe.
+
+```{r}
+duplicates_by_variable <- 
+  column_meta_data %>% 
+  pull(variable) %>% 
+  map_lgl(~dupe_check(in_data = dupe_01, .))
+
+duplicates_by_variable
+```
+
+Add this to the column_meta_data dataframe.
+
+```{r}
+column_meta_data <- 
+  column_meta_data %>% 
+  add_column(
+    duplicates_by_variable = duplicates_by_variable
+  )
+
+column_meta_data
+```
+
+Create dataframe of only variables that cause duplicates.
+
+```{r}
+duplicating_variables <- 
+  column_meta_data %>% 
+  filter(duplicates_by_variable)
+
+duplicating_variables
+```
+
+Grouping variables.
+
+```{r}
+duplicating_variables <- 
+  duplicating_variables %>% 
+  mutate(group = 
+           case_when(variable == "short_id" ~ "short_id",
+                     variable == "dept_id" ~ "short_id",
+                    TRUE ~ variable
+                     ))
+
+duplicating_variables
+```
+
+Create list of groups.
+
+```{r}
+duplicating_groups <- 
+  duplicating_variables %>% 
+  select(group) %>% 
+  distinct() %>% 
+  pull()
+
+duplicating_groups
+```
+
+### Duplication removal
+
+```{r}
+step_n <- 0
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+```
+
+Not too many duplicates here.
+
+First count `sso` across the original data.
+
+```{r}
+prep_base %>% count(sso)
+```
+
+There are just a few, but we'll want to transform these into indicators.
+
+We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
+
+```{r}
+prep_xx <- 
+  prep_base %>% 
+  character_to_indicator(params$unique_identifier_1,sso,"sso")
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Rename dataframe.
+
+```{r}
+prep_01 <- prep_xx
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1) %>% view()
+```
+
+Quite a few duplicates here.
+
+First count `short_id` and `dept_id` across the original data.
+
+```{r}
+prep_base %>% count(short_id,dept_id)
+```
+
+Counting `short_id`.
+
+```{r}
+prep_base %>% count(short_id)
+```
+
+Counting `dept_id`.
+
+```{r}
+prep_base %>% count(dept_id)
+```
+
+Too many options to create useful indicators.
+
+For lack better option, we'll select the rows with shorter ids.
+
+```{r}
+dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  arrange(length(short_id),length(dept_id))
 ```

### 2023-02-15 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd

@@
                      variable == "dept_id" ~ "short_id",
+                     variable == "supervisor_name" ~ "short_id",
+                     variable == "location" ~ "short_id",
                     TRUE ~ variable
@@
   distinct() %>% 
-  get_dupes(params$unique_identifier_1) %>% view()
+  get_dupes(params$unique_identifier_1)
 ```
 
-Quite a few duplicates here.
+Quite a few duplicates here and they are associated with supervisor and location.
 
@@
 ```{r}
+dedupe <- 
   dupe_01 %>% 
@@
   distinct() %>% 
-  arrange(length(short_id),length(dept_id))
+  arrange(!!!params$unique_identifier_1,length(short_id),length(dept_id)) %>% 
+  group_by(across(all_of(params$unique_identifier_1))) %>% 
+  summarise(
+    across(.fns = ~first(.))
+  )
+
+dedupe %>% 
+  get_dupes(params$unique_identifier_1)
+```
+
+Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.
+
+First create a dataframe of distinct rows of the variables from the original data.
+
+```{r}
+working_01 <- 
+  prep_base %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct()
+
+working_01 %>% 
+  glimpse()
+
+working_01 %>% 
+  skim()
+```
+
+Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.
+
+```{r}
+working_02 <- 
+  working_01 %>% 
+  anti_join(dedupe %>% select(params$unique_identifier_1))
+
+working_02 %>% 
+  glimpse()
+
+working_02 %>% 
+  skim()
+```
+
+Last bind this dataframe to the deduplicated set above.
+
+```{r}
+prep_xx <- 
+  working_02 %>% 
+  bind_rows(dedupe)
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Rename dataframe
+
+```{r}
+prep_02 <- prep_xx
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
 ```

### 2023-02-15 04. Analysis/scripts/01_data_preparation_roster.Rmd
Create 01_data_preparation_roster.Rmd
Redirected to roster because roster data may help with duplicates in daily check in

--- 2023-02-15 04. Analysis/scripts/01_data_preparation.Rmd
@@
   google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Occupancy Patterns"
-  data_folder_1: "Occupancy Data Pull"
-  unique_identifier_1: !r c("employee_name","date")
+  data_folder_1: "Rosters"
+  unique_identifier_1: !r c("snapshot_date","employee_e_mail_address")
 ---
@@
 knitr::opts_chunk$set(echo = TRUE)
-install.packages("arsenal")
-devtools::install_github(repo = "GSA/oesrrr")
+# install.packages("arsenal")
+# devtools::install_github(repo = "GSA/oesrrr")
 library(oesrrr)
@@
 library(Hmisc)
+library(readxl)
 ```
@@
 
+## Functions
+
+Create function to drop rows with null unique identifiers.
+
+```{r}
+filter_unique <- function(in_data, ...)
+{
+  in_data %>% 
+  filter(!(if_any(c(...),~is.na(.))))
+}
+```
+
 ## Load data {.tabset .tabset-pills}
@@
 files <- 
-  list.files(file.path(params$google_drive_home,"03. Data Collection",params$data_folder_1), pattern = ".csv", full.names = TRUE)
+  list.files(file.path(params$google_drive_home,"03. Data Collection",params$data_folder_1), pattern = ".xlsx", full.names = TRUE)
 files
@@
 prep_base <- files %>% 
-  map_dfr(~mutate(.data = read_csv(., 
-    col_types = cols(Date = col_date(format = "%m_%d_%Y"))), 
+  map_dfr(~mutate(.data = read_xlsx(path = ., 
+                                    col_types = c("date", "text", "text", 
+        "text", "text", "text", "text", "text", 
+        "text", "date", "text", "text", "text", 
+        "text", "text", "text", "text", "text", 
+        "text", "text", "text", "text", "text", 
+        "text", "text", "text", "text", "text")), 
         file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
@@
 prep_base %>% skim()
+```
+
+## Filter null unique ids
+
+```{r}
+prep_base <- 
+  prep_base %>% 
+  filter_unique(params$unique_identifier_1)
+```
+
+### Review data
+
+```{r}
+prep_base %>% skim()
+```
+
+### Identifying and categorizing columns
+
+Created a dataframe of variable metadata
+
+```{r}
+column_meta_data <- 
+  prep_base %>% 
+  contents()
+
+column_meta_data <- 
+  column_meta_data$contents %>% 
+  as.data.frame()
+
+column_meta_data <-
+  column_meta_data %>% 
+  rownames_to_column(var = "variable")
+
+column_meta_data
 ```
@@
   skim()
+```
+
+No duplication found.
+
+## Addressing blanks
+
+Function that checks whether there are duplicates for different variables
+
+```{r}
+blank_check <- function(in_data,in_variable_name)
+{
+  if(prep_base %>% select(!!in_variable_name) %>% pull() %>% class() %>% head(1) == "POSIXct")
+    {
+    out <- FALSE
+  }
+
+  if(prep_base %>% select(!!in_variable_name) %>% pull() %>% class() %>% head(1) != "POSIXct")
+   {
+      check_01 <- 
+  in_data %>% 
+    filter(!!sym(in_variable_name) == "") %>% 
+  distinct()
+
+out <- nrow(check_01) > 0 
+   }
+
+return(out)
+}
+```
+
+Checking duplicates for each variable in the dataframe.
+
+```{r}
+blanks_by_variable <- 
+  column_meta_data %>% 
+  pull(variable) %>% 
+  map_lgl(~blank_check(in_data = prep_base,.))
+
+blanks_by_variable
+```
+
+Add this to the `column_meta_data` dataframe.
+
+```{r}
+column_meta_data <- 
+  column_meta_data %>% 
+  add_column(
+    blanks_by_variable = blanks_by_variable
+  )
+
+column_meta_data
+```
+
+Create dataframe of only variables that have blanks.
+
+```{r}
+blanking_variables <- 
+  column_meta_data %>% 
+  filter(blanks_by_variable)
+
+blanking_variables
+```
+
+No variables with blank entries.
+
+## Addressing nulls
+
+Function that checks whether there are duplicates for different variables
+
+```{r}
+null_check <- function(in_data,in_variable_name)
+{
+  check_01 <- 
+  in_data %>% 
+    filter(is.na(!!sym(in_variable_name))) %>% 
+  distinct()
+
+out <- nrow(check_01) > 0
+
+return(out)
+}
+```
+
+Checking duplicates for each variable in the dataframe.
+
+```{r}
+nulls_by_variable <- 
+  column_meta_data %>% 
+  pull(variable) %>% 
+  map_lgl(~null_check(in_data = prep_base,.))
+
+nulls_by_variable
+```
+
+Add this to the `column_meta_data` dataframe.
+
+```{r}
+column_meta_data <- 
+  column_meta_data %>% 
+  add_column(
+    nulls_by_variable = nulls_by_variable
+  )
+
+column_meta_data
+```
+
+Create dataframe of only variables that have blanks.
+
+```{r}
+null_variables <- 
+  column_meta_data %>% 
+  filter(nulls_by_variable)
+
+null_variables
+```
+
+Grouping variables.
+
+```{r}
+null_variables <- 
+  null_variables %>% 
+  mutate(group = 
+           case_when(
+             variable == "supervisor_display_name" ~ "supervisor_display_name",
+             variable == "supervisor_e_mail_address" ~ "supervisor_display_name",
+             variable == "business_line_2_letter_department_id" ~ "business_line_2_letter_department_id",
+             variable == "location_city" ~ "business_line_2_letter_department_id",
+             variable == "location_state" ~ "business_line_2_letter_department_id",
+             variable == "position_category_code" ~ "position_category_code",
+             variable == "position_category_description" ~ "position_category_code",
+             TRUE ~ variable
+             )
+         )
+
+null_variables
+```
+
+Create list of groups.
+
+```{r}
+null_groups <- 
+  null_variables %>% 
+  select(group) %>% 
+  distinct() %>% 
+  pull()
+
+null_groups
+```
+
+### Nulls removal
+
+```{r}
+step_n <- 0
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`
+
+Removing nulls produced by:
+
+```{r}
+null_variable <- 
+  null_variables %>% 
+  filter(group == null_groups[step_n])
+
+null_variable
+```
+
+Reviewing blanks.
+
+```{r}
+null_01 <- 
+  prep_base %>% 
+  filter(if_any(all_of(null_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(null_variable %>% pull(variable)),everything())
+
+null_01
+```
+
+Not too many.
+
+For those with null `supervisor_display_name` and `supervisor_e_mail_address`, do they have these names in other parts of the data?
+
+```{r}
+null_01 %>%
+  filter(if_all(all_of(null_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(employee_e_mail_address) %>% 
+  distinct() %>% 
+  inner_join(prep_base) %>% 
+  select(params$unique_identifier_1,all_of(null_variable %>% pull(variable)))
 ```

### 2023-02-22 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd
Testing out joining between monthly check in data and roster data. Need to join on the current month and the following month to collect roster data.

@@
   unique_identifier_1: !r c("employee_name","date")
+  data_folder_2: "Rosters"
+  unique_identifier_2: !r c("snapshot_date","employee_e_mail_address")
 ---
@@
 
-### Data from `r params$data_folder_1`
+### Data files
 
@@
 ```{r}
-files <- 
+files_1 <- 
   list.files(file.path(params$google_drive_home,"03. Data Collection",params$data_folder_1), pattern = ".csv", full.names = TRUE)
-files
+files_1
+```
+
+Find the list of .csv files in the `r params$data_folder_2` data folder.
+
+```{r}
+files_2 <- 
+  list.files(file.path(params$google_drive_home,"03. Data Collection",params$data_folder_2), pattern = ".xlsx", full.names = TRUE)
+files_2
 ```
@@
 ```{r}
-prep_base <- files %>% 
+prep_base_1 <- files_1[1] %>% 
   map_dfr(~mutate(.data = read_csv(., 
@@
   clean_names() %>% 
+  distinct() %>% 
+  separate(supervisor_name,into = c("sup_last","sup_first"), sep = ",") %>% 
+  mutate(
+    across(
+      .cols = starts_with("sup_"),
+      .fns = ~word(.,1)
+    )
+  ) %>% 
+  unite(col = "supervisor_display_name",sup_first,sup_last, sep = " ") %>% 
+  rename(file_name_1 =file_name)
+```
+
+```{r}
+prep_base_1_names <- names(prep_base_1)
+```
+
+Load all data files in the `r params$data_folder_2` data folder.
+
+```{r}
+prep_base_2_1 <- files_2[1] %>% 
+  map_dfr(~mutate(.data = read_xlsx(path = ., 
+                                    col_types = c("date", "text", "text", 
+        "text", "text", "text", "text", "text", 
+        "text", "date", "text", "text", "text", 
+        "text", "text", "text", "text", "text", 
+        "text", "text", "text", "text", "text", 
+        "text", "text", "text", "text", "text")), 
+        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
+      )) %>% 
+  clean_names() %>% 
   distinct()
+```
+
+```{r}
+prep_base_2_2 <- files_2[2] %>% 
+  map_dfr(~mutate(.data = read_xlsx(path = ., 
+                                    col_types = c("date", "text", "text", 
+        "text", "text", "text", "text", "text", 
+        "text", "date", "text", "text", "text", 
+        "text", "text", "text", "text", "text", 
+        "text", "text", "text", "text", "text", 
+        "text", "text", "text", "text", "text")), 
+        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
+      )) %>% 
+  clean_names() %>% 
+  distinct()
+```
+
+```{r}
+prep_base_2_3 <- files_2[3] %>% 
+  map_dfr(~mutate(.data = read_xlsx(path = ., 
+                                    col_types = c("date", "text", "text", 
+        "text", "text", "text", "text", "text", 
+        "text", "date", "text", "text", "text", 
+        "text", "text", "text", "text", "text", 
+        "text", "text", "text", "text", "text", 
+        "text", "text", "text", "text", "text")), 
+        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
+      )) %>% 
+  clean_names() %>% 
+  distinct()
+```
+
+Joining data
+
+```{r}
+step_1 <- prep_base_1 %>% 
+   left_join(prep_base_2_1,
+            by = c("employee_name" = "full_name",
+                   "sso" = "gsa_sso",
+                   "dept_id" = "department_id",
+                   "supervisor_display_name" = "supervisor_display_name"
+                   )) %>% 
+  # filter(rollback(date) == snapshot_date |
+  #          rollforward(date) == snapshot_date) %>%
+  # select(-snapshot_date, -starts_with("file_name")) %>% 
+  distinct()
+  # skim()
+  # get_dupes(employee_e_mail_address,date)
+```
+
+```{r}
+step_2 <- 
+  step_1 %>% 
+  filter(is.na(employee_e_mail_address)) %>% 
+  select(all_of(prep_base_1_names)) %>% 
+  left_join(prep_base_2_2,
+            by = c("employee_name" = "full_name",
+                   "sso" = "gsa_sso",
+                   "dept_id" = "department_id",
+                   "supervisor_display_name" = "supervisor_display_name"
+                   )) %>% 
+  # filter(rollback(date) == snapshot_date |
+  #          rollforward(date) == snapshot_date) %>%
+  # select(-snapshot_date, -starts_with("file_name")) %>% 
+  distinct()
+```
+
+```{r}
+step_3 <- 
+  step_2 %>% 
+  filter(is.na(employee_e_mail_address)) %>% 
+  select(all_of(prep_base_1_names)) %>% 
+  left_join(prep_base_2_3,
+            by = c("employee_name" = "full_name",
+                   "sso" = "gsa_sso",
+                   "dept_id" = "department_id",
+                   "supervisor_display_name" = "supervisor_display_name"
+                   )) %>% 
+  # filter(rollback(date) == snapshot_date |
+  #          rollforward(date) == snapshot_date) %>%
+  # select(-snapshot_date, -starts_with("file_name")) %>% 
+  distinct()
+```
+
+```{r}
+step_3 %>% 
+  filter(!is.na(employee_e_mail_address))
+```
+
+```{r}
+rollback(ymd('2022-12-01'))
+rollforward(ymd('2022-12-01'))
 ```

### 2023-03-06 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Added Mike's comments, updated data description tables

--- 2023-02-13 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
@@
 ```
+
+# MIKES COMMENTS
+Proofread for typos
+
+Why start cohort in March? I believe because of data availability, but good to clarify in text.
+
+Not sure i follow the deduping logic. If two employees have the same name, then they may have different EOD Dates. But maybe there are no duplicates on full name so it’s not an issue.
+
+The analysis plan is a good place to define the rules for classification
+Re: missing supervisor name and some other values.
+It is possible that people change supervisors or departments.
+Do we care about this?
+And how should we deal with it?
+At a minimum, maybe we want a slightly different imputation like if supervisor is the same both with earlier and later nonmissing observations, use that value, otherwise use prior supervisor?
+
+How are you doing team classification? Are you going to generate a team ID based on some rule? If so what is it, and to the prior point, how do you handle changing team composition over time?
+
+Not sure about using percentiles for cutoffs.
+I would assume based on classifications that more that 5 percent of teams are fully remote.
+For individuals, i think there is more alignment on things like number of days in a pay period in the office because of policy definitions for people who are not remote and have to be in the office 2 days per pay period.
+For teams maybe an extension of that basic ideas (e.g., fewer than 2 days in office on average is fully remote)
+
+Are all of these taking averages over the whole time period (9 months or whatever)? Would we potentially want to know about things like people who have more specific weekly patterns?
+
+Why mention sq(num obs)/2 if you are not going to use that rule?
+
+The thing that is missing here that is potentially more complicated is figuring out more about how teams operate as collections of individuals.
+For example, you could I think in this approach have a team that is 20 percent average telework where everyone goes in person on Mondays and the rest of the time is distributed, or you could have a team that is 20 percent telework where people go in at random times and never see each other.
+I am interested to know the extent to which people are co-locating with their teams (and if some people are being left out—which may help motivate some equity questions about performance ratings for people who don’t get face time with the boss, for example).
+I think we are missing that level of analysis here.
 
@@
   # Is SSO single sign on? What did we decide?
-"",
+"Staff or service office",
 "2-digit department id",
 "Full department id code",
-"Employee name (Last,First Middle)",
-"Supervisor name (Last,First Middle)",
-"State abbreviation-City-Site (e.g., home or address); could string split and match state with roster, possibly city too.",
-"E.g., Teleworking, Leave, Supervisor Corrected, No Response, Reporting to Job Site, Other",
+"Employee name (Last, First Middle)",
+"Supervisor name (Last, First Middle)",
+"State abbreviation-City-Site (e.g. MA-WESTFORD-HOME and MA-BOSTON-FB Causeway St)",
+"Status of the staff on that day (e.g., Teleworking, Leave, Supervisor Corrected, No Response, Reporting to Job Site, Other)",
 # I think that this is an indicator for whether the supervisor corrected the record
-""
+"If daily status is Supervisor Corrected, then this is the work status entered by the supervisor"
 )
@@
 ```{r}
-tbl <- tibble("Variable Name" = c(
-"Snapshot.Date",
-"Department.ID",
-"Employee.Job.Business.Unit.Description",
-"Full.Name",
-"Employee.E.Mail.Address",
-"Position.Title",
-"Pay.Plan",
-"Occupational.Series",
-"Grade",
-"EOD.Date",
-"Supervisor.Level",
-"Supervisor.Level.Description",
-"Supervisor.Display.Name",
-"Supervisor.E.Mail.Address",
-"Business.Line.2.Letter.Department.ID.",
-"GSA.SSO",
-"Agency.Subelement.Code.Description",
-"GSA.Region",
-"GSA.Duty.Station.Region",
-"Location.City",
-"Location.State",
-"Duty.Station.Code",
-"Employee.Job.Bargaining.Unit.Description",
-"Employee.Summary.Bargaining.Unit",
-"Payroll.Accounting.Code",
-"Position.Number",
-"Position.Category.Code",
-"Position.Category.Description"
+tbl <- tibble("Variable Name" = c("snapshot_date", "department_id", "employee_job_business_unit_description", "full_name", "employee_e_mail_address", "position_title", "pay_plan", "occupational_series", "grade", "eod_date", "supervisor_level", "supervisor_level_description", "supervisor_display_name", "supervisor_e_mail_address", "business_line_2_letter_department_id", "gsa_sso", "agency_subelement_code_description", "gsa_region", "gsa_duty_station_region", "location_city", "location_state", "duty_station_code", "employee_job_bargaining_unit_description", "employee_summary_bargaining_unit", "payroll_accounting_code", "position_number", "position_category_code", "position_category_description"
+                                  # , "file_name"
 ),
@@
  "Date of data export",
-"Should align with check-in’s 'dept_id'",
-"",
-"Last,First Middle; should align with check-in’s 'employee_name'",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"First, Last",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"E.g., Onsite flexible, Offsite, Onsite required, Not specified, Position has changed"
+"GSA department ID",
+"Business unit of the staff person",
+"Employee name as Last,First Middle",
+"Email address of staff",
+"Position title",
+"Pay plan code",
+"Occupational series code",
+"Position grade",
+"Entry on duty i.e. staff's first day on the job",
+"Supervisor status code of staff",
+"Supervisor status description of staff",
+"Supervisor name as First Last",
+"Supervisor email address",
+"First two letters of GSA department ID",
+"Staff or service office code",
+"Staff or service office description",
+"GSA region number",
+"Duty station GSA region number",
+"Staff city",
+"Staff state",
+"Duty station number",
+"Staff bargaining unit descripton",
+"Staff bargaining unit number",
+"Payroll accounting code",
+"POsition number",
+"Position location category code",
+"Position location category description (e.g., Onsite flexible, Offsite, Onsite required, Not specified)"
 )

### 2023-03-08 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Updating based on Mike's feed back, creating tables of variables from the data, added more detail to the cohort, explaining joins and deduplication in more detail, updating missing data table to reflect combined data, removed rule of thumb note for cluster number

--- 2023-02-13 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
@@
 ```
+
+<!-- # MIKES COMMENTS -->
+
+<!-- Proofread for typos -->
+
+<!-- The analysis plan is a good place to define the rules for classification -->
+<!-- Re: missing supervisor name and some other values. It is possible that -->
+<!-- people change supervisors or departments. Do we care about this? And how -->
+<!-- should we deal with it? At a minimum, maybe we want a slightly different -->
+<!-- imputation like if supervisor is the same both with earlier and later -->
+<!-- nonmissing observations, use that value, otherwise use prior supervisor? -->
+
+<!-- How are you doing team classification? Are you going to generate a team -->
+<!-- ID based on some rule? If so what is it, and to the prior point, how do -->
+<!-- you handle changing team composition over time? -->
+
+<!-- Not sure about using percentiles for cutoffs. I would assume based on -->
+<!-- classifications that more that 5 percent of teams are fully remote. For -->
+<!-- individuals, i think there is more alignment on things like number of -->
+<!-- days in a pay period in the office because of policy definitions for -->
+<!-- people who are not remote and have to be in the office 2 days per pay -->
+<!-- period. For teams maybe an extension of that basic ideas (e.g., fewer -->
+<!-- than 2 days in office on average is fully remote) -->
+
+<!-- Are all of these taking averages over the whole time period (9 months or -->
+<!-- whatever)? Would we potentially want to know about things like people -->
+<!-- who have more specific weekly patterns? -->
+
+<!-- The thing that is missing here that is potentially more complicated is -->
+<!-- figuring out more about how teams operate as collections of individuals. -->
+<!-- For example, you could I think in this approach have a team that is 20 -->
+<!-- percent average telework where everyone goes in person on Mondays and -->
+<!-- the rest of the time is distributed, or you could have a team that is 20 -->
+<!-- percent telework where people go in at random times and never see each -->
+<!-- other. I am interested to know the extent to which people are -->
+<!-- co-locating with their teams (and if some people are being left -->
+<!-- out---which may help motivate some equity questions about performance -->
+<!-- ratings for people who don't get face time with the boss, for example). -->
+<!-- I think we are missing that level of analysis here. -->
 
@@
 
+<!-- Table 1 and 2 could use better updating of description column -->
+
+<!-- SSO=Staff or service office -->
+
+<!-- Done -->
+
 ```{r}
-tbl <- tibble("Variable Name" = c(
+tbl_daily_check_in <- tibble("Variable Name" = c(
   "date",
-"SSO",
+"sso",
 "short_id",
@@
 "supervisor_correction"
-),
+)
+)
+```
+
+```{r}
+tbl <- 
+  tbl_daily_check_in %>% 
+  add_column(
     "Description" = c(
@@
 ```{r}
-tbl <- tibble("Variable Name" = c(
-"Snapshot.Date",
-"Department.ID",
-"Employee.Job.Business.Unit.Description",
-"Full.Name",
-"Employee.E.Mail.Address",
-"Position.Title",
-"Pay.Plan",
-"Occupational.Series",
-"Grade",
-"EOD.Date",
-"Supervisor.Level",
-"Supervisor.Level.Description",
-"Supervisor.Display.Name",
-"Supervisor.E.Mail.Address",
-"Business.Line.2.Letter.Department.ID.",
-"GSA.SSO",
-"Agency.Subelement.Code.Description",
-"GSA.Region",
-"GSA.Duty.Station.Region",
-"Location.City",
-"Location.State",
-"Duty.Station.Code",
-"Employee.Job.Bargaining.Unit.Description",
-"Employee.Summary.Bargaining.Unit",
-"Payroll.Accounting.Code",
-"Position.Number",
-"Position.Category.Code",
-"Position.Category.Description"
-),
+tbl_roster <- tibble("Variable Name" = c("snapshot_date", "department_id", "employee_job_business_unit_description", "full_name", "employee_e_mail_address", "position_title", "pay_plan", "occupational_series", "grade", "eod_date", "supervisor_level", "supervisor_level_description", "supervisor_display_name", "supervisor_e_mail_address", "business_line_2_letter_department_id", "gsa_sso", "agency_subelement_code_description", "gsa_region", "gsa_duty_station_region", "location_city", "location_state", "duty_station_code", "employee_job_bargaining_unit_description", "employee_summary_bargaining_unit", "payroll_accounting_code", "position_number", "position_category_code", "position_category_description"
+                                  # , "file_name"
+)
+)
+```
+
+```{r}
+tbl <- 
+  tbl_roster %>% 
+  add_column(
 "Description" = c(
  "Date of data export",
-"Should align with check-in’s 'dept_id'",
-"",
-"Last,First Middle; should align with check-in’s 'employee_name'",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"First, Last",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"",
-"E.g., Onsite flexible, Offsite, Onsite required, Not specified, Position has changed"
+"GSA department ID",
+"Business unit of the staff person",
+"Employee name as Last,First Middle",
+"Email address of staff",
+"Position title",
+"Pay plan code",
+"Occupational series code",
+"Position grade",
+"Entry on duty i.e. staff's first day on the job",
+"Supervisor status code of staff",
+"Supervisor status description of staff",
+"Supervisor name as First Last",
+"Supervisor email address",
+"First two letters of GSA department ID",
+"Staff or service office code",
+"Staff or service office description",
+"GSA region number",
+"Duty station GSA region number",
+"Staff city",
+"Staff state",
+"Duty station number",
+"Staff bargaining unit descripton",
+"Staff bargaining unit number",
+"Payroll accounting code",
+"Position number",
+"Position location category code",
+"Position location category description (e.g., Onsite flexible, Offsite, Onsite required, Not specified)"
 )
@@
 
+<!-- Why start cohort in March? I believe because of data availability, but good to clarify in text. -->
+
+<!-- Done -->
+
 For all analysis, we will used a defined cohort of staff to examine work
@@
 March 2022 will be followed over six months. Teams will be defined by
-the supervisors of groups of staff in the beginning of March 2022. Any
-analysis we conduct may be reproduced on a separate cohort or may be
-combined with multiple cohorts depending on the data availability.
+the supervisors of groups of staff in the beginning of March 2022. We
+are choosing March 2022 because we were told by the data providers that
+earlier data was less reliable. We also wanted to have enough time to
+pass to examine work patterns. March 2022 is a good start for both data
+reliability and length of time to examine behavior. Any analysis we
+conduct may be reproduced on a separate cohort or may be combined with
+multiple cohorts depending on the data availability.
+
+<!-- Not sure i follow the deduping logic. If two employees have the same name, then they may have different EOD Dates. But maybe there are no duplicates on full name so it’s not an issue. -->
 
 Both data sources will be checked for duplication and deduplicated. The
-unique identifiers of the daily check-in data are `employee_name` and
-`date`. For the roster data the unique identifier is `Full.Name` and
-`Snapshot.Date`. The general approach to deduplication will be that
-categorical variables will be restructured as indicator variables taking
-on a one for each category associated with the duplicate. From the
-roster data, if the duplication is based off of `EOD.Date`, the later
-date will be selected along with the other variables associated with
-that date. There appear to be no numeric variables.
+daily check-in data has no true unique identifier. The roster data is
+uniquely identified by `employee_e_mail_address` and `snapshot_date`.
+The roster data *should not* have any duplications on
+`employee_e_mail_address` and `snapshot_date`, but this will be checked.
+To create a unique identifier in the daily check-in data, we will
+following process:
 
-The analysis will be done for staff and teams separately and aggregated independently. The table below defines how we plan to aggregate for staff and teams.
+1.  Start with check-in data from one month (call this *month 1*)
+
+2.  Transform supervisor name to match format of the roster data
+
+3.  Join roster data from the previous month (call this *month 0*) on
+    employee name, staff or service office, department ID and supervisor
+    name
+
+4.  Check to see if any rows are missing `employee_e_mail_address` after
+    the join
+
+5.  For any rows missing `employee_e_mail_address`, join roster data
+    from data from *month 1*
+
+6.  Check to see if any rows are missing `employee_e_mail_address` after
+    the join
+
+7.  For any rows missing `employee_e_mail_address`, join roster data
+    from data from *month 2*
+
+8.  Repeat steps 5 and 6 until no new `employee_e_mail_address` entries
+    are found, or no roster data is available
+
+9.  Repeat steps 1 through 7 for all other months in observation window
+
+10. Bind all joined data across observation window.
+
+After this, the combined data *should* be uniquely identified by
+`employee_e_mail_address` and `date`. The data set will contain all the
+daily check-in and roster information across the observation window.
+
+If any duplicates remain after the steps above, the general approach to
+deduplication will be that categorical variables will be restructured as
+indicator variables taking on a one for each category associated with
+the duplicate. There appear to be no numeric variables.
+
+The analysis will be done for staff and teams separately and aggregated
+independently. The table below defines how we plan to aggregate for
+staff and teams.
 
@@
 <!-- [I might be more discerning about using "staff" vs. "employees" vs. "teams" vs. "groups" vs. "clusters" -- we are grouping employees into teams, but also categorizing them.]  -->
+
 We will approach grouping staff and teams in two ways. First,
@@
 
-Missing data from daily check in will be treated as defined in the table below.
+Missing data from the combined data in will be treated as defined in the
+table below.
 
@@
 ```{r}
-tbl <- tibble("Variable Name" = c(
-  "date",
-"SSO",
-"short_id",
-"dept_id",
-"employee_name",
-"supervisor_name",
-"location",
-"daily_status",
-"supervisor_correction"
-),
-"Treatment if missing" = c(
-  "Drop observation",
-  "",
-  "Impute from other observations of same staff",
-  "Impute from other observations of same staff",
-  "Drop observation",
-  "Impute from other observations of same staff",
-  "Label as missing",
-  "Label as missing",
-  "Label as missing"
-)
-)
+tbl_combined <- 
+  tbl_daily_check_in %>% 
+  bind_rows(tbl_roster)
+# tbl_combined
 ```
@@
 ```{r}
-tbl %>% 
-  flextable() %>% 
-  # add_header_row(values = c("","","Type of analysis", "Type of analysis")) %>% 
-  # set_header_labels(Group = "Level of analysis") %>% 
-  merge_h(part = "header") %>% 
-  merge_v(j = 1) %>% 
-  theme_vanilla() %>% 
-  autofit()
-```
-
-Missing data from the roster will be treated as show in the table below.
-
-```{r}
-table_n <- table_n + 1
-```
-
-#### Table `r table_n`. Treatment of missing data from roster
-
-```{r}
-tbl <- tibble("Variable Name" = c(
-"Snapshot.Date",
-"Department.ID",
-"Employee.Job.Business.Unit.Description",
-"Full.Name",
-"Employee.E.Mail.Address",
-"Position.Title",
-"Pay.Plan",
-"Occupational.Series",
-"Grade",
-"EOD.Date",
-"Supervisor.Level",
-"Supervisor.Level.Description",
-"Supervisor.Display.Name",
-"Supervisor.E.Mail.Address",
-"Business.Line.2.Letter.Department.ID.",
-"GSA.SSO",
-"Agency.Subelement.Code.Description",
-"GSA.Region",
-"GSA.Duty.Station.Region",
-"Location.City",
-"Location.State",
-"Duty.Station.Code",
-"Employee.Job.Bargaining.Unit.Description",
-"Employee.Summary.Bargaining.Unit",
-"Payroll.Accounting.Code",
-"Position.Number",
-"Position.Category.Code",
-"Position.Category.Description"
-),
+tbl <- 
+tbl_combined %>% 
+add_column(
 "Treatment if missing" = c(
+  "Drop observation",
+  "Joined with gsa_sso from roster data, impute from other observations of same staff",
+  "Impute from other observations of same staff",
+  "Joined with department_id from roster data, impute from other observations of same staff",
+  "Joined with full_name from roster data, drop observation",
+  "Joined with supervisor_display_name from roster data, impute from other observations of same staff",
   "Label as missing",
+  "Label as missing",
+  "Label as missing", "Label as missing",
   "Label as missing",
@@
 )
-)
+) %>% 
+  filter(!(`Variable Name` %in% c("gsa_sso","department_id","full_name","supervisor_display_name")))
 ```
@@
 
+<!-- Why mention sq(num obs)/2 if you are not going to use that rule? -->
+
+<!-- Removed -->
+
 To determine the number appropriate number of clusters, several methods
-exist. A rule of thumb to identify the correct number is to use the
-number calculated from:
-
-$$
-\frac{\sqrt{NumberOfObservations}}{2}
-$$
-
-However, for this work, the *elbow method* will be used. To do this, the
+exist. For this work, the *elbow method* will be used. To do this, the
 k-means algorithm will be executed for different numbers of clusters
@@
 clusters appears to be the point where the returns to more cluster
-diminishes. We will also construct silhouette charts to confirm the number of clusters.
+diminishes. We will also construct silhouette charts to confirm the
+number of clusters.
 
@@
 
-    -   Number and proportion of staff by most frequent occupational series
+    -   Number and proportion of staff by most frequent occupational
+        series
 
-    -   Number and proportion of staff by most frequent position category
+    -   Number and proportion of staff by most frequent position
+        category
 
@@
 
-To understand the relationship between staff work patterns and their supervisor, we will calculate the proportion of the staff that fall into the same rule-based and clusters as their supervisors overall, as well as by the above categories.
+To understand the relationship between staff work patterns and their
+supervisor, we will calculate the proportion of the staff that fall into
+the same rule-based and clusters as their supervisors overall, as well
+as by the above categories.
 
-The results will be presented in tables, and we will generate visualizations for a subset of the results for streamlined communication.
-We will use visualizations to validate the work pattern groupings and demonstrate any deviation between clusters, rules-based categories, and stated telework position.
+The results will be presented in tables, and we will generate
+visualizations for a subset of the results for streamlined
+communication. We will use visualizations to validate the work pattern
+groupings and demonstrate any deviation between clusters, rules-based
+categories, and stated telework position.
 
@@
 
-We plan no exploratory analyses. Though, all this work may be considered exploratory.
+We plan no exploratory analyses. Though, all this work may be considered
+exploratory.
 
@@
 
-This is non causal research.
-The work will not demonstrate if changes or attributes caused differences, only if there are relationships.
-K-means clustering can be sensetive to the random locations of the first points selected to calculate differences and define clusters.
+This is non causal research. The work will not demonstrate if changes or
+attributes caused differences, only if there are relationships. K-means
+clustering can be sensetive to the random locations of the first points
+selected to calculate differences and define clusters.

### 2023-03-08 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd
Testing other joins

@@
 ```{r}
-prep_base_1 <- files_1[1] %>% 
+prep_base_1 <- files_1 %>% 
   map_dfr(~mutate(.data = read_csv(., 
@@
   unite(col = "supervisor_display_name",sup_first,sup_last, sep = " ") %>% 
-  rename(file_name_1 =file_name)
+  rename(file_name_1 =file_name)%>% 
+  mutate(
+    date_month = floor_date(date,unit = "month"),
+    date_month_rollback = rollback(date_month),
+    date_month_forward = rollforward(date_month)
+  )
 ```
@@
 prep_base_1_names <- names(prep_base_1)
+```
+
+```{r}
+prep_base_2 <- files_2 %>% 
+  map_dfr(~mutate(.data = read_xlsx(path = ., 
+                                    col_types = c("date", "text", "text", 
+        "text", "text", "text", "text", "text", 
+        "text", "date", "text", "text", "text", 
+        "text", "text", "text", "text", "text", 
+        "text", "text", "text", "text", "text", 
+        "text", "text", "text", "text", "text")), 
+        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
+      )) %>% 
+  clean_names() %>% 
+  distinct() %>% 
+  mutate(
+    across(
+      .cols = where(is.POSIXct),
+      .fns = ~as_date(.)
+    )
+  )
+```
+
+```{r}
+step_1 <- prep_base_1 %>% 
+  inner_join(prep_base_2,
+            by =  c("employee_name" = "full_name"),
+            suffix = c("_daily","_roster")
+  ) %>% 
+  select(-starts_with("file_name")) %>% 
+  distinct() %>% 
+  filter(supervisor_display_name_daily == supervisor_display_name_roster) %>%
+  filter(dept_id == department_id) %>%
+  filter(date_month_rollback == snapshot_date)
+```
+
+```{r}
+step_1 %>%
+  get_dupes(date,employee_e_mail_address) %>%
+  arrange(desc(dupe_count))
+```
+
+```{r}
+step_2 <- 
+  prep_base_1 %>% 
+  anti_join(step_1) %>% 
+  inner_join(prep_base_2,
+            by =  c("employee_name" = "full_name"),
+            suffix = c("_daily","_roster")
+  ) %>% 
+  select(-starts_with("file_name")) %>% 
+  distinct() %>% 
+  filter(supervisor_display_name_daily == supervisor_display_name_roster) %>%
+  filter(dept_id == department_id) %>%
+  filter(date_month_forward == snapshot_date)
+```
+
+```{r}
+prep_base_1 %>% 
+  anti_join(step_1) %>%
+  anti_join(step_2) %>% 
+  inner_join(prep_base_2,
+            by =  c("employee_name" = "full_name"),
+            suffix = c("_daily","_roster")
+  ) %>% 
+  select(-starts_with("file_name")) %>% 
+  distinct() %>% 
+  filter(supervisor_display_name_daily == supervisor_display_name_roster) %>%
+  filter(dept_id == department_id) %>% 
+  select(-snapshot_date) %>% 
+  distinct()
 ```
@@
 step_1 <- prep_base_1 %>% 
+  # select(employee_name) %>% 
+  # distinct() %>% 
    left_join(prep_base_2_1,
@@
   # get_dupes(employee_e_mail_address,date)
+```
+
+```{r}
+step_1 %>% 
+  filter(!is.na(employee_e_mail_address)) %>% 
+  get_dupes(employee_name,date,sso, dept_id, supervisor_display_name)
+```
+
+```{r}
+step_1 %>% 
+  filter(!is.na(employee_e_mail_address)) %>% 
+  get_dupes(employee_e_mail_address,date)
+```
+
+```{r}
+step_2 <- 
+  step_1 %>% 
+  filter(!is.na(employee_e_mail_address)) %>% 
+  get_dupes(employee_name) %>% 
+  select(employee_name) %>% 
+  distinct()
+```
+
+```{r}
+step_3 <- 
+  step_2 %>% 
+  inner_join(prep_base_1 %>% 
+  select(employee_name,sso) %>% 
+    distinct()) %>% 
+  left_join(prep_base_2_1,
+            by = c("employee_name" = "full_name",
+                   "sso" = "gsa_sso"
+                   # ,
+                   # "dept_id" = "department_id",
+                   # "supervisor_display_name" = "supervisor_display_name"
+                   )) %>% 
+  # filter(rollback(date) == snapshot_date |
+  #          rollforward(date) == snapshot_date) %>%
+  # select(-snapshot_date, -starts_with("file_name")) %>% 
+  distinct()
+```
+
+```{r}
+step_3 %>% 
+  filter(!is.na(employee_e_mail_address)) %>% 
+  get_dupes(employee_name,employee_e_mail_address)
 ```

### 2023-03-15 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd
Rewriting with joins including a third step that will be removed

@@
   project_name: "Occupancy Patterns"
-  google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Occupancy Patterns"
+  google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
   data_folder_1: "Occupancy Data Pull"
@@
 knitr::opts_chunk$set(echo = TRUE)
+if(!("arsenal" %in% installed.packages()[,"Package"]))
+{
   install.packages("arsenal")
+}
+if(!("oesrrr" %in% installed.packages()[,"Package"]))
+{
   devtools::install_github(repo = "GSA/oesrrr")
+}
 library(oesrrr)
@@
 
+### Load data
+
 Load all data files in the `r params$data_folder_1` data folder.
@@
 
+Review.
+
+```{r}
+prep_base_1 %>% 
+  skim()
+```
+
+Count number of unique employee_name.
+
+```{r}
+unique_name_base <- prep_base_1 %>% summarise(n_distinct(employee_name)) %>% pull()
+unique_name_base
+```
+
 ```{r}
@@
 ```
+
+Load all data files in the `r params$data_folder_2` data folder.
 
@@
 
+Review.
+
 ```{r}
-step_1 <- prep_base_1 %>% 
+prep_base_2 %>% 
+  skim()
+```
+
+Count number of unique email addresses.
+
+```{r}
+unique_email_base <- prep_base_2 %>% summarise(n_distinct(employee_e_mail_address)) %>% pull()
+unique_email_base
+```
+
+### Join data
+
+First inner join by employee name, supervisor name, department id, and the last date, using the last day of the month before the daily checkin.
+
+```{r}
+prep_xx <- prep_base_1 %>% 
   inner_join(prep_base_2,
-            by =  c("employee_name" = "full_name"),
+            by =  c("employee_name" = "full_name",
+                    "supervisor_display_name" = "supervisor_display_name",
+                    "dept_id" = "department_id",
+                    "date_month_rollback" = "snapshot_date"
+                    ),
             suffix = c("_daily","_roster")
@@
   select(-starts_with("file_name")) %>% 
-  distinct() %>% 
-  filter(supervisor_display_name_daily == supervisor_display_name_roster) %>%
-  filter(dept_id == department_id) %>%
-  filter(date_month_rollback == snapshot_date)
+  distinct()
+```
+
+Review.
+
+```{r}
+prep_xx %>% 
+  skim()
 ```
@@
 ```{r}
-step_1 %>%
+prep_xx %>%
   get_dupes(date,employee_e_mail_address) %>%
@@
 
+Create building dataframe.
+
 ```{r}
-step_2 <- 
+prep_building <- prep_xx
+```
+
+Count unique email addresses in building dataframe.
+
+```{r}
+unique_email_building <- prep_building %>% summarise(n_distinct(employee_e_mail_address)) %>% pull()
+unique_email_building
+```
+
+Test: This does not differ from the base.
+
+```{r}
+unique_email_base == unique_email_building
+```
+Review.
+
+```{r}
+prep_building %>%  skim()
+```
+
+Second, remove data from building dataframe, then inner join by employee name, supervisor name, department id, and the last date, using the last day of the month after the daily checkin.
+
+```{r}
+prep_xx <- 
   prep_base_1 %>% 
-  anti_join(step_1) %>% 
+  anti_join(prep_building) %>% 
   inner_join(prep_base_2,
-            by =  c("employee_name" = "full_name"),
+            by =  c("employee_name" = "full_name",
+                    "supervisor_display_name" = "supervisor_display_name",
+                    "dept_id" = "department_id",
+                    "date_month_forward" = "snapshot_date"
+                    ),
             suffix = c("_daily","_roster")
@@
   select(-starts_with("file_name")) %>% 
-  distinct() %>% 
-  filter(supervisor_display_name_daily == supervisor_display_name_roster) %>%
-  filter(dept_id == department_id) %>%
-  filter(date_month_forward == snapshot_date)
+  distinct()
+```
+
+Review.
+
+```{r}
+prep_xx %>%  skim()
 ```
@@
 ```{r}
+prep_xx %>%
+  get_dupes(date,employee_e_mail_address) %>%
+  arrange(desc(dupe_count))
+```
+
+Bind to buidling dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  bind_rows(prep_xx) %>% 
+  distinct()
+```
+
+Count unique email addresses
+
+```{r}
+unique_email_building <- prep_building %>% summarise(n_distinct(employee_e_mail_address)) %>% pull()
+unique_email_building
+```
+
+Test: This does not differ from the base.
+
+```{r}
+unique_email_base == unique_email_building
+```
+
+Review.
+
+```{r}
+prep_building %>%  skim()
+```
+
+```{r}
+prep_xx <- 
   prep_base_1 %>% 
-  anti_join(step_1) %>%
-  anti_join(step_2) %>% 
+  anti_join(prep_building) %>%
   inner_join(prep_base_2,
-            by =  c("employee_name" = "full_name"),
+            by =  c("employee_name" = "full_name",
+                    "supervisor_display_name" = "supervisor_display_name",
+                    "dept_id" = "department_id"
+                    ),
             suffix = c("_daily","_roster")
@@
   select(-starts_with("file_name")) %>% 
+  distinct()
+```
+
+Review.
+
+```{r}
+prep_xx %>%  skim()
+```
+
+Bind to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  bind_rows(prep_xx) %>% 
+  distinct()
+```
+
+```{r}
+unique_email_building <- prep_building %>% summarise(n_distinct(employee_e_mail_address)) %>% pull()
+unique_email_building
+```
+
+Test: This does not differ from the base.
+
+```{r}
+unique_email_base == unique_email_building
+```
+
+```{r}
+prep_building %>%  skim()
+```
+
+### Create unique person id
+
+```{r}
+prep_unique_id <- 
+  prep_building %>% 
+  select(employee_name,employee_e_mail_address) %>% 
   distinct() %>% 
-  filter(supervisor_display_name_daily == supervisor_display_name_roster) %>%
-  filter(dept_id == department_id) %>% 
-  select(-snapshot_date) %>% 
+  rownames_to_column(var = "person_id")
+```
+
+Review.
+
+```{r}
+prep_unique_id %>% 
+  skim()
+```
+
+### Join to building dataframe
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_unique_id) %>% 
+  select(person_id,everything())
+```
+
+Review.
+
+```{r}
+prep_building %>% 
+  skim()
+```
+
+Check for duplicates on `person_id` and `date`.
+
+```{r}
+prep_building %>% 
+  get_dupes(person_id,date)
+```
+
+Third, remove data from building dataframe, then inner join by employee name.
+
+```{r}
+prep_xx <- 
+  prep_base_1 %>% 
+  anti_join(prep_building) %>%
+  inner_join(prep_base_2,
+            by =  c("employee_name" = "full_name"
+                    ),
+            suffix = c("_daily","_roster")
+  ) %>% 
+  select(-starts_with("file_name")) %>% 
   distinct()
+```
+
+Review.
+
+```{r}
+prep_xx %>%  skim()
+```
+
+Bind to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  bind_rows(prep_xx) %>% 
+  distinct()
+```
+
+```{r}
+unique_email_building <- prep_building %>% summarise(n_distinct(employee_e_mail_address)) %>% pull()
+unique_email_building
+```
+
+Test: This does not differ from the base.
+
+```{r}
+unique_email_base == unique_email_building
+```
+
+```{r}
+prep_building %>%  skim()
 ```

### 2023-03-15 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd
Removing third join that didn't include dates

@@
 Review.
-
-```{r}
-prep_building %>%  skim()
-```
-
-```{r}
-prep_xx <- 
-  prep_base_1 %>% 
-  anti_join(prep_building) %>%
-  inner_join(prep_base_2,
-            by =  c("employee_name" = "full_name",
-                    "supervisor_display_name" = "supervisor_display_name",
-                    "dept_id" = "department_id"
-                    ),
-            suffix = c("_daily","_roster")
-  ) %>% 
-  select(-starts_with("file_name")) %>% 
-  distinct()
-```
-
-Review.
-
-```{r}
-prep_xx %>%  skim()
-```
-
-Bind to building dataframe.
-
-```{r}
-prep_building <- prep_building %>% 
-  bind_rows(prep_xx) %>% 
-  distinct()
-```
-
-```{r}
-unique_email_building <- prep_building %>% summarise(n_distinct(employee_e_mail_address)) %>% pull()
-unique_email_building
-```
-
-Test: This does not differ from the base.
-
-```{r}
-unique_email_base == unique_email_building
-```
 

### 2023-03-15 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Re-arranged Mike's notes, added notes from lab, updated deduplication process

@@
 
-<!-- # MIKES COMMENTS -->
-
-<!-- Proofread for typos -->
-
-<!-- The analysis plan is a good place to define the rules for classification -->
-<!-- Re: missing supervisor name and some other values. It is possible that -->
-<!-- people change supervisors or departments. Do we care about this? And how -->
-<!-- should we deal with it? At a minimum, maybe we want a slightly different -->
-<!-- imputation like if supervisor is the same both with earlier and later -->
-<!-- nonmissing observations, use that value, otherwise use prior supervisor? -->
-
-<!-- How are you doing team classification? Are you going to generate a team -->
-<!-- ID based on some rule? If so what is it, and to the prior point, how do -->
-<!-- you handle changing team composition over time? -->
-
-<!-- Not sure about using percentiles for cutoffs. I would assume based on -->
-<!-- classifications that more that 5 percent of teams are fully remote. For -->
-<!-- individuals, i think there is more alignment on things like number of -->
-<!-- days in a pay period in the office because of policy definitions for -->
-<!-- people who are not remote and have to be in the office 2 days per pay -->
-<!-- period. For teams maybe an extension of that basic ideas (e.g., fewer -->
-<!-- than 2 days in office on average is fully remote) -->
-
-<!-- Are all of these taking averages over the whole time period (9 months or -->
-<!-- whatever)? Would we potentially want to know about things like people -->
-<!-- who have more specific weekly patterns? -->
-
-<!-- The thing that is missing here that is potentially more complicated is -->
-<!-- figuring out more about how teams operate as collections of individuals. -->
-<!-- For example, you could I think in this approach have a team that is 20 -->
-<!-- percent average telework where everyone goes in person on Mondays and -->
-<!-- the rest of the time is distributed, or you could have a team that is 20 -->
-<!-- percent telework where people go in at random times and never see each -->
-<!-- other. I am interested to know the extent to which people are -->
-<!-- co-locating with their teams (and if some people are being left -->
-<!-- out---which may help motivate some equity questions about performance -->
-<!-- ratings for people who don't get face time with the boss, for example). -->
-<!-- I think we are missing that level of analysis here. -->
+#Proofread for typos
 
@@
 daily check-in data has no true unique identifier. The roster data is
-uniquely identified by `employee_e_mail_address` and `snapshot_date`.
+uniquely identified by `employee_e_mail_address` and `snapshot_date`, but some entries for `employee_e_mail_address` are null. 
 The roster data *should not* have any duplications on
@@
 
-1.  Start with check-in data from one month (call this *month 1*)
+1.  Import all months of check-in data
 
-2.  Transform supervisor name to match format of the roster data
+2.
+Transform supervisor name to match format of the roster data, and create new variables for the end of the month prior to the check-in date and the end of the month of the check-in date to match the `snapshot_date`
 
-3.  Join roster data from the previous month (call this *month 0*) on
-    employee name, staff or service office, department ID and supervisor
-    name
+3.  Inner join check-in and roster data  on employee name, department ID and supervisor name, and prior month, creating a new data set called `joined data 1`
 
-4.  Check to see if any rows are missing `employee_e_mail_address` after
-    the join
+4.
+Remove rows in `joined data 1` from the check-in data (i.e.
+anti-join), then inner join check-in and roster data  on employee name, department ID and supervisor name, and current month, creating a new data set called `joined data 2`
 
-5.  For any rows missing `employee_e_mail_address`, join roster data
-    from data from *month 1*
+5.  Bind row from `joined data 1` and `joined data 2`, creating a new data set called `bound data`
 
-6.  Check to see if any rows are missing `employee_e_mail_address` after
-    the join
+6.  Select the distinct employee email addresses and names from `bound data` and assign a unique identifier to this called `person_id`, creating a new data set called `unique ID`
 
-7.  For any rows missing `employee_e_mail_address`, join roster data
-    from data from *month 2*
+7.  Join the `unique ID` to `bound data` on employee email addresses and names
 
@@
 After this, the combined data *should* be uniquely identified by
-`employee_e_mail_address` and `date`. The data set will contain all the
+`person_id` and `date`. The data set will contain all the
 daily check-in and roster information across the observation window.
@@
 <!-- [I might be more discerning about using "staff" vs. "employees" vs. "teams" vs. "groups" vs. "clusters" -- we are grouping employees into teams, but also categorizing them.]  -->
+
+<!-- How are you doing team classification? Are you going to generate a team -->
+<!-- ID based on some rule? If so what is it, and to the prior point, how do -->
+<!-- you handle changing team composition over time? -->
+
+ADD TEAM CLAFFICATION RULES FOR STAFF AND TEAM ANALYSIS
 
@@
 <!-- [Describe criteria you will use to determine whether any observations should be excluded from analysis (e.g., values that are likely data-recording errors, outliers, etc.).] -->
+
+<!-- The analysis plan is a good place to define the rules for classification -->
+<!-- Re: missing supervisor name and some other values. It is possible that -->
+<!-- people change supervisors or departments. Do we care about this? And how -->
+<!-- should we deal with it? At a minimum, maybe we want a slightly different -->
+<!-- imputation like if supervisor is the same both with earlier and later -->
+<!-- nonmissing observations, use that value, otherwise use prior supervisor? -->
 
@@
 <!-- [prompt] -->
+
+<!-- Not sure about using percentiles for cutoffs. I would assume based on -->
+<!-- classifications that more that 5 percent of teams are fully remote. For -->
+<!-- individuals, i think there is more alignment on things like number of -->
+<!-- days in a pay period in the office because of policy definitions for -->
+<!-- people who are not remote and have to be in the office 2 days per pay -->
+<!-- period. For teams maybe an extension of that basic ideas (e.g., fewer -->
+<!-- than 2 days in office on average is fully remote) -->
+
+<!-- Are all of these taking averages over the whole time period (9 months or -->
+<!-- whatever)? Would we potentially want to know about things like people -->
+<!-- who have more specific weekly patterns? -->
+
+<!-- The thing that is missing here that is potentially more complicated is -->
+<!-- figuring out more about how teams operate as collections of individuals. -->
+<!-- For example, you could I think in this approach have a team that is 20 -->
+<!-- percent average telework where everyone goes in person on Mondays and -->
+<!-- the rest of the time is distributed, or you could have a team that is 20 -->
+<!-- percent telework where people go in at random times and never see each -->
+<!-- other. I am interested to know the extent to which people are -->
+<!-- co-locating with their teams (and if some people are being left -->
+<!-- out---which may help motivate some equity questions about performance -->
+<!-- ratings for people who don't get face time with the boss, for example). -->
+<!-- I think we are missing that level of analysis here. -->
+
+<!-- MD: There are policy definitions of remote.
+100% of days could be classified as all remote (separate rule); policy rules if you are not a full-time worker (you are a teleworker) you report two days a pay period; could align cut-offs with policy type definitions.
+# of days cutoff.
+-->
+<!-- Ben: the way I defined groups is mutually exclusive, but does not need to be that way -->
+<!-- Ben: Other rules to examine -->
+<!-- JB: policy side, missingness (whole groups of people missing on some dimension tells you something about data collection procedure) -->
+
+<!-- MD: other roster data might be relevant - position category could give diff patterns for people who are analysts vs.
+building inspectors or supervisors vs.
+non supervisors, pay grade; lower pay grade less likely to have remote option -->
+<!-- Ben: confusion matrix - assume that some group works in this sort of way but guess what they don’t! What is happening? -->
+
+<!-- MD: categories: onsite flexible, onsite, remote; but not sure of levels of going in within categories. What is the average of going in? -->
+<!-- MD: discretion of work patterns by regional commissioners  -->
 

### 2023-03-15 04. Analysis/scripts/01-data-preparation-joas.Rmd
Update 01-data-preparation-joas.Rmd
example from opm work updated

@@
   date_earliest_open: '2022-01-01'
-  data_latest_close: '2022-12-01'
+  data_latest_close: '2022-12-31'
 ---
@@
     across(
-      .cols = c(usajobs_control_number,
+      .cols = starts_with("usajobs_control_number")|
                 # announcement_closing_type,
@@
                 # hiring_department_code,
-                series),
+                starts_with("series"),
       .fns = ~as.character(.)
@@
   files %>% 
-  filter(str_detect(file,"_full_") | str_detect(file,"Positions_Updated_Dec2022")) %>%
+  filter(str_detect(file,"_full_") | 
+           str_detect(file,"Positions_Updated_Dec2022") 
+         ) %>%
   select(file,encoding)
@@
 files_full
+```
+
+#### Load 'allpositionsopenedduring2022'
+
+Load position headers for the data.
+
+```{r}
+positions_headers <- 
+  here::here(params$data_folder_1,"positions_headers.csv") %>% 
+  read_csv() %>% 
+      distinct()
+```
+
+Load the data and apply the position headers.
+
+```{r}
+prep_all_positions <- 
+  files %>% 
+  filter(
+    str_detect(file,"allpositionsopenedduring2022")
+         ) %>%
+  pull(file) %>%  
+  load_utf8(
+  ) %>% 
+  rename_all(~names(positions_headers)) %>% 
+  clean_names() %>% 
+  prepare_joa()
 ```
@@
   ) %>% 
+  bind_rows(prep_all_positions) %>% 
   distinct()
@@
 
+#### Load 'hiring path' files
+
+Load first hiring path file.
+
+```{r}
+prep_hiring_path_01 <- 
+   read_csv(here::here(params$data_folder_1,"hiringpath_remotework.csv"),
+   col_types = cols(`Hiring Path` = col_character(), 
+        `Position Open Date` = col_skip(), 
+        `Position Close Date` = col_skip(), 
+        `USAJOBS Control Number` = col_character())
+   ) %>% 
+  clean_names() %>% 
+  distinct()
+```
+
+Collect the names from the dataframe.
+
+```{r}
+prep_hiring_path_01_names <- sort(names(prep_hiring_path_01), decreasing = TRUE)
+```
+
+Load second hiring path file, and apply names from the first dataset.
+
+```{r}
+prep_hiring_path_02 <- read_csv(here::here(params$data_folder_1,"positions - hiring path - 2022.csv"),
+    col_names = FALSE, col_types = cols(X1 = col_character(), 
+        X2 = col_skip(), X3 = col_skip(), 
+        X4 = col_character())) %>% 
+  distinct() %>% 
+  rename_at(
+    vars(everything()),
+    ~prep_hiring_path_01_names
+  )
+```
+
+Bind dataframes and convert hiring path to indicators.
+
+```{r}
+prep_hiring_path <- 
+  prep_hiring_path_01 %>% 
+  bind_rows(prep_hiring_path_02) %>% 
+  distinct() %>% 
+  character_to_indicator(in_unique_identifier = params$unique_identifier_1,
+                         in_variable = hiring_path,
+                         in_prefix = "hiring_path")
+
+```
+
+```{r}
+prep_hiring_path %>% 
+  skim()
+```
+
+#### Load 'work schedule and appointment type' files
+
+Load first work schedule and appointment type file.
+
+```{r}
+prep_work_schedule_appointment_01 <- 
+   read_csv(here::here(params$data_folder_1,"positions - work schedule and appointment type.csv"), 
+    col_types = cols(Announcement_Number = col_skip(), 
+        USAJOBS_Control_Number = col_character())
+   ) %>% 
+  clean_names() %>% 
+  distinct()
+```
+
+Convert work schedule to indicators.
+
+```{r}
+prep_work_schedule <- 
+  prep_work_schedule_appointment_01 %>% 
+  distinct() %>% 
+  character_to_indicator(in_unique_identifier = params$unique_identifier_1,
+                         in_variable = position_work_schedule_type,
+                         in_prefix = "work_schedule")
+
+```
+
+Convert appointment type to indicators.
+
+```{r}
+prep_appointment <- 
+  prep_work_schedule_appointment_01 %>% 
+  distinct() %>% 
+  character_to_indicator(in_unique_identifier = params$unique_identifier_1,
+                         in_variable = position_appointment_type,
+                         in_prefix = "appointment_type")
+
+```
+
+Join indicator dataframes.
+
+```{r}
+prep_work_schedule_appointment <- 
+  prep_work_schedule %>% 
+  full_join(prep_appointment)
+```
+
+```{r}
+prep_work_schedule_appointment %>% 
+  skim()
+```
+
+#### Load 'series' files
+
+Load first series file.
+
+```{r}
+prep_series_01 <- 
+   read_csv(here::here(params$data_folder_1,"positions - series - 2022.csv"), 
+    col_types = cols(USAJOBS_Control_Number = col_character(), 
+        Announcement_Number = col_skip(), 
+        Series = col_character(), Series_Title = col_character())) %>% 
+  clean_names() %>% 
+  distinct()
+```
+
+Rename.
+
+```{r}
+prep_series <- 
+  prep_series_01
+```
+
+```{r}
+prep_series %>% 
+  skim()
+```
+
+#### Load 'locations' files
+
+Load first locations file.
+
+```{r}
+prep_locations_01 <- 
+   read_csv(here::here(params$data_folder_1,"positions - locations - 2022.csv"), 
+   col_types = cols(`Announcement Number` = col_skip(), 
+        `USAJOBS Control Number` = col_character(), 
+        `Position Open Date` = col_date(format = "%m/%d/%Y"), 
+        `Position Close Date` = col_date(format = "%m/%d/%Y"), 
+        `Position Location City` = col_character(), 
+        `Position Location Country` = col_character(), 
+        `Position Location Geo-location Code` = col_character(), 
+        `Position Location State` = col_character(), 
+        `Position Location Zip` = col_character())) %>% 
+  clean_names() %>% 
+  distinct()
+```
+
+Rename.
+
+```{r}
+prep_location <- 
+  prep_locations_01
+```
+
+```{r}
+prep_location %>% 
+  skim()
+```
+
+Check for duplicates.
+
+```{r}
+dupes_location <- 
+  prep_location %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupes_location
+```
+
+Count by number of duplications.
+
+```{r}
+dupes_location %>% 
+  count(dupe_count)
+```
+Count number of `position_location_geo_location_code`.
+
+```{r}
+location_count <- 
+  prep_location %>% 
+  group_by(position_location_city,position_location_country,
+           position_location_geo_location_code,
+           position_location_state,position_location_zip) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rownames_to_column(var = 'rank')
+
+location_count
+```
+
+Check to see if any of these 'NULL' are duplicated.
+
+```{r}
+dupes_location %>% 
+  filter(position_location_geo_location_code == "NULL")
+```
+
+Aggregate location data to deduplicate, counting multiple locations.
+
+```{r}
+prep_location_n_distinct <- 
+  prep_location %>%
+  group_by(usajobs_control_number
+           ,position_close_date, 
+           position_open_date
+           ) %>%
+  summarise(
+    across(
+      .cols = everything(),
+      .fns = ~n_distinct(.),
+      .names = "{.col}_n_distinct"
+      )
+  ) %>% 
+  ungroup() %>% 
+  mutate(
+    multiple_location_ind = 
+      case_when(if_any(ends_with("_n_distinct"), ~ .x > 1) ~ 1,
+                TRUE ~ 0
+                ),
+  ) %>% 
+  arrange(position_location_geo_location_code_n_distinct)
+
+prep_location_n_distinct %>% 
+  skim()
+```
+
+Aggregate location data to deduplicate, assigning locations by least and most common.
+
+```{r}
+prep_location_common <-
+  prep_location %>%
+  left_join(location_count) %>% 
+  group_by(usajobs_control_number
+           ,position_close_date, 
+           position_open_date
+           ) %>%
+  arrange(usajobs_control_number
+           ,position_close_date, 
+           position_open_date,
+          rank) %>% 
+  summarise(
+    across(
+      .cols = everything(),
+      .fns = list(most_common = first, least_common = last),
+      .names = "{.col}_{.fn}"
+      )
+  ) %>% 
+  ungroup()
+
+prep_location_common %>% 
+  skim()
+```
+
+# CONTINUE FROM HERE
+
 ## Filter to correct dates
@@
   count()
+```
+
+Also create a building dataframe to add other deduplicated dataframes.
+
+```{r}
+prep_building <- prep_uniq
 ```
@@
   duplicating_variables %>% 
+  mutate(group = 
+           case_when(variable == "position_open_date" ~ "dates",
+                     variable == "position_close_date" ~ "dates",
+                     variable == "announcement_closing_type" ~ "announcement_closing_type",
+                     variable == "announcement_closing_type_description" ~ "announcement_closing_type",
+                     variable == "announcement_closing_type_option" ~ "announcement_closing_type",
+                     variable == "application_limit" ~ "application_limit",
+                     variable == "application_limit_set" ~ "application_limit",
+                     variable == "application_limit_number" ~ "application_limit",
+                     variable == "agency_level" ~ "agency_level",
+                     variable == "agency_level_sort" ~ "agency_level",
+                     variable == "hiring_agency_code" ~ "agency_level",
+                     variable == "hiring_agency_name" ~ "agency_level",
+                     variable == "hiring_department_code" ~ "agency_level",
+                     variable == "hiring_department_name" ~ "agency_level",
+                     variable == "maximum_salary" ~ "maximum_salary",
+                     variable == "minimum_salary" ~ "maximum_salary",
+                     variable == "maximum_grade" ~ "maximum_salary",
+                     variable == "minimum_grade" ~ "maximum_salary",
+                     variable == "series" ~ "series",
+                     variable == "series_title" ~ "series",
+                     variable == "mission_critical_code" ~ "mission_critical_code",
+                     variable == "mission_critical_code_description" ~ "mission_critical_code",
+                     variable == "mission_critical_source" ~ "mission_critical_code",
+                     TRUE ~ variable
+                     ))
+
+duplicating_variables
+```
+
+Create list of groups.
+
+```{r}
+duplicating_groups <- 
+  duplicating_variables %>% 
+  select(group) %>% 
+  distinct() %>% 
+  arrange(group) %>% 
+  pull()
+
+duplicating_groups
+```
+
+### Duplication removal
+
+```{r}
+step_n <- 0
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `agency_level`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+A few things going on here:
+
+1.    Department of Defense agencies are duplicated because sometimes sub-departments (e.i. Department of Navy) are considered the *Department*
+2.    Many duplicates are caused by blank values in hiring agency code and agency level.
+
+First let's remove duplicates because of department.
+To do this, we will group by control number, then arrange by and control number and descending agency level.
+Then, we take the data in the first entry.
+
+```{r}
+dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  group_by_at(params$unique_identifier_1) %>% 
+  arrange(usajobs_control_number,desc(agency_level)) %>% 
+  summarise(
+    across(
+      .cols = everything(),
+      .fns = first
+    )
+  ) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+```
+
+Now we will apply all of these to the whole dataframe.
+
+```{r}
+dedupe <- 
+  prep_base %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  group_by_at(params$unique_identifier_1) %>% 
+  arrange(usajobs_control_number,desc(agency_level)) %>% 
+  summarise(
+    across(
+      .cols = everything(),
+      .fns = first
+    )
+  ) %>% 
+  distinct() %>% 
+  ungroup()
+
+dedupe %>% 
+  get_dupes(params$unique_identifier_1)
+```
+
+Let's review this data set.
+
+```{r}
+prep_xx <- 
+  dedupe
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `announcement_closing_type`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Check to see if the type codes are consistent to the description.
+
+```{r}
+prep_base %>% 
+  count(announcement_closing_type,announcement_closing_type_description)
+```
+
+Codes are consistent to description, but the code adds no new information. We will drop the code and transform the description into columns of indicators.
+
+We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
+We will update the NA column to include announcements where there are no other indicators equal to one except NA.
+
+```{r}
+prep_xx <-
+  prep_base %>% 
+  character_to_indicator(params$unique_identifier_1,announcement_closing_type_description,"closing_type") %>% 
+  mutate(
+    closing_type_na = case_when(
+      closing_type_closing_date == 1 ~ 0,
+      closing_type_applicant_cut_off == 1 ~ 0,
+      closing_type_open_continuous == 1 ~ 0,
+      closing_type_missing == 1 ~ 0,
+      closing_type_closing_time == 1 ~ 0,
+      closing_type_na == 1 ~ 1,
+    )
+  )
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Rename dataframe and count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `announcement_number`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+```
+
+Some of these duplicates may be due to small typos. Transforming the string to upper case.
+
+```{r}
+dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  mutate(
+    announcement_number = str_to_upper(announcement_number)
+  ) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+```
+
+This fixes some, but not all.
+
+Without better information, we will take the lower of the two values for the remainder.
+
+Apply this to the entire dataframe.
+
+```{r}
+dedupe <- 
+  prep_base %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  mutate(
+    announcement_number = str_to_upper(announcement_number)
+  ) %>% 
+  distinct() %>% 
+  arrange(params$unique_identifier_1,announcement_number) %>% 
+  group_by_at(params$unique_identifier_1) %>% 
+  summarise(announcement_number = first(announcement_number)) %>% 
+  ungroup()
+
+dedupe %>% 
+  get_dupes(params$unique_identifier_1)
+```
+
+Review the dataframe.
+
+```{r}
+prep_xx <- 
+  dedupe
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Rename dataframe and count rows.
+
+```{r}
+prep_01 <- prep_xx
+
+prep_01 %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_01 %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `application_limit`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Not too many.
+It appears that `application_limit_set` is "N" when `application_limit` is "Applicant Cut-Off".
+Also `application_limit_number` appears to only be valid when `application_limit_set` is NA.
+
+First count the statuses across the original data.
+
+```{r}
+prep_base %>% count(application_limit,application_limit_set)
+```
+
+Now let's look at `application_limit_number`.
+
+```{r}
+prep_base %>% 
+  filter(!is.na(application_limit_number)) %>% 
+  select(all_of(params$unique_identifier_1),application_limit_number) %>% 
+  distinct()
+```
+
+Only a very few rows have values for `application_limit_number`. We will drop this column.
+
+All NA `application_limit` are "N" `application_limit_set`.
+Also NA in `application_limit_set` have values in `application_limit`.
+We will apply the `application_limit` values to NAs in `application_limit_set`.
+
+We will consider "Y" the correct response for all and we will change this into an indicator.
+
+We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
+
+```{r}
+prep_xx <- 
+  prep_base %>% 
+  mutate(
+    application_limit_set = case_when(is.na(application_limit_set) ~ application_limit,
+                                      TRUE ~ application_limit_set)
+  ) %>% 
+  character_to_indicator(params$unique_identifier_1,application_limit_set,"application_limit_set") %>% 
+  # Drop the "N" column
+  select(-application_limit_set_n)
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `appointment_type``
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Lots of them, but appears to be mainly because of NAs.
+
+First count the statuses across the original data.
+
+```{r}
+prep_base %>% count(appointment_type)
+```
+
+We'll want to transform these into indicators and transform the NAs so that they are only for *true* NAs.
+
+We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
+
+```{r}
+prep_xx <- 
+  prep_base %>% 
+  character_to_indicator(params$unique_identifier_1,appointment_type,"appointment_type") %>% 
+  mutate(
+    appointment_type_na = case_when(
+      appointment_type_permanent == 1 ~ 0,
+      appointment_type_term == 1 ~ 0,
+      appointment_type_intermittent == 1 ~ 0,
+      appointment_type_temporary == 1 ~ 0,
+      appointment_type_internships == 1 ~ 0,
+      appointment_type_multiple_appointment_types == 1 ~ 0,
+      appointment_type_temporary_promotion == 1 ~ 0,
+      appointment_type_recent_graduates == 1 ~ 0,
+      appointment_type_detail == 1 ~ 0,
+      appointment_type_seasonal == 1 ~ 0,
+      appointment_type_agency_employees_only == 1 ~ 0,
+      appointment_type_summer == 1 ~ 0,
+      appointment_type_ictap_only == 1 ~ 0,
+      appointment_type_presidential_management_fellows == 1 ~ 0,
+      appointment_type_telework == 1 ~ 0,
+      appointment_type_na == 1 ~ 1
+    )
+  )
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `dates`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Duplication appear to be because of difference in open and close dates. After messaging with Melissa, we decide to retain the dates as determined by the close date.
+
+We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
+
+```{r}
+prep_xx <- 
+  prep_base %>% 
+   select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>%
+  arrange(params$unique_identifier_1, position_close_date) %>% 
+  group_by(usajobs_control_number) %>% 
+  summarise(
+    across(
+      .cols = all_of(duplicating_group %>% pull(variable)),
+      .fns = last
+    )
+  )
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `disable_apply_online`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Quite a few. It appears that `disable_apply_online` in NA in many duplicates.
+
+First count the statuses across the original data.
+
+```{r}
+prep_base %>% count(disable_apply_online)
+```
+
+There are just a few, but we'll want to transform these into indicators.
+
+We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
+
+Since there is only one instance of this type of duplication, we will still drop the no column.
+
+```{r}
+prep_xx <- 
+  prep_base %>% 
+  character_to_indicator(params$unique_identifier_1,disable_apply_online,"disable_apply_online") %>% 
+  mutate(
+    disable_apply_online_na = case_when(
+      disable_apply_online_n == 1 ~ 0,
+      disable_apply_online_y == 1 ~ 0,
+      disable_apply_online_na == 1 ~ 1
+    )
+  )
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `hiring_subelement_name`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Count types.
+
+```{r}
+prep_base %>% 
+  count(hiring_subelement_name)
+```
+
+Many blank entries and a level of detail we don't need. We will drop this column.
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `is_remote_work_eligible`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Duplication appear to be because `r duplicating_group %>% pull(variable)` is empty in one row. Transform the empties into 'N'.
+
+We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
+
+```{r}
+prep_xx <- 
+  prep_base %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  mutate(
+    is_remote_work_eligible = case_when(is_remote_work_eligible == "" ~ "N",
+                                        is_remote_work_eligible == "NULL" ~ "N",
+                                        TRUE ~ is_remote_work_eligible)
+  ) %>% 
+  distinct() %>% 
+  character_to_indicator(in_unique_identifier = params$unique_identifier_1,
+                         in_variable = is_remote_work_eligible,
+                         in_prefix = "is_remote_work_eligible") %>% 
+  # Drop the "n" indicatoris_remote_work_eligible
+  select(-is_remote_work_eligible_n)
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `maximum_salary`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Appears like this comes from posting the job again with revised salary information.
+
+Like above we decide to retain the later dates as determined by the close date.
+
+```{r}
+prep_xx <- 
+  prep_base %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
+  arrange(params$unique_identifier_1, position_close_date) %>% 
+  group_by(usajobs_control_number) %>% 
+  summarise(
+    across(
+      .cols = all_of(duplicating_group %>% pull(variable)),
+      .fns = last
+    )
+  )
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `mission_critical_code`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Let's count the entries here.
+
+```{r}
+prep_base %>% 
+  group_by(across(all_of(duplicating_group %>% pull(variable)))) %>% 
+  count()
+```
+
+Lots of entries here. So we don't want to make indicators. Looks like they are created by rows with a null. We'll count how many nulls and entries with values.
+
+```{r}
+dupe_02 %>% 
+  mutate(cause = case_when(is.na(mission_critical_code) ~ 'null',
+                           TRUE ~ 'value'),
+         ind = 1) %>% 
+  select(usajobs_control_number,cause,ind) %>% 
+  distinct() %>% 
+  pivot_wider(names_from = cause, values_from = ind) %>% 
+  summarise(
+    unique = n_distinct(usajobs_control_number),
+    nulls = sum(null),
+    values = sum(value, na.rm = TRUE)
+  )
+```
+
+Select the rows that have an entry if they have that.
+
+```{r}
+prep_xx <- 
+  prep_base %>% 
+    select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>%
+  arrange(usajobs_control_number,mission_critical_code) %>% 
+  group_by(usajobs_control_number) %>% 
+  summarise(
+    across(
+      .fns = first
+    )
+  ) %>% 
+  ungroup()
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `number_of_views`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Let's count the entries here.
+
+```{r}
+prep_base %>% 
+  group_by(across(all_of(duplicating_group %>% pull(variable)))) %>% 
+  count()
+```
+
+This looks pretty unreliable. We dill drop `number_of_views`.
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `position_opening_status`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Let's count the entries.
+
+```{r}
+prep_base %>% 
+  group_by(across(all_of(duplicating_group %>% pull(variable)))) %>% 
+  count()
+```
+
+We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
+We will update the NA column to include announcements where there are no other indicators equal to one except NA.
+
+```{r}
+prep_xx <-
+  prep_base %>% 
+  character_to_indicator(params$unique_identifier_1,
+                         position_opening_status,
+                         "position_opening_status") %>%
+  mutate(
+    position_opening_status_na = case_when(
+      position_opening_status_job_canceled == 1 ~ 0,
+      position_opening_status_applications_under_review == 1 ~ 0,
+      position_opening_status_candidate_selected == 1 ~ 0,
+      position_opening_status_accepting_applications == 1 ~ 0,
+      position_opening_status_job_closed == 1 ~ 0,
+      position_opening_status_missing == 1 ~ 0,
+      position_opening_status_na	== 1 ~ 1,
+    )
+  )
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `position_title`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Let's count the entries here.
+
+```{r}
+prep_base %>% 
+  group_by(across(all_of(duplicating_group %>% pull(variable)))) %>% 
+  count()
+```
+
+Lots of options. We'll try to use the ones associated with later closing dates.
+
+```{r}
+prep_xx <- 
+  prep_base %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
+  arrange(params$unique_identifier_1, position_close_date) %>% 
+  group_by(usajobs_control_number) %>% 
+  summarise(
+    across(
+      .cols = all_of(duplicating_group %>% pull(variable)),
+      .fns = last
+    )
+  )
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `series`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Let's count the entries here.
+
+```{r}
+prep_base %>% 
+  group_by(across(all_of(duplicating_group %>% pull(variable)))) %>% 
+  count()
+```
+
+There are more series types than we want to make indicators for.
+
+Let's reviewing duplicates, but include closing date.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1,position_close_date)
+
+dupe_02
+```
+
+Duplication also exists for `position_close_date`.
+If an announcement has multiple series on a the same closing date, we'll define the announcement as "(Multiple)".
+For others, we'll use close date to select the correct value.
+
+```{r}
+prep_xx_01 <- 
+  prep_base %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
+  group_by(across(all_of(params$unique_identifier_1)),position_close_date) %>% 
+  summarise(
+    across(
+      .cols = all_of(duplicating_group %>% pull(variable)),
+      .fns = ~n_distinct(.),
+      .names = "{.col}_n_distinct"
+    )
+  ) %>% 
+  ungroup()
+
+prep_xx_02 <- 
+  prep_base %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
+  left_join(prep_xx_01) %>% 
+  mutate(
+    series = case_when(series_n_distinct > 1 ~ "(Multiple)",
+                       TRUE ~ series),
+    series_title = case_when(series_title_n_distinct > 1 ~ "(Multiple)",
+                       TRUE ~ series_title)
+  )
+
+prep_xx <-
+  prep_xx_02 %>% 
+  arrange(params$unique_identifier_1, position_close_date) %>% 
+  group_by(across(all_of(params$unique_identifier_1))) %>% 
+  summarise(
+    across(
+      .cols = all_of(c(duplicating_group %>% pull(variable),"series_n_distinct","series_title_n_distinct")),
+      .fns = last
+    )
+  )
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `supervisory_status`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Let's count the entries here.
+
+```{r}
+prep_base %>% 
+  group_by(across(all_of(duplicating_group %>% pull(variable)))) %>% 
+  count()
+```
+
+Only two options, but they don't make sense as indicators. We'll use close date to select the correct value.
+
+```{r}
+prep_xx <- 
+  prep_base %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
+  arrange(params$unique_identifier_1, position_close_date) %>% 
+  group_by(usajobs_control_number) %>% 
+  summarise(
+    across(
+      .cols = all_of(duplicating_group %>% pull(variable)),
+      .fns = last
+    )
+  )
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `telework_eligibility_description`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Let's count the entries here.
+
+```{r}
+prep_base %>% 
+  group_by(across(all_of(duplicating_group %>% pull(variable)))) %>% 
+  count()
+```
+
+No useful information here. We will drop this column.
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `total_openings`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Let's count the entries here.
+
+```{r}
+prep_base %>% 
+  group_by(across(all_of(duplicating_group %>% pull(variable)))) %>% 
+  count()
+```
+
+We'll take the entries associated with the later closing date.
+
+```{r}
+prep_xx <- 
+  prep_base %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
+  arrange(params$unique_identifier_1, position_close_date) %>% 
+  group_by(usajobs_control_number) %>% 
+  summarise(
+    across(
+      .cols = all_of(duplicating_group %>% pull(variable)),
+      .fns = last
+    )
+  )
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `who_may_apply`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Let's count the entries here.
+
+```{r}
+prep_base %>% 
+  group_by(across(all_of(duplicating_group %>% pull(variable)))) %>% 
+  count()
+```
+
+Only a few categories. We will transform these into indicators.
+
+```{r}
+prep_xx <- 
+  prep_base %>% 
+  character_to_indicator(params$unique_identifier_1,who_may_apply,"who_may_apply") %>% 
+  mutate(
+    who_may_apply_missing = case_when(
+      who_may_apply_united_states_citizens == 1 ~ 0,
+      who_may_apply_agency_employees_only == 1 ~ 0,
+      who_may_apply_status_candidates_merit_promotion_and_veoa_eligibles == 1 ~ 0,
+      who_may_apply_missing == 1 ~ 1,
+      who_may_apply_null == 1 ~ 1,
+    )
+  ) %>% 
+  select(-who_may_apply_null)
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `work_schedule`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+Reviewing duplicates.
+
+```{r}
+dupe_02 <- 
+  dupe_01 %>% 
+  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  distinct() %>% 
+  get_dupes(params$unique_identifier_1)
+
+dupe_02
+```
+
+Let's count the entries here.
+
+```{r}
+prep_base %>% 
+  group_by(across(all_of(duplicating_group %>% pull(variable)))) %>% 
+  count()
+```
+
+Only a few categories. We will transform these into indicators. Many NAs.
+
+```{r}
+prep_xx <- 
+  prep_base %>% 
+  character_to_indicator(params$unique_identifier_1,work_schedule,"work_schedule") %>%
+  mutate(
+    work_schedule_na = case_when(
+      work_schedule_full_time == 1 ~ 0,
+      work_schedule_part_time == 1 ~ 0,
+      work_schedule_intermittent == 1 ~ 0,
+      work_schedule_multiple_schedules == 1 ~ 0,
+      work_schedule_shift_work == 1 ~ 0,
+      work_schedule_job_sharing == 1 ~ 0,
+      work_schedule_na == 1 ~ 1
+    )
+  )
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`
+
+Removing duplicates produced by:
+
+```{r}
+duplicating_group <- 
+  duplicating_variables %>% 
+  filter(group == duplicating_groups[step_n])
+duplicating_group
+```
+
+All done with duplicates!
+
+### Combinding deduplicated data
+
+#### Create dataframe off non-duplicating columns
+
+Collect column names of variables not creating duplicates.
+
+```{r}
+non_duplicating_variables <- 
+  column_meta_data %>% 
+  filter(!duplicates_by_variable) %>% 
+  pull(variable)
+
+non_duplicating_variables
+```
+
+Create dataframe of only these variables.
+
+```{r}
+prep_xx <- 
+  prep_base %>% 
+  select(any_of(non_duplicating_variables)) %>% 
+  distinct()
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Count rows.
+
+```{r}
+prep_xx %>% 
+  count()
+```
+
+Do the number of in this dataframe match the number of unique identifiers?
+
+```{r}
+prep_xx %>% 
+  count() %>% 
+  pull() ==
+  prep_uniq %>% 
+  count() %>% 
+  pull()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_building %>% 
+  left_join(prep_xx)
+```
+
+### Checking duplicating columns have been fixed
+
+Created a dataframe of variable metadata.
+
+```{r}
+column_meta_data_dedupe <- 
+  prep_building %>% 
+  contents()
+
+column_meta_data_dedupe <- 
+  column_meta_data_dedupe$contents %>% 
+  as.data.frame()
+
+column_meta_data_dedupe <-
+  column_meta_data_dedupe %>% 
+  rownames_to_column(var = "variable")
+
+column_meta_data_dedupe
+```
+
+Checking duplicates for each variable in the dataframe.
+
+```{r}
+duplicates_by_variable <- 
+  column_meta_data_dedupe %>% 
+  pull(variable) %>% 
+  map_lgl(~dupe_check(in_data = prep_building, .))
+
+duplicates_by_variable
+```
+
+Add this to the column_meta_data dataframe.
+
+```{r}
+column_meta_data_dedupe <- 
+  column_meta_data_dedupe %>% 
+  add_column(
+    duplicates_by_variable = duplicates_by_variable
+  )
+
+column_meta_data_dedupe
+```
+
+Create dataframe of only variables that cause duplicates.
+
+```{r}
+duplicating_variables <- 
+  column_meta_data_dedupe %>% 
+  filter(duplicates_by_variable)
+
+duplicating_variables
+```
+
+## Addressing blanks
+
+Function that checks whether there are blanks for different variables
+
+```{r}
+blank_check <- function(in_data,in_variable_name)
+{
+  check_01 <- 
+  in_data %>% 
+    filter(!!sym(in_variable_name) == "") %>% 
+  distinct()
+
+out <- nrow(check_01) > 0
+
+return(out)
+}
+```
+
+Checking duplicates for each variable in the dataframe.
+
+```{r}
+blanks_by_variable <- 
+  column_meta_data_dedupe %>% 
+  pull(variable) %>% 
+  map_lgl(~blank_check(in_data = prep_building,.))
+
+blanks_by_variable
+```
+
+Add this to the `column_meta_data_dedupe` dataframe.
+
+```{r}
+column_meta_data_dedupe <- 
+  column_meta_data_dedupe %>% 
+  add_column(
+    blanks_by_variable = blanks_by_variable
+  )
+
+column_meta_data_dedupe
+```
+
+Create dataframe of only variables that have blanks.
+
+```{r}
+blanking_variables <- 
+  column_meta_data_dedupe %>% 
+  filter(blanks_by_variable)
+
+blanking_variables
+```
+
+Grouping variables.
+
+```{r}
+blanking_variables <- 
+  blanking_variables %>% 
   mutate(group = 
@@
                      variable == "series_title" ~ "series",
+                     variable == "mission_critical_code" ~ "mission_critical_code",
+                     variable == "mission_critical_code_description" ~ "mission_critical_code",
+                     variable == "mission_critical_source" ~ "mission_critical_code",
                      TRUE ~ variable
@@
 
-duplicating_variables
+blanking_variables
 ```
@@
 ```{r}
-duplicating_groups <- 
-  duplicating_variables %>% 
+blanking_groups <- 
+  blanking_variables %>% 
   select(group) %>% 
   distinct() %>% 
+  arrange(group) %>% 
   pull()
 
-duplicating_groups
-```
-
-### Duplication removal
+blanking_groups
+```
+
+Also create a building dataframe to add other dataframes where missing have been removed.
+
+```{r}
+prep_building_missing <- prep_uniq
+```
+
+### Blanks removal
 
@@
 
+#### Step `r step_n`: `agency_level`
+
+Removing blanks produced by
+
+```{r}
+blanking_variable <- 
+  blanking_variables %>% 
+  filter(group == blanking_groups[step_n])
+
+blanking_variable
+```
+
+Reviewing blanks.
+
+```{r}
+blanks_01 <- 
+  prep_building %>% 
+  filter(if_any(all_of(blanking_variable %>% pull(variable)),  ~.x == "")) %>% 
+  select(all_of(blanking_variable %>% pull(variable)),everything())
+
+blanks_01
+```
+
+Blanks appear to be caused by a few columns:
+
+1.    `hiring_agency_code` appears to be blank for agencies that don't fall into departments
+2.    `hiring_agency_name` appears to be blank for the Air Force
+
+Let's count the extent of the issues.
+
+```{r}
+blanking_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~blanks_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(!!sym(.x) == "")
+  )
+```
+
+A lot of blanks in `hiring_agency_code`, some in `hiring_agency_name`, and very few in `hiring_department_name`.
+
+Let's see what happens when we assign rows with `hiring_department_name` "Department of the Air Force" with "Department of Defense" and place "Department of the Air Force" in `hiring_agency_name`.
+
+```{r}
+blanks_01 <- 
+  prep_building %>% 
+  mutate(
+    hiring_agency_name = case_when(
+      hiring_agency_name == "" & hiring_department_name == "Department of the Air Force" ~ "Department of the Air Force",
+      TRUE ~ hiring_agency_name
+    ),
+    hiring_department_name = case_when(
+      hiring_agency_name == "" & hiring_department_name == "Department of the Air Force" ~ "Department of Defense",
+      TRUE ~ hiring_department_name
+    )
+  ) %>% 
+  filter(if_any(all_of(blanking_variable %>% pull(variable)),  ~.x == "")) %>% 
+  select(all_of(blanking_variable %>% pull(variable)),everything())
+
+blanks_01
+```
+
+That gets rid of many. Now let's investigate `hiring_agency_code`.
+
+```{r}
+prep_building %>% 
+  count(hiring_agency_code,hiring_agency_name)
+```
+
+This doesn't appear to add addition information to `hiring_agency_name`. We will drop and test for blanks.
+
+```{r}
+blanks_01 <- 
+  prep_building %>% 
+  mutate(
+    hiring_agency_name = case_when(
+      hiring_agency_name == "" & hiring_department_name == "Department of the Air Force" ~ "Department of the Air Force",
+      TRUE ~ hiring_agency_name
+    ),
+    hiring_department_name = case_when(
+      hiring_agency_name == "" & hiring_department_name == "Department of the Air Force" ~ "Department of Defense",
+      TRUE ~ hiring_department_name
+    )
+  ) %>% 
+  select(-hiring_agency_code) %>% 
+  filter(if_any(c(hiring_agency_name,hiring_department_name),  ~.x == "")) %>% 
+  select(hiring_agency_name,hiring_department_name,everything())
+
+blanks_01
+```
+
+Still a few thousand with missing `hiring_agency_name`. Replace these with "(Missing)" and test.
+
+```{r}
+blanks_01 <- 
+  prep_building %>% 
+  mutate(
+    hiring_agency_name = case_when(
+      hiring_agency_name == "" & hiring_department_name == "Department of the Air Force" ~ "Department of the Air Force",
+      TRUE ~ hiring_agency_name
+    ),
+    hiring_department_name = case_when(
+      hiring_agency_name == "" & hiring_department_name == "Department of the Air Force" ~ "Department of Defense",
+      TRUE ~ hiring_department_name
+    )
+  ) %>% 
+  select(-hiring_agency_code) %>% 
+  mutate(
+    hiring_agency_name = case_when(
+      hiring_agency_name == "" ~ "(Missing)",
+      TRUE ~ hiring_agency_name
+    )
+  ) %>% 
+  filter(if_any(c(hiring_agency_name,hiring_department_name),  ~.x == "")) %>% 
+  select(hiring_agency_name,hiring_department_name,everything())
+
+blanks_01
+```
+
+Now a few with missing `hiring_department_name`.
+These appear to have "Public Defender Service for the District of Columbia" in `hiring_agency_name`.
+Replace the blank in `hiring_department_name` for "Other Agencies and Independent Organizations".
+
+```{r}
+blanks_01 <- 
+  prep_building %>% 
+  mutate(
+    hiring_agency_name = case_when(
+      hiring_agency_name == "" & hiring_department_name == "Department of the Air Force" ~ "Department of the Air Force",
+      TRUE ~ hiring_agency_name
+    ),
+    hiring_department_name = case_when(
+      hiring_agency_name == "" & hiring_department_name == "Department of the Air Force" ~ "Department of Defense",
+      TRUE ~ hiring_department_name
+    )
+  ) %>% 
+  select(-hiring_agency_code) %>% 
+  mutate(
+    hiring_agency_name = case_when(
+      hiring_agency_name == "" ~ "(Missing)",
+      TRUE ~ hiring_agency_name
+    )
+  ) %>% 
+  mutate(
+    hiring_department_name = case_when(
+      hiring_department_name == "" & hiring_agency_name == "Public Defender Service for the District of Columbia" ~ 
+        "Other Agencies and Independent Organizations",
+      TRUE ~ hiring_department_name
+    )
+  ) %>% 
+  filter(if_any(c(hiring_agency_name,hiring_department_name),  ~.x == "")) %>% 
+  select(hiring_agency_name,hiring_department_name,everything())
+
+blanks_01
+```
+
+Now apply this to the entire dataframe.
+
+```{r}
+prep_xx <- 
+  prep_building %>% 
+  mutate(
+    hiring_agency_name = case_when(
+      hiring_agency_name == "" & hiring_department_name == "Department of the Air Force" ~ "Department of the Air Force",
+      TRUE ~ hiring_agency_name
+    ),
+    hiring_department_name = case_when(
+      hiring_agency_name == "" & hiring_department_name == "Department of the Air Force" ~ "Department of Defense",
+      TRUE ~ hiring_department_name
+    )
+  ) %>% 
+  select(-hiring_agency_code) %>% 
+  mutate(
+    hiring_agency_name = case_when(
+      hiring_agency_name == "" ~ "(Missing)",
+      TRUE ~ hiring_agency_name
+    )
+  ) %>% 
+  mutate(
+    hiring_department_name = case_when(
+      hiring_department_name == "" & hiring_agency_name == "Public Defender Service for the District of Columbia" ~ 
+        "Other Agencies and Independent Organizations",
+      TRUE ~ hiring_department_name
+    )
+  ) %>% 
+  select(usajobs_control_number,hiring_agency_name,hiring_department_name)
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building_missing <- prep_building_missing %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `mission_critical_code`
+
+Removing blanks produced by
+
+```{r}
+blanking_variable <- 
+  blanking_variables %>% 
+  filter(group == blanking_groups[step_n])
+
+blanking_variable
+```
+
+Reviewing blanks.
+
+```{r}
+blanks_01 <- 
+  prep_building %>% 
+  filter(if_any(all_of(blanking_variable %>% pull(variable)),  ~.x == "")) %>% 
+  select(all_of(blanking_variable %>% pull(variable)),everything())
+
+blanks_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+blanking_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~blanks_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(!!sym(.x) == "")
+  )
+```
+
+The same number or missing from each group.
+
+Let's count the entries here.
+
+```{r}
+prep_building %>% 
+  group_by(across(all_of(blanking_variable %>% pull(variable)))) %>% 
+  count()
+```
+
+The case majority are missing. For all of these, we will recode to "(Missing)". We'll do that and test.
+
+```{r}
+blanks_01 <- 
+  prep_building %>% 
+  mutate(
+    across(
+      .cols = all_of(blanking_variable %>% pull(variable)),
+      .fns = ~case_when(
+        . == "" ~ "(Missing)",
+        . == "NULL" ~ "(Missing)",
+        is.na(.) ~ "(Missing)",
+        TRUE ~ .
+      )
+    )
+  ) %>% 
+  filter(if_any(all_of(blanking_variable %>% pull(variable)),  ~.x == "")) %>% 
+  select(all_of(blanking_variable %>% pull(variable)),everything())
+
+blanks_01
+```
+
+Now apply this to the entire dataframe.
+
+```{r}
+prep_xx <- 
+  prep_building %>% 
+   mutate(
+    across(
+      .cols = all_of(blanking_variable %>% pull(variable)),
+      .fns = ~case_when(
+        . == "" ~ "(Missing)",
+        . == "NULL" ~ "(Missing)",
+        is.na(.) ~ "(Missing)",
+        TRUE ~ .
+      )
+    )
+  ) %>% 
+    select(usajobs_control_number,all_of(blanking_variable %>% pull(variable)))
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building_missing <- prep_building_missing %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `series_title`
+
+Removing blanks produced by
+
+```{r}
+blanking_variable <- 
+  blanking_variables %>% 
+  filter(group == blanking_groups[step_n])
+
+blanking_variable
+```
+
+Reviewing blanks.
+
+```{r}
+blanks_01 <- 
+  prep_building %>% 
+  filter(if_any(all_of(blanking_variable %>% pull(variable)),  ~.x == "")) %>% 
+  select(all_of(blanking_variable %>% pull(variable)),everything())
+
+blanks_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+blanking_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~blanks_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(!!sym(.x) == "")
+  )
+```
+
+The same number or missing from each group.
+
+Let's count the entries here. We'll add `series` as well.
+
+```{r}
+prep_building %>% 
+  group_by(across(all_of(blanking_variable %>% pull(variable))),series) %>% 
+  count()
+```
+
+Just one row is blank. We'll replace `series_title` with "(Missing)" and test.
+
+```{r}
+blanks_01 <- 
+  prep_building %>% 
+  mutate(
+    series_title = case_when(
+      series_title == "" ~ "(Missing)",
+      TRUE ~ series_title
+    )
+  ) %>% 
+  filter(if_any(all_of(blanking_variable %>% pull(variable)),  ~.x == "")) %>% 
+  select(all_of(blanking_variable %>% pull(variable)),everything())
+
+blanks_01
+```
+
+Now apply this to the entire dataframe.
+
+```{r}
+prep_xx <- 
+  prep_building %>% 
+    mutate(
+    series_title = case_when(
+      series_title == "" ~ "(Missing)",
+      TRUE ~ series_title
+    )
+  ) %>% 
+    select(usajobs_control_number,all_of(blanking_variable %>% pull(variable)))
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building_missing <- prep_building_missing %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
 #### Step `r step_n`
 
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+Removing blanks produced by
+
+```{r}
+blanking_variable <- 
+  blanking_variables %>% 
+  filter(group == blanking_groups[step_n])
+
+blanking_variable
+```
+
+All done!
+
+### Combinding blank data
+
+#### Create dataframe off non-blank columns
+
+Collect column names of variables not creating duplicates.
+
+```{r}
+non_blanking_variables <- 
+  column_meta_data_dedupe %>% 
+  filter(!blanks_by_variable) %>% 
+  pull(variable)
+
+non_blanking_variables
+```
+
+Create dataframe of only these variables.
+
+```{r}
+prep_xx <- 
+  prep_building %>% 
+  select(any_of(non_blanking_variables)) %>% 
+  distinct()
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building_missing <- prep_building_missing %>% 
+  left_join(prep_xx)
+```
+
+### Checking blanking columns have been fixed
+
+Created a dataframe of variable metadata.
+
+```{r}
+column_meta_data_dedupe_missing <- 
+  prep_building_missing %>% 
+  contents()
+
+column_meta_data_dedupe_missing <- 
+  column_meta_data_dedupe_missing$contents %>% 
+  as.data.frame()
+
+column_meta_data_dedupe_missing <-
+  column_meta_data_dedupe_missing %>% 
+  rownames_to_column(var = "variable")
+
+column_meta_data_dedupe_missing
+```
+
+Checking duplicates for each variable in the dataframe.
+
+```{r}
+blanks_by_variable <- 
+  column_meta_data_dedupe_missing %>% 
+  pull(variable) %>% 
+  map_lgl(~blank_check(in_data = prep_building_missing,.))
+
+blanks_by_variable
+```
+
+Add this to the `column_meta_data_dedupe` dataframe.
+
+```{r}
+column_meta_data_dedupe_missing <- 
+  column_meta_data_dedupe_missing %>% 
+  add_column(
+    blanks_by_variable = blanks_by_variable
+  )
+
+column_meta_data_dedupe_missing
+```
+
+Create dataframe of only variables that have blanks.
+
+```{r}
+blanking_variables <- 
+  column_meta_data_dedupe_missing %>% 
+  filter(blanks_by_variable)
+
+blanking_variables
+```
+
+## Addressing nulls
+
+Create variable to identify columns with NAs.
+
+```{r}
+column_meta_data_dedupe_missing <- 
+  column_meta_data_dedupe_missing %>% 
+  mutate(
+    nulls_by_variable = case_when(
+      NAs == 0 ~ FALSE,
+      NAs > 0 ~ TRUE
+    )
+  )
+
+column_meta_data_dedupe_missing
+```
+
+Create dataframe of only variables that have blanks.
+
+```{r}
+nulling_variables <- 
+  column_meta_data_dedupe_missing %>% 
+  filter(nulls_by_variable)
+
+nulling_variables
+```
+
+Grouping variables.
+
+```{r}
+nulling_variables <- 
+  nulling_variables %>% 
+  mutate(group = 
+           case_when(variable == "position_open_date" ~ "dates",
+                     variable == "position_close_date" ~ "dates",
+                     variable == "announcement_closing_type" ~ "announcement_closing_type",
+                     variable == "announcement_closing_type_description" ~ "announcement_closing_type",
+                     variable == "application_limit" ~ "application_limit",
+                     variable == "application_limit_set" ~ "application_limit",
+                     variable == "agency_level" ~ "agency_level",
+                     variable == "agency_level_sort" ~ "agency_level",
+                     variable == "hiring_agency_code" ~ "agency_level",
+                     variable == "hiring_agency_name" ~ "agency_level",
+                     variable == "hiring_department_code" ~ "agency_level",
+                     variable == "hiring_department_name" ~ "agency_level",
+                     variable == "maximum_salary" ~ "maximum_salary",
+                     variable == "minimum_salary" ~ "maximum_salary",
+                     variable == "maximum_grade" ~ "maximum_salary",
+                     variable == "minimum_grade" ~ "maximum_salary",
+                     variable == "series" ~ "series",
+                     variable == "series_title" ~ "series",
+                     variable == "mission_critical_code" ~ "mission_critical_code",
+                     variable == "mission_critical_code_description" ~ "mission_critical_code",
+                     variable == "mission_critical_source" ~ "mission_critical_code",
+                     TRUE ~ variable
+                     ))
+
+nulling_variables
+```
+
+Create list of groups.
+
+```{r}
+nulling_groups <- 
+  nulling_variables %>% 
+  select(group) %>% 
   distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-Some of these duplicates may be due to small typos. Transforming the string to upper case.
-
-```{r}
-dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  arrange(group) %>% 
+  pull()
+
+nulling_groups
+```
+
+Also create a building dataframe to add other dataframes where missing have been removed.
+
+```{r}
+prep_building_missing_nulls <- prep_uniq
+```
+
+### Nulls removal
+
+```{r}
+step_n <- 0
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `agency_level`
+
+Removing nulls produced by
+
+```{r}
+nulling_variable <- 
+  nulling_variables %>% 
+  filter(group == nulling_groups[step_n])
+
+nulling_variable
+```
+
+Reviewing blanks.
+
+```{r}
+nulls_01 <- 
+  prep_building_missing %>% 
+  filter(if_any(all_of(nulling_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(nulling_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+nulling_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~nulls_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(is.na(!!sym(.x)))
+  )
+```
+
+Let's count the entries here.
+
+```{r}
+prep_building_missing %>% 
+  group_by(across(all_of(nulling_variable %>% pull(variable))),hiring_department_name, hiring_agency_name) %>% 
+  count() %>% 
+  arrange(agency_level_sort)
+```
+
+None of these columns appear to added information that isn't part of `hiring_department_name` or `hiring_agency_name`. We will drop them
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `maximum_salary`
+
+Removing nulls produced by
+
+```{r}
+nulling_variable <- 
+  nulling_variables %>% 
+  filter(group == nulling_groups[step_n])
+
+nulling_variable
+```
+
+Reviewing blanks.
+
+```{r}
+nulls_01 <- 
+  prep_building_missing %>% 
+  filter(if_any(all_of(nulling_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(nulling_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+nulling_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~nulls_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(is.na(!!sym(.x)))
+  )
+```
+
+Let's count the entries here.
+
+```{r}
+prep_building_missing %>% 
+  group_by(across(all_of(nulling_variable %>% pull(variable)))) %>% 
+  count() %>% 
+  arrange()
+```
+
+Very few examples. We will transform these to "(Missing)" and then test.
+
+```{r}
+nulls_01 <- 
+  prep_building_missing %>% 
   mutate(
-    announcement_number = str_to_upper(announcement_number)
-  ) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-This fixes some, but not all.
-
-Without better information, we will take the lower of the two values for the remainder.
-
-```{r}
-dedupe <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+    across(
+      .cols = all_of(nulling_variable %>% pull(variable)),
+      .fns = ~case_when(is.na(.) ~ "(Missing)",
+                        TRUE ~ .)
+    )
+  ) %>% 
+  filter(if_any(all_of(nulling_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(nulling_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Now apply this to the entire dataframe.
+
+```{r}
+prep_xx <- 
+  prep_building_missing %>% 
     mutate(
-    announcement_number = str_to_upper(announcement_number)
-  ) %>% 
-  distinct() %>% 
-  arrange(params$unique_identifier_1,announcement_number) %>% 
-  group_by_at(params$unique_identifier_1) %>% 
-  summarise(announcement_number = first(announcement_number))
-
-dedupe %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.
-
-First create a dataframe of distinct rows of the variables from the original data.
-
-```{r}
-working_01 <- 
-  prep_base %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+    across(
+      .cols = all_of(nulling_variable %>% pull(variable)),
+      .fns = ~case_when(is.na(.) ~ "(Missing)",
+                        TRUE ~ .)
+    )
+  ) %>% 
+    select(usajobs_control_number,all_of(nulling_variable %>% pull(variable)))
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building_missing_nulls <- prep_building_missing_nulls %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `pay_scale`
+
+Removing nulls produced by
+
+```{r}
+nulling_variable <- 
+  nulling_variables %>% 
+  filter(group == nulling_groups[step_n])
+
+nulling_variable
+```
+
+Reviewing blanks.
+
+```{r}
+nulls_01 <- 
+  prep_building_missing %>% 
+  filter(if_any(all_of(nulling_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(nulling_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+nulling_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~nulls_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(is.na(!!sym(.x)))
+  )
+```
+
+Let's count the entries here.
+
+```{r}
+prep_building_missing %>% 
+  group_by(across(all_of(nulling_variable %>% pull(variable))),pay_scale_description) %>% 
+  count() %>% 
+  arrange()
+```
+
+No additional information in `pay_scale`. We will drop this column.
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `second_announcement`
+
+Removing nulls produced by
+
+```{r}
+nulling_variable <- 
+  nulling_variables %>% 
+  filter(group == nulling_groups[step_n])
+
+nulling_variable
+```
+
+Reviewing blanks.
+
+```{r}
+nulls_01 <- 
+  prep_building_missing %>% 
+  filter(if_any(all_of(nulling_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(nulling_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+nulling_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~nulls_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(is.na(!!sym(.x)))
+  )
+```
+
+Let's count the entries here.
+
+```{r}
+prep_building_missing %>% 
+  group_by(across(all_of(nulling_variable %>% pull(variable)))) %>% 
+  count() %>% 
+  arrange()
+```
+
+Completely blank. We will drop.
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `series`
+
+Removing nulls produced by
+
+```{r}
+nulling_variable <- 
+  nulling_variables %>% 
+  filter(group == nulling_groups[step_n])
+
+nulling_variable
+```
+
+Reviewing blanks.
+
+```{r}
+nulls_01 <- 
+  prep_building_missing %>% 
+  filter(if_any(all_of(nulling_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(nulling_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+nulling_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~nulls_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(is.na(!!sym(.x)))
+  )
+```
+
+Let's count the entries here.
+
+```{r}
+prep_building_missing %>% 
+  group_by(across(all_of(nulling_variable %>% pull(variable)))) %>% 
+  count()
+```
+
+All examples have missing series titles. We will transform these to "(Missing)" and then test.
+
+```{r}
+nulls_01 <- 
+  prep_building_missing %>% 
+  mutate(
+    across(
+      .cols = all_of(nulling_variable %>% pull(variable)),
+      .fns = ~case_when(is.na(.) ~ "(Missing)",
+                        TRUE ~ .)
+    )
+  ) %>% 
+  filter(if_any(all_of(nulling_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(nulling_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Now apply this to the entire dataframe.
+
+```{r}
+prep_xx <- 
+  prep_building_missing %>% 
+    mutate(
+    across(
+      .cols = all_of(nulling_variable %>% pull(variable)),
+      .fns = ~case_when(is.na(.) ~ "(Missing)",
+                        TRUE ~ .)
+    )
+  ) %>% 
+    select(usajobs_control_number,all_of(nulling_variable %>% pull(variable)))
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building_missing_nulls <- prep_building_missing_nulls %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `total_openings`
+
+Removing nulls produced by
+
+```{r}
+nulling_variable <- 
+  nulling_variables %>% 
+  filter(group == nulling_groups[step_n])
+
+nulling_variable
+```
+
+Reviewing blanks.
+
+```{r}
+nulls_01 <- 
+  prep_building_missing %>% 
+  filter(if_any(all_of(nulling_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(nulling_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+nulling_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~nulls_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(is.na(!!sym(.x)))
+  )
+```
+
+Let's count the entries here.
+
+```{r}
+prep_building_missing %>% 
+  group_by(across(all_of(nulling_variable %>% pull(variable)))) %>% 
+  count() %>% 
+  arrange()
+```
+
+We will replace the nulls with the median value of the existing values for the column and create an indicator for rows that had data missing.
+
+First, calculate the median value.
+
+```{r}
+total_openings_median <- 
+  prep_building_missing %>% 
+  summarise(
+    median(total_openings,na.rm = TRUE)
+  ) %>% 
+  pull()
+
+total_openings_median
+```
+
+Now apply to nulls and create indicator.
+
+```{r}
+nulls_01 <- 
+  prep_building_missing %>% 
+  mutate(
+    total_openings_na = case_when(is.na(total_openings) ~ 1,
+                                  TRUE ~ 0),
+    total_openings = case_when(is.na(total_openings) ~ total_openings_median,
+                                  TRUE ~ total_openings),
+  ) %>% 
+  filter(if_any(all_of(c(nulling_variable %>% pull(variable),"total_openings_na")),  ~is.na(.x))) %>% 
+  select(all_of(nulling_variable %>% pull(variable)),total_openings_na,everything())
+
+nulls_01
+```
+
+Now apply this to the entire dataframe.
+
+```{r}
+prep_xx <- 
+  prep_building_missing %>% 
+    mutate(
+    total_openings_na = case_when(is.na(total_openings) ~ 1,
+                                  TRUE ~ 0),
+    total_openings = case_when(is.na(total_openings) ~ total_openings_median,
+                                  TRUE ~ total_openings),
+  ) %>% 
+    select(usajobs_control_number,all_of(nulling_variable %>% pull(variable)),total_openings_na)
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building_missing_nulls <- prep_building_missing_nulls %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `telework_eligibility_description`
+
+Removing nulls produced by
+
+```{r}
+nulling_variable <- 
+  nulling_variables %>% 
+  filter(group == nulling_groups[step_n])
+
+nulling_variable
+```
+
+Reviewing blanks.
+
+```{r}
+nulls_01 <- 
+  prep_building_missing %>% 
+  filter(if_any(all_of(nulling_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(nulling_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+nulling_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~nulls_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(is.na(!!sym(.x)))
+  )
+```
+
+Let's count the entries here.
+
+```{r}
+prep_building_missing %>% 
+  group_by(across(all_of(nulling_variable %>% pull(variable)))) %>% 
+  count() %>% 
+  arrange()
+```
+
+`r nulling_variable %>% pull(variable)` is either null or has the value "NULL".
+
+We will drop this column.
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`
+
+Removing nulls produced by
+
+```{r}
+nulling_variable <- 
+  nulling_variables %>% 
+  filter(group == nulling_groups[step_n])
+
+nulling_variable
+```
+
+Done with nulls.
+
+### Combinding nulls data
+
+#### Create dataframe off non-null columns
+
+Collect column names of variables not creating duplicates.
+
+```{r}
+non_nulling_variables <- 
+  column_meta_data_dedupe_missing %>% 
+  filter(!nulls_by_variable) %>% 
+  pull(variable)
+
+non_nulling_variables
+```
+
+Create dataframe of only these variables.
+
+```{r}
+prep_xx <- 
+  prep_building_missing %>% 
+  select(any_of(non_nulling_variables)) %>% 
   distinct()
 
-working_01 %>% 
+prep_xx %>% 
   glimpse()
 
-working_01 %>% 
+prep_xx %>% 
   skim()
@@
 
-Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.
-
-```{r}
-working_02 <- 
-  working_01 %>% 
-  anti_join(dedupe %>% select(params$unique_identifier_1))
-
-working_02 %>% 
-  glimpse()
-
-working_02 %>% 
+Join to building dataframe.
+
+```{r}
+prep_building_missing_nulls <- prep_building_missing_nulls %>% 
+  left_join(prep_xx)
+```
+
+### Checking nulling columns have been fixed
+
+Created a dataframe of variable metadata.
+
+```{r}
+column_meta_data_dedupe_missing_nulls <- 
+  prep_building_missing_nulls %>% 
+  contents()
+
+column_meta_data_dedupe_missing_nulls <- 
+  column_meta_data_dedupe_missing_nulls$contents %>% 
+  as.data.frame()
+
+column_meta_data_dedupe_missing_nulls <-
+  column_meta_data_dedupe_missing_nulls %>% 
+  rownames_to_column(var = "variable")
+
+column_meta_data_dedupe_missing_nulls
+```
+
+Function that checks whether there are duplicates for different variables
+
+```{r}
+null_check <- function(in_data,in_variable_name)
+{
+  check_01 <- 
+  in_data %>% 
+    filter(is.na(!!sym(in_variable_name))) %>% 
+  distinct()
+
+out <- nrow(check_01) > 0
+
+return(out)
+}
+```
+
+Checking duplicates for each variable in the dataframe.
+
+```{r}
+nulls_by_variable <- 
+  column_meta_data_dedupe_missing_nulls %>% 
+  pull(variable) %>% 
+  map_lgl(~null_check(in_data = prep_building_missing_nulls,.))
+
+nulls_by_variable
+```
+
+Add this to the `column_meta_data_dedupe_missing_nulls` dataframe.
+
+```{r}
+column_meta_data_dedupe_missing_nulls <- 
+  column_meta_data_dedupe_missing_nulls %>% 
+  add_column(
+    nulls_by_variable = nulls_by_variable
+  )
+
+column_meta_data_dedupe_missing_nulls
+```
+
+Create dataframe of only variables that have blanks.
+
+```{r}
+nulling_variables <- 
+  column_meta_data_dedupe_missing_nulls %>% 
+  filter(nulls_by_variable)
+
+nulling_variables
+```
+
+## Attaching telework data
+
+Left join telework data to announcement data and then review.
+
+```{r}
+prep_building_missing_nulls %>% 
+  left_join(prep_telework, by = "usajobs_control_number", suffix = c("_building", "_telework")) %>% 
+  skim(usajobs_control_number,starts_with("telework_eligible"))
+```
+
+Left join and count results.
+
+```{r}
+prep_building_missing_nulls %>% 
+  left_join(prep_telework, by = "usajobs_control_number", suffix = c("_building", "_telework")) %>% 
+  count(telework_eligible_building, telework_eligible_telework)
+```
+
+`telework_eligible_building` has no variable and `telework_eligible_telework` has lots of NULLs.
+
+We will attach the data and drop `telework_eligible_building` from the `prep_building_missing_nulls` dataframe.
+We will transform this into indicators for a position being telework eligible and for the value being null.
+
+```{r}
+prep_xx <- 
+  prep_building_missing_nulls %>% 
+  select(-telework_eligible) %>% 
+  left_join(prep_telework, by = "usajobs_control_number") %>% 
+  mutate(
+    telework_eligible = case_when(telework_eligible == 1 ~ "y",
+                                  telework_eligible == 0 ~ "n")
+  ) %>% 
+  character_to_indicator(in_unique_identifier = params$unique_identifier_1, in_variable = telework_eligible, in_prefix = "telework_eligible") %>% 
+  select(-telework_eligible_n)
+
+prep_xx %>% 
+  skim(starts_with("telework_eligible"))
+```
+
+Join onto existing data.
+
+```{r}
+prep_building_missing_nulls <- 
+  prep_building_missing_nulls %>% 
+  left_join(prep_xx)
+
+prep_building_missing_nulls %>% 
+  skim(starts_with("telework_eligible"))
+```
+
+## Attaching hiring path data
+
+Left join hiring path data to announcement data and then review.
+
+```{r}
+prep_building_missing_nulls %>% 
+  left_join(prep_hiring_path, by = "usajobs_control_number", suffix = c("_building", "_telework")) %>% 
+  skim(usajobs_control_number,starts_with("hiring_path"))
+```
+
+Looks good, but we have some nulls. Let's review those.
+
+```{r}
+names_hiring_path <- prep_hiring_path %>% 
+  select(starts_with("hiring_path")) %>% 
+  names()
+prep_building_missing_nulls %>% 
+  left_join(prep_hiring_path, by = "usajobs_control_number", suffix = c("_building", "_telework")) %>% 
+  filter(if_any(names_hiring_path,  ~is.na(.x))) %>% 
+  select(all_of(names_hiring_path),everything())
+```
+
+All the same entries. We'll set these `hiring_path_na` to 1 for these rows and the other `hiring_path_*` variables to 0.
+
+```{r}
+prep_building_missing_nulls %>% 
+  left_join(prep_hiring_path, by = "usajobs_control_number", suffix = c("_building", "_telework")) %>% 
+  mutate(
+    hiring_path_na = case_when(is.na(hiring_path_na) ~ 1, 
+                               TRUE ~ hiring_path_na)
+  ) %>% 
+  mutate(
+    across(
+      .cols = starts_with("hiring_path"),
+      .fns = ~case_when(is.na(.) ~ 0, 
+                               TRUE ~ .)
+    )
+  ) %>% 
+  skim(usajobs_control_number,starts_with("hiring_path"))
+```
+
+```{r}
+prep_xx <- 
+  prep_uniq %>% 
+ left_join(prep_hiring_path, by = "usajobs_control_number", suffix = c("_building", "_telework")) %>% 
+  mutate(
+    hiring_path_na = case_when(is.na(hiring_path_na) ~ 1, 
+                               TRUE ~ hiring_path_na)
+  ) %>% 
+  mutate(
+    across(
+      .cols = starts_with("hiring_path"),
+      .fns = ~case_when(is.na(.) ~ 0, 
+                               TRUE ~ .)
+    )
+  )
+
+prep_xx %>% 
   skim()
@@
 
-Last bind this dataframe to the deduplicated set above.
+Join onto existing data.
+
+```{r}
+prep_building_missing_nulls <- 
+  prep_building_missing_nulls %>% 
+  left_join(prep_xx)
+
+prep_building_missing_nulls %>% 
+  skim(starts_with("hiring_path"))
+```
+
+## Attaching appointment and work schedule data
+
+Left join appointment and work schedule data to announcement data and then review.
 
@@
 prep_xx <- 
-  working_02 %>% 
-  bind_rows(dedupe)
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
+  prep_building_missing_nulls %>% 
+  left_join(prep_work_schedule_appointment, by = "usajobs_control_number", suffix = c("_building", "_join")) %>% 
+  select(usajobs_control_number,starts_with("appointment_"),starts_with("work_schedule_")) 
+prep_xx %>% 
+  select(order(colnames(prep_xx))) %>% 
   skim()
@@
 
-Rename dataframe and count rows.
-
-```{r}
-prep_01 <- prep_xx
-
-prep_01 %>% 
+Collect names.
+
+```{r}
+names_xx <- prep_work_schedule_appointment %>% names()
+```
+
+Function to count differences between columns by variable prefix.
+
+```{r}
+counting_differences <- function(in_data,in_variable_prefix)
+{
+   in_data %>%
+    select(starts_with(in_variable_prefix)) %>%
+    group_by(across(all_of(starts_with(in_variable_prefix)))) %>% 
     count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_01 %>% 
-  count() %>% 
-  pull() ==
+}
+```
+
+Counting differences.
+
+```{r}
+ names_xx[-1] %>% 
+  map(
+    ~counting_differences(in_data = prep_xx, in_variable_prefix = .)
+  )
+```
+
+We want to take the values from the attached dataframe, unless they are null.
+
+Exact matches.
+
+```{r}
+ prep_xx_01 <- 
+  prep_building_missing_nulls %>% 
+  select(all_of(names_xx)) %>% 
+  inner_join(prep_work_schedule_appointment)
+```
+
+`r params$unique_identifier_1` not in `prep_work_schedule_appointment`.
+
+```{r}
+ prep_xx_02 <- 
+  prep_building_missing_nulls %>% 
+  select(usajobs_control_number) %>% 
+  anti_join(prep_work_schedule_appointment) %>% 
+  inner_join(prep_building_missing_nulls) %>% 
+  select(all_of(names_xx)) 
+```
+
+In `prep_work_schedule_appointment`, but not above two.
+
+```{r}
+prep_xx_03 <- 
+  prep_work_schedule_appointment %>% 
+  anti_join(
+    prep_xx_01 %>% 
+      bind_rows(prep_xx_02) %>% 
+      select(usajobs_control_number) %>% 
+      distinct()
+
+  )
+```
+Bind the above.
+
+```{r}
+prep_xx_04 <- 
+  prep_xx_01 %>% 
+  bind_rows(prep_xx_02) %>% 
+  bind_rows(prep_xx_03) %>% 
+  distinct()
+```
+
+Join to the unique `r params$unique_identifier_1`.
+
+```{r}
+prep_xx <- 
   prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_02 <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-
-dupe_02
-```
-
-Duplication appear to be because of difference in open and close dates. After messaging with Melissa, we decide to retain the later dates as determined by the close date.
-
-```{r}
-dedupe <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>%
-  arrange(params$unique_identifier_1, position_close_date) %>% 
-  group_by(usajobs_control_number) %>% 
-  summarise(
-    across(
-      .cols = all_of(duplicating_group %>% pull(variable)),
-      .fns = last
-    )
-  )
-
-dedupe %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.
-
-First create a dataframe of distinct rows of the variables from the original data.
-
-```{r}
-working_01 <- 
-  prep_base %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+  left_join(prep_xx_04)
+
+prep_xx %>% 
+  skim()
+```
+
+Join onto existing data, while droping the original colums.
+
+```{r}
+prep_building_missing_nulls <-
+  prep_building_missing_nulls  %>% 
+  select(-all_of(names_xx[-1])) %>% 
+  left_join(prep_xx)
+
+prep_building_missing_nulls %>% 
+  skim(all_of(names_xx))
+```
+
+## Attaching series data
+
+Left join series data to announcement data and then review.
+
+```{r}
+prep_xx <- 
+  prep_building_missing_nulls %>% 
+  left_join(prep_series, by = "usajobs_control_number", suffix = c("_building", "_join")) %>% 
+  select(usajobs_control_number,starts_with("series_")) 
+prep_xx %>% 
+  select(order(colnames(prep_xx))) %>% 
+  skim()
+```
+
+Collect names.
+
+```{r}
+names_xx <- prep_series %>% names()
+```
+
+Counting differences.
+
+```{r}
+ names_xx[-1] %>% 
+  map(
+    ~counting_differences(in_data = prep_xx, in_variable_prefix = .)
+  )
+```
+
+We want to take the values from the attached dataframe, unless they are null.
+
+Exact matches.
+
+```{r}
+ prep_xx_01 <-
+  prep_building_missing_nulls %>% 
+  select(all_of(names_xx)) %>% 
+  inner_join(prep_series)
+```
+
+`r params$unique_identifier_1` not in `prep_work_schedule_appointment`.
+
+```{r}
+ prep_xx_02 <-
+  prep_building_missing_nulls %>% 
+  select(usajobs_control_number) %>% 
+  anti_join(prep_series) %>% 
+  inner_join(prep_building_missing_nulls) %>% 
+  select(all_of(names_xx)) 
+```
+
+In `prep_work_schedule_appointment`, but not above two.
+
+```{r}
+prep_xx_03 <- 
+  prep_series %>% 
+  anti_join(
+    prep_xx_01 %>% 
+      bind_rows(prep_xx_02) %>% 
+      select(usajobs_control_number) %>% 
       distinct()
 
-working_01 %>% 
-  glimpse()
-
-working_01 %>% 
+  )
+```
+
+Bind the above.
+
+```{r}
+prep_xx_04 <- 
+  prep_xx_01 %>% 
+  bind_rows(prep_xx_02) %>% 
+  bind_rows(prep_xx_03) %>% 
+  distinct()
+```
+
+Join to the unique `r params$unique_identifier_1`.
+
+```{r}
+prep_xx <- 
+  prep_uniq %>% 
+  left_join(prep_xx_04)
+
+prep_xx %>% 
   skim()
@@
 
-Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.
-
-```{r}
-working_02 <- 
-  working_01 %>% 
-  anti_join(dedupe %>% select(params$unique_identifier_1))
-
-working_02 %>% 
-  glimpse()
-
-working_02 %>% 
+Join onto existing data, while dropping the original colums.
+
+```{r}
+prep_building_missing_nulls <-
+  prep_building_missing_nulls  %>% 
+  select(-all_of(names_xx[-1])) %>% 
+  left_join(prep_xx)
+
+prep_building_missing_nulls %>% 
+  skim(all_of(names_xx))
+```
+
+## Attaching locations data
+
+Left join locations data to announcement data and then review.
+
+```{r}
+prep_xx <-
+  prep_building_missing_nulls %>% 
+  left_join(prep_location, by = "usajobs_control_number", suffix = c("_building", "_join")) %>% 
+  select(usajobs_control_number,ends_with( c("_building", "_join")),position_location_city, 
+         position_location_country, position_location_geo_location_code,
+         position_location_state,position_location_zip)
+prep_xx %>% 
+  select(order(colnames(prep_xx))) %>% 
   skim()
@@
 
-Last bind this dataframe to the deduplicated set above.
+Collect names.
+
+```{r}
+names_xx <- prep_location %>% names()
+
+names_base <- prep_building_missing_nulls %>% names()
+
+names_overlap <- intersect(names_xx,names_base)
+```
+
+Counting differences.
+
+```{r}
+names_xx[-1] %>% 
+  map(
+    ~counting_differences(in_data = prep_xx, in_variable_prefix = .)
+  )
+```
+
+We want to take the values from the attached dataframe, unless they are null.
+
+Exact matches.
+
+```{r}
+ prep_xx_01 <-
+  prep_building_missing_nulls %>% 
+  select(all_of(names_overlap)) %>% 
+  inner_join(prep_location)
+```
+
+`r params$unique_identifier_1` not in `prep_location`.
+
+```{r}
+ prep_xx_02 <-
+  prep_building_missing_nulls %>% 
+  select(usajobs_control_number) %>% 
+  anti_join(prep_location) %>% 
+  inner_join(prep_building_missing_nulls) %>% 
+  select(all_of(names_overlap)) 
+```
+
+In `prep_building_missing_nulls`, but not above two.
+
+```{r}
+prep_xx_03 <- 
+  prep_building_missing_nulls %>% 
+  anti_join(
+    prep_xx_01 %>% 
+      bind_rows(prep_xx_02) %>% 
+      select(usajobs_control_number) %>% 
+      distinct()
+
+  ) %>% 
+  select(all_of(names_overlap))  %>% 
+      distinct()
+
+```
+
+Bind the above.
+
+```{r}
+prep_xx_04 <- 
+  prep_xx_01 %>% 
+  bind_rows(prep_xx_02) %>% 
+  bind_rows(prep_xx_03) %>% 
+  distinct()
+```
+
+Join to the unique `r params$unique_identifier_1`.
 
@@
 prep_xx <- 
-  working_02 %>% 
-  bind_rows(dedupe)
-
-prep_xx %>% 
-  glimpse()
+  prep_uniq %>% 
+  left_join(prep_xx_04)
 
@@
 
-Count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-Rename dataframe
-
-```{r}
-prep_02 <- prep_xx
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_02 <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-
-dupe_02
-```
-
-Duplication appear to be because `r duplicating_group %>% pull(variable)` is empty in one row. Transform the empties into 'N'.
-
-We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
-
-```{r}
-prep_xx <- 
-  prep_base %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
+# CONTINUE FROM HERE
+
+Is this covering the whole year?
+
+```{r}
+prep_building_missing_nulls %>% 
+  count(position_open_date) %>% 
+  ggplot(aes(x = position_open_date, y = n)) + 
+  geom_line()
+```
+
+```{r}
+prep_building_missing_nulls %>% 
+  count(position_open_date,maximum_grade) %>% 
+  ggplot(aes(x = position_open_date, y = n, color = maximum_grade)) + 
+  geom_line() 
++
+  facet_wrap('maximum_grade', scales = "free")
+```
+
+```{r}
+prep_building_missing_nulls %>% 
+  count(position_open_date,minimum_grade) %>% 
+  ggplot(aes(x = position_open_date, y = n, color = minimum_grade)) + 
+  geom_line() 
+```
+
+```{r}
+prep_building_missing_nulls %>% 
+  count(position_close_date) %>% 
+  ggplot(aes(x = position_close_date, y = n)) + 
+  geom_line()
+```
+
+`telework_eligible_building` has no variable and `telework_eligible_telework` has lots of NULLs.
+
+We will attach the data and drop `telework_eligible_building` from the `prep_building_missing_nulls` dataframe.
+We will transform this into indicators for a position being telework eligible and for the value being null.
+
+```{r}
+prep_building_missing_nulls <- 
+  prep_building_missing_nulls %>% 
+  select(-telework_eligible) %>% 
+  left_join(prep_telework, by = "usajobs_control_number") %>% 
   mutate(
-    is_remote_work_eligible = case_when(is_remote_work_eligible == "" ~ "N",
-                                        TRUE ~ is_remote_work_eligible)
-  ) %>% 
-  distinct() %>% 
-  character_to_indicator(in_unique_identifier = params$unique_identifier_1,
-                         in_variable = is_remote_work_eligible,
-                         in_prefix = "is_remote_work_eligible") %>% 
-  # Drop the "n" indicatoris_remote_work_eligible
-  select(-is_remote_work_eligible_n)
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-Rename dataframe
-
-```{r}
-prep_03 <- prep_xx
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_02 <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-
-dupe_02
-```
-
-Check to see if the type codes are consistent to the description.
-
-```{r}
-prep_base %>% 
-  count(announcement_closing_type,announcement_closing_type_description)
-```
-
-Codes are consistent to description, but the code adds no new information. We will drop the code and transform the description into columns of indicators.
-
-We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
-
-```{r}
-prep_xx <- 
-  prep_base %>% 
-  character_to_indicator(params$unique_identifier_1,announcement_closing_type_description,"closing_type")
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Rename dataframe and count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-Rename dataframe
-
-```{r}
-prep_04 <- prep_xx
-
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_02 <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-
-dupe_02
-```
-
-Announcements have multiple open statuses.
-
-First count the statuses across the original data.
-
-```{r}
-prep_base %>% count(position_opening_status)
-```
-
-Not too many of them. Like above, we will transform these into indicator columns.
-
-We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
-
-```{r}
-prep_xx <- 
-  prep_base %>% 
-  character_to_indicator(params$unique_identifier_1,position_opening_status,"position_opening_status")
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-Rename dataframe
-
-```{r}
-prep_05 <- prep_xx
-
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_02 <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-
-dupe_02
-```
-
-Not too many. It appears that `application_limit_set` is "N" when `application_limit` is "Applicant Cut-Off".
-
-First count the statuses across the original data.
-
-```{r}
-prep_base %>% count(application_limit,application_limit_set)
-```
-
-All NA `application_limit` are "N" `application_limit_set`.
-
-We will consider "Y" the correct response for all and we will change this into an indicator.
-
-We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
-
-```{r}
-prep_xx <- 
-  prep_base %>% 
-  character_to_indicator(params$unique_identifier_1,application_limit_set,"application_limit_set") %>% 
-  # Drop the "N" column
-  select(-application_limit_set_n)
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-Rename dataframe
-
-```{r}
-prep_06 <- prep_xx
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_02 <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-
-dupe_02
-```
-
-Not too many. It appears that `work_schedule` might have different.
-
-First count the statuses across the original data.
-
-```{r}
-prep_base %>% count(work_schedule)
-```
-
-There are just a few, but we'll want to transform these into indicators.
-
-We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
-
-```{r}
-prep_xx <- 
-  prep_base %>% 
-  character_to_indicator(params$unique_identifier_1,work_schedule,"work_schedule")
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-Rename dataframe
-
-```{r}
-prep_07 <- prep_xx
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_02 <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-
-dupe_02
-```
-
-Not too many. It appears that `disable_apply_online` might have different.
-
-First count the statuses across the original data.
-
-```{r}
-prep_base %>% count(disable_apply_online)
-```
-
-There are just a few, but we'll want to transform these into indicators.
-
-We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
-
-Since there is only one instance of this type of duplication, we will still drop the no column.
-
-```{r}
-prep_xx <- 
-  prep_base %>% 
-  character_to_indicator(params$unique_identifier_1,disable_apply_online,"disable_apply_online") %>% 
-  # Drop the "N" column
-  select(-disable_apply_online_n)
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-Rename dataframe
-
-```{r}
-prep_08 <- prep_xx
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_02 <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-
-dupe_02
-```
-
-Not too many.
-
-First count the statuses across the original data.
-
-```{r}
-prep_base %>% count(appointment_type)
-```
-
-There are just a few, but we'll want to transform these into indicators.
-
-We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
-
-Since there is only one instance of this type of duplication, we will still drop the no column.
-
-```{r}
-prep_xx <- 
-  prep_base %>% 
-  character_to_indicator(params$unique_identifier_1,appointment_type,"appointment_type")
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-Rename dataframe
-
-```{r}
-prep_09 <- prep_xx
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_02 <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-
-dupe_02
-```
-
-A few things going on here:
-
-1.    Department of Defense agencies are duplicated because sometimes sub-departments (e.i. Department of Navy) are considered the *Department*
-2.    Many duplicates are caused by blank values in hiring agency code
-
-First let's remove duplicates because of department. To do this, we'll use the maximum agency level to limit to just the entries with the most levels.
-
-```{r}
-dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  group_by(usajobs_control_number) %>% 
-  filter(agency_level == max(agency_level)) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-We can still see the duplications from blank hiring agency codes. We'll drop those.
-
-```{r}
-dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  group_by(usajobs_control_number) %>% 
-  filter(agency_level == max(agency_level)) %>% 
-  filter(!is.na(hiring_department_code)) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-We still have one duplicate remaining. For this we'll, select the entry with the later position closing date.
-
-```{r}
-dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>% 
-  group_by(usajobs_control_number) %>% 
-  filter(agency_level == max(agency_level)) %>% 
-  filter(!is.na(hiring_department_code)) %>% 
-  filter(position_close_date == max(position_close_date)) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-Now we will apply all of these to the duplicated rows.
-
-```{r}
-dedupe <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>% 
-  group_by(usajobs_control_number) %>% 
-  filter(agency_level == max(agency_level)) %>% 
-  filter(!is.na(hiring_department_code)) %>% 
-  filter(position_close_date == max(position_close_date)) %>% 
-  distinct() %>% 
-  ungroup() %>% 
-  select(-position_close_date)
-
-dedupe %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.
-
-First create a dataframe of distinct rows of the variables from the original data.
-
-```{r}
-working_01 <- 
-  prep_base %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct()
-
-working_01 %>% 
-  glimpse()
-
-working_01 %>% 
-  skim()
-```
-
-Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.
-
-```{r}
-working_02 <- 
-  working_01 %>% 
-  anti_join(dedupe %>% select(params$unique_identifier_1))
-
-working_02 %>% 
-  glimpse()
-
-working_02 %>% 
-  skim()
-```
-
-Last bind this dataframe to the deduplicated set above.
-
-```{r}
-prep_xx <- 
-  working_02 %>% 
-  bind_rows(dedupe)
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-Rename dataframe
-
-```{r}
-prep_10 <- prep_xx
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_02 <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-
-dupe_02
-```
-
-Count types.
-
-```{r}
-prep_base %>% 
-  count(hiring_subelement_name)
-```
-
-Many blank entries and a level of detail we don't need. We will drop this column.
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_02 <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-
-dupe_02
-```
-
-Appears like this comes from posting the job again with revised salary information.
-
-Like above we decide to retain the later dates as determined by the close date.
-
-```{r}
-dedupe <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
-  arrange(params$unique_identifier_1, position_close_date) %>% 
-  group_by(usajobs_control_number) %>% 
-  summarise(
-    across(
-      .cols = all_of(duplicating_group %>% pull(variable)),
-      .fns = last
-    )
-  )
-
-dedupe %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.
-
-First create a dataframe of distinct rows of the variables from the original data.
-
-```{r}
-working_01 <- 
-  prep_base %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct()
-
-working_01 %>% 
-  glimpse()
-
-working_01 %>% 
-  skim()
-```
-
-Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.
-
-```{r}
-working_02 <- 
-  working_01 %>% 
-  anti_join(dedupe %>% select(params$unique_identifier_1))
-
-working_02 %>% 
-  glimpse()
-
-working_02 %>% 
-  skim()
-```
-
-Last bind this dataframe to the deduplicated set above.
-
-```{r}
-prep_xx <- 
-  working_02 %>% 
-  bind_rows(dedupe)
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-Rename dataframe
-
-```{r}
-prep_11 <- prep_xx
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_02 <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-
-dupe_02
-```
-Count types.
-
-```{r}
-prep_base %>% 
-  count(series, series_title)
-```
-
-Many different titles and series.
-
-Check if the series numbers are duplicated.
-
-```{r}
-prep_base %>% 
-  count(series, series_title) %>% 
-  ungroup() %>% 
-  get_dupes(series)
-```
-
-None.
-
-Now the titles.
-
-```{r}
-prep_base %>% 
-  count(series, series_title) %>% 
-  ungroup() %>% 
-  get_dupes(series_title)
-```
-
-None.
-
-Since the `series` adds no information and is uniquely matched to the titles, we will drop `series`.
-
-There are too many series to want indicators, we'll use the last closing date to select the appropriate series.
-
-Like above we decide to retain the later dates as determined by the close date.
-
-```{r}
-dedupe <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
-  arrange(params$unique_identifier_1, position_close_date) %>% 
-  group_by(usajobs_control_number) %>% 
-  summarise(
-    across(
-      .cols = all_of(duplicating_group %>% pull(variable)),
-      .fns = last
-    )
-  )
-
-dedupe %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.
-
-First create a dataframe of distinct rows of the variables from the original data.
-
-```{r}
-working_01 <- 
-  prep_base %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct()
-
-working_01 %>% 
-  glimpse()
-
-working_01 %>% 
-  skim()
-```
-
-Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.
-
-```{r}
-working_02 <- 
-  working_01 %>% 
-  anti_join(dedupe %>% select(params$unique_identifier_1))
-
-working_02 %>% 
-  glimpse()
-
-working_02 %>% 
-  skim()
-```
-
-Last bind this dataframe to the deduplicated set above.
-
-```{r}
-prep_xx <- 
-  working_02 %>% 
-  bind_rows(dedupe) %>% 
-  select(-series)
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-Rename dataframe
-
-```{r}
-prep_12 <- prep_xx
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_02 <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-
-dupe_02
-```
-
-Not too many duplicates. We'll follow the same procedure, taking the number from the row wiht the later closing date.
-
-Like above we decide to retain the later dates as determined by the close date.
-
-```{r}
-dedupe <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
-  arrange(params$unique_identifier_1, position_close_date) %>% 
-  group_by(usajobs_control_number) %>% 
-  summarise(
-    across(
-      .cols = all_of(duplicating_group %>% pull(variable)),
-      .fns = last
-    )
-  )
-
-dedupe %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.
-
-First create a dataframe of distinct rows of the variables from the original data.
-
-```{r}
-working_01 <- 
-  prep_base %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct()
-
-working_01 %>% 
-  glimpse()
-
-working_01 %>% 
-  skim()
-```
-
-Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.
-
-```{r}
-working_02 <- 
-  working_01 %>% 
-  anti_join(dedupe %>% select(params$unique_identifier_1))
-
-working_02 %>% 
-  glimpse()
-
-working_02 %>% 
-  skim()
-```
-
-Last bind this dataframe to the deduplicated set above.
-
-```{r}
-prep_xx <- 
-  working_02 %>% 
-  bind_rows(dedupe)
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-Rename dataframe
-
-```{r}
-prep_13 <- prep_xx
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_02 <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-
-dupe_02
-```
-
-Not too many duplicates.
-
-Like above we decide to retain the later dates as determined by the close date.
-
-```{r}
-dedupe <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable)),position_close_date) %>%
-  arrange(params$unique_identifier_1, position_close_date) %>% 
-  group_by(usajobs_control_number) %>% 
-  summarise(
-    across(
-      .cols = all_of(duplicating_group %>% pull(variable)),
-      .fns = last
-    )
-  )
-
-dedupe %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.
-
-First create a dataframe of distinct rows of the variables from the original data.
-
-```{r}
-working_01 <- 
-  prep_base %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct()
-
-working_01 %>% 
-  glimpse()
-
-working_01 %>% 
-  skim()
-```
-
-Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.
-
-```{r}
-working_02 <- 
-  working_01 %>% 
-  anti_join(dedupe %>% select(params$unique_identifier_1))
-
-working_02 %>% 
-  glimpse()
-
-working_02 %>% 
-  skim()
-```
-
-Last bind this dataframe to the deduplicated set above.
-
-```{r}
-prep_xx <- 
-  working_02 %>% 
-  bind_rows(dedupe)
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-Rename dataframe
-
-```{r}
-prep_14 <- prep_xx
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-No more deplicated columns!!
-
-### Combinding deduplicated data
-
-#### Created dataframe on non-duplicating columns
-
-Collect column names of variables not creating duplicates.
-
-```{r}
-non_duplicating_variables <- 
-  column_meta_data %>% 
-  filter(!duplicates_by_variable) %>% 
-  pull(variable)
-
-non_duplicating_variables
-```
-
-Create dataframe of only these variables.
-
-```{r}
-prep_xx <- 
-  prep_base %>% 
-  select(any_of(non_duplicating_variables)) %>% 
-  distinct()
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-Rename dataframe.
-
-```{r}
-prep_11 <- prep_xx
-```
+    telework_eligible = case_when(telework_eligible == 1 ~ "y",
+                                  telework_eligible == 0 ~ "n")
+  ) %>% 
+  character_to_indicator(in_unique_identifier = params$unique_identifier_1, in_variable = telework_eligible, in_prefix = "telework_eligible") %>% 
+  select(-telework_eligible_n)
+
+prep_building_missing_nulls %>% 
+  skim(starts_with("telework_eligible"))
+```
+
+join series, workschedule and appointment, locations
 

### 2023-03-15 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd
Added headers, include section comparing combined dataframe to originals, began to address nulls and blanks.

@@
 library(readxl)
+library(flextable)
+library(ggthemes)
 ```
@@
 
-### Join data
+## Joining data
+
+### Join 1
 
@@
 ```
+
+### Join 2
 
@@
 ```
+
+## Compare to original dataframes
+
+```{r}
+prep_base_1_summary <- 
+  prep_base_1 %>% 
+  unite(employee_name_date,employee_name,date,remove = FALSE) %>% 
+  summarise(
+    rows = n(),
+    employee_name = n_distinct(employee_name),
+    employee_name_date = n_distinct(employee_name_date),
+  ) %>% 
+  mutate(dataframe = "prep_base_1")
+```
+
+```{r}
+prep_base_2_summary <- 
+  prep_base_2 %>% 
+  # unite(employee_name_date,employee_name,date,remove = FALSE) %>% 
+  summarise(
+    rows = n(),
+    employee_name = n_distinct(full_name),
+    employee_e_mail_address = n_distinct(employee_e_mail_address)
+  ) %>% 
+  mutate(dataframe = "prep_base_2")
+```
+
+```{r}
+prep_building_summary <- 
+  prep_building %>% 
+  unite(employee_name_date,employee_name,date,remove = FALSE) %>%
+  summarise(
+    rows = n(),
+    person_id = n_distinct(person_id),
+    employee_name = n_distinct(employee_name),
+    employee_e_mail_address = n_distinct(employee_e_mail_address),
+    employee_name_date = n_distinct(employee_name_date),
+  ) %>% 
+  mutate(dataframe = "prep_building")
+```
+
+```{r}
+prep_summary <- 
+  prep_base_1_summary %>% 
+  bind_rows(prep_base_2_summary) %>% 
+  bind_rows(prep_building_summary) %>% 
+  pivot_longer(-dataframe) %>% 
+  pivot_wider(names_from = dataframe,values_from = value)
+```
+
+```{r}
+prep_summary %>% 
+  flextable() %>% 
+  theme_zebra() %>% 
+  autofit()
+```
+
+```{r}
+prep_base_1_rows <- prep_summary %>% filter(name == 'rows') %>% pull(prep_base_1)
+
+prep_base_1_employee_name <- prep_summary %>% filter(name == 'employee_name') %>% pull(prep_base_1)
+
+diff_rows_count <- 
+  (prep_base_1_rows) -
+  (prep_summary %>% filter(name == 'rows') %>% pull(prep_building))
+
+diff_rows_prop <- 
+  diff_rows_count/prep_base_1_rows
+
+diff_employee_name_count <- 
+  (prep_base_1_employee_name) -
+  (prep_summary %>% filter(name == 'employee_name') %>% pull(prep_building))
+
+diff_employee_name_prop <- 
+  diff_employee_name_count/prep_base_1_employee_name
+```
+
+From this table, we find:
+
+1.    A loss of `r scales::comma(diff_rows_count)` rows between `prep_1_base` and `prep_building`, about `r scales::percent(diff_rows_prop)`
+2.    A loss of `r scales::comma(diff_employee_name_count)` rows between `prep_1_base` and `prep_building`, about `r scales::percent(diff_employee_name_prop)`
+
+These losses of data are reasonable.
+
+Create a unique dataframe of just `date` and `person_id`.
+
+```{r}
+prep_uniq <- 
+  prep_building %>% 
+  select(date,person_id)
+```
+
+## Addressing blanks, nulls, and other values
+
+Created a dataframe of variable metadata.
+
+```{r}
+column_meta_data <- 
+  prep_building %>% 
+  contents()
+
+column_meta_data <- 
+  column_meta_data$contents %>% 
+  as.data.frame()
+
+column_meta_data <-
+  column_meta_data %>% 
+  rownames_to_column(var = "variable")
+
+column_meta_data <- 
+  column_meta_data %>% 
+  mutate(
+    nulls_by_variable = case_when(NAs > 0 ~ TRUE,
+                                  NAs == 0 ~ FALSE)
+  )
+
+column_meta_data
+```
+
+Counting top 10 values for all character or factor columns to identify other common values.
+
+```{r}
+values_count <- 
+  prep_building %>% 
+  select(where(is.character) | where(is.factor)) %>% 
+  names()
+
+values_count %>% 
+  map(~count(prep_building,!!sym(.)) %>% 
+  arrange(desc(n)) %>%
+  slice_head(n = 10))
+
+```
+
+No obvious values.
+
+Function that checks whether there are blanks for different variables
+
+```{r}
+blank_check <- function(in_data,in_variable_name)
+{
+  check_01 <- 
+  in_data %>% 
+    filter(!!sym(in_variable_name) == "") %>% 
+  distinct()
+
+out <- nrow(check_01) > 0
+
+return(out)
+}
+```
+
+Checking blanks for each variable in the dataframe.
+
+```{r}
+blanks_by_variable <- 
+  column_meta_data %>% 
+  pull(variable) %>% 
+  map_lgl(~blank_check(in_data = prep_building,.))
+
+blanks_by_variable
+```
+
+Add this to the `column_meta_data` dataframe.
+
+```{r}
+column_meta_data <- 
+  column_meta_data %>% 
+  add_column(
+    blanks_by_variable = blanks_by_variable
+  )
+
+column_meta_data
+```
+
+Create dataframe of only variables that have blanks.
+
+```{r}
+problem_variables <- 
+  column_meta_data %>% 
+  filter(blanks_by_variable | nulls_by_variable)
+
+problem_variables
+```
+
+Grouping variables.
+
+```{r}
+problem_variables <- 
+  problem_variables %>% 
+  mutate(group = 
+           case_when(variable == "position_category_code" ~ "position_category_code",
+                     variable == "position_category_description" ~ "position_category_code",
+                     TRUE ~ variable
+                     ))
+
+problem_variables
+```
+
+Create list of groups.
+
+```{r}
+problem_groups <- 
+  problem_variables %>% 
+  select(group) %>% 
+  distinct() %>% 
+  arrange(group) %>% 
+  pull()
+
+problem_groups
+```
+Also create a building dataframe to add other dataframes where missing have been removed.
+
+```{r}
+prep_problem <- prep_uniq
+```
+
+### Problems removal
+
+```{r}
+step_n <- 0
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `business_line_2_letter_department_id`
+
+Removing blanks produced by
+
+```{r}
+problem_variable <- 
+  problem_variables %>% 
+  filter(group == problem_groups[step_n])
+
+problem_variable
+```
+
+Reviewing blanks.
+
+```{r}
+nulls_01 <- 
+  prep_building %>% 
+  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(problem_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+problem_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~nulls_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(is.na(!!sym(.x)))
+  )
+```
+
+Let's count the entries here.
+
+```{r}
+prep_building %>% 
+  group_by(across(all_of(problem_variable %>% pull(variable)))) %>% 
+  count() %>% 
+  arrange(desc(n))
+```
+
+Lot's of entries.
+
+Check relationship with time.
+
+```{r}
+prep_building %>% 
+  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  group_by(across(all_of(problem_variable %>% pull(variable))),date) %>% 
+  count() %>% 
+  ggplot(aes(x = date, y = n)) +
+  geom_point() +
+  geom_smooth()
+```
+
+Increase in July.
+
+Is this an important variable?
+
+No. We'll replace nulls with "(Missing)".
+
+```{r}
+prep_xx <- 
+  prep_building %>% 
+  select(date, person_id,all_of(problem_variable %>% pull(variable))) %>% 
+  distinct() %>% 
+  mutate(
+    across(
+      .cols = all_of(problem_variable %>% pull(variable)),
+      .fns = ~case_when(is.na(.) ~ "(Missing)",
+                        TRUE ~ .)
+    )
+  )
+
+prep_xx %>% skim()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_problem <- prep_problem %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `employee_e_mail_address`
+
+Removing problems produced by
+
+```{r}
+problem_variable <- 
+  problem_variables %>% 
+  filter(group == problem_groups[step_n])
+
+problem_variable
+```
+
+Reviewing blanks.
+
+```{r}
+nulls_01 <- 
+  prep_building %>% 
+  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(problem_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+problem_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~nulls_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(is.na(!!sym(.x)))
+  )
+```
+
+Let's count the entries here.
+
+```{r}
+prep_building %>% 
+  group_by(across(all_of(problem_variable %>% pull(variable)))) %>% 
+  count() %>% 
+  arrange(desc(n))
+```
+
+Lot's of entries.
+
+Check relationship with time.
+
+```{r}
+prep_building %>% 
+  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  group_by(across(all_of(problem_variable %>% pull(variable))),date) %>% 
+  count() %>% 
+  ggplot(aes(x = date, y = n)) +
+  geom_jitter() +
+  geom_smooth() +
+  theme_fivethirtyeight()
+```
+
+Looks pretty random.
+
+Is this an important variable?
+
+Yes, but we won't be using it directly in the analysis. We'll replace nulls with "(Missing)".
+
+```{r}
+prep_xx <- 
+  prep_building %>% 
+  select(date, person_id,all_of(problem_variable %>% pull(variable))) %>% 
+  distinct() %>% 
+  mutate(
+    across(
+      .cols = all_of(problem_variable %>% pull(variable)),
+      .fns = ~case_when(is.na(.) ~ "(Missing)",
+                        TRUE ~ .)
+    )
+  )
+
+prep_xx %>% skim()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_problem <- prep_problem %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `location_city`
+
+Removing problems produced by
+
+```{r}
+problem_variable <- 
+  problem_variables %>% 
+  filter(group == problem_groups[step_n])
+
+problem_variable
+```
+
+Reviewing blanks.
+
+```{r}
+nulls_01 <- 
+  prep_building %>% 
+  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(problem_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+problem_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~nulls_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(is.na(!!sym(.x)))
+  )
+```
+
+Let's count the entries here.
+
+```{r}
+prep_building %>% 
+  group_by(across(all_of(problem_variable %>% pull(variable)))) %>% 
+  count() %>% 
+  arrange(desc(n))
+```
+
+Lot's of entries.
+
+Check relationship with time.
+
+```{r}
+prep_building %>% 
+  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  group_by(across(all_of(problem_variable %>% pull(variable))),date) %>% 
+  count() %>% 
+  ggplot(aes(x = date, y = n)) +
+  geom_jitter() +
+  geom_smooth() +
+  theme_fivethirtyeight()
+```
+
+Weird that early in the year is low, then gets steady later.
+
+Is this an important variable?
+
+Yes, but we have other location variables to rely on. We'll replace nulls with "(Missing)".
+
+```{r}
+prep_xx <- 
+  prep_building %>% 
+  select(date, person_id,all_of(problem_variable %>% pull(variable))) %>% 
+  distinct() %>% 
+  mutate(
+    across(
+      .cols = all_of(problem_variable %>% pull(variable)),
+      .fns = ~case_when(is.na(.) ~ "(Missing)",
+                        TRUE ~ .)
+    )
+  )
+
+prep_xx %>% skim()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_problem <- prep_problem %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `location_state`
+
+Removing problems produced by
+
+```{r}
+problem_variable <- 
+  problem_variables %>% 
+  filter(group == problem_groups[step_n])
+
+problem_variable
+```
+
+Reviewing blanks.
+
+```{r}
+nulls_01 <- 
+  prep_building %>% 
+  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(problem_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+problem_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~nulls_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(is.na(!!sym(.x)))
+  )
+```
+
+Let's count the entries here.
+
+```{r}
+prep_building %>% 
+  group_by(across(all_of(problem_variable %>% pull(variable)))) %>% 
+  count() %>% 
+  arrange(desc(n))
+```
+
+Lot's of entries.
+
+Check relationship with time.
+
+```{r}
+prep_building %>% 
+  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  group_by(across(all_of(problem_variable %>% pull(variable))),date) %>% 
+  count() %>% 
+  ggplot(aes(x = date, y = n)) +
+  geom_jitter() +
+  geom_smooth() +
+  theme_fivethirtyeight()
+```
+
+Looks pretty random, and low numbers.
+
+Is this an important variable?
+
+Yes, but we have other location variables to rely on. It appears from above that these are international locations. We'll replace nulls with "(International)".
+
+```{r}
+prep_xx <- 
+  prep_building %>% 
+  select(date, person_id,all_of(problem_variable %>% pull(variable))) %>% 
+  distinct() %>% 
+  mutate(
+    across(
+      .cols = all_of(problem_variable %>% pull(variable)),
+      .fns = ~case_when(is.na(.) ~ "(International)",
+                        TRUE ~ .)
+    )
+  )
+
+prep_xx %>% skim()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_problem <- prep_problem %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+# CONTINUE FROM HERE.
 

### 2023-03-16 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Added some details on how to assign employees to teams, and how to define a team

@@
 The analysis will be done for staff and teams separately and aggregated
-independently. The table below defines how we plan to aggregate for
+independently.
+Employees will be categorized.
+Also, employees with be grouped into teams based on supervisor.
+These teams will also be categorized.
+The table below defines how we plan to aggregate for
 staff and teams.
@@
 
-<!-- How are you doing team classification? Are you going to generate a team -->
-<!-- ID based on some rule? If so what is it, and to the prior point, how do -->
-<!-- you handle changing team composition over time? -->
+<!-- Done -->
 
@@
 
--   Indicator for a switch in supervisor
+-   Number of supervisors
 
 -   Size of team over observation window
+
+<!-- How are you doing team classification? Are you going to generate a team -->
+<!-- ID based on some rule? If so what is it, and to the prior point, how do -->
+<!-- you handle changing team composition over time? -->
+
+Teams will be defined based on the supervisors in March 2022.
+The unique identifier for teams will be the `supervisor_e_mail_address`.
+All employees under those supervisors will be defined as part of the team.
+Employees may join and leave a team over the observation window.
 
@@
 
--   Size of team over observation window
+-   Average size of team over observation window
+
+-   Total employees in team over observation window
 

### 2023-03-16 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd
Addressing nulls in position_category_code

@@
 
+#### Step `r step_n`: `position_category_code`
+
+Removing problems produced by
+
+```{r}
+problem_variable <- 
+  problem_variables %>% 
+  filter(group == problem_groups[step_n])
+
+problem_variable
+```
+
+Reviewing blanks.
+
+```{r}
+nulls_01 <- 
+  prep_building %>% 
+  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(problem_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+problem_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~nulls_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(is.na(!!sym(.x)))
+  )
+```
+
+Let's count the entries here.
+
+```{r}
+prep_building %>% 
+  group_by(across(all_of(problem_variable %>% pull(variable)))) %>% 
+  count() %>% 
+  arrange(desc(n))
+```
+
+Lot's of entries.
+
+Check relationship with time.
+
+```{r}
+prep_building %>% 
+  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  group_by(across(all_of(problem_variable %>% pull(variable))),date) %>% 
+  count() %>% 
+  ggplot(aes(x = date, y = n)) +
+  geom_jitter() +
+  geom_smooth() +
+  theme_fivethirtyeight()
+```
+
+Looks pretty random, and low numbers.
+
+```{r}
+prep_01 <-
+  prep_building %>% 
+  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(person_id) %>% 
+  distinct() %>% 
+  inner_join(prep_building) %>% 
+  arrange(person_id,date) %>% 
+  select(person_id,date,all_of(problem_variable %>% pull(variable)))
+
+prep_01
+```
+
+```{r}
+prep_02 <- 
+  prep_01 %>% 
+  group_by(across(all_of(problem_variable %>% pull(variable))),person_id) %>% 
+  summarise(
+    n = n(),
+    date_first = first(date),
+    date_last = last(date)
+  ) %>% 
+  arrange(person_id,n)
+
+prep_02
+```
+
+Is this an important variable?
+
+Yes, but we have other location variables to rely on. It appears from above that these are international locations. We'll replace nulls with "(International)".
+
+```{r}
+prep_xx <- 
+  prep_building %>% 
+  select(date, person_id,all_of(problem_variable %>% pull(variable))) %>% 
+  distinct() %>% 
+  mutate(
+    across(
+      .cols = all_of(problem_variable %>% pull(variable)),
+      .fns = ~case_when(is.na(.) ~ "(International)",
+                        TRUE ~ .)
+    )
+  )
+
+prep_xx %>% skim()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_problem <- prep_problem %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
 # CONTINUE FROM HERE.

### 2023-03-16 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd
Addressed nulls in position categories, supervisor corrections, and supervisor email addresses, added a check that they are addressed.

@@
 
+Let's investigate whether these employees ever have other values for `r problem_variable %>% pull(variable)`.
+
 ```{r}
@@
 
-prep_01
-```
+prep_01 %>% 
+  DT::datatable(class = 'cell-border stripe')
+```
+
+They do have some.
+
+Now let's look at how they change.
 
@@
 
-prep_02
+prep_02 %>% 
+  DT::datatable(class = 'cell-border stripe')
+```
+
+It apprears that most start with nulls then became a category.
+
+Let's check their position category at the earliest date and count.
+
+```{r}
+prep_02 %>% 
+  group_by(person_id) %>% 
+  filter(date_first == min(date_first)) %>% 
+  ungroup() %>% 
+  count(position_category_code,position_category_description)
+```
+
+Most of this group are null at the beginning. Some not.
+
+Let's check the position category at the latest date and count.
+
+```{r}
+prep_02 %>% 
+  group_by(person_id) %>% 
+  filter(date_first == max(date_first)) %>% 
+  ungroup() %>% 
+  count(position_category_code,position_category_description)
 ```
@@
 
-Yes, but we have other location variables to rely on. It appears from above that these are international locations. We'll replace nulls with "(International)".
+Yes, but we want to use this in the analysis. We will fill the variable the most proximate value and create an indicator that these values were imputed.
 
@@
   mutate(
+    position_category_imputed = case_when(is.na(position_category_code) ~ 1,
+                                          is.na(position_category_description) ~ 1,
+                                          TRUE ~ 0) 
+  ) %>% 
+  arrange(person_id, date) %>% 
+  group_by(person_id) %>% 
+  fill(position_category_code, .direction = "downup") %>% 
+  fill(position_category_description, .direction = "downup") %>% 
+  ungroup() %>% 
+  mutate(
     across(
       .cols = all_of(problem_variable %>% pull(variable)),
-      .fns = ~case_when(is.na(.) ~ "(International)",
+      .fns = ~case_when(is.na(.) ~ "(Missing)",
                         TRUE ~ .)
@@
   )
-
-prep_xx %>% skim()
-```
+  )
+
+prep_xx %>%
+  skim()
+```
+
+Compare against the identified cases above.
+
+```{r}
+prep_xx %>% 
+  inner_join(prep_01,
+            by =  c("person_id", "date"),
+            suffix = c("_xx","_01")
+  ) %>% 
+  DT::datatable(class = 'cell-border stripe')
+```
+
+Looks good.
 
@@
 step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `supervisor_correction`
+
+Removing problems produced by
+
+```{r}
+problem_variable <- 
+  problem_variables %>% 
+  filter(group == problem_groups[step_n])
+
+problem_variable
+```
+
+Reviewing blanks.
+
+```{r}
+nulls_01 <- 
+  prep_building %>% 
+  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(problem_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+problem_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~nulls_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(is.na(!!sym(.x)))
+  )
+```
+
+Let's count the entries here.
+
+```{r}
+prep_building %>% 
+  group_by(across(all_of(problem_variable %>% pull(variable)))) %>% 
+  count() %>% 
+  arrange(desc(n)) %>% 
+   flextable() %>% 
+  theme_zebra() %>% 
+  autofit()
+```
+
+Lot's of entries.
+
+Check relationship with time.
+
+```{r}
+prep_building %>% 
+  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  group_by(across(all_of(problem_variable %>% pull(variable))),date) %>% 
+  count() %>% 
+  ggplot(aes(x = date, y = n)) +
+  geom_jitter() +
+  geom_smooth() +
+  theme_fivethirtyeight()
+```
+
+Some increase in the use of this over time.
+
+Let's count this along side `daily_status`.
+
+```{r}
+prep_building %>% 
+  group_by(across(all_of(problem_variable %>% pull(variable))),daily_status) %>% 
+  count() %>% 
+   flextable() %>% 
+  theme_zebra() %>% 
+  autofit()
+```
+
+Is this an important variable?
+
+Yes, but we want to use this in the analysis. We will use with `daily_status` to define status.
+
+```{r}
+prep_xx <- 
+  prep_building %>% 
+  select(date, person_id,all_of(problem_variable %>% pull(variable)),daily_status) %>% 
+  distinct() %>% 
+  mutate(
+    daily_status_imputed = case_when(is.na(supervisor_correction) &
+                                       daily_status == "Supervisor Corrected" ~ "(Missing)",
+                                     is.na(supervisor_correction) ~ daily_status,
+                                     daily_status == "Supervisor Corrected" ~ supervisor_correction
+                                     ) 
+  )
+
+prep_xx %>%
+  skim()
+```
+
+Let's count these variables to make sure they are coming out correctly.
+
+```{r}
+prep_xx %>% 
+  count(supervisor_correction,daily_status,daily_status_imputed) %>% 
+  flextable() %>% 
+  theme_zebra() %>% 
+  autofit()
+```
+
+Looks good.
+
+Join to building dataframe.
+
+```{r}
+prep_problem <- prep_problem %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: `supervisor_e_mail_address`
+
+Removing problems produced by
+
+```{r}
+problem_variable <- 
+  problem_variables %>% 
+  filter(group == problem_groups[step_n])
+
+problem_variable
+```
+
+Reviewing blanks.
+
+```{r}
+nulls_01 <- 
+  prep_building %>% 
+  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  select(all_of(problem_variable %>% pull(variable)),everything())
+
+nulls_01
+```
+
+Let's count the extent of the issues.
+
+```{r}
+problem_variable %>% 
+  pull(variable) %>% 
+  map(
+    ~nulls_01 %>% 
+  count(!!sym(.x)) %>% 
+  arrange(desc(n)) %>% 
+    filter(is.na(!!sym(.x)))
+  )
+```
+
+Not too many.
+
+Check relationship with time.
+
+```{r}
+prep_building %>% 
+  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
+  group_by(across(all_of(problem_variable %>% pull(variable))),date) %>% 
+  count() %>% 
+  ggplot(aes(x = date, y = n)) +
+  geom_jitter() +
+  geom_smooth() +
+  theme_fivethirtyeight()
+```
+
+Let's see if we can find these names in the roster data.
+
+```{r}
+nulls_01 %>% 
+  select(supervisor_display_name) %>% 
+  distinct() %>% 
+  separate(supervisor_display_name,c("supervisor_first_name","supervisor_last_name"), sep = " ") %>% 
+  mutate(
+    full_name = glue::glue("{supervisor_last_name},{supervisor_first_name}")
+  ) %>% 
+  inner_join(prep_base_2)
+```
+
+Let's see if anyone has the same last name.
+
+```{r}
+prep_01 <- 
+  nulls_01 %>% 
+  select(supervisor_display_name) %>% 
+  distinct() %>% 
+  separate(supervisor_display_name,c("supervisor_first_name","supervisor_last_name"), sep = " ",
+           remove = FALSE) %>% 
+  mutate(
+    full_name = glue::glue("{supervisor_last_name},{supervisor_first_name}")
+  ) %>% 
+  inner_join(prep_base_2 %>% 
+               separate(full_name,c("supervisor_last_name","supervisor_first_name"), sep = ","),
+             by = "supervisor_last_name") %>% 
+  select(starts_with("supervisor_"), employee_e_mail_address,everything())
+
+prep_01
+```
+
+This looks like the right person. Let's collect her information.
+
+```{r}
+prep_02 <- 
+  prep_01 %>% 
+  select(supervisor_display_name.x,employee_e_mail_address) %>% 
+  distinct() %>% 
+  filter(!is.na(employee_e_mail_address)) %>% 
+  rename(supervisor_display_name = supervisor_display_name.x,
+         supervisor_e_mail_address = employee_e_mail_address)
+
+prep_02
+```
+
+```{r}
+prep_xx <- 
+  prep_building %>% 
+  select(date, person_id,all_of(problem_variable %>% pull(variable)),supervisor_display_name) %>% 
+  distinct() %>% 
+  left_join(prep_02,by = "supervisor_display_name") %>% 
+  mutate(
+    supervisor_e_mail_address.z = 
+      case_when(is.na(supervisor_e_mail_address.x) ~ supervisor_e_mail_address.y,
+                TRUE ~supervisor_e_mail_address.x
+                                     )
+  )
+
+prep_xx %>%
+  skim()
+```
+
+Let's make sure it only effected this case.
+
+```{r}
+prep_xx %>% 
+  filter(supervisor_e_mail_address.y == supervisor_e_mail_address.z) %>% 
+  count(supervisor_display_name)
+  arrange(desc(supervisor_e_mail_address.z))
+```
+
+Looks good. Let's only use `person_id`, `date`, and rename `supervisor_e_mail_address.z`.
+
+```{r}
+prep_xx <- 
+  prep_xx %>% 
+  select(person_id,date,supervisor_e_mail_address.z) %>% 
+  rename(supervisor_e_mail_address = supervisor_e_mail_address.z)
+
+prep_xx %>%
+  skim()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_problem <- prep_problem %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+step_n <- step_n + 1
+```
+
+#### Step `r step_n`: Done!
+
+Removing problems produced by
+
+```{r}
+problem_variable <- 
+  problem_variables %>% 
+  filter(group == problem_groups[step_n])
+
+problem_variable
+```
+
+Done.
+
+### Combining  data
+
+#### Create dataframe off non-null columns
+
+Collect column names of variables not creating duplicates.
+
+```{r}
+non_problem_variables <- 
+  column_meta_data  %>% 
+  filter(!(blanks_by_variable | nulls_by_variable)) %>% 
+  pull(variable)
+
+non_problem_variables
+```
+
+Create dataframe of only these variables.
+
+```{r}
+prep_xx <- 
+  prep_building %>% 
+  select(any_of(non_problem_variables)) %>% 
+  distinct()
+
+prep_xx %>% 
+  glimpse()
+
+prep_xx %>% 
+  skim()
+```
+
+Join to building dataframe.
+
+```{r}
+prep_building <- prep_problem %>% 
+  left_join(prep_xx)
+```
+
+### Checking problems
+
+Created a dataframe of variable metadata.
+
+```{r}
+column_meta_data <- 
+  prep_building %>% 
+  contents()
+
+column_meta_data <- 
+  column_meta_data$contents %>% 
+  as.data.frame()
+
+column_meta_data <-
+  column_meta_data %>% 
+  rownames_to_column(var = "variable")
+
+column_meta_data <- 
+  column_meta_data %>% 
+  mutate(
+    nulls_by_variable = case_when(NAs > 0 ~ TRUE,
+                                  NAs == 0 ~ FALSE)
+  )
+
+column_meta_data
 ```

### 2023-03-22 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Updating missingness, teams for employees,  and staff rule-based groups

@@
 
+<!--# Done -->
+
 Both data sources will be checked for duplication and deduplicated. The
 daily check-in data has no true unique identifier. The roster data is
-uniquely identified by `employee_e_mail_address` and `snapshot_date`, but some entries for `employee_e_mail_address` are null. 
-The roster data *should not* have any duplications on
-`employee_e_mail_address` and `snapshot_date`, but this will be checked.
-To create a unique identifier in the daily check-in data, we will
-following process:
+uniquely identified by `employee_e_mail_address` and `snapshot_date`,
+but some entries for `employee_e_mail_address` are null. The roster data
+*should not* have any duplications on `employee_e_mail_address` and
+`snapshot_date`, but this will be checked. To create a unique identifier
+in the daily check-in data, we will following process:
 
@@
 
-2.
-Transform supervisor name to match format of the roster data, and create new variables for the end of the month prior to the check-in date and the end of the month of the check-in date to match the `snapshot_date`
+2.  Transform supervisor name to match format of the roster data, and
+    create new variables for the end of the month prior to the check-in
+    date and the end of the month of the check-in date to match the
+    `snapshot_date`
 
-3.  Inner join check-in and roster data  on employee name, department ID and supervisor name, and prior month, creating a new data set called `joined data 1`
+3.  Inner join check-in and roster data on employee name, department ID
+    and supervisor name, and prior month, creating a new data set called
+    `joined data 1`
 
-4.
-Remove rows in `joined data 1` from the check-in data (i.e.
-anti-join), then inner join check-in and roster data  on employee name, department ID and supervisor name, and current month, creating a new data set called `joined data 2`
+4.  Remove rows in `joined data 1` from the check-in data (i.e.
+    anti-join), then inner join check-in and roster data on employee
+    name, department ID and supervisor name, and current month, creating
+    a new data set called `joined data 2`
 
-5.  Bind row from `joined data 1` and `joined data 2`, creating a new data set called `bound data`
+5.  Bind row from `joined data 1` and `joined data 2`, creating a new
+    data set called `bound data`
 
-6.  Select the distinct employee email addresses and names from `bound data` and assign a unique identifier to this called `person_id`, creating a new data set called `unique ID`
+6.  Select the distinct employee email addresses and names from
+    `bound data` and assign a unique identifier to this called
+    `person_id`, creating a new data set called `unique ID`
 
-7.  Join the `unique ID` to `bound data` on employee email addresses and names
+7.  Join the `unique ID` to `bound data` on employee email addresses and
+    names
 
@@
 After this, the combined data *should* be uniquely identified by
-`person_id` and `date`. The data set will contain all the
-daily check-in and roster information across the observation window.
+`person_id` and `date`. The data set will contain all the daily check-in
+and roster information across the observation window.
 
@@
 The analysis will be done for staff and teams separately and aggregated
-independently.
-Employees will be categorized.
-Also, employees with be grouped into teams based on supervisor.
-These teams will also be categorized.
-The table below defines how we plan to aggregate for
-staff and teams.
+independently. Employees will be categorized. Also, employees with be
+grouped into teams based on supervisor. These teams will also be
+categorized. The table below defines how we plan to aggregate for staff
+and teams.
 
@@
 
+For staff-level analysis, the team will be defined by the employee's
+supervisor. Changes in supervisors will come from staff moving teams or
+an existing team changing supervisors. The size of the team will be
+caluculated with the mode of staff with the supervisor over the
+observations window. For employees with multiple supervisors, the size
+of the team will be the average of the modes of team sizes for each
+supervisor.
+
 <!-- How are you doing team classification? Are you going to generate a team -->
+
 <!-- ID based on some rule? If so what is it, and to the prior point, how do -->
+
 <!-- you handle changing team composition over time? -->
 
-Teams will be defined based on the supervisors in March 2022.
-The unique identifier for teams will be the `supervisor_e_mail_address`.
-All employees under those supervisors will be defined as part of the team.
+<!--# Done -->
+
+Teams will be defined based on the supervisors in March 2022. The unique
+identifier for teams will be the `supervisor_e_mail_address`. All
+employees under those supervisors will be defined as part of the team.
 Employees may join and leave a team over the observation window.
@@
 <!-- The analysis plan is a good place to define the rules for classification -->
+
 <!-- Re: missing supervisor name and some other values. It is possible that -->
+
 <!-- people change supervisors or departments. Do we care about this? And how -->
+
 <!-- should we deal with it? At a minimum, maybe we want a slightly different -->
+
 <!-- imputation like if supervisor is the same both with earlier and later -->
+
 <!-- nonmissing observations, use that value, otherwise use prior supervisor? -->
+
+<!--# Done -->
 
@@
   "Drop observation",
-  "Joined with gsa_sso from roster data, impute from other observations of same staff",
-  "Impute from other observations of same staff",
-  "Joined with department_id from roster data, impute from other observations of same staff",
+  "Joined with gsa_sso from roster data, impute from earlier observations of same staff",
+  "Impute from earlier observations of same staff",
+  "Joined with department_id from roster data, impute from earlier observations of same staff",
   "Joined with full_name from roster data, drop observation",
-  "Joined with supervisor_display_name from roster data, impute from other observations of same staff",
+  "Joined with supervisor_display_name from roster data, impute from earlier observations of same staff",
   "Label as missing",
@@
 <!-- Not sure about using percentiles for cutoffs. I would assume based on -->
+
 <!-- classifications that more that 5 percent of teams are fully remote. For -->
+
 <!-- individuals, i think there is more alignment on things like number of -->
+
 <!-- days in a pay period in the office because of policy definitions for -->
+
 <!-- people who are not remote and have to be in the office 2 days per pay -->
+
 <!-- period. For teams maybe an extension of that basic ideas (e.g., fewer -->
+
 <!-- than 2 days in office on average is fully remote) -->
@@
 <!-- Are all of these taking averages over the whole time period (9 months or -->
+
 <!-- whatever)? Would we potentially want to know about things like people -->
+
 <!-- who have more specific weekly patterns? -->
@@
 <!-- The thing that is missing here that is potentially more complicated is -->
+
 <!-- figuring out more about how teams operate as collections of individuals. -->
+
 <!-- For example, you could I think in this approach have a team that is 20 -->
+
 <!-- percent average telework where everyone goes in person on Mondays and -->
+
 <!-- the rest of the time is distributed, or you could have a team that is 20 -->
+
 <!-- percent telework where people go in at random times and never see each -->
+
 <!-- other. I am interested to know the extent to which people are -->
+
 <!-- co-locating with their teams (and if some people are being left -->
+
 <!-- out---which may help motivate some equity questions about performance -->
+
 <!-- ratings for people who don't get face time with the boss, for example). -->
+
 <!-- I think we are missing that level of analysis here. -->
@@
 -->
+
 <!-- Ben: the way I defined groups is mutually exclusive, but does not need to be that way -->
+
 <!-- Ben: Other rules to examine -->
+
 <!-- JB: policy side, missingness (whole groups of people missing on some dimension tells you something about data collection procedure) -->
@@
 non supervisors, pay grade; lower pay grade less likely to have remote option -->
+
 <!-- Ben: confusion matrix - assume that some group works in this sort of way but guess what they don’t! What is happening? -->
@@
 <!-- MD: categories: onsite flexible, onsite, remote; but not sure of levels of going in within categories. What is the average of going in? -->
+
 <!-- MD: discretion of work patterns by regional commissioners  -->
@@
 
-1.  **All remote** - Staff who work remotely above the 95th percentile
-    <!-- could be 75th -->
-2.  **Mostly remote** - Staff who work remotely between the median and
+1.  **All remote** - A policy definition for staff that are 100% remote.
+2.  **Teleworker** - A policy definition for staff that require two days
+    per pay period onsite.
+3.  **Primarily remote** - Staff who work remotely above the 95th
+    percentile <!-- could be 75th -->
+4.  **Mostly remote** - Staff who work remotely between the median and
     the 95th percentile <!-- could be 75th -->
-3.  **Mostly onsite** - Staff who work remotely between 5th percentile
+5.  **Mostly onsite** - Staff who work remotely between 5th percentile
     and the median <!-- could be 25th -->
-4.  **All onsite** - Staff who work remotely below the 5th percentile
-    <!-- could be 75th -->
+6.  **Primarly onsite** - Staff who work remotely below the 5th
+    percentile <!-- could be 75th -->
 
@@
 
-1.  **All remote** - Teams that work remotely above the 95th percentile
-    <!-- could be 75th -->
+1.  **Primarily remote** - Teams that work remotely above the 95th
+    percentile <!-- could be 75th -->
 2.  **Mostly remote** - Teams that work remotely between the median and
@@
     and the median <!-- could be 25th -->
-4.  **All onsite** - Teams that work remotely below the 5th percentile
-    <!-- could be 75th -->
+4.  **Primarily onsite** - Teams that work remotely below the 5th
+    percentile <!-- could be 75th -->
 

### 2023-03-23 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Added a table defining terms, clarified how teams are defined, started cleaning use of terms, added comments from Jake, added variables to capture colocation, and added new rules-based categorization based on position category

@@
 environment.
+
+```{r}
+table_n <- table_n + 1
+```
+
+#### Table `r table_n`: Definitions of teams used in this document
+
+<!-- Table 1 and 2 could use better updating of description column -->
+
+<!-- SSO=Staff or service office -->
+
+<!-- Done -->
+
+```{r}
+tbl_definitions <- tibble("Term" = c(
+  "Staff",
+  "Employee",
+  "Team",
+  "Team member",
+  "Supervisor",
+"Category",
+"Rule-based group",
+"Cluster"
+
+)
+)
+```
+
+```{r}
+tbl <- 
+  tbl_definitions %>% 
+  add_column(
+    "Description" = c(
+  "GSA staff, used when writing more generally",
+"GSA staff when writing about employee-level analysis",
+"A group of employees when writing about team-level analysis",
+"Employee when writing about employee-level analysis",
+"GSA staff who supervise a team, used to define who is in a team",
+"General team for classifications of employees or teams",
+"Category based on some defined rule (i.e. remote worker)",
+"Category based on results for cluster analysis"
+)
+)
+```
+
+```{r}
+tbl %>% 
+  flextable() %>% 
+  # add_header_row(values = c("","","Type of analysis", "Type of analysis")) %>% 
+  # set_header_labels(Group = "Level of analysis") %>% 
+  merge_h(part = "header") %>% 
+  merge_v(j = 1) %>% 
+  theme_vanilla() %>%
+  bold(j = 1) %>% 
+  autofit()
+```
+
+```{r}
+table_n <- table_n + 1
+```
 
@@
 
-The analysis will be done for staff and teams separately and aggregated
-independently. Employees will be categorized. Also, employees with be
-grouped into teams based on supervisor. These teams will also be
+The analysis will be done for employees and teams separately and aggregated
+independently. Employees will be categorized. Also, team members will be defined as belonging to a team based on supervisor. These teams will also be
 categorized. The table below defines how we plan to aggregate for staff
@@
 
-ADD TEAM CLAFFICATION RULES FOR STAFF AND TEAM ANALYSIS
+# CONTINUE REVIEWING TERMS FROM HERE.
 
-We will approach grouping staff and teams in two ways. First,
+# Update based on notes from conversation with Jake 3-23-23
+
+<!-- scaling variables -->
+<!--  - use rank -->
+<!--  - demean and divide by std deviation -->
+<!-- compare clustering results -->
+<!-- check variable distribution -->
+<!-- check pairwise plots of variables -->
+
+We will categorize employees and teams in two ways. First,
 rules-based groups will be formed. For these, definitions of different
-types of work will be defined. Second, groups will be formed using
+types of work will be defined based on the proportion of work done remotely, by policy rules, and by position category. Second, groups will be formed using
 k-means clustering. This unsupervised machine learning method produces a
@@
 
+-   Proportion of working days co-located with at least one other team
+    member
+
+-   Proportion of working days co-located with supervisor
+
+-   Proportion of working days co-located with entire team
+
+-   Proportion of working days entire team is remote
+
 For staff-level analysis, the team will be defined by the employee's
@@
 an existing team changing supervisors. The size of the team will be
-caluculated with the mode of staff with the supervisor over the
+calculated with the mode of staff with the supervisor over the
 observations window. For employees with multiple supervisors, the size
@@
 
--   Proportion of days of staff concurrent remote status
-
--   Proportion of days of staff concurrent onsite status
-
 -   Proportion of staff exiting team
@@
 -   Number of staff working days
+
+-   Proportion of working days at least two team member co-located
+
+-   Proportion of working days supervisor is co-located with at least
+    one team member
+
+-   Proportion of working days entire team is co-located
+
+-   Proportion of working days entire team is remote
 
@@
 
-For the rules based approach, the portion of working days remote will be
-the key variable to determine what category a staff or team will be in.
-Staff will be grouped as follows:
+For the rules-based approach, policy definitions, the position category
+(as defined by `position_category_description`), and the portion of
+working days remote will be determine what category a staff or team will
+be in. Staff will be grouped as follows:
 
-1.  **All remote** - A policy definition for staff that are 100% remote.
+1.  **All remote** - A policy definition for staff that are 100% remote
 2.  **Teleworker** - A policy definition for staff that require two days
     per pay period onsite.
-3.  **Primarily remote** - Staff who work remotely above the 95th
+3.  **Onsite Flexible** - Defined by `position_category_description` in
+    the roster data
+4.  **Offsite** - Defined by `position_category_description` in the
+    roster data
+5.  **Onsite Required** - Defined by `position_category_description` in
+    the roster data
+6.  **Primarily remote** - Staff who work remotely above the 95th
     percentile <!-- could be 75th -->
-4.  **Mostly remote** - Staff who work remotely between the median and
+7.  **Mostly remote** - Staff who work remotely between the median and
     the 95th percentile <!-- could be 75th -->
-5.  **Mostly onsite** - Staff who work remotely between 5th percentile
+8.  **Mostly onsite** - Staff who work remotely between 5th percentile
     and the median <!-- could be 25th -->
-6.  **Primarly onsite** - Staff who work remotely below the 5th
+9.  **Primarily onsite** - Staff who work remotely below the 5th
     percentile <!-- could be 75th -->
@@
 
-1.  **Primarily remote** - Teams that work remotely above the 95th
+1.  **All remote** - All team members are100% remote
+2.  **Teleworker** - All team members work two days per pay period
+    onsite.
+3.  **Onsite Flexible** - All team members are *Onsite Flexible* as
+    defined by `position_category_description` in the roster data
+4.  **Offsite** - All team members are *Offsite* as defined by
+    `position_category_description` in the roster data
+5.  **Onsite Required** - All team members are *Onsite Required* as
+    defined by `position_category_description` in the roster data
+6.  Mixed position categories - Team members are different position
+    categories as as defined by `position_category_description` in the
+    roster data
+7.  **Primarily remote** - Teams that work remotely above the 95th
     percentile <!-- could be 75th -->
-2.  **Mostly remote** - Teams that work remotely between the median and
+8.  **Mostly remote** - Teams that work remotely between the median and
     the 95th percentile <!-- could be 75th -->
-3.  **Mostly onsite** - Teams that work remotely between 5th percentile
+9.  **Mostly onsite** - Teams that work remotely between 5th percentile
     and the median <!-- could be 25th -->
-4.  **Primarily onsite** - Teams that work remotely below the 5th
+10. **Primarily onsite** - Teams that work remotely below the 5th
     percentile <!-- could be 75th -->
@@
 
-For staff clusters, the following variables will be used to define the
-clusters:
+For employee clusters, the following variables will be used to define
+the clusters:
 
@@
 
--   Average size of team over observation window
+-   Modal size of team over observation window
+
+-   Proportion of working days co-located with at least one other team
+    member
+
+-   Proportion of working days co-located with supervisor
+
+-   Proportion of working days co-located with entire team
+
+-   Proportion of working days entire team is remote
 
@@
 
--   Averages size of team over observation window
+-   Modal size of team over observation window
 
@@
 
+    -   Proportion of working days co-located with at least one other
+        team member
+
+    -   Proportion of working days co-located with supervisor
+
+    -   Proportion of working days co-located with entire team
+
+    -   Proportion of working days entire team is remote
+
 -   Team work pattern statistics:
@@
 
-    -   Proportion of concurrent remote days for team members
-
-    -   Proportion of concurrent onsite days for team members
-
     -   Size of teams
@@
     -   Number of staff working days
+
+    -   Proportion of working days at least two team member co-located
+
+    -   Proportion of working days supervisor is co-located with at
+        least one team member
+
+    -   Proportion of working days entire team is co-located
+
+    -   Proportion of working days entire team is remote
 

### 2023-03-29 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Checked for consistent use of terms and updated based on discussion with Jake on clustering.

@@
 
-#Proofread for typos
+<!-- #Proofread for typos -->
 
@@
 
-The analysis will be done for employees and teams separately and aggregated
-independently. Employees will be categorized. Also, team members will be defined as belonging to a team based on supervisor. These teams will also be
-categorized. The table below defines how we plan to aggregate for staff
-and teams.
+The analysis will be done for employees and teams separately and
+aggregated independently. Employees will be categorized. Also, team
+members will be defined as belonging to a team based on supervisor.
+These teams will also be categorized. The table below defines how we
+plan to aggregate for staff and teams.
 
@@
 
-# CONTINUE REVIEWING TERMS FROM HERE.
-
-# Update based on notes from conversation with Jake 3-23-23
-
-<!-- scaling variables -->
-<!--  - use rank -->
-<!--  - demean and divide by std deviation -->
-<!-- compare clustering results -->
-<!-- check variable distribution -->
-<!-- check pairwise plots of variables -->
-
-We will categorize employees and teams in two ways. First,
-rules-based groups will be formed. For these, definitions of different
-types of work will be defined based on the proportion of work done remotely, by policy rules, and by position category. Second, groups will be formed using
+We will categorize employees and teams in two ways. First, rules-based
+groups will be formed. For these, definitions of different types of work
+will be defined based on the proportion of work done remotely, by policy
+rules, and by position category. Second, groups will be formed using
 k-means clustering. This unsupervised machine learning method produces a
@@
 
-For both rules-based and cluster classification of individual staff, the
-daily check-in data will be transformed so that each row is one staff
-person. From the raw data, the following variables will be defined:
+For both rules-based and cluster classification of employee, the daily
+check-in data will be transformed so that each row is one employee. From
+the raw data, the following variables will be defined:
 
@@
 
-For staff-level analysis, the team will be defined by the employee's
-supervisor. Changes in supervisors will come from staff moving teams or
-an existing team changing supervisors. The size of the team will be
-calculated with the mode of staff with the supervisor over the
+For employee analysis, the team will be defined by the employee's
+supervisor. Changes in supervisors will come from employees moving teams
+or an existing team changing supervisors. The size of the team will be
+calculated with the mode of team members with the supervisor over the
 observations window. For employees with multiple supervisors, the size
@@
 Teams will be defined based on the supervisors in March 2022. The unique
-identifier for teams will be the `supervisor_e_mail_address`. All
-employees under those supervisors will be defined as part of the team.
-Employees may join and leave a team over the observation window.
+identifier for teams will be the `supervisor_e_mail_address`. All team
+members under those supervisors will be defined as part of the team.
+Team members may join and leave a team over the observation window.
 
@@
 defined by the supervisor. Supervisors may be in multiple teams as
-supervisor and subordinate. From the raw data, the following variables
+supervisor and team member. From the raw data, the following variables
 will be defined:
@@
 
--   Proportion of staff working days onsite
-
--   Proportion of staff working days remote
-
--   Proportion of staff working days remote by the day of the week
-
--   Proportion of staff exiting team
-
--   Number of staff working days
+-   Proportion of team members working days onsite
+
+-   Proportion of team members working days remote
+
+-   Proportion of team members working days remote by the day of the
+    week
+
+-   Proportion of team members exiting team
+
+-   Number of team members working days
 
@@
     the roster data
-6.  **Primarily remote** - Staff who work remotely above the 95th
+6.  **Primarily remote** - Employees who work remotely above the 95th
     percentile <!-- could be 75th -->
-7.  **Mostly remote** - Staff who work remotely between the median and
-    the 95th percentile <!-- could be 75th -->
-8.  **Mostly onsite** - Staff who work remotely between 5th percentile
-    and the median <!-- could be 25th -->
-9.  **Primarily onsite** - Staff who work remotely below the 5th
+7.  **Mostly remote** - Employees who work remotely between the median
+    and the 95th percentile <!-- could be 75th -->
+8.  **Mostly onsite** - Employees who work remotely between 5th
+    percentile and the median <!-- could be 25th -->
+9.  **Primarily onsite** - Employees who work remotely below the 5th
     percentile <!-- could be 75th -->
@@
     defined by `position_category_description` in the roster data
-4.  **Offsite** - All team members are *Offsite* as defined by
-    `position_category_description` in the roster data
+4.  **Offsite** - All team members are *Offsite* as defined byteam
+    members `position_category_description` in the roster data
 5.  **Onsite Required** - All team members are *Onsite Required* as
@@
 
+<!-- # Update based on notes from conversation with Jake 3-23-23 -->
+
+<!-- scaling variables -->
+
+<!--  - use rank -->
+
+<!--  - demean and divide by std deviation -->
+
+<!-- compare clustering results -->
+
+<!-- check variable distribution -->
+
+<!-- check pairwise plots of variables -->
+
 All of the these variables will be scaled to reduce the effects of
-outliers should they be present.
+outliers should they be present. Two scaling methods will be used:
+
+1.  Normalize - Data will have the mean that that element subtracted and
+    then divided by the standard deviation, using the `scale()`
+    function[^1]
+
+2.  Rank - The rank of each element will be used instead of the element.
+
+[^1]: [Documentation for the scale
+    function.](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/scale)
+
+The scaled elements will be compared to the true data by reviewing their
+distributions and comparing the results of the clusters.
 
@@
 
--   Staff work pattern statistics:
-
-    -   Proportion in staff time telework
-
-    -   Proportion in staff time telework by the day of the week
-
-    -   Proportion in staff time onsite
-
-    -   Proportion in staff time onsite by the day of the week
-
-    -   Correlations of by staff time between the days of the week
+-   Employee work pattern statistics:
+
+    -   Proportion in employee time telework
+
+    -   Proportion in employee time telework by the day of the week
+
+    -   Proportion in employee time onsite
+
+    -   Proportion in employee time onsite by the day of the week
+
+    -   Correlations of by employee time between the days of the week
 
@@
 
-    -   Proportion in staff time telework
-
-    -   Proportion in staff time onsite
+    -   Proportion in team members time telework
+
+    -   Proportion in team members time onsite
 
@@
 
-    -   Number of staff working days
+    -   Number of team members working days
 
@@
 
--   Staff descriptive statistics
-
-    -   Number and proportion of staff by grade
-
-    -   Number and proportion of staff by occupational series
-
-    -   Number and proportion of staff by position category
-
-    -   Number and proportion of staff by GSA region
-
-    -   Number and proportion of staff by SSO
-
-    -   Number and proportion of staff by state
-
-    -   Number and proportion of staff by city
-
-    -   Number and proportion of staff by supervisor level
+-   Employee descriptive statistics
+
+    -   Number and proportion of employees by grade
+
+    -   Number and proportion of employees by occupational series
+
+    -   Number and proportion of employees by position category
+
+    -   Number and proportion of employees by GSA region
+
+    -   Number and proportion of employees by SSO
+
+    -   Number and proportion of employees by state
+
+    -   Number and proportion of employees by city
+
+    -   Number and proportion of employees by supervisor level
 
@@
 
-    -   Number and proportion of staff by most frequent grade
-
-    -   Number and proportion of staff by most frequent occupational
-        series
-
-    -   Number and proportion of staff by most frequent position
+    -   Number and proportion of team members by most frequent grade
+
+    -   Number and proportion of team members by most frequent
+        occupational series
+
+    -   Number and proportion of team members by most frequent position
         category
 
-    -   Number and proportion of staff by most frequent GSA region
-
-    -   Number and proportion of staff by most frequent SSO
-
-    -   Number and proportion of staff by most frequent state
-
-    -   Number and proportion of staff by most frequent city
-
-    -   Number and proportion of staff by most frequent supervisor level
-
-The staff statistics will be calculated for the following groups:
-
-1.  Whole cohort of staff
+    -   Number and proportion of team members by most frequent GSA
+        region
+
+    -   Number and proportion of team members by most frequent SSO
+
+    -   Number and proportion of team members by most frequent state
+
+    -   Number and proportion of team members by most frequent city
+
+    -   Number and proportion of team members by most frequent
+        supervisor level
+
+The employees statistics will be calculated for the following groups:
+
+1.  Whole cohort of employees
 2.  By rule-based categories of work pattern
@@
 
-To understand the relationship between staff work patterns and their
-supervisor, we will calculate the proportion of the staff that fall into
-the same rule-based and clusters as their supervisors overall, as well
-as by the above categories.
+To understand the relationship between employees work patterns and their
+supervisor, we will calculate the proportion of the employees that fall
+into the same rule-based and clusters as their supervisors overall, as
+well as by the above categories.
 

### 2023-03-29 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd
Fixing errors, checking data after addressing problems

@@
   )
-  )
 
@@
   count(supervisor_display_name)
-  arrange(desc(supervisor_e_mail_address.z))
 ```
@@
 column_meta_data
+```
+
+Counting top 10 values for all character or factor columns to identify other common values.
+
+```{r}
+values_count <- 
+  prep_building %>% 
+  select(where(is.character) | where(is.factor)) %>% 
+  names()
+
+values_count %>% 
+  map(~count(prep_building,!!sym(.)) %>% 
+  arrange(desc(n)) %>%
+  slice_head(n = 10))
+
+```
+
+No obvious values.
+
+Function that checks whether there are blanks for different variables
+
+```{r}
+blank_check <- function(in_data,in_variable_name)
+{
+  check_01 <- 
+  in_data %>% 
+    filter(!!sym(in_variable_name) == "") %>% 
+  distinct()
+
+out <- nrow(check_01) > 0
+
+return(out)
+}
+```
+
+Checking blanks for each variable in the dataframe.
+
+```{r}
+blanks_by_variable <- 
+  column_meta_data %>% 
+  pull(variable) %>% 
+  map_lgl(~blank_check(in_data = prep_building,.))
+
+blanks_by_variable
+```
+
+Add this to the `column_meta_data` dataframe.
+
+```{r}
+column_meta_data <- 
+  column_meta_data %>% 
+  add_column(
+    blanks_by_variable = blanks_by_variable
+  )
+
+column_meta_data
+```
+
+Create dataframe of only variables that have blanks.
+
+```{r}
+problem_variables <- 
+  column_meta_data %>% 
+  filter(blanks_by_variable | nulls_by_variable)
+
+problem_variables
+```
+
+Grouping variables.
+
+```{r}
+problem_variables <- 
+  problem_variables %>% 
+  mutate(group = 
+           case_when(variable == "position_category_code" ~ "position_category_code",
+                     variable == "position_category_description" ~ "position_category_code",
+                     TRUE ~ variable
+                     ))
+
+problem_variables
+```
+
+Create list of groups.
+
+```{r}
+problem_groups <- 
+  problem_variables %>% 
+  select(group) %>% 
+  distinct() %>% 
+  arrange(group) %>% 
+  pull()
+
+problem_groups
 ```

### 2023-04-12 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd

@@
 ---
+
+```{r}
+tictoc::tic()
+```
 
@@
 
+## Functions
+
+Function to display datatable.
+
+```{r}
+datatable_with_sampling <- function(in_data, in_max_rows)
+{
+  if(nrow(in_data) > in_max_rows)
+{
+  print(glue::glue("Big dataframe. Sampling {scales::comma(in_max_rows)} rows. {Sys.time()}"))
+  prep_01 <- 
+    in_data %>% 
+    sample_n(size = in_max_rows)
+}
+
+if(nrow(in_data) <= in_max_rows)
+{
+  prep_01 <- 
+    in_data
+}
+prep_01 %>% 
+  DT::datatable(class = 'cell-border stripe')
+}
+```
+
 ## Load data {.tabset .tabset-pills}
@@
   get_dupes(date,employee_e_mail_address) %>%
-  arrange(desc(dupe_count))
+  arrange(desc(dupe_count)) %>% 
+  datatable_with_sampling(in_max_rows = 5000)
 ```
@@
 prep_building %>% 
-  get_dupes(person_id,date)
+  get_dupes(person_id,date) %>% 
+  datatable_with_sampling(in_max_rows = 5000)
 ```
@@
 ```
+
 Also create a building dataframe to add other dataframes where missing have been removed.
@@
 prep_01 %>% 
-  DT::datatable(class = 'cell-border stripe')
+  datatable_with_sampling(in_max_rows = 5000)
 ```
@@
 prep_02 %>% 
-  DT::datatable(class = 'cell-border stripe')
-```
-
-It apprears that most start with nulls then became a category.
+  datatable_with_sampling(in_max_rows = 5000)
+```
+
+It appears that most start with nulls then became a category.
 
@@
   ) %>% 
-  DT::datatable(class = 'cell-border stripe')
+  datatable_with_sampling(in_max_rows = 5000)
 ```
@@
 
-nulls_01
+nulls_01 %>% 
+  datatable_with_sampling(in_max_rows = 5000)
 ```
@@
 
+Let's remove `supervisor_correction`.
+
+```{r}
+prep_xx <- 
+  prep_xx %>% 
+  select(-supervisor_correction)
+```
+
 Join to building dataframe.
@@
 
-prep_01
+prep_01 %>% 
+  datatable_with_sampling(in_max_rows = 5000)
 ```
@@
 
-prep_02
+prep_02 %>% 
+  datatable_with_sampling(in_max_rows = 5000)
 ```
@@
 
+if("NAs" %in% names(column_meta_data))
+{
   column_meta_data <- 
@@
   )
+}
+
+if(!("NAs" %in% names(column_meta_data)))
+{
+  column_meta_data <- 
+  column_meta_data %>% 
+  mutate(
+    nulls_by_variable = FALSE
+  )
+}
 
@@
 
-Grouping variables.
-
-```{r}
-problem_variables <- 
-  problem_variables %>% 
-  mutate(group = 
-           case_when(variable == "position_category_code" ~ "position_category_code",
-                     variable == "position_category_description" ~ "position_category_code",
-                     TRUE ~ variable
-                     ))
-
-problem_variables
-```
-
-Create list of groups.
-
-```{r}
-problem_groups <- 
-  problem_variables %>% 
-  select(group) %>% 
-  distinct() %>% 
-  arrange(group) %>% 
-  pull()
-
-problem_groups
-```
-
-# CONTINUE FROM HERE.
-
-Third, remove data from building dataframe, then inner join by employee name.
-
-```{r}
-prep_xx <- 
-  prep_base_1 %>% 
-  anti_join(prep_building) %>%
-  inner_join(prep_base_2,
-            by =  c("employee_name" = "full_name"
-                    ),
-            suffix = c("_daily","_roster")
-  ) %>% 
-  select(-starts_with("file_name")) %>% 
-  distinct()
-```
-
-Review.
-
-```{r}
-prep_xx %>%  skim()
-```
-
-Bind to building dataframe.
-
-```{r}
-prep_building <- prep_building %>% 
-  bind_rows(prep_xx) %>% 
-  distinct()
-```
-
-```{r}
-unique_email_building <- prep_building %>% summarise(n_distinct(employee_e_mail_address)) %>% pull()
-unique_email_building
-```
-
-Test: This does not differ from the base.
-
-```{r}
-unique_email_base == unique_email_building
-```
-
-```{r}
-prep_building %>%  skim()
-```
-
-Load all data files in the `r params$data_folder_2` data folder.
-
-```{r}
-prep_base_2_1 <- files_2[1] %>% 
-  map_dfr(~mutate(.data = read_xlsx(path = ., 
-                                    col_types = c("date", "text", "text", 
-        "text", "text", "text", "text", "text", 
-        "text", "date", "text", "text", "text", 
-        "text", "text", "text", "text", "text", 
-        "text", "text", "text", "text", "text", 
-        "text", "text", "text", "text", "text")), 
-        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
-      )) %>% 
-  clean_names() %>% 
-  distinct()
-```
-
-```{r}
-prep_base_2_2 <- files_2[2] %>% 
-  map_dfr(~mutate(.data = read_xlsx(path = ., 
-                                    col_types = c("date", "text", "text", 
-        "text", "text", "text", "text", "text", 
-        "text", "date", "text", "text", "text", 
-        "text", "text", "text", "text", "text", 
-        "text", "text", "text", "text", "text", 
-        "text", "text", "text", "text", "text")), 
-        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
-      )) %>% 
-  clean_names() %>% 
-  distinct()
-```
-
-```{r}
-prep_base_2_3 <- files_2[3] %>% 
-  map_dfr(~mutate(.data = read_xlsx(path = ., 
-                                    col_types = c("date", "text", "text", 
-        "text", "text", "text", "text", "text", 
-        "text", "date", "text", "text", "text", 
-        "text", "text", "text", "text", "text", 
-        "text", "text", "text", "text", "text", 
-        "text", "text", "text", "text", "text")), 
-        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
-      )) %>% 
-  clean_names() %>% 
-  distinct()
-```
-
-Joining data
-
-```{r}
-step_1 <- prep_base_1 %>% 
-  # select(employee_name) %>% 
-  # distinct() %>% 
-   left_join(prep_base_2_1,
-            by = c("employee_name" = "full_name",
-                   "sso" = "gsa_sso",
-                   "dept_id" = "department_id",
-                   "supervisor_display_name" = "supervisor_display_name"
-                   )) %>% 
-  # filter(rollback(date) == snapshot_date |
-  #          rollforward(date) == snapshot_date) %>%
-  # select(-snapshot_date, -starts_with("file_name")) %>% 
-  distinct()
-  # skim()
-  # get_dupes(employee_e_mail_address,date)
-```
-
-```{r}
-step_1 %>% 
-  filter(!is.na(employee_e_mail_address)) %>% 
-  get_dupes(employee_name,date,sso, dept_id, supervisor_display_name)
-```
-
-```{r}
-step_1 %>% 
-  filter(!is.na(employee_e_mail_address)) %>% 
-  get_dupes(employee_e_mail_address,date)
-```
-
-```{r}
-step_2 <- 
-  step_1 %>% 
-  filter(!is.na(employee_e_mail_address)) %>% 
-  get_dupes(employee_name) %>% 
-  select(employee_name) %>% 
-  distinct()
-```
-
-```{r}
-step_3 <- 
-  step_2 %>% 
-  inner_join(prep_base_1 %>% 
-  select(employee_name,sso) %>% 
-    distinct()) %>% 
-  left_join(prep_base_2_1,
-            by = c("employee_name" = "full_name",
-                   "sso" = "gsa_sso"
-                   # ,
-                   # "dept_id" = "department_id",
-                   # "supervisor_display_name" = "supervisor_display_name"
-                   )) %>% 
-  # filter(rollback(date) == snapshot_date |
-  #          rollforward(date) == snapshot_date) %>%
-  # select(-snapshot_date, -starts_with("file_name")) %>% 
-  distinct()
-```
-
-```{r}
-step_3 %>% 
-  filter(!is.na(employee_e_mail_address)) %>% 
-  get_dupes(employee_name,employee_e_mail_address)
-```
-
-```{r}
-step_2 <- 
-  step_1 %>% 
-  filter(is.na(employee_e_mail_address)) %>% 
-  select(all_of(prep_base_1_names)) %>% 
-  left_join(prep_base_2_2,
-            by = c("employee_name" = "full_name",
-                   "sso" = "gsa_sso",
-                   "dept_id" = "department_id",
-                   "supervisor_display_name" = "supervisor_display_name"
-                   )) %>% 
-  # filter(rollback(date) == snapshot_date |
-  #          rollforward(date) == snapshot_date) %>%
-  # select(-snapshot_date, -starts_with("file_name")) %>% 
-  distinct()
-```
-
-```{r}
-step_3 <- 
-  step_2 %>% 
-  filter(is.na(employee_e_mail_address)) %>% 
-  select(all_of(prep_base_1_names)) %>% 
-  left_join(prep_base_2_3,
-            by = c("employee_name" = "full_name",
-                   "sso" = "gsa_sso",
-                   "dept_id" = "department_id",
-                   "supervisor_display_name" = "supervisor_display_name"
-                   )) %>% 
-  # filter(rollback(date) == snapshot_date |
-  #          rollforward(date) == snapshot_date) %>%
-  # select(-snapshot_date, -starts_with("file_name")) %>% 
-  distinct()
-```
-
-```{r}
-step_3 %>% 
-  filter(!is.na(employee_e_mail_address))
-```
-
-```{r}
-rollback(ymd('2022-12-01'))
-rollforward(ymd('2022-12-01'))
-```
-
-### Review data
-
-```{r}
-prep_base %>% skim()
-```
-
-## Addressing duplication
-
-We are using `r params$unique_identifier_1` as the unique identifier.
-
-### Check for duplication
-
-```{r}
-dupe_01 <- 
-  prep_base %>%
-  get_dupes(params$unique_identifier_1)
-```
-
-#### Data review
-
-```{r}
-dupe_01 %>% 
+## Other data issues
+
+Review the data.
+
+```{r}
+prep_building %>% 
   skim()
@@
 
-### Dataframe of the unique identifier
-
-```{r}
-prep_uniq <- 
-  prep_base %>% 
-  select(params$unique_identifier_1) %>% 
-  distinct()
-
-prep_uniq %>% 
-  count()
-```
-
-### Identifying and categorizing columns
-
-Created a dataframe of variable metadata
-
-```{r}
-column_meta_data <- 
-  prep_base %>% 
-  contents()
-
-column_meta_data <- 
-  column_meta_data$contents %>% 
-  as.data.frame()
-
-column_meta_data <-
-  column_meta_data %>% 
-  rownames_to_column(var = "variable")
-
-column_meta_data
-```
-
-Function that checks whether there are duplicates for different variables
-
-```{r}
-dupe_check <- function(in_data,in_variable_name)
-{
-  check_01 <- 
-  in_data %>% 
-  select(params$unique_identifier_1,all_of(in_variable_name)) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-
-out <- nrow(check_01) > 0
-
-return(out)
-}
-```
-
-Checking duplicates for each variable in the dataframe.
-
-```{r}
-duplicates_by_variable <- 
-  column_meta_data %>% 
-  pull(variable) %>% 
-  map_lgl(~dupe_check(in_data = dupe_01, .))
-
-duplicates_by_variable
-```
-
-Add this to the column_meta_data dataframe.
-
-```{r}
-column_meta_data <- 
-  column_meta_data %>% 
-  add_column(
-    duplicates_by_variable = duplicates_by_variable
-  )
-
-column_meta_data
-```
-
-Create dataframe of only variables that cause duplicates.
-
-```{r}
-duplicating_variables <- 
-  column_meta_data %>% 
-  filter(duplicates_by_variable)
-
-duplicating_variables
-```
-
-Grouping variables.
-
-```{r}
-duplicating_variables <- 
-  duplicating_variables %>% 
-  mutate(group = 
-           case_when(variable == "short_id" ~ "short_id",
-                     variable == "dept_id" ~ "short_id",
-                     variable == "supervisor_name" ~ "short_id",
-                     variable == "location" ~ "short_id",
-                    TRUE ~ variable
-                     ))
-
-duplicating_variables
-```
-
-Create list of groups.
-
-```{r}
-duplicating_groups <- 
-  duplicating_variables %>% 
-  select(group) %>% 
-  distinct() %>% 
-  pull()
-
-duplicating_groups
-```
-
-### Duplication removal
-
-```{r}
-step_n <- 0
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-Not too many duplicates here.
-
-First count `sso` across the original data.
-
-```{r}
-prep_base %>% count(sso)
-```
-
-There are just a few, but we'll want to transform these into indicators.
-
-We want to have this change to affect the whole dataframe so we address the duplicates off the original dataframe.
-
-```{r}
-prep_xx <- 
-  prep_base %>% 
-  character_to_indicator(params$unique_identifier_1,sso,"sso")
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-Rename dataframe.
-
-```{r}
-prep_01 <- prep_xx
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-Quite a few duplicates here and they are associated with supervisor and location.
-
-First count `short_id` and `dept_id` across the original data.
-
-```{r}
-prep_base %>% count(short_id,dept_id)
-```
-
-Counting `short_id`.
-
-```{r}
-prep_base %>% count(short_id)
-```
-
-Counting `dept_id`.
-
-```{r}
-prep_base %>% count(dept_id)
-```
-
-Too many options to create useful indicators.
-
-For lack better option, we'll select the rows with shorter ids.
-
-```{r}
-dedupe <- 
-  dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  arrange(!!!params$unique_identifier_1,length(short_id),length(dept_id)) %>% 
-  group_by(across(all_of(params$unique_identifier_1))) %>% 
-  summarise(
-    across(.fns = ~first(.))
-  )
-
-dedupe %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-Creating a deduplicated dataframe of `r params$unique_identifier_1` and `r duplicating_groups[step_n]`.
-
-First create a dataframe of distinct rows of the variables from the original data.
-
-```{r}
-working_01 <- 
-  prep_base %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct()
-
-working_01 %>% 
-  glimpse()
-
-working_01 %>% 
-  skim()
-```
-
-Next remove rows that dataframe that were found to be duplicated and save that as a new dataframe.
-
-```{r}
-working_02 <- 
-  working_01 %>% 
-  anti_join(dedupe %>% select(params$unique_identifier_1))
-
-working_02 %>% 
-  glimpse()
-
-working_02 %>% 
-  skim()
-```
-
-Last bind this dataframe to the deduplicated set above.
-
-```{r}
-prep_xx <- 
-  working_02 %>% 
-  bind_rows(dedupe)
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Count rows.
-
-```{r}
-prep_xx %>% 
-  count()
-```
-
-Do the number of in this dataframe match the number of unique identifiers?
-
-```{r}
-prep_xx %>% 
-  count() %>% 
-  pull() ==
-  prep_uniq %>% 
-  count() %>% 
-  pull()
-```
-
-Rename dataframe
-
-```{r}
-prep_02 <- prep_xx
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`
-
-Removing duplicates produced by:
-
-```{r}
-duplicating_group <- 
-  duplicating_variables %>% 
-  filter(group == duplicating_groups[step_n])
-duplicating_group
-```
-
-Reviewing duplicates.
-
-```{r}
-dupe_01 %>% 
-  select(params$unique_identifier_1,all_of(duplicating_group %>% pull(variable))) %>% 
-  distinct() %>% 
-  get_dupes(params$unique_identifier_1)
-```
-
-Create function to drop rows with null unique identifiers.
-
-```{r}
-filter_unique <- function(in_data, ...)
-{
-  in_data %>% 
-  filter(if_all(c(...),~!is.na(.)))
-}
-```
-
-Drop rows with null unique identifiers.
-
-```{r}
-prep_01 <- 
-  prep_01 %>% 
-  filter_unique(params$unique_identifier_1)
-```
-
-Review data.
-
-```{r}
-prep_01 %>% skim()
-```
-
-Identify columns with amounts unique values less than 30.
-
-```{r}
-low_unique_value_cols <- 
-  prep_01 %>% 
-  summarise(across(.fns = ~n_distinct(.))) %>% 
-  rownames_to_column() %>% 
-  pivot_longer(-rowname) %>% 
-  filter(value < 30) %>% 
-  pull(name)
-```
-
-**Unique low value columns**: `r low_unique_value_cols`
-
-Convert low unique value variables to factors.
-
-```{r}
-prep_01 <- 
-  prep_01 %>% 
-  mutate(across(all_of(low_unique_value_cols),as.factor))
-```
-
-Review data.
-
-```{r}
-prep_01 %>% skim()
-```
-
-## Join/bind data {.tabset .tabset-pills}
-
-No data to join or bind so far.
-
-```{r}
-d <- prep_01
-```
-
-Review data.
-
-```{r}
-d %>% skim()
+## Creating final dataframe
+
+```{r}
+check_in_panel <- prep_building
+```
+
+```{r}
+rm(prep_building)
 ```
@@
 ```{r}
-save(d, file = here::here("03. Data Collection",params$data_folder_1,"prepared_data.rdata"))
-```
+save(check_in_panel, file = file.path(params$google_drive_home,"03. Data Collection","prepared-data",
+          glue::glue("check_in_panel_{Sys.Date()}.rdata")))
+```
+
+Remove all data elements.
+
+```{r}
+rm(list = ls())
+gc()
+```
+
+## Extraction time {.tabset .tabset-pills}
+
+```{r}
+tictoc::toc()
+```

### 2023-04-12 04. Analysis/scripts/01_data_preparation.Rmd
Update 01_data_preparation.Rmd
Adding timer and removing function that was moved to oesrrr

@@
 
-```{r}
-tictoc::tic()
-```
-
 ```{r setup, include=FALSE}
 knitr::opts_chunk$set(echo = TRUE)
+tictoc::tic()
 if(!("arsenal" %in% installed.packages()[,"Package"]))
@@
 
-## Functions
-
-Function to display datatable.
-
-```{r}
-datatable_with_sampling <- function(in_data, in_max_rows)
-{
-  if(nrow(in_data) > in_max_rows)
-{
-  print(glue::glue("Big dataframe. Sampling {scales::comma(in_max_rows)} rows. {Sys.time()}"))
-  prep_01 <- 
-    in_data %>% 
-    sample_n(size = in_max_rows)
-}
-
-if(nrow(in_data) <= in_max_rows)
-{
-  prep_01 <- 
-    in_data
-}
-prep_01 %>% 
-  DT::datatable(class = 'cell-border stripe')
-}
-```
-
 ## Load data {.tabset .tabset-pills}

### 2023-04-12 04. Analysis/scripts/01_data_preparation.R
Update 01_data_preparation.R

@@ -14,8 +14,11 @@ library(purrr)
 author <- "Ben Jaques-Leslie"
 project_number <- 2312
 project_name <- "Occupancy Patterns"
+google_drive_home <- "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
 data_folder_1 <- "Occupancy Data Pull"
-unique_identifier_1 <- c("employee_name")
+unique_identifier_1 <- c("employee_name","date")
+data_folder_2 <- "Rosters"
+unique_identifier_2 <- c("snapshot_date","employee_e_mail_address")
 
 # Determine file name -----------------------------------------------------
 
@@ -32,8 +35,11 @@ rmarkdown::render(input = here::here("04. Analysis",
                     author = author,
                     project_number = project_number,
                     project_name = project_name,
+                    google_drive_home = google_drive_home,
                     data_folder_1 = data_folder_1,
-                    unique_identifier_1 = unique_identifier_1
+                    unique_identifier_1 = unique_identifier_1,
+                    data_folder_2 = data_folder_2,
+                    unique_identifier_2 = unique_identifier_2
                   ),
                   output_file =
                     here::here("04. Analysis",

### 2023-04-19 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Adding variable for teams that don't exist during entire period
Update MSG-P2312-Analysis Plan-1-clusters.rmd
More updates for proportion of observation window

@@
 telework behaviors match position category (e.g., onsite, offsite, etc.)
-in the roster? 3. At what rates to teams work together onsite vs.
+in the roster? 3. At what rates do teams work together onsite vs.
 remotely? 4. Do the telework patterns of supervisors match the telework
@@
 `snapshot_date`, but this will be checked. To create a unique identifier
-in the daily check-in data, we will following process:
+in the daily check-in data, we will use the following process:
 
@@
 -   Proportion of working days entire team is remote
+
+-   Proportion of observation window the team existed
 
@@
 
+-   Proportion of observation window the team existed.
+
 <!-- # Update based on notes from conversation with Jake 3-23-23 -->
@@
     -   Proportion of working days entire team is remote
+
+    -   Proportion of observation window the team exists
 

### 2023-04-19 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Create 02_data_preparation_clusters_employee.Rmd
initial commit

--- 2023-04-12 04. Analysis/scripts/01_data_preparation.Rmd
@@
 ---
-title: "Data preparation"
+title: "Data preparation for employee category analysis"
 date: "`r Sys.Date()`"
@@
   google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
-  data_folder_1: "Occupancy Data Pull"
-  unique_identifier_1: !r c("employee_name","date")
-  data_folder_2: "Rosters"
-  unique_identifier_2: !r c("snapshot_date","employee_e_mail_address")
+  data_folder_1: "prepared-data"
+  data_file_1: "check_in_panel_2023-04-12.rdata"
+  unique_identifier_1: !r c("date","person_id")
+  date_cohort_month: "2022-03-01"
+  observation_window_length_months: 6
 ---
@@
 
+```{r cohort dates}
+date_cohort_month_start <- ymd(params$date_cohort_month)
+date_cohort_month_end <- ceiling_date(date_cohort_month_start,unit = "month") %>% rollbackward()
+date_observation_window_month_start <- date_cohort_month_start %m+% months(params$observation_window_length_months)
+date_observation_window_month_end <- ceiling_date(date_observation_window_month_start,unit = "month") %>% rollbackward()
+```
+
 # Data preparation {.tabset .tabset-pills}
@@
 
-**Data folder 1**: `r params$data_folder_`'
-
-**Unique identifier for data folder 1**: `r params$unique_identifier_1`
+**Data folder 1**: `r params$data_folder_1`
+
+**Data file 1**: `r params$data_file_1`
+
+**Unique identifier for data file 1**: `r params$unique_identifier_1`
+
+**Cohort start month**: `r nice_month_year(date_cohort_month_start)`
+
+**Observation window**: `r nice_month_year(date_cohort_month_start)` to `r nice_month_year(date_observation_window_month_end)` (`r params$observation_window_length_months` months)
 
@@
 
-### Data files
-
-Find the list of .csv files in the `r params$data_folder_1` data folder.
-
-```{r}
-files_1 <- 
-  list.files(file.path(params$google_drive_home,"03. Data Collection",params$data_folder_1), pattern = ".csv", full.names = TRUE)
-files_1
-```
-
-Find the list of .csv files in the `r params$data_folder_2` data folder.
-
-```{r}
-files_2 <- 
-  list.files(file.path(params$google_drive_home,"03. Data Collection",params$data_folder_2), pattern = ".xlsx", full.names = TRUE)
-files_2
-```
-
-### Load data
-
-Load all data files in the `r params$data_folder_1` data folder.
-
-```{r}
-prep_base_1 <- files_1 %>% 
-  map_dfr(~mutate(.data = read_csv(., 
-    col_types = cols(Date = col_date(format = "%m_%d_%Y"))), 
-        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
-      )) %>% 
+Load `r params$data_file_1` from `r params$data_folder_1` data folder.
+
+```{r}
+load(file = file.path(params$google_drive_home,"03. Data Collection",params$data_folder_1,params$data_file_1))
+```
+
+Review.
+
+```{r}
+check_in_panel %>% 
+  skim()
+```
+
+## Creating cohort
+
+Collect `person_id` of employees that worked in `r nice_month_year(date_cohort_month_start)`.
+
+```{r}
+cohort_ids <- 
+  check_in_panel %>% 
+  filter(date >= date_cohort_month_start & date <= date_cohort_month_end) %>% 
+  select(person_id) %>% 
+  distinct()
+```
+
+Review.
+
+```{r}
+cohort_ids %>% 
+  skim()
+```
+
+Join with full panel.
+
+```{r}
+cohort_panel <- 
+  cohort_ids %>% 
+  inner_join(check_in_panel) %>% 
+  filter(date >= date_cohort_month_start & date <= date_observation_window_month_end)
+```
+
+Review.
+
+```{r}
+cohort_panel %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  cohort_panel %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Create dataframe of all initial characteristics.
+
+```{r}
+cohort_first <- 
+  cohort_panel %>% 
+  arrange(person_id,date) %>% 
+  group_by(person_id) %>% 
+  summarise(
+    across(
+      .cols = everything(),
+      .fns = first
+    )
+  ) %>% 
+  ungroup()
+```
+
+Review.
+
+```{r}
+cohort_first %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  cohort_first %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+````
+
+## Creating aggregated variables
+
+```{r}
+cohort_panel %>% 
+  summarise(working_days = n_distinct(date)) %>% 
+  ungroup()
+```
+
+```{r}
+cohort_panel %>% 
+  group_by(person_id) %>% 
+  filter(daily_status_imputed != "Leave") %>% 
+  summarise(working_days = n_distinct(date)) %>% 
+  ungroup()
+```
+
+```{r}
+cohort_panel %>%
+  mutate(daily_status_imputed = factor(daily_status_imputed)) %>% 
+  group_by(person_id,daily_status_imputed,.drop = FALSE) %>% 
+  summarise(working_days = n_distinct(date)) %>% 
+  ungroup() %>% 
+  pivot_wider(values_from = working_days, names_from = daily_status_imputed) %>% 
   clean_names() %>% 
-  distinct() %>% 
-  separate(supervisor_name,into = c("sup_last","sup_first"), sep = ",") %>% 
-  mutate(
-    across(
-      .cols = starts_with("sup_"),
-      .fns = ~word(.,1)
-    )
-  ) %>% 
-  unite(col = "supervisor_display_name",sup_first,sup_last, sep = " ") %>% 
-  rename(file_name_1 =file_name)%>% 
-  mutate(
-    date_month = floor_date(date,unit = "month"),
-    date_month_rollback = rollback(date_month),
-    date_month_forward = rollforward(date_month)
-  )
-```
-
-Review.
-
-```{r}
-prep_base_1 %>% 
-  skim()
-```
+  rename_with(~glue::glue("daily_status_imputed_{.}"), -person_id)
+```
+
+-   Proportion of days onsite
+
+-   Proportion of days remote
+
+-   Proportion of days remote by the day of the week
+
+-   Correlation of work status between days of the week
+
+-   Number of working days
+
+-   Modal size of team over observation window
+
+-   Proportion of working days co-located with at least one other team
+    member
+
+-   Proportion of working days co-located with supervisor
+
+-   Proportion of working days co-located with entire team
+
+-   Proportion of working days entire team is remote
 

### 2023-04-19 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Developed person-level who period aggregates

@@
 
+Updated data type for check-in status.
+
+```{r}
+check_in_panel <- 
+  check_in_panel %>% mutate(
+    daily_status_imputed = factor(daily_status_imputed),
+    daily_status_imputed =
+      fct_recode(daily_status_imputed,
+                 permanent_departure = "This employee is no longer with the agency (retired, resigned, or other form of permanent departure)")
+  )
+```
+
 ## Creating cohort
@@
   pull()
-````
+```
+
+Set up `prep_building`.
+
+```{r}
+prep_building <- 
+  cohort_ids
+```
 
@@
 
-```{r}
+### Employee, whole period variables
+
+For following variables are aggregated for the whole period for each employee:
+
+-   Proportion of days onsite
+
+-   Proportion of days remote
+
+-   Number of working days
+
+First, calculating the number of days in the observation window.
+
+```{r}
+observation_window_days <- 
   cohort_panel %>% 
-  summarise(working_days = n_distinct(date)) %>% 
-  ungroup()
-```
-
-```{r}
+  summarise(observation_window_days = n_distinct(date)) %>% 
+  ungroup() %>% 
+  pull()
+
+observation_window_days
+```
+
+Now calculating the number of days per employee by `daily_status_imputed`.
+Proportions are caluculated for onsite and telework only.
+The calculations are made in two ways in two ways.
+First as a proportion of employee working days:
+
+$$
+\frac{DailyStatusDays}{WorkingDays}
+$$
+
+where
+
+$$
+WorkingDays = OnsiteDays + TeleworkDays
+$$
+
+Second as a proportion of days in the observations window:
+
+$$
+\frac{DailyStatusDays}{ObservationWindowDays}
+$$
+
+```{r}
+prep_xx <- 
   cohort_panel %>%
-  group_by(person_id) %>% 
-  filter(daily_status_imputed != "Leave") %>% 
-  summarise(working_days = n_distinct(date)) %>% 
-  ungroup()
-```
-
-```{r}
-cohort_panel %>%
-  mutate(daily_status_imputed = factor(daily_status_imputed)) %>% 
   group_by(person_id,daily_status_imputed,.drop = FALSE) %>% 
@@
   clean_names() %>% 
-  rename_with(~glue::glue("daily_status_imputed_{.}"), -person_id)
-```
-
--   Proportion of days onsite
-
--   Proportion of days remote
+  rename_with(~glue::glue("daily_status_{.}"), -person_id) %>% 
+  mutate(
+    working_days = daily_status_reporting_to_job_site + daily_status_teleworking,
+    daily_status_reporting_to_job_site_working_prop = daily_status_reporting_to_job_site/working_days,
+    daily_status_teleworking_working_prop = daily_status_teleworking/working_days,
+    daily_status_reporting_to_job_site_observation_prop = daily_status_reporting_to_job_site/observation_window_days,
+    daily_status_teleworking_observation_prop = daily_status_teleworking/observation_window_days
+  ) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  )
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+prep_xx %>% 
+  pivot_longer(-person_id) %>% 
+  filter(str_detect(name, "_prop")) %>% 
+  ggplot(aes(x = value)) +
+  geom_histogram() +
+  facet_wrap(facets = vars(name))
+```
 
@@
 
--   Number of working days
-
 -   Modal size of team over observation window
 
--   Proportion of working days co-located with at least one other team
-    member
+-   Proportion of working days co-located with at least one other team member
 
@@
 ```
+
 Review.

### 2023-04-19 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Adding section of days of the week and correlations

@@
 check_in_panel <- 
-  check_in_panel %>% mutate(
+  check_in_panel %>% 
+  mutate(
     daily_status_imputed = factor(daily_status_imputed),
@@
   )
+```
+
+Create days of the week for dates.
+
+```{r}
+check_in_panel <- 
+  check_in_panel %>% 
+  mutate(date_day_of_week = wday(date, label = TRUE))
 ```
@@
 
+### Employee, day of week variables
+
+For following variables are aggregated for the whole period by day of the week for each employee:
+
+-   Proportion of days remote by the day of the week
+
+-   Correlation of work status between days of the week
+
+First, calculating the number of days in the observation window.
+
+```{r}
+observation_window_days_day_of_week <- 
+  cohort_panel %>% 
+  group_by(date_day_of_week) %>% 
+  summarise(observation_window_days = n_distinct(date)) %>% 
+  ungroup()
+
+observation_window_days_day_of_week
+```
+
+We make the same calculations as above, but by the day of the week.
+
+```{r}
+prep_xx <-
+  cohort_panel %>%
+  group_by(person_id,daily_status_imputed,date_day_of_week,) %>% 
+  summarise(working_days = n_distinct(date)) %>% 
+  ungroup() %>% 
+  pivot_wider(values_from = working_days, names_from = c(daily_status_imputed)) %>% 
+  left_join(observation_window_days_day_of_week) %>% 
+  clean_names() %>% 
+  rename_with(~glue::glue("daily_status_{.}"), c(-person_id,-date_day_of_week,-observation_window_days))  %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  ) %>% 
+  mutate(
+    working_days = daily_status_reporting_to_job_site + daily_status_teleworking,
+    daily_status_reporting_to_job_site_working_prop = daily_status_reporting_to_job_site/working_days,
+    daily_status_teleworking_working_prop = daily_status_teleworking/working_days,
+    daily_status_reporting_to_job_site_observation_prop = daily_status_reporting_to_job_site/observation_window_days,
+    daily_status_teleworking_observation_prop = daily_status_teleworking/observation_window_days
+  )  %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  )
+```
+
+```{r}
+cohort_panel %>% 
+  select(person_id,date,date_day_of_week,daily_status_imputed) %>% 
+  mutate(ind = 1) %>% 
+  pivot_wider(names_from = daily_status_imputed, values_from = ind) %>% 
+  clean_names() %>% 
+  select(person_id,date,date_day_of_week,teleworking) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  ) %>% 
+  mutate(
+    date_week_start = floor_date(date,unit = "week")) %>% 
+  select(-date) %>% 
+  pivot_wider(values_from = teleworking,names_from = date_day_of_week) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  ) %>% 
+  group_by(person_id) %>%
+  # filter(person_id == "10070")
+  summarise(cor = cor(Fri,Wed,method = "kendall", use = "complete.obs"))
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
+```{r}
+cor(check_in_panel$daily_status_imputed,check_in_panel$date_day_of_week)
+```
+
 ```{r}
@@
 ```
-
--   Proportion of days remote by the day of the week
-
--   Correlation of work status between days of the week
 

### 2023-04-20 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Testing another approach to correlations between days

@@
 
-```{r}
+```{r correlation remote only}
 cohort_panel %>% 
@@
   summarise(cor = cor(Fri,Wed,method = "kendall", use = "complete.obs"))
+```
+
+```{r correlation ordered status}
+cohort_panel %>% 
+  select(person_id,date,date_day_of_week,daily_status_imputed) %>% 
+  mutate(
+    daily_status_imputed = fct_lump_prop(daily_status_imputed, prop = .1),
+    daily_status_imputed = fct_infreq(daily_status_imputed),
+    daily_status_imputed = factor(daily_status_imputed, ordered = TRUE)
+  )  %>% 
+  mutate(
+    date_week_start = floor_date(date,unit = "week")) %>% 
+  select(-date) %>% 
+  pivot_wider(values_from = daily_status_imputed,names_from = date_day_of_week) %>% 
+  mutate(
+    across(
+      .cols = where(is.factor),
+      .fns = ~replace_na(.,"Other")
+    )
+  ) %>% 
+  group_by(person_id) %>%
+  # filter(person_id == "10070")
+  summarise(cor = cor(as.numeric(Fri),as.numeric(Wed),method = "spearman", use = "complete.obs"))
+# %>% 
+  count(daily_status_imputed)
 ```

### 2023-04-20 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Adding day to day proportions

@@
 # %>% 
-  count(daily_status_imputed)
+  # count(daily_status_imputed)
+```
+
+```{r proportion remote only prep dataframe}
+prep_a <- 
+  cohort_panel %>% 
+  select(person_id,date,date_day_of_week,daily_status_imputed) %>% 
+  mutate(ind = 1) %>% 
+  pivot_wider(names_from = daily_status_imputed, values_from = ind) %>% 
+  clean_names() %>% 
+  select(person_id,date,date_day_of_week,teleworking) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  ) %>% 
+  mutate(
+    date_week_start = floor_date(date,unit = "week")) %>% 
+  select(-date) %>% 
+  pivot_wider(values_from = teleworking,names_from = date_day_of_week) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  ) %>% 
+  clean_names()
+```
+
+```{r proportion remote only function}
+day_to_day_proportions <- function(in_data,in_var)
+{
+  var_string <- rlang::as_name(enquo(in_var))
+
+  # print(person_id)
+
+  out <- 
+    in_data %>% 
+  filter({{in_var}} == 1) %>% 
+  group_by(person_id) %>% 
+  summarise(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~sum(.,na.rm = TRUE)
+  )) %>% 
+  mutate(
+    across(
+      .cols = c(-person_id,-{{in_var}}),
+      .fns = ~./{{in_var}},
+      .names = "{var_string}_{.col}"
+    )
+  ) %>% 
+  ungroup() %>% 
+    select(person_id,starts_with(var_string),-{{in_var}})
+
+  return(out)
+}
+```
+
+```{r proportion remote only function}
+prep_a %>% 
+  day_to_day_proportions(mon)
+
+prep_a %>% 
+  select(thu:fri) %>%
+  names() %>% 
+  #na.omit() %>% 
+  map(~day_to_day_proportions(prep_a,!!sym(.))) %>% 
+  reduce(full_join, by = "person_id")
+
+%>% 
+  group_by(person_id) %>%
+  # filter(person_id == "10070")
+  summarise(cor = cor(Fri,Wed,method = "kendall", use = "complete.obs"))
 ```

### 2023-04-20 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Completing day of week correlations.

--- 2023-04-19 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
@@
 ```
+
 Check: These have the same number of unique `person_id`.
@@
 -   Correlation of work status between days of the week
+
+#### Proportion of days remote by day of the week
 
@@
 ```{r}
-prep_xx <-
+prep_day_of_week <-
   cohort_panel %>%
@@
 
-```{r}
+Review data.
+
+```{r}
+prep_day_of_week %>% 
+  skim()
+```
+
+Now collect only the results for telework.
+
+```{r}
+prep_xx <- 
+  prep_day_of_week %>% 
+  select(person_id,date_day_of_week,daily_status_teleworking_working_prop,daily_status_teleworking_observation_prop) %>% 
+  pivot_longer(cols = starts_with("daily_status")) %>% 
+  mutate(date_day_of_week = str_to_lower(date_day_of_week)) %>% 
+  unite("name",date_day_of_week,name) %>% 
+  pivot_wider(values_from = value, names_from = name) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  )
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
+#### Correlation of work status between days of the week
+
+Three strategies to captured relationships between day are below:
+
+1.  Correlation in telework between days of week
+
+2.  Correlation in status (as an ordered factor) between days of week
+
+3.  Proportion of telework on other days of week, if the employ teleworked on a specific day
+
+##### Correlation in telework between days of week
+
+The script below calculates the correlation in telework between days of the week.
+
+```{r correlation remote only}
+prep_day_of_week_cor_telework <- 
   cohort_panel %>% 
@@
   ) %>% 
+  clean_names() %>% 
   group_by(person_id) %>%
   # filter(person_id == "10070")
-  summarise(cor = cor(Fri,Wed,method = "kendall", use = "complete.obs"))
+  summarise(
+    mon_tue_cor_telework = cor(mon,tue,method = "kendall", use = "complete.obs"),
+    mon_wed_cor_telework = cor(mon,wed,method = "kendall", use = "complete.obs"),
+    mon_thu_cor_telework = cor(mon,thu,method = "kendall", use = "complete.obs"),
+    mon_fri_cor_telework = cor(mon,fri,method = "kendall", use = "complete.obs"),
+    tue_wed_cor_telework = cor(tue,wed,method = "kendall", use = "complete.obs"),
+    tue_thu_cor_telework = cor(tue,thu,method = "kendall", use = "complete.obs"),
+    tue_fri_cor_telework = cor(tue,fri,method = "kendall", use = "complete.obs"),
+    wed_thu_cor_telework = cor(wed,thu,method = "kendall", use = "complete.obs"),
+    wed_fri_cor_telework = cor(wed,fri,method = "kendall", use = "complete.obs"),
+    thu_fri_cor_telework = cor(thu,fri,method = "kendall", use = "complete.obs")
+    ) %>% 
+  ungroup()
+```
+
+Now rename to attach to `prep_building`.
+
+```{r}
+prep_xx <- 
+  prep_day_of_week_cor_telework
 ```
@@
 
-```{r}
-cor(check_in_panel$daily_status_imputed,check_in_panel$date_day_of_week)
+##### Correlation in status between days of week
+
+The script below calculates the correlation between work status.
+
+```{r correlation ordered status}
+prep_day_of_week_cor_status <- 
+  cohort_panel %>% 
+  select(person_id,date,date_day_of_week,daily_status_imputed) %>% 
+  mutate(
+    daily_status_imputed = fct_lump_prop(daily_status_imputed, prop = .1),
+    daily_status_imputed = fct_infreq(daily_status_imputed),
+    daily_status_imputed = factor(daily_status_imputed, ordered = TRUE)
+  )  %>% 
+  mutate(
+    date_week_start = floor_date(date,unit = "week")) %>% 
+  select(-date) %>% 
+  pivot_wider(values_from = daily_status_imputed,names_from = date_day_of_week) %>% 
+  mutate(
+    across(
+      .cols = where(is.factor),
+      .fns = ~replace_na(.,"Other")
+    )
+  ) %>% 
+  clean_names() %>% 
+  group_by(person_id) %>%
+  summarise(
+    mon_tue_cor_status = cor(as.numeric(mon),as.numeric(tue),method = "spearman", use = "complete.obs"),
+    mon_wed_cor_status = cor(as.numeric(mon),as.numeric(wed),method = "spearman", use = "complete.obs"),
+    mon_thu_cor_status = cor(as.numeric(mon),as.numeric(thu),method = "spearman", use = "complete.obs"),
+    mon_fri_cor_status = cor(as.numeric(mon),as.numeric(fri),method = "spearman", use = "complete.obs"),
+    tue_wed_cor_status = cor(as.numeric(tue),as.numeric(wed),method = "spearman", use = "complete.obs"),
+    tue_thu_cor_status = cor(as.numeric(tue),as.numeric(thu),method = "spearman", use = "complete.obs"),
+    tue_fri_cor_status = cor(as.numeric(tue),as.numeric(fri),method = "spearman", use = "complete.obs"),
+    wed_thu_cor_status = cor(as.numeric(wed),as.numeric(thu),method = "spearman", use = "complete.obs"),
+    wed_fri_cor_status = cor(as.numeric(wed),as.numeric(fri),method = "spearman", use = "complete.obs"),
+    thu_fri_cor_status = cor(as.numeric(thu),as.numeric(fri),method = "spearman", use = "complete.obs")
+    ) %>% 
+  ungroup()
+```
+
+Now rename to attach to `prep_building`.
+
+```{r}
+prep_xx <- 
+  prep_day_of_week_cor_status
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
+##### Proportion of telework week day pairs
+
+First, create a dataframe of telework by days of the week.
+
+```{r proportion remote only prep dataframe}
+prep_a <- 
+  cohort_panel %>% 
+  select(person_id,date,date_day_of_week,daily_status_imputed) %>% 
+  mutate(ind = 1) %>% 
+  pivot_wider(names_from = daily_status_imputed, values_from = ind) %>% 
+  clean_names() %>% 
+  select(person_id,date,date_day_of_week,teleworking) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  ) %>% 
+  mutate(
+    date_week_start = floor_date(date,unit = "week")) %>% 
+  select(-date) %>% 
+  pivot_wider(values_from = teleworking,names_from = date_day_of_week) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  ) %>% 
+  clean_names()
+```
+
+Now, a function to calculate the proportion of telework on a different day, if the employee teleworked on a specific day.
+
+```{r proportion remote only function}
+day_to_day_proportions <- function(in_data,in_var)
+{
+  var_string <- rlang::as_name(enquo(in_var))
+
+  # print(person_id)
+
+  out <- 
+    in_data %>% 
+  filter({{in_var}} == 1) %>% 
+  group_by(person_id) %>% 
+  summarise(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~sum(.,na.rm = TRUE)
+  )) %>% 
+  mutate(
+    across(
+      .cols = c(-person_id,-{{in_var}}),
+      .fns = ~./{{in_var}},
+      .names = "{var_string}_{.col}"
+    )
+  ) %>% 
+  ungroup() %>% 
+    select(person_id,starts_with(var_string),-{{in_var}})
+
+  return(out)
+}
+```
+
+Iterated over the days of the week and join results.
+
+```{r proportion remote only function}
+prep_day_of_week_proportion_pairs <- 
+  prep_a %>% 
+  select(thu:fri) %>%
+  names() %>% 
+  map(~day_to_day_proportions(prep_a,!!sym(.))) %>% 
+  reduce(full_join, by = "person_id")
+
+```
+
+Now rename to attach to `prep_building`.
+
+```{r}
+prep_xx <- 
+  prep_day_of_week_proportion_pairs %>% 
+  rename_with(-person_id,
+              .fn = ~glue::glue("{.}_prop_pairs")
+  )
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
 ```

### 2023-04-24 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Developing code to calculate team mode

@@
 
+#### Modal size of team over observation window
+
+Calculate number of team members per day by supervisor email.
+
+```{r}
+prep_a <- 
+  cohort_panel %>% 
+  group_by(date,supervisor_e_mail_address) %>% 
+  summarise(team_size = n_distinct(person_id)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Join to `cohort_panel` only selecting, `person_id`, `date`, and `supervisor_e_mail_address`.
+
+```{r}
+prep_b <- 
+  cohort_panel %>% 
+  select(date,person_id,supervisor_e_mail_address) %>% 
+  left_join(prep_a)
+```
+
+Review data.
+
+```{r}
+prep_b %>% 
+  skim()
+```
+
+#### Proportion of working days co-located with at least one other team member
+#### Proportion of working days co-located with supervisor
+#### Proportion of working days co-located with entire team
+#### Proportion of working days entire team is remote
+
 ```{r}

### 2023-04-24 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Finishing team mode and starting colocation

@@
 
+Calculate the mode team size for each employee.
+
+```{r}
+prep_xx <- 
+  prep_b %>% 
+  group_by(person_id) %>% 
+  summarise(team_size_mode = getmode(team_size)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
 #### Proportion of working days co-located with at least one other team member
+
+```{r}
+prep_a <- 
+  cohort_panel %>% 
+  filter(daily_status_imputed)
+  select
+```
+
 #### Proportion of working days co-located with supervisor

### 2023-04-25 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Completing co-location metrics, starting rule-based groups

@@
 
+Identify employees who report to the site and collect `person_id`, `dates`, `location`, and `supervisor_e_mail_address`.
+
 ```{r}
@@
   cohort_panel %>%
-  filter(daily_status_imputed)
-  select
+  filter(daily_status_imputed == "Reporting to Job Site") %>%
+  select(person_id, date, location, supervisor_e_mail_address) %>%
+  distinct()
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Self left join on `dates`, `location`, and `supervisor_e_mail_address` and filter to rows where the `person_id`s do not match.
+
+```{r}
+prep_b <- 
+  prep_a %>% 
+  left_join(prep_a,
+            by = c("date", "location", "supervisor_e_mail_address"),
+            suffix = c("","_joined")) %>%
+  filter(person_id != person_id_joined)
+```
+
+Review data.
+
+```{r}
+prep_b %>% 
+  skim()
+```
+
+Count dates where co-location occurs by `person_id`.
+
+```{r}
+prep_c <- 
+  prep_b %>% 
+  group_by(person_id) %>% 
+  summarise(days_colocated_1 = n_distinct(date)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_c %>% 
+  skim()
+```
+
+Full join `working_days` from `prep_building`, calculate proportion of co-located days with at least one team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days`.
+
+```{r}
+prep_xx <- 
+  prep_c %>% 
+  full_join(prep_building %>% 
+              select(person_id,working_days)) %>% 
+  mutate(days_colocated_1_working_prop = days_colocated_1/working_days,
+         days_colocated_1_observation_prop = days_colocated_1/observation_window_days) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  ) %>% 
+  select(-working_days)
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
 ```
@@
 #### Proportion of working days co-located with supervisor
+
+Identify employees who report to the site and collect `person_id`, `dates`, `location`, `employee_e_mail_address`, and `supervisor_e_mail_address`.
+
+```{r}
+prep_a <-
+  cohort_panel %>%
+  filter(daily_status_imputed == "Reporting to Job Site") %>%
+  select(person_id, date, location, employee_e_mail_address, supervisor_e_mail_address) %>%
+  distinct()
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Self inner join on `dates`, `location`, and `supervisor_e_mail_address` equal to `employee_e_mail_address` in the right table, and filter to rows where the `person_id`s do not match.
+
+```{r}
+prep_b <- 
+  prep_a %>% 
+  inner_join(prep_a,
+            by = c("date", "location", "supervisor_e_mail_address" = "employee_e_mail_address"),
+            suffix = c("","_joined")) 
+```
+
+Review data.
+
+```{r}
+prep_b %>% 
+  skim()
+```
+
+Count dates where co-location with supervisor occurs by `person_id`.
+
+```{r}
+prep_c <- 
+  prep_b %>% 
+  group_by(person_id) %>% 
+  summarise(days_colocated_supervisor = n_distinct(date)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_c %>% 
+  skim()
+```
+
+Full join `working_days` from `prep_building`, calculate proportion of co-located days with at least one team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days`.
+
+```{r}
+prep_xx <- 
+  prep_c %>% 
+  full_join(prep_building %>% 
+              select(person_id,working_days)) %>% 
+  mutate(days_colocated_supervisor_working_prop = days_colocated_supervisor/working_days,
+         days_colocated_supervisor_observation_prop = days_colocated_supervisor/observation_window_days) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  ) %>% 
+  select(-working_days)
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
 #### Proportion of working days co-located with entire team
+
+Identify employees who report to the site and collect `person_id`, `dates`, `location`, and `supervisor_e_mail_address`.
+
+```{r}
+prep_a <-
+  cohort_panel %>%
+  filter(daily_status_imputed == "Reporting to Job Site") %>%
+  select(person_id, date, location, supervisor_e_mail_address) %>%
+  distinct()
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Self left join on `dates`, `location`, and `supervisor_e_mail_address`.
+
+```{r}
+prep_b <- 
+  prep_a %>% 
+  left_join(prep_a,
+            by = c("date", "location", "supervisor_e_mail_address"),
+            suffix = c("","_joined"))
+```
+
+Review data.
+
+```{r}
+prep_b %>% 
+  skim()
+```
+
+Count number of team members co-located by `person_id` and `date` by counting unique `person_id_joined`.
+
+```{r}
+prep_c <- 
+  prep_b %>% 
+  group_by(person_id,date,supervisor_e_mail_address) %>% 
+  summarise(colocated_team_members = n_distinct(person_id_joined)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_c %>% 
+  skim()
+```
+
+Calculate number of team members per day by supervisor email.
+
+```{r}
+prep_d <- 
+  cohort_panel %>% 
+  group_by(date,supervisor_e_mail_address) %>% 
+  summarise(team_size = n_distinct(person_id)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_d %>% 
+  skim()
+```
+
+Left join co-located team members and teams size, but `date` and `supervisor_e_mail_address`, then filter to when co-located team members is the same size as the team
+
+```{r}
+prep_e <- 
+  prep_c %>% 
+  left_join(prep_d) %>% 
+  filter(colocated_team_members == team_size)
+```
+
+Review data.
+
+```{r}
+prep_e %>% 
+  skim()
+```
+
+Count dates where co-location with whole team occurs by `person_id`.
+
+```{r}
+prep_f <- 
+  prep_e %>% 
+  group_by(person_id) %>% 
+  summarise(days_colocated_team = n_distinct(date)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_f %>% 
+  skim()
+```
+
+Full join `working_days` from `prep_building`, calculate proportion of co-located days with team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days`.
+
+```{r}
+prep_xx <- 
+  prep_f %>% 
+  full_join(prep_building %>% 
+              select(person_id,working_days)) %>% 
+  mutate(days_colocated_team_working_prop = days_colocated_team/working_days,
+         days_colocated_team_observation_prop = days_colocated_team/observation_window_days) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  ) %>% 
+  select(-working_days)
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
 #### Proportion of working days entire team is remote
+
+Identify employees who telework and collect `person_id`, `dates`, `location`, and `supervisor_e_mail_address`.
+
+```{r}
+prep_a <-
+  cohort_panel %>% 
+  filter(daily_status_imputed == "Teleworking") %>%
+  select(person_id, date, location, supervisor_e_mail_address) %>%
+  distinct()
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Self left join on `dates`, `location`, and `supervisor_e_mail_address`.
+
+```{r}
+prep_b <- 
+  prep_a %>% 
+  left_join(prep_a,
+            by = c("date", "location", "supervisor_e_mail_address"),
+            suffix = c("","_joined"))
+```
+
+Review data.
+
+```{r}
+prep_b %>% 
+  skim()
+```
+
+Count number of team members co-located by `person_id` and `date` by counting unique `person_id_joined`.
+
+```{r}
+prep_c <- 
+  prep_b %>% 
+  group_by(person_id,date,supervisor_e_mail_address) %>% 
+  summarise(telework_team_members = n_distinct(person_id_joined)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_c %>% 
+  skim()
+```
+
+Calculate number of team members per day by supervisor email.
+
+```{r}
+prep_d <- 
+  cohort_panel %>% 
+  group_by(date,supervisor_e_mail_address) %>% 
+  summarise(team_size = n_distinct(person_id)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_d %>% 
+  skim()
+```
+
+Left join telework team members and teams size, but `date` and `supervisor_e_mail_address`, then filter to when telework team members is the same size as the team
+
+```{r}
+prep_e <- 
+  prep_c %>% 
+  left_join(prep_d) %>% 
+  filter(telework_team_members == team_size)
+```
+
+Review data.
+
+```{r}
+prep_e %>% 
+  skim()
+```
+
+Count dates where telework with whole team occurs by `person_id`.
+
+```{r}
+prep_f <- 
+  prep_e %>% 
+  group_by(person_id) %>% 
+  summarise(days_telework_team = n_distinct(date)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_f %>% 
+  skim()
+```
+
+Full join `working_days` from `prep_building`, calculate proportion of telework days with team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days`.
+
+```{r}
+prep_xx <- 
+  prep_f %>% 
+  full_join(prep_building %>% 
+              select(person_id,working_days)) %>% 
+  mutate(days_telework_team_working_prop = days_telework_team/working_days,
+         days_telework_team_observation_prop = days_telework_team/observation_window_days) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  ) %>% 
+  select(-working_days)
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
+## Define rule-based groups
+
+The analysis plan defines nine rule-based groups for analysis:
+
+1.  **All remote** - A policy definition for staff that are 100% remote
+2.  **Teleworker** - A policy definition for staff that require two days
+    per pay period onsite.
+3.  **Onsite Flexible** - Defined by `position_category_description` in
+    the roster data
+4.  **Offsite** - Defined by `position_category_description` in the
+    roster data
+5.  **Onsite Required** - Defined by `position_category_description` in
+    the roster data
+6.  **Primarily remote** - Employees who work remotely above the 95th
+    percentile <!-- could be 75th -->
+7.  **Mostly remote** - Employees who work remotely between the median
+    and the 95th percentile <!-- could be 75th -->
+8.  **Mostly onsite** - Employees who work remotely between 5th
+    percentile and the median <!-- could be 25th -->
+9.  **Primarily onsite** - Employees who work remotely below the 5th
+    percentile <!-- could be 75th -->
+
+Below the variables for the groups are created.
+
+### All remote
+
+Define workers with 100% of their time as **all remote**.
+
+```{r}
+prep_xx <- 
+  prep_building %>% 
+  mutate(
+    rule_based_all_remote = case_when(
+      daily_status_teleworking_working_prop == 1 ~ 1,
+                                      TRUE ~ 0)
+  ) %>% 
+  select(person_id,starts_with("rule_based_"))
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+### Teleworker
+
+First define pay periods based on this: https://www.gsa.gov/cdnstatic/GSA_Payroll_Calendar_2022_Revised.pdf. File is also saved in `r file.path(params$google_drive_home,"04. Analysis","documents")`.
+
+```{r}
+prep_a <- 
+  tibble(
+  date = seq.Date(from = ymd("2022-01-01"),
+         to = ymd("2022-12-31"),
+         by = "2 weeks")
+) %>% 
+  rownames_to_column(var = "period_number") 
+# %>% 
+#   mutate(
+#     date_pay_period_start_lead = lead(date_pay_period_start)
+  # )
+```
+
+```{r}
+prep_b <- 
+  tibble(
+  date = seq.Date(from = ymd("2022-01-01"),
+         to = ymd("2022-12-31"),
+         by = "days")
+)
+```
+
+```{r}
+prep_c <- 
+  prep_b %>% 
+  left_join(prep_a) %>% 
+  fill(period_number, .direction = "down")
+```
+
+```{r}
+prep_d <- 
+  cohort_panel %>% 
+  select(person_id,date, daily_status_imputed) %>% 
+  left_join(prep_c)
+```
+
+```{r}
+prep_e <- 
+      prep_d %>% 
+  group_by(person_id,daily_status_imputed,period_number) %>% 
+  summarise(days = n_distinct(date)) %>% 
+  ungroup()
+```
+
+#CONTINUE FROM HERE
+
+```{r}
+prep_e %>% 
+  filter(daily_status_imputed == "Reporting to Job Site") %>% 
+  mutate(
+    telework_onsite_minimum = case_when(days >= 2 ~ 1,
+                                        TRUE ~ 0)
+  ) %>% 
+  group_by(person_id) %>% 
+  summarise(
+    telework_onsite_minimum = mean(telework_onsite_minimum)
+  )
+```
+
+### Primarily, mostly onsite and remote
+
+First, calculate the quantiles for probabilities 0.50 and 0.95.
+
+```{r}
+prep_a <- 
+  prep_building %>% 
+  summarise(
+    across(
+      .cols = c(daily_status_reporting_to_job_site_working_prop,daily_status_teleworking_working_prop,
+                daily_status_reporting_to_job_site_observation_prop,daily_status_teleworking_observation_prop),
+      .fns = list(q_95 = ~quantile(.,probs = .95),
+                  q_50 = ~quantile(.,probs = .50))
+    )
+  )
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Use the quantiles above to create new variables for `primarily_` and `mostly_` working remote or onsite.
+
+```{r}
+prep_xx <-
+  prep_building %>%
+  select(
+    person_id,
+    daily_status_reporting_to_job_site_working_prop,
+    daily_status_teleworking_working_prop,
+    daily_status_reporting_to_job_site_observation_prop,
+    daily_status_teleworking_observation_prop
+  ) %>%
+  mutate(
+    rule_based_primarily_reporting_to_job_site_working =
+      case_when(
+        daily_status_reporting_to_job_site_working_prop >= prep_a$daily_status_reporting_to_job_site_working_prop_q_95 ~ 1,
+        TRUE ~ 0
+      ),
+    rule_based_primarily_teleworking_working =
+      case_when(
+        daily_status_teleworking_working_prop >= prep_a$daily_status_teleworking_working_prop_q_95 ~ 1,
+        TRUE ~ 0
+      ),
+    rule_based_primarily_reporting_to_job_site_observation =
+      case_when(
+        daily_status_reporting_to_job_site_observation_prop >= prep_a$daily_status_reporting_to_job_site_observation_prop_q_95 ~ 1,
+        TRUE ~ 0
+      ),
+    rule_based_primarily_teleworking_observation =
+      case_when(
+        daily_status_teleworking_observation_prop >= prep_a$daily_status_teleworking_observation_prop_q_95 ~ 1,
+        TRUE ~ 0
+      ),
+    rule_based_mostly_reporting_to_job_site_working =
+      case_when(
+        daily_status_reporting_to_job_site_working_prop >= prep_a$daily_status_reporting_to_job_site_working_prop_q_50 ~ 1,
+        TRUE ~ 0
+      ),
+    rule_based_mostly_teleworking_working =
+      case_when(
+        daily_status_teleworking_working_prop >= prep_a$daily_status_teleworking_working_prop_q_50 ~ 1,
+        TRUE ~ 0
+      ),
+    rule_based_mostly_reporting_to_job_site_observation =
+      case_when(
+        daily_status_reporting_to_job_site_observation_prop >= prep_a$daily_status_reporting_to_job_site_observation_prop_q_50 ~ 1,
+        TRUE ~ 0
+      ),
+    rule_based_mostly_teleworking_observation =
+      case_when(
+        daily_status_teleworking_observation_prop >= prep_a$daily_status_teleworking_observation_prop_q_50 ~ 1,
+        TRUE ~ 0
+      ),
+  ) %>%
+  select(person_id, starts_with("rule_based_"))
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
+#CONTINUE FROM HERE
 

### 2023-04-27 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Adding notes, working more on onsite minimum

@@
   rownames_to_column(var = "period_number") 
-# %>% 
-#   mutate(
-#     date_pay_period_start_lead = lead(date_pay_period_start)
-  # )
-```
+```
+
+Second, create a dataframe of all the days of the year.
 
@@
 
+Third, left join the pay periods dataframe (`prep_a`) to the days of the year (`prep_b`), then fill the null `period_number` values with the entry above.
 ```{r}
@@
 
-#CONTINUE FROM HERE
-
-```{r}
+```{r}
+prep_f <- 
   prep_e %>% 
@@
   summarise(
-    telework_onsite_minimum = mean(telework_onsite_minimum)
-  )
-```
+    telework_onsite_minimum_mean = mean(telework_onsite_minimum)
+  ) %>% 
+  ungroup() %>% 
+  mutate(
+    telework_onsite_minimum = case_when(telework_onsite_minimum_mean == 1 ~ 1,
+                                        TRUE ~ 0)
+  )
+```
+
+#CONTINUE FROM HERE
 
@@
 
+### Position description categories
+
+```{r}
+prep_a <- 
+  cohort_first %>% 
+  select(person_id,position_category_description) %>% 
+  character_to_indicator(in_unique_identifier = person_id,
+                         position_category_description,
+                         in_prefix = "rules_based_position_category_")
+```
+
 #CONTINUE FROM HERE

### 2023-05-04 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Clarifying what descriptive values will be used.
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Updating the Teleworker rule-based category to Routine teleworker based on HR documentation

@@
 1.  **All remote** - A policy definition for staff that are 100% remote
-2.  **Teleworker** - A policy definition for staff that require two days
-    per pay period onsite.
+2.  **Routine teleworker** - Employees with
+    `position_category_description`'s *Onsite Flexible* or *Offsite*
+    that work at least two two days per pay period onsite.[^1]
 3.  **Onsite Flexible** - Defined by `position_category_description` in
@@
 
+[^1]: See [Position Categorization Supervisor Discussion
+    Guides](https://docs.google.com/presentation/d/1nyAh7SuaTXphJlheMTkEUjV0cNYmqiJdWv8TmyNQrJ0/edit#slide=id.gb82d1263be_0_0).
+
 Teams will be categorized similarly:
@@
 1.  **All remote** - All team members are100% remote
-2.  **Teleworker** - All team members work two days per pay period
-    onsite.
+2.  **Routine teleworker** - All team members have
+    `position_category_description`'s *Onsite Flexible* or *Offsite* and
+    work at least two two days per pay period onsite.
 3.  **Onsite Flexible** - All team members are *Onsite Flexible* as
@@
     then divided by the standard deviation, using the `scale()`
-    function[^1]
+    function[^2]
 
@@
 
-[^1]: [Documentation for the scale
+[^2]: [Documentation for the scale
     function.](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/scale)
@@
 data by those groups. Lastly, difference in k-means cluster by work
-patterns and descriptive data.
+patterns and descriptive data. The initial condition of descriptive
+variables will be used to calculate the statistics. That is, the values
+of these variables for employees and teams at the beginning of the
+observation window: March 2022.
 

### 2023-05-04 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Updating Teleworker rule-based category to Routine teleworker based on HR documentation and then reorders the rule-based categories.

@@
 1.  **All remote** - A policy definition for staff that are 100% remote
-2.  **Teleworker** - A policy definition for staff that require two days
+2.  **Routine teleworker** - Employees with position_category_description's *Onsite Flexible* or *Offsite* that work at least two two days per pay period onsite.
     per pay period onsite.
@@
 ```
-### Teleworker
-
-First define pay periods based on this: https://www.gsa.gov/cdnstatic/GSA_Payroll_Calendar_2022_Revised.pdf. File is also saved in `r file.path(params$google_drive_home,"04. Analysis","documents")`.
-
-```{r}
-prep_a <- 
-  tibble(
-  date = seq.Date(from = ymd("2022-01-01"),
-         to = ymd("2022-12-31"),
-         by = "2 weeks")
-) %>% 
-  rownames_to_column(var = "period_number") 
-```
-
-Second, create a dataframe of all the days of the year.
-
-```{r}
-prep_b <- 
-  tibble(
-  date = seq.Date(from = ymd("2022-01-01"),
-         to = ymd("2022-12-31"),
-         by = "days")
-)
-```
-
-Third, left join the pay periods dataframe (`prep_a`) to the days of the year (`prep_b`), then fill the null `period_number` values with the entry above.
-```{r}
-prep_c <- 
-  prep_b %>% 
-  left_join(prep_a) %>% 
-  fill(period_number, .direction = "down")
-```
-
-```{r}
-prep_d <- 
-  cohort_panel %>% 
-  select(person_id,date, daily_status_imputed) %>% 
-  left_join(prep_c)
-```
-
-```{r}
-prep_e <- 
-      prep_d %>% 
-  group_by(person_id,daily_status_imputed,period_number) %>% 
-  summarise(days = n_distinct(date)) %>% 
-  ungroup()
-```
-
-```{r}
-prep_f <- 
-  prep_e %>% 
-  filter(daily_status_imputed == "Reporting to Job Site") %>% 
-  mutate(
-    telework_onsite_minimum = case_when(days >= 2 ~ 1,
-                                        TRUE ~ 0)
-  ) %>% 
-  group_by(person_id) %>% 
-  summarise(
-    telework_onsite_minimum_mean = mean(telework_onsite_minimum)
-  ) %>% 
-  ungroup() %>% 
-  mutate(
-    telework_onsite_minimum = case_when(telework_onsite_minimum_mean == 1 ~ 1,
-                                        TRUE ~ 0)
-  )
-```
-
-#CONTINUE FROM HERE
 
@@
 
-```{r}
-prep_a <- 
+```{r, eval=FALSE}
+prep_b <- 
+  cohort_panel %>% 
+  group_by(person_id) %>% 
+  summarise(
+    across(
+      .cols = position_category_description,
+      .fns = getmode
+    )
+  )
+
+prep_c <- 
+  cohort_first %>% 
+  select(person_id,position_category_description)
+
+prep_c %>% 
+  inner_join(prep_a, by = "person_id") %>% 
+  filter(position_category_description.x != position_category_description.y)
+```
+
+Identify the `position_category_description` at the beginning of the observation window and convert the categories into indicators.
+
+```{r}
+prep_xx <- 
   cohort_first %>% 
   select(person_id,position_category_description) %>% 
-  character_to_indicator(in_unique_identifier = person_id,
+  character_to_indicator(in_unique_identifier = "person_id",
                          position_category_description,
@@
 ```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
+### Teleworker
+
+First define pay periods based on this: https://www.gsa.gov/cdnstatic/GSA_Payroll_Calendar_2022_Revised.pdf. File is also saved in `r file.path(params$google_drive_home,"04. Analysis","documents")`.
+
+```{r}
+prep_a <- 
+  tibble(
+  date = seq.Date(from = ymd("2022-01-01"),
+         to = ymd("2022-12-31"),
+         by = "2 weeks")
+) %>% 
+  rownames_to_column(var = "period_number") 
+```
+
+Second, create a dataframe of all the days of the year.
+
+```{r}
+prep_b <- 
+  tibble(
+  date = seq.Date(from = ymd("2022-01-01"),
+         to = ymd("2022-12-31"),
+         by = "days")
+)
+```
+
+Third, left join the pay periods dataframe (`prep_a`) to the days of the year (`prep_b`), then fill the null `period_number` values with the entry above.
+
+```{r}
+prep_c <- 
+  prep_b %>% 
+  left_join(prep_a) %>% 
+  fill(period_number, .direction = "down")
+```
+
+Fourth, take the cohort panel (`cohort_panel`) select `person_id`, `date`, and `daily_status_imputed` and left join to calendar dataframe with filled `period_number` (`prep_c`) on `date`.
+
+```{r}
+prep_d <- 
+  cohort_panel %>% 
+  select(person_id,date, daily_status_imputed) %>% 
+  left_join(prep_c)
+```
+
+```{r}
+prep_e <- 
+      prep_d %>% 
+  group_by(person_id,daily_status_imputed,period_number) %>% 
+  summarise(days = n_distinct(date)) %>% 
+  ungroup()
+```
+
+```{r}
+prep_f <- 
+  prep_e %>% 
+  filter(daily_status_imputed == "Reporting to Job Site") %>% 
+  mutate(
+    telework_onsite_minimum = case_when(days >= 2 ~ 1,
+                                        TRUE ~ 0)
+  ) %>% 
+  group_by(person_id) %>% 
+  summarise(
+    telework_onsite_minimum_mean = mean(telework_onsite_minimum)
+  ) %>% 
+  ungroup() %>% 
+  mutate(
+    telework_onsite_minimum = case_when(telework_onsite_minimum_mean == 1 ~ 1,
+                                        TRUE ~ 0)
+  )
+```
+
+#CONTINUE FROM HERE
 

### 2023-05-11 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Completing rule based categories and saving data.

@@
 
-## Creating cohort
+## Creating cohort {.tabset .tabset-pills}
 
@@
 
-## Creating aggregated variables
+## Creating aggregated variables {.tabset .tabset-pills}
 
@@
 
-```{r proportion remote only function}
+```{r}
 day_to_day_proportions <- function(in_data,in_var)
@@
 
-```{r proportion remote only function}
+```{r}
 prep_day_of_week_proportion_pairs <- 
@@
 
-## Define rule-based groups
+## Define rule-based groups {.tabset .tabset-pills}
 
@@
                          position_category_description,
-                         in_prefix = "rules_based_position_category_")
+                         in_prefix = "rule_based_position_category_")
 ```
@@
 
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
 Second, create a dataframe of all the days of the year.
@@
 
+Review data.
+
+```{r}
+prep_b %>% 
+  skim()
+```
+
 Third, left join the pay periods dataframe (`prep_a`) to the days of the year (`prep_b`), then fill the null `period_number` values with the entry above.
@@
 ```
+Review data.
+
+```{r}
+prep_c %>% 
+  skim()
+```
 
@@
 ```
+
+Review data.
+
+```{r}
+prep_d %>% 
+  skim()
+```
+
+Fifth, count the number of unique days by `person_id`, `daily_status_imputed`, and `period_number`.
 
@@
 
+Review data.
+
+```{r}
+prep_e %>% 
+  skim()
+```
+
+Sixth, filter to only see observations where `daily_status_imputed` is "Reporting to Job Site" and create `telework_onsite_minimum` to be 1 when `days` is greater than or equal to 2, that is employees have at least two days in the office in that pay period.
+Then, calculate the mean `telework_onsite_minimum` (`telework_onsite_minimum_mean`) per employee.
+Those where this is 1 are in the office at least two days per pay period for the whole observation window.
+Lastly, create `telework_onsite_minimum` to be 1 when `telework_onsite_minimum_mean` is 1.
+
 ```{r}
@@
 
-#CONTINUE FROM HERE
-
-#CONTINUE FROM HERE
-
-```{r}
-prep_xx %>% 
-  pivot_longer(-person_id) %>% 
-  filter(str_detect(name, "_prop")) %>% 
-  ggplot(aes(x = value)) +
-  geom_histogram() +
-  facet_wrap(facets = vars(name))
-```
-
--   Modal size of team over observation window
-
--   Proportion of working days co-located with at least one other team member
-
--   Proportion of working days co-located with supervisor
-
--   Proportion of working days co-located with entire team
-
--   Proportion of working days entire team is remote
-
-Count number of unique employee_name.
-
-```{r}
-unique_name_base <- prep_base_1 %>% summarise(n_distinct(employee_name)) %>% pull()
-unique_name_base
-```
-
-```{r}
-prep_base_1_names <- names(prep_base_1)
-```
-
-Load all data files in the `r params$data_folder_2` data folder.
-
-```{r}
-prep_base_2 <- files_2 %>% 
-  map_dfr(~mutate(.data = read_xlsx(path = ., 
-                                    col_types = c("date", "text", "text", 
-        "text", "text", "text", "text", "text", 
-        "text", "date", "text", "text", "text", 
-        "text", "text", "text", "text", "text", 
-        "text", "text", "text", "text", "text", 
-        "text", "text", "text", "text", "text")), 
-        file_name = str_remove(.,pattern = file.path(params$google_drive_home,"03. Data Collection"))
-      )) %>% 
-  clean_names() %>% 
-  distinct() %>% 
-  mutate(
-    across(
-      .cols = where(is.POSIXct),
-      .fns = ~as_date(.)
-    )
-  )
-```
-
-Review.
-
-```{r}
-prep_base_2 %>% 
-  skim()
-```
-
-Count number of unique email addresses.
-
-```{r}
-unique_email_base <- prep_base_2 %>% summarise(n_distinct(employee_e_mail_address)) %>% pull()
-unique_email_base
-```
-
-## Joining data
-
-### Join 1
-
-First inner join by employee name, supervisor name, department id, and the last date, using the last day of the month before the daily checkin.
-
-```{r}
-prep_xx <- prep_base_1 %>% 
-  inner_join(prep_base_2,
-            by =  c("employee_name" = "full_name",
-                    "supervisor_display_name" = "supervisor_display_name",
-                    "dept_id" = "department_id",
-                    "date_month_rollback" = "snapshot_date"
-                    ),
-            suffix = c("_daily","_roster")
-  ) %>% 
-  select(-starts_with("file_name")) %>% 
-  distinct()
-```
-
-Review.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-```{r}
-prep_xx %>%
-  get_dupes(date,employee_e_mail_address) %>%
-  arrange(desc(dupe_count)) %>% 
-  datatable_with_sampling(in_max_rows = 5000)
-```
-
-Create building dataframe.
-
-```{r}
-prep_building <- prep_xx
-```
-
-Count unique email addresses in building dataframe.
-
-```{r}
-unique_email_building <- prep_building %>% summarise(n_distinct(employee_e_mail_address)) %>% pull()
-unique_email_building
-```
-
-Test: This does not differ from the base.
-
-```{r}
-unique_email_base == unique_email_building
-```
-
-Review.
-
-```{r}
-prep_building %>%  skim()
-```
-
-### Join 2
-
-Second, remove data from building dataframe, then inner join by employee name, supervisor name, department id, and the last date, using the last day of the month after the daily checkin.
+Review data.
+
+```{r}
+prep_f %>% 
+  skim()
+```
+
+Seventh, select `person_id`, and `position_category_description` from the beginning of the observation window (`cohort_first`) and left join the above (`prep_f`).
+Then, create `rule_based_telework_onsite_minimum` when `telework_onsite_minimum` is 1 and `position_category_description` is *Onsite Flexible* or *Offsite*.
 
@@
 prep_xx <- 
-  prep_base_1 %>% 
-  anti_join(prep_building) %>% 
-  inner_join(prep_base_2,
-            by =  c("employee_name" = "full_name",
-                    "supervisor_display_name" = "supervisor_display_name",
-                    "dept_id" = "department_id",
-                    "date_month_forward" = "snapshot_date"
-                    ),
-            suffix = c("_daily","_roster")
-  ) %>% 
-  select(-starts_with("file_name")) %>% 
-  distinct()
-```
-
-Review.
-
-```{r}
-prep_xx %>%  skim()
-```
-
-```{r}
-prep_xx %>%
-  get_dupes(date,employee_e_mail_address) %>%
-  arrange(desc(dupe_count)) %>% 
-  datatable_with_sampling(in_max_rows = 5000)
-```
-
-Bind to buidling dataframe.
-
-```{r}
-prep_building <- prep_building %>% 
-  bind_rows(prep_xx) %>% 
-  distinct()
-```
-
-Count unique email addresses
-
-```{r}
-unique_email_building <- prep_building %>% summarise(n_distinct(employee_e_mail_address)) %>% pull()
-unique_email_building
-```
-
-Test: This does not differ from the base.
-
-```{r}
-unique_email_base == unique_email_building
-```
-
-Review.
-
-```{r}
-prep_building %>%  skim()
-```
-
-### Create unique person id
-
-```{r}
-prep_unique_id <- 
-  prep_building %>% 
-  select(employee_name,employee_e_mail_address) %>% 
-  distinct() %>% 
-  rownames_to_column(var = "person_id")
-```
-
-Review.
-
-```{r}
-prep_unique_id %>% 
-  skim()
-```
-
-### Join to building dataframe
+  cohort_first %>% 
+  select(person_id,position_category_description) %>% 
+  left_join(prep_f) %>% 
+  mutate(
+    rule_based_telework_onsite_minimum = 
+      case_when(telework_onsite_minimum == 1 & position_category_description == "Onsite Flexible" ~ 1,
+                telework_onsite_minimum == 1 & position_category_description == "Offsite" ~ 1,
+                TRUE ~ 0)
+  ) %>%
+  select(person_id, starts_with("rule_based_"))
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
 
@@
   prep_building %>% 
-  left_join(prep_unique_id) %>% 
-  select(person_id,everything())
-```
-
-Review.
-
-```{r}
-prep_building %>% 
-  skim()
-```
-
-Check for duplicates on `person_id` and `date`.
-
-```{r}
-prep_building %>% 
-  get_dupes(person_id,date) %>% 
-  datatable_with_sampling(in_max_rows = 5000)
-```
-
-## Compare to original dataframes
-
-```{r}
-prep_base_1_summary <- 
-  prep_base_1 %>% 
-  unite(employee_name_date,employee_name,date,remove = FALSE) %>% 
-  summarise(
-    rows = n(),
-    employee_name = n_distinct(employee_name),
-    employee_name_date = n_distinct(employee_name_date),
-  ) %>% 
-  mutate(dataframe = "prep_base_1")
-```
-
-```{r}
-prep_base_2_summary <- 
-  prep_base_2 %>% 
-  # unite(employee_name_date,employee_name,date,remove = FALSE) %>% 
-  summarise(
-    rows = n(),
-    employee_name = n_distinct(full_name),
-    employee_e_mail_address = n_distinct(employee_e_mail_address)
-  ) %>% 
-  mutate(dataframe = "prep_base_2")
-```
-
-```{r}
-prep_building_summary <- 
-  prep_building %>% 
-  unite(employee_name_date,employee_name,date,remove = FALSE) %>%
-  summarise(
-    rows = n(),
-    person_id = n_distinct(person_id),
-    employee_name = n_distinct(employee_name),
-    employee_e_mail_address = n_distinct(employee_e_mail_address),
-    employee_name_date = n_distinct(employee_name_date),
-  ) %>% 
-  mutate(dataframe = "prep_building")
-```
-
-```{r}
-prep_summary <- 
-  prep_base_1_summary %>% 
-  bind_rows(prep_base_2_summary) %>% 
-  bind_rows(prep_building_summary) %>% 
-  pivot_longer(-dataframe) %>% 
-  pivot_wider(names_from = dataframe,values_from = value)
-```
-
-```{r}
-prep_summary %>% 
-  flextable() %>% 
-  theme_zebra() %>% 
-  autofit()
-```
-
-```{r}
-prep_base_1_rows <- prep_summary %>% filter(name == 'rows') %>% pull(prep_base_1)
-
-prep_base_1_employee_name <- prep_summary %>% filter(name == 'employee_name') %>% pull(prep_base_1)
-
-diff_rows_count <- 
-  (prep_base_1_rows) -
-  (prep_summary %>% filter(name == 'rows') %>% pull(prep_building))
-
-diff_rows_prop <- 
-  diff_rows_count/prep_base_1_rows
-
-diff_employee_name_count <- 
-  (prep_base_1_employee_name) -
-  (prep_summary %>% filter(name == 'employee_name') %>% pull(prep_building))
-
-diff_employee_name_prop <- 
-  diff_employee_name_count/prep_base_1_employee_name
-```
-
-From this table, we find:
-
-1.  A loss of `r scales::comma(diff_rows_count)` rows between `prep_1_base` and `prep_building`, about `r scales::percent(diff_rows_prop)`
-2.  A loss of `r scales::comma(diff_employee_name_count)` rows between `prep_1_base` and `prep_building`, about `r scales::percent(diff_employee_name_prop)`
-
-These losses of data are reasonable.
-
-Create a unique dataframe of just `date` and `person_id`.
-
-```{r}
-prep_uniq <- 
-  prep_building %>% 
-  select(date,person_id)
+  left_join(prep_xx)
+```
+
+## Attach characteristics
+
+Define `cohort_first` as `prep_xx`.
+
+```{r}
+prep_xx <- cohort_first
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
 ```
@@
 
-Grouping variables.
-
-```{r}
-problem_variables <- 
-  problem_variables %>% 
-  mutate(group = 
-           case_when(variable == "position_category_code" ~ "position_category_code",
-                     variable == "position_category_description" ~ "position_category_code",
-                     TRUE ~ variable
-                     ))
-
-problem_variables
-```
-
-Create list of groups.
-
-```{r}
-problem_groups <- 
-  problem_variables %>% 
-  select(group) %>% 
-  distinct() %>% 
-  arrange(group) %>% 
-  pull()
-
-problem_groups
-```
-
-Also create a building dataframe to add other dataframes where missing have been removed.
-
-```{r}
-prep_problem <- prep_uniq
-```
-
-### Problems removal
-
-```{r}
-step_n <- 0
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`: `business_line_2_letter_department_id`
-
-Removing blanks produced by
-
-```{r}
-problem_variable <- 
-  problem_variables %>% 
-  filter(group == problem_groups[step_n])
-
-problem_variable
-```
-
-Reviewing blanks.
-
-```{r}
-nulls_01 <- 
-  prep_building %>% 
-  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
-  select(all_of(problem_variable %>% pull(variable)),everything())
-
-nulls_01
-```
-
-Let's count the extent of the issues.
-
-```{r}
-problem_variable %>% 
-  pull(variable) %>% 
-  map(
-    ~nulls_01 %>% 
-  count(!!sym(.x)) %>% 
-  arrange(desc(n)) %>% 
-    filter(is.na(!!sym(.x)))
-  )
-```
-
-Let's count the entries here.
-
-```{r}
-prep_building %>% 
-  group_by(across(all_of(problem_variable %>% pull(variable)))) %>% 
-  count() %>% 
-  arrange(desc(n))
-```
-
-Lot's of entries.
-
-Check relationship with time.
-
-```{r}
-prep_building %>% 
-  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
-  group_by(across(all_of(problem_variable %>% pull(variable))),date) %>% 
-  count() %>% 
-  ggplot(aes(x = date, y = n)) +
-  geom_point() +
-  geom_smooth()
-```
-
-Increase in July.
-
-Is this an important variable?
-
-No. We'll replace nulls with "(Missing)".
-
-```{r}
-prep_xx <- 
-  prep_building %>% 
-  select(date, person_id,all_of(problem_variable %>% pull(variable))) %>% 
-  distinct() %>% 
-  mutate(
-    across(
-      .cols = all_of(problem_variable %>% pull(variable)),
-      .fns = ~case_when(is.na(.) ~ "(Missing)",
-                        TRUE ~ .)
-    )
-  )
-
-prep_xx %>% skim()
-```
-
-Join to building dataframe.
-
-```{r}
-prep_problem <- prep_problem %>% 
-  left_join(prep_xx)
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`: `employee_e_mail_address`
-
-Removing problems produced by
-
-```{r}
-problem_variable <- 
-  problem_variables %>% 
-  filter(group == problem_groups[step_n])
-
-problem_variable
-```
-
-Reviewing blanks.
-
-```{r}
-nulls_01 <- 
-  prep_building %>% 
-  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
-  select(all_of(problem_variable %>% pull(variable)),everything())
-
-nulls_01
-```
-
-Let's count the extent of the issues.
-
-```{r}
-problem_variable %>% 
-  pull(variable) %>% 
-  map(
-    ~nulls_01 %>% 
-  count(!!sym(.x)) %>% 
-  arrange(desc(n)) %>% 
-    filter(is.na(!!sym(.x)))
-  )
-```
-
-Let's count the entries here.
-
-```{r}
-prep_building %>% 
-  group_by(across(all_of(problem_variable %>% pull(variable)))) %>% 
-  count() %>% 
-  arrange(desc(n))
-```
-
-Lot's of entries.
-
-Check relationship with time.
-
-```{r}
-prep_building %>% 
-  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
-  group_by(across(all_of(problem_variable %>% pull(variable))),date) %>% 
-  count() %>% 
-  ggplot(aes(x = date, y = n)) +
-  geom_jitter() +
-  geom_smooth() +
-  theme_fivethirtyeight()
-```
-
-Looks pretty random.
-
-Is this an important variable?
-
-Yes, but we won't be using it directly in the analysis. We'll replace nulls with "(Missing)".
-
-```{r}
-prep_xx <- 
-  prep_building %>% 
-  select(date, person_id,all_of(problem_variable %>% pull(variable))) %>% 
-  distinct() %>% 
-  mutate(
-    across(
-      .cols = all_of(problem_variable %>% pull(variable)),
-      .fns = ~case_when(is.na(.) ~ "(Missing)",
-                        TRUE ~ .)
-    )
-  )
-
-prep_xx %>% skim()
-```
-
-Join to building dataframe.
-
-```{r}
-prep_problem <- prep_problem %>% 
-  left_join(prep_xx)
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`: `location_city`
-
-Removing problems produced by
-
-```{r}
-problem_variable <- 
-  problem_variables %>% 
-  filter(group == problem_groups[step_n])
-
-problem_variable
-```
-
-Reviewing blanks.
-
-```{r}
-nulls_01 <- 
-  prep_building %>% 
-  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
-  select(all_of(problem_variable %>% pull(variable)),everything())
-
-nulls_01
-```
-
-Let's count the extent of the issues.
-
-```{r}
-problem_variable %>% 
-  pull(variable) %>% 
-  map(
-    ~nulls_01 %>% 
-  count(!!sym(.x)) %>% 
-  arrange(desc(n)) %>% 
-    filter(is.na(!!sym(.x)))
-  )
-```
-
-Let's count the entries here.
-
-```{r}
-prep_building %>% 
-  group_by(across(all_of(problem_variable %>% pull(variable)))) %>% 
-  count() %>% 
-  arrange(desc(n))
-```
-
-Lot's of entries.
-
-Check relationship with time.
-
-```{r}
-prep_building %>% 
-  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
-  group_by(across(all_of(problem_variable %>% pull(variable))),date) %>% 
-  count() %>% 
-  ggplot(aes(x = date, y = n)) +
-  geom_jitter() +
-  geom_smooth() +
-  theme_fivethirtyeight()
-```
-
-Weird that early in the year is low, then gets steady later.
-
-Is this an important variable?
-
-Yes, but we have other location variables to rely on. We'll replace nulls with "(Missing)".
-
-```{r}
-prep_xx <- 
-  prep_building %>% 
-  select(date, person_id,all_of(problem_variable %>% pull(variable))) %>% 
-  distinct() %>% 
-  mutate(
-    across(
-      .cols = all_of(problem_variable %>% pull(variable)),
-      .fns = ~case_when(is.na(.) ~ "(Missing)",
-                        TRUE ~ .)
-    )
-  )
-
-prep_xx %>% skim()
-```
-
-Join to building dataframe.
-
-```{r}
-prep_problem <- prep_problem %>% 
-  left_join(prep_xx)
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`: `location_state`
-
-Removing problems produced by
-
-```{r}
-problem_variable <- 
-  problem_variables %>% 
-  filter(group == problem_groups[step_n])
-
-problem_variable
-```
-
-Reviewing blanks.
-
-```{r}
-nulls_01 <- 
-  prep_building %>% 
-  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
-  select(all_of(problem_variable %>% pull(variable)),everything())
-
-nulls_01
-```
-
-Let's count the extent of the issues.
-
-```{r}
-problem_variable %>% 
-  pull(variable) %>% 
-  map(
-    ~nulls_01 %>% 
-  count(!!sym(.x)) %>% 
-  arrange(desc(n)) %>% 
-    filter(is.na(!!sym(.x)))
-  )
-```
-
-Let's count the entries here.
-
-```{r}
-prep_building %>% 
-  group_by(across(all_of(problem_variable %>% pull(variable)))) %>% 
-  count() %>% 
-  arrange(desc(n))
-```
-
-Lot's of entries.
-
-Check relationship with time.
-
-```{r}
-prep_building %>% 
-  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
-  group_by(across(all_of(problem_variable %>% pull(variable))),date) %>% 
-  count() %>% 
-  ggplot(aes(x = date, y = n)) +
-  geom_jitter() +
-  geom_smooth() +
-  theme_fivethirtyeight()
-```
-
-Looks pretty random, and low numbers.
-
-Is this an important variable?
-
-Yes, but we have other location variables to rely on. It appears from above that these are international locations. We'll replace nulls with "(International)".
-
-```{r}
-prep_xx <- 
-  prep_building %>% 
-  select(date, person_id,all_of(problem_variable %>% pull(variable))) %>% 
-  distinct() %>% 
-  mutate(
-    across(
-      .cols = all_of(problem_variable %>% pull(variable)),
-      .fns = ~case_when(is.na(.) ~ "(International)",
-                        TRUE ~ .)
-    )
-  )
-
-prep_xx %>% skim()
-```
-
-Join to building dataframe.
-
-```{r}
-prep_problem <- prep_problem %>% 
-  left_join(prep_xx)
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`: `position_category_code`
-
-Removing problems produced by
-
-```{r}
-problem_variable <- 
-  problem_variables %>% 
-  filter(group == problem_groups[step_n])
-
-problem_variable
-```
-
-Reviewing blanks.
-
-```{r}
-nulls_01 <- 
-  prep_building %>% 
-  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
-  select(all_of(problem_variable %>% pull(variable)),everything())
-
-nulls_01
-```
-
-Let's count the extent of the issues.
-
-```{r}
-problem_variable %>% 
-  pull(variable) %>% 
-  map(
-    ~nulls_01 %>% 
-  count(!!sym(.x)) %>% 
-  arrange(desc(n)) %>% 
-    filter(is.na(!!sym(.x)))
-  )
-```
-
-Let's count the entries here.
-
-```{r}
-prep_building %>% 
-  group_by(across(all_of(problem_variable %>% pull(variable)))) %>% 
-  count() %>% 
-  arrange(desc(n))
-```
-
-Lot's of entries.
-
-Check relationship with time.
-
-```{r}
-prep_building %>% 
-  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
-  group_by(across(all_of(problem_variable %>% pull(variable))),date) %>% 
-  count() %>% 
-  ggplot(aes(x = date, y = n)) +
-  geom_jitter() +
-  geom_smooth() +
-  theme_fivethirtyeight()
-```
-
-Looks pretty random, and low numbers.
-
-Let's investigate whether these employees ever have other values for `r problem_variable %>% pull(variable)`.
-
-```{r}
-prep_01 <-
-  prep_building %>% 
-  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
-  select(person_id) %>% 
-  distinct() %>% 
-  inner_join(prep_building) %>% 
-  arrange(person_id,date) %>% 
-  select(person_id,date,all_of(problem_variable %>% pull(variable)))
-
-prep_01 %>% 
-  datatable_with_sampling(in_max_rows = 5000)
-```
-
-They do have some.
-
-Now let's look at how they change.
-
-```{r}
-prep_02 <- 
-  prep_01 %>% 
-  group_by(across(all_of(problem_variable %>% pull(variable))),person_id) %>% 
-  summarise(
-    n = n(),
-    date_first = first(date),
-    date_last = last(date)
-  ) %>% 
-  arrange(person_id,n)
-
-prep_02 %>% 
-  datatable_with_sampling(in_max_rows = 5000)
-```
-
-It appears that most start with nulls then became a category.
-
-Let's check their position category at the earliest date and count.
-
-```{r}
-prep_02 %>% 
-  group_by(person_id) %>% 
-  filter(date_first == min(date_first)) %>% 
-  ungroup() %>% 
-  count(position_category_code,position_category_description)
-```
-
-Most of this group are null at the beginning. Some not.
-
-Let's check the position category at the latest date and count.
-
-```{r}
-prep_02 %>% 
-  group_by(person_id) %>% 
-  filter(date_first == max(date_first)) %>% 
-  ungroup() %>% 
-  count(position_category_code,position_category_description)
-```
-
-Is this an important variable?
-
-Yes, but we want to use this in the analysis. We will fill the variable the most proximate value and create an indicator that these values were imputed.
-
-```{r}
-prep_xx <- 
-  prep_building %>% 
-  select(date, person_id,all_of(problem_variable %>% pull(variable))) %>% 
-  distinct() %>% 
-  mutate(
-    position_category_imputed = case_when(is.na(position_category_code) ~ 1,
-                                          is.na(position_category_description) ~ 1,
-                                          TRUE ~ 0) 
-  ) %>% 
-  arrange(person_id, date) %>% 
-  group_by(person_id) %>% 
-  fill(position_category_code, .direction = "downup") %>% 
-  fill(position_category_description, .direction = "downup") %>% 
-  ungroup() %>% 
-  mutate(
-    across(
-      .cols = all_of(problem_variable %>% pull(variable)),
-      .fns = ~case_when(is.na(.) ~ "(Missing)",
-                        TRUE ~ .)
-    )
-  )
-
-prep_xx %>%
-  skim()
-```
-
-Compare against the identified cases above.
-
-```{r}
-prep_xx %>% 
-  inner_join(prep_01,
-            by =  c("person_id", "date"),
-            suffix = c("_xx","_01")
-  ) %>% 
-  datatable_with_sampling(in_max_rows = 5000)
-```
-
-Looks good.
-
-Join to building dataframe.
-
-```{r}
-prep_problem <- prep_problem %>% 
-  left_join(prep_xx)
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`: `supervisor_correction`
-
-Removing problems produced by
-
-```{r}
-problem_variable <- 
-  problem_variables %>% 
-  filter(group == problem_groups[step_n])
-
-problem_variable
-```
-
-Reviewing blanks.
-
-```{r}
-nulls_01 <- 
-  prep_building %>% 
-  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
-  select(all_of(problem_variable %>% pull(variable)),everything())
-
-nulls_01 %>% 
-  datatable_with_sampling(in_max_rows = 5000)
-```
-
-Let's count the extent of the issues.
-
-```{r}
-problem_variable %>% 
-  pull(variable) %>% 
-  map(
-    ~nulls_01 %>% 
-  count(!!sym(.x)) %>% 
-  arrange(desc(n)) %>% 
-    filter(is.na(!!sym(.x)))
-  )
-```
-
-Let's count the entries here.
-
-```{r}
-prep_building %>% 
-  group_by(across(all_of(problem_variable %>% pull(variable)))) %>% 
-  count() %>% 
-  arrange(desc(n)) %>% 
-   flextable() %>% 
-  theme_zebra() %>% 
-  autofit()
-```
-
-Lot's of entries.
-
-Check relationship with time.
-
-```{r}
-prep_building %>% 
-  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
-  group_by(across(all_of(problem_variable %>% pull(variable))),date) %>% 
-  count() %>% 
-  ggplot(aes(x = date, y = n)) +
-  geom_jitter() +
-  geom_smooth() +
-  theme_fivethirtyeight()
-```
-
-Some increase in the use of this over time.
-
-Let's count this along side `daily_status`.
-
-```{r}
-prep_building %>% 
-  group_by(across(all_of(problem_variable %>% pull(variable))),daily_status) %>% 
-  count() %>% 
-   flextable() %>% 
-  theme_zebra() %>% 
-  autofit()
-```
-
-Is this an important variable?
-
-Yes, but we want to use this in the analysis. We will use with `daily_status` to define status.
-
-```{r}
-prep_xx <- 
-  prep_building %>% 
-  select(date, person_id,all_of(problem_variable %>% pull(variable)),daily_status) %>% 
-  distinct() %>% 
-  mutate(
-    daily_status_imputed = case_when(is.na(supervisor_correction) &
-                                       daily_status == "Supervisor Corrected" ~ "(Missing)",
-                                     is.na(supervisor_correction) ~ daily_status,
-                                     daily_status == "Supervisor Corrected" ~ supervisor_correction
-                                     ) 
-  )
-
-prep_xx %>%
-  skim()
-```
-
-Let's count these variables to make sure they are coming out correctly.
-
-```{r}
-prep_xx %>% 
-  count(supervisor_correction,daily_status,daily_status_imputed) %>% 
-  flextable() %>% 
-  theme_zebra() %>% 
-  autofit()
-```
-
-Looks good.
-
-Let's remove `supervisor_correction`.
-
-```{r}
-prep_xx <- 
-  prep_xx %>% 
-  select(-supervisor_correction)
-```
-
-Join to building dataframe.
-
-```{r}
-prep_problem <- prep_problem %>% 
-  left_join(prep_xx)
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`: `supervisor_e_mail_address`
-
-Removing problems produced by
-
-```{r}
-problem_variable <- 
-  problem_variables %>% 
-  filter(group == problem_groups[step_n])
-
-problem_variable
-```
-
-Reviewing blanks.
-
-```{r}
-nulls_01 <- 
-  prep_building %>% 
-  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
-  select(all_of(problem_variable %>% pull(variable)),everything())
-
-nulls_01 %>% 
-  datatable_with_sampling(in_max_rows = 5000)
-```
-
-Let's count the extent of the issues.
-
-```{r}
-problem_variable %>% 
-  pull(variable) %>% 
-  map(
-    ~nulls_01 %>% 
-  count(!!sym(.x)) %>% 
-  arrange(desc(n)) %>% 
-    filter(is.na(!!sym(.x)))
-  )
-```
-
-Not too many.
-
-Check relationship with time.
-
-```{r}
-prep_building %>% 
-  filter(if_any(all_of(problem_variable %>% pull(variable)),  ~is.na(.x))) %>% 
-  group_by(across(all_of(problem_variable %>% pull(variable))),date) %>% 
-  count() %>% 
-  ggplot(aes(x = date, y = n)) +
-  geom_jitter() +
-  geom_smooth() +
-  theme_fivethirtyeight()
-```
-
-Let's see if we can find these names in the roster data.
-
-```{r}
-nulls_01 %>% 
-  select(supervisor_display_name) %>% 
-  distinct() %>% 
-  separate(supervisor_display_name,c("supervisor_first_name","supervisor_last_name"), sep = " ") %>% 
-  mutate(
-    full_name = glue::glue("{supervisor_last_name},{supervisor_first_name}")
-  ) %>% 
-  inner_join(prep_base_2)
-```
-
-Let's see if anyone has the same last name.
-
-```{r}
-prep_01 <- 
-  nulls_01 %>% 
-  select(supervisor_display_name) %>% 
-  distinct() %>% 
-  separate(supervisor_display_name,c("supervisor_first_name","supervisor_last_name"), sep = " ",
-           remove = FALSE) %>% 
-  mutate(
-    full_name = glue::glue("{supervisor_last_name},{supervisor_first_name}")
-  ) %>% 
-  inner_join(prep_base_2 %>% 
-               separate(full_name,c("supervisor_last_name","supervisor_first_name"), sep = ","),
-             by = "supervisor_last_name") %>% 
-  select(starts_with("supervisor_"), employee_e_mail_address,everything())
-
-prep_01 %>% 
-  datatable_with_sampling(in_max_rows = 5000)
-```
-
-This looks like the right person. Let's collect her information.
-
-```{r}
-prep_02 <- 
-  prep_01 %>% 
-  select(supervisor_display_name.x,employee_e_mail_address) %>% 
-  distinct() %>% 
-  filter(!is.na(employee_e_mail_address)) %>% 
-  rename(supervisor_display_name = supervisor_display_name.x,
-         supervisor_e_mail_address = employee_e_mail_address)
-
-prep_02 %>% 
-  datatable_with_sampling(in_max_rows = 5000)
-```
-
-```{r}
-prep_xx <- 
-  prep_building %>% 
-  select(date, person_id,all_of(problem_variable %>% pull(variable)),supervisor_display_name) %>% 
-  distinct() %>% 
-  left_join(prep_02,by = "supervisor_display_name") %>% 
-  mutate(
-    supervisor_e_mail_address.z = 
-      case_when(is.na(supervisor_e_mail_address.x) ~ supervisor_e_mail_address.y,
-                TRUE ~supervisor_e_mail_address.x
-                                     )
-  )
-
-prep_xx %>%
-  skim()
-```
-
-Let's make sure it only effected this case.
-
-```{r}
-prep_xx %>% 
-  filter(supervisor_e_mail_address.y == supervisor_e_mail_address.z) %>% 
-  count(supervisor_display_name)
-```
-
-Looks good. Let's only use `person_id`, `date`, and rename `supervisor_e_mail_address.z`.
-
-```{r}
-prep_xx <- 
-  prep_xx %>% 
-  select(person_id,date,supervisor_e_mail_address.z) %>% 
-  rename(supervisor_e_mail_address = supervisor_e_mail_address.z)
-
-prep_xx %>%
-  skim()
-```
-
-Join to building dataframe.
-
-```{r}
-prep_problem <- prep_problem %>% 
-  left_join(prep_xx)
-```
-
-```{r}
-step_n <- step_n + 1
-```
-
-#### Step `r step_n`: Done!
-
-Removing problems produced by
-
-```{r}
-problem_variable <- 
-  problem_variables %>% 
-  filter(group == problem_groups[step_n])
-
-problem_variable
-```
-
-Done.
-
-### Combining data
-
-#### Create dataframe off non-null columns
-
-Collect column names of variables not creating duplicates.
-
-```{r}
-non_problem_variables <- 
-  column_meta_data  %>% 
-  filter(!(blanks_by_variable | nulls_by_variable)) %>% 
-  pull(variable)
-
-non_problem_variables
-```
-
-Create dataframe of only these variables.
-
-```{r}
-prep_xx <- 
-  prep_building %>% 
-  select(any_of(non_problem_variables)) %>% 
-  distinct()
-
-prep_xx %>% 
-  glimpse()
-
-prep_xx %>% 
-  skim()
-```
-
-Join to building dataframe.
-
-```{r}
-prep_building <- prep_problem %>% 
-  left_join(prep_xx)
-```
-
-### Checking problems
-
-Created a dataframe of variable metadata.
-
-```{r}
-column_meta_data <- 
-  prep_building %>% 
-  contents()
-
-column_meta_data <- 
-  column_meta_data$contents %>% 
-  as.data.frame()
-
-column_meta_data <-
-  column_meta_data %>% 
-  rownames_to_column(var = "variable")
-
-if("NAs" %in% names(column_meta_data))
-{
-  column_meta_data <- 
-  column_meta_data %>% 
-  mutate(
-    nulls_by_variable = case_when(NAs > 0 ~ TRUE,
-                                  NAs == 0 ~ FALSE)
-  )
-}
-
-if(!("NAs" %in% names(column_meta_data)))
-{
-  column_meta_data <- 
-  column_meta_data %>% 
-  mutate(
-    nulls_by_variable = FALSE
-  )
-}
-
-column_meta_data
-```
-
-Counting top 10 values for all character or factor columns to identify other common values.
-
-```{r}
-values_count <- 
-  prep_building %>% 
-  select(where(is.character) | where(is.factor)) %>% 
-  names()
-
-values_count %>% 
-  map(~count(prep_building,!!sym(.)) %>% 
-  arrange(desc(n)) %>%
-  slice_head(n = 10))
-
-```
-
-No obvious values.
-
-Function that checks whether there are blanks for different variables
-
-```{r}
-blank_check <- function(in_data,in_variable_name)
-{
-  check_01 <- 
-  in_data %>% 
-    filter(!!sym(in_variable_name) == "") %>% 
-  distinct()
-
-out <- nrow(check_01) > 0
-
-return(out)
-}
-```
-
-Checking blanks for each variable in the dataframe.
-
-```{r}
-blanks_by_variable <- 
-  column_meta_data %>% 
-  pull(variable) %>% 
-  map_lgl(~blank_check(in_data = prep_building,.))
-
-blanks_by_variable
-```
-
-Add this to the `column_meta_data` dataframe.
-
-```{r}
-column_meta_data <- 
-  column_meta_data %>% 
-  add_column(
-    blanks_by_variable = blanks_by_variable
-  )
-
-column_meta_data
-```
-
-Create dataframe of only variables that have blanks.
-
-```{r}
-problem_variables <- 
-  column_meta_data %>% 
-  filter(blanks_by_variable | nulls_by_variable)
-
-problem_variables
-```
-
-## Other data issues
-
-Review the data.
-
-```{r}
-prep_building %>% 
-  skim()
-```
+All of these are null correlations, which will address in analysis.
 
@@
 ```{r}
-check_in_panel <- prep_building
+prep_employees <- prep_building
 ```
@@
 ```{r}
-save(check_in_panel, file = file.path(params$google_drive_home,"03. Data Collection","prepared-data",
-          glue::glue("check_in_panel_{Sys.Date()}.rdata")))
+save(prep_employees, file = file.path(params$google_drive_home,"03. Data Collection","prepared-data",
+          glue::glue("prep_employees_{Sys.Date()}.rdata")))
 ```

### 2023-05-11 04. Analysis/scripts/02_data_preparation_clusters_employee.R
Create 02_data_preparation_clusters_employee.R

@@ -1,0 +1,56 @@
+
+# Start timer -------------------------------------------------------------
+
+tictoc::tic()
+
+# Libraries ---------------------------------------------------------------
+
+library(tidyverse)
+library(lubridate)
+library(purrr)
+
+# Parameters --------------------------------------------------------------
+
+author <-  "Ben Jaques-Leslie"
+project_number <-  2312
+project_name <-  "Occupancy Patterns"
+google_drive_home <-  "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
+data_folder_1 <-  "prepared-data"
+data_file_1 <-  "check_in_panel_2023-04-12.rdata"
+unique_identifier_1 <- c("date","person_id")
+date_cohort_month <-  "2022-03-01"
+observation_window_length_months <-  6
+
+# Determine file name -----------------------------------------------------
+
+file_name <- glue::glue("02_data_preparation_clusters_employee-{project_number}-{str_replace_all(str_to_lower(project_name),' ','-')}-{today()}.html")
+
+file_name
+
+# Render data extraction --------------------------------------------------
+
+rmarkdown::render(input = here::here("04. Analysis",
+                                     "scripts",
+                                     "02_data_preparation_clusters_employee.Rmd"),
+                  params = list(
+                    author = author,
+                    project_number = project_number,
+                    project_name = project_name,
+                    google_drive_home = google_drive_home,
+                    data_folder_1 = data_folder_1,
+                    data_file_1 = data_file_1,
+                    unique_identifier_1 = unique_identifier_1,
+                    date_cohort_month = date_cohort_month,
+                    observation_window_length_months = observation_window_length_months
+                  ),
+                  output_file =
+                    here::here("04. Analysis",
+                               "output",
+                               'html',
+                               file_name))
+
+
+# End timer ---------------------------------------------------------------
+
+tictoc::toc()
+

### 2023-05-11 04. Analysis/scripts/02_data_preparation_clusters_team.Rmd
Create 02_data_preparation_clusters_team.Rmd
Getting started on team categories data preparation

--- 2023-05-11 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
@@
 ---
-title: "Data preparation for employee category analysis"
+title: "Data preparation for team category analysis"
 date: "`r Sys.Date()`"
@@
 
-Collect `person_id` of employees that worked in `r nice_month_year(date_cohort_month_start)`.
+Collect `person_id` and `supervisor_e_mail_address` of employees that worked in `r nice_month_year(date_cohort_month_start)`. If a team member had multiple supervisors, select the first one.
 
@@
   filter(date >= date_cohort_month_start & date <= date_cohort_month_end) %>% 
-  select(person_id) %>% 
-  distinct()
+  arrange(person_id,date) %>% 
+  group_by(person_id) %>% 
+  summarise(
+    supervisor_e_mail_address = first(supervisor_e_mail_address)
+  ) %>% 
+  ungroup()
 ```
@@
   summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Check: These have the same number of unique `supervisor_e_mail_address`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
+  pull() ==
+  cohort_panel %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
   pull()
@@
 
+Check: These have the same number of unique `supervisor_e_mail_address`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
+  pull() ==
+  cohort_panel %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
+  pull()
+```
+
 Set up `prep_building`.
@@
 prep_building <- 
-  cohort_ids
+  cohort_ids %>% 
+  select(supervisor_e_mail_address) %>% 
+  distinct()
 ```
@@
 
-Now calculating the number of days per employee by `daily_status_imputed`.
+Now calculating the number of days per team by `daily_status_imputed`.
 Proportions are caluculated for onsite and telework only.
 The calculations are made in two ways in two ways.
-First as a proportion of employee working days:
+First as a proportion of team working days:
 
 $$
-\frac{DailyStatusDays}{WorkingDays}
+\frac{\sum_{m=1}^{x}DailyStatusDays_m}{\sum_{m=1}^{x}WorkingDays_m}
 $$
@@
 $$
-WorkingDays = OnsiteDays + TeleworkDays
+WorkingDays_m = OnsiteDays_m + TeleworkDays_m
 $$
 
+$OnsiteDays_m$ is the number of onsite days for team member $m$ and $TeleworkDays_m$ is the number of telework days for team member $m$. $x$ is number of members on team
+
 Second as a proportion of days in the observations window:
@@
 $$
-\frac{DailyStatusDays}{ObservationWindowDays}
+\frac{\sum_{m=1}^{x}DailyStatusDays_m}{x\times ObservationWindowDays}
 $$
@@
 ```{r}
-prep_xx <- 
-  cohort_panel %>%
-  group_by(person_id,daily_status_imputed,.drop = FALSE) %>% 
+prep_a <-
+  cohort_panel %>%
+  group_by(supervisor_e_mail_address,person_id,daily_status_imputed,.drop = FALSE) %>% 
   summarise(working_days = n_distinct(date)) %>% 
+  ungroup() %>% 
+  filter(
+    daily_status_imputed == "Reporting to Job Site" |
+      daily_status_imputed == "Teleworking"
+  )
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+```{r}
+prep_b <- 
+  prep_a %>% 
+  group_by(supervisor_e_mail_address) %>% 
+  summarise(
+    working_days = sum(working_days)
+  ) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_b %>% 
+  skim()
+```
+
+```{r}
+prep_c <- 
+  prep_a %>% 
+  group_by(supervisor_e_mail_address,daily_status_imputed) %>% 
+  summarise(
+    working_days = sum(working_days)
+  ) %>% 
   ungroup() %>% 
@@
   clean_names() %>% 
-  rename_with(~glue::glue("daily_status_{.}"), -person_id) %>% 
-  mutate(
-    working_days = daily_status_reporting_to_job_site + daily_status_teleworking,
+  rename_with(~glue::glue("daily_status_{.}"), -supervisor_e_mail_address)
+```
+
+Review data.
+
+```{r}
+prep_c %>% 
+  skim()
+```
+
+```{r}
+prep_d <-
+  cohort_panel %>%
+  group_by(supervisor_e_mail_address) %>% 
+  summarise(
+    team_members = n_distinct(person_id)
+  ) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_d %>% 
+  skim()
+```
+
+```{r}
+prep_e <- 
+  prep_b %>% 
+  full_join(prep_c) %>% 
+  full_join(prep_d)
+```
+
+Review data.
+
+```{r}
+prep_e %>% 
+  skim()
+```
+
+```{r}
+prep_xx <- 
+  prep_e %>% 
+  mutate(
+    observation_window_days = team_members*observation_window_days,
     daily_status_reporting_to_job_site_working_prop = daily_status_reporting_to_job_site/working_days,
@@
 
-Check: These have the same number of unique `person_id`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(person_id)) %>% 
+Check: These have the same number of unique `supervisor_e_mail_address`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
   pull() ==
   prep_xx %>% 
-  summarise(n_distinct(person_id)) %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
   pull()
@@
 ```
+# CONTINUE FROM HERE
 

### 2023-05-17 04. Analysis/scripts/02_data_preparation_clusters_team.Rmd
Update 02_data_preparation_clusters_team.Rmd
Adding notes for the aggregate whole period variables.

@@
 
-### Employee, whole period variables
-
-For following variables are aggregated for the whole period for each employee:
-
--   Proportion of days onsite
-
--   Proportion of days remote
-
--   Number of working days
+### Team, whole period variables
+
+For following variables are aggregated for the whole period for the whole team:
+
+-   Proportion of team members working days onsite
+
+-   Proportion of team members working days remote
+
+-   Number of team members working days
 
@@
 
-$OnsiteDays_m$ is the number of onsite days for team member $m$ and $TeleworkDays_m$ is the number of telework days for team member $m$. $x$ is number of members on team
+$OnsiteDays_m$ is the number of onsite days for team member $m$ and $TeleworkDays_m$ is the number of telework days for team member $m$. $x$ is number of members on team.
 
@@
 $$
+
+Now we calculate the values for the data.
+
+First count the number of distinct days per `supervisor_e_mail_address`, `person_id`, and `daily_status_imputed`, then filter to daily status: *Reporting to Job Site* or *Teleworking*.
 
@@
 
+Second, sum the number days by `supervisor_e_mail_address` from dataframe `prep_a`.
+
 ```{r}
@@
 
+Third, sum the number days by `supervisor_e_mail_address` and `daily_status_imputed` from dataframe `prep_a` and reshape the data wide so that statuses are in columns, `daily_status_*`.
+
 ```{r}
@@
 
+Fourth, count the number of unique team members per supervisor.
+
 ```{r}
@@
 ```
+
+Join working days, working days per status, and team members into one datafram by `supervisor_e_mail_address`.
 
@@
 ```
+
+Calucate `observation_window_days`, `daily_status_reporting_to_job_site_working_prop`, `daily_status_teleworking_working_prop`, `daily_status_reporting_to_job_site_observation_prop`, and `daily_status_teleworking_observation_prop`, then replace missing values with zero.
 
@@
 
+-   Modal size of team over observation window
+
+-   Proportion of team members working days remote by the day of the
+    week
+
+-   Proportion of team members exiting team
+
+-   Proportion of working days at least two team member co-located
+
+-   Proportion of working days supervisor is co-located with at least
+    one team member
+
+-   Proportion of working days entire team is co-located
+
+-   Proportion of working days entire team is remote
+
+-   Proportion of observation window the team existed.
+
 ### Employee, day of week variables
 
-For following variables are aggregated for the whole period by day of the week for each employee:
-
--   Proportion of days remote by the day of the week
-
--   Correlation of work status between days of the week
+For following variables are aggregated for the whole period by day of the week for the whole team:
+
+-   Proportion of team members working days remote by the day of the
+    week
 

### 2023-05-17 04. Analysis/scripts/02_data_preparation_clusters_team.Rmd
Update 02_data_preparation_clusters_team.Rmd
Adding day of week proportion telework.

@@
 
-Join working days, working days per status, and team members into one datafram by `supervisor_e_mail_address`.
+Join working days, working days per status, and team members into one dataframe by `supervisor_e_mail_address`.
 
@@
 ```
-# CONTINUE FROM HERE
-
--   Modal size of team over observation window
-
--   Proportion of team members working days remote by the day of the
-    week
-
--   Proportion of team members exiting team
-
--   Proportion of working days at least two team member co-located
-
--   Proportion of working days supervisor is co-located with at least
-    one team member
-
--   Proportion of working days entire team is co-located
-
--   Proportion of working days entire team is remote
-
--   Proportion of observation window the team existed.
-
-### Employee, day of week variables
+
+### Team, day of week variables
 
@@
 
-We make the same calculations as above, but by the day of the week.
-
-```{r}
-prep_day_of_week <-
-  cohort_panel %>%
-  group_by(person_id,daily_status_imputed,date_day_of_week,) %>% 
+First count the number of distinct days per `supervisor_e_mail_address`, `date_day_of_week`, `person_id`, and `daily_status_imputed`, then filter to daily status: *Reporting to Job Site* or *Teleworking*.
+
+```{r}
+prep_a <-
+  cohort_panel %>%
+  group_by(supervisor_e_mail_address,person_id,daily_status_imputed,date_day_of_week,.drop = FALSE) %>% 
   summarise(working_days = n_distinct(date)) %>% 
   ungroup() %>% 
-  pivot_wider(values_from = working_days, names_from = c(daily_status_imputed)) %>% 
-  left_join(observation_window_days_day_of_week) %>% 
+  filter(
+    daily_status_imputed == "Reporting to Job Site" |
+      daily_status_imputed == "Teleworking"
+  )
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Second, sum the number days by `supervisor_e_mail_address` and `date_day_of_week` from dataframe `prep_a`.
+
+```{r}
+prep_b <- 
+  prep_a %>% 
+  group_by(supervisor_e_mail_address,date_day_of_week) %>% 
+  summarise(
+    working_days = sum(working_days)
+  ) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_b %>% 
+  skim()
+```
+
+Third, sum the number days by `supervisor_e_mail_address`, `date_day_of_week` and `daily_status_imputed` from dataframe `prep_a` and reshape the data wide so that statuses are in columns, `daily_status_*`.
+
+```{r}
+prep_c <- 
+  prep_a %>% 
+  group_by(supervisor_e_mail_address,daily_status_imputed,date_day_of_week) %>% 
+  summarise(
+    working_days = sum(working_days)
+  ) %>% 
+  ungroup() %>% 
+  pivot_wider(values_from = working_days, names_from = daily_status_imputed) %>% 
   clean_names() %>% 
-  rename_with(~glue::glue("daily_status_{.}"), c(-person_id,-date_day_of_week,-observation_window_days))  %>% 
-  mutate(
-    across(
-      .cols = where(is.numeric),
-      .fns = ~replace_na(.,0)
-    )
-  ) %>% 
-  mutate(
-    working_days = daily_status_reporting_to_job_site + daily_status_teleworking,
+  rename_with(~glue::glue("daily_status_{.}"), c(-supervisor_e_mail_address,-date_day_of_week))
+```
+
+Review data.
+
+```{r}
+prep_c %>% 
+  skim()
+```
+
+Fourth, count the number of unique team members per `supervisor_e_mail_address` and `date_day_of_week`.
+
+```{r}
+prep_d <-
+  cohort_panel %>%
+  group_by(supervisor_e_mail_address,date_day_of_week) %>% 
+  summarise(
+    team_members = n_distinct(person_id)
+  ) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_d %>% 
+  skim()
+```
+
+Join working days, working days per status, and team members into one dataframe by `supervisor_e_mail_address`.
+
+```{r}
+prep_e <- 
+  prep_b %>% 
+  full_join(prep_c) %>% 
+  full_join(prep_d) %>% 
+  left_join(observation_window_days_day_of_week)
+```
+
+Review data.
+
+```{r}
+prep_e %>% 
+  skim()
+```
+
+Review data by `date_day_of_week`.
+
+```{r}
+prep_e %>% 
+  group_by(date_day_of_week) %>% 
+  skim()
+```
+
+Filter out *Sat* and *Sun* as there are no working days.
+
+```{r}
+prep_f <- 
+  prep_e %>% 
+  filter(date_day_of_week != "Sat" &
+           date_day_of_week != "Sun")
+```
+
+Review data.
+
+```{r}
+prep_f %>% 
+  skim()
+```
+
+Calucate `observation_window_days`, `daily_status_reporting_to_job_site_working_prop`, `daily_status_teleworking_working_prop`, `daily_status_reporting_to_job_site_observation_prop`, and `daily_status_teleworking_observation_prop`, then replace missing values with zero.
+
+```{r}
+prep_g <- 
+  prep_f %>% 
+  mutate(
+    observation_window_days = team_members*observation_window_days,
     daily_status_reporting_to_job_site_working_prop = daily_status_reporting_to_job_site/working_days,
@@
 ```{r}
-prep_day_of_week %>% 
+prep_g %>% 
   skim()
@@
 prep_xx <- 
-  prep_day_of_week %>% 
-  select(person_id,date_day_of_week,daily_status_teleworking_working_prop,daily_status_teleworking_observation_prop) %>% 
+  prep_g %>% 
+  select(supervisor_e_mail_address,
+         date_day_of_week,daily_status_teleworking_working_prop,daily_status_teleworking_observation_prop) %>% 
   pivot_longer(cols = starts_with("daily_status")) %>% 
@@
 ```
+
+# CONTINUE FROM HERE
+
+<!-- -   Modal size of team over observation window -->
+
+<!-- -   Proportion of team members working days remote by the day of the -->
+<!--     week -->
+
+<!-- -   Proportion of team members exiting team -->
+
+<!-- -   Proportion of working days at least two team member co-located -->
+
+<!-- -   Proportion of working days supervisor is co-located with at least -->
+<!--     one team member -->
+
+<!-- -   Proportion of working days entire team is co-located -->
+
+<!-- -   Proportion of working days entire team is remote -->
+
+<!-- -   Proportion of observation window the team existed. -->
 

### 2023-05-17 04. Analysis/scripts/02_data_preparation_clusters_team.Rmd
Update 02_data_preparation_clusters_team.Rmd
Added modal size of team, proportion of team exiting, proportion of observation window the team existed, and proportion of working days at least two team members were co-located

@@
 
+### Modal size of team over observation window
+
+Calculate number of team members per day by supervisor email.
+
+```{r}
+prep_a <- 
+  cohort_panel %>% 
+  group_by(date,supervisor_e_mail_address) %>% 
+  summarise(team_size = n_distinct(person_id)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Calculate the mode team size for each `supervisor_e_mail_address`.
+
+```{r}
+prep_xx <- 
+  prep_a %>% 
+  group_by(supervisor_e_mail_address) %>% 
+  summarise(team_size_mode = getmode(team_size)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `supervisor_e_mail_address`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
+### Proportion of team members exiting team
+
+Calculate the number of days and last day of team members by `supervisor_e_mail_address`, and `person_id`.
+
+```{r}
+prep_a <- 
+  cohort_panel %>% 
+  group_by(supervisor_e_mail_address,person_id) %>% 
+  summarise(days = n_distinct(date),
+            last_day = max(date)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Identify team members that exit by limiting the list above to those who had few than the maximum number of days and whose last day was before the maxium day in the dataframe, then count the number per `supervisor_e_mail_address`.
+
+```{r}
+prep_b <- 
+  prep_a %>% 
+  filter(days < max(days)) %>% 
+  filter(last_day < max(last_day)) %>% 
+  group_by(supervisor_e_mail_address) %>% 
+  summarise(employee_exits = n_distinct(person_id)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_b %>% 
+  skim()
+```
+
+Attach to `prep_building` selecting `supervisor_e_mail_address` and `team_members` from that dataframe to calucalate the proportio of the team exiting.
+
+```{r}
+prep_c <- 
+  prep_building %>% 
+  select(supervisor_e_mail_address, team_members) %>% 
+  distinct() %>% 
+  left_join(prep_b) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  ) %>% 
+  mutate(
+    employee_exits_prop = employee_exits/team_members
+  )
+```
+
+Review data.
+
+```{r}
+prep_c %>% 
+  skim()
+```
+
+Remove `team_members`.
+
+```{r}
+prep_xx <- 
+  prep_c %>% 
+  select(-team_members)
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `supervisor_e_mail_address`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
+### Proportion of observation window the team existed
+
+Calculate the number of days and last day of team members by `supervisor_e_mail_address`.
+
+```{r}
+prep_a <- 
+  cohort_panel %>% 
+  group_by(supervisor_e_mail_address) %>% 
+  summarise(team_days = n_distinct(date)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Calculate the number of days and last day of team members by `supervisor_e_mail_address`.
+
+```{r}
+prep_xx <- 
+  prep_a %>% 
+  mutate(
+    team_days_prop = team_days/observation_window_days
+  )
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `supervisor_e_mail_address`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
+### Proportion of working days at least two team members co-located
+
+Identify employees who report to the site and collect `person_id`, `dates`, `location`, and `supervisor_e_mail_address`.
+
+```{r}
+prep_a <-
+  cohort_panel %>%
+  filter(daily_status_imputed == "Reporting to Job Site") %>%
+  select(person_id, date, location, supervisor_e_mail_address) %>%
+  distinct()
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Self left join on `dates`, `location`, and `supervisor_e_mail_address` and filter to rows where the `person_id`s do not match.
+
+```{r}
+prep_b <- 
+  prep_a %>% 
+  left_join(prep_a,
+            by = c("date", "location", "supervisor_e_mail_address"),
+            suffix = c("","_joined")) %>%
+  filter(person_id != person_id_joined)
+```
+
+Review data.
+
+```{r}
+prep_b %>% 
+  skim()
+```
+
+Count dates where co-location occurs by `supervisor_e_mail_address`.
+
+```{r}
+prep_c <- 
+  prep_b %>% 
+  group_by(supervisor_e_mail_address) %>% 
+  summarise(days_colocated_1 = n_distinct(date)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_c %>% 
+  skim()
+```
+
+Full join `working_days` from `prep_building`, calculate proportion of co-located days with at least one team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days`.
+
+```{r}
+prep_xx <- 
+  prep_c %>% 
+  full_join(prep_building %>% 
+              select(supervisor_e_mail_address,working_days)) %>% 
+  mutate(days_colocated_1_working_prop = days_colocated_1/working_days,
+         days_colocated_1_observation_prop = days_colocated_1/observation_window_days) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  ) %>% 
+  select(-working_days)
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `supervisor_e_mail_address`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
 # CONTINUE FROM HERE
-
-<!-- -   Modal size of team over observation window -->
-
-<!-- -   Proportion of team members working days remote by the day of the -->
-<!--     week -->
-
-<!-- -   Proportion of team members exiting team -->
-
-<!-- -   Proportion of working days at least two team member co-located -->
 
@@
 <!-- -   Proportion of working days entire team is remote -->
-
-<!-- -   Proportion of observation window the team existed. -->
 

### 2023-05-24 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Corrected calculation of whole team teleworking

@@
 
-Identify employees who telework and collect `person_id`, `dates`, `location`, and `supervisor_e_mail_address`.
+Identify employees who telework and collect `person_id`, `dates`, and `supervisor_e_mail_address`.
 
@@
   filter(daily_status_imputed == "Teleworking") %>%
-  select(person_id, date, location, supervisor_e_mail_address) %>%
+  select(person_id, date, supervisor_e_mail_address) %>%
   distinct()
@@
 
-Self left join on `dates`, `location`, and `supervisor_e_mail_address`.
+Count number of distinct `person_id`s by `dates`, and `supervisor_e_mail_address`.
 
@@
   prep_a %>% 
-  left_join(prep_a,
-            by = c("date", "location", "supervisor_e_mail_address"),
-            suffix = c("","_joined"))
+  group_by(date, supervisor_e_mail_address) %>%
+  summarise(telework_team_members = n_distinct(person_id)) %>% 
+  ungroup()
 ```
@@
 
-Count number of team members co-located by `person_id` and `date` by counting unique `person_id_joined`.
+Calculate number of team members per day by supervisor email.
 
@@
 prep_c <- 
-  prep_b %>% 
-  group_by(person_id,date,supervisor_e_mail_address) %>% 
-  summarise(telework_team_members = n_distinct(person_id_joined)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_c %>% 
-  skim()
-```
-
-Calculate number of team members per day by supervisor email.
-
-```{r}
-prep_d <- 
   cohort_panel %>% 
@@
 ```{r}
+prep_c %>% 
+  skim()
+```
+
+Left join telework team members and teams size, but `date` and `supervisor_e_mail_address`, then filter to when telework team members is the same size as the team
+
+```{r}
+prep_d <- 
+  prep_b %>% 
+  left_join(prep_c) %>% 
+  filter(telework_team_members == team_size)
+```
+
+Review data.
+
+```{r}
 prep_d %>% 
@@
 
-Left join telework team members and teams size, but `date` and `supervisor_e_mail_address`, then filter to when telework team members is the same size as the team
+Inner join `cohort_panel` to `prep_d` to only capture employees on days where the whole team is remote.
 
@@
 prep_e <- 
-  prep_c %>% 
-  left_join(prep_d) %>% 
-  filter(telework_team_members == team_size)
+  cohort_panel %>% 
+  select(person_id,supervisor_e_mail_address,date) %>% 
+  distinct() %>% 
+  inner_join(prep_d)
 ```

### 2023-05-24 04. Analysis/scripts/02_data_preparation_clusters_team.Rmd
Update 02_data_preparation_clusters_team.Rmd
Removed between day correlations, added supervisor co-location with one team member, whole team co-located, whole team remote, and started rules-based categories

@@
 
-# CONTINUE FROM HERE
-
-<!-- -   Proportion of working days supervisor is co-located with at least -->
-<!--     one team member -->
-
-<!-- -   Proportion of working days entire team is co-located -->
-
-<!-- -   Proportion of working days entire team is remote -->
-
-#### Correlation of work status between days of the week
-
-Three strategies to captured relationships between day are below:
-
-1.  Correlation in telework between days of week
-
-2.  Correlation in status (as an ordered factor) between days of week
-
-3.  Proportion of telework on other days of week, if the employ teleworked on a specific day
-
-##### Correlation in telework between days of week
-
-The script below calculates the correlation in telework between days of the week.
-
-```{r correlation remote only}
-prep_day_of_week_cor_telework <- 
-  cohort_panel %>% 
-  select(person_id,date,date_day_of_week,daily_status_imputed) %>% 
-  mutate(ind = 1) %>% 
-  pivot_wider(names_from = daily_status_imputed, values_from = ind) %>% 
-  clean_names() %>% 
-  select(person_id,date,date_day_of_week,teleworking) %>% 
-  mutate(
-    across(
-      .cols = where(is.numeric),
-      .fns = ~replace_na(.,0)
-    )
-  ) %>% 
-  mutate(
-    date_week_start = floor_date(date,unit = "week")) %>% 
-  select(-date) %>% 
-  pivot_wider(values_from = teleworking,names_from = date_day_of_week) %>% 
-  mutate(
-    across(
-      .cols = where(is.numeric),
-      .fns = ~replace_na(.,0)
-    )
-  ) %>% 
-  clean_names() %>% 
-  group_by(person_id) %>%
-  # filter(person_id == "10070")
-  summarise(
-    mon_tue_cor_telework = cor(mon,tue,method = "kendall", use = "complete.obs"),
-    mon_wed_cor_telework = cor(mon,wed,method = "kendall", use = "complete.obs"),
-    mon_thu_cor_telework = cor(mon,thu,method = "kendall", use = "complete.obs"),
-    mon_fri_cor_telework = cor(mon,fri,method = "kendall", use = "complete.obs"),
-    tue_wed_cor_telework = cor(tue,wed,method = "kendall", use = "complete.obs"),
-    tue_thu_cor_telework = cor(tue,thu,method = "kendall", use = "complete.obs"),
-    tue_fri_cor_telework = cor(tue,fri,method = "kendall", use = "complete.obs"),
-    wed_thu_cor_telework = cor(wed,thu,method = "kendall", use = "complete.obs"),
-    wed_fri_cor_telework = cor(wed,fri,method = "kendall", use = "complete.obs"),
-    thu_fri_cor_telework = cor(thu,fri,method = "kendall", use = "complete.obs")
-    ) %>% 
-  ungroup()
-```
-
-Now rename to attach to `prep_building`.
-
-```{r}
-prep_xx <- 
-  prep_day_of_week_cor_telework
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `person_id`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(person_id)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(person_id)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-##### Correlation in status between days of week
-
-The script below calculates the correlation between work status.
-
-```{r correlation ordered status}
-prep_day_of_week_cor_status <- 
-  cohort_panel %>% 
-  select(person_id,date,date_day_of_week,daily_status_imputed) %>% 
-  mutate(
-    daily_status_imputed = fct_lump_prop(daily_status_imputed, prop = .1),
-    daily_status_imputed = fct_infreq(daily_status_imputed),
-    daily_status_imputed = factor(daily_status_imputed, ordered = TRUE)
-  )  %>% 
-  mutate(
-    date_week_start = floor_date(date,unit = "week")) %>% 
-  select(-date) %>% 
-  pivot_wider(values_from = daily_status_imputed,names_from = date_day_of_week) %>% 
-  mutate(
-    across(
-      .cols = where(is.factor),
-      .fns = ~replace_na(.,"Other")
-    )
-  ) %>% 
-  clean_names() %>% 
-  group_by(person_id) %>%
-  summarise(
-    mon_tue_cor_status = cor(as.numeric(mon),as.numeric(tue),method = "spearman", use = "complete.obs"),
-    mon_wed_cor_status = cor(as.numeric(mon),as.numeric(wed),method = "spearman", use = "complete.obs"),
-    mon_thu_cor_status = cor(as.numeric(mon),as.numeric(thu),method = "spearman", use = "complete.obs"),
-    mon_fri_cor_status = cor(as.numeric(mon),as.numeric(fri),method = "spearman", use = "complete.obs"),
-    tue_wed_cor_status = cor(as.numeric(tue),as.numeric(wed),method = "spearman", use = "complete.obs"),
-    tue_thu_cor_status = cor(as.numeric(tue),as.numeric(thu),method = "spearman", use = "complete.obs"),
-    tue_fri_cor_status = cor(as.numeric(tue),as.numeric(fri),method = "spearman", use = "complete.obs"),
-    wed_thu_cor_status = cor(as.numeric(wed),as.numeric(thu),method = "spearman", use = "complete.obs"),
-    wed_fri_cor_status = cor(as.numeric(wed),as.numeric(fri),method = "spearman", use = "complete.obs"),
-    thu_fri_cor_status = cor(as.numeric(thu),as.numeric(fri),method = "spearman", use = "complete.obs")
-    ) %>% 
-  ungroup()
-```
-
-Now rename to attach to `prep_building`.
-
-```{r}
-prep_xx <- 
-  prep_day_of_week_cor_status
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `person_id`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(person_id)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(person_id)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-##### Proportion of telework week day pairs
-
-First, create a dataframe of telework by days of the week.
-
-```{r proportion remote only prep dataframe}
+### Proportion of working days supervisor is co-located with at least one team member
+
+Identify employees who report to the site and collect `person_id`, `dates`, `location`, `employee_e_mail_address`, and `supervisor_e_mail_address`.
+
+```{r}
 prep_a <-
   cohort_panel %>%
-  select(person_id,date,date_day_of_week,daily_status_imputed) %>% 
-  mutate(ind = 1) %>% 
-  pivot_wider(names_from = daily_status_imputed, values_from = ind) %>% 
-  clean_names() %>% 
-  select(person_id,date,date_day_of_week,teleworking) %>% 
-  mutate(
-    across(
-      .cols = where(is.numeric),
-      .fns = ~replace_na(.,0)
-    )
-  ) %>% 
-  mutate(
-    date_week_start = floor_date(date,unit = "week")) %>% 
-  select(-date) %>% 
-  pivot_wider(values_from = teleworking,names_from = date_day_of_week) %>% 
-  mutate(
-    across(
-      .cols = where(is.numeric),
-      .fns = ~replace_na(.,0)
-    )
-  ) %>% 
-  clean_names()
-```
-
-Now, a function to calculate the proportion of telework on a different day, if the employee teleworked on a specific day.
-
-```{r}
-day_to_day_proportions <- function(in_data,in_var)
-{
-  var_string <- rlang::as_name(enquo(in_var))
-
-  # print(person_id)
-
-  out <- 
-    in_data %>% 
-  filter({{in_var}} == 1) %>% 
-  group_by(person_id) %>% 
-  summarise(
-    across(
-      .cols = where(is.numeric),
-      .fns = ~sum(.,na.rm = TRUE)
-  )) %>% 
-  mutate(
-    across(
-      .cols = c(-person_id,-{{in_var}}),
-      .fns = ~./{{in_var}},
-      .names = "{var_string}_{.col}"
-    )
-  ) %>% 
-  ungroup() %>% 
-    select(person_id,starts_with(var_string),-{{in_var}})
-
-  return(out)
-}
-```
-
-Iterated over the days of the week and join results.
-
-```{r}
-prep_day_of_week_proportion_pairs <- 
-  prep_a %>% 
-  select(thu:fri) %>%
-  names() %>% 
-  map(~day_to_day_proportions(prep_a,!!sym(.))) %>% 
-  reduce(full_join, by = "person_id")
-
-```
-
-Now rename to attach to `prep_building`.
-
-```{r}
-prep_xx <- 
-  prep_day_of_week_proportion_pairs %>% 
-  rename_with(-person_id,
-              .fn = ~glue::glue("{.}_prop_pairs")
-  )
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `person_id`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(person_id)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(person_id)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-#### Modal size of team over observation window
-
-Calculate number of team members per day by supervisor email.
-
-```{r}
-prep_a <- 
-  cohort_panel %>% 
-  group_by(date,supervisor_e_mail_address) %>% 
-  summarise(team_size = n_distinct(person_id)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_a %>% 
-  skim()
-```
-
-Join to `cohort_panel` only selecting, `person_id`, `date`, and `supervisor_e_mail_address`.
+  filter(daily_status_imputed == "Reporting to Job Site") %>%
+  select(person_id, date, location, employee_e_mail_address, supervisor_e_mail_address) %>%
+  distinct()
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Self inner join on `dates`, `location`, and `supervisor_e_mail_address` equal to `employee_e_mail_address` in the right table, and filter to rows where the `person_id`s do not match.
 
@@
 prep_b <- 
-  cohort_panel %>% 
-  select(date,person_id,supervisor_e_mail_address) %>% 
-  left_join(prep_a)
+  prep_a %>% 
+  inner_join(prep_a,
+            by = c("date", "location", "supervisor_e_mail_address" = "employee_e_mail_address"),
+            suffix = c("","_joined")) 
 ```
@@
 
-Calculate the mode team size for each employee.
-
-```{r}
-prep_xx <- 
-  prep_b %>% 
-  group_by(person_id) %>% 
-  summarise(team_size_mode = getmode(team_size)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `person_id`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(person_id)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(person_id)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-#### Proportion of working days co-located with at least one other team member
-
-Identify employees who report to the site and collect `person_id`, `dates`, `location`, and `supervisor_e_mail_address`.
-
-```{r}
-prep_a <-
-  cohort_panel %>%
-  filter(daily_status_imputed == "Reporting to Job Site") %>%
-  select(person_id, date, location, supervisor_e_mail_address) %>%
-  distinct()
-```
-
-Review data.
-
-```{r}
-prep_a %>% 
-  skim()
-```
-
-Self left join on `dates`, `location`, and `supervisor_e_mail_address` and filter to rows where the `person_id`s do not match.
-
-```{r}
-prep_b <- 
-  prep_a %>% 
-  left_join(prep_a,
-            by = c("date", "location", "supervisor_e_mail_address"),
-            suffix = c("","_joined")) %>%
-  filter(person_id != person_id_joined)
-```
-
-Review data.
-
-```{r}
-prep_b %>% 
-  skim()
-```
-
-Count dates where co-location occurs by `person_id`.
+Count dates where co-location with supervisor occurs by `supervisor_e_mail_address`.
 
@@
   prep_b %>% 
-  group_by(person_id) %>% 
-  summarise(days_colocated_1 = n_distinct(date)) %>% 
+  group_by(supervisor_e_mail_address) %>% 
+  summarise(days_colocated_supervisor = n_distinct(date)) %>% 
   ungroup()
@@
 
-Full join `working_days` from `prep_building`, calculate proportion of co-located days with at least one team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days`.
+Full join `working_days` and `observation_window_days` from `prep_building`, calculate proportion of co-located days with at least one team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days` and `observation_window_days`.
 
@@
   full_join(prep_building %>% 
-              select(person_id,working_days)) %>% 
-  mutate(days_colocated_1_working_prop = days_colocated_1/working_days,
-         days_colocated_1_observation_prop = days_colocated_1/observation_window_days) %>% 
-  mutate(
-    across(
-      .cols = where(is.numeric),
-      .fns = ~replace_na(.,0)
-    )
-  ) %>% 
-  select(-working_days)
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `person_id`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(person_id)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(person_id)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-#### Proportion of working days co-located with supervisor
-
-Identify employees who report to the site and collect `person_id`, `dates`, `location`, `employee_e_mail_address`, and `supervisor_e_mail_address`.
-
-```{r}
-prep_a <-
-  cohort_panel %>%
-  filter(daily_status_imputed == "Reporting to Job Site") %>%
-  select(person_id, date, location, employee_e_mail_address, supervisor_e_mail_address) %>%
-  distinct()
-```
-
-Review data.
-
-```{r}
-prep_a %>% 
-  skim()
-```
-
-Self inner join on `dates`, `location`, and `supervisor_e_mail_address` equal to `employee_e_mail_address` in the right table, and filter to rows where the `person_id`s do not match.
-
-```{r}
-prep_b <- 
-  prep_a %>% 
-  inner_join(prep_a,
-            by = c("date", "location", "supervisor_e_mail_address" = "employee_e_mail_address"),
-            suffix = c("","_joined")) 
-```
-
-Review data.
-
-```{r}
-prep_b %>% 
-  skim()
-```
-
-Count dates where co-location with supervisor occurs by `person_id`.
-
-```{r}
-prep_c <- 
-  prep_b %>% 
-  group_by(person_id) %>% 
-  summarise(days_colocated_supervisor = n_distinct(date)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_c %>% 
-  skim()
-```
-
-Full join `working_days` from `prep_building`, calculate proportion of co-located days with at least one team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days`.
-
-```{r}
-prep_xx <- 
-  prep_c %>% 
-  full_join(prep_building %>% 
-              select(person_id,working_days)) %>% 
+              select(supervisor_e_mail_address,working_days,observation_window_days)) %>% 
   mutate(days_colocated_supervisor_working_prop = days_colocated_supervisor/working_days,
@@
   ) %>% 
-  select(-working_days)
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `person_id`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(person_id)) %>% 
+  select(-working_days,-observation_window_days)
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `supervisor_e_mail_address`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
   pull() ==
   prep_xx %>% 
-  summarise(n_distinct(person_id)) %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
   pull()
@@
 ```
-
-#### Proportion of working days co-located with entire team
+### Proportion of working days entire team is co-located
 
@@
 
-Self left join on `dates`, `location`, and `supervisor_e_mail_address`.
+Count number of team members co-located by `supervisor_e_mail_address`, `location`, and `date` by counting unique `person_id`.
 
@@
   prep_a %>% 
-  left_join(prep_a,
-            by = c("date", "location", "supervisor_e_mail_address"),
-            suffix = c("","_joined"))
+  group_by(supervisor_e_mail_address,location, date) %>% 
+  summarise(colocated_team_members = n_distinct(person_id)) %>% 
+  ungroup()
 ```
@@
 prep_c <- 
-  prep_b %>% 
-  group_by(person_id,date,supervisor_e_mail_address) %>% 
-  summarise(colocated_team_members = n_distinct(person_id_joined)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_c %>% 
-  skim()
-```
-
-Calculate number of team members per day by supervisor email.
-
-```{r}
-prep_d <- 
   cohort_panel %>% 
@@
 ```{r}
+prep_c %>% 
+  skim()
+```
+
+Left join co-located team members and teams size, but `date` and `supervisor_e_mail_address`, then filter to when co-located team members is the same size as the team
+
+```{r}
+prep_d <- 
+  prep_b %>% 
+  left_join(prep_c) %>% 
+  filter(colocated_team_members == team_size)
+```
+
+Review data.
+
+```{r}
 prep_d %>% 
@@
 
-Left join co-located team members and teams size, but `date` and `supervisor_e_mail_address`, then filter to when co-located team members is the same size as the team
+Count dates where co-location with whole team occurs by `supervisor_e_mail_address`.
 
@@
 prep_e <- 
-  prep_c %>% 
-  left_join(prep_d) %>% 
-  filter(colocated_team_members == team_size)
+  prep_d %>% 
+  group_by(supervisor_e_mail_address) %>% 
+  summarise(days_colocated_team = n_distinct(date)) %>% 
+  ungroup()
 ```
@@
 
-Count dates where co-location with whole team occurs by `person_id`.
-
-```{r}
-prep_f <- 
+Full join `working_days` and `observation_window_days` from `prep_building`, calculate proportion of co-located days with team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days` and `observation_window_days`.
+
+```{r}
+prep_xx <- 
   prep_e %>% 
-  group_by(person_id) %>% 
-  summarise(days_colocated_team = n_distinct(date)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_f %>% 
-  skim()
-```
-
-Full join `working_days` from `prep_building`, calculate proportion of co-located days with team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days`.
-
-```{r}
-prep_xx <- 
-  prep_f %>% 
   full_join(prep_building %>% 
-              select(person_id,working_days)) %>% 
+              select(supervisor_e_mail_address,working_days,observation_window_days)) %>% 
   mutate(days_colocated_team_working_prop = days_colocated_team/working_days,
@@
 
-#### Proportion of working days entire team is remote
-
-Identify employees who telework and collect `person_id`, `dates`, `location`, and `supervisor_e_mail_address`.
+### Proportion of working days entire team is remote
+
+Identify employees who are teleworking and collect `person_id`, `dates`, and `supervisor_e_mail_address`.
 
@@
 
-Self left join on `dates`, `location`, and `supervisor_e_mail_address`.
+Count number of team members co-located by `supervisor_e_mail_address`, and `date` by counting unique `person_id`.
 
@@
   prep_a %>% 
-  left_join(prep_a,
-            by = c("date", "location", "supervisor_e_mail_address"),
-            suffix = c("","_joined"))
+  group_by(supervisor_e_mail_address,date) %>% 
+  summarise(telework_team_members = n_distinct(person_id)) %>% 
+  ungroup()
 ```
@@
 ```{r}
+prep_c %>% 
+  skim()
+```
+
+Left join teleworking team members and teams size, by `date` and `supervisor_e_mail_address`, then filter to when teleworking team members is the same size as the team.
+
+```{r}
+prep_d <- 
+  prep_b %>% 
+  left_join(prep_c) %>% 
+  filter(telework_team_members == team_size)
+```
+
+Review data.
+
+```{r}
 prep_d %>% 
@@
 
-Left join telework team members and teams size, but `date` and `supervisor_e_mail_address`, then filter to when telework team members is the same size as the team
+Count dates where co-location with whole team occurs by `supervisor_e_mail_address`.
 
@@
 prep_e <- 
-  prep_c %>% 
-  left_join(prep_d) %>% 
-  filter(telework_team_members == team_size)
+  prep_d %>% 
+  group_by(supervisor_e_mail_address) %>% 
+  summarise(days_telework_team = n_distinct(date)) %>% 
+  ungroup()
 ```
@@
 
-Count dates where telework with whole team occurs by `person_id`.
-
-```{r}
-prep_f <- 
+Full join `team_days` and `observation_window_days` from `prep_building`, calculate proportion of co-located days with team member by `team_days` and `observation_window_days`, replace nulls with 0, and remove `team_days` and `observation_window_days`.
+
+```{r}
+prep_xx <- 
   prep_e %>% 
-  group_by(person_id) %>% 
-  summarise(days_telework_team = n_distinct(date)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_f %>% 
-  skim()
-```
-
-Full join `working_days` from `prep_building`, calculate proportion of telework days with team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days`.
-
-```{r}
-prep_xx <- 
-  prep_f %>% 
   full_join(prep_building %>% 
-              select(person_id,working_days)) %>% 
-  mutate(days_telework_team_working_prop = days_telework_team/working_days,
+              select(supervisor_e_mail_address,team_days)) %>% 
+  mutate(days_telework_team_working_prop =  days_telework_team/team_days,
          days_telework_team_observation_prop = days_telework_team/observation_window_days) %>% 
@@
   ) %>% 
-  select(-working_days)
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `person_id`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(person_id)) %>% 
+  select(-team_days)
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `supervisor_e_mail_address`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
   pull() ==
   prep_xx %>% 
-  summarise(n_distinct(person_id)) %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
   pull()
@@
 
+# CONTINUE FROM HERE
+
 ## Define rule-based groups {.tabset .tabset-pills}
 
-The analysis plan defines nine rule-based groups for analysis:
-
-1.  **All remote** - A policy definition for staff that are 100% remote
-2.  **Routine teleworker** - Employees with position_category_description's *Onsite Flexible* or *Offsite* that work at least two two days per pay period onsite.
-    per pay period onsite.
-3.  **Onsite Flexible** - Defined by `position_category_description` in
-    the roster data
-4.  **Offsite** - Defined by `position_category_description` in the
+The analysis plan defines ten rule-based groups for analysis:
+
+1.  **All remote** - All team members are 100% remote
+2.  **Routine teleworker** - All team members have
+    `position_category_description`'s *Onsite Flexible* or *Offsite* and
+    work at least two two days per pay period onsite.
+3.  **Onsite Flexible** - All team members are *Onsite Flexible* as
+    defined by `position_category_description` in the roster data
+4.  **Offsite** - All team members are *Offsite* as defined by team
+    members `position_category_description` in the roster data
+5.  **Onsite Required** - All team members are *Onsite Required* as
+    defined by `position_category_description` in the roster data
+6.  **Mixed position categories** - Team members are different position
+    categories as as defined by `position_category_description` in the
     roster data
-5.  **Onsite Required** - Defined by `position_category_description` in
-    the roster data
-6.  **Primarily remote** - Employees who work remotely above the 95th
+7.  **Primarily remote** - Teams that work remotely above the 95th
     percentile <!-- could be 75th -->
-7.  **Mostly remote** - Employees who work remotely between the median
-    and the 95th percentile <!-- could be 75th -->
-8.  **Mostly onsite** - Employees who work remotely between 5th
-    percentile and the median <!-- could be 25th -->
-9.  **Primarily onsite** - Employees who work remotely below the 5th
+8.  **Mostly remote** - Teams that work remotely between the median and
+    the 95th percentile <!-- could be 75th -->
+9.  **Mostly onsite** - Teams that work remotely between 5th percentile
+    and the median <!-- could be 25th -->
+10. **Primarily onsite** - Teams that work remotely below the 5th
     percentile <!-- could be 75th -->
@@
   ) %>% 
-  select(person_id,starts_with("rule_based_"))
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `person_id`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(person_id)) %>% 
+  select(supervisor_e_mail_address,starts_with("rule_based_"))
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `supervisor_e_mail_address`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
   pull() ==
   prep_xx %>% 
-  summarise(n_distinct(person_id)) %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
   pull()
@@
   select(
-    person_id,
+    supervisor_e_mail_address,
     daily_status_reporting_to_job_site_working_prop,
@@
   ) %>%
-  select(person_id, starts_with("rule_based_"))
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `person_id`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(person_id)) %>% 
+  select(supervisor_e_mail_address, starts_with("rule_based_"))
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `supervisor_e_mail_address`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
   pull() ==
   prep_xx %>% 
-  summarise(n_distinct(person_id)) %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
   pull()
@@
 prep_c %>% 
-  inner_join(prep_a, by = "person_id") %>% 
+  inner_join(prep_b, by = "person_id") %>% 
   filter(position_category_description.x != position_category_description.y)
@@
 
-Identify the `position_category_description` at the beginning of the observation window and convert the categories into indicators.
+Identify the `position_category_description` at the beginning of the observation window and count number of team members per category by `supervisor_e_mail_address`.
+
+```{r}
+prep_a <- 
+  cohort_panel %>% 
+  group_by(supervisor_e_mail_address,position_category_description) %>% 
+  summarise(team_members = n_distinct(person_id)) %>% 
+  ungroup() %>% 
+  pivot_wider(values_from = team_members, names_from = position_category_description,
+              names_prefix = "rule_based_position_category_") %>% 
+  clean_names()
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Inner join with `prep_building` selecting `supervisor_e_mail_address`, and `team_members`.
+
+```{r}
+prep_b <- 
+  prep_building %>% 
+  select(supervisor_e_mail_address,team_members) %>% 
+  inner_join(prep_a)
+```
+
+Review data.
+
+```{r}
+prep_b %>% 
+  skim()
+```
+
+Create indicators for when the number of team members equals the number of members in a specific category.
+
+```{r}
+prep_c <- 
+  prep_b %>% 
+  mutate(
+    across(
+      .cols = starts_with("rule_based_position_category_"),
+      .fns = ~case_when(. == team_members ~ 1,
+                        TRUE ~ 0)
+    )
+  )
+```
+
+Review data.
+
+```{r}
+prep_c %>% 
+  skim()
+```
+
+Left join to `prep_building` selecting only `supervisor_e_mail_address` and remove `team_members`.
 
@@
 prep_xx <-
-  cohort_first %>% 
-  select(person_id,position_category_description) %>% 
-  character_to_indicator(in_unique_identifier = "person_id",
-                         position_category_description,
-                         in_prefix = "rule_based_position_category_")
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `person_id`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(person_id)) %>% 
+  prep_building %>% 
+  select(supervisor_e_mail_address) %>% 
+  left_join(prep_c) %>% 
+  select(-team_members)
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `supervisor_e_mail_address`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
   pull() ==
   prep_xx %>% 
-  summarise(n_distinct(person_id)) %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
   pull()
@@
 ```{r}
-prep_xx <- 
+prep_g <- 
   cohort_first %>% 
@@
 ```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `person_id`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(person_id)) %>% 
+prep_g %>% 
+  skim()
+```
+
+Left join to `cohort_ids`.
+
+```{r}
+prep_h <- 
+  cohort_ids %>% 
+  left_join(prep_g)
+```
+
+Review data.
+
+```{r}
+prep_h %>% 
+  skim()
+```
+
+```{r}
+prep_h %>% 
+  filter(rule_based_telework_onsite_minimum == 1) %>% 
+  group_by(supervisor_e_mail_address) %>% 
+  summarise(rule_based_telework_onsite_minimum = n_distinct(person_id))
+```
+
+Check: These have the same number of unique `supervisor_e_mail_address`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
   pull() ==
   prep_xx %>% 
-  summarise(n_distinct(person_id)) %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
   pull()

### 2023-05-24 02. Design/MSG-P2312-Analysis Plan-1-clusters.rmd
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Updated formatting
Update MSG-P2312-Analysis Plan-1-clusters.rmd
Updated to only be an indicator if all offsite or onsite flexible team members meet the two days per pay period requirement

@@
 1.  **All remote** - All team members are100% remote
-2.  **Routine teleworker** - All team members have
+2.  **Routine teleworker** - All team members who have
     `position_category_description`'s *Onsite Flexible* or *Offsite* and
@@
     defined by `position_category_description` in the roster data
-6.  Mixed position categories - Team members are different position
+6.  **Mixed position categories** - Team members are different position
     categories as as defined by `position_category_description` in the

### 2023-05-24 04. Analysis/scripts/02_data_preparation_clusters_team.Rmd
Update 02_data_preparation_clusters_team.Rmd
Added section for routine teleworker and began section on team characteristics

@@
 1.  **All remote** - All team members are 100% remote
-2.  **Routine teleworker** - All team members have
+2.  **Routine teleworker** - All team members who have
     `position_category_description`'s *Onsite Flexible* or *Offsite* and
@@
 
-```{r}
+Filter to team members who met the onsite minimum and count by `supervisor_e_mail_address`.
+
+```{r}
+prep_i <- 
   prep_h %>% 
@@
   group_by(supervisor_e_mail_address) %>% 
-  summarise(rule_based_telework_onsite_minimum = n_distinct(person_id))
+  summarise(rule_based_telework_onsite_minimum = n_distinct(person_id)) %>% 
+  ungroup()
+```
+
+Review data.
+
+```{r}
+prep_i %>% 
+  skim()
+```
+
+From `cohort_panel` count number of team members with **Onsite flexible** or **Offsite** `position_category_description` by `supervisor_e_mail_address`.
+
+```{r}
+prep_j <- 
+  cohort_panel %>% 
+  filter(position_category_description == "Onsite Flexible" |
+           position_category_description == "Offsite") %>% 
+  group_by(supervisor_e_mail_address) %>% 
+  summarise(team_members_telework = n_distinct(person_id)) %>% 
+  ungroup() 
+```
+
+Review data.
+
+```{r}
+prep_j %>% 
+  skim()
+```
+
+Full join and identify rows where all teleworking team members meet the minimum.
+
+```{r}
+prep_k <- 
+  prep_i %>% 
+  full_join(prep_j) %>% 
+  mutate(
+    rule_based_telework_onsite_minimum = case_when(rule_based_telework_onsite_minimum == team_members_telework ~ 1,
+                    TRUE ~ 0)
+  ) %>% 
+  select(-team_members_telework)
+```
+
+Review data.
+
+```{r}
+prep_k %>% 
+  skim()
+```
+
+Left join to `prep_building` selecting only `supervisor_e_mail_address` and remove `team_members`.
+
+```{r}
+prep_xx <-
+  prep_building %>% 
+  select(supervisor_e_mail_address) %>% 
+  left_join(prep_k) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  )
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
 ```
@@
 
+### Mixed categories
+
+From `cohort_panel` count team members by `position_category_description` and `supervisor_e_mail_address`, then filter to only `position_category_description`s that are **Onsite Flexible**, **Offsite**, or **Onsite Required**, then count `position_category_description` by `supervisor_e_mail_address`, then create `rule_based_mixed_position_category` identifying teams with more than one category, and last drop the temporary variable.
+
+```{r}
+prep_a <-
+  cohort_panel %>% 
+  group_by(supervisor_e_mail_address,position_category_description) %>% 
+  summarise(team_members = n_distinct(person_id)) %>% 
+  ungroup() %>% 
+  filter(position_category_description == "Onsite Flexible" |
+           position_category_description == "Offsite" |
+           position_category_description == "Onsite Required") %>% 
+  group_by(supervisor_e_mail_address) %>% 
+  summarise(temp_var = n_distinct(position_category_description)) %>% 
+  ungroup() %>% 
+   mutate(
+     rule_based_mixed_position_category = case_when(temp_var > 1 ~ 1,
+                                                    TRUE ~ 0)
+     ) %>% 
+  select(-temp_var)
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Left join to `prep_building` selecting only `supervisor_e_mail_address`.
+
+```{r}
+prep_xx <-
+  prep_building %>% 
+  select(supervisor_e_mail_address) %>% 
+  left_join(prep_a) %>% 
+  mutate(
+    across(
+      .cols = where(is.numeric),
+      .fns = ~replace_na(.,0)
+    )
+  )
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `supervisor_e_mail_address`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(supervisor_e_mail_address)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
 ## Attach characteristics
@@
 ```{r}
-prep_xx <- cohort_first
+cohort_first %>% 
+  group_by(supervisor_e_mail_address) %>% 
+  summarise(
+    across(
+      .cols = c(-where(is.Date),
+                -employee_e_mail_address,
+                -position_category_code,
+                -employee_name,
+                -supervisor_display_name,
+                -date_day_of_week,
+                -position_number,
+                -business_line_2_letter_department_id),
+      .fns = list(dist = n_distinct,mode = getmode),
+      .names = "{.col}_{.fn}"
+    )
+  ) %>% 
+  select(-person_id_mode,
+         -business_line_2_letter_department_id_dist) %>% 
+  # skim()
+  glimpse()
+```
+
+```{r}
+cohort_first %>% 
+  group_by(supervisor_e_mail_address) %>% 
+  summarise(
+    across(
+      .cols = c(grade),
+      .fns = list(min = min, max = max),
+      .names = "{.col}_{.fn}"
+    )
+  ) %>% 
+  # select(-person_id_mode,
+  #        -business_line_2_letter_department_id_dist) %>% 
+  # skim()
+  glimpse()
+```
+
+```{r}
+# prep_xx <- 
+  cohort_ids %>% 
+  select(supervisor_e_mail_address) %>% 
+  distinct() %>% 
+  inner_join(
+    cohort_panel %>% 
+      filter(date >= date_cohort_month_start & date <= date_cohort_month_end),
+    by = c("supervisor_e_mail_address" = "employee_e_mail_address")
+  ) %>% 
+  skim()
 ```

### 2023-05-31 04. Analysis/scripts/02_data_preparation_clusters_team.Rmd
Update 02_data_preparation_clusters_team.Rmd
Completed team and supervisor characteristics section and saved

@@
 ```
-
-# CONTINUE FROM HERE
 
@@
 
-Define `cohort_first` as `prep_xx`.
-
-```{r}
+Collect initial characteristics for supervisors for `check_in_panel` by joining `supervisor_e_mail_address` in `prep_building` to `employee_e_mail_address` and selecting for the first rows for each `supervisor_e_mail_address` by `date`.
+
+```{r}
+prep_a <-
+  prep_building %>%
+  select(supervisor_e_mail_address) %>%
+  distinct() %>%
+  inner_join(
+    check_in_panel,
+    by = c("supervisor_e_mail_address" = "employee_e_mail_address"),
+    suffix = c("", "_of_supervisor")
+  ) %>%
+  arrange(supervisor_e_mail_address, date) %>%
+  group_by(supervisor_e_mail_address) %>%
+  summarise(across(.cols = everything(),
+                   .fns = first)) %>%
+  ungroup()
+```
+
+Review data
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Create initial summary data of the team aggregating `cohort_first` by `supervisor_e_mail_address` and collecting the mode and distinct count for most variables.
+
+```{r}
+prep_b <-
   cohort_first %>%
   group_by(supervisor_e_mail_address) %>%
-  summarise(
-    across(
-      .cols = c(-where(is.Date),
-                -employee_e_mail_address,
-                -position_category_code,
-                -employee_name,
-                -supervisor_display_name,
-                -date_day_of_week,
-                -position_number,
-                -business_line_2_letter_department_id),
-      .fns = list(dist = n_distinct,mode = getmode),
+  summarise(across(
+    .cols = c(
+      -where(is.Date),-employee_e_mail_address,-position_category_code,-employee_name,-supervisor_display_name,-date_day_of_week,-position_number,-business_line_2_letter_department_id
+    ),
+    .fns = list(dist = n_distinct, mode = getmode),
     .names = "{.col}_{.fn}"
-    )
-  ) %>% 
-  select(-person_id_mode,
-         -business_line_2_letter_department_id_dist) %>% 
-  # skim()
-  glimpse()
-```
-
-```{r}
+  )) %>%
+  select(-person_id_mode) %>%
+  ungroup()
+```
+
+Review data
+
+```{r}
+prep_b %>% 
+  skim()
+```
+
+Collect the minimum and maximum GS levels for the team by `supervisor_e_mail_address` from `cohort_first`.
+
+```{r}
+prep_c <-
   cohort_first %>%
   group_by(supervisor_e_mail_address) %>%
-  summarise(
-    across(
+  summarise(across(
     .cols = c(grade),
@@
     .names = "{.col}_{.fn}"
-    )
-  ) %>% 
-  # select(-person_id_mode,
-  #        -business_line_2_letter_department_id_dist) %>% 
-  # skim()
-  glimpse()
-```
-
-```{r}
-# prep_xx <- 
+  )) %>%
+  ungroup()
+```
+
+Review data
+
+```{r}
+prep_c %>% 
+  skim()
+```
+
+Create `prep_xx` by left joining the above to `supervisor_e_mail_address` in `prep_building`.
+
+```{r}
+prep_xx <-
   cohort_ids %>%
@@
   distinct() %>%
-  inner_join(
-    cohort_panel %>% 
-      filter(date >= date_cohort_month_start & date <= date_cohort_month_end),
-    by = c("supervisor_e_mail_address" = "employee_e_mail_address")
-  ) %>% 
-  skim()
+  left_join(prep_a) %>%
+  left_join(prep_b) %>%
+  left_join(prep_c)
 ```
@@
 
-All of these are null correlations, which will address in analysis.
+All of these are null from supervisors that didn't show up in the panel data.
 
@@
 ```{r}
-prep_employees <- prep_building
+prep_team <- prep_building
 ```
@@
 ```{r}
-save(prep_employees, file = file.path(params$google_drive_home,"03. Data Collection","prepared-data",
-          glue::glue("prep_employees_{Sys.Date()}.rdata")))
+save(prep_team, file = file.path(params$google_drive_home,"03. Data Collection","prepared-data",
+          glue::glue("prep_team_{Sys.Date()}.rdata")))
 ```

### 2023-05-31 04. Analysis/scripts/02_data_preparation_clusters_team.R
Create 02_data_preparation_clusters_team.R
Initial commit

@@ -1,0 +1,56 @@
+
+# Start timer -------------------------------------------------------------
+
+tictoc::tic()
+
+# Libraries ---------------------------------------------------------------
+
+library(tidyverse)
+library(lubridate)
+library(purrr)
+
+# Parameters --------------------------------------------------------------
+
+author <-  "Ben Jaques-Leslie"
+project_number <-  2312
+project_name <-  "Occupancy Patterns"
+google_drive_home <-  "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
+data_folder_1 <-  "prepared-data"
+data_file_1 <-  "check_in_panel_2023-04-12.rdata"
+unique_identifier_1 <- c("date","person_id")
+date_cohort_month <-  "2022-03-01"
+observation_window_length_months <-  6
+
+# Determine file name -----------------------------------------------------
+
+file_name <- glue::glue("02-data_preparation-clusters-team-{project_number}-{str_replace_all(str_to_lower(project_name),' ','-')}-{today()}.html")
+
+file_name
+
+# Render data extraction --------------------------------------------------
+
+rmarkdown::render(input = here::here("04. Analysis",
+                                     "scripts",
+                                     "02_data_preparation_clusters_team.Rmd"),
+                  params = list(
+                    author = author,
+                    project_number = project_number,
+                    project_name = project_name,
+                    google_drive_home = google_drive_home,
+                    data_folder_1 = data_folder_1,
+                    data_file_1 = data_file_1,
+                    unique_identifier_1 = unique_identifier_1,
+                    date_cohort_month = date_cohort_month,
+                    observation_window_length_months = observation_window_length_months
+                  ),
+                  output_file =
+                    here::here("04. Analysis",
+                               "output",
+                               'html',
+                               file_name))
+
+
+# End timer ---------------------------------------------------------------
+
+tictoc::toc()
+

### 2023-05-31 04. Analysis/scripts/03-01-data-analysis-employee-categories.Rmd
Create 03-01-data-analysis-employee-categories.Rmd
Initial commit

--- 2023-05-24 04. Analysis/scripts/02_data_preparation_clusters_team.Rmd
@@
 ---
-title: "Data preparation for team category analysis"
+title: "Data analysis for employee categories"
 date: "`r Sys.Date()`"
@@
   data_folder_1: "prepared-data"
-  data_file_1: "check_in_panel_2023-04-12.rdata"
+  data_file_1: "prep_employees_2023-05-24.rdata"
   unique_identifier_1: !r c("date","person_id")
@@
 ```
-
-Updated data type for check-in status.
-
-```{r}
-check_in_panel <- 
-  check_in_panel %>% 
-  mutate(
-    daily_status_imputed = factor(daily_status_imputed),
-    daily_status_imputed =
-      fct_recode(daily_status_imputed,
-                 permanent_departure = "This employee is no longer with the agency (retired, resigned, or other form of permanent departure)")
-  )
-```
-
-Create days of the week for dates.
-
-```{r}
-check_in_panel <- 
-  check_in_panel %>% 
-  mutate(date_day_of_week = wday(date, label = TRUE))
-```
-
-## Creating cohort {.tabset .tabset-pills}
-
-Collect `person_id` and `supervisor_e_mail_address` of employees that worked in `r nice_month_year(date_cohort_month_start)`. If a team member had multiple supervisors, select the first one.
-
-```{r}
-cohort_ids <- 
-  check_in_panel %>% 
-  filter(date >= date_cohort_month_start & date <= date_cohort_month_end) %>% 
-  arrange(person_id,date) %>% 
-  group_by(person_id) %>% 
-  summarise(
-    supervisor_e_mail_address = first(supervisor_e_mail_address)
-  ) %>% 
-  ungroup()
-```
-
-Review.
-
-```{r}
-cohort_ids %>% 
-  skim()
-```
-
-Join with full panel.
-
-```{r}
-cohort_panel <- 
-  cohort_ids %>% 
-  inner_join(check_in_panel) %>% 
-  filter(date >= date_cohort_month_start & date <= date_observation_window_month_end)
-```
-
-Review.
-
-```{r}
-cohort_panel %>% 
-  skim()
-```
-
-Check: These have the same number of unique `person_id`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(person_id)) %>% 
-  pull() ==
-  cohort_panel %>% 
-  summarise(n_distinct(person_id)) %>% 
-  pull()
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  cohort_panel %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Create dataframe of all initial characteristics.
-
-```{r}
-cohort_first <- 
-  cohort_panel %>% 
-  arrange(person_id,date) %>% 
-  group_by(person_id) %>% 
-  summarise(
-    across(
-      .cols = everything(),
-      .fns = first
-    )
-  ) %>% 
-  ungroup()
-```
-
-Review.
-
-```{r}
-cohort_first %>% 
-  skim()
-```
-
-Check: These have the same number of unique `person_id`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(person_id)) %>% 
-  pull() ==
-  cohort_first %>% 
-  summarise(n_distinct(person_id)) %>% 
-  pull()
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  cohort_panel %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Set up `prep_building`.
-
-```{r}
-prep_building <- 
-  cohort_ids %>% 
-  select(supervisor_e_mail_address) %>% 
-  distinct()
-```
-
-## Creating aggregated variables {.tabset .tabset-pills}
-
-### Team, whole period variables
-
-For following variables are aggregated for the whole period for the whole team:
-
--   Proportion of team members working days onsite
-
--   Proportion of team members working days remote
-
--   Number of team members working days
-
-First, calculating the number of days in the observation window.
-
-```{r}
-observation_window_days <- 
-  cohort_panel %>% 
-  summarise(observation_window_days = n_distinct(date)) %>% 
-  ungroup() %>% 
-  pull()
-
-observation_window_days
-```
-
-Now calculating the number of days per team by `daily_status_imputed`.
-Proportions are caluculated for onsite and telework only.
-The calculations are made in two ways in two ways.
-First as a proportion of team working days:
-
-$$
-\frac{\sum_{m=1}^{x}DailyStatusDays_m}{\sum_{m=1}^{x}WorkingDays_m}
-$$
-
-where
-
-$$
-WorkingDays_m = OnsiteDays_m + TeleworkDays_m
-$$
-
-$OnsiteDays_m$ is the number of onsite days for team member $m$ and $TeleworkDays_m$ is the number of telework days for team member $m$. $x$ is number of members on team.
-
-Second as a proportion of days in the observations window:
-
-$$
-\frac{\sum_{m=1}^{x}DailyStatusDays_m}{x\times ObservationWindowDays}
-$$
-
-Now we calculate the values for the data.
-
-First count the number of distinct days per `supervisor_e_mail_address`, `person_id`, and `daily_status_imputed`, then filter to daily status: *Reporting to Job Site* or *Teleworking*.
-
-```{r}
-prep_a <-
-  cohort_panel %>%
-  group_by(supervisor_e_mail_address,person_id,daily_status_imputed,.drop = FALSE) %>% 
-  summarise(working_days = n_distinct(date)) %>% 
-  ungroup() %>% 
-  filter(
-    daily_status_imputed == "Reporting to Job Site" |
-      daily_status_imputed == "Teleworking"
-  )
-```
-
-Review data.
-
-```{r}
-prep_a %>% 
-  skim()
-```
-
-Second, sum the number days by `supervisor_e_mail_address` from dataframe `prep_a`.
-
-```{r}
-prep_b <- 
-  prep_a %>% 
-  group_by(supervisor_e_mail_address) %>% 
-  summarise(
-    working_days = sum(working_days)
-  ) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_b %>% 
-  skim()
-```
-
-Third, sum the number days by `supervisor_e_mail_address` and `daily_status_imputed` from dataframe `prep_a` and reshape the data wide so that statuses are in columns, `daily_status_*`.
-
-```{r}
-prep_c <- 
-  prep_a %>% 
-  group_by(supervisor_e_mail_address,daily_status_imputed) %>% 
-  summarise(
-    working_days = sum(working_days)
-  ) %>% 
-  ungroup() %>% 
-  pivot_wider(values_from = working_days, names_from = daily_status_imputed) %>% 
-  clean_names() %>% 
-  rename_with(~glue::glue("daily_status_{.}"), -supervisor_e_mail_address)
-```
-
-Review data.
-
-```{r}
-prep_c %>% 
-  skim()
-```
-
-Fourth, count the number of unique team members per supervisor.
-
-```{r}
-prep_d <-
-  cohort_panel %>%
-  group_by(supervisor_e_mail_address) %>% 
-  summarise(
-    team_members = n_distinct(person_id)
-  ) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_d %>% 
-  skim()
-```
-
-Join working days, working days per status, and team members into one dataframe by `supervisor_e_mail_address`.
-
-```{r}
-prep_e <- 
-  prep_b %>% 
-  full_join(prep_c) %>% 
-  full_join(prep_d)
-```
-
-Review data.
-
-```{r}
-prep_e %>% 
-  skim()
-```
-
-Calucate `observation_window_days`, `daily_status_reporting_to_job_site_working_prop`, `daily_status_teleworking_working_prop`, `daily_status_reporting_to_job_site_observation_prop`, and `daily_status_teleworking_observation_prop`, then replace missing values with zero.
-
-```{r}
-prep_xx <- 
-  prep_e %>% 
-  mutate(
-    observation_window_days = team_members*observation_window_days,
-    daily_status_reporting_to_job_site_working_prop = daily_status_reporting_to_job_site/working_days,
-    daily_status_teleworking_working_prop = daily_status_teleworking/working_days,
-    daily_status_reporting_to_job_site_observation_prop = daily_status_reporting_to_job_site/observation_window_days,
-    daily_status_teleworking_observation_prop = daily_status_teleworking/observation_window_days
-  ) %>% 
-  mutate(
-    across(
-      .cols = where(is.numeric),
-      .fns = ~replace_na(.,0)
-    )
-  )
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-### Team, day of week variables
-
-For following variables are aggregated for the whole period by day of the week for the whole team:
-
--   Proportion of team members working days remote by the day of the
-    week
-
-#### Proportion of days remote by day of the week
-
-First, calculating the number of days in the observation window.
-
-```{r}
-observation_window_days_day_of_week <- 
-  cohort_panel %>% 
-  group_by(date_day_of_week) %>% 
-  summarise(observation_window_days = n_distinct(date)) %>% 
-  ungroup()
-
-observation_window_days_day_of_week
-```
-
-First count the number of distinct days per `supervisor_e_mail_address`, `date_day_of_week`, `person_id`, and `daily_status_imputed`, then filter to daily status: *Reporting to Job Site* or *Teleworking*.
-
-```{r}
-prep_a <-
-  cohort_panel %>%
-  group_by(supervisor_e_mail_address,person_id,daily_status_imputed,date_day_of_week,.drop = FALSE) %>% 
-  summarise(working_days = n_distinct(date)) %>% 
-  ungroup() %>% 
-  filter(
-    daily_status_imputed == "Reporting to Job Site" |
-      daily_status_imputed == "Teleworking"
-  )
-```
-
-Review data.
-
-```{r}
-prep_a %>% 
-  skim()
-```
-
-Second, sum the number days by `supervisor_e_mail_address` and `date_day_of_week` from dataframe `prep_a`.
-
-```{r}
-prep_b <- 
-  prep_a %>% 
-  group_by(supervisor_e_mail_address,date_day_of_week) %>% 
-  summarise(
-    working_days = sum(working_days)
-  ) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_b %>% 
-  skim()
-```
-
-Third, sum the number days by `supervisor_e_mail_address`, `date_day_of_week` and `daily_status_imputed` from dataframe `prep_a` and reshape the data wide so that statuses are in columns, `daily_status_*`.
-
-```{r}
-prep_c <- 
-  prep_a %>% 
-  group_by(supervisor_e_mail_address,daily_status_imputed,date_day_of_week) %>% 
-  summarise(
-    working_days = sum(working_days)
-  ) %>% 
-  ungroup() %>% 
-  pivot_wider(values_from = working_days, names_from = daily_status_imputed) %>% 
-  clean_names() %>% 
-  rename_with(~glue::glue("daily_status_{.}"), c(-supervisor_e_mail_address,-date_day_of_week))
-```
-
-Review data.
-
-```{r}
-prep_c %>% 
-  skim()
-```
-
-Fourth, count the number of unique team members per `supervisor_e_mail_address` and `date_day_of_week`.
-
-```{r}
-prep_d <-
-  cohort_panel %>%
-  group_by(supervisor_e_mail_address,date_day_of_week) %>% 
-  summarise(
-    team_members = n_distinct(person_id)
-  ) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_d %>% 
-  skim()
-```
-
-Join working days, working days per status, and team members into one dataframe by `supervisor_e_mail_address`.
-
-```{r}
-prep_e <- 
-  prep_b %>% 
-  full_join(prep_c) %>% 
-  full_join(prep_d) %>% 
-  left_join(observation_window_days_day_of_week)
-```
-
-Review data.
-
-```{r}
-prep_e %>% 
-  skim()
-```
-
-Review data by `date_day_of_week`.
-
-```{r}
-prep_e %>% 
-  group_by(date_day_of_week) %>% 
-  skim()
-```
-
-Filter out *Sat* and *Sun* as there are no working days.
-
-```{r}
-prep_f <- 
-  prep_e %>% 
-  filter(date_day_of_week != "Sat" &
-           date_day_of_week != "Sun")
-```
-
-Review data.
-
-```{r}
-prep_f %>% 
-  skim()
-```
-
-Calucate `observation_window_days`, `daily_status_reporting_to_job_site_working_prop`, `daily_status_teleworking_working_prop`, `daily_status_reporting_to_job_site_observation_prop`, and `daily_status_teleworking_observation_prop`, then replace missing values with zero.
-
-```{r}
-prep_g <- 
-  prep_f %>% 
-  mutate(
-    observation_window_days = team_members*observation_window_days,
-    daily_status_reporting_to_job_site_working_prop = daily_status_reporting_to_job_site/working_days,
-    daily_status_teleworking_working_prop = daily_status_teleworking/working_days,
-    daily_status_reporting_to_job_site_observation_prop = daily_status_reporting_to_job_site/observation_window_days,
-    daily_status_teleworking_observation_prop = daily_status_teleworking/observation_window_days
-  ) %>% 
-  mutate(
-    across(
-      .cols = where(is.numeric),
-      .fns = ~replace_na(.,0)
-    )
-  )
-```
-
-Review data.
-
-```{r}
-prep_g %>% 
-  skim()
-```
-
-Now collect only the results for telework.
-
-```{r}
-prep_xx <- 
-  prep_g %>% 
-  select(supervisor_e_mail_address,
-         date_day_of_week,daily_status_teleworking_working_prop,daily_status_teleworking_observation_prop) %>% 
-  pivot_longer(cols = starts_with("daily_status")) %>% 
-  mutate(date_day_of_week = str_to_lower(date_day_of_week)) %>% 
-  unite("name",date_day_of_week,name) %>% 
-  pivot_wider(values_from = value, names_from = name) %>% 
-  mutate(
-    across(
-      .cols = where(is.numeric),
-      .fns = ~replace_na(.,0)
-    )
-  )
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-### Modal size of team over observation window
-
-Calculate number of team members per day by supervisor email.
-
-```{r}
-prep_a <- 
-  cohort_panel %>% 
-  group_by(date,supervisor_e_mail_address) %>% 
-  summarise(team_size = n_distinct(person_id)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_a %>% 
-  skim()
-```
-
-Calculate the mode team size for each `supervisor_e_mail_address`.
-
-```{r}
-prep_xx <- 
-  prep_a %>% 
-  group_by(supervisor_e_mail_address) %>% 
-  summarise(team_size_mode = getmode(team_size)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-### Proportion of team members exiting team
-
-Calculate the number of days and last day of team members by `supervisor_e_mail_address`, and `person_id`.
-
-```{r}
-prep_a <- 
-  cohort_panel %>% 
-  group_by(supervisor_e_mail_address,person_id) %>% 
-  summarise(days = n_distinct(date),
-            last_day = max(date)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_a %>% 
-  skim()
-```
-
-Identify team members that exit by limiting the list above to those who had few than the maximum number of days and whose last day was before the maxium day in the dataframe, then count the number per `supervisor_e_mail_address`.
-
-```{r}
-prep_b <- 
-  prep_a %>% 
-  filter(days < max(days)) %>% 
-  filter(last_day < max(last_day)) %>% 
-  group_by(supervisor_e_mail_address) %>% 
-  summarise(employee_exits = n_distinct(person_id)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_b %>% 
-  skim()
-```
-
-Attach to `prep_building` selecting `supervisor_e_mail_address` and `team_members` from that dataframe to calucalate the proportio of the team exiting.
-
-```{r}
-prep_c <- 
-  prep_building %>% 
-  select(supervisor_e_mail_address, team_members) %>% 
-  distinct() %>% 
-  left_join(prep_b) %>% 
-  mutate(
-    across(
-      .cols = where(is.numeric),
-      .fns = ~replace_na(.,0)
-    )
-  ) %>% 
-  mutate(
-    employee_exits_prop = employee_exits/team_members
-  )
-```
-
-Review data.
-
-```{r}
-prep_c %>% 
-  skim()
-```
-
-Remove `team_members`.
-
-```{r}
-prep_xx <- 
-  prep_c %>% 
-  select(-team_members)
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-### Proportion of observation window the team existed
-
-Calculate the number of days and last day of team members by `supervisor_e_mail_address`.
-
-```{r}
-prep_a <- 
-  cohort_panel %>% 
-  group_by(supervisor_e_mail_address) %>% 
-  summarise(team_days = n_distinct(date)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_a %>% 
-  skim()
-```
-
-Calculate the number of days and last day of team members by `supervisor_e_mail_address`.
-
-```{r}
-prep_xx <- 
-  prep_a %>% 
-  mutate(
-    team_days_prop = team_days/observation_window_days
-  )
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-### Proportion of working days at least two team members co-located
-
-Identify employees who report to the site and collect `person_id`, `dates`, `location`, and `supervisor_e_mail_address`.
-
-```{r}
-prep_a <-
-  cohort_panel %>%
-  filter(daily_status_imputed == "Reporting to Job Site") %>%
-  select(person_id, date, location, supervisor_e_mail_address) %>%
-  distinct()
-```
-
-Review data.
-
-```{r}
-prep_a %>% 
-  skim()
-```
-
-Self left join on `dates`, `location`, and `supervisor_e_mail_address` and filter to rows where the `person_id`s do not match.
-
-```{r}
-prep_b <- 
-  prep_a %>% 
-  left_join(prep_a,
-            by = c("date", "location", "supervisor_e_mail_address"),
-            suffix = c("","_joined")) %>%
-  filter(person_id != person_id_joined)
-```
-
-Review data.
-
-```{r}
-prep_b %>% 
-  skim()
-```
-
-Count dates where co-location occurs by `supervisor_e_mail_address`.
-
-```{r}
-prep_c <- 
-  prep_b %>% 
-  group_by(supervisor_e_mail_address) %>% 
-  summarise(days_colocated_1 = n_distinct(date)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_c %>% 
-  skim()
-```
-
-Full join `working_days` from `prep_building`, calculate proportion of co-located days with at least one team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days`.
-
-```{r}
-prep_xx <- 
-  prep_c %>% 
-  full_join(prep_building %>% 
-              select(supervisor_e_mail_address,working_days)) %>% 
-  mutate(days_colocated_1_working_prop = days_colocated_1/working_days,
-         days_colocated_1_observation_prop = days_colocated_1/observation_window_days) %>% 
-  mutate(
-    across(
-      .cols = where(is.numeric),
-      .fns = ~replace_na(.,0)
-    )
-  ) %>% 
-  select(-working_days)
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-### Proportion of working days supervisor is co-located with at least one team member
-
-Identify employees who report to the site and collect `person_id`, `dates`, `location`, `employee_e_mail_address`, and `supervisor_e_mail_address`.
-
-```{r}
-prep_a <-
-  cohort_panel %>%
-  filter(daily_status_imputed == "Reporting to Job Site") %>%
-  select(person_id, date, location, employee_e_mail_address, supervisor_e_mail_address) %>%
-  distinct()
-```
-
-Review data.
-
-```{r}
-prep_a %>% 
-  skim()
-```
-
-Self inner join on `dates`, `location`, and `supervisor_e_mail_address` equal to `employee_e_mail_address` in the right table, and filter to rows where the `person_id`s do not match.
-
-```{r}
-prep_b <- 
-  prep_a %>% 
-  inner_join(prep_a,
-            by = c("date", "location", "supervisor_e_mail_address" = "employee_e_mail_address"),
-            suffix = c("","_joined")) 
-```
-
-Review data.
-
-```{r}
-prep_b %>% 
-  skim()
-```
-
-Count dates where co-location with supervisor occurs by `supervisor_e_mail_address`.
-
-```{r}
-prep_c <- 
-  prep_b %>% 
-  group_by(supervisor_e_mail_address) %>% 
-  summarise(days_colocated_supervisor = n_distinct(date)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_c %>% 
-  skim()
-```
-
-Full join `working_days` and `observation_window_days` from `prep_building`, calculate proportion of co-located days with at least one team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days` and `observation_window_days`.
-
-```{r}
-prep_xx <- 
-  prep_c %>% 
-  full_join(prep_building %>% 
-              select(supervisor_e_mail_address,working_days,observation_window_days)) %>% 
-  mutate(days_colocated_supervisor_working_prop = days_colocated_supervisor/working_days,
-         days_colocated_supervisor_observation_prop = days_colocated_supervisor/observation_window_days) %>% 
-  mutate(
-    across(
-      .cols = where(is.numeric),
-      .fns = ~replace_na(.,0)
-    )
-  ) %>% 
-  select(-working_days,-observation_window_days)
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-### Proportion of working days entire team is co-located
-
-Identify employees who report to the site and collect `person_id`, `dates`, `location`, and `supervisor_e_mail_address`.
-
-```{r}
-prep_a <-
-  cohort_panel %>%
-  filter(daily_status_imputed == "Reporting to Job Site") %>%
-  select(person_id, date, location, supervisor_e_mail_address) %>%
-  distinct()
-```
-
-Review data.
-
-```{r}
-prep_a %>% 
-  skim()
-```
-
-Count number of team members co-located by `supervisor_e_mail_address`, `location`, and `date` by counting unique `person_id`.
-
-```{r}
-prep_b <- 
-  prep_a %>% 
-  group_by(supervisor_e_mail_address,location, date) %>% 
-  summarise(colocated_team_members = n_distinct(person_id)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_b %>% 
-  skim()
-```
-
-Calculate number of team members per day by supervisor email.
-
-```{r}
-prep_c <- 
-  cohort_panel %>% 
-  group_by(date,supervisor_e_mail_address) %>% 
-  summarise(team_size = n_distinct(person_id)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_c %>% 
-  skim()
-```
-
-Left join co-located team members and teams size, but `date` and `supervisor_e_mail_address`, then filter to when co-located team members is the same size as the team
-
-```{r}
-prep_d <- 
-  prep_b %>% 
-  left_join(prep_c) %>% 
-  filter(colocated_team_members == team_size)
-```
-
-Review data.
-
-```{r}
-prep_d %>% 
-  skim()
-```
-
-Count dates where co-location with whole team occurs by `supervisor_e_mail_address`.
-
-```{r}
-prep_e <- 
-  prep_d %>% 
-  group_by(supervisor_e_mail_address) %>% 
-  summarise(days_colocated_team = n_distinct(date)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_e %>% 
-  skim()
-```
-
-Full join `working_days` and `observation_window_days` from `prep_building`, calculate proportion of co-located days with team member by `working_days` and `observation_window_days`, replace nulls with 0, and remove `working_days` and `observation_window_days`.
-
-```{r}
-prep_xx <- 
-  prep_e %>% 
-  full_join(prep_building %>% 
-              select(supervisor_e_mail_address,working_days,observation_window_days)) %>% 
-  mutate(days_colocated_team_working_prop = days_colocated_team/working_days,
-         days_colocated_team_observation_prop = days_colocated_team/observation_window_days) %>% 
-  mutate(
-    across(
-      .cols = where(is.numeric),
-      .fns = ~replace_na(.,0)
-    )
-  ) %>% 
-  select(-working_days,-observation_window_days)
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-### Proportion of working days entire team is remote
-
-Identify employees who are teleworking and collect `person_id`, `dates`, and `supervisor_e_mail_address`.
-
-```{r}
-prep_a <-
-  cohort_panel %>%
-  filter(daily_status_imputed == "Teleworking") %>%
-  select(person_id, date, supervisor_e_mail_address) %>%
-  distinct()
-```
-
-Review data.
-
-```{r}
-prep_a %>% 
-  skim()
-```
-
-Count number of team members co-located by `supervisor_e_mail_address`, and `date` by counting unique `person_id`.
-
-```{r}
-prep_b <- 
-  prep_a %>% 
-  group_by(supervisor_e_mail_address,date) %>% 
-  summarise(telework_team_members = n_distinct(person_id)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_b %>% 
-  skim()
-```
-
-Calculate number of team members per day by supervisor email.
-
-```{r}
-prep_c <- 
-  cohort_panel %>% 
-  group_by(date,supervisor_e_mail_address) %>% 
-  summarise(team_size = n_distinct(person_id)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_c %>% 
-  skim()
-```
-
-Left join teleworking team members and teams size, by `date` and `supervisor_e_mail_address`, then filter to when teleworking team members is the same size as the team.
-
-```{r}
-prep_d <- 
-  prep_b %>% 
-  left_join(prep_c) %>% 
-  filter(telework_team_members == team_size)
-```
-
-Review data.
-
-```{r}
-prep_d %>% 
-  skim()
-```
-
-Count dates where co-location with whole team occurs by `supervisor_e_mail_address`.
-
-```{r}
-prep_e <- 
-  prep_d %>% 
-  group_by(supervisor_e_mail_address) %>% 
-  summarise(days_telework_team = n_distinct(date)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_e %>% 
-  skim()
-```
-
-Full join `team_days` and `observation_window_days` from `prep_building`, calculate proportion of co-located days with team member by `team_days` and `observation_window_days`, replace nulls with 0, and remove `team_days` and `observation_window_days`.
-
-```{r}
-prep_xx <- 
-  prep_e %>% 
-  full_join(prep_building %>% 
-              select(supervisor_e_mail_address,team_days)) %>% 
-  mutate(days_telework_team_working_prop =  days_telework_team/team_days,
-         days_telework_team_observation_prop = days_telework_team/observation_window_days) %>% 
-  mutate(
-    across(
-      .cols = where(is.numeric),
-      .fns = ~replace_na(.,0)
-    )
-  ) %>% 
-  select(-team_days)
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-# CONTINUE FROM HERE
-
-## Define rule-based groups {.tabset .tabset-pills}
-
-The analysis plan defines ten rule-based groups for analysis:
-
-1.  **All remote** - All team members are 100% remote
-2.  **Routine teleworker** - All team members have
-    `position_category_description`'s *Onsite Flexible* or *Offsite* and
-    work at least two two days per pay period onsite.
-3.  **Onsite Flexible** - All team members are *Onsite Flexible* as
-    defined by `position_category_description` in the roster data
-4.  **Offsite** - All team members are *Offsite* as defined by team
-    members `position_category_description` in the roster data
-5.  **Onsite Required** - All team members are *Onsite Required* as
-    defined by `position_category_description` in the roster data
-6.  **Mixed position categories** - Team members are different position
-    categories as as defined by `position_category_description` in the
-    roster data
-7.  **Primarily remote** - Teams that work remotely above the 95th
-    percentile <!-- could be 75th -->
-8.  **Mostly remote** - Teams that work remotely between the median and
-    the 95th percentile <!-- could be 75th -->
-9.  **Mostly onsite** - Teams that work remotely between 5th percentile
-    and the median <!-- could be 25th -->
-10. **Primarily onsite** - Teams that work remotely below the 5th
-    percentile <!-- could be 75th -->
-
-Below the variables for the groups are created.
-
-### All remote
-
-Define workers with 100% of their time as **all remote**.
-
-```{r}
-prep_xx <- 
-  prep_building %>% 
-  mutate(
-    rule_based_all_remote = case_when(
-      daily_status_teleworking_working_prop == 1 ~ 1,
-                                      TRUE ~ 0)
-  ) %>% 
-  select(supervisor_e_mail_address,starts_with("rule_based_"))
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-### Primarily, mostly onsite and remote
-
-First, calculate the quantiles for probabilities 0.50 and 0.95.
-
-```{r}
-prep_a <- 
-  prep_building %>% 
-  summarise(
-    across(
-      .cols = c(daily_status_reporting_to_job_site_working_prop,daily_status_teleworking_working_prop,
-                daily_status_reporting_to_job_site_observation_prop,daily_status_teleworking_observation_prop),
-      .fns = list(q_95 = ~quantile(.,probs = .95),
-                  q_50 = ~quantile(.,probs = .50))
-    )
-  )
-```
-
-Review data.
-
-```{r}
-prep_a %>% 
-  skim()
-```
-
-Use the quantiles above to create new variables for `primarily_` and `mostly_` working remote or onsite.
-
-```{r}
-prep_xx <-
-  prep_building %>%
-  select(
-    supervisor_e_mail_address,
-    daily_status_reporting_to_job_site_working_prop,
-    daily_status_teleworking_working_prop,
-    daily_status_reporting_to_job_site_observation_prop,
-    daily_status_teleworking_observation_prop
-  ) %>%
-  mutate(
-    rule_based_primarily_reporting_to_job_site_working =
-      case_when(
-        daily_status_reporting_to_job_site_working_prop >= prep_a$daily_status_reporting_to_job_site_working_prop_q_95 ~ 1,
-        TRUE ~ 0
-      ),
-    rule_based_primarily_teleworking_working =
-      case_when(
-        daily_status_teleworking_working_prop >= prep_a$daily_status_teleworking_working_prop_q_95 ~ 1,
-        TRUE ~ 0
-      ),
-    rule_based_primarily_reporting_to_job_site_observation =
-      case_when(
-        daily_status_reporting_to_job_site_observation_prop >= prep_a$daily_status_reporting_to_job_site_observation_prop_q_95 ~ 1,
-        TRUE ~ 0
-      ),
-    rule_based_primarily_teleworking_observation =
-      case_when(
-        daily_status_teleworking_observation_prop >= prep_a$daily_status_teleworking_observation_prop_q_95 ~ 1,
-        TRUE ~ 0
-      ),
-    rule_based_mostly_reporting_to_job_site_working =
-      case_when(
-        daily_status_reporting_to_job_site_working_prop >= prep_a$daily_status_reporting_to_job_site_working_prop_q_50 ~ 1,
-        TRUE ~ 0
-      ),
-    rule_based_mostly_teleworking_working =
-      case_when(
-        daily_status_teleworking_working_prop >= prep_a$daily_status_teleworking_working_prop_q_50 ~ 1,
-        TRUE ~ 0
-      ),
-    rule_based_mostly_reporting_to_job_site_observation =
-      case_when(
-        daily_status_reporting_to_job_site_observation_prop >= prep_a$daily_status_reporting_to_job_site_observation_prop_q_50 ~ 1,
-        TRUE ~ 0
-      ),
-    rule_based_mostly_teleworking_observation =
-      case_when(
-        daily_status_teleworking_observation_prop >= prep_a$daily_status_teleworking_observation_prop_q_50 ~ 1,
-        TRUE ~ 0
-      ),
-  ) %>%
-  select(supervisor_e_mail_address, starts_with("rule_based_"))
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-### Position description categories
-
-```{r, eval=FALSE}
-prep_b <- 
-  cohort_panel %>% 
-  group_by(person_id) %>% 
-  summarise(
-    across(
-      .cols = position_category_description,
-      .fns = getmode
-    )
-  )
-
-prep_c <- 
-  cohort_first %>% 
-  select(person_id,position_category_description)
-
-prep_c %>% 
-  inner_join(prep_b, by = "person_id") %>% 
-  filter(position_category_description.x != position_category_description.y)
-```
-
-Identify the `position_category_description` at the beginning of the observation window and count number of team members per category by `supervisor_e_mail_address`.
-
-```{r}
-prep_a <- 
-  cohort_panel %>% 
-  group_by(supervisor_e_mail_address,position_category_description) %>% 
-  summarise(team_members = n_distinct(person_id)) %>% 
-  ungroup() %>% 
-  pivot_wider(values_from = team_members, names_from = position_category_description,
-              names_prefix = "rule_based_position_category_") %>% 
-  clean_names()
-```
-
-Review data.
-
-```{r}
-prep_a %>% 
-  skim()
-```
-
-Inner join with `prep_building` selecting `supervisor_e_mail_address`, and `team_members`.
-
-```{r}
-prep_b <- 
-  prep_building %>% 
-  select(supervisor_e_mail_address,team_members) %>% 
-  inner_join(prep_a)
-```
-
-Review data.
-
-```{r}
-prep_b %>% 
-  skim()
-```
-
-Create indicators for when the number of team members equals the number of members in a specific category.
-
-```{r}
-prep_c <- 
-  prep_b %>% 
-  mutate(
-    across(
-      .cols = starts_with("rule_based_position_category_"),
-      .fns = ~case_when(. == team_members ~ 1,
-                        TRUE ~ 0)
-    )
-  )
-```
-
-Review data.
-
-```{r}
-prep_c %>% 
-  skim()
-```
-
-Left join to `prep_building` selecting only `supervisor_e_mail_address` and remove `team_members`.
-
-```{r}
-prep_xx <-
-  prep_building %>% 
-  select(supervisor_e_mail_address) %>% 
-  left_join(prep_c) %>% 
-  select(-team_members)
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-### Teleworker
-
-First define pay periods based on this: https://www.gsa.gov/cdnstatic/GSA_Payroll_Calendar_2022_Revised.pdf. File is also saved in `r file.path(params$google_drive_home,"04. Analysis","documents")`.
-
-```{r}
-prep_a <- 
-  tibble(
-  date = seq.Date(from = ymd("2022-01-01"),
-         to = ymd("2022-12-31"),
-         by = "2 weeks")
-) %>% 
-  rownames_to_column(var = "period_number") 
-```
-
-Review data.
-
-```{r}
-prep_a %>% 
-  skim()
-```
-
-Second, create a dataframe of all the days of the year.
-
-```{r}
-prep_b <- 
-  tibble(
-  date = seq.Date(from = ymd("2022-01-01"),
-         to = ymd("2022-12-31"),
-         by = "days")
-)
-```
-
-Review data.
-
-```{r}
-prep_b %>% 
-  skim()
-```
-
-Third, left join the pay periods dataframe (`prep_a`) to the days of the year (`prep_b`), then fill the null `period_number` values with the entry above.
-
-```{r}
-prep_c <- 
-  prep_b %>% 
-  left_join(prep_a) %>% 
-  fill(period_number, .direction = "down")
-```
-Review data.
-
-```{r}
-prep_c %>% 
-  skim()
-```
-
-Fourth, take the cohort panel (`cohort_panel`) select `person_id`, `date`, and `daily_status_imputed` and left join to calendar dataframe with filled `period_number` (`prep_c`) on `date`.
-
-```{r}
-prep_d <- 
-  cohort_panel %>% 
-  select(person_id,date, daily_status_imputed) %>% 
-  left_join(prep_c)
-```
-
-Review data.
-
-```{r}
-prep_d %>% 
-  skim()
-```
-
-Fifth, count the number of unique days by `person_id`, `daily_status_imputed`, and `period_number`.
-
-```{r}
-prep_e <- 
-      prep_d %>% 
-  group_by(person_id,daily_status_imputed,period_number) %>% 
-  summarise(days = n_distinct(date)) %>% 
-  ungroup()
-```
-
-Review data.
-
-```{r}
-prep_e %>% 
-  skim()
-```
-
-Sixth, filter to only see observations where `daily_status_imputed` is "Reporting to Job Site" and create `telework_onsite_minimum` to be 1 when `days` is greater than or equal to 2, that is employees have at least two days in the office in that pay period.
-Then, calculate the mean `telework_onsite_minimum` (`telework_onsite_minimum_mean`) per employee.
-Those where this is 1 are in the office at least two days per pay period for the whole observation window.
-Lastly, create `telework_onsite_minimum` to be 1 when `telework_onsite_minimum_mean` is 1.
-
-```{r}
-prep_f <- 
-  prep_e %>% 
-  filter(daily_status_imputed == "Reporting to Job Site") %>% 
-  mutate(
-    telework_onsite_minimum = case_when(days >= 2 ~ 1,
-                                        TRUE ~ 0)
-  ) %>% 
-  group_by(person_id) %>% 
-  summarise(
-    telework_onsite_minimum_mean = mean(telework_onsite_minimum)
-  ) %>% 
-  ungroup() %>% 
-  mutate(
-    telework_onsite_minimum = case_when(telework_onsite_minimum_mean == 1 ~ 1,
-                                        TRUE ~ 0)
-  )
-```
-
-Review data.
-
-```{r}
-prep_f %>% 
-  skim()
-```
-
-Seventh, select `person_id`, and `position_category_description` from the beginning of the observation window (`cohort_first`) and left join the above (`prep_f`).
-Then, create `rule_based_telework_onsite_minimum` when `telework_onsite_minimum` is 1 and `position_category_description` is *Onsite Flexible* or *Offsite*.
-
-```{r}
-prep_g <- 
-  cohort_first %>% 
-  select(person_id,position_category_description) %>% 
-  left_join(prep_f) %>% 
-  mutate(
-    rule_based_telework_onsite_minimum = 
-      case_when(telework_onsite_minimum == 1 & position_category_description == "Onsite Flexible" ~ 1,
-                telework_onsite_minimum == 1 & position_category_description == "Offsite" ~ 1,
-                TRUE ~ 0)
-  ) %>%
-  select(person_id, starts_with("rule_based_"))
-```
-
-Review data.
-
-```{r}
-prep_g %>% 
-  skim()
-```
-
-Left join to `cohort_ids`.
-
-```{r}
-prep_h <- 
-  cohort_ids %>% 
-  left_join(prep_g)
-```
-
-Review data.
-
-```{r}
-prep_h %>% 
-  skim()
-```
-
-```{r}
-prep_h %>% 
-  filter(rule_based_telework_onsite_minimum == 1) %>% 
-  group_by(supervisor_e_mail_address) %>% 
-  summarise(rule_based_telework_onsite_minimum = n_distinct(person_id))
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-## Attach characteristics
-
-Define `cohort_first` as `prep_xx`.
-
-```{r}
-prep_xx <- cohort_first
-```
-
-Review data.
-
-```{r}
-prep_xx %>% 
-  skim()
-```
-
-Check: These have the same number of unique `supervisor_e_mail_address`.
-
-```{r}
-cohort_ids %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull() ==
-  prep_xx %>% 
-  summarise(n_distinct(supervisor_e_mail_address)) %>% 
-  pull()
-```
-
-Join to `prep_building`.
-
-```{r}
-prep_building <- 
-  prep_building %>% 
-  left_join(prep_xx)
-```
-
-## Addressing blanks, nulls, and other values
-
-Created a dataframe of variable metadata.
-
-```{r}
-column_meta_data <- 
-  prep_building %>% 
-  contents()
-
-column_meta_data <- 
-  column_meta_data$contents %>% 
-  as.data.frame()
-
-column_meta_data <-
-  column_meta_data %>% 
-  rownames_to_column(var = "variable")
-
-column_meta_data <- 
-  column_meta_data %>% 
-  mutate(
-    nulls_by_variable = case_when(NAs > 0 ~ TRUE,
-                                  NAs == 0 ~ FALSE)
-  )
-
-column_meta_data
-```
-
-Counting top 10 values for all character or factor columns to identify other common values.
-
-```{r}
-values_count <- 
-  prep_building %>% 
-  select(where(is.character) | where(is.factor)) %>% 
-  names()
-
-values_count %>% 
-  map(~count(prep_building,!!sym(.)) %>% 
-  arrange(desc(n)) %>%
-  slice_head(n = 10))
-
-```
-
-No obvious values.
-
-Function that checks whether there are blanks for different variables
-
-```{r}
-blank_check <- function(in_data,in_variable_name)
-{
-  check_01 <- 
-  in_data %>% 
-    filter(!!sym(in_variable_name) == "") %>% 
-  distinct()
-
-out <- nrow(check_01) > 0
-
-return(out)
-}
-```
-
-Checking blanks for each variable in the dataframe.
-
-```{r}
-blanks_by_variable <- 
-  column_meta_data %>% 
-  pull(variable) %>% 
-  map_lgl(~blank_check(in_data = prep_building,.))
-
-blanks_by_variable
-```
-
-Add this to the `column_meta_data` dataframe.
-
-```{r}
-column_meta_data <- 
-  column_meta_data %>% 
-  add_column(
-    blanks_by_variable = blanks_by_variable
-  )
-
-column_meta_data
-```
-
-Create dataframe of only variables that have blanks.
-
-```{r}
-problem_variables <- 
-  column_meta_data %>% 
-  filter(blanks_by_variable | nulls_by_variable)
-
-problem_variables
-```
-
-All of these are null correlations, which will address in analysis.
-
-## Creating final dataframe
-
-```{r}
-prep_employees <- prep_building
-```
-
-```{r}
-rm(prep_building)
-```
-
-## Save data {.tabset .tabset-pills}
-
-```{r}
-save(prep_employees, file = file.path(params$google_drive_home,"03. Data Collection","prepared-data",
-          glue::glue("prep_employees_{Sys.Date()}.rdata")))
-```
-
-Remove all data elements.
-
-```{r}
-rm(list = ls())
-gc()
-```
-
-## Extraction time {.tabset .tabset-pills}
-
-```{r}
-tictoc::toc()
-```

### 2023-05-31 04. Analysis/scripts/03-01-data-analysis-employee-categories.Rmd
Update 03-01-data-analysis-employee-categories.Rmd
Scaled variables for clusters and began testing cluster analysis

@@
 library(ggthemes)
+library(tidymodels)
 ```
@@
 date_observation_window_month_end <- ceiling_date(date_observation_window_month_start,unit = "month") %>% rollbackward()
+```
+
+```{r}
+set.seed(27)
 ```
@@
 ```{r}
-check_in_panel %>% 
+prep_employees %>% 
   skim()
 ```
+
+## Scale data {.tabset .tabset-pills}
+
+```{r}
+d <- 
+  prep_employees %>% 
+  mutate(
+    across(
+      .cols = c(daily_status_reporting_to_job_site_working_prop,
+                daily_status_teleworking_working_prop,
+                daily_status_reporting_to_job_site_observation_prop,
+                daily_status_teleworking_observation_prop,
+                starts_with("mon_"),
+                starts_with("tue_"),
+                starts_with("wed_"),
+                starts_with("thu_"),
+                starts_with("fri_"),
+                working_days,
+                team_size_mode,
+                starts_with("days_colocated_"),
+                starts_with("days_telework_"),
+                -days_colocated_1,
+                -days_colocated_supervisor,
+                -days_colocated_team,
+                -days_telework_team
+                ),
+      .fns = list(scale = scale,rank = rank),
+      .names = "{.col}_{.fn}"
+    )
+  )
+```
+
+Review data.
+
+```{r}
+d %>% 
+  skim()
+```
+
+## Create clusters {.tabset .tabset-pills}
+
+### Scale
+
+#### Observation
+
+##### Correlation telework
+
+```{r}
+prep_a <-
+  d %>%
+  select(
+    person_id,
+    ends_with("_scale"),
+    -contains("_working_prop_"),
+    -contains("_cor_status_"),
+    -contains("_prop_pairs_"),
+    ) %>% 
+  drop_na()
+```
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+```{r}
+prep_b <- 
+  prep_a %>% 
+  select(-person_id)
+```
+
+Review data.
+
+```{r}
+prep_b %>% 
+  skim()
+```
+
+```{r}
+kclusts <- 
+  tibble(k = 1:9) %>%
+  mutate(
+    kclust = map(k, ~kmeans(prep_b, .x)),
+    tidied = map(kclust, tidy),
+    glanced = map(kclust, glance),
+    augmented = map(kclust, augment, prep_b)
+  )
+
+```
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+```
+
+```{r}
+p1 <- 
+  ggplot(assignments, aes(x = days_colocated_1_observation_prop_scale, y = days_colocated_supervisor_observation_prop_scale)) +
+  geom_point(aes(color = .cluster), alpha = 0.8) + 
+  facet_wrap(~ k)
+p1
+
+```
+
+```{r}
+ggplot(clusterings, aes(k, tot.withinss)) +
+  geom_line() +
+  geom_point()
+
+```
+
+```{r}
+clusterings %>% 
+  select(k,tot.withinss) %>% 
+  mutate(
+    tot.withinss_lag = lag(tot.withinss),
+    diff = tot.withinss_lag - tot.withinss,
+    change = diff/tot.withinss_lag,
+    change_lag = lag(change),
+    diff_2 = change_lag - change
+  )
+```
+
+```{r}
+kclust <- kmeans(points, centers = 3)
+kclust
+#> K-means clustering with 3 clusters of sizes 148, 51, 101
+#> 
+#> Cluster means:
+#>        x1    x2
+#> 1  0.0885  1.05
+#> 2 -3.1429 -2.00
+#> 3  5.0040 -1.05
+#> 
+#> Clustering vector:
+#>   [1] 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3
+#>  [38] 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3
+#>  [75] 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 3 1 1 1 1 1 1 1 1 1 1 1
+#> [112] 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1
+#> [149] 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1
+#> [186] 1 1 1 1 1 1 1 1 1 1 1 1 1 3 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1
+#> [223] 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 1 2 1 1 1 1 1 1 2 2 2 2 2 2 2 2 2
+#> [260] 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2 2
+#> [297] 2 2 2 2
+#> 
+#> Within cluster sum of squares by cluster:
+#> [1] 299 109 243
+#>  (between_SS / total_SS =  82.5 %)
+#> 
+#> Available components:
+#> 
+#> [1] "cluster"      "centers"      "totss"        "withinss"     "tot.withinss"
+#> [6] "betweenss"    "size"         "iter"         "ifault"
+summary(kclust)
+#>              Length Class  Mode   
+#> cluster      300    -none- numeric
+#> centers        6    -none- numeric
+#> totss          1    -none- numeric
+#> withinss       3    -none- numeric
+#> tot.withinss   1    -none- numeric
+#> betweenss      1    -none- numeric
+#> size           3    -none- numeric
+#> iter           1    -none- numeric
+#> ifault         1    -none- numeric
+
+```
+
+##### Correlation status
+
+##### Proportion pairs
+
+#### Working
+
+##### Correlation telework
+
+##### Correlation status
+
+##### Proportion pairs
+
+### Rank
+
+#### Observation
+
+##### Correlation telework
+
+##### Correlation status
+
+##### Proportion pairs
+
+#### Working
+
+##### Correlation telework
+
+##### Correlation status
+
+##### Proportion pairs

### 2023-06-01 04. Analysis/scripts/03-01-data-analysis-employee-cluster-identification.Rmd
Create 03-01-data-analysis-employee-cluster-identification.Rmd
Initial commit

---
title: "Data analysis for employee categories"
date: "`r Sys.Date()`"
output: 
  html_document:
    theme: united
    highlight: tango
    code_folding: hide
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
  data_folder_1: "prepared-data"
  data_file_1: "prep_employees_2023-05-24.rdata"
  unique_identifier_1: !r c("date","person_id")
  date_cohort_month: "2022-03-01"
  observation_window_length_months: 6
  in_number_of_clusters_start: 1
  in_number_of_clusters_end: 10

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
tictoc::tic()
if(!("arsenal" %in% installed.packages()[,"Package"]))
{
  install.packages("arsenal")
}
if(!("oesrrr" %in% installed.packages()[,"Package"]))
{
  devtools::install_github(repo = "GSA/oesrrr")
}
library(oesrrr)
library(tidyverse)
library(janitor)
library(skimr)
library(DataExplorer)
library(readr)
library(arsenal)
library(Hmisc)
library(readxl)
library(flextable)
library(ggthemes)
library(tidymodels)
```

```{r cohort dates}
date_cohort_month_start <- ymd(params$date_cohort_month)
date_cohort_month_end <- ceiling_date(date_cohort_month_start,unit = "month") %>% rollbackward()
date_observation_window_month_start <- date_cohort_month_start %m+% months(params$observation_window_length_months)
date_observation_window_month_end <- ceiling_date(date_observation_window_month_start,unit = "month") %>% rollbackward()
```

```{r}
set.seed(27)
```

# Data preparation {.tabset .tabset-pills}

**Project number**: `r params$project_number`

**Project name**: `r params$project_name`

**Author**: `r params$author`

**Data folder 1**: `r params$data_folder_1`

**Data file 1**: `r params$data_file_1`

**Unique identifier for data file 1**: `r params$unique_identifier_1`

**Cohort start month**: `r nice_month_year(date_cohort_month_start)`

**Observation window**: `r nice_month_year(date_cohort_month_start)` to `r nice_month_year(date_observation_window_month_end)` (`r params$observation_window_length_months` months)

**Number of clusters**: Testing `r params$in_number_of_clusters_start` to `r params$in_number_of_clusters_end`

## Load data {.tabset .tabset-pills}

Load `r params$data_file_1` from `r params$data_folder_1` data folder.

```{r}
load(file = file.path(params$google_drive_home,"03. Data Collection",params$data_folder_1,params$data_file_1))
```

Review.

```{r}
prep_employees %>% 
  skim()
```

## Scale data {.tabset .tabset-pills}

Scaling the data in two ways:

1.  Normalize - Data will have the mean that that element subtracted and
    then divided by the standard deviation, using the `scale()`
    function[^2]

2.  Rank - The rank of each element will be used instead of the element.

[^2]: [Documentation for the scale
    function.](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/scale)

```{r}
d <- 
  prep_employees %>% 
  mutate(
    across(
      .cols = c(daily_status_reporting_to_job_site_working_prop,
                daily_status_teleworking_working_prop,
                daily_status_reporting_to_job_site_observation_prop,
                daily_status_teleworking_observation_prop,
                starts_with("mon_"),
                starts_with("tue_"),
                starts_with("wed_"),
                starts_with("thu_"),
                starts_with("fri_"),
                working_days,
                team_size_mode,
                starts_with("days_colocated_"),
                starts_with("days_telework_"),
                -days_colocated_1,
                -days_colocated_supervisor,
                -days_colocated_team,
                -days_telework_team
                ),
      .fns = list(scale = scale,rank = rank),
      .names = "{.col}_{.fn}"
    )
  )
```

Review data.

```{r}
d %>% 
  skim()
```

## Create clusters {.tabset .tabset-pills}

### Functions

#### Selecting data for cluster analysis

```{r}
#' Selects the correct columns for employee cluster analysis
#'
#' @param in_data Data to use
#' @param in_scale_or_rank Option for which scaling procedure: "scale" (normalization) or "rank" (rank order)
#' @param in_working_or_observation_window Option for proportion denominator: "observation" (proportion of entire observation window) or "working" (proportion of period employ was working onsite or via telework)
#' @param in_weekday_correlation Option for inter weekday relationship: "correlation telework" (telework correlation between days of the week), "correlation status" (work status correlation based on ordered work status by days of the week), or "proportion pairs" (proportion of telework in pairs)
#'
#' @return Dataframe with only selected columns and dropped null observations
#' @export
#'
#' @examples
select_cluster_cols <-
  function(in_data,
           in_scale_or_rank,
           in_working_or_observation_window,
           in_weekday_correlation)
  {
    stopifnot(in_scale_or_rank %in% c("scale", "rank"))
    stopifnot(in_working_or_observation_window %in% c("observation", "working"))
    stopifnot(in_weekday_correlation %in% c("correlation telework", "correlation status","proportion pairs"))

    if (in_scale_or_rank == "scale" &
        in_working_or_observation_window == "observation" &
        in_weekday_correlation == "correlation telework")
    {
      step_01 <-
        in_data %>%
        select(
          person_id,
          ends_with("_scale"),
          -contains("_working_prop_"),
          -contains("_cor_status_"),
          -contains("_prop_pairs_"),
        ) %>%
        drop_na()
    }

    if (in_scale_or_rank == "rank" &
        in_working_or_observation_window == "observation" &
        in_weekday_correlation == "correlation telework")
    {
      step_01 <-
        in_data %>%
        select(
          person_id,
          ends_with("_rank"),
          -contains("_working_prop_"),
          -contains("_cor_status_"),
          -contains("_prop_pairs_"),
        ) %>%
        drop_na()
    }

    if (in_scale_or_rank == "scale" &
        in_working_or_observation_window == "working" &
        in_weekday_correlation == "correlation telework")
    {
      step_01 <-
        in_data %>%
        select(
          person_id,
          ends_with("_scale"),
          -contains("_observation_"),
          -contains("_cor_status_"),
          -contains("_prop_pairs_"),
        ) %>%
        drop_na()
    }

    if (in_scale_or_rank == "rank" &
        in_working_or_observation_window == "working" &
        in_weekday_correlation == "correlation telework")
    {
      step_01 <-
        in_data %>%
        select(
          person_id,
          ends_with("_rank"),
          -contains("_observation_"),
          -contains("_cor_status_"),
          -contains("_prop_pairs_"),
        ) %>%
        drop_na()
    }

    if (in_scale_or_rank == "scale" &
        in_working_or_observation_window == "observation" &
        in_weekday_correlation == "correlation status")
    {
      step_01 <-
        in_data %>%
        select(
          person_id,
          ends_with("_scale"),
          -contains("_working_prop_"),
          -contains("_cor_telework_"),
          -contains("_prop_pairs_"),
        ) %>%
        drop_na()
    }

    if (in_scale_or_rank == "rank" &
        in_working_or_observation_window == "observation" &
        in_weekday_correlation == "correlation status")
    {
      step_01 <-
        in_data %>%
        select(
          person_id,
          ends_with("_rank"),
          -contains("_working_prop_"),
          -contains("_cor_telework_"),
          -contains("_prop_pairs_"),
        ) %>%
        drop_na()
    }

    if (in_scale_or_rank == "scale" &
        in_working_or_observation_window == "working" &
        in_weekday_correlation == "correlation status")
    {
      step_01 <-
        in_data %>%
        select(
          person_id,
          ends_with("_scale"),
          -contains("_observation_"),
          -contains("_cor_telework_"),
          -contains("_prop_pairs_"),
        ) %>%
        drop_na()
    }

    if (in_scale_or_rank == "rank" &
        in_working_or_observation_window == "working" &
        in_weekday_correlation == "correlation status")
    {
      step_01 <-
        in_data %>%
        select(
          person_id,
          ends_with("_rank"),
          -contains("_observation_"),
          -contains("_cor_telework_"),
          -contains("_prop_pairs_"),
        ) %>%
        drop_na()
    }

    if (in_scale_or_rank == "scale" &
        in_working_or_observation_window == "observation" &
        in_weekday_correlation == "proportion pairs")
    {
      step_01 <-
        in_data %>%
        select(
          person_id,
          ends_with("_scale"),
          -contains("_working_prop_"),
          -contains("_cor_status_"),
          -contains("cor_telework"),
        ) %>%
        drop_na()
    }

    if (in_scale_or_rank == "rank" &
        in_working_or_observation_window == "observation" &
        in_weekday_correlation == "proportion pairs")
    {
      step_01 <-
        in_data %>%
        select(
          person_id,
          ends_with("_rank"),
          -contains("_working_prop_"),
          -contains("_cor_status_"),
          -contains("cor_telework"),
        ) %>%
        drop_na()
    }

    if (in_scale_or_rank == "scale" &
        in_working_or_observation_window == "working" &
        in_weekday_correlation == "proportion pairs")
    {
      step_01 <-
        in_data %>%
        select(
          person_id,
          ends_with("_scale"),
          -contains("_observation_"),
          -contains("_cor_status_"),
          -contains("cor_telework"),
        ) %>%
        drop_na()
    }

    if (in_scale_or_rank == "rank" &
        in_working_or_observation_window == "working" &
        in_weekday_correlation == "proportion pairs")
    {
      step_01 <-
        in_data %>%
        select(
          person_id,
          ends_with("_rank"),
          -contains("_observation_"),
          -contains("_cor_status_"),
          -contains("cor_telework"),
        ) %>%
        drop_na()
    }

    out <- 
      step_01 %>% 
      as_tibble()

    return(out)
  }
```

#### Making clusters of different sizes

```{r}
#' Make employee clusters of a variety of sizes and different specifications
#'
#' @param in_data Data to use
#' @param in_scale_or_rank Option for which scaling procedure: "scale" (normalization) or "rank" (rank order)
#' @param in_working_or_observation_window Option for proportion denominator: "observation" (proportion of entire observation window) or "working" (proportion of period employ was working onsite or via telework)
#' @param in_weekday_correlation Option for inter weekday relationship: "correlation telework" (telework correlation between days of the week), "correlation status" (work status correlation based on ordered work status by days of the week), or "proportion pairs" (proportion of telework in pairs)
#' @param in_number_of_clusters_start Minimum number of clusters to test
#' @param in_number_of_clusters_end Maximum number of clusters to test
#'
#' @return Dataframe of clusters and associatied statistics
#' @export
#'
#' @examples
make_clusters <-
  function(in_data,
           in_scale_or_rank,
           in_working_or_observation_window,
           in_weekday_correlation,
           in_number_of_clusters_start,
           in_number_of_clusters_end)
  {
    stopifnot(in_scale_or_rank %in% c("scale", "rank"))
    stopifnot(in_working_or_observation_window %in% c("observation", "working"))
    stopifnot(
      in_weekday_correlation %in% c(
        "correlation telework",
        "correlation status",
        "proportion pairs"
      )
    )
    stopifnot(in_number_of_clusters_start >= 1)
    stopifnot(in_number_of_clusters_start <= in_number_of_clusters_end)

    step_01 <-
      in_data %>%
      select_cluster_cols(
        in_scale_or_rank = in_scale_or_rank,
        in_working_or_observation_window = in_working_or_observation_window,
        in_weekday_correlation = in_weekday_correlation
      )

    print(glue::glue("Review data for step 1. {Sys.time()}"))

    step_01 %>%
      skim() %>%
      print()

    print(glue::glue("Remove person_id. {Sys.time()}"))

    step_02 <-
      step_01 %>%
      select(-person_id)

    print(glue::glue("Review data for step 2. {Sys.time()}"))

    step_02 %>%
      skim() %>%
      print()

    print(
      glue::glue(
        "Create clusters of the data from {in_number_of_clusters_start} to {in_number_of_clusters_end}. {Sys.time()}"
      )
    )

    out <-
      tibble(k = in_number_of_clusters_start:in_number_of_clusters_end) %>%
      mutate(
        kclust = map(k, ~ kmeans(step_02, .x)),
        tidied = map(kclust, tidy),
        glanced = map(kclust, glance),
        augmented = map(kclust, augment, step_01)
      )

    return(out)
  }
```

#### Making clusters of different sizes, but only for `d` and adding specification

```{r}
make_clusters_d <- function(in_specification,
                            in_scale_or_rank,
                            in_working_or_observation_window,
                            in_weekday_correlation,
                            in_number_of_clusters_start,
                            in_number_of_clusters_end)
{
  make_clusters(
    in_data = d,
    in_scale_or_rank = in_scale_or_rank,
    in_working_or_observation_window = in_working_or_observation_window,
    in_weekday_correlation = in_weekday_correlation,
    in_number_of_clusters_start = in_number_of_clusters_start,
    in_number_of_clusters_end = in_number_of_clusters_end
  ) %>%
    mutate(specification = in_specification)
}
```

### Create clusters

#### Create dataframe of all permutations

This table shows all permutations of scaling (normalization, or rank), denominators for proportions (observation window or working days), and types of inter day correlations.

```{r}
specs <- 
  tibble(
  in_scale_or_rank = c(rep("scale", 6), rep("rank", 6)),
  in_working_or_observation_window = rep(c(rep("observation", 3), rep("working", 3)), 2),
  in_weekday_correlation = rep(
    c(
      "correlation telework",
      "correlation status",
      "proportion pairs"
    ),
    4
  ),
  in_number_of_clusters_start = rep(params$in_number_of_clusters_start, 12),
  in_number_of_clusters_end = rep(params$in_number_of_clusters_end, 12)
) %>% 
  unite(col = "in_specification",everything(),remove = FALSE)
```

Review data.

```{r}
specs
```

#### Create clusters

Iterate over `specs` creating and collecting dataframe of clusters from all of the above specifications.

```{r}
kclusts <- 
  specs %>%
  pmap_dfr(make_clusters_d)
```

## Save data {.tabset .tabset-pills}

File name.

```{r}
file_name <- glue::glue("clusters-employee-{Sys.Date()}.rdata")
file_name
```

```{r}
save(kclusts, file = file.path(params$google_drive_home,"03. Data Collection","prepared-data",file_name))
```

Remove all data elements.

```{r}
rm(list = ls())
gc()
```

## Extraction time {.tabset .tabset-pills}

```{r}
tictoc::toc()
```

### 2023-06-01 04. Analysis/scripts/03-01-data-analysis-employee-categories.Rmd
Update 03-01-data-analysis-employee-categories.Rmd
Developing functions and analysis that will appear in other files

--- 2023-05-31 04. Analysis/scripts/03-01-data-analysis-employee-categories.Rmd
@@
 ```{r}
-check_in_panel %>% 
+prep_employees %>% 
   skim()
 ```
+
+## Scale data {.tabset .tabset-pills}
+
+```{r}
+d <- 
+  prep_employees %>% 
+  mutate(
+    across(
+      .cols = c(daily_status_reporting_to_job_site_working_prop,
+                daily_status_teleworking_working_prop,
+                daily_status_reporting_to_job_site_observation_prop,
+                daily_status_teleworking_observation_prop,
+                starts_with("mon_"),
+                starts_with("tue_"),
+                starts_with("wed_"),
+                starts_with("thu_"),
+                starts_with("fri_"),
+                working_days,
+                team_size_mode,
+                starts_with("days_colocated_"),
+                starts_with("days_telework_"),
+                -days_colocated_1,
+                -days_colocated_supervisor,
+                -days_colocated_team,
+                -days_telework_team
+                ),
+      .fns = list(scale = scale,rank = rank),
+      .names = "{.col}_{.fn}"
+    )
+  )
+```
+
+Review data.
+
+```{r}
+d %>% 
+  skim()
+```
+
+## Create clusters {.tabset .tabset-pills}
+
+### Functions
+
+#### Selecting data for cluster analysis
+
+```{r}
+#' Selects the correct columns for employee cluster analysis
+#'
+#' @param in_data Data to use
+#' @param in_scale_or_rank Option for which scaling procedure: "scale" (normalization) or "rank" (rank order)
+#' @param in_working_or_observation_window Option for proportion denominator: "observation" (proportion of entire observation window) or "working" (proportion of period employ was working onsite or via telework)
+#' @param in_weekday_correlation Option for inter weekday relationship: "correlation telework" (telework correlation between days of the week), "correlation status" (work status correlation based on ordered work status by days of the week), or "proportion pairs" (proportion of telework in pairs)
+#'
+#' @return Dataframe with only selected columns and dropped null observations
+#' @export
+#'
+#' @examples
+select_cluster_cols <-
+  function(in_data,
+           in_scale_or_rank,
+           in_working_or_observation_window,
+           in_weekday_correlation)
+  {
+    stopifnot(in_scale_or_rank %in% c("scale", "rank"))
+    stopifnot(in_working_or_observation_window %in% c("observation", "working"))
+    stopifnot(in_weekday_correlation %in% c("correlation telework", "correlation status","proportion pairs"))
+
+    if (in_scale_or_rank == "scale" &
+        in_working_or_observation_window == "observation" &
+        in_weekday_correlation == "correlation telework")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_scale"),
+          -contains("_working_prop_"),
+          -contains("_cor_status_"),
+          -contains("_prop_pairs_"),
+        ) %>%
+        drop_na()
+    }
+
+    if (in_scale_or_rank == "rank" &
+        in_working_or_observation_window == "observation" &
+        in_weekday_correlation == "correlation telework")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_rank"),
+          -contains("_working_prop_"),
+          -contains("_cor_status_"),
+          -contains("_prop_pairs_"),
+        ) %>%
+        drop_na()
+    }
+
+    if (in_scale_or_rank == "scale" &
+        in_working_or_observation_window == "working" &
+        in_weekday_correlation == "correlation telework")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_scale"),
+          -contains("_observation_"),
+          -contains("_cor_status_"),
+          -contains("_prop_pairs_"),
+        ) %>%
+        drop_na()
+    }
+
+    if (in_scale_or_rank == "rank" &
+        in_working_or_observation_window == "working" &
+        in_weekday_correlation == "correlation telework")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_rank"),
+          -contains("_observation_"),
+          -contains("_cor_status_"),
+          -contains("_prop_pairs_"),
+        ) %>%
+        drop_na()
+    }
+
+    if (in_scale_or_rank == "scale" &
+        in_working_or_observation_window == "observation" &
+        in_weekday_correlation == "correlation status")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_scale"),
+          -contains("_working_prop_"),
+          -contains("_cor_telework_"),
+          -contains("_prop_pairs_"),
+        ) %>%
+        drop_na()
+    }
+
+    if (in_scale_or_rank == "rank" &
+        in_working_or_observation_window == "observation" &
+        in_weekday_correlation == "correlation status")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_rank"),
+          -contains("_working_prop_"),
+          -contains("_cor_telework_"),
+          -contains("_prop_pairs_"),
+        ) %>%
+        drop_na()
+    }
+
+    if (in_scale_or_rank == "scale" &
+        in_working_or_observation_window == "working" &
+        in_weekday_correlation == "correlation status")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_scale"),
+          -contains("_observation_"),
+          -contains("_cor_telework_"),
+          -contains("_prop_pairs_"),
+        ) %>%
+        drop_na()
+    }
+
+    if (in_scale_or_rank == "rank" &
+        in_working_or_observation_window == "working" &
+        in_weekday_correlation == "correlation status")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_rank"),
+          -contains("_observation_"),
+          -contains("_cor_telework_"),
+          -contains("_prop_pairs_"),
+        ) %>%
+        drop_na()
+    }
+
+    if (in_scale_or_rank == "scale" &
+        in_working_or_observation_window == "observation" &
+        in_weekday_correlation == "proportion pairs")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_scale"),
+          -contains("_working_prop_"),
+          -contains("_cor_status_"),
+          -contains("cor_telework"),
+        ) %>%
+        drop_na()
+    }
+
+    if (in_scale_or_rank == "rank" &
+        in_working_or_observation_window == "observation" &
+        in_weekday_correlation == "proportion pairs")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_rank"),
+          -contains("_working_prop_"),
+          -contains("_cor_status_"),
+          -contains("cor_telework"),
+        ) %>%
+        drop_na()
+    }
+
+    if (in_scale_or_rank == "scale" &
+        in_working_or_observation_window == "working" &
+        in_weekday_correlation == "proportion pairs")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_scale"),
+          -contains("_observation_"),
+          -contains("_cor_status_"),
+          -contains("cor_telework"),
+        ) %>%
+        drop_na()
+    }
+
+    if (in_scale_or_rank == "rank" &
+        in_working_or_observation_window == "working" &
+        in_weekday_correlation == "proportion pairs")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_rank"),
+          -contains("_observation_"),
+          -contains("_cor_status_"),
+          -contains("cor_telework"),
+        ) %>%
+        drop_na()
+    }
+
+    out <- 
+      step_01 %>% 
+      as_tibble()
+
+    return(out)
+  }
+```
+
+#### Making clusters of different sizes
+
+```{r}
+#' Make employee clusters of a variety of sizes and different specifications
+#'
+#' @param in_data Data to use
+#' @param in_scale_or_rank Option for which scaling procedure: "scale" (normalization) or "rank" (rank order)
+#' @param in_working_or_observation_window Option for proportion denominator: "observation" (proportion of entire observation window) or "working" (proportion of period employ was working onsite or via telework)
+#' @param in_weekday_correlation Option for inter weekday relationship: "correlation telework" (telework correlation between days of the week), "correlation status" (work status correlation based on ordered work status by days of the week), or "proportion pairs" (proportion of telework in pairs)
+#' @param in_number_of_clusters_start Minimum number of clusters to test
+#' @param in_number_of_clusters_end Maximum number of clusters to test
+#'
+#' @return Dataframe of clusters and associatied statistics
+#' @export
+#'
+#' @examples
+make_clusters <-
+  function(in_data,
+           in_scale_or_rank,
+           in_working_or_observation_window,
+           in_weekday_correlation,
+           in_number_of_clusters_start,
+           in_number_of_clusters_end)
+  {
+    stopifnot(in_scale_or_rank %in% c("scale", "rank"))
+    stopifnot(in_working_or_observation_window %in% c("observation", "working"))
+    stopifnot(
+      in_weekday_correlation %in% c(
+        "correlation telework",
+        "correlation status",
+        "proportion pairs"
+      )
+    )
+    stopifnot(in_number_of_clusters_start >= 1)
+    stopifnot(in_number_of_clusters_start <= in_number_of_clusters_end)
+
+    step_01 <-
+      in_data %>%
+      select_cluster_cols(
+        in_scale_or_rank = in_scale_or_rank,
+        in_working_or_observation_window = in_working_or_observation_window,
+        in_weekday_correlation = in_weekday_correlation
+      )
+
+    print(glue::glue("Review data for step 1. {Sys.time()}"))
+
+    step_01 %>%
+      skim() %>%
+      print()
+
+    print(glue::glue("Remove person_id. {Sys.time()}"))
+
+    step_02 <-
+      step_01 %>%
+      select(-person_id)
+
+    print(glue::glue("Review data for step 2. {Sys.time()}"))
+
+    step_02 %>%
+      skim() %>%
+      print()
+
+    print(
+      glue::glue(
+        "Create clusters of the data from {in_number_of_clusters_start} to {in_number_of_clusters_end}. {Sys.time()}"
+      )
+    )
+
+    out <-
+      tibble(k = in_number_of_clusters_start:in_number_of_clusters_end) %>%
+      mutate(
+        kclust = map(k, ~ kmeans(step_02, .x)),
+        tidied = map(kclust, tidy),
+        glanced = map(kclust, glance),
+        augmented = map(kclust, augment, step_01)
+      )
+
+    return(out)
+  }
+```
+
+```{r}
+make_clusters_d <- function(
+    in_specification,
+    in_scale_or_rank,
+                            in_working_or_observation_window,
+                            in_weekday_correlation,
+                            in_number_of_clusters_start,
+                            in_number_of_clusters_end)
+{
+  make_clusters(
+    in_data = d,
+    in_scale_or_rank = in_scale_or_rank,
+    in_working_or_observation_window = in_working_or_observation_window,
+    in_weekday_correlation = in_weekday_correlation,
+    in_number_of_clusters_start = in_number_of_clusters_start,
+    in_number_of_clusters_end = in_number_of_clusters_end
+  ) %>% 
+    mutate(specification = in_specification)
+}
+```
+
+```{r}
+specs <- 
+  tibble(
+  in_scale_or_rank = c(rep("scale", 6), rep("rank", 6)),
+  in_working_or_observation_window = rep(c(rep("observation", 3), rep("working", 3)), 2),
+  in_weekday_correlation = rep(
+    c(
+      "correlation telework",
+      "correlation status",
+      "proportion pairs"
+    ),
+    4
+  ),
+  in_number_of_clusters_start = rep(1, 12),
+  in_number_of_clusters_end = rep(10, 12)
+) %>% 
+  unite(col = "in_specification",everything(),remove = FALSE)
+```
+
+```{r}
+specs
+```
+
+```{r}
+# specs[1,] %>% 
+  pmap(specs[1:2,]$in_scale_or_rank,specs[1:2,]$in_working_or_observation_window,specs[1:2,]$in_weekday_correlation,
+       specs[1:2,]$in_number_of_clusters_start,specs[1:2,]$in_number_of_clusters_end,make_clusters_d)
+```
+
+```{r}
+kclusts <- 
+  specs[1,] %>%
+  pmap_dfr(make_clusters_d)
+
+```
+
+### Scale
+
+#### Observation
+
+##### Correlation telework
+
+```{r}
+kclusts <- d %>%
+   make_clusters(
+    in_scale_or_rank = "scale",
+    in_working_or_observation_window = "observation",
+    in_weekday_correlation = "correlation telework",
+    in_number_of_clusters_start = 1,
+    in_number_of_clusters_end = 10
+  )
+```
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+```
+
+```{r}
+ggplot(clusterings, aes(k, tot.withinss)) +
+  geom_line() +
+  geom_point()
+
+```
+
+```{r}
+prep_01 <- clusterings %>% 
+  select(k,tot.withinss) %>% 
+  mutate(
+    tot.withinss_lag = lag(tot.withinss),
+    rate_of_change = tot.withinss - tot.withinss_lag,
+    rate_of_change_lag = lag(rate_of_change),
+    acceleration = rate_of_change - rate_of_change_lag
+  )
+
+prep_01
+```
+
+##### Correlation status
+
+```{r}
+kclusts <- d %>%
+   make_clusters(
+    in_scale_or_rank = "scale",
+    in_working_or_observation_window = "observation",
+    in_weekday_correlation = "correlation status",
+    in_number_of_clusters_start = 1,
+    in_number_of_clusters_end = 10
+  )
+```
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+```
+
+```{r}
+ggplot(clusterings, aes(k, tot.withinss)) +
+  geom_line() +
+  geom_point()
+
+```
+
+```{r}
+prep_01 <- clusterings %>% 
+  select(k,tot.withinss) %>% 
+  mutate(
+    tot.withinss_lag = lag(tot.withinss),
+    rate_of_change = tot.withinss - tot.withinss_lag,
+    rate_of_change_lag = lag(rate_of_change),
+    acceleration = rate_of_change - rate_of_change_lag
+  )
+
+prep_01
+```
+
+##### Proportion pairs
+
+```{r}
+kclusts <- d %>%
+   make_clusters(
+    in_scale_or_rank = "scale",
+    in_working_or_observation_window = "observation",
+    in_weekday_correlation = "proportion pairs",
+    in_number_of_clusters_start = 1,
+    in_number_of_clusters_end = 10
+  )
+```
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+```
+
+```{r}
+ggplot(clusterings, aes(k, tot.withinss)) +
+  geom_line() +
+  geom_point()
+
+```
+
+```{r}
+prep_01 <- clusterings %>% 
+  select(k,tot.withinss) %>% 
+  mutate(
+    tot.withinss_lag = lag(tot.withinss),
+    rate_of_change = tot.withinss - tot.withinss_lag,
+    rate_of_change_lag = lag(rate_of_change),
+    acceleration = rate_of_change - rate_of_change_lag
+  )
+
+prep_01
+```
+
+#### Working
+
+##### Correlation telework
+
+```{r}
+kclusts <- d %>%
+   make_clusters(
+    in_scale_or_rank = "scale",
+    in_working_or_observation_window = "working",
+    in_weekday_correlation = "correlation telework",
+    in_number_of_clusters_start = 1,
+    in_number_of_clusters_end = 10
+  )
+```
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+```
+
+```{r}
+ggplot(clusterings, aes(k, tot.withinss)) +
+  geom_line() +
+  geom_point()
+
+```
+
+```{r}
+prep_01 <- clusterings %>% 
+  select(k,tot.withinss) %>% 
+  mutate(
+    tot.withinss_lag = lag(tot.withinss),
+    rate_of_change = tot.withinss - tot.withinss_lag,
+    rate_of_change_lag = lag(rate_of_change),
+    acceleration = rate_of_change - rate_of_change_lag
+  )
+
+prep_01
+```
+
+##### Correlation status
+
+```{r}
+kclusts <- d %>%
+   make_clusters(
+    in_scale_or_rank = "scale",
+    in_working_or_observation_window = "working",
+    in_weekday_correlation = "correlation status",
+    in_number_of_clusters_start = 1,
+    in_number_of_clusters_end = 10
+  )
+```
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+```
+
+```{r}
+ggplot(clusterings, aes(k, tot.withinss)) +
+  geom_line() +
+  geom_point()
+
+```
+
+```{r}
+prep_01 <- clusterings %>% 
+  select(k,tot.withinss) %>% 
+  mutate(
+    tot.withinss_lag = lag(tot.withinss),
+    rate_of_change = tot.withinss - tot.withinss_lag,
+    rate_of_change_lag = lag(rate_of_change),
+    acceleration = rate_of_change - rate_of_change_lag
+  )
+
+prep_01
+```
+
+##### Proportion pairs
+
+```{r}
+kclusts <- d %>%
+   make_clusters(
+    in_scale_or_rank = "scale",
+    in_working_or_observation_window = "working",
+    in_weekday_correlation = "proportion pairs",
+    in_number_of_clusters_start = 1,
+    in_number_of_clusters_end = 10
+  )
+```
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+```
+
+```{r}
+ggplot(clusterings, aes(k, tot.withinss)) +
+  geom_line() +
+  geom_point()
+
+```
+
+```{r}
+prep_01 <- clusterings %>% 
+  select(k,tot.withinss) %>% 
+  mutate(
+    tot.withinss_lag = lag(tot.withinss),
+    rate_of_change = tot.withinss - tot.withinss_lag,
+    rate_of_change_lag = lag(rate_of_change),
+    acceleration = rate_of_change - rate_of_change_lag
+  )
+
+prep_01
+```
+
+### Rank
+
+#### Observation
+
+##### Correlation telework
+
+```{r}
+kclusts <- d %>%
+   make_clusters(
+    in_scale_or_rank = "rank",
+    in_working_or_observation_window = "observation",
+    in_weekday_correlation = "correlation telework",
+    in_number_of_clusters_start = 1,
+    in_number_of_clusters_end = 10
+  )
+```
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+```
+
+```{r}
+ggplot(clusterings, aes(k, tot.withinss)) +
+  geom_line() +
+  geom_point()
+
+```
+
+```{r}
+prep_01 <- clusterings %>% 
+  select(k,tot.withinss) %>% 
+  mutate(
+    tot.withinss_lag = lag(tot.withinss),
+    rate_of_change = tot.withinss - tot.withinss_lag,
+    rate_of_change_lag = lag(rate_of_change),
+    acceleration = rate_of_change - rate_of_change_lag
+  )
+
+prep_01
+```
+
+##### Correlation status
+
+```{r}
+kclusts <- d %>%
+   make_clusters(
+    in_scale_or_rank = "rank",
+    in_working_or_observation_window = "observation",
+    in_weekday_correlation = "correlation status",
+    in_number_of_clusters_start = 1,
+    in_number_of_clusters_end = 10
+  )
+```
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+```
+
+```{r}
+ggplot(clusterings, aes(k, tot.withinss)) +
+  geom_line() +
+  geom_point()
+
+```
+
+```{r}
+prep_01 <- clusterings %>% 
+  select(k,tot.withinss) %>% 
+  mutate(
+    tot.withinss_lag = lag(tot.withinss),
+    rate_of_change = tot.withinss - tot.withinss_lag,
+    rate_of_change_lag = lag(rate_of_change),
+    acceleration = rate_of_change - rate_of_change_lag
+  )
+
+prep_01
+```
+
+##### Proportion pairs
+
+```{r}
+kclusts <- d %>%
+   make_clusters(
+    in_scale_or_rank = "rank",
+    in_working_or_observation_window = "observation",
+    in_weekday_correlation = "proportion pairs",
+    in_number_of_clusters_start = 1,
+    in_number_of_clusters_end = 10
+  )
+```
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+```
+
+```{r}
+ggplot(clusterings, aes(k, tot.withinss)) +
+  geom_line() +
+  geom_point()
+
+```
+
+```{r}
+prep_01 <- clusterings %>% 
+  select(k,tot.withinss) %>% 
+  mutate(
+    tot.withinss_lag = lag(tot.withinss),
+    rate_of_change = tot.withinss - tot.withinss_lag,
+    rate_of_change_lag = lag(rate_of_change),
+    acceleration = rate_of_change - rate_of_change_lag
+  )
+
+prep_01
+```
+
+#### Working
+
+##### Correlation telework
+
+```{r}
+kclusts <- d %>%
+   make_clusters(
+    in_scale_or_rank = "rank",
+    in_working_or_observation_window = "working",
+    in_weekday_correlation = "correlation telework",
+    in_number_of_clusters_start = 1,
+    in_number_of_clusters_end = 10
+  )
+```
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+```
+
+```{r}
+ggplot(clusterings, aes(k, tot.withinss)) +
+  geom_line() +
+  geom_point()
+
+```
+
+```{r}
+prep_01 <- clusterings %>% 
+  select(k,tot.withinss) %>% 
+  mutate(
+    tot.withinss_lag = lag(tot.withinss),
+    rate_of_change = tot.withinss - tot.withinss_lag,
+    rate_of_change_lag = lag(rate_of_change),
+    acceleration = rate_of_change - rate_of_change_lag
+  )
+
+prep_01
+```
+
+##### Correlation status
+
+```{r}
+kclusts <- d %>%
+   make_clusters(
+    in_scale_or_rank = "rank",
+    in_working_or_observation_window = "working",
+    in_weekday_correlation = "correlation status",
+    in_number_of_clusters_start = 1,
+    in_number_of_clusters_end = 10
+  )
+```
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+```
+
+```{r}
+ggplot(clusterings, aes(k, tot.withinss)) +
+  geom_line() +
+  geom_point()
+
+```
+
+```{r}
+prep_01 <- clusterings %>% 
+  select(k,tot.withinss) %>% 
+  mutate(
+    tot.withinss_lag = lag(tot.withinss),
+    rate_of_change = tot.withinss - tot.withinss_lag,
+    rate_of_change_lag = lag(rate_of_change),
+    acceleration = rate_of_change - rate_of_change_lag
+  )
+
+prep_01
+```
+
+##### Proportion pairs
+
+```{r}
+kclusts <- d %>%
+   make_clusters(
+    in_scale_or_rank = "rank",
+    in_working_or_observation_window = "working",
+    in_weekday_correlation = "proportion pairs",
+    in_number_of_clusters_start = 1,
+    in_number_of_clusters_end = 10
+  )
+```
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+```
+
+```{r}
+ggplot(clusterings, aes(k, tot.withinss)) +
+  geom_line() +
+  geom_point()
+
+```
+
+```{r}
+prep_01 <- clusterings %>% 
+  select(k,tot.withinss) %>% 
+  mutate(
+    tot.withinss_lag = lag(tot.withinss),
+    rate_of_change = tot.withinss - tot.withinss_lag,
+    rate_of_change_lag = lag(rate_of_change),
+    acceleration = rate_of_change - rate_of_change_lag
+  )
+
+prep_01
+```

### 2023-06-01 04. Analysis/scripts/03-01-data-analysis-employee-cluster-identification.R
Create 03-01-data-analysis-employee-cluster-identification.R
Initial commit

@@ -1,0 +1,60 @@
+
+# Start timer -------------------------------------------------------------
+
+tictoc::tic()
+
+# Libraries ---------------------------------------------------------------
+
+library(tidyverse)
+library(lubridate)
+library(purrr)
+
+# Parameters --------------------------------------------------------------
+
+author <-  "Ben Jaques-Leslie"
+project_number <-  2312
+project_name <-  "Occupancy Patterns"
+google_drive_home <-  "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
+data_folder_1 <-  "prepared-data"
+data_file_1 <-  "prep_employees_2023-05-24.rdata"
+unique_identifier_1 <- c("date","person_id")
+date_cohort_month <-  "2022-03-01"
+observation_window_length_months <-  6
+in_number_of_clusters_start <- 1
+in_number_of_clusters_end <- 10
+
+# Determine file name -----------------------------------------------------
+
+file_name <- glue::glue("03-01-data-analysis-employee-cluster-identification-{project_number}-{str_replace_all(str_to_lower(project_name),' ','-')}-{today()}.html")
+
+file_name
+
+# Render data extraction --------------------------------------------------
+
+rmarkdown::render(input = here::here("04. Analysis",
+                                     "scripts",
+                                     "03-01-data-analysis-employee-cluster-identification.Rmd"),
+                  params = list(
+                    author = author,
+                    project_number = project_number,
+                    project_name = project_name,
+                    google_drive_home = google_drive_home,
+                    data_folder_1 = data_folder_1,
+                    data_file_1 = data_file_1,
+                    unique_identifier_1 = unique_identifier_1,
+                    date_cohort_month = date_cohort_month,
+                    observation_window_length_months = observation_window_length_months,
+                    in_number_of_clusters_start = in_number_of_clusters_start,
+                    in_number_of_clusters_end = in_number_of_clusters_end
+                  ),
+                  output_file =
+                    here::here("04. Analysis",
+                               "output",
+                               'html',
+                               file_name))
+
+
+# End timer ---------------------------------------------------------------
+
+tictoc::toc()
+

### 2023-06-07 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Initial commit
Mainly worked on decriptive statistics. Other file is to review the different numbers and types of clusters.

--- 2023-06-01 04. Analysis/scripts/03-01-data-analysis-employee-cluster-identification.Rmd
@@
 ---
-title: "Data analysis for employee categories"
+title: "Data analysis for employee cluster descriptive statistics"
 date: "`r Sys.Date()`"
@@
   data_folder_1: "prepared-data"
-  data_file_1: "prep_employees_2023-05-24.rdata"
-  unique_identifier_1: !r c("date","person_id")
-  date_cohort_month: "2022-03-01"
-  observation_window_length_months: 6
-  in_number_of_clusters_start: 1
-  in_number_of_clusters_end: 10
+  data_file_1: "clusters-employee-2023-06-01.rdata"
+  in_number_of_clusters: 5
+  in_specification: "scale_working_proportion_pairs_1_10"
 
@@
 
-**Unique identifier for data file 1**: `r params$unique_identifier_1`
+**Number of clusters**: `r params$in_number_of_clusters`
 
-**Cohort start month**: `r nice_month_year(date_cohort_month_start)`
-
-**Observation window**: `r nice_month_year(date_cohort_month_start)` to `r nice_month_year(date_observation_window_month_end)` (`r params$observation_window_length_months` months)
-
-**Number of clusters**: Testing `r params$in_number_of_clusters_start` to `r params$in_number_of_clusters_end`
+**Specification** `r params$in_specification`
 
@@
 ```{r}
-prep_employees %>% 
+kclusts %>% 
   skim()
+```
+
+## Select and unnest data {.tabset .tabset-pills}
+
+### Filter to specification and cluster
+
+Filter to data with `r params$in_number_of_clusters` clusters with specification `r params$in_specification`.
+
+```{r}
+clust <- 
+  kclusts %>% 
+  filter(
+    k == params$in_number_of_clusters &
+      specification == params$in_specification
+  )
+```
+
+### Unnest
+
+Filter to data with `r params$in_number_of_clusters` clusters with specification `r params$in_specification`.
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
 ```

### 2023-06-07 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Initial commit
Mainly worked on decriptive statistics. Other file is to review the different numbers and types of clusters.

--- 2023-06-07 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
@@
   data_file_1: "clusters-employee-2023-06-01.rdata"
+  data_file_2: "prep_employees_2023-05-24.rdata"
   in_number_of_clusters: 5
@@
   install.packages("arsenal")
+}
+if(!("geomtextpath" %in% installed.packages()[,"Package"]))
+{
+  install.packages("geomtextpath")
 }
@@
 ```{r cohort dates}
-date_cohort_month_start <- ymd(params$date_cohort_month)
-date_cohort_month_end <- ceiling_date(date_cohort_month_start,unit = "month") %>% rollbackward()
-date_observation_window_month_start <- date_cohort_month_start %m+% months(params$observation_window_length_months)
-date_observation_window_month_end <- ceiling_date(date_observation_window_month_start,unit = "month") %>% rollbackward()
-```
-
-```{r}
-set.seed(27)
+# date_cohort_month_start <- ymd(params$date_cohort_month)
+# date_cohort_month_end <- ceiling_date(date_cohort_month_start,unit = "month") %>% rollbackward()
+# date_observation_window_month_start <- date_cohort_month_start %m+% months(params$observation_window_length_months)
+# date_observation_window_month_end <- ceiling_date(date_observation_window_month_start,unit = "month") %>% rollbackward()
 ```
@@
 **Data file 1**: `r params$data_file_1`
+
+**Data file 2**: `r params$data_file_2`
 
@@
 kclusts %>% 
+  skim()
+```
+
+Load `r params$data_file_2` from `r params$data_folder_1` data folder.
+
+```{r}
+load(file = file.path(params$google_drive_home,"03. Data Collection",params$data_folder_1,params$data_file_2))
+```
+
+Review.
+
+```{r}
+prep_employees %>% 
   skim()
@@
 clusters <- 
-  kclusts %>%
+  clust %>%
   unnest(cols = c(tidied))
@@
 assignments <- 
-  kclusts %>% 
+  clust %>% 
   unnest(cols = c(augmented))
@@
 clusterings <- 
-  kclusts %>%
+  clust %>%
   unnest(cols = c(glanced))
@@
 ```
+
+```{r}
+assignments %>% 
+  glimpse()
+```
+
+### Join assignments to employee data
+
+```{r}
+d <-
+  assignments %>%
+  select(k, person_id, .cluster, specification) %>%
+  full_join(prep_employees) %>% 
+  mutate(
+    .cluster = fct_na_value_to_level(.cluster, level = "(Missing)")
+  )
+```
+Review data.
+
+```{r}
+d %>% 
+  skim()
+```
+
+## Work pattern statistics {.tabset .tabset-pills}
+
+```{r}
+summaries <- function(in_data,...)
+{
+  in_data %>% 
+  group_by(...) %>% 
+  summarise(
+    across(
+      .cols = c(daily_status_teleworking,daily_status_reporting_to_job_site,
+                daily_status_teleworking_working_prop,daily_status_reporting_to_job_site_working_prop,
+                daily_status_teleworking_observation_prop,daily_status_reporting_to_job_site_observation_prop,
+                starts_with("mon_daily_"),
+                starts_with("tue_daily_"),
+                starts_with("wed_daily_"),
+                starts_with("thu_daily_"),
+                starts_with("fri_daily_"),
+                ends_with("_cor_telework"),
+                ends_with("_cor_status"),
+                ends_with("prop_pairs"),
+                team_size_mode,
+                starts_with("days_colocated"),
+                starts_with("days_telework"),
+                working_days
+                ),
+      .fns = ~mean(.,na.rm = TRUE)
+    )
+  ) %>% 
+    mutate(
+      statistic = "mean"
+    )
+}
+
+filter_rule_base <- function(in_summaries_data,in_filter)
+{
+  filt_var_mod <- enquo(in_filter) 
+  in_summaries_data %>% 
+     dplyr::filter((!!filt_var_mod) == 1) %>% 
+    pivot_longer(cols = !!filt_var_mod) %>% 
+    mutate(
+      temp = str_remove(name,"rule_based_"),
+      temp = str_replace_all(temp,"_"," "),
+      temp = str_to_sentence(temp),
+      group = glue::glue("Rule-based: {temp}")
+    ) %>% 
+    select(-name, -value,-temp)
+}
+
+summaries_rule_based <- function(in_data,in_rule_based_var)
+{
+  d %>% 
+    summaries({{in_rule_based_var}}) %>% 
+    filter_rule_base({{in_rule_based_var}})
+}
+
+prep_a <- bind_rows(
+  d %>%
+    summaries() %>%
+    mutate(group = "Whole cohort"),
+  d %>%
+    summaries(.cluster) %>%
+    mutate(group = glue::glue("Cluster: {.cluster}")) %>%
+    select(-.cluster),
+  d %>% 
+    summaries_rule_based(rule_based_all_remote),
+  d %>% 
+    summaries_rule_based(rule_based_primarily_teleworking_observation),
+  d %>% 
+    summaries_rule_based(rule_based_primarily_teleworking_working),
+  d %>% 
+    summaries_rule_based(rule_based_primarily_reporting_to_job_site_observation),
+  d %>% 
+    summaries_rule_based(rule_based_primarily_reporting_to_job_site_working),
+  d %>% 
+    summaries_rule_based(rule_based_mostly_teleworking_observation),
+  d %>% 
+    summaries_rule_based(rule_based_mostly_teleworking_working),
+  d %>% 
+    summaries_rule_based(rule_based_mostly_reporting_to_job_site_observation),
+  d %>% 
+    summaries_rule_based(rule_based_mostly_reporting_to_job_site_working),
+  d %>% 
+    summaries_rule_based(rule_based_position_category_missing),
+  d %>% 
+    summaries_rule_based(rule_based_position_category_onsite_flexible),
+  d %>% 
+    summaries_rule_based(rule_based_position_category_offsite),
+  d %>% 
+    summaries_rule_based(rule_based_position_category_onsite_required),
+  d %>% 
+    summaries_rule_based(rule_based_position_category_position_has_changed),
+  d %>% 
+    summaries_rule_based(rule_based_position_category_not_specified),
+  d %>% 
+    summaries_rule_based(rule_based_telework_onsite_minimum),
+)
+```
+
+### Daily telework
+
+```{r}
+prep_a %>% 
+  select(group,statistic,starts_with("daily_status_teleworking")) %>% 
+  rename_all(.funs = ~str_to_sentence(str_replace_all(.,"_"," "))) %>% 
+  flextable() %>% 
+   colformat_double(
+    big.mark = ",", decimal.mark = ".",
+    digits = 2,
+    na_str = "na") %>% 
+  autofit() %>% 
+  theme_zebra()
+```
+
+### Daily telework by day of week
+
+#### Monday
+
+```{r}
+prep_a %>% 
+  select(group,statistic,starts_with("mon_daily_status_teleworking")) %>% 
+  rename_all(.funs = ~str_to_sentence(str_replace_all(.,"_"," "))) %>% 
+  flextable() %>% 
+   colformat_double(
+    big.mark = ",", decimal.mark = ".",
+    digits = 2,
+    na_str = "na") %>% 
+  autofit() %>% 
+  theme_zebra()
+```
+
+#### Tuesday
+
+```{r}
+prep_a %>% 
+  select(group,statistic,starts_with("tue_daily_status_teleworking")) %>% 
+  rename_all(.funs = ~str_to_sentence(str_replace_all(.,"_"," "))) %>% 
+  flextable() %>% 
+   colformat_double(
+    big.mark = ",", decimal.mark = ".",
+    digits = 2,
+    na_str = "na") %>% 
+  autofit() %>% 
+  theme_zebra()
+```
+
+#### Wednesday
+
+```{r}
+prep_a %>% 
+  select(group,statistic,starts_with("wed_daily_status_teleworking")) %>% 
+  rename_all(.funs = ~str_to_sentence(str_replace_all(.,"_"," "))) %>% 
+  flextable() %>% 
+   colformat_double(
+    big.mark = ",", decimal.mark = ".",
+    digits = 2,
+    na_str = "na") %>% 
+  autofit() %>% 
+  theme_zebra()
+```
+
+#### Thursday
+
+```{r}
+prep_a %>% 
+  select(group,statistic,starts_with("thu_daily_status_teleworking")) %>% 
+  rename_all(.funs = ~str_to_sentence(str_replace_all(.,"_"," "))) %>% 
+  flextable() %>% 
+   colformat_double(
+    big.mark = ",", decimal.mark = ".",
+    digits = 2,
+    na_str = "na") %>% 
+  autofit() %>% 
+  theme_zebra()
+```
+
+#### Friday
+
+```{r}
+prep_a %>% 
+  select(group,statistic,starts_with("fri_daily_status_teleworking")) %>% 
+  rename_all(.funs = ~str_to_sentence(str_replace_all(.,"_"," "))) %>% 
+  flextable() %>% 
+   colformat_double(
+    big.mark = ",", decimal.mark = ".",
+    digits = 2,
+    na_str = "na") %>% 
+  autofit() %>% 
+  theme_zebra()
+```
+
+### Daily reporting to site
+
+```{r}
+prep_a %>% 
+  select(group,statistic,starts_with("daily_status_reporting_to_job_site")) %>% 
+  rename_all(.funs = ~str_to_sentence(str_replace_all(.,"_"," "))) %>% 
+  flextable() %>% 
+   colformat_double(
+    big.mark = ",", decimal.mark = ".",
+    digits = 2,
+    na_str = "na") %>% 
+  autofit() %>% 
+  theme_zebra()
+```
+
+### Team size
+
+```{r}
+prep_a %>% 
+  select(group,statistic,starts_with("team_size")) %>% 
+  rename_all(.funs = ~str_to_sentence(str_replace_all(.,"_"," "))) %>% 
+  flextable() %>% 
+   colformat_double(
+    big.mark = ",", decimal.mark = ".",
+    digits = 2,
+    na_str = "na") %>% 
+  autofit() %>% 
+  theme_zebra()
+```
+
+### Working days
+
+```{r}
+prep_a %>% 
+  select(group,statistic,starts_with("working_days")) %>% 
+  rename_all(.funs = ~str_to_sentence(str_replace_all(.,"_"," "))) %>% 
+  flextable() %>% 
+   colformat_double(
+    big.mark = ",", decimal.mark = ".",
+    digits = 2,
+    na_str = "na") %>% 
+  autofit() %>% 
+  theme_zebra()
+```
+
+### Co-located days with at least one team member
+
+```{r}
+prep_a %>% 
+  select(group,statistic,starts_with("days_colocated_1")) %>% 
+  rename_all(.funs = ~str_to_sentence(str_replace_all(.,"_"," "))) %>% 
+  flextable() %>% 
+   colformat_double(
+    big.mark = ",", decimal.mark = ".",
+    digits = 2,
+    na_str = "na") %>% 
+  autofit() %>% 
+  theme_zebra()
+```
+
+### Co-located days with at whole team
+
+```{r}
+prep_a %>% 
+  select(group,statistic,starts_with("days_colocated_team_")) %>% 
+  rename_all(.funs = ~str_to_sentence(str_replace_all(.,"_"," "))) %>% 
+  flextable() %>% 
+   colformat_double(
+    big.mark = ",", decimal.mark = ".",
+    digits = 2,
+    na_str = "na") %>% 
+  autofit() %>% 
+  theme_zebra()
+```
+
+### Co-located days with supervisor
+
+```{r}
+prep_a %>% 
+  select(group,statistic,starts_with("days_colocated_supervisor_")) %>% 
+  rename_all(.funs = ~str_to_sentence(str_replace_all(.,"_"," "))) %>% 
+  flextable() %>% 
+   colformat_double(
+    big.mark = ",", decimal.mark = ".",
+    digits = 2,
+    na_str = "na") %>% 
+  autofit() %>% 
+  theme_zebra()
+```
+
+### Days team teleworks
+
+```{r}
+prep_a %>% 
+  select(group,statistic,starts_with("days_telework_team_")) %>% 
+  rename_all(.funs = ~str_to_sentence(str_replace_all(.,"_"," "))) %>% 
+  flextable() %>% 
+   colformat_double(
+    big.mark = ",", decimal.mark = ".",
+    digits = 2,
+    na_str = "na") %>% 
+  autofit() %>% 
+  theme_zebra()
+```
+
+The principle work pattern statistics are as follows:
+
+-   Employee work pattern statistics:
+
+    -   Proportion in employee time onsite by the day of the week
+
+    -   Correlations of by employee time between the days of the week
+
+    -   Number exiting employment
+
+    -   Number changing supervisors
+
+## Descriptive statistics {.tabset .tabset-pills}
+
+ Employee descriptive statistics
+
+    -   Number and proportion of employees by grade
+
+    -   Number and proportion of employees by occupational series
+
+    -   Number and proportion of employees by position category
+
+    -   Number and proportion of employees by GSA region
+
+    -   Number and proportion of employees by SSO
+
+    -   Number and proportion of employees by state
+
+    -   Number and proportion of employees by city
+
+    -   Number and proportion of employees by supervisor level
+
+## Distributions by cluster {.tabset .tabset-pills}
+
+### Function
+
+Function to create a density plot for a specific numeric variable.
+
+```{r}
+gg_density <- function(in_data,in_variable)
+{
+  in_variable_sym <- sym(in_variable)
+
+  spec <- unique(in_data$specification)
+
+  clus <- unique(in_data$k)
+
+  in_data %>% 
+  ggplot(aes(x = !!in_variable_sym, color = .cluster, fill = .cluster)) +
+  geom_density(alpha = .25) +
+    geomtextpath::geom_textdensity(aes(label = .cluster), 
+                   hjust = "ymax", 
+                   vjust = 1, text_only = TRUE, text_smoothing = 0, straight = TRUE) + 
+    oescolorrrs::scale_color_oes(palette = 'accent colors') +
+    oescolorrrs::scale_fill_oes(palette = 'accent colors') +
+    theme_fivethirtyeight() +
+    labs(
+      title = glue::glue("Histogram of `{in_variable}`"),
+      caption = glue::glue("For specification {spec} with {clus} clusters.")
+    ) +
+    theme(
+      legend.position = "none",
+      panel.background = element_rect(fill = "white"),
+      plot.background = element_rect(fill = "white"),
+      # panel.border = element_blank()
+    )
+}
+```
+
+### List of numeric variables
+
+```{r}
+num_vars <- 
+  d %>% 
+  select_if(is.numeric) %>% 
+  select(-k) %>% 
+  names()
+
+num_vars
+```
+
+### Distributions
+
+```{r}
+num_vars[1:20] %>% 
+  map(~gg_density(d,in_variable = .))
+```
+
+## Descriptive
+
+The descriptive statistics are:
+
+-  
+The employees statistics will be calculated for the following groups:
+
+1.  Whole cohort of employees
+2.  By rule-based categories of work pattern
+3.  By cluster defined categories of work pattern
 

### 2023-06-08 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Update 03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd

@@
   data_folder_1: "prepared-data"
-  data_file_1: "clusters-employee-2023-06-01.rdata"
+  data_file_1: "clusters-employee-2023-06-08.rdata"
   data_file_2: "prep_employees_2023-05-24.rdata"

### 2023-06-13 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Attempting to update this with new variables
Update 02_data_preparation_clusters_employee.Rmd
Added to day of week counts telework and counts and proportion report to the job site, indicator for exiting employment, and count of unique supervisors, and indicator for multiple supervisors

@@
 
-#### Proportion of days remote by day of the week
+#### Proportion of days remote or reporting to site by day of the week
 
@@
   prep_day_of_week %>% 
-  select(person_id,date_day_of_week,daily_status_teleworking_working_prop,daily_status_teleworking_observation_prop) %>% 
+  select(person_id,date_day_of_week,
+         daily_status_teleworking,
+         daily_status_teleworking_working_prop,
+         daily_status_teleworking_observation_prop,
+         daily_status_reporting_to_job_site,
+         daily_status_reporting_to_job_site_working_prop,
+         daily_status_reporting_to_job_site_observation_prop) %>% 
   pivot_longer(cols = starts_with("daily_status")) %>% 
@@
   select(-working_days)
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
+### Exit employment
+
+Identify employees who had a report date earlier than the last reporting day.
+
+```{r}
+prep_a <-
+  cohort_panel %>% 
+  select(person_id,date,daily_status_imputed) %>% 
+  arrange(person_id,date) %>% 
+  group_by(person_id) %>% 
+  summarise(
+    across(
+      .cols = c(date,daily_status_imputed),
+      .fns = last
+    )
+  ) %>% 
+  ungroup() %>%
+  mutate(
+    exit_employment = case_when(date < max(date) ~ 1,
+                                TRUE ~ 0)
+  ) %>% 
+  distinct()
+```
+
+Review data.
+
+```{r}
+prep_a %>% 
+  skim()
+```
+
+Review grouping by `daily_status_imputed`.
+
+```{r}
+prep_a %>% 
+  group_by(daily_status_imputed) %>% 
+  skim()
+```
+
+Remove `daily_status_imputed`.
+
+```{r}
+prep_xx <- 
+  prep_a %>% 
+  select(-daily_status_imputed)
+```
+
+Review data.
+
+```{r}
+prep_xx %>% 
+  skim()
+```
+
+Check: These have the same number of unique `person_id`.
+
+```{r}
+cohort_ids %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull() ==
+  prep_xx %>% 
+  summarise(n_distinct(person_id)) %>% 
+  pull()
+```
+
+Join to `prep_building`.
+
+```{r}
+prep_building <- 
+  prep_building %>% 
+  left_join(prep_xx)
+```
+
+### Number of supervisors
+
+Count number of unique supervisors per employee.
+
+```{r}
+prep_xx <-
+  cohort_panel %>% 
+  select(person_id,supervisor_e_mail_address) %>% 
+  group_by(person_id) %>% 
+  summarise(
+    across(
+      .cols = c(supervisor_e_mail_address),
+      .fns = c(n_distinct = n_distinct),
+      .names = "{.col}_{.fn}"
+    )
+  ) %>% 
+  ungroup() %>%
+  mutate(
+    multiple_supervisors = case_when(supervisor_e_mail_address_n_distinct > 1 ~ 1,
+                                     supervisor_e_mail_address_n_distinct == 1 ~ 0,
+                                TRUE ~ 0)
+  ) %>% 
+  distinct()
 ```

### 2023-07-11 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Update 03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
working on developing charts to assess clusters, not going too well

@@
 ---
-title: "Data analysis for employee cluster descriptive statistics"
+title: "Data analysis for employee cluster assessment"
 date: "`r Sys.Date()`"
@@
   data_folder_1: "prepared-data"
-  data_file_1: "clusters-employee-2023-06-01.rdata"
+  data_file_1: "clusters-employee-2023-06-08.rdata"
+  data_file_2: "prep_employees_2023-05-24.rdata"
   in_number_of_clusters: 5
@@
 library(oesrrr)
+library(factoextra)
 library(tidyverse)
@@
 library(tidymodels)
-```
-
-```{r cohort dates}
-date_cohort_month_start <- ymd(params$date_cohort_month)
-date_cohort_month_end <- ceiling_date(date_cohort_month_start,unit = "month") %>% rollbackward()
-date_observation_window_month_start <- date_cohort_month_start %m+% months(params$observation_window_length_months)
-date_observation_window_month_end <- ceiling_date(date_observation_window_month_start,unit = "month") %>% rollbackward()
-```
-
-```{r}
-set.seed(27)
 ```
@@
 
+Load `r params$data_file_2` from `r params$data_folder_1` data folder.
+
+```{r}
+load(file = file.path(params$google_drive_home,"03. Data Collection",params$data_folder_1,params$data_file_2))
+```
+
+Review.
+
+```{r}
+prep_employees %>% 
+  skim()
+```
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+```
+
+```{r}
+clusterings %>% skim()
+```
+
+```{r}
+clusterings %>% 
+  ggplot(aes(x = k, y = tot.withinss, color = specification)) +
+  geom_line() +
+  geom_point() +
+  facet_wrap(facets = vars(specification),
+             scales = "free")
+
+```
+
+```{r}
+clust <- 
+  kclusts %>% 
+  filter(
+    k == 5 &
+      specification == params$in_specification
+  )
+```
+
+```{r}
+# prep_01 <- clust %>%
+#   unnest(cols = c(kclust))
+
+# prep_01 <- clust$kclust
+
+clust$kclust[[1]] %>% summary()
+
+clust %>% 
+  unnest(cols = c(augmented)) %>% 
+  summary()
+```
+
+```{r}
+fviz_cluster(object = clust$kclust[[1]], 
+             data = prep_employees %>% select(where(is.numeric)) %>% drop_na()
+             )
+```
+
 ## Select and unnest data {.tabset .tabset-pills}
@@
   filter(
-    k == params$in_number_of_clusters &
+    k == params$in_number_of_clusters
+    &
       specification == params$in_specification
   )
+```
+
+```{r}
+clust$kclust %>% head()
+```
+
+```{r}
+kclusts %>% 
+  count(specification)
 ```

### 2023-07-11 04. Analysis/scripts/make_clusters.R
Creating functions to make consistent across files

@@ -1,0 +1,76 @@
+#' Make employee clusters of a variety of sizes and different specifications
+#'
+#' @param in_data Data to use
+#' @param in_scale_or_rank Option for which scaling procedure: "scale" (normalization) or "rank" (rank order)
+#' @param in_working_or_observation_window Option for proportion denominator: "observation" (proportion of entire observation window) or "working" (proportion of period employ was working onsite or via telework)
+#' @param in_weekday_correlation Option for inter weekday relationship: "correlation telework" (telework correlation between days of the week), "correlation status" (work status correlation based on ordered work status by days of the week), or "proportion pairs" (proportion of telework in pairs)
+#' @param in_number_of_clusters_start Minimum number of clusters to test
+#' @param in_number_of_clusters_end Maximum number of clusters to test
+#'
+#' @return Dataframe of clusters and associatied statistics
+#' @export
+#'
+#' @examples
+make_clusters <-
+  function(in_data,
+           in_scale_or_rank,
+           in_working_or_observation_window,
+           in_weekday_correlation,
+           in_number_of_clusters_start,
+           in_number_of_clusters_end)
+  {
+    stopifnot(in_scale_or_rank %in% c("scale", "rank"))
+    stopifnot(in_working_or_observation_window %in% c("observation", "working"))
+    stopifnot(
+      in_weekday_correlation %in% c(
+        "correlation telework",
+        "correlation status",
+        "proportion pairs"
+      )
+    )
+    stopifnot(in_number_of_clusters_start >= 1)
+    stopifnot(in_number_of_clusters_start <= in_number_of_clusters_end)
+    
+    step_01 <-
+      in_data %>%
+      select_cluster_cols(
+        in_scale_or_rank = in_scale_or_rank,
+        in_working_or_observation_window = in_working_or_observation_window,
+        in_weekday_correlation = in_weekday_correlation
+      )
+    
+    print(glue::glue("Review data for step 1. {Sys.time()}"))
+    
+    step_01 %>%
+      skim() %>%
+      print()
+    
+    print(glue::glue("Remove person_id. {Sys.time()}"))
+    
+    step_02 <-
+      step_01 %>%
+      select(-person_id)
+    
+    print(glue::glue("Review data for step 2. {Sys.time()}"))
+    
+    step_02 %>%
+      skim() %>%
+      print()
+    
+    print(
+      glue::glue(
[…]

### 2023-07-11 04. Analysis/scripts/make_fviz_clusters.R

@@ -1,0 +1,83 @@
+#' Make employee clusters of a variety of sizes and different specifications
+#'
+#' @param in_data Data to use
+#' @param in_scale_or_rank Option for which scaling procedure: "scale" (normalization) or "rank" (rank order)
+#' @param in_working_or_observation_window Option for proportion denominator: "observation" (proportion of entire observation window) or "working" (proportion of period employ was working onsite or via telework)
+#' @param in_weekday_correlation Option for inter weekday relationship: "correlation telework" (telework correlation between days of the week), "correlation status" (work status correlation based on ordered work status by days of the week), or "proportion pairs" (proportion of telework in pairs)
+#' @param in_number_of_clusters_start Minimum number of clusters to test
+#' @param in_number_of_clusters_end Maximum number of clusters to test
+#'
+#' @return Dataframe of clusters and associatied statistics
+#' @export
+#'
+#' @examples
+make_fviz_clusters <-
+  function(in_data,
+           in_scale_or_rank,
+           in_working_or_observation_window,
+           in_weekday_correlation,
+           in_number_of_clusters_start,
+           in_number_of_clusters_end)
+  {
+    stopifnot(in_scale_or_rank %in% c("scale", "rank"))
+    stopifnot(in_working_or_observation_window %in% c("observation", "working"))
+    stopifnot(
+      in_weekday_correlation %in% c(
+        "correlation telework",
+        "correlation status",
+        "proportion pairs"
+      )
+    )
+    stopifnot(in_number_of_clusters_start >= 1)
+    stopifnot(in_number_of_clusters_start <= in_number_of_clusters_end)
+    
+    step_01 <-
+      in_data %>%
+      select_cluster_cols(
+        in_scale_or_rank = in_scale_or_rank,
+        in_working_or_observation_window = in_working_or_observation_window,
+        in_weekday_correlation = in_weekday_correlation
+      )
+    
+    print(glue::glue("Review data for step 1. {Sys.time()}"))
+    
+    step_01 %>%
+      skim() %>%
+      print()
+    
+    print(glue::glue("Remove person_id. {Sys.time()}"))
+    
+    step_02 <-
+      step_01 %>%
+      select(-person_id)
+    
+    print(glue::glue("Review data for step 2. {Sys.time()}"))
+    
+    step_02 %>%
+      skim() %>%
+      print()
[…]

### 2023-07-11 04. Analysis/scripts/make_specs.R

@@ -1,0 +1,19 @@
+specs <- 
+  tibble(
+  in_scale_or_rank = c(rep("scale", 6), rep("rank", 6)),
+  in_working_or_observation_window = rep(c(rep("observation", 3), rep("working", 3)), 2),
+  in_weekday_correlation = rep(
+    c(
+      "correlation telework",
+      "correlation status",
+      "proportion pairs"
+    ),
+    4
+  ),
+  in_number_of_clusters_start = rep(params$in_number_of_clusters_start, 12),
+  in_number_of_clusters_end = rep(params$in_number_of_clusters_end, 12)
+) %>% 
+  unite(col = "in_specification",everything(),remove = FALSE) %>% 
+  mutate(
+    in_specification = str_replace_all(in_specification," ","_")
+  )

### 2023-07-11 04. Analysis/scripts/prep_employees_to_d.R

@@ -1,0 +1,26 @@
+d <- 
+  prep_employees %>% 
+  mutate(
+    across(
+      .cols = c(daily_status_reporting_to_job_site_working_prop,
+                daily_status_teleworking_working_prop,
+                daily_status_reporting_to_job_site_observation_prop,
+                daily_status_teleworking_observation_prop,
+                starts_with("mon_"),
+                starts_with("tue_"),
+                starts_with("wed_"),
+                starts_with("thu_"),
+                starts_with("fri_"),
+                working_days,
+                team_size_mode,
+                starts_with("days_colocated_"),
+                starts_with("days_telework_"),
+                -days_colocated_1,
+                -days_colocated_supervisor,
+                -days_colocated_team,
+                -days_telework_team
+                ),
+      .fns = list(scale = scale,rank = rank),
+      .names = "{.col}_{.fn}"
+    )
+  )

### 2023-07-11 04. Analysis/scripts/select_cluster_cols.R

@@ -1,0 +1,219 @@
+#' Selects the correct columns for employee cluster analysis
+#'
+#' @param in_data Data to use
+#' @param in_scale_or_rank Option for which scaling procedure: "scale" (normalization) or "rank" (rank order)
+#' @param in_working_or_observation_window Option for proportion denominator: "observation" (proportion of entire observation window) or "working" (proportion of period employ was working onsite or via telework)
+#' @param in_weekday_correlation Option for inter weekday relationship: "correlation telework" (telework correlation between days of the week), "correlation status" (work status correlation based on ordered work status by days of the week), or "proportion pairs" (proportion of telework in pairs)
+#'
+#' @return Dataframe with only selected columns and dropped null observations
+#' @export
+#'
+#' @examples
+select_cluster_cols <-
+  function(in_data,
+           in_scale_or_rank,
+           in_working_or_observation_window,
+           in_weekday_correlation)
+  {
+    stopifnot(in_scale_or_rank %in% c("scale", "rank"))
+    stopifnot(in_working_or_observation_window %in% c("observation", "working"))
+    stopifnot(in_weekday_correlation %in% c("correlation telework", "correlation status","proportion pairs"))
+    
+    if (in_scale_or_rank == "scale" &
+        in_working_or_observation_window == "observation" &
+        in_weekday_correlation == "correlation telework")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_scale"),
+          -contains("_working_prop_"),
+          -contains("_cor_status_"),
+          -contains("_prop_pairs_"),
+        ) %>%
+        drop_na()
+    }
+    
+    if (in_scale_or_rank == "rank" &
+        in_working_or_observation_window == "observation" &
+        in_weekday_correlation == "correlation telework")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_rank"),
+          -contains("_working_prop_"),
+          -contains("_cor_status_"),
+          -contains("_prop_pairs_"),
+        ) %>%
+        drop_na()
+    }
+    
+    if (in_scale_or_rank == "scale" &
+        in_working_or_observation_window == "working" &
+        in_weekday_correlation == "correlation telework")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_scale"),
[…]

### 2023-07-11 04. Analysis/scripts/03-01-data-analysis-employee-cluster-identification.Rmd
Update 03-01-data-analysis-employee-cluster-identification.Rmd
Cleaned up `specification` column and added data review.
Update 03-01-data-analysis-employee-cluster-identification.Rmd
shifting some code to source and creating new parameters

@@
   in_number_of_clusters_end: 10
+  in_seed: 27
 
@@
 ```{r}
-set.seed(27)
+set.seed(params$in_seed)
 ```
@@
 **Number of clusters**: Testing `r params$in_number_of_clusters_start` to `r params$in_number_of_clusters_end`
+
+**Random seed** `r params$in_seed`
 
@@
 ```{r}
-#' Selects the correct columns for employee cluster analysis
-#'
-#' @param in_data Data to use
-#' @param in_scale_or_rank Option for which scaling procedure: "scale" (normalization) or "rank" (rank order)
-#' @param in_working_or_observation_window Option for proportion denominator: "observation" (proportion of entire observation window) or "working" (proportion of period employ was working onsite or via telework)
-#' @param in_weekday_correlation Option for inter weekday relationship: "correlation telework" (telework correlation between days of the week), "correlation status" (work status correlation based on ordered work status by days of the week), or "proportion pairs" (proportion of telework in pairs)
-#'
-#' @return Dataframe with only selected columns and dropped null observations
-#' @export
-#'
-#' @examples
-select_cluster_cols <-
-  function(in_data,
-           in_scale_or_rank,
-           in_working_or_observation_window,
-           in_weekday_correlation)
-  {
-    stopifnot(in_scale_or_rank %in% c("scale", "rank"))
-    stopifnot(in_working_or_observation_window %in% c("observation", "working"))
-    stopifnot(in_weekday_correlation %in% c("correlation telework", "correlation status","proportion pairs"))
-
-    if (in_scale_or_rank == "scale" &
-        in_working_or_observation_window == "observation" &
-        in_weekday_correlation == "correlation telework")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_scale"),
-          -contains("_working_prop_"),
-          -contains("_cor_status_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "rank" &
-        in_working_or_observation_window == "observation" &
-        in_weekday_correlation == "correlation telework")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_rank"),
-          -contains("_working_prop_"),
-          -contains("_cor_status_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "scale" &
-        in_working_or_observation_window == "working" &
-        in_weekday_correlation == "correlation telework")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_scale"),
-          -contains("_observation_"),
-          -contains("_cor_status_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "rank" &
-        in_working_or_observation_window == "working" &
-        in_weekday_correlation == "correlation telework")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_rank"),
-          -contains("_observation_"),
-          -contains("_cor_status_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "scale" &
-        in_working_or_observation_window == "observation" &
-        in_weekday_correlation == "correlation status")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_scale"),
-          -contains("_working_prop_"),
-          -contains("_cor_telework_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "rank" &
-        in_working_or_observation_window == "observation" &
-        in_weekday_correlation == "correlation status")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_rank"),
-          -contains("_working_prop_"),
-          -contains("_cor_telework_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "scale" &
-        in_working_or_observation_window == "working" &
-        in_weekday_correlation == "correlation status")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_scale"),
-          -contains("_observation_"),
-          -contains("_cor_telework_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "rank" &
-        in_working_or_observation_window == "working" &
-        in_weekday_correlation == "correlation status")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_rank"),
-          -contains("_observation_"),
-          -contains("_cor_telework_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "scale" &
-        in_working_or_observation_window == "observation" &
-        in_weekday_correlation == "proportion pairs")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_scale"),
-          -contains("_working_prop_"),
-          -contains("_cor_status_"),
-          -contains("cor_telework"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "rank" &
-        in_working_or_observation_window == "observation" &
-        in_weekday_correlation == "proportion pairs")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_rank"),
-          -contains("_working_prop_"),
-          -contains("_cor_status_"),
-          -contains("cor_telework"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "scale" &
-        in_working_or_observation_window == "working" &
-        in_weekday_correlation == "proportion pairs")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_scale"),
-          -contains("_observation_"),
-          -contains("_cor_status_"),
-          -contains("cor_telework"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "rank" &
-        in_working_or_observation_window == "working" &
-        in_weekday_correlation == "proportion pairs")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_rank"),
-          -contains("_observation_"),
-          -contains("_cor_status_"),
-          -contains("cor_telework"),
-        ) %>%
-        drop_na()
-    }
-
-    out <- 
-      step_01 %>% 
-      as_tibble()
-
-    return(out)
-  }
+source(here::here("04. Analysis","scripts","select_cluster_cols.R"))
 ```
@@
 ```{r}
-#' Make employee clusters of a variety of sizes and different specifications
-#'
-#' @param in_data Data to use
-#' @param in_scale_or_rank Option for which scaling procedure: "scale" (normalization) or "rank" (rank order)
-#' @param in_working_or_observation_window Option for proportion denominator: "observation" (proportion of entire observation window) or "working" (proportion of period employ was working onsite or via telework)
-#' @param in_weekday_correlation Option for inter weekday relationship: "correlation telework" (telework correlation between days of the week), "correlation status" (work status correlation based on ordered work status by days of the week), or "proportion pairs" (proportion of telework in pairs)
-#' @param in_number_of_clusters_start Minimum number of clusters to test
-#' @param in_number_of_clusters_end Maximum number of clusters to test
-#'
-#' @return Dataframe of clusters and associatied statistics
-#' @export
-#'
-#' @examples
-make_clusters <-
-  function(in_data,
-           in_scale_or_rank,
-           in_working_or_observation_window,
-           in_weekday_correlation,
-           in_number_of_clusters_start,
-           in_number_of_clusters_end)
-  {
-    stopifnot(in_scale_or_rank %in% c("scale", "rank"))
-    stopifnot(in_working_or_observation_window %in% c("observation", "working"))
-    stopifnot(
-      in_weekday_correlation %in% c(
-        "correlation telework",
-        "correlation status",
-        "proportion pairs"
-      )
-    )
-    stopifnot(in_number_of_clusters_start >= 1)
-    stopifnot(in_number_of_clusters_start <= in_number_of_clusters_end)
-
-    step_01 <-
-      in_data %>%
-      select_cluster_cols(
-        in_scale_or_rank = in_scale_or_rank,
-        in_working_or_observation_window = in_working_or_observation_window,
-        in_weekday_correlation = in_weekday_correlation
-      )
-
-    print(glue::glue("Review data for step 1. {Sys.time()}"))
-
-    step_01 %>%
-      skim() %>%
-      print()
-
-    print(glue::glue("Remove person_id. {Sys.time()}"))
-
-    step_02 <-
-      step_01 %>%
-      select(-person_id)
-
-    print(glue::glue("Review data for step 2. {Sys.time()}"))
-
-    step_02 %>%
-      skim() %>%
-      print()
-
-    print(
-      glue::glue(
-        "Create clusters of the data from {in_number_of_clusters_start} to {in_number_of_clusters_end}. {Sys.time()}"
-      )
-    )
-
-    out <-
-      tibble(k = in_number_of_clusters_start:in_number_of_clusters_end) %>%
-      mutate(
-        kclust = map(k, ~ kmeans(step_02, .x)),
-        tidied = map(kclust, tidy),
-        glanced = map(kclust, glance),
-        augmented = map(kclust, augment, step_01)
-      )
-
-    return(out)
-  }
+source(here::here("04. Analysis","scripts","make_clusters.R"))
 ```
@@
 ```{r}
-specs <- 
-  tibble(
-  in_scale_or_rank = c(rep("scale", 6), rep("rank", 6)),
-  in_working_or_observation_window = rep(c(rep("observation", 3), rep("working", 3)), 2),
-  in_weekday_correlation = rep(
-    c(
-      "correlation telework",
-      "correlation status",
-      "proportion pairs"
-    ),
-    4
-  ),
-  in_number_of_clusters_start = rep(params$in_number_of_clusters_start, 12),
-  in_number_of_clusters_end = rep(params$in_number_of_clusters_end, 12)
-) %>% 
-  unite(col = "in_specification",everything(),remove = FALSE)
+source(here::here("04. Analysis","scripts","make_specs.R"))
 ```
@@
   pmap_dfr(make_clusters_d)
+```
+
+Add underscore to specification.
+
+```{r}
+kclusts <- 
+  kclusts %>% 
+  mutate(
+    specification = str_replace_all(specification," ","_")
+  )
+```
+
+Check `specification` results.
+
+```{r}
+kclusts %>% 
+  count(specification)
+```
+
+Review data.
+
+```{r}
+kclusts %>% 
+  skim()
 ```

### 2023-07-11 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Update 03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Developing code for PCA data visualization

@@
   in_number_of_clusters: 5
+  in_number_of_clusters_start: 1
+  in_number_of_clusters_end: 10
   in_specification: "scale_working_proportion_pairs_1_10"
+  in_seed: 27
 
@@
 
+```{r}
+set.seed(params$in_seed)
+```
+
 # Data preparation {.tabset .tabset-pills}
@@
 **Specification** `r params$in_specification`
+
+**Random seed** `r params$in_seed`
 
@@
   skim()
+```
+
+### Functions
+
+#### Selecting data for cluster analysis
+
+```{r}
+source(here::here("04. Analysis","scripts","select_cluster_cols.R"))
+```
+
+#### Making clusters of different sizes
+
+```{r}
+source(here::here("04. Analysis","scripts","make_clusters.R"))
+```
+
+#### Making clusters visualizations using PCA
+
+```{r}
+source(here::here("04. Analysis","scripts","make_fviz_clusters.R"))
+```
+
+#### Creating d for cluster analysis
+
+```{r}
+source(here::here("04. Analysis","scripts","prep_employees_to_d.R"))
+```
+
+#### Making clusters  visualizations using PCA of different sizes, but only for `d` and adding specification
+
+```{r}
+make_fviz_clusters_d <- function(in_specification,
+                            in_scale_or_rank,
+                            in_working_or_observation_window,
+                            in_weekday_correlation,
+                            in_number_of_clusters_start,
+                            in_number_of_clusters_end)
+{
+  make_fviz_clusters(
+    in_data = d,
+    in_scale_or_rank = in_scale_or_rank,
+    in_working_or_observation_window = in_working_or_observation_window,
+    in_weekday_correlation = in_weekday_correlation,
+    in_number_of_clusters_start = in_number_of_clusters_start,
+    in_number_of_clusters_end = in_number_of_clusters_end
+  ) %>%
+    mutate(specification = in_specification)
+}
+```
+
+### Create clusters
+
+#### Create dataframe of all permutations
+
+This table shows all permutations of scaling (normalization, or rank), denominators for proportions (observation window or working days), and types of inter day correlations.
+
+```{r}
+source(here::here("04. Analysis","scripts","make_specs.R"))
+```
+
+Review data.
+
+```{r}
+specs
+```
+
+#### Create clusters
+
+Iterate over `specs` creating and collecting dataframe of clusters from all of the above specifications.
+
+```{r}
+v <- 
+  specs %>%
+  pmap_dfr(make_fviz_clusters_d)
+```
+
+```{r}
+v %>% #count(specification)
+  filter(specification == params$in_specification) %>% 
+  .$fviz_cluster
 ```

### 2023-07-12 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Update 03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Restructuring

@@
 
-### Functions
+## Functions {.tabset .tabset-pills}
 
-#### Selecting data for cluster analysis
+### Selecting data for cluster analysis
 
@@
 
-#### Making clusters of different sizes
+### Making clusters of different sizes
 
@@
 
-#### Making clusters visualizations using PCA
+### Making clusters visualizations using PCA
 
@@
 
-#### Creating d for cluster analysis
+### Creating d for cluster analysis
 
@@
 
-#### Making clusters  visualizations using PCA of different sizes, but only for `d` and adding specification
+### Making clusters  visualizations using PCA of different sizes, but only for `d` and adding specification
 
@@
 
-### Create clusters
+## Intra-cluster visualizations {.tabset .tabset-pills}
+
+### Unnest
+
+```{r}
+clusters <- 
+  kclusts %>%
+  unnest(cols = c(tidied))
+
+assignments <- 
+  kclusts %>% 
+  unnest(cols = c(augmented))
+
+clusterings <- 
+  kclusts %>%
+  unnest(cols = c(glanced))
+
+```
+
+### Elbow
+
+```{r}
+clusterings %>% 
+  ggplot(aes(x = k, y = tot.withinss, color = specification)) +
+  geom_line() +
+  geom_point() +
+  facet_wrap(facets = vars(specification),
+             scales = "free")
+
+```
+
+## Inter-cluster visaulizations {.tabset .tabset-pills}
+
+### Two-dimensional groupings
 
@@
 clusterings %>% skim()
-```
-
-```{r}
-clusterings %>% 
-  ggplot(aes(x = k, y = tot.withinss, color = specification)) +
-  geom_line() +
-  geom_point() +
-  facet_wrap(facets = vars(specification),
-             scales = "free")
-
 ```
@@
   count(specification)
-```
-
-### Unnest
-
-Filter to data with `r params$in_number_of_clusters` clusters with specification `r params$in_specification`.
-
-```{r}
-clusters <- 
-  kclusts %>%
-  unnest(cols = c(tidied))
-
-assignments <- 
-  kclusts %>% 
-  unnest(cols = c(augmented))
-
-clusterings <- 
-  kclusts %>%
-  unnest(cols = c(glanced))
-
 ```

### 2023-07-13 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Update 03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Adding silhouette and gap statistic draft visualizations

@@
 library(tidymodels)
+library(cluster)
 ```
@@
 
+```
+
+### Average silhouette
+
+```{r}
+avg_sil <- function(k) {
+  km.res <- kmeans(df, centers = k, nstart = 25)
+  ss <- silhouette(km.res$cluster, dist(df))
+  mean(ss[, 3])
+}
+
+k.values <- 2:15
+
+# extract avg silhouette for 2-15 clusters
+avg_sil_values <- map_dbl(k.values, avg_sil)
+
+step_01 <- tibble(
+  k = k.values,
+  silh = avg_sil_values
+)
+
+step_01 %>% 
+  ggplot(aes(x = k.values, y = silh)) +
+  geom_point() +
+  geom_line()
+
+plot(k.values, avg_sil_values,
+       type = "b", pch = 19, frame = FALSE, 
+       xlab = "Number of clusters K",
+       ylab = "Average Silhouettes")
+
+fviz_nbclust(df, kmeans, method = "silhouette") +
+  theme_economist()
+```
+
+```{r}
+df <- iris %>% select(where(is.numeric)) %>% drop_na()
+```
+
+```{r}
+d %>% 
+  select_cluster_cols(in_scale_or_rank = "scale",
+                      in_working_or_observation_window = "working",
+                      in_weekday_correlation = "correlation telework") %>% 
+  select(where(is.numeric)) %>% 
+  fviz_nbclust(., kmeans, method = "silhouette") +
+  theme_fivethirtyeight()
+```
+
+### Gap statistic
+
+```{r}
+gap_stat <- d %>% 
+  select_cluster_cols(in_scale_or_rank = "scale",
+                      in_working_or_observation_window = "working",
+                      in_weekday_correlation = "correlation telework") %>%
+  select(where(is.numeric)) %>% 
+  clusGap(., FUN = kmeans, nstart = 25,
+                    K.max = 10, B = 50)
+```
+
+```{r}
+fviz_gap_stat(gap_stat)
 ```

### 2023-07-14 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Update 03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Got gap statistic visualization working, wrote helper functions for elbow, silhouette, and gap statistic

--- 2023-07-12 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
@@
 
+### Making elbow visualizations
+
+```{r}
+make_elbow_d <- function(in_specification,
+                         in_scale_or_rank,
+                         in_working_or_observation_window,
+                         in_weekday_correlation)
+{
+  d %>%
+    select_cluster_cols(
+      in_scale_or_rank = in_scale_or_rank,
+      in_working_or_observation_window = in_working_or_observation_window,
+      in_weekday_correlation = in_weekday_correlation
+    ) %>%
+    select(where(is.numeric)) %>%
+    fviz_nbclust(., kmeans, method = "wss") +
+    theme_fivethirtyeight()
+}
+
+```
+
+### Making silhouette visualizations
+
+```{r}
+make_silhouette_d <- function(in_specification,
+                              in_scale_or_rank,
+                              in_working_or_observation_window,
+                              in_weekday_correlation)
+{
+  d %>%
+    select_cluster_cols(
+      in_scale_or_rank = in_scale_or_rank,
+      in_working_or_observation_window = in_working_or_observation_window,
+      in_weekday_correlation = in_weekday_correlation
+    ) %>%
+    select(where(is.numeric)) %>%
+    fviz_nbclust(., kmeans, method = "silhouette") +
+    theme_fivethirtyeight()
+}
+
+```
+
+### Making gap statistic visualizations
+
+```{r}
+make_gap_stat_d <- function(in_specification,
+                              in_scale_or_rank,
+                              in_working_or_observation_window,
+                              in_weekday_correlation)
+{
+  d %>%
+    select_cluster_cols(
+      in_scale_or_rank = in_scale_or_rank,
+      in_working_or_observation_window = in_working_or_observation_window,
+      in_weekday_correlation = in_weekday_correlation
+    ) %>%
+    select(where(is.numeric)) %>%
+    fviz_nbclust(.,  kmeans, 
+               nstart = 25,
+               method = "gap_stat", 
+               nboot = 10,
+               # algorithm="Lloyd",
+               algorithm="MacQueen",
+               iter.max=200,
+               verbose = TRUE) +
+    theme_fivethirtyeight()
+}
+
+```
+
+## Create dataframe of all permutations {.tabset .tabset-pills}
+
+This table shows all permutations of scaling (normalization, or rank), denominators for proportions (observation window or working days), and types of inter day correlations.
+
+```{r}
+source(here::here("04. Analysis","scripts","make_specs.R"))
+```
+
+Review data.
+
+```{r}
+specs
+```
+
 ## Intra-cluster visualizations {.tabset .tabset-pills}
@@
   geom_point() +
-  facet_wrap(facets = vars(specification),
-             scales = "free")
+  # facet_wrap(facets = vars(specification),
+  #            scales = "free") +
+  facet_grid(
+    rows = "specification",
+    scales = "free"
+  ) +
+  theme(
+    legend.position = "none"
+  )
 
+```
+
+```{r}
+d %>% 
+  select_cluster_cols(in_scale_or_rank = "scale",
+                      in_working_or_observation_window = "working",
+                      in_weekday_correlation = "correlation telework") %>% 
+  select(where(is.numeric)) %>% 
+  fviz_nbclust(., kmeans, method = "wss") +
+  theme_fivethirtyeight()
+```
+
+```{r}
+make_elbow_d(in_scale_or_rank = "scale",
+                      in_working_or_observation_window = "working",
+                      in_weekday_correlation = "correlation telework")
+```
+
+### Average silhouette
+
+```{r}
+make_silhouette_d(in_scale_or_rank = "scale",
+                      in_working_or_observation_window = "working",
+                      in_weekday_correlation = "correlation telework")
+```
+
+```{r}
+kclusts <- 
+  specs %>%
+  pmap_dfr(make_clusters_d)
+```
+
+Add underscore to specification.
+
+```{r}
+kclusts <- 
+  kclusts %>% 
+  mutate(
+    specification = str_replace_all(specification," ","_")
+  )
+```
+
+### Gap statistic
+
+```{r}
+gc()
+d %>% 
+  select_cluster_cols(in_scale_or_rank = "scale",
+                      in_working_or_observation_window = "working",
+                      in_weekday_correlation = "correlation telework") %>% 
+  select(where(is.numeric)) %>% 
+  fviz_nbclust(.,  kmeans, 
+               nstart = 25,
+               method = "gap_stat", 
+               nboot = 10,
+               # algorithm="Lloyd",
+               algorithm="MacQueen",
+               iter.max=200,
+               verbose = TRUE) +
+  theme_fivethirtyeight()
+```
+
+```{r}
+gc()
+make_gap_stat_d(in_scale_or_rank = "scale",
+                      in_working_or_observation_window = "working",
+                      in_weekday_correlation = "correlation telework")
 ```
@@
 
-#### Create clusters
+#### Create cluster visualizations
 
@@
 ```{r}
-v %>% #count(specification)
+v %>% 
   filter(specification == params$in_specification) %>% 

### 2023-07-20 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Update 03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Adding average silhouette, gap statistic, PCA, and silhouette diagram

--- 2023-07-12 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
@@
   in_seed: 27
-
 ---
@@
 
-## Intra-cluster visualizations {.tabset .tabset-pills}
+### Making elbow visualizations
 
-### Unnest
+Generates 1 to 10 new clusters for specifications and creates elbow charts for each specification.
 
 ```{r}
-clusters <- 
-  kclusts %>%
-  unnest(cols = c(tidied))
-
-assignments <- 
-  kclusts %>% 
-  unnest(cols = c(augmented))
-
-clusterings <- 
-  kclusts %>%
-  unnest(cols = c(glanced))
+make_elbow_d <- function(in_specification,
+                         in_scale_or_rank,
+                         in_working_or_observation_window,
+                         in_weekday_correlation)
+{
+  d %>%
+    select_cluster_cols(
+      in_scale_or_rank = in_scale_or_rank,
+      in_working_or_observation_window = in_working_or_observation_window,
+      in_weekday_correlation = in_weekday_correlation
+    ) %>%
+    select(where(is.numeric)) %>%
+    fviz_nbclust(
+      .,
+      kmeans,
+      method = "wss",
+      nstart = 25,
+      nboot = 10,
+      # algorithm="Lloyd",
+      algorithm = "MacQueen",
+      iter.max = 200,
+      verbose = TRUE
+    ) +
+    theme_fivethirtyeight() +
+  labs(
+    subtitle = in_specification
+  )
+}
 
@@
 
-### Elbow
+### Making silhouette visualizations
+
+Generates 1 to 10 new clusters for specifications and creates average silhouette charts for each specification.
 
 ```{r}
-clusterings %>% 
-  ggplot(aes(x = k, y = tot.withinss, color = specification)) +
-  geom_line() +
-  geom_point() +
-  facet_wrap(facets = vars(specification),
-             scales = "free")
+make_silhouette_d <- function(in_specification,
+                              in_scale_or_rank,
+                              in_working_or_observation_window,
+                              in_weekday_correlation)
+{
+  d %>%
+    select_cluster_cols(
+      in_scale_or_rank = in_scale_or_rank,
+      in_working_or_observation_window = in_working_or_observation_window,
+      in_weekday_correlation = in_weekday_correlation
+    ) %>%
+    select(where(is.numeric)) %>%
+    fviz_nbclust(
+      .,
+      kmeans,
+      method = "silhouette",
+      nstart = 25,
+      nboot = 10,
+      # algorithm="Lloyd",
+      algorithm = "MacQueen",
+      iter.max = 200,
+      verbose = TRUE
+    ) +
+    theme_fivethirtyeight() +
+  labs(
+    subtitle = in_specification
+  )
+}
 
@@
 
-## Inter-cluster visaulizations {.tabset .tabset-pills}
+### Making gap statistic visualizations
 
-### Two-dimensional groupings
+Generates 1 to 10 new clusters for specifications and creates gap statistic charts for each specification.
 
-#### Create dataframe of all permutations
+```{r}
+make_gap_stat_d <- function(in_specification,
+                            in_scale_or_rank,
+                            in_working_or_observation_window,
+                            in_weekday_correlation)
+{
+  d %>%
+    select_cluster_cols(
+      in_scale_or_rank = in_scale_or_rank,
+      in_working_or_observation_window = in_working_or_observation_window,
+      in_weekday_correlation = in_weekday_correlation
+    ) %>%
+    select(where(is.numeric)) %>%
+    fviz_nbclust(
+      .,
+      kmeans,
+      nstart = 25,
+      method = "gap_stat",
+      nboot = 10,
+      # algorithm="Lloyd",
+      algorithm = "MacQueen",
+      iter.max = 200,
+      verbose = TRUE
+    ) +
+    theme_fivethirtyeight() +
+  labs(
+    subtitle = in_specification
+  )
+}
+
+```
+
+### Making silhouette diagram visualizations[^1]
+
+[^1]: <https://rdrr.io/cran/factoextra/man/fviz_silhouette.html>
+
+Generates a specific number of clusters for specifications and creates silhouette diagram charts for each specification and cluster number.
+
+```{r}
+make_fviz_silhouette_d <- function(in_specification,
+                            in_scale_or_rank,
+                            in_working_or_observation_window,
+                            in_weekday_correlation,
+                            in_clusters)
+{
+  step_01 <- 
+    d %>%
+    select_cluster_cols(
+      in_scale_or_rank = in_scale_or_rank,
+      in_working_or_observation_window = in_working_or_observation_window,
+      in_weekday_correlation = in_weekday_correlation
+    ) %>%
+    select(where(is.numeric))
+
+  km.res <- kmeans(step_01, in_clusters, nstart = 2)
+
+  sil <- silhouette(km.res$cluster, dist(step_01))
+
+  fviz_silhouette(sil) +
+    theme_fivethirtyeight() +
+  labs(
+    subtitle = in_specification
+  )
+}
+
+```
+
+## Create dataframe of all permutations {.tabset .tabset-pills}
 
@@
 
-#### Create clusters
+## Intra-cluster visualizations {.tabset .tabset-pills}
+
+### Elbow
+
+```{r}
+elbows <- 
+  specs %>%
+   select(
+    in_scale_or_rank,
+    in_working_or_observation_window,
+    in_weekday_correlation,
+    in_specification
+  ) %>%
+  distinct() %>% 
+  pmap(make_elbow_d)
+```
+
+The elbow charts below look consistent across the different specifications of clusters. Five clusters appears to be an acceptable number of clusters by this metric.
+
+```{r}
+elbows
+```
+
+### Silhouette score
+
+```{r}
+silhouette_scores <-
+  specs %>%
+  select(
+    in_scale_or_rank,
+    in_working_or_observation_window,
+    in_weekday_correlation,
+    in_specification
+  ) %>%
+  distinct() %>%
+  # slice_head(n = 1) %>%
+  pmap(make_silhouette_d)
+```
+
+The mean silhouette coefficient measures how close a point in one cluster is the the points in neighboring clusters.
+
+Mathematically this is:
+
+$$
+\frac{b-a}{max(a,b)}
+$$
+
+where $a$ is the mean distance to other points in the same cluster and $b$ is the mean nearest cluster distance[^2].
+
+[^2]: <https://medium.com/geekculture/stop-using-the-elbow-method-96bcfbbbe9fd>
+
+Average silhouette charts below suggest a different number of clusters than the elbow charts above.
+Most specifications recommend only two clusters, though three clusters are recommended for the specification where the observation window time is used to calculate percentages, the intra-workday correlations are calculated from an indicator for telework, and scaling is done by ranks.
+
+```{r}
+silhouette_scores
+```
+
+### Gap statistic
+
+```{r}
+gc()
+gap_stats <- 
+  specs %>%
+   select(
+    in_scale_or_rank,
+    in_working_or_observation_window,
+    in_weekday_correlation,
+    in_specification
+  ) %>%
+  distinct() %>% 
+  pmap(make_gap_stat_d)
+```
+
+```{r}
+gap_stats
+```
+
+## Inter-cluster visaulizations {.tabset .tabset-pills}
+
+### PCA cluster visualizations
 
@@
 ```{r}
-v <- 
+pca <- 
   specs %>%
+  slice_head(n = 1) %>% 
   pmap_dfr(make_fviz_clusters_d)
@@
 ```{r}
-v %>% #count(specification)
-  filter(specification == params$in_specification) %>% 
+pca %>% 
+  # filter(specification == params$in_specification) %>% 
   .$fviz_cluster
@@
 
+### Silhouette diagram visualizations
+
 ```{r}
-clusters <- 
-  kclusts %>%
-  unnest(cols = c(tidied))
-
-assignments <- 
-  kclusts %>% 
-  unnest(cols = c(augmented))
-
-clusterings <- 
-  kclusts %>%
-  unnest(cols = c(glanced))
-
+silhouette_diagrams <- 
+  specs %>%
+   select(
+    in_scale_or_rank,
+    in_working_or_observation_window,
+    in_weekday_correlation,
+    in_specification
+  ) %>%
+  distinct() %>% 
+  slice(rep(1:n(), each = 10)) %>% 
+  rownames_to_column(var = "temp_01") %>% 
+  mutate(temp_02 = as.numeric(temp_01),
+         temp_03 = temp_02/10,
+         temp_04 = ceiling(temp_03),
+         temp_05 = temp_04*10-10,
+         temp_06 = temp_02 - temp_05) %>% 
+  rename(in_clusters = temp_06) %>% 
+  select(-starts_with("temp_")) %>% 
+  filter(in_clusters > 1) %>% 
+  # slice(2) %>% 
+  pmap(make_fviz_silhouette_d)
 ```
@@
 ```{r}
-clusterings %>% skim()
+silhouette_diagrams
 ```
 
-```{r}
-clust <- 
-  kclusts %>% 
-  filter(
-    k == 5 &
-      specification == params$in_specification
-  )
-```
+## Notes {.tabset .tabset-pills}
 
-```{r}
-# prep_01 <- clust %>%
-#   unnest(cols = c(kclust))
-
-# prep_01 <- clust$kclust
-
-clust$kclust[[1]] %>% summary()
-
-clust %>% 
-  unnest(cols = c(augmented)) %>% 
-  summary()
-```
-
-```{r}
-fviz_cluster(object = clust$kclust[[1]], 
-             data = prep_employees %>% select(where(is.numeric)) %>% drop_na()
-             )
-```
-
-## Select and unnest data {.tabset .tabset-pills}
-
-### Filter to specification and cluster
-
-Filter to data with `r params$in_number_of_clusters` clusters with specification `r params$in_specification`.
-
-```{r}
-clust <- 
-  kclusts %>% 
-  filter(
-    k == params$in_number_of_clusters
-    &
-      specification == params$in_specification
-  )
-```
-
-```{r}
-clust$kclust %>% head()
-```
-
-```{r}
-kclusts %>% 
-  count(specification)
-```
-
-## Scale data {.tabset .tabset-pills}
-
-Scaling the data in two ways:
-
-1.  Normalize - Data will have the mean that that element subtracted and
-    then divided by the standard deviation, using the `scale()`
-    function[^2]
-
-2.  Rank - The rank of each element will be used instead of the element.
-
-[^2]: [Documentation for the scale
-    function.](https://www.rdocumentation.org/packages/base/versions/3.6.2/topics/scale)
-
-```{r}
-d <- 
-  prep_employees %>% 
-  mutate(
-    across(
-      .cols = c(daily_status_reporting_to_job_site_working_prop,
-                daily_status_teleworking_working_prop,
-                daily_status_reporting_to_job_site_observation_prop,
-                daily_status_teleworking_observation_prop,
-                starts_with("mon_"),
-                starts_with("tue_"),
-                starts_with("wed_"),
-                starts_with("thu_"),
-                starts_with("fri_"),
-                working_days,
-                team_size_mode,
-                starts_with("days_colocated_"),
-                starts_with("days_telework_"),
-                -days_colocated_1,
-                -days_colocated_supervisor,
-                -days_colocated_team,
-                -days_telework_team
-                ),
-      .fns = list(scale = scale,rank = rank),
-      .names = "{.col}_{.fn}"
-    )
-  )
-```
-
-Review data.
-
-```{r}
-d %>% 
-  skim()
-```
-
-## Create clusters {.tabset .tabset-pills}
-
-### Functions
-
-#### Selecting data for cluster analysis
-
-```{r}
-#' Selects the correct columns for employee cluster analysis
-#'
-#' @param in_data Data to use
-#' @param in_scale_or_rank Option for which scaling procedure: "scale" (normalization) or "rank" (rank order)
-#' @param in_working_or_observation_window Option for proportion denominator: "observation" (proportion of entire observation window) or "working" (proportion of period employ was working onsite or via telework)
-#' @param in_weekday_correlation Option for inter weekday relationship: "correlation telework" (telework correlation between days of the week), "correlation status" (work status correlation based on ordered work status by days of the week), or "proportion pairs" (proportion of telework in pairs)
-#'
-#' @return Dataframe with only selected columns and dropped null observations
-#' @export
-#'
-#' @examples
-select_cluster_cols <-
-  function(in_data,
-           in_scale_or_rank,
-           in_working_or_observation_window,
-           in_weekday_correlation)
-  {
-    stopifnot(in_scale_or_rank %in% c("scale", "rank"))
-    stopifnot(in_working_or_observation_window %in% c("observation", "working"))
-    stopifnot(in_weekday_correlation %in% c("correlation telework", "correlation status","proportion pairs"))
-
-    if (in_scale_or_rank == "scale" &
-        in_working_or_observation_window == "observation" &
-        in_weekday_correlation == "correlation telework")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_scale"),
-          -contains("_working_prop_"),
-          -contains("_cor_status_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "rank" &
-        in_working_or_observation_window == "observation" &
-        in_weekday_correlation == "correlation telework")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_rank"),
-          -contains("_working_prop_"),
-          -contains("_cor_status_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "scale" &
-        in_working_or_observation_window == "working" &
-        in_weekday_correlation == "correlation telework")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_scale"),
-          -contains("_observation_"),
-          -contains("_cor_status_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "rank" &
-        in_working_or_observation_window == "working" &
-        in_weekday_correlation == "correlation telework")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_rank"),
-          -contains("_observation_"),
-          -contains("_cor_status_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "scale" &
-        in_working_or_observation_window == "observation" &
-        in_weekday_correlation == "correlation status")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_scale"),
-          -contains("_working_prop_"),
-          -contains("_cor_telework_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "rank" &
-        in_working_or_observation_window == "observation" &
-        in_weekday_correlation == "correlation status")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_rank"),
-          -contains("_working_prop_"),
-          -contains("_cor_telework_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "scale" &
-        in_working_or_observation_window == "working" &
-        in_weekday_correlation == "correlation status")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_scale"),
-          -contains("_observation_"),
-          -contains("_cor_telework_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "rank" &
-        in_working_or_observation_window == "working" &
-        in_weekday_correlation == "correlation status")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_rank"),
-          -contains("_observation_"),
-          -contains("_cor_telework_"),
-          -contains("_prop_pairs_"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "scale" &
-        in_working_or_observation_window == "observation" &
-        in_weekday_correlation == "proportion pairs")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_scale"),
-          -contains("_working_prop_"),
-          -contains("_cor_status_"),
-          -contains("cor_telework"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "rank" &
-        in_working_or_observation_window == "observation" &
-        in_weekday_correlation == "proportion pairs")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_rank"),
-          -contains("_working_prop_"),
-          -contains("_cor_status_"),
-          -contains("cor_telework"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "scale" &
-        in_working_or_observation_window == "working" &
-        in_weekday_correlation == "proportion pairs")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_scale"),
-          -contains("_observation_"),
-          -contains("_cor_status_"),
-          -contains("cor_telework"),
-        ) %>%
-        drop_na()
-    }
-
-    if (in_scale_or_rank == "rank" &
-        in_working_or_observation_window == "working" &
-        in_weekday_correlation == "proportion pairs")
-    {
-      step_01 <-
-        in_data %>%
-        select(
-          person_id,
-          ends_with("_rank"),
-          -contains("_observation_"),
-          -contains("_cor_status_"),
-          -contains("cor_telework"),
-        ) %>%
-        drop_na()
-    }
-
-    out <- 
-      step_01 %>% 
-      as_tibble()
-
-    return(out)
-  }
-```
-
-#### Making clusters of different sizes
-
-```{r}
-#' Make employee clusters of a variety of sizes and different specifications
-#'
-#' @param in_data Data to use
-#' @param in_scale_or_rank Option for which scaling procedure: "scale" (normalization) or "rank" (rank order)
-#' @param in_working_or_observation_window Option for proportion denominator: "observation" (proportion of entire observation window) or "working" (proportion of period employ was working onsite or via telework)
-#' @param in_weekday_correlation Option for inter weekday relationship: "correlation telework" (telework correlation between days of the week), "correlation status" (work status correlation based on ordered work status by days of the week), or "proportion pairs" (proportion of telework in pairs)
-#' @param in_number_of_clusters_start Minimum number of clusters to test
-#' @param in_number_of_clusters_end Maximum number of clusters to test
-#'
-#' @return Dataframe of clusters and associatied statistics
-#' @export
-#'
-#' @examples
-make_clusters <-
-  function(in_data,
-           in_scale_or_rank,
-           in_working_or_observation_window,
-           in_weekday_correlation,
-           in_number_of_clusters_start,
-           in_number_of_clusters_end)
-  {
-    stopifnot(in_scale_or_rank %in% c("scale", "rank"))
-    stopifnot(in_working_or_observation_window %in% c("observation", "working"))
-    stopifnot(
-      in_weekday_correlation %in% c(
-        "correlation telework",
-        "correlation status",
-        "proportion pairs"
-      )
-    )
-    stopifnot(in_number_of_clusters_start >= 1)
-    stopifnot(in_number_of_clusters_start <= in_number_of_clusters_end)
-
-    step_01 <-
-      in_data %>%
-      select_cluster_cols(
-        in_scale_or_rank = in_scale_or_rank,
-        in_working_or_observation_window = in_working_or_observation_window,
-        in_weekday_correlation = in_weekday_correlation
-      )
-
-    print(glue::glue("Review data for step 1. {Sys.time()}"))
-
-    step_01 %>%
-      skim() %>%
-      print()
-
-    print(glue::glue("Remove person_id. {Sys.time()}"))
-
-    step_02 <-
-      step_01 %>%
-      select(-person_id)
-
-    print(glue::glue("Review data for step 2. {Sys.time()}"))
-
-    step_02 %>%
-      skim() %>%
-      print()
-
-    print(
-      glue::glue(
-        "Create clusters of the data from {in_number_of_clusters_start} to {in_number_of_clusters_end}. {Sys.time()}"
-      )
-    )
-
-    out <-
-      tibble(k = in_number_of_clusters_start:in_number_of_clusters_end) %>%
-      mutate(
-        kclust = map(k, ~ kmeans(step_02, .x)),
-        tidied = map(kclust, tidy),
-        glanced = map(kclust, glance),
-        augmented = map(kclust, augment, step_01)
-      )
-
-    return(out)
-  }
-```
-
-#### Making clusters of different sizes, but only for `d` and adding specification
-
-```{r}
-make_clusters_d <- function(in_specification,
-                            in_scale_or_rank,
-                            in_working_or_observation_window,
-                            in_weekday_correlation,
-                            in_number_of_clusters_start,
-                            in_number_of_clusters_end)
-{
-  make_clusters(
-    in_data = d,
-    in_scale_or_rank = in_scale_or_rank,
-    in_working_or_observation_window = in_working_or_observation_window,
-    in_weekday_correlation = in_weekday_correlation,
-    in_number_of_clusters_start = in_number_of_clusters_start,
-    in_number_of_clusters_end = in_number_of_clusters_end
-  ) %>%
-    mutate(specification = in_specification)
-}
-```
-
-### Create clusters
-
-#### Create dataframe of all permutations
-
-This table shows all permutations of scaling (normalization, or rank), denominators for proportions (observation window or working days), and types of inter day correlations.
-
-```{r}
-specs <- 
-  tibble(
-  in_scale_or_rank = c(rep("scale", 6), rep("rank", 6)),
-  in_working_or_observation_window = rep(c(rep("observation", 3), rep("working", 3)), 2),
-  in_weekday_correlation = rep(
-    c(
-      "correlation telework",
-      "correlation status",
-      "proportion pairs"
-    ),
-    4
-  ),
-  in_number_of_clusters_start = rep(params$in_number_of_clusters_start, 12),
-  in_number_of_clusters_end = rep(params$in_number_of_clusters_end, 12)
-) %>% 
-  unite(col = "in_specification",everything(),remove = FALSE)
-```
-
-Review data.
-
-```{r}
-specs
-```
-
-#### Create clusters
-
-Iterate over `specs` creating and collecting dataframe of clusters from all of the above specifications.
-
-```{r}
-kclusts <- 
-  specs %>%
-  pmap_dfr(make_clusters_d)
-```
+<https://towardsdatascience.com/silhouette-method-better-than-elbow-method-to-find-optimal-clusters-378d62ff6891>
 
@@
 
-```{r}
+```{r eval=FALSE, include=FALSE}
 file_name <- glue::glue("clusters-employee-{Sys.Date()}.rdata")
@@
 
-```{r}
+```{r eval=FALSE, include=FALSE}
 save(kclusts, file = file.path(params$google_drive_home,"03. Data Collection","prepared-data",file_name))
@@
 
-```{r}
+```{r eval=FALSE, include=FALSE}
 rm(list = ls())
@@
 
-## Extraction time {.tabset .tabset-pills}
+## Analysis time {.tabset .tabset-pills}
 

### 2023-07-20 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessment.R
Create 03-02-data-analysis-employee-cluster-assessment.R

@@ -1,0 +1,56 @@
+
+# Start timer -------------------------------------------------------------
+
+tictoc::tic()
+
+# Libraries ---------------------------------------------------------------
+
+library(tidyverse)
+library(lubridate)
+library(purrr)
+
+# Parameters --------------------------------------------------------------
+
+author <- "Ben Jaques-Leslie"
+project_number <- 2312
+project_name <- "Occupancy Patterns"
+google_drive_home <- "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
+data_folder_1 <- "prepared-data"
+data_file_1 <- "prep_employees_2023-05-24.rdata"
+in_number_of_clusters_start <- 1
+in_number_of_clusters_end <- 20
+in_seed <- 27
+
+# Determine file name -----------------------------------------------------
+
+file_name <- glue::glue("03-02-data-analysis-employee-cluster-assessing-clusters-{project_number}-{str_replace_all(str_to_lower(project_name),' ','-')}-{today()}.html")
+
+file_name
+
+# Render data extraction --------------------------------------------------
+
+rmarkdown::render(input = here::here("04. Analysis",
+                                     "scripts",
+                                     "03-02-data-analysis-employee-cluster-assessing-clusters.Rmd"),
+                  params = list(
+                    author = author,
+                    project_number = project_number,
+                    project_name = project_name,
+                    google_drive_home = google_drive_home,
+                    data_folder_1 = data_folder_1,
+                    data_file_1 = data_file_1,
+                    in_number_of_clusters_start = in_number_of_clusters_start,
+                    in_number_of_clusters_end = in_number_of_clusters_end,
+                    in_seed = in_seed
+                  ),
+                  output_file =
+                    here::here("04. Analysis",
+                               "output",
+                               'html',
+                               file_name))
+
+
+# End timer ---------------------------------------------------------------
+
+tictoc::toc()
+

### 2023-07-20 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Update 03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Removed unneeded code and added parameters for the maximum number of clusters

@@
   data_folder_1: "prepared-data"
-  data_file_1: "clusters-employee-2023-06-08.rdata"
-  data_file_2: "prep_employees_2023-05-24.rdata"
-  in_number_of_clusters: 5
+  data_file_1: "prep_employees_2023-05-24.rdata"
   in_number_of_clusters_start: 1
-  in_number_of_clusters_end: 10
-  in_specification: "scale_working_proportion_pairs_1_10"
+  in_number_of_clusters_end: 20
   in_seed: 27
@@
 
-**Number of clusters**: `r params$in_number_of_clusters`
-
-**Specification** `r params$in_specification`
+**Number of clusters**: Testing `r params$in_number_of_clusters_start` to `r params$in_number_of_clusters_end`
 
@@
 
-Load `r params$data_file_1` from `r params$data_folder_1` data folder.
+Load `r params$data_file_2` from `r params$data_folder_1` data folder.
 
@@
 load(file = file.path(params$google_drive_home,"03. Data Collection",params$data_folder_1,params$data_file_1))
-```
-
-Review.
-
-```{r}
-kclusts %>% 
-  skim()
-```
-
-Load `r params$data_file_2` from `r params$data_folder_1` data folder.
-
-```{r}
-load(file = file.path(params$google_drive_home,"03. Data Collection",params$data_folder_1,params$data_file_2))
 ```
@@
 
-Generates 1 to 10 new clusters for specifications and creates elbow charts for each specification.
+Generates `r params$in_number_of_clusters_start` to `r params$in_number_of_clusters_end` new clusters for specifications and creates elbow charts for each specification.
 
@@
                          in_working_or_observation_window,
-                         in_weekday_correlation)
+                         in_weekday_correlation, 
+                            in_max_clusters)
 {
@@
       kmeans,
+      k.max = in_max_clusters,
       method = "wss",
@@
 
-Generates 1 to 10 new clusters for specifications and creates average silhouette charts for each specification.
+Generates `r params$in_number_of_clusters_start` to `r params$in_number_of_clusters_end` new clusters for specifications and creates average silhouette charts for each specification.
 
@@
                               in_working_or_observation_window,
-                              in_weekday_correlation)
+                              in_weekday_correlation, 
+                            in_max_clusters)
 {
@@
       kmeans,
+      k.max = in_max_clusters,
       method = "silhouette",
@@
 
-Generates 1 to 10 new clusters for specifications and creates gap statistic charts for each specification.
+Generates `r params$in_number_of_clusters_start` to `r params$in_number_of_clusters_end` new clusters for specifications and creates gap statistic charts for each specification.
 
@@
                             in_working_or_observation_window,
-                            in_weekday_correlation)
+                            in_weekday_correlation, 
+                            in_max_clusters)
 {
@@
       kmeans,
+      k.max = in_max_clusters,
       nstart = 25,
@@
   ) %>%
+   mutate(
+    in_max_clusters = params$in_number_of_clusters_end
+    ) %>% 
   distinct() %>% 
@@
   ) %>%
+  mutate(
+    in_max_clusters = params$in_number_of_clusters_end
+    ) %>% 
   distinct() %>%
-  # slice_head(n = 1) %>%
+  slice_head(n = 4) %>%
   pmap(make_silhouette_d)
@@
     in_specification
+  ) %>%
+   mutate(
+    in_max_clusters = params$in_number_of_clusters_end
     ) %>% 
@@
   distinct() %>% 
-  slice(rep(1:n(), each = 10)) %>% 
+  slice(rep(1:n(), each = params$in_number_of_clusters_end)) %>% 
   rownames_to_column(var = "temp_01") %>% 
   mutate(temp_02 = as.numeric(temp_01),
-         temp_03 = temp_02/10,
+         temp_03 = temp_02/params$in_number_of_clusters_end,
          temp_04 = ceiling(temp_03),
-         temp_05 = temp_04*10-10,
+         temp_05 = temp_04*params$in_number_of_clusters_end-params$in_number_of_clusters_end,
          temp_06 = temp_02 - temp_05) %>% 
@@
   filter(in_clusters > 1) %>% 
-  # slice(2) %>% 
+  slice(2) %>%
   pmap(make_fviz_silhouette_d)

### 2023-07-20 04. Analysis/scripts/make_specs.R
Update make_specs.R
Added new specifications to remove between day correlations

@@ -1,17 +1,18 @@
 specs <- 
   tibble(
-  in_scale_or_rank = c(rep("scale", 6), rep("rank", 6)),
-  in_working_or_observation_window = rep(c(rep("observation", 3), rep("working", 3)), 2),
+  in_scale_or_rank = c(rep("scale", 8), rep("rank", 8)),
+  in_working_or_observation_window = rep(c(rep("observation", 4), rep("working", 4)), 2),
   in_weekday_correlation = rep(
     c(
       "correlation telework",
       "correlation status",
-      "proportion pairs"
+      "proportion pairs",
+      "none"
     ),
     4
   ),
-  in_number_of_clusters_start = rep(params$in_number_of_clusters_start, 12),
-  in_number_of_clusters_end = rep(params$in_number_of_clusters_end, 12)
+  in_number_of_clusters_start = rep(params$in_number_of_clusters_start, 16),
+  in_number_of_clusters_end = rep(params$in_number_of_clusters_end, 16)
 ) %>% 
   unite(col = "in_specification",everything(),remove = FALSE) %>% 
   mutate(

### 2023-07-20 04. Analysis/scripts/select_cluster_cols.R
Update select_cluster_cols.R
Added cluster selection for no inter-weekday correlations

@@ -17,7 +17,7 @@ select_cluster_cols <-
   {
     stopifnot(in_scale_or_rank %in% c("scale", "rank"))
     stopifnot(in_working_or_observation_window %in% c("observation", "working"))
-    stopifnot(in_weekday_correlation %in% c("correlation telework", "correlation status","proportion pairs"))
+    stopifnot(in_weekday_correlation %in% c("correlation telework", "correlation status","proportion pairs","none"))
     
     if (in_scale_or_rank == "scale" &
         in_working_or_observation_window == "observation" &
@@ -207,6 +207,74 @@ select_cluster_cols <-
           -contains("_observation_"),
           -contains("_cor_status_"),
           -contains("cor_telework"),
+        ) %>%
+        drop_na()
+    }
+    
+    if (in_scale_or_rank == "scale" &
+        in_working_or_observation_window == "observation" &
+        in_weekday_correlation == "none")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_scale"),
+          -contains("_working_prop_"),
+          -contains("_cor_status_"),
+          -contains("_prop_pairs_"),
+          -contains("cor_telework")
+        ) %>%
+        drop_na()
+    }
+    
+    if (in_scale_or_rank == "rank" &
+        in_working_or_observation_window == "observation" &
+        in_weekday_correlation == "none")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_rank"),
+          -contains("_working_prop_"),
+          -contains("_cor_status_"),
+          -contains("_prop_pairs_"),
+          -contains("cor_telework")
+        ) %>%
+        drop_na()
+    }
+    
+    if (in_scale_or_rank == "scale" &
+        in_working_or_observation_window == "working" &
+        in_weekday_correlation == "none")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_scale"),
+          -contains("_observation_"),
+          -contains("_cor_status_"),
+          -contains("_prop_pairs_"),
+          -contains("cor_telework")
+        ) %>%
+        drop_na()
+    }
+    
+    if (in_scale_or_rank == "rank" &
+        in_working_or_observation_window == "working" &
+        in_weekday_correlation == "none")
+    {
+      step_01 <-
+        in_data %>%
+        select(
+          person_id,
+          ends_with("_rank"),
[…]

### 2023-08-03 04. Analysis/scripts/03-01-data-analysis-employee-cluster-identification.Rmd
Remove other statuses
Updating code to add parameter to remove statuses like other, missing, no response, and permanent departure

@@
                             in_weekday_correlation,
+                            in_remove_other_statuses,
                             in_number_of_clusters_start,
@@
     in_weekday_correlation = in_weekday_correlation,
+    in_remove_other_statuses = in_remove_other_statuses,
     in_number_of_clusters_start = in_number_of_clusters_start,

### 2023-08-03 04. Analysis/scripts/make_clusters.R

@@ -6,8 +6,9 @@
 #' @param in_weekday_correlation Option for inter weekday relationship: "correlation telework" (telework correlation between days of the week), "correlation status" (work status correlation based on ordered work status by days of the week), or "proportion pairs" (proportion of telework in pairs)
 #' @param in_number_of_clusters_start Minimum number of clusters to test
 #' @param in_number_of_clusters_end Maximum number of clusters to test
+#' @param in_remove_other_statuses TRUE/FALSE to remove statuses: missing, other, no response, and permanent departure
 #'
-#' @return Dataframe of clusters and associatied statistics
+#' @return Dataframe of clusters and associated statistics
 #' @export
 #'
 #' @examples
@@ -16,6 +17,7 @@ make_clusters <-
            in_scale_or_rank,
            in_working_or_observation_window,
            in_weekday_correlation,
+           in_remove_other_statuses,
            in_number_of_clusters_start,
            in_number_of_clusters_end)
   {
@@ -36,7 +38,8 @@ make_clusters <-
       select_cluster_cols(
         in_scale_or_rank = in_scale_or_rank,
         in_working_or_observation_window = in_working_or_observation_window,
-        in_weekday_correlation = in_weekday_correlation
+        in_weekday_correlation = in_weekday_correlation,
+        in_remove_other_statuses = in_remove_other_statuses
       )
     
     print(glue::glue("Review data for step 1. {Sys.time()}"))

### 2023-08-03 04. Analysis/scripts/make_specs.R

@@ -1,4 +1,4 @@
-specs <- 
+step_01 <- 
   tibble(
   in_scale_or_rank = c(rep("scale", 8), rep("rank", 8)),
   in_working_or_observation_window = rep(c(rep("observation", 4), rep("working", 4)), 2),
@@ -13,7 +13,17 @@ specs <-
   ),
   in_number_of_clusters_start = rep(params$in_number_of_clusters_start, 16),
   in_number_of_clusters_end = rep(params$in_number_of_clusters_end, 16)
-) %>% 
+) 
+
+step_02 <- 
+  step_01 %>% 
+  mutate(in_remove_other_statuses = TRUE) %>% 
+  bind_rows(step_01 %>% 
+              mutate(in_remove_other_statuses = FALSE)
+            )
+
+specs <- 
+  step_02 %>% 
   unite(col = "in_specification",everything(),remove = FALSE) %>% 
   mutate(
     in_specification = str_replace_all(in_specification," ","_")

### 2023-08-03 04. Analysis/scripts/select_cluster_cols.R

@@ -4,6 +4,7 @@
 #' @param in_scale_or_rank Option for which scaling procedure: "scale" (normalization) or "rank" (rank order)
 #' @param in_working_or_observation_window Option for proportion denominator: "observation" (proportion of entire observation window) or "working" (proportion of period employ was working onsite or via telework)
 #' @param in_weekday_correlation Option for inter weekday relationship: "correlation telework" (telework correlation between days of the week), "correlation status" (work status correlation based on ordered work status by days of the week), or "proportion pairs" (proportion of telework in pairs)
+#' @param in_remove_other_statuses TRUE/FALSE to remove statuses: missing, other, no response, and permanent departure
 #'
 #' @return Dataframe with only selected columns and dropped null observations
 #' @export
@@ -13,7 +14,8 @@ select_cluster_cols <-
   function(in_data,
            in_scale_or_rank,
            in_working_or_observation_window,
-           in_weekday_correlation)
+           in_weekday_correlation,
+           in_remove_other_statuses)
   {
     stopifnot(in_scale_or_rank %in% c("scale", "rank"))
     stopifnot(in_working_or_observation_window %in% c("observation", "working"))
@@ -277,6 +279,18 @@ select_cluster_cols <-
           -contains("cor_telework")
         ) %>%
         drop_na()
+    }
+    
+    if(in_remove_other_statuses)
+    {
+      step_01 <- 
+        step_01 %>% 
+        select(
+          -daily_status_missing,
+          -daily_status_no_response,
+          -daily_status_other,
+          -daily_status_permanent_departure
+        )
     }
     
     out <- 

### 2023-08-07 04. Analysis/scripts/03-01-data-analysis-employee-cluster-identification.R
Update 03-01-data-analysis-employee-cluster-identification.R
Updating the number of clusters

@@ -21,7 +21,7 @@ unique_identifier_1 <- c("date","person_id")
 date_cohort_month <-  "2022-03-01"
 observation_window_length_months <-  6
 in_number_of_clusters_start <- 1
-in_number_of_clusters_end <- 10
+in_number_of_clusters_end <- 20
 
 # Determine file name -----------------------------------------------------
 

### 2023-08-07 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Update 03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Adding option to remove other statuses

@@
                          in_weekday_correlation, 
+                         in_remove_other_statuses,
                             in_max_clusters)
@@
       in_working_or_observation_window = in_working_or_observation_window,
-      in_weekday_correlation = in_weekday_correlation
+      in_weekday_correlation = in_weekday_correlation,
+      in_remove_other_statuses = in_remove_other_statuses
     ) %>%
@@
                               in_weekday_correlation,
+                              in_remove_other_statuses,
                             in_max_clusters)
@@
                             in_weekday_correlation, 
+                            in_remove_other_statuses,
                             in_max_clusters)
@@
                             in_weekday_correlation,
+                            in_remove_other_statuses,
                             in_clusters)
@@
     in_weekday_correlation,
-    in_specification
+    in_specification,
+    in_remove_other_statuses
   ) %>%
@@
   filter(in_clusters > 1) %>% 
-  slice(2) %>%
+  # slice(2) %>%
   pmap(make_fviz_silhouette_d)

### 2023-08-07 04. Analysis/scripts/make_clusters.R
Update make_clusters.R
Adding "none" as an option

@@ -27,7 +27,8 @@ make_clusters <-
       in_weekday_correlation %in% c(
         "correlation telework",
         "correlation status",
-        "proportion pairs"
+        "proportion pairs",
+        "none"
       )
     )
     stopifnot(in_number_of_clusters_start >= 1)

### 2023-08-07 04. Analysis/scripts/select_cluster_cols.R
Update select_cluster_cols.R

@@ -286,10 +286,10 @@ select_cluster_cols <-
       step_01 <- 
         step_01 %>% 
         select(
-          -daily_status_missing,
-          -daily_status_no_response,
-          -daily_status_other,
-          -daily_status_permanent_departure
+          -starts_with("daily_status_missing"),
+          -starts_with("daily_status_no_response"),
+          -starts_with("daily_status_other"),
+          -starts_with("daily_status_permanent_departure")
         )
     }
     

### 2023-08-08 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Update 03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd

@@
   data_folder_1: "prepared-data"
-  data_file_1: "clusters-employee-2023-06-08.rdata"
-  data_file_2: "prep_employees_2023-05-24.rdata"
-  in_number_of_clusters: 5
-  in_specification: "scale_working_proportion_pairs_1_10"
+  data_file_1: "clusters-employee-2023-08-07.rdata"
+  data_file_2: "prep_employees_2023-06-13.rdata"
+  in_number_of_clusters_1: 2
+  in_number_of_clusters_2: 5
+  in_specification: "scale_observation_none_1_20_TRUE"
 
@@
   install.packages("geomtextpath")
+}
+if(!("oesrrr" %in% installed.packages()[,"Package"]))
+{
+  devtools::install_github(repo = "GSA/oesrrr")
 }
@@
 
-Filter to data with `r params$in_number_of_clusters` clusters with specification `r params$in_specification`.
-
-```{r}
-clust <- 
+Filter to data with `r params$in_number_of_clusters_1` clusters with specification `r params$in_specification`.
+
+```{r}
+clust_1 <- 
   kclusts %>% 
   filter(
-    k == params$in_number_of_clusters &
+    k == params$in_number_of_clusters_1 &
       specification == params$in_specification
@@
 
+Filter to data with `r params$in_number_of_clusters_2` clusters with specification `r params$in_specification`.
+
+```{r}
+clust_2 <- 
+  kclusts %>% 
+  filter(
+    k == params$in_number_of_clusters_2 &
+      specification == params$in_specification
+  )
+```
+
 ### Unnest
 
-Filter to data with `r params$in_number_of_clusters` clusters with specification `r params$in_specification`.
-
-```{r}
-clusters <- 
-  clust %>%
+Filter to data with `r params$in_number_of_clusters_2` clusters with specification `r params$in_specification`.
+
+```{r}
+clusters_1 <- 
+  clust_1 %>%
   unnest(cols = c(tidied))
 
+assignments_1 <- 
+  clust_1 %>% 
+  unnest(cols = c(augmented))
+
+clusterings_1 <- 
+  clust_1 %>%
+  unnest(cols = c(glanced))
+
+```
+
+Check data.
+
+```{r}
+assignments_1 %>% 
+  glimpse()
+```
+
+Filter to data with `r params$in_number_of_clusters_2` clusters with specification `r params$in_specification`.
+
+```{r}
+clusters_2 <- 
+  clust_2 %>%
+  unnest(cols = c(tidied))
+
+assignments_2 <- 
+  clust_2 %>% 
+  unnest(cols = c(augmented))
+
+clusterings_2 <- 
+  clust_2 %>%
+  unnest(cols = c(glanced))
+
+```
+
+Check data.
+
+```{r}
+assignments_2 %>% 
+  glimpse()
+```
+
+### Join assignments to employee data
+
+Function to rename `.cluster` column to include the number of clusters.
+
+```{r}
+rename_to_k <- function(in_data)
+{
+  tot_cluster <- in_data %>% select(k) %>% distinct() %>% pull()
+  out_data <-
+    in_data %>% rename_with( ~ glue::glue("{.x}_{tot_cluster}"), .cluster)
+  return(out_data)
+}
+```
+
+Apply function to assignments and join.
+
+```{r}
 assignments <-
-  clust %>% 
-  unnest(cols = c(augmented))
-
-clusterings <- 
-  clust %>%
-  unnest(cols = c(glanced))
-
-```
+  assignments_1 %>%
+  rename_to_k() %>%
+  select(person_id, starts_with(".cluster")) %>%
+  full_join(assignments_2 %>%
+              rename_to_k() %>%
+              select(person_id, starts_with(".cluster")))
+```
+Check data.
 
@@
 
-### Join assignments to employee data
+Join to `prep_employees`
 
@@
   assignments %>%
-  select(k, person_id, .cluster, specification) %>%
+  select(person_id, starts_with(".cluster")) %>%
   full_join(prep_employees) %>% 
   mutate(
-    .cluster = fct_na_value_to_level(.cluster, level = "(Missing)")
+    across(
+      .cols = starts_with(".cluster"),
+      .fns = ~fct_na_value_to_level(., level = "(Missing)")
+    )
   )
@@
   d %>%
-    summaries(.cluster) %>%
-    mutate(group = glue::glue("Cluster: {.cluster}")) %>%
-    select(-.cluster),
+    summaries(.cluster_2) %>%
+    mutate(group = glue::glue("Cluster 2: {.cluster_2}")) %>%
+    select(-.cluster_2),
+  d %>%
+    summaries(.cluster_5) %>%
+    mutate(group = glue::glue("Cluster 5: {.cluster_5}")) %>%
+    select(-.cluster_5),
   d %>% 
@@
 ```{r}
-gg_density <- function(in_data,in_variable)
+gg_density <- function(in_data,in_variable,in_cluster_number)
 {
@@
 
-  spec <- unique(in_data$specification)
-
-  clus <- unique(in_data$k)
-
-  in_data %>% 
-  ggplot(aes(x = !!in_variable_sym, color = .cluster, fill = .cluster)) +
+  # spec <- unique(in_data$specification)
+  # 
+  # clus <- unique(in_data$k)
+
+  if(in_cluster_number==2)
+  {
+    step_01 <-
+      in_data %>%
+      ggplot(aes(
+        x = !!in_variable_sym,
+        color = .cluster_2,
+        fill = .cluster_2
+      )) +
       geom_density(alpha = .25) +
-    geomtextpath::geom_textdensity(aes(label = .cluster), 
+      geomtextpath::geom_textdensity(
+        aes(label = .cluster_2),
         hjust = "ymax",
-                   vjust = 1, text_only = TRUE, text_smoothing = 0, straight = TRUE) + 
-    oescolorrrs::scale_color_oes(palette = 'accent colors') +
-    oescolorrrs::scale_fill_oes(palette = 'accent colors') +
+        vjust = 1,
+        text_only = TRUE,
+        text_smoothing = 0,
+        straight = TRUE
+      )
+  }
+
+  if(in_cluster_number==5)
+  {
+    step_01 <-
+      in_data %>%
+      ggplot(aes(
+        x = !!in_variable_sym,
+        color = .cluster_5,
+        fill = .cluster_5
+      )) +
+      geom_density(alpha = .25) +
+      geomtextpath::geom_textdensity(
+        aes(label = .cluster_5),
+        hjust = "ymax",
+        vjust = 1,
+        text_only = TRUE,
+        text_smoothing = 0,
+        straight = TRUE
+      )
+  }
+
+  step_01 +
     theme_fivethirtyeight() +
@@
       title = glue::glue("Histogram of `{in_variable}`"),
-      caption = glue::glue("For specification {spec} with {clus} clusters.")
+      caption = glue::glue("For {in_cluster_number} clusters.")
     ) +
@@
   select_if(is.numeric) %>% 
-  select(-k) %>% 
   names()
@@
 num_vars[1:20] %>% 
-  map(~gg_density(d,in_variable = .))
+  map(~gg_density(d,in_variable = .,in_cluster_number = 2))
+```
+
+### Telework
+
+#### Number of days
+
+```{r}
+gg_density(d,"daily_status_teleworking", in_cluster_number = 2)
+```
+
+```{r}
+gg_density(d,"daily_status_teleworking", in_cluster_number = 5)
+```
+
+#### Proportion of observation window
+
+```{r}
+gg_density(d,"daily_status_teleworking_observation_prop", in_cluster_number = 2)
+```
+
+```{r}
+gg_density(d,"daily_status_teleworking_observation_prop", in_cluster_number = 5)
+```
+
+### Reporting to job site
+
+#### Number of days
+
+```{r}
+gg_density(d,"daily_status_reporting_to_job_site", in_cluster_number = 2)
+```
+
+```{r}
+gg_density(d,"daily_status_reporting_to_job_site", in_cluster_number = 5)
+```
+
+#### Proportion of observation window
+
+```{r}
+gg_density(d,"daily_status_reporting_to_job_site_observation_prop", in_cluster_number = 2)
+```
+
+```{r}
+gg_density(d,"daily_status_reporting_to_job_site_observation_prop", in_cluster_number = 5)
+```
+
+### Collocation with at least one team member
+
+#### Number of days
+
+```{r}
+gg_density(d,"days_colocated_1", in_cluster_number = 2)
+```
+
+```{r}
+gg_density(d,"days_colocated_1", in_cluster_number = 5)
+```
+
+#### Proportion of observation window
+
+```{r}
+gg_density(d,"days_colocated_1_observation_prop", in_cluster_number = 2)
+```
+
+```{r}
+gg_density(d,"days_colocated_1_observation_prop", in_cluster_number = 5)
+```
+
+### Collocation with supervisor
+
+#### Number of days
+
+```{r}
+gg_density(d,"days_colocated_supervisor", in_cluster_number = 2)
+```
+
+```{r}
+gg_density(d,"days_colocated_supervisor", in_cluster_number = 5)
+```
+
+#### Proportion of observation window
+
+```{r}
+gg_density(d,"days_colocated_supervisor_observation_prop", in_cluster_number = 2)
+```
+
+```{r}
+gg_density(d,"days_colocated_supervisor_observation_prop", in_cluster_number = 5)
+```
+
+### Collocation with teamn
+
+#### Number of days
+
+```{r}
+gg_density(d,"days_colocated_team", in_cluster_number = 2)
+```
+
+```{r}
+gg_density(d,"days_colocated_team", in_cluster_number = 5)
+```
+
+#### Proportion of observation window
+
+```{r}
+gg_density(d,"days_colocated_team_observation_prop", in_cluster_number = 2)
+```
+
+```{r}
+gg_density(d,"days_colocated_team_observation_prop", in_cluster_number = 5)
+```
+
+### Whole team telewords
+
+#### Number of days
+
+```{r}
+gg_density(d,"days_colocated_team", in_cluster_number = 2)
+```
+
+```{r}
+gg_density(d,"days_colocated_team", in_cluster_number = 5)
+```
+
+#### Proportion of observation window
+
+```{r}
+gg_density(d,"days_colocated_team_observation_prop", in_cluster_number = 2)
+```
+
+```{r}
+gg_density(d,"days_colocated_team_observation_prop", in_cluster_number = 5)
+```
+
+### Working days
+
+#### Number of days
+
+```{r}
+gg_density(d,"working_days", in_cluster_number = 2)
+```
+
+```{r}
+gg_density(d,"working_days", in_cluster_number = 5)
+```
+
+### Team size
+
+#### Number of employees
+
+```{r}
+gg_density(d,"team_size_mode", in_cluster_number = 2)
+```
+
+```{r}
+gg_density(d,"team_size_mode", in_cluster_number = 5)
+```
+
+#### Proportion of observation window
+
+```{r}
+gg_density(d,"daily_status_reporting_to_job_site_observation_prop", in_cluster_number = 2)
+```
+
+```{r}
+gg_density(d,"daily_status_reporting_to_job_site_observation_prop", in_cluster_number = 5)
+```
+
+## Summary statistics
+
+```{r}
+d %>% 
+  group_by(.cluster_2) %>% 
+  skim(daily_status_reporting_to_job_site,
+       daily_status_reporting_to_job_site_observation_prop,
+       daily_status_teleworking,
+       daily_status_teleworking_observation_prop,
+       days_colocated_1,
+       days_colocated_1_observation_prop,
+       days_colocated_supervisor,
+       days_colocated_supervisor_observation_prop,
+       days_colocated_team,
+       days_colocated_team_observation_prop,
+       days_telework_team,
+       days_telework_team_observation_prop,
+       working_days,
+       team_size_mode) %>% 
+  as.data.frame()
+```
+
+```{r}
+d %>% 
+  group_by(.cluster_5) %>% 
+  skim(daily_status_reporting_to_job_site,
+       daily_status_reporting_to_job_site_observation_prop,
+       daily_status_teleworking,
+       daily_status_teleworking_observation_prop,
+       days_colocated_1,
+       days_colocated_1_observation_prop,
+       days_colocated_supervisor,
+       days_colocated_supervisor_observation_prop,
+       days_colocated_team,
+       days_colocated_team_observation_prop,
+       days_telework_team,
+       days_telework_team_observation_prop,
+       working_days,
+       team_size_mode) %>% 
+  as.data.frame()
 ```

### 2023-08-09 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Update 03-02-data-analysis-employee-cluster-assessing-clusters.Rmd
Adding remove other statuses parameteer

@@
                             in_number_of_clusters_start,
-                            in_number_of_clusters_end)
+                            in_number_of_clusters_end,
+                            in_remove_other_statuses )
 {
@@
     in_number_of_clusters_start = in_number_of_clusters_start,
-    in_number_of_clusters_end = in_number_of_clusters_end
+    in_number_of_clusters_end = in_number_of_clusters_end,
+    in_remove_other_statuses  = in_remove_other_statuses 
   ) %>%
@@
   specs %>%
-  slice_head(n = 1) %>% 
+  # slice_head(n = 1) %>% 
   pmap_dfr(make_fviz_clusters_d)

### 2023-08-09 04. Analysis/scripts/make_fviz_clusters.R
Update make_fviz_clusters.R
Adding remove other statuses parameter

@@ -17,7 +17,8 @@ make_fviz_clusters <-
            in_working_or_observation_window,
            in_weekday_correlation,
            in_number_of_clusters_start,
-           in_number_of_clusters_end)
+           in_number_of_clusters_end,
+           in_remove_other_statuses)
   {
     stopifnot(in_scale_or_rank %in% c("scale", "rank"))
     stopifnot(in_working_or_observation_window %in% c("observation", "working"))
@@ -25,7 +26,8 @@ make_fviz_clusters <-
       in_weekday_correlation %in% c(
         "correlation telework",
         "correlation status",
-        "proportion pairs"
+        "proportion pairs",
+        "none"
       )
     )
     stopifnot(in_number_of_clusters_start >= 1)
@@ -36,7 +38,8 @@ make_fviz_clusters <-
       select_cluster_cols(
         in_scale_or_rank = in_scale_or_rank,
         in_working_or_observation_window = in_working_or_observation_window,
-        in_weekday_correlation = in_weekday_correlation
+        in_weekday_correlation = in_weekday_correlation,
+        in_remove_other_statuses
       )
     
     print(glue::glue("Review data for step 1. {Sys.time()}"))

### 2023-08-09 04. Analysis/scripts/03-01-data-analysis-employee-cluster-identification.R
Update 03-01-data-analysis-employee-cluster-identification.R
New version of data

@@ -16,7 +16,7 @@ project_number <-  2312
 project_name <-  "Occupancy Patterns"
 google_drive_home <-  "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
 data_folder_1 <-  "prepared-data"
-data_file_1 <-  "prep_employees_2023-05-24.rdata"
+data_file_1 <-  "prep_employees_2023-08-09.rdata"
 unique_identifier_1 <- c("date","person_id")
 date_cohort_month <-  "2022-03-01"
 observation_window_length_months <-  6

### 2023-08-09 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Update 03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Adding narrative descriptions

@@
 knitr::opts_chunk$set(echo = TRUE)
+options(scipen=999)
 tictoc::tic()
@@
 
+## Cluster descriptions {.tabset .tabset-pills}
+
+Clusters 2(1): **Teleworkers**
+
+Very low number of days reporting to the job site.
+Majority of time telework.
+Very few days co-located with at least one team member, a supervisor, or the whole team.
+Many days where the whole team is co-located, but not the majority.
+High number of working days.
+
+Clusters 2(2): **Everyone else**
+
+Higher number of days reporting to job site, but with large variance.
+Lower proportion of days teleworking, but still about a quarter of days.
+Again, higher variance of telework.
+Some days co-located with at least one team member and the majority of days working at the site.
+Many days working onsite with supervisor, but very few days where the whole team is co-located.
+Very few days where the whole team is co-located.
+Lower number of working days.
+
+Clusters 5(1): **Teleworkers**
+
+Very low number of days (~3) reporting to the job site.
+Most days (~119) employees telework.
+Hardly any days co-located with at least one team member (<1), supervisor (<1), or whole team (<1).
+Many days (~54) where entire team works remotely.
+Many working days (~122).
+Team is average size (~6).
+
+Clusters 5(2): **Teleworkers that go to the office sometimes**
+
+A few days (~14) working at the job site, but high variation.
+Majority of days(~98) employees telework.
+Some days co-located with at least one team member (~6) or supervisor (~3).
+Few days co-located with entire team (~1).
+Some days (~19) where the entire team works remotely.
+Many working days (~112).
+Team is large (~9).
+
+Clusters 5(3): **Hybrid workers**
+
+Some days (~69) with employees working to the job site.
+Staff often telework (~48), but high variance.
+Many days co-located with at least one team member (~29) or with supervisor (~13).
+Few days co-located with entire team (~1).
+Few days (~5) where the whole team is remote.
+Many working days (~115).
+Team is average size (~6).
+
+Clusters 5(4): **Onsite workers**
+
+Employees that report to the job site for most days (~97).
+Some days (~22) telework.
+Many days co-located with at least one team member (~74), supervisor (~60), or whole team (~17), but high variance.
+Few days (~4) where the whole team is remote, but high variance.
+Many working days (~119).
+Team is smaller (~5)
+
+Clusters 5(5): **Non-workers**
+Low number of days (~5) reporting to the site, but high variance.
+Some days (~27) telework, but high variance.
+Few days co-located with at least one team member (2)  or with supervisor (~1).
+Almost no days (<1) with the whole team co-located.
+Several days (~9) where the entire team works remotely.
+Few working days (~34) and high variance.
+Team is large (~9) and high variance.
+
 ## Work pattern statistics {.tabset .tabset-pills}
+
+### Summary statistics
+
+```{r}
+d %>% 
+  group_by(.cluster_2) %>% 
+  skim(daily_status_reporting_to_job_site,
+       daily_status_reporting_to_job_site_observation_prop,
+       daily_status_teleworking,
+       daily_status_teleworking_observation_prop,
+       days_colocated_1,
+       days_colocated_1_observation_prop,
+       days_colocated_supervisor,
+       days_colocated_supervisor_observation_prop,
+       days_colocated_team,
+       days_colocated_team_observation_prop,
+       days_telework_team,
+       days_telework_team_observation_prop,
+       working_days,
+       team_size_mode) %>% 
+  as.data.frame()
+```
+
+```{r}
+d %>% 
+  group_by(.cluster_5) %>% 
+  skim(daily_status_reporting_to_job_site,
+       daily_status_reporting_to_job_site_observation_prop,
+       daily_status_teleworking,
+       daily_status_teleworking_observation_prop,
+       days_colocated_1,
+       days_colocated_1_observation_prop,
+       days_colocated_supervisor,
+       days_colocated_supervisor_observation_prop,
+       days_colocated_team,
+       days_colocated_team_observation_prop,
+       days_telework_team,
+       days_telework_team_observation_prop,
+       working_days,
+       team_size_mode) %>% 
+  as.data.frame()
+```
+
+### Summary statistics
+
+```{r}
+d %>% 
+  group_by(.cluster_2) %>% 
+  skim(starts_with("rule_based_"),
+       -ends_with("working")) %>% 
+  as.data.frame()
+```
+
+```{r}
+d %>% 
+  group_by(.cluster_5) %>% 
+  skim(starts_with("rule_based_"),
+       -ends_with("working")) %>% 
+  as.data.frame()
+```
+
+```{r}
+d %>% 
+  group_by(.cluster_2) %>% 
+  skim(exit_employment,
+       multiple_supervisors,
+       gsa_sso) %>% 
+  as.data.frame()
+```
+
+```{r}
+d %>% 
+  group_by(.cluster_5) %>% 
+  skim(exit_employment,
+       multiple_supervisors,
+       gsa_sso) 
+```
+
+```{r}
+names(d)
+```
 
@@
 gg_density(d,"daily_status_reporting_to_job_site_observation_prop", in_cluster_number = 5)
-```
-
-## Summary statistics
-
-```{r}
-d %>% 
-  group_by(.cluster_2) %>% 
-  skim(daily_status_reporting_to_job_site,
-       daily_status_reporting_to_job_site_observation_prop,
-       daily_status_teleworking,
-       daily_status_teleworking_observation_prop,
-       days_colocated_1,
-       days_colocated_1_observation_prop,
-       days_colocated_supervisor,
-       days_colocated_supervisor_observation_prop,
-       days_colocated_team,
-       days_colocated_team_observation_prop,
-       days_telework_team,
-       days_telework_team_observation_prop,
-       working_days,
-       team_size_mode) %>% 
-  as.data.frame()
-```
-
-```{r}
-d %>% 
-  group_by(.cluster_5) %>% 
-  skim(daily_status_reporting_to_job_site,
-       daily_status_reporting_to_job_site_observation_prop,
-       daily_status_teleworking,
-       daily_status_teleworking_observation_prop,
-       days_colocated_1,
-       days_colocated_1_observation_prop,
-       days_colocated_supervisor,
-       days_colocated_supervisor_observation_prop,
-       days_colocated_team,
-       days_colocated_team_observation_prop,
-       days_telework_team,
-       days_telework_team_observation_prop,
-       working_days,
-       team_size_mode) %>% 
-  as.data.frame()
 ```

### 2023-08-09 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessment.R
Update 03-02-data-analysis-employee-cluster-assessment.R

@@ -16,7 +16,7 @@ project_number <- 2312
 project_name <- "Occupancy Patterns"
 google_drive_home <- "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
 data_folder_1 <- "prepared-data"
-data_file_1 <- "prep_employees_2023-05-24.rdata"
+data_file_1 <- "prep_employees_2023-08-09.rdata"
 in_number_of_clusters_start <- 1
 in_number_of_clusters_end <- 20
 in_seed <- 27

### 2023-08-10 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Update 03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Adding more detail to the descriptions

@@
   data_folder_1: "prepared-data"
-  data_file_1: "clusters-employee-2023-08-07.rdata"
-  data_file_2: "prep_employees_2023-06-13.rdata"
+  data_file_1: "clusters-employee-2023-08-09.rdata"
+  data_file_2: "prep_employees_2023-08-09.rdata"
   in_number_of_clusters_1: 2
@@
 ```{r}
+d %>% names()
+```
+
+```{r}
 d %>%
   group_by(.cluster_2) %>%
-  skim(exit_employment,
-       multiple_supervisors,
-       gsa_sso) %>% 
-  as.data.frame()
-```
+  skim(exit_employment,multiple_supervisors)
+```
+
+```{r}
+d %>%
+  group_by(.cluster_5) %>%
+  skim(exit_employment,multiple_supervisors)
+```
+
+```{r}
+d %>% 
+  group_by(.cluster_2) %>% 
+  count(sso) %>% 
+  ungroup() %>% 
+  left_join(
+    d %>% 
+  count(.cluster_2, name = "tot")
+  ) %>% 
+  mutate(
+    prop = n/tot
+  ) %>% 
+  ggplot(aes(x = sso, y =  prop,fill = .cluster_2)) +
+  geom_col(position = "dodge") 
+```
+
+```{r}
+d %>% 
+  group_by(.cluster_5) %>% 
+  count(sso) %>% 
+  ungroup() %>% 
+  left_join(
+    d %>% 
+  count(.cluster_5, name = "tot")
+  ) %>% 
+  mutate(
+    prop = n/tot
+  ) %>% 
+  ggplot(aes(x = sso, y =  prop,fill = .cluster_5)) +
+  geom_col(position = "dodge") +
+  facet_wrap(facets = vars(sso), scales = "free")
+```
+
+## Cluster descriptions {.tabset .tabset-pills}
+
+Clusters 2(1): **Teleworkers**
+
+Very low number of days reporting to the job site.
+Majority of time telework.
+Very few days co-located with at least one team member, a supervisor, or the whole team.
+Many days where the whole team is co-located, but not the majority.
+High number of working days.
+
+Few people exit employment (~3%) and some have multiple supervisors (~26%).
+
+Disproportionately from FAS, GSA IT, OCFO, OGP, and OHRM, and fewer in PBS
+
+Clusters 2(2): **Everyone else**
+
+Higher number of days reporting to job site, but with large variance.
+Lower proportion of days teleworking, but still about a quarter of days.
+Again, higher variance of telework.
+Some days co-located with at least one team member and the majority of days working at the site.
+Many days working onsite with supervisor, but very few days where the whole team is co-located.
+Very few days where the whole team is co-located.
+Lower number of working days.
+
+Some people exit employment (~15%) and some have multiple supervisors (~22%).
+
+Majority are from PBS.
+
+Clusters 5(1): **Teleworkers**
+
+Very low number of days (~3) reporting to the job site.
+Most days (~119) employees telework.
+Hardly any days co-located with at least one team member (<1), supervisor (<1), or whole team (<1).
+Many days (~54) where entire team works remotely.
+Many working days (~122).
+Team is average size (~6).
+
+Almost no one (<.1%) exit employment. Some have multiple employers (20-30%).
+
+Clusters 5(2): **Teleworkers that go to the office sometimes**
+
+A few days (~14) working at the job site, but high variation.
+Majority of days(~98) employees telework.
+Some days co-located with at least one team member (~6) or supervisor (~3).
+Few days co-located with entire team (~1).
+Some days (~19) where the entire team works remotely.
+Many working days (~112).
+Team is large (~9).
+
+Very few people exit employment (~3%). Some have multiple employers (20-30%).
+
+Clusters 5(3): **Hybrid workers**
+
+Some days (~69) with employees working to the job site.
+Staff often telework (~48), but high variance.
+Many days co-located with at least one team member (~29) or with supervisor (~13).
+Few days co-located with entire team (~1).
+Few days (~5) where the whole team is remote.
+Many working days (~115).
+Team is average size (~6).
+
+Very few people exit employment (~2%). Some have multiple employers (20-30%).
+
+Clusters 5(4): **Onsite workers**
+
+Employees that report to the job site for most days (~97).
+Some days (~22) telework.
+Many days co-located with at least one team member (~74), supervisor (~60), or whole team (~17), but high variance.
+Few days (~4) where the whole team is remote, but high variance.
+Many working days (~119).
+Team is smaller (~5).
+
+Very few people exit employment (~2%). Some have multiple employers (20-30%).
+
+Clusters 5(5): **Non-workers**
+
+Low number of days (~5) reporting to the site, but high variance.
+Some days (~27) telework, but high variance.
+Few days co-located with at least one team member (2)  or with supervisor (~1).
+Almost no days (<1) with the whole team co-located.
+Several days (~9) where the entire team works remotely.
+Few working days (~34) and high variance.
+Team is large (~9) and high variance.
+
+Many people exit employment (~54%). Some have multiple employers (20-30%).
 

### 2023-08-10 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Update 03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd

@@
   ggplot(aes(x = sso, y =  prop,fill = .cluster_2)) +
-  geom_col(position = "dodge") 
+  geom_col(position = "dodge")  +
+  facet_wrap(facets = vars(sso), scales = "free")
 ```
@@
 
+Majority are freom PBS.
+
 Clusters 5(4): **Onsite workers**
@@
 Very few people exit employment (~2%). Some have multiple employers (20-30%).
+
+Majority are freom PBS.
 

### 2023-08-21 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Update 03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Updated folder path and added some more descriptive

--- 2023-08-10 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
@@
   project_name: "Occupancy Patterns"
-  google_drive_home: "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
+  google_drive_home: "G:/Shared drives/GSA Evaluation Division/Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
   data_folder_1: "prepared-data"
@@
   install.packages("arsenal")
+}
+if(!("beepr" %in% installed.packages()[,"Package"]))
+{
+  install.packages("beepr")
 }
@@
 
-### Summary statistics
+### Cluster summary statistics
+
+#### Rule-based groups
+
+##### Two clusters
 
@@
 
+##### Five clusters
+
 ```{r}
@@
 
+#### Exiting employment and multiple supervisors
+
+##### Two clusters
+
 ```{r}
@@
 ```
+
+#### SSO
+
+##### Two clusters
 
@@
   ) %>% 
-  ggplot(aes(x = sso, y =  prop,fill = .cluster_2)) +
-  geom_col(position = "dodge") 
-```
+  ggplot(aes(x = .cluster_2, y =  prop,fill = .cluster_2)) +
+  geom_col(position = "dodge")  +
+  facet_wrap(facets = vars(sso), scales = "free_y")
+```
+
+##### Five clusters
 
@@
   ) %>% 
-  ggplot(aes(x = sso, y =  prop,fill = .cluster_5)) +
+  ggplot(aes(x = .cluster_5, y =  prop,fill = .cluster_5)) +
   geom_col(position = "dodge") +
-  facet_wrap(facets = vars(sso), scales = "free")
+  facet_wrap(facets = vars(sso)
+             , scales = "free_y"
+             )
+```
+
+#### SSO
+
+##### Two clusters
+
+```{r}
+d %>% 
+  group_by(.cluster_2) %>% 
+  count(short_id) %>% 
+  ungroup() %>% 
+  left_join(
+    d %>% 
+  count(.cluster_2, name = "tot")
+  ) %>% 
+  mutate(
+    prop = n/tot
+  ) %>% 
+  ggplot(aes(x = .cluster_2, y =  prop,fill = .cluster_2)) +
+  geom_col(position = "dodge")  +
+  facet_wrap(facets = vars(short_id), scales = "free_y")
+```
+
+##### Five clusters
+
+```{r}
+d %>% 
+  group_by(.cluster_5) %>% 
+  count(sso) %>% 
+  ungroup() %>% 
+  left_join(
+    d %>% 
+  count(.cluster_5, name = "tot")
+  ) %>% 
+  mutate(
+    prop = n/tot
+  ) %>% 
+  ggplot(aes(x = .cluster_5, y =  prop,fill = .cluster_5)) +
+  geom_col(position = "dodge") +
+  facet_wrap(facets = vars(sso)
+             , scales = "free_y"
+             )
 ```
@@
 
+High proportion in FAS, GSAIT, OCFO, OGP, OHRM, OSDBU and lower in PBS, OCE, IOA, and OMA.
+
 Clusters 5(2): **Teleworkers that go to the office sometimes**
@@
 
+High proportion in FAS, GSAIT, OCFO, OCR, OGP, OHRM, OSDBU and lower in PBS, OCE, OSC, OSDBU, IOA, and OMA.
+
 Clusters 5(3): **Hybrid workers**
@@
 
+High proportion in IOA, OGC, OMA, OSC, and PBS and lower in FAS, GSA IT, OCE, OCFO, OCR, OGP, OHRM, and OSDBU.
+
 Clusters 5(4): **Onsite workers**
@@
 Very few people exit employment (~2%). Some have multiple employers (20-30%).
+
+High proportion in OAS, and PBS, and lower in FAS, GSA IT, IOA, OCE, OCFO, OCIA, OCR, OGC, OGP, OHRM, OMA, OSC, and OSDBU.
 
@@
 
+High proportion in FAS, GSA IT, OCE, OCIA, OCR, OSC, and OSDBU and lower in OMA.
+
 ```{r}
@@
   skim(exit_employment,
-       multiple_supervisors,
-       gsa_sso) 
+       multiple_supervisors) 
 ```
@@
 names(d)
+```
+
+# CONTINUE FROM HERE
+
+```{r}
+beepr::beep(sound = 5)
+```
+
+```{r}
+
 ```

### 2023-08-22 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Update 03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Adding summaries for GSA regions, position categories and grades.

@@
 
-#### SSO
+#### GSA Region
 
@@
 ```{r}
-d %>% 
+level_10 <- 
+  d %>% 
+  count(gsa_region) %>% 
+  arrange(desc(n)) %>% 
+  slice(10) %>% 
+  pull(n)
+
+d %>%
+  # mutate(gsa_region = fct_lump_min(gsa_region, min = level_10)) %>%
   group_by(.cluster_2) %>%
-  count(short_id) %>% 
+  count(gsa_region) %>%
   ungroup() %>%
-  left_join(
-    d %>% 
-  count(.cluster_2, name = "tot")
-  ) %>% 
-  mutate(
-    prop = n/tot
-  ) %>% 
-  ggplot(aes(x = .cluster_2, y =  prop,fill = .cluster_2)) +
+  left_join(d %>%
+              count(.cluster_2, name = "tot")) %>%
+  mutate(prop = n / tot) %>%
+  ggplot(aes(x = .cluster_2, y =  prop, fill = .cluster_2)) +
   geom_col(position = "dodge")  +
-  facet_wrap(facets = vars(short_id), scales = "free_y")
+  facet_wrap(facets = vars(gsa_region), scales = "free_y")
 ```
@@
 ```{r}
-d %>% 
+level_10 <- 
+  d %>% 
+  count(gsa_region) %>% 
+  arrange(desc(n)) %>% 
+  slice(10) %>% 
+  pull(n)
+
+d %>%
+  # mutate(gsa_region = fct_lump_min(gsa_region, min = level_10)) %>%
   group_by(.cluster_5) %>%
-  count(sso) %>% 
+  count(gsa_region) %>%
   ungroup() %>%
-  left_join(
-    d %>% 
-  count(.cluster_5, name = "tot")
-  ) %>% 
-  mutate(
-    prop = n/tot
-  ) %>% 
-  ggplot(aes(x = .cluster_5, y =  prop,fill = .cluster_5)) +
+  left_join(d %>%
+              count(.cluster_5, name = "tot")) %>%
+  mutate(prop = n / tot) %>%
+  ggplot(aes(x = .cluster_5, y =  prop, fill = .cluster_5)) +
   geom_col(position = "dodge")  +
-  facet_wrap(facets = vars(sso)
-             , scales = "free_y"
-             )
+  facet_wrap(facets = vars(gsa_region), scales = "free_y")
+```
+
+#### Position category
+
+##### Two clusters
+
+```{r}
+level_10 <- 
+  d %>% 
+  count(position_category_description) %>% 
+  arrange(desc(n)) %>% 
+  slice(10) %>% 
+  pull(n)
+
+d %>%
+  # mutate(position_category_description = fct_lump_min(position_category_description, min = level_10)) %>%
+  group_by(.cluster_2) %>%
+  count(position_category_description) %>%
+  ungroup() %>%
+  left_join(d %>%
+              count(.cluster_2, name = "tot")) %>%
+  mutate(prop = n / tot) %>%
+  ggplot(aes(x = .cluster_2, y =  prop, fill = .cluster_2)) +
+  geom_col(position = "dodge")  +
+  facet_wrap(facets = vars(position_category_description), scales = "free_y")
+```
+
+##### Five clusters
+
+```{r}
+level_10 <- 
+  d %>% 
+  count(position_category_description) %>% 
+  arrange(desc(n)) %>% 
+  slice(10) %>% 
+  pull(n)
+
+d %>%
+  # mutate(position_category_description = fct_lump_min(position_category_description, min = level_10)) %>%
+  group_by(.cluster_5) %>%
+  count(position_category_description) %>%
+  ungroup() %>%
+  left_join(d %>%
+              count(.cluster_5, name = "tot")) %>%
+  mutate(prop = n / tot) %>%
+  ggplot(aes(x = .cluster_5, y =  prop, fill = .cluster_5)) +
+  geom_col(position = "dodge")  +
+  facet_wrap(facets = vars(position_category_description), scales = "free_y")
+```
+
+#### Position category
+
+##### Two clusters
+
+```{r}
+level_10 <- 
+  d %>% 
+  count(grade) %>% 
+  arrange(desc(n)) %>% 
+  slice(10) %>% 
+  pull(n)
+
+d %>%
+  mutate(grade = fct_lump_min(grade, min = level_10)) %>%
+  group_by(.cluster_2) %>%
+  count(grade) %>%
+  ungroup() %>%
+  left_join(d %>%
+              count(.cluster_2, name = "tot")) %>%
+  mutate(prop = n / tot) %>%
+  ggplot(aes(x = .cluster_2, y =  prop, fill = .cluster_2)) +
+  geom_col(position = "dodge")  +
+  facet_wrap(facets = vars(grade), scales = "free_y")
+```
+
+##### Five clusters
+
+```{r}
+level_10 <- 
+  d %>% 
+  count(grade) %>% 
+  arrange(desc(n)) %>% 
+  slice(10) %>% 
+  pull(n)
+
+d %>%
+  mutate(grade = fct_lump_min(grade, min = level_10)) %>%
+  group_by(.cluster_5) %>%
+  count(grade) %>%
+  ungroup() %>%
+  left_join(d %>%
+              count(.cluster_5, name = "tot")) %>%
+  mutate(prop = n / tot) %>%
+  ggplot(aes(x = .cluster_5, y =  prop, fill = .cluster_5)) +
+  geom_col(position = "dodge")  +
+  facet_wrap(facets = vars(grade), scales = "free_y")
 ```
@@
 
+Position categories tend to be Offsite, Onsite Flexible, and Position Has Changed. A very small proportion of Onsite Required.
+
 Few people exit employment (~3%) and some have multiple supervisors (~26%).
 
-Disproportionately from FAS, GSA IT, OCFO, OGP, and OHRM, and fewer in PBS
+Disproportionately from FAS, GSA IT, OCFO, OGP, and OHRM, and fewer in PBS.
+
+Disproportionately in Region 0.
 
@@
 
+Position categories tend to be Onsite Required. All (Missing) and most are in this cluster.
+
 Some people exit employment (~15%) and some have multiple supervisors (~22%).
@@
 Majority are from PBS.
+
+Disproportionately in all regions apart from 0.
 
@@
 
+Position categories tend to be Offsite and Position Has Changed. A small proportion of Onsite Required.
+
 Almost no one (<.1%) exit employment. Some have multiple employers (20-30%).
@@
 High proportion in FAS, GSAIT, OCFO, OGP, OHRM, OSDBU and lower in PBS, OCE, IOA, and OMA.
+
+Disproportionately in Region 0 and Region 2.
 
@@
 
+Position categories tend to be Offsite and Position Has Changed. A small proportion of Onsite Required.
+
 Very few people exit employment (~3%). Some have multiple employers (20-30%).
@@
 High proportion in FAS, GSAIT, OCFO, OCR, OGP, OHRM, OSDBU and lower in PBS, OCE, OSC, OSDBU, IOA, and OMA.
+
+Disproportionately in Region 0.
 
@@
 
+Position categories tend to be Onsite Flexible.
+
 Very few people exit employment (~2%). Some have multiple employers (20-30%).
@@
 High proportion in IOA, OGC, OMA, OSC, and PBS and lower in FAS, GSA IT, OCE, OCFO, OCR, OGP, OHRM, and OSDBU.
+
+Disproportionately in Region 1, Region 4, Region 5, Region 8, Region 9, and Region 10.
 
@@
 
+Position categories tend to be Onsite Required.
+
 Very few people exit employment (~2%). Some have multiple employers (20-30%).
@@
 High proportion in OAS, and PBS, and lower in FAS, GSA IT, IOA, OCE, OCFO, OCIA, OCR, OGC, OGP, OHRM, OMA, OSC, and OSDBU.
+
+Disproportionately in Region 1, Region 2, Region 3, Region 6, Region 7, Region 8, Region 9, Region 10, and Region 11. Very low proportion in Region 0.
 
@@
 
+Appear across all position categories and make up all of those that are (Missing).
+
 Many people exit employment (~54%). Some have multiple employers (20-30%).
@@
 
-```{r}
-d %>% 
-  group_by(.cluster_5) %>% 
-  skim(exit_employment,
-       multiple_supervisors) 
-```
+Fairly even dispersion across regions.
 

### 2023-08-22 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Update 03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
More descriptions

@@
 
-## Cluster descriptions {.tabset .tabset-pills}
-
-Clusters 2(1): **Teleworkers**
-
-Very low number of days reporting to the job site.
-Majority of time telework.
-Very few days co-located with at least one team member, a supervisor, or the whole team.
-Many days where the whole team is co-located, but not the majority.
-High number of working days.
-
-Clusters 2(2): **Everyone else**
-
-Higher number of days reporting to job site, but with large variance.
-Lower proportion of days teleworking, but still about a quarter of days.
-Again, higher variance of telework.
-Some days co-located with at least one team member and the majority of days working at the site.
-Many days working onsite with supervisor, but very few days where the whole team is co-located.
-Very few days where the whole team is co-located.
-Lower number of working days.
-
-Clusters 5(1): **Teleworkers**
-
-Very low number of days (~3) reporting to the job site.
-Most days (~119) employees telework.
-Hardly any days co-located with at least one team member (<1), supervisor (<1), or whole team (<1).
-Many days (~54) where entire team works remotely.
-Many working days (~122).
-Team is average size (~6).
-
-Clusters 5(2): **Teleworkers that go to the office sometimes**
-
-A few days (~14) working at the job site, but high variation.
-Majority of days(~98) employees telework.
-Some days co-located with at least one team member (~6) or supervisor (~3).
-Few days co-located with entire team (~1).
-Some days (~19) where the entire team works remotely.
-Many working days (~112).
-Team is large (~9).
-
-Clusters 5(3): **Hybrid workers**
-
-Some days (~69) with employees working to the job site.
-Staff often telework (~48), but high variance.
-Many days co-located with at least one team member (~29) or with supervisor (~13).
-Few days co-located with entire team (~1).
-Few days (~5) where the whole team is remote.
-Many working days (~115).
-Team is average size (~6).
-
-Clusters 5(4): **Onsite workers**
-
-Employees that report to the job site for most days (~97).
-Some days (~22) telework.
-Many days co-located with at least one team member (~74), supervisor (~60), or whole team (~17), but high variance.
-Few days (~4) where the whole team is remote, but high variance.
-Many working days (~119).
-Team is smaller (~5)
-
-Clusters 5(5): **Non-workers**
-Low number of days (~5) reporting to the site, but high variance.
-Some days (~27) telework, but high variance.
-Few days co-located with at least one team member (2)  or with supervisor (~1).
-Almost no days (<1) with the whole team co-located.
-Several days (~9) where the entire team works remotely.
-Few working days (~34) and high variance.
-Team is large (~9) and high variance.
-
 ## Work pattern statistics {.tabset .tabset-pills}
@@
 
-#### Position category
+#### Grade
 
@@
 
+#### Occupational series
+
+##### Two clusters
+
+```{r}
+level_10 <- 
+  d %>% 
+  count(occupational_series) %>% 
+  arrange(desc(n)) %>% 
+  slice(10) %>% 
+  pull(n)
+
+d %>%
+  mutate(occupational_series = fct_lump_min(occupational_series, min = level_10)) %>%
+  group_by(.cluster_2) %>%
+  count(occupational_series) %>%
+  ungroup() %>%
+  left_join(d %>%
+              count(.cluster_2, name = "tot")) %>%
+  mutate(prop = n / tot) %>%
+  ggplot(aes(x = .cluster_2, y =  prop, fill = .cluster_2)) +
+  geom_col(position = "dodge")  +
+  facet_wrap(facets = vars(occupational_series), scales = "free_y")
+```
+
+##### Five clusters
+
+```{r}
+level_10 <- 
+  d %>% 
+  count(occupational_series) %>% 
+  arrange(desc(n)) %>% 
+  slice(10) %>% 
+  pull(n)
+
+d %>%
+  mutate(occupational_series = fct_lump_min(occupational_series, min = level_10)) %>%
+  group_by(.cluster_5) %>%
+  count(occupational_series) %>%
+  ungroup() %>%
+  left_join(d %>%
+              count(.cluster_5, name = "tot")) %>%
+  mutate(prop = n / tot) %>%
+  ggplot(aes(x = .cluster_5, y =  prop, fill = .cluster_5)) +
+  geom_col(position = "dodge")  +
+  facet_wrap(facets = vars(occupational_series), scales = "free_y")
+```
+
+#### Position title
+
+##### Two clusters
+
+```{r}
+level_10 <- 
+  d %>% 
+  count(position_title) %>% 
+  arrange(desc(n)) %>% 
+  slice(10) %>% 
+  pull(n)
+
+d %>%
+  mutate(position_title = fct_lump_min(position_title, min = level_10)) %>%
+  group_by(.cluster_2) %>%
+  count(position_title) %>%
+  ungroup() %>%
+  left_join(d %>%
+              count(.cluster_2, name = "tot")) %>%
+  mutate(prop = n / tot) %>%
+  ggplot(aes(x = .cluster_2, y =  prop, fill = .cluster_2)) +
+  geom_col(position = "dodge")  +
+  facet_wrap(facets = vars(position_title), scales = "free_y", ncol = 3) +
+  theme(
+    legend.position = "none"
+  )
+```
+
+##### Five clusters
+
+```{r}
+level_10 <- 
+  d %>% 
+  count(position_title) %>% 
+  arrange(desc(n)) %>% 
+  slice(10) %>% 
+  pull(n)
+
+d %>%
+  mutate(position_title = fct_lump_min(position_title, min = level_10)) %>%
+  group_by(.cluster_5) %>%
+  count(position_title) %>%
+  ungroup() %>%
+  left_join(d %>%
+              count(.cluster_5, name = "tot")) %>%
+  mutate(prop = n / tot) %>%
+  ggplot(aes(x = .cluster_5, y =  prop, fill = .cluster_5)) +
+  geom_col(position = "dodge")  +
+   facet_wrap(facets = vars(position_title), scales = "free_y", ncol = 3) +
+  theme(
+    legend.position = "none"
+  )
+```
+
+#### State
+
+##### Two clusters
+
+```{r}
+level_10 <- 
+  d %>% 
+  count(location_state) %>% 
+  arrange(desc(n)) %>% 
+  slice(10) %>% 
+  pull(n)
+
+d %>%
+  mutate(location_state = fct_lump_min(location_state, min = level_10)) %>%
+  group_by(.cluster_2) %>%
+  count(location_state) %>%
+  ungroup() %>%
+  left_join(d %>%
+              count(.cluster_2, name = "tot")) %>%
+  mutate(prop = n / tot) %>%
+  ggplot(aes(x = .cluster_2, y =  prop, fill = .cluster_2)) +
+  geom_col(position = "dodge")  +
+  facet_wrap(facets = vars(location_state), scales = "free_y")
+```
+
+##### Five clusters
+
+```{r}
+level_10 <- 
+  d %>%
+  count(location_state) %>% 
+  arrange(desc(n)) %>% 
+  slice(10) %>% 
+  pull(n)
+
+d %>%
+  mutate(location_state = fct_lump_min(location_state, min = level_10)) %>%
+  group_by(.cluster_5) %>%
+  count(location_state) %>%
+  ungroup() %>%
+  left_join(d %>%
+              count(.cluster_5, name = "tot")) %>%
+  mutate(prop = n / tot) %>%
+  ggplot(aes(x = .cluster_5, y =  prop, fill = .cluster_5)) +
+  geom_col(position = "dodge")  +
+  facet_wrap(facets = vars(location_state), scales = "free_y")
+```
+
+#### City, State
+
+##### Two clusters
+
+```{r}
+level_10 <- 
+  d %>% 
+  unite(loc, location_city, location_state, sep = ", ") %>% 
+  count(loc) %>% 
+  arrange(desc(n)) %>% 
+  slice(15) %>% 
+  pull(n)
+
+d %>%
+  unite(loc, location_city, location_state, sep = ", ") %>% 
+  mutate(loc = fct_lump_min(loc, min = level_10)) %>%
+  group_by(.cluster_2) %>%
+  count(loc) %>%
+  ungroup() %>%
+  left_join(d %>%
+              count(.cluster_2, name = "tot")) %>%
+  mutate(prop = n / tot) %>%
+  ggplot(aes(x = .cluster_2, y =  prop, fill = .cluster_2)) +
+  geom_col(position = "dodge")  +
+  facet_wrap(facets = vars(loc), scales = "free_y")
+```
+
+##### Five clusters
+
+```{r}
+level_10 <- 
+  d %>%
+  unite(loc, location_city, location_state, sep = ", ") %>% 
+  count(loc) %>% 
+  arrange(desc(n)) %>% 
+  slice(15) %>% 
+  pull(n)
+
+d %>%
+  unite(loc, location_city, location_state, sep = ", ") %>% 
+  mutate(loc = fct_lump_min(loc, min = level_10)) %>%
+  group_by(.cluster_5) %>%
+  count(loc) %>%
+  ungroup() %>%
+  left_join(d %>%
+              count(.cluster_5, name = "tot")) %>%
+  mutate(prop = n / tot) %>%
+  ggplot(aes(x = .cluster_5, y =  prop, fill = .cluster_5)) +
+  geom_col(position = "dodge")  +
+  facet_wrap(facets = vars(loc), scales = "free_y")
+```
+
 ## Cluster descriptions {.tabset .tabset-pills}
@@
 Disproportionately in Region 0.
+
+More often located in the states of Georgia, Illinois, Maryland, Pennsylvania, and Virginia, and in the cities of Alexandria (VA), Arlington (VA), Atlanta (GA), Auburn (WA), Chicago (IL), Fort Worth (TX), Philadelphia (PA), San Diego (CA), and San Francisco (CA).
+
+Primarily Grades 13, 14, and 15.
+
+Higher proportion in series 0301 (Miscellaneous Administration and Program Series), 0343 (Management and Program Analysis Series), 0501 (Financial Administration and Program Series), 0560 (Budget Analysis Series), 1102 (Contracting Series), 1170 (Realty Series), 2150 (Transportation Operations Series), and 2210 (Information Technology Management Series).
+
+More likely to be Budget Analysts, Contract Specialists, Program Analysts, Realty Specialists, Supervisory Contract Specialists, Transportation Operations Specialists, and other less common series.
 
@@
 
+More often located in DC, and less common states, and in the cities of Boston (MA), Kansas City (MO), Los Angeles (CA), and Washington DC.
+
+Primarily in Grades below 13.
+
+Higher proportion in series 1176 (Building Management Series).
+
+More likely to be Building Management Specialists, Building Managers, and Construction Control Representatives.
+
 Clusters 5(1): **Teleworkers**
@@
 Disproportionately in Region 0 and Region 2.
+
+More often located in the states of Georgia, Maryland, Missouri, New York, Pennsylvania, and Virginia, and in the cities of Alexandria (VA), New York (NY), and Philadelphia (PA).
+
+Higher proportions in Grades 13, 14, and 15.
+
+Higher proportion in series 0343 (Management and Program Analysis Series), 0501 (Financial Administration and Program Series), 0560 (Budget Analysis Series), 1102 (Contracting Series), and 2210 (Information Technology Management Series).
+
+More likely to be Budget Analysts, Contract Specialists, Program Analysts, and Supervisory Constract Specialists.
 
@@
 
+More often located in the states of Georgia, Illinois, Maryland, and Virginia, and in the cities of Alexandria (VA), Arlington (VA), and San Diego (CA).
+
+Higher proportions in Grades 13, 14, and 15.
+
+Higher proportion in series series 0343 (Management and Program Analysis Series), 0501 (Financial Administration and Program Series), 0560 (Budget Analysis Series), 1102 (Contracting Series), and 2210 (Information Technology Management Series).
+
+More likely to be Budget Analysts, Contract Specialists, Program Analysts, Realty Specialists, and Supervisory Constract Specialists.
+
 Clusters 5(3): **Hybrid workers**
@@
 
+More often located in the states of California, Georgia, Illinois, and DC, and in the cities of Atlanta (GA), Auburn (WA), Boston (MA), Chicago (IL), Kansas City (MO), Lakewood (CO),  Los Angeles (CA), San Diego (CA), San Francisco (CA) and Washington DC.
+
+Higher proportions in Grades 00 and 13.
+
+Higher proportion in series 1101 (General Business and Industry Series), 1170 (Realty Series), 2150 (Transportation Operations Series), and other less common series.
+
+More likely to be Construction Control Representatives, Program Managers, Realty Specialists, and Transportation Operations Specialists.
+
 Clusters 5(4): **Onsite workers**
@@
 Disproportionately in Region 1, Region 2, Region 3, Region 6, Region 7, Region 8, Region 9, Region 10, and Region 11. Very low proportion in Region 0.
+
+More often located in the states of New York, DC, and less common states, and in the cities of Los Angeles (CA), and Washington DC.
+
+Higher proportions in Grades 05, 11, 12, and other grades with few people in them.
+
+Higher proportion in series in series 1176 (Building Management Series).
+
+More likely to be Building Management Specialists, Building Managers, and Construction Control Representatives.
 
@@
 Fairly even dispersion across regions.
+
+More often located in DC, and in the cities of Alexandria (VA), Arlington (VA), and Washington DC.
+
+Higher proportions in Grades 04, 15, and other grades with few people in them.
+
+Higher proportion in series 0301 (Miscellaneous Administration and Program Series), but common in all series.
+
+Fairly dispersed across position titles.
 

### 2023-08-22 04. Analysis/scripts/04-01-reporting-presentation.Rmd
Create 04-01-reporting-presentation.Rmd

---
title: "slides for lab"
author: "Ben Jaques-Leslie"
date: "2023-08-22"
output: powerpoint_presentation
params:
  author: "Ben Jaques-Leslie"
  project_number: 2312
  project_name: "Occupancy Patterns"
  google_drive_home: "G:/Shared drives/GSA Evaluation Division/Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
  data_folder_1: "prepared-data"
  data_file_1: "clusters-employee-2023-08-09.rdata"
  data_file_2: "prep_employees_2023-08-09.rdata"
  in_number_of_clusters_1: 2
  in_number_of_clusters_2: 5
  in_specification: "scale_observation_none_1_20_TRUE"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      fig.width = 8,
                      fig.height = 4,
                      dpi = 300)
options(scipen=999)
tictoc::tic()
if(!("arsenal" %in% installed.packages()[,"Package"]))
{
  install.packages("arsenal")
}
if(!("beepr" %in% installed.packages()[,"Package"]))
{
  install.packages("beepr")
}
if(!("geomtextpath" %in% installed.packages()[,"Package"]))
{
  install.packages("geomtextpath")
}
if(!("oesrrr" %in% installed.packages()[,"Package"]))
{
  devtools::install_github(repo = "GSA/oesrrr")
}
if(!("oesrrr" %in% installed.packages()[,"Package"]))
{
  devtools::install_github(repo = "GSA/oesrrr")
}
library(oesrrr)
library(tidyverse)
library(janitor)
library(skimr)
library(DataExplorer)
library(readr)
library(arsenal)
library(Hmisc)
library(readxl)
library(flextable)
library(ggthemes)
library(tidymodels)
library(patchwork)
```

```{r include=FALSE}
load(file = file.path(params$google_drive_home,"03. Data Collection",params$data_folder_1,params$data_file_1))
```

```{r include=FALSE}
load(file = file.path(params$google_drive_home,"03. Data Collection",params$data_folder_1,params$data_file_2))
```

```{r include=FALSE}
clust_1 <- 
  kclusts %>% 
  filter(
    k == params$in_number_of_clusters_1 &
      specification == params$in_specification
  )
```

```{r include=FALSE}
clust_2 <- 
  kclusts %>% 
  filter(
    k == params$in_number_of_clusters_2 &
      specification == params$in_specification
  )
```

```{r include=FALSE}
clusters_1 <- 
  clust_1 %>%
  unnest(cols = c(tidied))

assignments_1 <- 
  clust_1 %>% 
  unnest(cols = c(augmented))

clusterings_1 <- 
  clust_1 %>%
  unnest(cols = c(glanced))

```

```{r include=FALSE}
clusters_2 <- 
  clust_2 %>%
  unnest(cols = c(tidied))

assignments_2 <- 
  clust_2 %>% 
  unnest(cols = c(augmented))

clusterings_2 <- 
  clust_2 %>%
  unnest(cols = c(glanced))

```

```{r include=FALSE}
rename_to_k <- function(in_data)
{
  tot_cluster <- in_data %>% select(k) %>% distinct() %>% pull()
  out_data <-
    in_data %>% rename_with( ~ glue::glue("{.x}_{tot_cluster}"), .cluster)
  return(out_data)
}
```

```{r include=FALSE}
assignments <-
  assignments_1 %>%
  rename_to_k() %>%
  select(person_id, starts_with(".cluster")) %>%
  full_join(assignments_2 %>%
              rename_to_k() %>%
              select(person_id, starts_with(".cluster")))
```

```{r include=FALSE}
d <-
  assignments %>%
  select(person_id, starts_with(".cluster")) %>%
  full_join(prep_employees) %>% 
  mutate(
    across(
      .cols = starts_with(".cluster"),
      .fns = ~fct_na_value_to_level(., level = "(Missing)")
    )
  )
```

```{r include=FALSE}
d <- d %>% 
  mutate(
    .cluster_5 = fct_recode(.cluster_5,
                            "Teleworkers" = "1",
                            "Office visitors" = "2",
                            "Hybrid workers" = "3",
                            "Onsite workers" = "4",
                            "Disconnected workers" = "5"),
    .cluster_5 = fct_relabel(.cluster_5, ~str_wrap(.x,width = 10))
  )
```

# How much telework?

```{r include=FALSE}
prep_01 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  summarise(num = mean(daily_status_teleworking)) %>% 
  ungroup()

prep_02 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  summarise(xPos = max(daily_status_teleworking),
            yPos = max((density(daily_status_teleworking))$y))

prep_02 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  summarise(y = max(density(daily_status_teleworking)$y),
            x = density(daily_status_teleworking)$x[density(daily_status_teleworking)$y == max(density(daily_status_teleworking)$y)]
  )
```

```{r}
p_1 <- 
  prep_01 %>% 
  ggplot(
    aes(x = .cluster_5, y = num, fill = .cluster_5)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::comma) +
  ylab("Mean days of telework") +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8))

p_2 <- 
  d %>% 
  ggplot(
    aes(x = daily_status_teleworking, color = .cluster_5, fill = .cluster_5)
  ) +
  geom_density(alpha = .5) +
  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
  xlab("Days of telework") +
  ylab("Density") +
  theme_light() +
  theme(legend.position = "None")

p_1|p_2
```

# How much onsite work?

```{r include=FALSE}
prep_01 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  summarise(num = mean(daily_status_reporting_to_job_site)) %>% 
  ungroup()

prep_02 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  summarise(xPos = max(daily_status_reporting_to_job_site),
            yPos = max((density(daily_status_reporting_to_job_site))$y))

prep_02 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  summarise(y = max(density(daily_status_reporting_to_job_site)$y),
            x = density(daily_status_reporting_to_job_site)$x[density(daily_status_reporting_to_job_site)$y == max(density(daily_status_reporting_to_job_site)$y)]
  )
```

```{r}
p_1 <- 
  prep_01 %>% 
  ggplot(
    aes(x = .cluster_5, y = num, fill = .cluster_5)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::comma) +
  ylab("Mean days of onsite work") +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8))

p_2 <- 
  d %>% 
  ggplot(
    aes(x = daily_status_reporting_to_job_site, color = .cluster_5, fill = .cluster_5)
  ) +
  geom_density(alpha = .5) +
  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
  xlab("Days of onsite work") +
  ylab("Density") +
  theme_light() +
  theme(legend.position = "None")

p_1|p_2
```

# Disconnected workers: Working days

```{r include=FALSE}
prep_01 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  summarise(num = mean(working_days)) %>% 
  ungroup()

prep_02 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  summarise(xPos = max(working_days),
            yPos = max((density(working_days))$y))

prep_02 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  summarise(y = max(density(working_days)$y),
            x = density(working_days)$x[density(working_days)$y == max(density(working_days)$y)]
  )
```

```{r}
p_1 <- 
  prep_01 %>% 
  ggplot(
    aes(x = .cluster_5, y = num, fill = .cluster_5)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::comma) +
  ylab("Mean working days") +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8))

p_2 <- 
  d %>% 
  ggplot(
    aes(x = working_days, color = .cluster_5, fill = .cluster_5)
  ) +
  geom_density(alpha = .5) +
  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
  xlab("Working days") +
  ylab("Density") +
  theme_light() +
  theme(legend.position = "None")

p_1|p_2
```

# Disconnected workers: Exiting employment

```{r include=FALSE}
prep_01 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  summarise(num = sum(exit_employment)) %>% 
  ungroup()

prep_02 <- 
  d %>% 
  group_by(.cluster_5) %>% 
  count() %>% 
  ungroup()

prep_03 <- 
  prep_01 %>% 
  full_join(prep_02) %>% 
  mutate(
    num = num/n
  )
```

```{r}
p_1 <-
  prep_03 %>%
  ggplot(aes(x = .cluster_5, y = num, fill = .cluster_5)) +
  geom_col() +
  ylab("Percent exiting employment") +
  scale_y_continuous(labels = scales::percent) +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8)
  )

p_1
```

# Position categories

```{r}
prep_d_01 <- 
  d %>% 
  group_by(position_category_description) %>% 
  count() %>% 
  ungroup() %>% 
  arrange(desc(n))

prep_v_01 <- 
  prep_d_01 %>% 
  slice(3) %>% 
  pull(n)

prep_d_02 <-
  d %>%
  mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
         position_category_description = fct_infreq(position_category_description)) %>%
  group_by(position_category_description) %>%
  count() %>%
  ungroup() %>%
  arrange(desc(n)) %>% 
  rename(num = n)
```

```{r}
p_1 <- 
  prep_d_02 %>% 
  ggplot(
    aes(x = position_category_description, y = num, fill = position_category_description)
  ) +
  geom_col() +
  scale_y_continuous(labels = scales::comma) +
  ylab("Employees") +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8))

p_1
```

# Rule-based groups

```{r}
prep_d_01 <- 
  d %>%
  summarise(across(
    .cols = starts_with("rule_based"),
    .fns = ~ sum(., rm.na = T)
  )) %>%
  select(-contains("_position_category_")) %>%
  select(-ends_with("observation")) %>%
  rownames_to_column() %>%
  pivot_longer(-rowname) %>%
  select(-rowname) %>%
  mutate(
    name = str_remove(name, "rule_based_"),
    name = str_remove(name, "_working"),
    name = str_replace_all(name, "_", " "),
    name = str_to_sentence(name),
    name = fct_relevel(
      name,
      "Primarily teleworking",
      "Mostly teleworking",
      "Mostly reporting to job site",
      "Primarily reporting to job site",
      "All remote",
      "Telework onsite minimum"
    ),
    name = fct_relabel(name, ~str_wrap(.,width = 20))
  ) %>% 
  arrange(name)

prep_d_02 <- 
  prep_d_01 %>% 
  mutate(tot = d %>% count() %>% pull(),
         prop = value/tot,
         text = scales::percent(prop, accuracy = .1))
```

```{r}
p_1 <- 
  prep_d_01 %>% 
  ggplot(
    aes(x = name, y = value, fill = name)
  ) +
  geom_col() +
  geom_text(data = prep_d_02, aes(x = name, y = .5*value, label = text), color = "white") +
  scale_y_continuous(labels = scales::comma) +
  ylab("Employees") +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8))

p_1
```

# Clusters

```{r}
prep_d_01 <- 
  d %>%
  group_by(.cluster_5) %>% 
  count() %>% 
  ungroup()

prep_d_02 <- 
  prep_d_01 %>% 
  mutate(tot = d %>% count() %>% pull(),
         prop = n/tot,
         text = scales::percent(prop, accuracy = .1))
```

```{r}
p_1 <- 
  prep_d_01 %>% 
  ggplot(
    aes(x = .cluster_5, y = n, fill = .cluster_5)
  ) +
  geom_col() +
  geom_text(data = prep_d_02, aes(x = .cluster_5, y = .5*n, label = text), color = "white") +
  scale_y_continuous(labels = scales::comma) +
  ylab("Employees") +
  theme_light() +
  theme(
    legend.position = "None",
    axis.title.x = element_blank(),
    axis.text.x = element_text(size = 8))

p_1
```

### 2023-08-23 04. Analysis/scripts/04-01-reporting-presentation.Rmd
Update 04-01-reporting-presentation.Rmd

@@
 knitr::opts_chunk$set(echo = FALSE,
+                      warning = FALSE,
+                      message = FALSE,
                       fig.width = 8,
@@
 }
+install.packages("tigris")
 library(oesrrr)
@@
 library(patchwork)
+library(sf)
+library(tigris)
+options(tigris_class = "sf")
+options(tigris_use_cache = TRUE)
 ```
@@
 ```
+
+# Clusters and position categories
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(position_category_description) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n))
+
+prep_v_01 <- 
+  prep_d_01 %>% 
+  slice(3) %>% 
+  pull(n)
+
+prep_d_02 <-
+  d %>%
+  mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
+         position_category_description = fct_infreq(position_category_description)) %>%
+  group_by(position_category_description,.cluster_5) %>%
+  count() %>%
+  ungroup() %>%
+  arrange(desc(n)) %>% 
+  rename(num = n) %>% 
+  mutate(
+    position_category_description = fct_relevel(position_category_description, 
+                                               "Offsite",
+                                               "Onsite Flexible",
+                                               "Onsite Required",
+                                               "Other")
+  )
+
+prep_d_03 <- 
+  prep_d_02 %>% 
+  filter(position_category_description != "Other")
+
+prep_d_04 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_05 <- 
+  prep_d_03 %>% 
+  full_join(prep_d_04) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  ) 
+```
+
+```{r}
+p_1 <- 
+  prep_d_05 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = n, fill = .cluster_5)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::percent) +
+  ylab("Percent of cluster in position category") +
+  facet_wrap(facets = vars(position_category_description), nrow = 1) +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_1
+```
+
+# Teleworkers, office visitors, and regions
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(gsa_region,.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(num = n)
+
+prep_d_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_03 <- 
+  prep_d_01 %>% 
+  full_join(prep_d_02) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  ) %>% 
+  mutate(
+    gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
+  )
+
+prep_d_04 <- 
+  prep_d_03 %>% 
+  filter(.cluster_5 == "Teleworkers" |
+           .cluster_5 == "Office\nvisitors"
+           )
+```
+
+```{r}
+p_1 <- 
+  prep_d_04 %>% 
+  ggplot(
+    aes(x = gsa_region, y = n, fill = gsa_region)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::percent) +
+  ylab("Percent of cluster in region") +
+  facet_wrap(facets = vars(.cluster_5), nrow = 1) +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_1
+```
+
+# Hybrid, onsite, and disconnected workers and regions
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(gsa_region,.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(num = n)
+
+prep_d_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_03 <- 
+  prep_d_01 %>% 
+  full_join(prep_d_02) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  ) %>% 
+  mutate(
+    gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
+  )
+
+prep_d_04 <- 
+  prep_d_03 %>% 
+  filter(.cluster_5 == "Hybrid\nworkers" |
+           .cluster_5 == "Onsite\nworkers" |
+           .cluster_5 == "Disconnected\nworkers")
+```
+
+```{r}
+p_1 <- 
+  prep_d_04 %>% 
+  ggplot(
+    aes(x = gsa_region, y = n, fill = gsa_region)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::percent) +
+  ylab("Percent of cluster in region") +
+  facet_wrap(facets = vars(.cluster_5), nrow = 1) +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_1
+```
+
+# States: MD, PA, and VA
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(location_state,.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(num = n)
+
+prep_d_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_03 <- 
+  prep_d_01 %>% 
+  full_join(prep_d_02) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  )# %>% 
+  # mutate(
+  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
+  # )
+
+prep_d_04 <- 
+  prep_d_03 %>% 
+  filter(location_state %in% c("MD","PA","VA")
+           )
+```
+
+```{r}
+p_1 <- 
+  prep_d_04 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = n, fill = .cluster_5)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::percent) +
+  ylab("Percent of cluster in state") +
+  facet_wrap(facets = vars(location_state), nrow = 1) +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_1
+```
+
+# States: CA and IL
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(location_state,.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(num = n)
+
+prep_d_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_03 <- 
+  prep_d_01 %>% 
+  full_join(prep_d_02) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  )# %>% 
+  # mutate(
+  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
+  # )
+
+prep_d_04 <- 
+  prep_d_03 %>% 
+  filter(location_state %in% c("CA", "IL")
+           )
+```
+
+```{r}
+p_1 <- 
+  prep_d_04 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = n, fill = .cluster_5)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::percent) +
+  ylab("Percent of cluster in state") +
+  facet_wrap(facets = vars(location_state), nrow = 1) +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_1
+```
+
+# District of Columbia
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(location_state,.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(num = n)
+
+prep_d_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_03 <- 
+  prep_d_01 %>% 
+  full_join(prep_d_02) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  )# %>% 
+  # mutate(
+  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
+  # )
+
+prep_d_04 <- 
+  prep_d_03 %>% 
+  filter(location_state %in% c("DC")
+           )
+```
+
+```{r}
+p_1 <- 
+  prep_d_04 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = n, fill = .cluster_5)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::percent) +
+  ylab("Percent of cluster in state") +
+  facet_wrap(facets = vars(location_state), nrow = 1) +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_1
+```
+
+# Clusters and staff offices
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(gsa_sso) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n))
+
+prep_v_01 <- 
+  prep_d_01 %>% 
+  slice(2) %>% 
+  pull(n)
+
+prep_d_02 <-
+  d %>%
+  mutate(gsa_sso = fct_lump_min(gsa_sso, min = prep_v_01),
+         gsa_sso = fct_infreq(gsa_sso)) %>%
+  group_by(gsa_sso,.cluster_5) %>%
+  count() %>%
+  ungroup() %>%
+  arrange(desc(n)) %>% 
+  rename(num = n) %>% 
+  mutate(gsa_sso = fct_relevel(gsa_sso,
+                               "PBS",
+                               "FAS",
+                               "OCFO",
+                               "Other"))
+
+prep_d_03 <- 
+  prep_d_02 %>% 
+  filter(gsa_sso != "Other")
+
+prep_d_04 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_05 <- 
+  prep_d_03 %>% 
+  full_join(prep_d_04) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  ) 
+```
+
+```{r}
+p_1 <- 
+  prep_d_05 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = n, fill = .cluster_5)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::percent) +
+  ylab("Percent of cluster in staff office") +
+  facet_wrap(facets = vars(gsa_sso), nrow = 1) +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 7))
+
+p_1
+```
+
+# Clusters and series
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(occupational_series) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n))
+
+prep_v_01 <- 
+  prep_d_01 %>% 
+  slice(3) %>% 
+  pull(n)
+
+prep_d_02 <-
+  d %>%
+  mutate(
+    # occupational_series = fct_lump_min(occupational_series, min = prep_v_01),
+    occupational_series = fct_infreq(occupational_series)
+  ) %>%
+  group_by(occupational_series, .cluster_5) %>%
+  count() %>%
+  ungroup() %>%
+  arrange(desc(n)) %>%
+  rename(num = n) %>%
+  mutate(
+    # occupational_series = fct_relevel(occupational_series,
+    #                                   "1102",
+    #                                   "1101",
+    #                                   "0343",
+    #                                   "Other"),
+    occupational_series = recode(occupational_series,
+                                 "1102" = "Contracting",
+                                 "1101" = "General Business and Industry",
+                                 "0343" = "Management and Program Analysis",
+                                 "0501" = "Financial Administration and Program",
+                                 "0560" = "Budget Analysis",
+                                 "0301" = "Miscellaneous Administration and Program",
+                                 "1170" = "Realty",
+                                 "1176" = "Building Management",
+                                 "2150" = "Transportation Operations",
+                                 "2210" = "Information Technology Management"
+                                 ),
+    occupational_series = fct_relevel(
+      occupational_series,
+      "Budget Analysis",
+      "Building Management",
+      "Contracting",
+      "Financial Administration and Program",
+      "General Business and Industry",
+      "Information Technology Management",
+      "Management and Program Analysis",
+      "Miscellaneous Administration and Program",
+      "Realty",
+      "Transportation Operations",
+    )
+  )
+
+# prep_d_02
+```
+
+```{r}
+prep_d_03 <-
+  prep_d_02 %>%
+  filter(
+    occupational_series %in%
+      c(
+        # "Budget Analysis",
+        # "Building Management",
+        "Contracting",
+        # "Financial Administration and Program",
+        # "General Business and Industry",
+        # "Information Technology Management",
+        "Management and Program Analysis",
+        "Miscellaneous Administration and Program"
+        # "Realty",
+        # "Transportation Operations"
+      )
+  )
+
+prep_d_04 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_05 <- 
+  prep_d_03 %>% 
+  full_join(prep_d_04) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  ) %>% 
+  mutate(
+    occupational_series = fct_relabel(occupational_series,~str_wrap(.,width = 15))
+  )
+```
+
+```{r}
+p_1 <- 
+  prep_d_05 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = n, fill = .cluster_5)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::percent) +
+  ylab("Percent of cluster in series") +
+  facet_wrap(facets = vars(occupational_series), nrow = 1) +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 7))
+
+p_1
+```
+
+# Clusters and series
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(occupational_series) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n))
+
+prep_v_01 <- 
+  prep_d_01 %>% 
+  slice(3) %>% 
+  pull(n)
+
+prep_d_02 <-
+  d %>%
+  mutate(
+    # occupational_series = fct_lump_min(occupational_series, min = prep_v_01),
+    occupational_series = fct_infreq(occupational_series)
+  ) %>%
+  group_by(occupational_series, .cluster_5) %>%
+  count() %>%
+  ungroup() %>%
+  arrange(desc(n)) %>%
+  rename(num = n) %>%
+  mutate(
+    # occupational_series = fct_relevel(occupational_series,
+    #                                   "1102",
+    #                                   "1101",
+    #                                   "0343",
+    #                                   "Other"),
+    occupational_series = recode(occupational_series,
+                                 "1102" = "Contracting",
+                                 "1101" = "General Business and Industry",
+                                 "0343" = "Management and Program Analysis",
+                                 "0501" = "Financial Administration and Program",
+                                 "0560" = "Budget Analysis",
+                                 "0301" = "Miscellaneous Administration and Program",
+                                 "1170" = "Realty",
+                                 "1176" = "Building Management",
+                                 "2150" = "Transportation Operations",
+                                 "2210" = "Information Technology Management"
+                                 ),
+    occupational_series = fct_relevel(
+      occupational_series,
+      "Budget Analysis",
+      "Building Management",
+      "Contracting",
+      "Financial Administration and Program",
+      "General Business and Industry",
+      "Information Technology Management",
+      "Management and Program Analysis",
+      "Miscellaneous Administration and Program",
+      "Realty",
+      "Transportation Operations",
+    )
+  )
+
+# prep_d_02
+```
+
+```{r}
+prep_d_03 <-
+  prep_d_02 %>%
+  filter(
+    occupational_series %in%
+      c(
+        "Budget Analysis",
+        # "Building Management",
+        # "Contracting",
+        "Financial Administration and Program",
+        # "General Business and Industry",
+        "Information Technology Management",
+        # "Management and Program Analysis",
+        # "Miscellaneous Administration and Program"
+        # "Realty",
+        # "Transportation Operations"
+      )
+  )
+
+prep_d_04 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_05 <- 
+  prep_d_03 %>% 
+  full_join(prep_d_04) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  ) %>% 
+  mutate(
+    occupational_series = fct_relabel(occupational_series,~str_wrap(.,width = 15))
+  )
+```
+
+```{r}
+p_1 <- 
+  prep_d_05 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = n, fill = .cluster_5)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::percent) +
+  ylab("Percent of cluster in series") +
+  facet_wrap(facets = vars(occupational_series), nrow = 1) +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 7))
+
+p_1
+```
+
+# Clusters and series
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(occupational_series) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n))
+
+prep_v_01 <- 
+  prep_d_01 %>% 
+  slice(3) %>% 
+  pull(n)
+
+prep_d_02 <-
+  d %>%
+  mutate(
+    # occupational_series = fct_lump_min(occupational_series, min = prep_v_01),
+    occupational_series = fct_infreq(occupational_series)
+  ) %>%
+  group_by(occupational_series, .cluster_5) %>%
+  count() %>%
+  ungroup() %>%
+  arrange(desc(n)) %>%
+  rename(num = n) %>%
+  mutate(
+    # occupational_series = fct_relevel(occupational_series,
+    #                                   "1102",
+    #                                   "1101",
+    #                                   "0343",
+    #                                   "Other"),
+    occupational_series = recode(occupational_series,
+                                 "1102" = "Contracting",
+                                 "1101" = "General Business and Industry",
+                                 "0343" = "Management and Program Analysis",
+                                 "0501" = "Financial Administration and Program",
+                                 "0560" = "Budget Analysis",
+                                 "0301" = "Miscellaneous Administration and Program",
+                                 "1170" = "Realty",
+                                 "1176" = "Building Management",
+                                 "2150" = "Transportation Operations",
+                                 "2210" = "Information Technology Management"
+                                 ),
+    occupational_series = fct_relevel(
+      occupational_series,
+      "Budget Analysis",
+      "Building Management",
+      "Contracting",
+      "Financial Administration and Program",
+      "General Business and Industry",
+      "Information Technology Management",
+      "Management and Program Analysis",
+      "Miscellaneous Administration and Program",
+      "Realty",
+      "Transportation Operations",
+    )
+  )
+
+# prep_d_02
+```
+
+```{r}
+prep_d_03 <-
+  prep_d_02 %>%
+  filter(
+    occupational_series %in%
+      c(
+        # "Budget Analysis",
+        "Building Management",
+        # "Contracting",
+        # "Financial Administration and Program",
+        "General Business and Industry",
+        # "Information Technology Management",
+        # "Management and Program Analysis",
+        # "Miscellaneous Administration and Program"
+        "Realty",
+        "Transportation Operations"
+      )
+  )
+
+prep_d_04 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_05 <- 
+  prep_d_03 %>% 
+  full_join(prep_d_04) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  )  %>% 
+  mutate(
+    occupational_series = fct_relabel(occupational_series,~str_wrap(.,width = 15))
+  )
+```
+
+```{r}
+p_1 <- 
+  prep_d_05 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = n, fill = .cluster_5)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::percent) +
+  ylab("Percent of cluster in series") +
+  facet_wrap(facets = vars(occupational_series), nrow = 1) +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 7))
+
+p_1
+```
+
+# Clusters and series
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(occupational_series) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n))
+
+prep_v_01 <- 
+  prep_d_01 %>% 
+  slice(3) %>% 
+  pull(n)
+
+prep_d_02 <-
+  d %>%
+  mutate(
+    # occupational_series = fct_lump_min(occupational_series, min = prep_v_01),
+    occupational_series = fct_infreq(occupational_series)
+  ) %>%
+  group_by(occupational_series, .cluster_5) %>%
+  count() %>%
+  ungroup() %>%
+  arrange(desc(n)) %>%
+  rename(num = n) %>%
+  mutate(
+    # occupational_series = fct_relevel(occupational_series,
+    #                                   "1102",
+    #                                   "1101",
+    #                                   "0343",
+    #                                   "Other"),
+    occupational_series = recode(occupational_series,
+                                 "1102" = "Contracting",
+                                 "1101" = "General Business and Industry",
+                                 "0343" = "Management and Program Analysis",
+                                 "0501" = "Financial Administration and Program",
+                                 "0560" = "Budget Analysis",
+                                 "0301" = "Miscellaneous Administration and Program",
+                                 "1170" = "Realty",
+                                 "1176" = "Building Management",
+                                 "2150" = "Transportation Operations",
+                                 "2210" = "Information Technology Management"
+                                 ),
+    occupational_series = fct_relevel(
+      occupational_series,
+      "Budget Analysis",
+      "Building Management",
+      "Contracting",
+      "Financial Administration and Program",
+      "General Business and Industry",
+      "Information Technology Management",
+      "Management and Program Analysis",
+      "Miscellaneous Administration and Program",
+      "Realty",
+      "Transportation Operations",
+    )
+  )
+
+# prep_d_02
+```
+
+```{r}
+prep_d_03 <-
+  prep_d_02 %>%
+  filter(
+    occupational_series %in%
+      c(
+        # "Budget Analysis",
+        "Building Management",
+        # "Contracting",
+        # "Financial Administration and Program",
+        "General Business and Industry",
+        # "Information Technology Management",
+        # "Management and Program Analysis",
+        # "Miscellaneous Administration and Program"
+        "Realty",
+        "Transportation Operations"
+      )
+  )
+
+prep_d_04 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_05 <- 
+  prep_d_03 %>% 
+  full_join(prep_d_04) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  )  %>% 
+  mutate(
+    occupational_series = fct_relabel(occupational_series,~str_wrap(.,width = 15))
+  )
+```
+
+```{r}
+p_1 <- 
+  prep_d_05 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = n, fill = .cluster_5)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::percent) +
+  ylab("Percent of cluster in series") +
+  facet_wrap(facets = vars(occupational_series), nrow = 1) +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 7))
+
+p_1
+```
+
+```{r}
+# f <- file.path(params$google_drive_home,"03. Data Collection","tiger","tl_2022_us_state.zip")
+# library(tigris)
+# tigris::load_tiger(url = f)
+```
+
+# CONTINUE FROM HERE
+
+```{r}
+beepr::beep(sound = 5)
+```
+
+```{r}
+
+```

### 2023-08-24 04. Analysis/scripts/04-01-reporting-presentation.Rmd
Update 04-01-reporting-presentation.Rmd
Added oescolorrrs and created new charts

@@
   in_specification: "scale_observation_none_1_20_TRUE"
-
 ---
@@
 }
-if(!("oesrrr" %in% installed.packages()[,"Package"]))
+if(!("oescolorrrs" %in% installed.packages()[,"Package"]))
 {
-  devtools::install_github(repo = "GSA/oesrrr")
+  devtools::install_github(repo = "GSA/oescolorrrs")
 }
-install.packages("tigris")
+# install.packages("tigris")
 library(oesrrr)
@@
 library(tigris)
+library(ggrepel)
 options(tigris_class = "sf")
@@
 
-# How much telework?
-
-```{r include=FALSE}
-prep_01 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(num = mean(daily_status_teleworking)) %>% 
-  ungroup()
-
-prep_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(xPos = max(daily_status_teleworking),
-            yPos = max((density(daily_status_teleworking))$y))
-
-prep_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(y = max(density(daily_status_teleworking)$y),
-            x = density(daily_status_teleworking)$x[density(daily_status_teleworking)$y == max(density(daily_status_teleworking)$y)]
-  )
-```
-
-```{r}
-p_1 <- 
-  prep_01 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = num, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Mean days of telework") +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_2 <- 
-  d %>% 
-  ggplot(
-    aes(x = daily_status_teleworking, color = .cluster_5, fill = .cluster_5)
-  ) +
-  geom_density(alpha = .5) +
-  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
-  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
-  xlab("Days of telework") +
-  ylab("Density") +
-  theme_light() +
-  theme(legend.position = "None")
-
-p_1|p_2
-```
-
-# How much onsite work?
-
-```{r include=FALSE}
-prep_01 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(num = mean(daily_status_reporting_to_job_site)) %>% 
-  ungroup()
-
-prep_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(xPos = max(daily_status_reporting_to_job_site),
-            yPos = max((density(daily_status_reporting_to_job_site))$y))
-
-prep_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(y = max(density(daily_status_reporting_to_job_site)$y),
-            x = density(daily_status_reporting_to_job_site)$x[density(daily_status_reporting_to_job_site)$y == max(density(daily_status_reporting_to_job_site)$y)]
-  )
-```
-
-```{r}
-p_1 <- 
-  prep_01 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = num, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Mean days of onsite work") +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_2 <- 
-  d %>% 
-  ggplot(
-    aes(x = daily_status_reporting_to_job_site, color = .cluster_5, fill = .cluster_5)
-  ) +
-  geom_density(alpha = .5) +
-  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
-  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
-  xlab("Days of onsite work") +
-  ylab("Density") +
-  theme_light() +
-  theme(legend.position = "None")
-
-p_1|p_2
-```
-
-# Disconnected workers: Working days
-
-```{r include=FALSE}
-prep_01 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(num = mean(working_days)) %>% 
-  ungroup()
-
-prep_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(xPos = max(working_days),
-            yPos = max((density(working_days))$y))
-
-prep_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(y = max(density(working_days)$y),
-            x = density(working_days)$x[density(working_days)$y == max(density(working_days)$y)]
-  )
-```
-
-```{r}
-p_1 <- 
-  prep_01 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = num, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Mean working days") +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_2 <- 
-  d %>% 
-  ggplot(
-    aes(x = working_days, color = .cluster_5, fill = .cluster_5)
-  ) +
-  geom_density(alpha = .5) +
-  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
-  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
-  xlab("Working days") +
-  ylab("Density") +
-  theme_light() +
-  theme(legend.position = "None")
-
-p_1|p_2
-```
-
-# Disconnected workers: Exiting employment
-
-```{r include=FALSE}
-prep_01 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(num = sum(exit_employment)) %>% 
-  ungroup()
-
-prep_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup()
-
-prep_03 <- 
-  prep_01 %>% 
-  full_join(prep_02) %>% 
-  mutate(
-    num = num/n
-  )
-```
-
-```{r}
-p_1 <-
-  prep_03 %>%
-  ggplot(aes(x = .cluster_5, y = num, fill = .cluster_5)) +
-  geom_col() +
-  ylab("Percent exiting employment") +
-  scale_y_continuous(labels = scales::percent) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8)
-  )
-
-p_1
-```
+# What is the GSA priority?
+
+-   Telework has become very common
+
+-   Much of GSA staff telework
+
+-   How employees use telework is not clear
+
+-   Defining and describing different work patterns may help to understand organizational health
+
+-   By understanding how staff work (remote, hybrid, or onsite), different strategies may be developed to improve productivity and staff engagement
+
+# How did the evaluation work?
+
+-   Data:
+
+    -   GSA check-in data, GSA staff roster
+
+    -   March - September 2023
+
+-   All GSA staff
+
+    -   Categorized work patterns by remote or onsite
+
+    -   Rules: Mostly remote or onsite, staff category (flexible, onsite, etc), flexible onsite
+
+    -   Clusters: K-means clusters defined using frequency of work location status, collocation with team members, and team remote work
 
@@
   theme_light() +
+  oescolorrrs::scale_fill_oes() +
   theme(
@@
 ```
+
+# Clusters
+
+1.  Teleworkers
+
+2.  Office visitors
+
+3.  Hybrid workers
+
+4.  Onsite workers
+
+5.  Disconnected workers
 
@@
     axis.text.x = element_text(size = 8))
+
+p_1
+```
+
+# Clusters: How much telework?
+
+```{r include=FALSE}
+prep_01 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(num = mean(daily_status_reporting_to_job_site)) %>% 
+  ungroup()
+
+prep_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(y = max(density(daily_status_teleworking)$y),
+            x = density(daily_status_teleworking)$x[density(daily_status_teleworking)$y == max(density(daily_status_teleworking)$y)]
+  )
+```
+
+```{r}
+p_1 <- 
+  prep_01 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = num, fill = .cluster_5)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::comma) +
+  ylab("Mean days of telework") +
+  theme_light() +
+  oescolorrrs::scale_fill_oes() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_2 <- 
+  d %>% 
+  ggplot(
+    aes(x = daily_status_teleworking, color = .cluster_5, fill = .cluster_5)
+  ) +
+  geom_density(alpha = .5) +
+  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
+  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
+  xlab("Days of telework") +
+  ylab("Density") +
+  theme_light() +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme(legend.position = "None")
+
+p_1|p_2
+```
+
+# Clusters: How much onsite work?
+
+```{r include=FALSE}
+prep_01 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(num = mean(daily_status_reporting_to_job_site)) %>% 
+  ungroup()
+
+prep_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(xPos = max(daily_status_reporting_to_job_site),
+            yPos = max((density(daily_status_reporting_to_job_site))$y))
+
+prep_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(y = max(density(daily_status_reporting_to_job_site)$y),
+            x = density(daily_status_reporting_to_job_site)$x[density(daily_status_reporting_to_job_site)$y == max(density(daily_status_reporting_to_job_site)$y)]
+  )
+```
+
+```{r}
+p_1 <- 
+  prep_01 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = num, fill = .cluster_5)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::comma) +
+  ylab("Mean days of onsite work") +
+  theme_light() +
+  oescolorrrs::scale_fill_oes() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_2 <- 
+  d %>% 
+  ggplot(
+    aes(x = daily_status_reporting_to_job_site, color = .cluster_5, fill = .cluster_5)
+  ) +
+  geom_density(alpha = .5) +
+  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
+  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
+  xlab("Days of onsite work") +
+  ylab("Density") +
+  theme_light() +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme(legend.position = "None")
+
+p_1|p_2
+```
+
+# Clusters: Telework and onsite
+
+```{r}
+prep_01 <-
+  d %>%
+  mutate(
+    .cluster_5 = fct_relabel(.cluster_5,~str_wrap(.,width = 50))
+  ) %>% 
+  group_by(.cluster_5) %>%
+  summarise(across
+            (
+              .cols = c(
+                daily_status_teleworking,
+                daily_status_reporting_to_job_site,
+                working_days
+              ),
+              .fns = mean
+            )) %>%
+  ungroup()
+
+d %>%
+  mutate(
+    .cluster_5 = fct_relabel(.cluster_5,~str_wrap(.,width = 50))
+  ) %>% 
+  ggplot(
+    aes(
+      x = daily_status_reporting_to_job_site,
+      y = daily_status_teleworking,
+      color = .cluster_5,
+      fill = .cluster_5,
+      linetype = .cluster_5
+    )
+  ) +
+  geom_jitter(# aes(size = working_days),
+    alpha = .5) +
+  stat_ellipse(
+    geom = "polygon",
+    alpha = .15,
+    size = 2,
+    level = .99
+  ) +
+  geom_text_repel(
+    data = prep_01,
+    aes(x = daily_status_reporting_to_job_site, y = daily_status_teleworking, 
+        label = .cluster_5,
+        fill = .cluster_5),
+    # fill = "white",
+    # alpha = .15,
+    size = 3,
+    force             = 0.5,
+    # nudge_x           = 100,
+    xlim = c(125),
+    ylim = c(50,150),
+    direction         = "y",
+    hjust             = 0,
+    segment.size      = 0.2,
+    segment.curvature = -0.1,
+    color = "black"
+  ) +
+  theme_light() +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme(legend.position = "None")
+```
+
+# Disconnected workers: Working days
+
+```{r include=FALSE}
+prep_01 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(num = mean(working_days)) %>% 
+  ungroup()
+
+prep_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(xPos = max(working_days),
+            yPos = max((density(working_days))$y))
+
+prep_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(y = max(density(working_days)$y),
+            x = density(working_days)$x[density(working_days)$y == max(density(working_days)$y)]
+  )
+```
+
+```{r}
+p_1 <- 
+  prep_01 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = num, fill = .cluster_5)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::comma) +
+  ylab("Mean working days") +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_2 <- 
+  d %>% 
+  ggplot(
+    aes(x = working_days, color = .cluster_5, fill = .cluster_5)
+  ) +
+  geom_density(alpha = .5) +
+  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
+  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
+  xlab("Working days") +
+  ylab("Density") +
+  theme_light() +
+  theme(legend.position = "None")
+
+p_1|p_2
+```
+
+# Disconnected workers: Exiting employment
+
+```{r include=FALSE}
+prep_01 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(num = sum(exit_employment)) %>% 
+  ungroup()
+
+prep_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup()
+
+prep_03 <- 
+  prep_01 %>% 
+  full_join(prep_02) %>% 
+  mutate(
+    num = num/n
+  )
+```
+
+```{r}
+p_1 <-
+  prep_03 %>%
+  ggplot(aes(x = .cluster_5, y = num, fill = .cluster_5)) +
+  geom_col() +
+  ylab("Percent exiting employment") +
+  scale_y_continuous(labels = scales::percent) +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8)
+  )
 
@@
         # "General Business and Industry",
-        "Information Technology Management",
+        "Information Technology Management"
         # "Management and Program Analysis",
@@
         # "Financial Administration and Program",
-        "General Business and Industry",
+        "General Business and Industry"
         # "Information Technology Management",
@@
         # "Miscellaneous Administration and Program"
-        "Realty",
-        "Transportation Operations"
+        # "Realty",
+        # "Transportation Operations"
       )
@@
         # "Budget Analysis",
-        "Building Management",
+        # "Building Management",
         # "Contracting",
         # "Financial Administration and Program",
-        "General Business and Industry",
+        # "General Business and Industry",
         # "Information Technology Management",
@@
 ```{r}
-# f <- file.path(params$google_drive_home,"03. Data Collection","tiger","tl_2022_us_state.zip")
-# library(tigris)
-# tigris::load_tiger(url = f)
+states()
+```
+
+# TIL
+
+-   Telework is very common - most GSA employees telework
+
+-   Teleworkers and office visitors are very common for those that live in states neighboring DC
+
+-   Employees living in DC are more likely to come to the office
+
+-   PBS has considerable more onsite work than other offices
+
+# Appendix
+
+# Position Categories: How much telework?
+
+```{r include=FALSE}
+prep_d_01 <- 
+  d %>% 
+  group_by(position_category_description) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n))
+
+prep_v_01 <- 
+  prep_d_01 %>% 
+  slice(3) %>% 
+  pull(n)
+
+prep_01 <- 
+  d %>% 
+   mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
+         position_category_description = fct_infreq(position_category_description)) %>%
+  group_by(position_category_description) %>% 
+  summarise(num = mean(daily_status_teleworking)) %>% 
+  ungroup()
+
+prep_02 <- 
+  d %>% 
+   mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
+         position_category_description = fct_infreq(position_category_description)) %>%
+  group_by(position_category_description) %>% 
+  summarise(y = max(density(daily_status_teleworking)$y),
+            x = density(daily_status_teleworking)$x[density(daily_status_teleworking)$y == max(density(daily_status_teleworking)$y)]
+  )
+```
+
+```{r}
+p_1 <- 
+  prep_01 %>% 
+  ggplot(
+    aes(x = position_category_description, y = num, fill = position_category_description)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::comma) +
+  ylab("Mean days of telework") +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_2 <- 
+  d %>% 
+  mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
+         position_category_description = fct_infreq(position_category_description)) %>%
+  ggplot(
+    aes(x = daily_status_teleworking, color = position_category_description, fill = position_category_description)
+  ) +
+  geom_density(alpha = .5) +
+  # geom_vline(data = prep_01, aes(xintercept = num, color = position_category_description)) +
+  geom_text(data=prep_02, aes(x=x, y=y, label=position_category_description), size = 3, hjust = "inward") +
+  xlab("Days of telework") +
+  ylab("Density") +
+  theme_light() +
+  theme(legend.position = "None")
+
+p_1|p_2
+```
+
+# Position Categories: How much onsite work?
+
+```{r include=FALSE}
+prep_d_01 <- 
+  d %>% 
+  group_by(position_category_description) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n))
+
+prep_v_01 <- 
+  prep_d_01 %>% 
+  slice(3) %>% 
+  pull(n)
+
+prep_01 <- 
+  d %>% 
+   mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
+         position_category_description = fct_infreq(position_category_description)) %>%
+  group_by(position_category_description) %>% 
+  summarise(num = mean(daily_status_reporting_to_job_site)) %>% 
+  ungroup()
+
+prep_02 <- 
+  d %>% 
+   mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
+         position_category_description = fct_infreq(position_category_description)) %>%
+  group_by(position_category_description) %>% 
+  summarise(y = max(density(daily_status_reporting_to_job_site)$y),
+            x = density(daily_status_reporting_to_job_site)$x[density(daily_status_reporting_to_job_site)$y == max(density(daily_status_reporting_to_job_site)$y)]
+  )
+```
+
+```{r}
+p_1 <- 
+  prep_01 %>% 
+  ggplot(
+    aes(x = position_category_description, y = num, fill = position_category_description)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::comma) +
+  ylab("Mean days of onsite work") +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_2 <- 
+  d %>% 
+  mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
+         position_category_description = fct_infreq(position_category_description)) %>%
+  ggplot(
+    aes(x = daily_status_reporting_to_job_site, color = position_category_description, fill = position_category_description)
+  ) +
+  geom_density(alpha = .5) +
+  # geom_vline(data = prep_01, aes(xintercept = num, color = position_category_description)) +
+  geom_text(data=prep_02, aes(x=x, y=y, label=position_category_description), size = 3, hjust = "inward") +
+  xlab("Days of onsite work") +
+  ylab("Density") +
+  theme_light() +
+  theme(legend.position = "None")
+
+p_1|p_2
+```
+
+# Rule-based groups: How much telework?
+
+```{r}
+prep_d_01 <-
+  d %>%
+  select(person_id, 
+         rule_based_primarily_teleworking_working,
+         rule_based_mostly_teleworking_working,
+         rule_based_mostly_reporting_to_job_site_working,
+         rule_based_primarily_reporting_to_job_site_working,
+         rule_based_all_remote,
+         rule_based_telework_onsite_minimum,
+         daily_status_teleworking) %>% 
+  pivot_longer(starts_with("rule_based_")) %>% 
+  filter(value == 1) %>% 
+  mutate(
+    name = str_remove(name, "rule_based_"),
+    name = str_remove(name, "_working"),
+    name = str_replace_all(name, "_", " "),
+    name = str_to_sentence(name),
+    name = fct_relevel(
+      name,
+      "Primarily teleworking",
+      "Mostly teleworking",
+      "Mostly reporting to job site",
+      "Primarily reporting to job site",
+      "All remote",
+      "Telework onsite minimum"
+    ),
+    name = fct_relabel(name, ~str_wrap(.,width = 20))
+  ) %>% 
+  arrange(name)
+
+prep_01 <- 
+  prep_d_01 %>% 
+  group_by(name) %>% 
+  summarise(num = mean(daily_status_teleworking)) %>% 
+  ungroup()
+
+prep_02 <- 
+  prep_d_01 %>% 
+  group_by(name) %>% 
+  summarise(y = max(density(daily_status_teleworking)$y),
+            x = density(daily_status_teleworking)$x[density(daily_status_teleworking)$y == max(density(daily_status_teleworking)$y)]
+  )
+```
+
+```{r}
+p_1 <- 
+  prep_01 %>% 
+  ggplot(
+    aes(x = name, y = num, fill = name)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::comma) +
+  ylab("Mean days of telework") +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_2 <- 
+  prep_d_01 %>% 
+  ggplot(
+    aes(x = daily_status_teleworking, color = name, fill = name)
+  ) +
+  geom_density(alpha = .5) +
+  # geom_vline(data = prep_01, aes(xintercept = num, color = name)) +
+  geom_text(data=prep_02, aes(x=x, y=y, label=name), size = 3, hjust = "inward") +
+  xlab("Days of telework") +
+  ylab("Density") +
+  theme_light() +
+  theme(legend.position = "None")
+
+p_1|p_2
+```
+
+# Rule-based groups: How much telework?
+
+```{r}
+prep_d_01 <-
+  d %>%
+  select(person_id, 
+         rule_based_primarily_teleworking_working,
+         rule_based_mostly_teleworking_working,
+         rule_based_mostly_reporting_to_job_site_working,
+         rule_based_primarily_reporting_to_job_site_working,
+         rule_based_all_remote,
+         rule_based_telework_onsite_minimum,
+         daily_status_reporting_to_job_site) %>% 
+  pivot_longer(starts_with("rule_based_")) %>% 
+  filter(value == 1) %>% 
+  mutate(
+    name = str_remove(name, "rule_based_"),
+    name = str_remove(name, "_working"),
+    name = str_replace_all(name, "_", " "),
+    name = str_to_sentence(name),
+    name = fct_relevel(
+      name,
+      "Primarily teleworking",
+      "Mostly teleworking",
+      "Mostly reporting to job site",
+      "Primarily reporting to job site",
+      "All remote",
+      "Telework onsite minimum"
+    ),
+    name = fct_relabel(name, ~str_wrap(.,width = 20))
+  ) %>% 
+  arrange(name)
+
+prep_01 <- 
+  prep_d_01 %>% 
+  group_by(name) %>% 
+  summarise(num = mean(daily_status_reporting_to_job_site)) %>% 
+  ungroup()
+
+prep_02 <- 
+  prep_d_01 %>% 
+  group_by(name) %>% 
+  summarise(y = max(density(daily_status_reporting_to_job_site)$y),
+            x = density(daily_status_reporting_to_job_site)$x[density(daily_status_reporting_to_job_site)$y == max(density(daily_status_reporting_to_job_site)$y)]
+  )
+```
+
+```{r}
+p_1 <- 
+  prep_01 %>% 
+  ggplot(
+    aes(x = name, y = num, fill = name)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::comma) +
+  ylab("Mean days of onsite work") +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_2 <- 
+  prep_d_01 %>% 
+  ggplot(
+    aes(x = daily_status_reporting_to_job_site, color = name, fill = name)
+  ) +
+  geom_density(alpha = .5) +
+  # geom_vline(data = prep_01, aes(xintercept = num, color = name)) +
+  geom_text(data=prep_02, aes(x=x, y=y, label=name), size = 3, hjust = "inward") +
+  xlab("Days of onsite work") +
+  ylab("Density") +
+  theme_light() +
+  theme(legend.position = "None")
+
+p_1|p_2
+```
+
+# Onsite Flexible: Rule-based groups
+
+```{r}
+prep_d_01 <- 
+  d %>%
+  filter(position_category_description == "Onsite Flexible") %>% 
+  summarise(across(
+    .cols = starts_with("rule_based"),
+    .fns = ~ sum(., rm.na = T)
+  )) %>%
+  select(-contains("_position_category_")) %>%
+  select(-ends_with("observation")) %>%
+  rownames_to_column() %>%
+  pivot_longer(-rowname) %>%
+  select(-rowname) %>%
+  mutate(
+    name = str_remove(name, "rule_based_"),
+    name = str_remove(name, "_working"),
+    name = str_replace_all(name, "_", " "),
+    name = str_to_sentence(name),
+    name = fct_relevel(
+      name,
+      "Primarily teleworking",
+      "Mostly teleworking",
+      "Mostly reporting to job site",
+      "Primarily reporting to job site",
+      "All remote",
+      "Telework onsite minimum"
+    ),
+    name = fct_relabel(name, ~str_wrap(.,width = 20))
+  ) %>% 
+  arrange(name)
+
+prep_d_02 <- 
+  prep_d_01 %>% 
+  mutate(tot = d %>% count() %>% pull(),
+         prop = value/tot,
+         text = scales::percent(prop, accuracy = .1))
+```
+
+```{r}
+p_1 <- 
+  prep_d_01 %>% 
+  ggplot(
+    aes(x = name, y = value, fill = name)
+  ) +
+  geom_col() +
+  geom_text(data = prep_d_02, aes(x = name, y = .5*value, label = text), color = "white") +
+  scale_y_continuous(labels = scales::comma) +
+  ylab("Employees") +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_1
 ```

### 2023-09-05 04. Analysis/scripts/04-01-reporting-presentation.Rmd
Update 04-01-reporting-presentation.Rmd

@@
 tictoc::tic()
+if(!("ggalluvial" %in% installed.packages()[,"Package"]))
+{
+  install.packages("ggalluvial")
+}
 if(!("arsenal" %in% installed.packages()[,"Package"]))
@@
 }
+if(!("ggrain" %in% installed.packages()[,"Package"]))
+{
+  install.packages("ggrain")
+}
 # install.packages("tigris")
@@
 library(ggrepel)
+library(ggalluvial)
+library(ggrain)
 options(tigris_class = "sf")
@@
                             "Hybrid workers" = "3",
-                            "Onsite workers" = "4",
+                            "In-office workers" = "4",
                             "Disconnected workers" = "5"),
@@
   group_by(.cluster_5) %>% 
-  summarise(num = mean(daily_status_reporting_to_job_site)) %>% 
+  summarise(num = mean(daily_status_teleworking)) %>% 
   ungroup()
@@
 p_1|p_2
+```
+
+# Clusters: How much telework? (proportion of working)
+
+```{r include=FALSE}
+prep_01 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(num = mean(daily_status_teleworking_working_prop)) %>% 
+  ungroup()
+
+prep_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(y = max(density(daily_status_teleworking_working_prop)$y),
+            x = density(daily_status_teleworking_working_prop)$x[density(daily_status_teleworking_working_prop)$y == max(density(daily_status_teleworking_working_prop)$y)]
+  )
+```
+
+```{r}
+p_1 <- 
+  prep_01 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = num, fill = .cluster_5)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::comma) +
+  ylab("Mean days of telework") +
+  theme_light() +
+  oescolorrrs::scale_fill_oes() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_2 <- 
+  d %>% 
+  ggplot(
+    aes(x = daily_status_teleworking_working_prop, color = .cluster_5, fill = .cluster_5)
+  ) +
+  geom_density(alpha = .5) +
+  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
+  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
+  xlab("Days of telework") +
+  ylab("Density") +
+  theme_light() +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme(legend.position = "None")
+
+p_1|p_2
+```
+
+# Clusters: How much telework? (proportion of working) (rain)
+
+```{r}
+d %>% 
+  ggplot(
+    aes(x = 1, y = daily_status_teleworking_working_prop, fill = .cluster_5)
+  ) +
+ geom_rain(alpha = .5,
+           rain.side = "r") +
+  coord_flip()
+```
+
+# Clusters: How much telework? (proportion of working) (rain)
+
+```{r}
+prep_01 <-
+  d %>%
+  group_by(.cluster_5) %>%
+  summarise(
+    num = mean(daily_status_teleworking_working_prop),
+    l = quantile(daily_status_teleworking_working_prop, probs = .25),
+    u = quantile(daily_status_teleworking_working_prop, probs = .75)
+  ) %>%
+  ungroup()
+
+# d %>%
+  ggplot(
+  ) +
+  geom_jitter(data = d,
+    aes(
+      x = .cluster_5,
+      y = daily_status_teleworking_working_prop,
+      fill = .cluster_5,
+      color = .cluster_5
+    ),
+    position = position_jitter(0.2), color = "darkgray") +
+  geom_pointrange(
+    aes(
+      x = .cluster_5,
+      fill = .cluster_5,
+      color = .cluster_5,
+      y = num,
+      ymin = l,
+      ymax = u
+    ),
+    data = prep_01
+  )
+
+# Combine with violin plots
+# d %>% 
+#   ggplot(df, aes(dose, len)) +
+#   geom_violin(color = "darkgray", trim = FALSE) + 
+#   geom_pointrange(aes(ymin = len-sd, ymax = len+sd), data = df.summary)
 ```
@@
   ungroup()
-
-d %>%
+```
+
+```{r}
+prep_gg_1 <- d %>%
   mutate(
@@
     )
-  ) +
+  )
+```
+
+```{r}
+p_1 <- 
+  prep_gg_1 +
   geom_jitter(# aes(size = working_days),
@@
   ) +
+  xlab("Days reporting to the site") +
+  ylab("Days teleworking") +
   theme_light() +
@@
   theme(legend.position = "None")
+```
+
+```{r}
+p_1
+```
+
+```{r}
+p_2 <- 
+  prep_gg_1 +
+  geom_jitter(# aes(size = working_days),
+    alpha = .5,
+    size = .5) +
+  stat_ellipse(
+    geom = "polygon",
+    alpha = .15,
+    size = .5,
+    level = .99
+  ) +
+  geom_text_repel(
+    data = prep_01,
+    aes(x = daily_status_reporting_to_job_site, y = daily_status_teleworking, 
+        label = .cluster_5,
+        fill = .cluster_5),
+    # fill = "white",
+    # alpha = .15,
+    size = 3,
+    force             = 0.5,
+    # nudge_x           = 100,
+    xlim = c(100, 150),
+    ylim = c(75,150),
+    direction         = "y",
+    hjust             = 0,
+    segment.size      = 0.2,
+    segment.curvature = -0.1,
+    color = "black"
+  ) +
+  xlab("Days reporting to the site") +
+  ylab("Days teleworking") +
+  theme_light() +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme(legend.position = "None",
+        axis.title = element_text(size = 8))
+```
+
+```{r}
+p_2
+```
+
+```{r}
+file_name <- "abstract_1.png"
+fp <- file.path(params$google_drive_home,"04. Analysis", "output", "png",file_name)
+```
+
+```{r}
+ggsave(filename = fp, plot = p_2, width = 3, height = 3, units = "in")
 ```
@@
 p_1
+```
+
+# Clusters and position categories (alluvial)
+
+```{r}
+is_alluvia_form(prep_d_05)
+```
+
+```{r}
+p_1 <- 
+  prep_d_05 %>% 
+  mutate(.cluster_5 = fct_relabel(.cluster_5,~str_wrap(.,width = 50))) %>% 
+  ggplot(aes(y = num, axis1 = .cluster_5, axis2 = position_category_description, fill = .cluster_5)) +
+  geom_alluvium(width = 1/12) +
+  geom_stratum(width = 1/12,
+               # alpha = 1,
+               fill = "black",
+               color = "white"
+               ) +
+  geom_label(stat = "stratum", aes(label = after_stat(stratum)),
+             fill = "white",
+             # , alpha = .05,
+             hjust = "inward"
+             ) +
+  ylab("Number of employees") +
+  scale_y_continuous(labels = scales::comma) +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_blank())
+```
+
+```{r}
+p_1
+```
+
+```{r}
+p_2 <- 
+  prep_d_05 %>% 
+  mutate(.cluster_5 = fct_relabel(.cluster_5,~str_wrap(.,width = 50))) %>% 
+  ggplot(aes(y = num, axis1 = .cluster_5, axis2 = position_category_description, fill = .cluster_5)) +
+  geom_alluvium(width = 1/12) +
+  geom_stratum(width = 1/12,
+               # alpha = 1,
+               fill = "black",
+               color = "white"
+               ) +
+  geom_label(stat = "stratum", aes(label = after_stat(stratum)),
+             fill = "white",
+             # , alpha = .05,
+              size = 2,
+             hjust = "inward"
+             ) +
+  ylab("Number of employees") +
+  scale_y_continuous(labels = scales::comma) +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.y = element_text(size = 8),
+    axis.title.x = element_blank(),
+    axis.text.x = element_blank())
+```
+
+```{r}
+p_2
+```
+
+```{r}
+file_name <- "abstract_2.png"
+fp <- file.path(params$google_drive_home,"04. Analysis", "output", "png",file_name)
+```
+
+```{r}
+ggsave(filename = fp, plot = p_2, width = 3, height = 3, units = "in")
 ```

### 2023-09-06 04. Analysis/scripts/02_data_preparation_clusters_employee.Rmd
Update 02_data_preparation_clusters_employee.Rmd
Limited join to just person_id
Updates for the abstract

@@
 date_observation_window_month_start <- date_cohort_month_start %m+% months(params$observation_window_length_months)
-date_observation_window_month_end <- ceiling_date(date_observation_window_month_start,unit = "month") %>% rollbackward()
+date_observation_window_month_end <- 
+  # ceiling_date(date_observation_window_month_start,unit = "month") %>% 
+  date_observation_window_month_start %>% 
+  rollbackward()
 ```
@@
   prep_building %>% 
-  left_join(prep_xx)
+  left_join(prep_xx, by = "person_id")
 ```

### 2023-09-06 04. Analysis/scripts/03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Update 03-03-data-analysis-employee-cluster-descriptive-statistics.Rmd
Updates for the abstract

@@
   data_folder_1: "prepared-data"
-  data_file_1: "clusters-employee-2023-08-09.rdata"
-  data_file_2: "prep_employees_2023-08-09.rdata"
+  data_file_1: "clusters-employee-2023-09-06.rdata"
+  data_file_2: "prep_employees_2023-09-06.rdata"
   in_number_of_clusters_1: 2
@@
 names(d)
+```
+
+```{r}
+d %>% count(duty_station_code)
 ```

### 2023-09-06 04. Analysis/scripts/04-01-reporting-presentation.Rmd
Updates for the abstract

@@
     .cluster_5 = fct_recode(.cluster_5,
-                            "Teleworkers" = "1",
+                            "Telecommuters" = "1",
                             "Office visitors" = "2",
@@
 
-1.  Teleworkers
+1.  Telecommuters
 
@@
 
-# Teleworkers, office visitors, and regions
+# Telecommuters, office visitors, and regions
 
@@
   prep_d_03 %>% 
-  filter(.cluster_5 == "Teleworkers" |
+  filter(.cluster_5 == "Telecommuters" |
            .cluster_5 == "Office\nvisitors"
@@
 
--   Teleworkers and office visitors are very common for those that live in states neighboring DC
+-   Telecommuters and office visitors are very common for those that live in states neighboring DC
 

### 2023-09-06 04. Analysis/scripts/04-02-abstract.Rmd
Updates for the abstract

--- 2023-08-24 04. Analysis/scripts/04-01-reporting-presentation.Rmd
@@
 ---
-title: "slides for lab"
-author: "Ben Jaques-Leslie"
-date: "2023-08-22"
-output: powerpoint_presentation
+title: "Analysis plan"
+# date: "`r Sys.Date()`"
+output: 
+  html_document:
+    theme: united
+    highlight: tango
+    code_folding: hide
 params:
@@
   in_specification: "scale_observation_none_1_20_TRUE"
+  date_cohort_month: "2022-03-01"
+  observation_window_length_months: 6
 ---
@@
 knitr::opts_chunk$set(echo = FALSE,
-                      warning = FALSE,
-                      message = FALSE,
-                      fig.width = 8,
-                      fig.height = 4,
                       dpi = 300)
@@
     .cluster_5 = fct_recode(.cluster_5,
-                            "Teleworkers" = "1",
+                            "Telecommuters" = "1",
                             "Office visitors" = "2",
                             "Hybrid workers" = "3",
-                            "Onsite workers" = "4",
-                            "Disconnected workers" = "5"),
+                            "Disconnected workers" = "4",
+                            "In-office workers" = "5"),
     .cluster_5 = fct_relabel(.cluster_5, ~str_wrap(.x,width = 10))
@@
 
-# What is the GSA priority?
-
--   Telework has become very common
-
--   Much of GSA staff telework
-
--   How employees use telework is not clear
-
--   Defining and describing different work patterns may help to understand organizational health
-
--   By understanding how staff work (remote, hybrid, or onsite), different strategies may be developed to improve productivity and staff engagement
-
-# How did the evaluation work?
-
--   Data:
-
-    -   GSA check-in data, GSA staff roster
-
-    -   March - September 2023
-
--   All GSA staff
-
-    -   Categorized work patterns by remote or onsite
-
-    -   Rules: Mostly remote or onsite, staff category (flexible, onsite, etc), flexible onsite
-
-    -   Clusters: K-means clusters defined using frequency of work location status, collocation with team members, and team remote work
-
-# Position categories
-
 ```{r}
-prep_d_01 <- 
 d %>% 
-  group_by(position_category_description) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n))
-
-prep_v_01 <- 
-  prep_d_01 %>% 
-  slice(3) %>% 
-  pull(n)
-
-prep_d_02 <-
-  d %>%
-  mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
-         position_category_description = fct_infreq(position_category_description)) %>%
-  group_by(position_category_description) %>%
-  count() %>%
-  ungroup() %>%
-  arrange(desc(n)) %>% 
-  rename(num = n)
+  skim()
 ```
@@
 ```{r}
-p_1 <- 
-  prep_d_02 %>% 
-  ggplot(
-    aes(x = position_category_description, y = num, fill = position_category_description)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Employees") +
-  theme_light() +
-  oescolorrrs::scale_fill_oes() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
+d %>% 
+  group_by(.cluster_5) %>% 
+  skim(daily_status_reporting_to_job_site,
+       daily_status_reporting_to_job_site_observation_prop,
+       daily_status_teleworking,
+       daily_status_teleworking_observation_prop,
+       days_colocated_1,
+       days_colocated_1_observation_prop,
+       days_colocated_supervisor,
+       days_colocated_supervisor_observation_prop,
+       days_colocated_team,
+       days_colocated_team_observation_prop,
+       days_telework_team,
+       days_telework_team_observation_prop,
+       working_days,
+       team_size_mode) %>% 
+  as.data.frame()
 ```
 
-# Rule-based groups
+# Table data
 
-```{r}
-prep_d_01 <- 
-  d %>%
-  summarise(across(
-    .cols = starts_with("rule_based"),
-    .fns = ~ sum(., rm.na = T)
-  )) %>%
-  select(-contains("_position_category_")) %>%
-  select(-ends_with("observation")) %>%
-  rownames_to_column() %>%
-  pivot_longer(-rowname) %>%
-  select(-rowname) %>%
-  mutate(
-    name = str_remove(name, "rule_based_"),
-    name = str_remove(name, "_working"),
-    name = str_replace_all(name, "_", " "),
-    name = str_to_sentence(name),
-    name = fct_relevel(
-      name,
-      "Primarily teleworking",
-      "Mostly teleworking",
-      "Mostly reporting to job site",
-      "Primarily reporting to job site",
-      "All remote",
-      "Telework onsite minimum"
-    ),
-    name = fct_relabel(name, ~str_wrap(.,width = 20))
-  ) %>% 
-  arrange(name)
-
-prep_d_02 <- 
-  prep_d_01 %>% 
-  mutate(tot = d %>% count() %>% pull(),
-         prop = value/tot,
-         text = scales::percent(prop, accuracy = .1))
-```
-
-```{r}
-p_1 <- 
-  prep_d_01 %>% 
-  ggplot(
-    aes(x = name, y = value, fill = name)
-  ) +
-  geom_col() +
-  geom_text(data = prep_d_02, aes(x = name, y = .5*value, label = text), color = "white") +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Employees") +
-  theme_light() +
-  oescolorrrs::scale_fill_oes() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
-```
-
-# Clusters
-
-1.  Teleworkers
-
-2.  Office visitors
-
-3.  Hybrid workers
-
-4.  Onsite workers
-
-5.  Disconnected workers
-
-# Clusters
+## Percent of GSA employees
 
@@
          text = scales::percent(prop, accuracy = .1))
+
+prep_d_02
+```
+
+## Days per pay period
+
+```{r}
+date_cohort_month_start <- ymd(params$date_cohort_month)
+date_cohort_month_end <- ceiling_date(date_cohort_month_start,unit = "month") %>% rollbackward()
+date_observation_window_month_start <- date_cohort_month_start %m+% months(params$observation_window_length_months)
+date_observation_window_month_end <- 
+  # ceiling_date(date_observation_window_month_start,unit = "month") %>% 
+  date_observation_window_month_start %>% 
+  rollbackward()
 ```
@@
 ```{r}
-p_1 <- 
-  prep_d_01 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = n, fill = .cluster_5)
-  ) +
-  geom_col() +
-  geom_text(data = prep_d_02, aes(x = .cluster_5, y = .5*n, label = text), color = "white") +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Employees") +
-  theme_light() +
-  oescolorrrs::scale_fill_oes() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
+prep_a <- 
+  tibble(
+  date = seq.Date(from = ymd("2022-01-01"),
+         to = ymd("2022-12-31"),
+         by = "2 weeks")
+) %>% 
+  rownames_to_column(var = "period_number") 
 ```
 
-# Clusters: How much telework?
+Review data.
 
-```{r include=FALSE}
-prep_01 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(num = mean(daily_status_reporting_to_job_site)) %>% 
-  ungroup()
+```{r}
+prep_a %>% 
+  skim()
+```
 
-prep_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(y = max(density(daily_status_teleworking)$y),
-            x = density(daily_status_teleworking)$x[density(daily_status_teleworking)$y == max(density(daily_status_teleworking)$y)]
+```{r}
+params$date_cohort_month %m+% months(params$observation_window_length_months)
+```
+
+Second, create a dataframe of all the days of the year.
+
+```{r}
+prep_b <- 
+  tibble(
+  date = seq.Date(from = ymd("2022-01-01"),
+         to = ymd("2022-12-31"),
+         by = "days")
 )
@@
 
+Review data.
+
 ```{r}
-p_1 <- 
-  prep_01 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = num, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Mean days of telework") +
-  theme_light() +
-  oescolorrrs::scale_fill_oes() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_2 <- 
-  d %>% 
-  ggplot(
-    aes(x = daily_status_teleworking, color = .cluster_5, fill = .cluster_5)
-  ) +
-  geom_density(alpha = .5) +
-  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
-  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
-  xlab("Days of telework") +
-  ylab("Density") +
-  theme_light() +
-  oescolorrrs::scale_fill_oes() +
-  oescolorrrs::scale_color_oes() +
-  theme(legend.position = "None")
-
-p_1|p_2
+prep_b %>% 
+  skim()
 ```
 
-# Clusters: How much onsite work?
-
-```{r include=FALSE}
-prep_01 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(num = mean(daily_status_reporting_to_job_site)) %>% 
-  ungroup()
-
-prep_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(xPos = max(daily_status_reporting_to_job_site),
-            yPos = max((density(daily_status_reporting_to_job_site))$y))
-
-prep_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(y = max(density(daily_status_reporting_to_job_site)$y),
-            x = density(daily_status_reporting_to_job_site)$x[density(daily_status_reporting_to_job_site)$y == max(density(daily_status_reporting_to_job_site)$y)]
-  )
-```
-
-```{r}
-p_1 <- 
-  prep_01 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = num, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Mean days of onsite work") +
-  theme_light() +
-  oescolorrrs::scale_fill_oes() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_2 <- 
-  d %>% 
-  ggplot(
-    aes(x = daily_status_reporting_to_job_site, color = .cluster_5, fill = .cluster_5)
-  ) +
-  geom_density(alpha = .5) +
-  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
-  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
-  xlab("Days of onsite work") +
-  ylab("Density") +
-  theme_light() +
-  oescolorrrs::scale_fill_oes() +
-  oescolorrrs::scale_color_oes() +
-  theme(legend.position = "None")
-
-p_1|p_2
-```
-
-# Clusters: Telework and onsite
-
-```{r}
-prep_01 <-
-  d %>%
-  mutate(
-    .cluster_5 = fct_relabel(.cluster_5,~str_wrap(.,width = 50))
-  ) %>% 
-  group_by(.cluster_5) %>%
-  summarise(across
-            (
-              .cols = c(
-                daily_status_teleworking,
-                daily_status_reporting_to_job_site,
-                working_days
-              ),
-              .fns = mean
-            )) %>%
-  ungroup()
-
-d %>%
-  mutate(
-    .cluster_5 = fct_relabel(.cluster_5,~str_wrap(.,width = 50))
-  ) %>% 
-  ggplot(
-    aes(
-      x = daily_status_reporting_to_job_site,
-      y = daily_status_teleworking,
-      color = .cluster_5,
-      fill = .cluster_5,
-      linetype = .cluster_5
-    )
-  ) +
-  geom_jitter(# aes(size = working_days),
-    alpha = .5) +
-  stat_ellipse(
-    geom = "polygon",
-    alpha = .15,
-    size = 2,
-    level = .99
-  ) +
-  geom_text_repel(
-    data = prep_01,
-    aes(x = daily_status_reporting_to_job_site, y = daily_status_teleworking, 
-        label = .cluster_5,
-        fill = .cluster_5),
-    # fill = "white",
-    # alpha = .15,
-    size = 3,
-    force             = 0.5,
-    # nudge_x           = 100,
-    xlim = c(125),
-    ylim = c(50,150),
-    direction         = "y",
-    hjust             = 0,
-    segment.size      = 0.2,
-    segment.curvature = -0.1,
-    color = "black"
-  ) +
-  theme_light() +
-  oescolorrrs::scale_fill_oes() +
-  oescolorrrs::scale_color_oes() +
-  theme(legend.position = "None")
-```
-
-# Disconnected workers: Working days
-
-```{r include=FALSE}
-prep_01 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(num = mean(working_days)) %>% 
-  ungroup()
-
-prep_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(xPos = max(working_days),
-            yPos = max((density(working_days))$y))
-
-prep_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(y = max(density(working_days)$y),
-            x = density(working_days)$x[density(working_days)$y == max(density(working_days)$y)]
-  )
-```
-
-```{r}
-p_1 <- 
-  prep_01 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = num, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Mean working days") +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_2 <- 
-  d %>% 
-  ggplot(
-    aes(x = working_days, color = .cluster_5, fill = .cluster_5)
-  ) +
-  geom_density(alpha = .5) +
-  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
-  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
-  xlab("Working days") +
-  ylab("Density") +
-  theme_light() +
-  theme(legend.position = "None")
-
-p_1|p_2
-```
-
-# Disconnected workers: Exiting employment
-
-```{r include=FALSE}
-prep_01 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  summarise(num = sum(exit_employment)) %>% 
-  ungroup()
-
-prep_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup()
-
-prep_03 <- 
-  prep_01 %>% 
-  full_join(prep_02) %>% 
-  mutate(
-    num = num/n
-  )
-```
-
-```{r}
-p_1 <-
-  prep_03 %>%
-  ggplot(aes(x = .cluster_5, y = num, fill = .cluster_5)) +
-  geom_col() +
-  ylab("Percent exiting employment") +
-  scale_y_continuous(labels = scales::percent) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8)
-  )
-
-p_1
-```
-
-# Clusters and position categories
+# Clusters and position categories (alluvial)
 
@@
 ```{r}
-p_1 <- 
-  prep_d_05 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = n, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in position category") +
-  facet_wrap(facets = vars(position_category_description), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
-```
-
-# Teleworkers, office visitors, and regions
-
-```{r}
-prep_d_01 <- 
-  d %>% 
-  group_by(gsa_region,.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(num = n)
-
-prep_d_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(tot = n)
-
-prep_d_03 <- 
-  prep_d_01 %>% 
-  full_join(prep_d_02) %>% 
-  mutate(
-    n = num/tot,
-    text = scales::comma(num)
-  ) %>% 
-  mutate(
-    gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
-  )
-
-prep_d_04 <- 
-  prep_d_03 %>% 
-  filter(.cluster_5 == "Teleworkers" |
-           .cluster_5 == "Office\nvisitors"
-           )
-```
-
-```{r}
-p_1 <- 
-  prep_d_04 %>% 
-  ggplot(
-    aes(x = gsa_region, y = n, fill = gsa_region)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in region") +
-  facet_wrap(facets = vars(.cluster_5), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
-```
-
-# Hybrid, onsite, and disconnected workers and regions
-
-```{r}
-prep_d_01 <- 
-  d %>% 
-  group_by(gsa_region,.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(num = n)
-
-prep_d_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(tot = n)
-
-prep_d_03 <- 
-  prep_d_01 %>% 
-  full_join(prep_d_02) %>% 
-  mutate(
-    n = num/tot,
-    text = scales::comma(num)
-  ) %>% 
-  mutate(
-    gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
-  )
-
-prep_d_04 <- 
-  prep_d_03 %>% 
-  filter(.cluster_5 == "Hybrid\nworkers" |
-           .cluster_5 == "Onsite\nworkers" |
-           .cluster_5 == "Disconnected\nworkers")
-```
-
-```{r}
-p_1 <- 
-  prep_d_04 %>% 
-  ggplot(
-    aes(x = gsa_region, y = n, fill = gsa_region)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in region") +
-  facet_wrap(facets = vars(.cluster_5), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
-```
-
-# States: MD, PA, and VA
-
-```{r}
-prep_d_01 <- 
-  d %>% 
-  group_by(location_state,.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(num = n)
-
-prep_d_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(tot = n)
-
-prep_d_03 <- 
-  prep_d_01 %>% 
-  full_join(prep_d_02) %>% 
-  mutate(
-    n = num/tot,
-    text = scales::comma(num)
-  )# %>% 
-  # mutate(
-  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
-  # )
-
-prep_d_04 <- 
-  prep_d_03 %>% 
-  filter(location_state %in% c("MD","PA","VA")
-           )
-```
-
-```{r}
-p_1 <- 
-  prep_d_04 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = n, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in state") +
-  facet_wrap(facets = vars(location_state), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
-```
-
-# States: CA and IL
-
-```{r}
-prep_d_01 <- 
-  d %>% 
-  group_by(location_state,.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(num = n)
-
-prep_d_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(tot = n)
-
-prep_d_03 <- 
-  prep_d_01 %>% 
-  full_join(prep_d_02) %>% 
-  mutate(
-    n = num/tot,
-    text = scales::comma(num)
-  )# %>% 
-  # mutate(
-  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
-  # )
-
-prep_d_04 <- 
-  prep_d_03 %>% 
-  filter(location_state %in% c("CA", "IL")
-           )
-```
-
-```{r}
-p_1 <- 
-  prep_d_04 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = n, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in state") +
-  facet_wrap(facets = vars(location_state), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
-```
-
-# District of Columbia
-
-```{r}
-prep_d_01 <- 
-  d %>% 
-  group_by(location_state,.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(num = n)
-
-prep_d_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(tot = n)
-
-prep_d_03 <- 
-  prep_d_01 %>% 
-  full_join(prep_d_02) %>% 
-  mutate(
-    n = num/tot,
-    text = scales::comma(num)
-  )# %>% 
-  # mutate(
-  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
-  # )
-
-prep_d_04 <- 
-  prep_d_03 %>% 
-  filter(location_state %in% c("DC")
-           )
-```
-
-```{r}
-p_1 <- 
-  prep_d_04 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = n, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in state") +
-  facet_wrap(facets = vars(location_state), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
-```
-
-# Clusters and staff offices
-
-```{r}
-prep_d_01 <- 
-  d %>% 
-  group_by(gsa_sso) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n))
-
-prep_v_01 <- 
-  prep_d_01 %>% 
-  slice(2) %>% 
-  pull(n)
-
-prep_d_02 <-
-  d %>%
-  mutate(gsa_sso = fct_lump_min(gsa_sso, min = prep_v_01),
-         gsa_sso = fct_infreq(gsa_sso)) %>%
-  group_by(gsa_sso,.cluster_5) %>%
-  count() %>%
-  ungroup() %>%
-  arrange(desc(n)) %>% 
-  rename(num = n) %>% 
-  mutate(gsa_sso = fct_relevel(gsa_sso,
-                               "PBS",
-                               "FAS",
-                               "OCFO",
-                               "Other"))
-
-prep_d_03 <- 
-  prep_d_02 %>% 
-  filter(gsa_sso != "Other")
-
-prep_d_04 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(tot = n)
-
-prep_d_05 <- 
-  prep_d_03 %>% 
-  full_join(prep_d_04) %>% 
-  mutate(
-    n = num/tot,
-    text = scales::comma(num)
-  ) 
+is_alluvia_form(prep_d_05)
 ```
@@
   prep_d_05 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = n, fill = .cluster_5)
+  mutate(.cluster_5 = fct_relabel(.cluster_5,~str_wrap(.,width = 50))) %>% 
+  ggplot(aes(y = num, axis1 = .cluster_5, axis2 = position_category_description, fill = .cluster_5)) +
+  geom_alluvium(width = 1/12) +
+  geom_stratum(width = 1/12,
+               # alpha = 1,
+               fill = "black",
+               color = "white"
                ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in staff office") +
-  facet_wrap(facets = vars(gsa_sso), nrow = 1) +
+  geom_label(stat = "stratum", aes(label = after_stat(stratum)),
+             fill = "white",
+             # , alpha = .05,
+             hjust = "inward"
+             ) +
+  ylab("Number of employees") +
+  scale_y_continuous(labels = scales::comma) +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
   theme_light() +
@@
     axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 7))
-
-p_1
-```
-
-# Clusters and series
-
-```{r}
-prep_d_01 <- 
-  d %>% 
-  group_by(occupational_series) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n))
-
-prep_v_01 <- 
-  prep_d_01 %>% 
-  slice(3) %>% 
-  pull(n)
-
-prep_d_02 <-
-  d %>%
-  mutate(
-    # occupational_series = fct_lump_min(occupational_series, min = prep_v_01),
-    occupational_series = fct_infreq(occupational_series)
-  ) %>%
-  group_by(occupational_series, .cluster_5) %>%
-  count() %>%
-  ungroup() %>%
-  arrange(desc(n)) %>%
-  rename(num = n) %>%
-  mutate(
-    # occupational_series = fct_relevel(occupational_series,
-    #                                   "1102",
-    #                                   "1101",
-    #                                   "0343",
-    #                                   "Other"),
-    occupational_series = recode(occupational_series,
-                                 "1102" = "Contracting",
-                                 "1101" = "General Business and Industry",
-                                 "0343" = "Management and Program Analysis",
-                                 "0501" = "Financial Administration and Program",
-                                 "0560" = "Budget Analysis",
-                                 "0301" = "Miscellaneous Administration and Program",
-                                 "1170" = "Realty",
-                                 "1176" = "Building Management",
-                                 "2150" = "Transportation Operations",
-                                 "2210" = "Information Technology Management"
-                                 ),
-    occupational_series = fct_relevel(
-      occupational_series,
-      "Budget Analysis",
-      "Building Management",
-      "Contracting",
-      "Financial Administration and Program",
-      "General Business and Industry",
-      "Information Technology Management",
-      "Management and Program Analysis",
-      "Miscellaneous Administration and Program",
-      "Realty",
-      "Transportation Operations",
-    )
-  )
-
-# prep_d_02
+    axis.text.x = element_blank())
 ```
@@
 ```{r}
-prep_d_03 <-
-  prep_d_02 %>%
-  filter(
-    occupational_series %in%
-      c(
-        # "Budget Analysis",
-        # "Building Management",
-        "Contracting",
-        # "Financial Administration and Program",
-        # "General Business and Industry",
-        # "Information Technology Management",
-        "Management and Program Analysis",
-        "Miscellaneous Administration and Program"
-        # "Realty",
-        # "Transportation Operations"
-      )
-  )
-
-prep_d_04 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(tot = n)
-
-prep_d_05 <- 
-  prep_d_03 %>% 
-  full_join(prep_d_04) %>% 
-  mutate(
-    n = num/tot,
-    text = scales::comma(num)
-  ) %>% 
-  mutate(
-    occupational_series = fct_relabel(occupational_series,~str_wrap(.,width = 15))
-  )
-```
-
-```{r}
-p_1 <- 
-  prep_d_05 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = n, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in series") +
-  facet_wrap(facets = vars(occupational_series), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 7))
-
-p_1
-```
-
-# Clusters and series
-
-```{r}
-prep_d_01 <- 
-  d %>% 
-  group_by(occupational_series) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n))
-
-prep_v_01 <- 
-  prep_d_01 %>% 
-  slice(3) %>% 
-  pull(n)
-
-prep_d_02 <-
-  d %>%
-  mutate(
-    # occupational_series = fct_lump_min(occupational_series, min = prep_v_01),
-    occupational_series = fct_infreq(occupational_series)
-  ) %>%
-  group_by(occupational_series, .cluster_5) %>%
-  count() %>%
-  ungroup() %>%
-  arrange(desc(n)) %>%
-  rename(num = n) %>%
-  mutate(
-    # occupational_series = fct_relevel(occupational_series,
-    #                                   "1102",
-    #                                   "1101",
-    #                                   "0343",
-    #                                   "Other"),
-    occupational_series = recode(occupational_series,
-                                 "1102" = "Contracting",
-                                 "1101" = "General Business and Industry",
-                                 "0343" = "Management and Program Analysis",
-                                 "0501" = "Financial Administration and Program",
-                                 "0560" = "Budget Analysis",
-                                 "0301" = "Miscellaneous Administration and Program",
-                                 "1170" = "Realty",
-                                 "1176" = "Building Management",
-                                 "2150" = "Transportation Operations",
-                                 "2210" = "Information Technology Management"
-                                 ),
-    occupational_series = fct_relevel(
-      occupational_series,
-      "Budget Analysis",
-      "Building Management",
-      "Contracting",
-      "Financial Administration and Program",
-      "General Business and Industry",
-      "Information Technology Management",
-      "Management and Program Analysis",
-      "Miscellaneous Administration and Program",
-      "Realty",
-      "Transportation Operations",
-    )
-  )
-
-# prep_d_02
-```
-
-```{r}
-prep_d_03 <-
-  prep_d_02 %>%
-  filter(
-    occupational_series %in%
-      c(
-        "Budget Analysis",
-        # "Building Management",
-        # "Contracting",
-        "Financial Administration and Program",
-        # "General Business and Industry",
-        "Information Technology Management"
-        # "Management and Program Analysis",
-        # "Miscellaneous Administration and Program"
-        # "Realty",
-        # "Transportation Operations"
-      )
-  )
-
-prep_d_04 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(tot = n)
-
-prep_d_05 <- 
-  prep_d_03 %>% 
-  full_join(prep_d_04) %>% 
-  mutate(
-    n = num/tot,
-    text = scales::comma(num)
-  ) %>% 
-  mutate(
-    occupational_series = fct_relabel(occupational_series,~str_wrap(.,width = 15))
-  )
-```
-
-```{r}
-p_1 <- 
-  prep_d_05 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = n, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in series") +
-  facet_wrap(facets = vars(occupational_series), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 7))
-
-p_1
-```
-
-# Clusters and series
-
-```{r}
-prep_d_01 <- 
-  d %>% 
-  group_by(occupational_series) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n))
-
-prep_v_01 <- 
-  prep_d_01 %>% 
-  slice(3) %>% 
-  pull(n)
-
-prep_d_02 <-
-  d %>%
-  mutate(
-    # occupational_series = fct_lump_min(occupational_series, min = prep_v_01),
-    occupational_series = fct_infreq(occupational_series)
-  ) %>%
-  group_by(occupational_series, .cluster_5) %>%
-  count() %>%
-  ungroup() %>%
-  arrange(desc(n)) %>%
-  rename(num = n) %>%
-  mutate(
-    # occupational_series = fct_relevel(occupational_series,
-    #                                   "1102",
-    #                                   "1101",
-    #                                   "0343",
-    #                                   "Other"),
-    occupational_series = recode(occupational_series,
-                                 "1102" = "Contracting",
-                                 "1101" = "General Business and Industry",
-                                 "0343" = "Management and Program Analysis",
-                                 "0501" = "Financial Administration and Program",
-                                 "0560" = "Budget Analysis",
-                                 "0301" = "Miscellaneous Administration and Program",
-                                 "1170" = "Realty",
-                                 "1176" = "Building Management",
-                                 "2150" = "Transportation Operations",
-                                 "2210" = "Information Technology Management"
-                                 ),
-    occupational_series = fct_relevel(
-      occupational_series,
-      "Budget Analysis",
-      "Building Management",
-      "Contracting",
-      "Financial Administration and Program",
-      "General Business and Industry",
-      "Information Technology Management",
-      "Management and Program Analysis",
-      "Miscellaneous Administration and Program",
-      "Realty",
-      "Transportation Operations",
-    )
-  )
-
-# prep_d_02
-```
-
-```{r}
-prep_d_03 <-
-  prep_d_02 %>%
-  filter(
-    occupational_series %in%
-      c(
-        # "Budget Analysis",
-        "Building Management",
-        # "Contracting",
-        # "Financial Administration and Program",
-        "General Business and Industry"
-        # "Information Technology Management",
-        # "Management and Program Analysis",
-        # "Miscellaneous Administration and Program"
-        # "Realty",
-        # "Transportation Operations"
-      )
-  )
-
-prep_d_04 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(tot = n)
-
-prep_d_05 <- 
-  prep_d_03 %>% 
-  full_join(prep_d_04) %>% 
-  mutate(
-    n = num/tot,
-    text = scales::comma(num)
-  )  %>% 
-  mutate(
-    occupational_series = fct_relabel(occupational_series,~str_wrap(.,width = 15))
-  )
-```
-
-```{r}
-p_1 <- 
-  prep_d_05 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = n, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in series") +
-  facet_wrap(facets = vars(occupational_series), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 7))
-
-p_1
-```
-
-# Clusters and series
-
-```{r}
-prep_d_01 <- 
-  d %>% 
-  group_by(occupational_series) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n))
-
-prep_v_01 <- 
-  prep_d_01 %>% 
-  slice(3) %>% 
-  pull(n)
-
-prep_d_02 <-
-  d %>%
-  mutate(
-    # occupational_series = fct_lump_min(occupational_series, min = prep_v_01),
-    occupational_series = fct_infreq(occupational_series)
-  ) %>%
-  group_by(occupational_series, .cluster_5) %>%
-  count() %>%
-  ungroup() %>%
-  arrange(desc(n)) %>%
-  rename(num = n) %>%
-  mutate(
-    # occupational_series = fct_relevel(occupational_series,
-    #                                   "1102",
-    #                                   "1101",
-    #                                   "0343",
-    #                                   "Other"),
-    occupational_series = recode(occupational_series,
-                                 "1102" = "Contracting",
-                                 "1101" = "General Business and Industry",
-                                 "0343" = "Management and Program Analysis",
-                                 "0501" = "Financial Administration and Program",
-                                 "0560" = "Budget Analysis",
-                                 "0301" = "Miscellaneous Administration and Program",
-                                 "1170" = "Realty",
-                                 "1176" = "Building Management",
-                                 "2150" = "Transportation Operations",
-                                 "2210" = "Information Technology Management"
-                                 ),
-    occupational_series = fct_relevel(
-      occupational_series,
-      "Budget Analysis",
-      "Building Management",
-      "Contracting",
-      "Financial Administration and Program",
-      "General Business and Industry",
-      "Information Technology Management",
-      "Management and Program Analysis",
-      "Miscellaneous Administration and Program",
-      "Realty",
-      "Transportation Operations",
-    )
-  )
-
-# prep_d_02
-```
-
-```{r}
-prep_d_03 <-
-  prep_d_02 %>%
-  filter(
-    occupational_series %in%
-      c(
-        # "Budget Analysis",
-        # "Building Management",
-        # "Contracting",
-        # "Financial Administration and Program",
-        # "General Business and Industry",
-        # "Information Technology Management",
-        # "Management and Program Analysis",
-        # "Miscellaneous Administration and Program"
-        "Realty",
-        "Transportation Operations"
-      )
-  )
-
-prep_d_04 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(tot = n)
-
-prep_d_05 <- 
-  prep_d_03 %>% 
-  full_join(prep_d_04) %>% 
-  mutate(
-    n = num/tot,
-    text = scales::comma(num)
-  )  %>% 
-  mutate(
-    occupational_series = fct_relabel(occupational_series,~str_wrap(.,width = 15))
-  )
-```
-
-```{r}
-p_1 <- 
-  prep_d_05 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = n, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in series") +
-  facet_wrap(facets = vars(occupational_series), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 7))
-
 p_1
@@
 ```{r}
-states()
-```
-
-# TIL
-
--   Telework is very common - most GSA employees telework
-
--   Teleworkers and office visitors are very common for those that live in states neighboring DC
-
--   Employees living in DC are more likely to come to the office
-
--   PBS has considerable more onsite work than other offices
-
-# Appendix
-
-# Position Categories: How much telework?
-
-```{r include=FALSE}
-prep_d_01 <- 
-  d %>% 
-  group_by(position_category_description) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n))
-
-prep_v_01 <- 
-  prep_d_01 %>% 
-  slice(3) %>% 
-  pull(n)
-
-prep_01 <- 
-  d %>% 
-   mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
-         position_category_description = fct_infreq(position_category_description)) %>%
-  group_by(position_category_description) %>% 
-  summarise(num = mean(daily_status_teleworking)) %>% 
-  ungroup()
-
-prep_02 <- 
-  d %>% 
-   mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
-         position_category_description = fct_infreq(position_category_description)) %>%
-  group_by(position_category_description) %>% 
-  summarise(y = max(density(daily_status_teleworking)$y),
-            x = density(daily_status_teleworking)$x[density(daily_status_teleworking)$y == max(density(daily_status_teleworking)$y)]
-  )
+p_2 <- 
+  prep_d_05 %>% 
+  mutate(.cluster_5 = fct_relabel(.cluster_5,~str_wrap(.,width = 50))) %>% 
+  ggplot(aes(y = num, axis1 = position_category_description, axis2 = .cluster_5, fill = .cluster_5)) +
+  geom_alluvium(width = 1/12) +
+  geom_stratum(width = 1/12,
+               # alpha = 1,
+               fill = "black",
+               color = "white"
+               ) +
+  geom_label(stat = "stratum", aes(label = after_stat(stratum)),
+             fill = "white",
+             # , alpha = .05,
+              size = 2,
+             hjust = "inward"
+             ) +
+  labs(title = "Linking position categories to work pattern groups") +
+  ylab("Number of employees") +
+  scale_y_continuous(labels = scales::comma) +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.y = element_text(size = 8),
+    axis.title.x = element_blank(),
+    axis.text.x = element_blank())
 ```
@@
 ```{r}
-p_1 <- 
-  prep_01 %>% 
-  ggplot(
-    aes(x = position_category_description, y = num, fill = position_category_description)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Mean days of telework") +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_2 <- 
-  d %>% 
-  mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
-         position_category_description = fct_infreq(position_category_description)) %>%
-  ggplot(
-    aes(x = daily_status_teleworking, color = position_category_description, fill = position_category_description)
-  ) +
-  geom_density(alpha = .5) +
-  # geom_vline(data = prep_01, aes(xintercept = num, color = position_category_description)) +
-  geom_text(data=prep_02, aes(x=x, y=y, label=position_category_description), size = 3, hjust = "inward") +
-  xlab("Days of telework") +
-  ylab("Density") +
-  theme_light() +
-  theme(legend.position = "None")
-
-p_1|p_2
-```
-
-# Position Categories: How much onsite work?
-
-```{r include=FALSE}
-prep_d_01 <- 
-  d %>% 
-  group_by(position_category_description) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n))
-
-prep_v_01 <- 
-  prep_d_01 %>% 
-  slice(3) %>% 
-  pull(n)
-
-prep_01 <- 
-  d %>% 
-   mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
-         position_category_description = fct_infreq(position_category_description)) %>%
-  group_by(position_category_description) %>% 
-  summarise(num = mean(daily_status_reporting_to_job_site)) %>% 
-  ungroup()
-
-prep_02 <- 
-  d %>% 
-   mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
-         position_category_description = fct_infreq(position_category_description)) %>%
-  group_by(position_category_description) %>% 
-  summarise(y = max(density(daily_status_reporting_to_job_site)$y),
-            x = density(daily_status_reporting_to_job_site)$x[density(daily_status_reporting_to_job_site)$y == max(density(daily_status_reporting_to_job_site)$y)]
-  )
+p_2
 ```
@@
 ```{r}
-p_1 <- 
-  prep_01 %>% 
-  ggplot(
-    aes(x = position_category_description, y = num, fill = position_category_description)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Mean days of onsite work") +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_2 <- 
-  d %>% 
-  mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
-         position_category_description = fct_infreq(position_category_description)) %>%
-  ggplot(
-    aes(x = daily_status_reporting_to_job_site, color = position_category_description, fill = position_category_description)
-  ) +
-  geom_density(alpha = .5) +
-  # geom_vline(data = prep_01, aes(xintercept = num, color = position_category_description)) +
-  geom_text(data=prep_02, aes(x=x, y=y, label=position_category_description), size = 3, hjust = "inward") +
-  xlab("Days of onsite work") +
-  ylab("Density") +
-  theme_light() +
-  theme(legend.position = "None")
-
-p_1|p_2
-```
-
-# Rule-based groups: How much telework?
-
-```{r}
-prep_d_01 <-
-  d %>%
-  select(person_id, 
-         rule_based_primarily_teleworking_working,
-         rule_based_mostly_teleworking_working,
-         rule_based_mostly_reporting_to_job_site_working,
-         rule_based_primarily_reporting_to_job_site_working,
-         rule_based_all_remote,
-         rule_based_telework_onsite_minimum,
-         daily_status_teleworking) %>% 
-  pivot_longer(starts_with("rule_based_")) %>% 
-  filter(value == 1) %>% 
-  mutate(
-    name = str_remove(name, "rule_based_"),
-    name = str_remove(name, "_working"),
-    name = str_replace_all(name, "_", " "),
-    name = str_to_sentence(name),
-    name = fct_relevel(
-      name,
-      "Primarily teleworking",
-      "Mostly teleworking",
-      "Mostly reporting to job site",
-      "Primarily reporting to job site",
-      "All remote",
-      "Telework onsite minimum"
-    ),
-    name = fct_relabel(name, ~str_wrap(.,width = 20))
-  ) %>% 
-  arrange(name)
-
-prep_01 <- 
-  prep_d_01 %>% 
-  group_by(name) %>% 
-  summarise(num = mean(daily_status_teleworking)) %>% 
-  ungroup()
-
-prep_02 <- 
-  prep_d_01 %>% 
-  group_by(name) %>% 
-  summarise(y = max(density(daily_status_teleworking)$y),
-            x = density(daily_status_teleworking)$x[density(daily_status_teleworking)$y == max(density(daily_status_teleworking)$y)]
-  )
+file_name <- "abstract_2.png"
+fp <- file.path(params$google_drive_home,"04. Analysis", "output", "png",file_name)
 ```
@@
 ```{r}
-p_1 <- 
-  prep_01 %>% 
-  ggplot(
-    aes(x = name, y = num, fill = name)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Mean days of telework") +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_2 <- 
-  prep_d_01 %>% 
-  ggplot(
-    aes(x = daily_status_teleworking, color = name, fill = name)
-  ) +
-  geom_density(alpha = .5) +
-  # geom_vline(data = prep_01, aes(xintercept = num, color = name)) +
-  geom_text(data=prep_02, aes(x=x, y=y, label=name), size = 3, hjust = "inward") +
-  xlab("Days of telework") +
-  ylab("Density") +
-  theme_light() +
-  theme(legend.position = "None")
-
-p_1|p_2
+ggsave(filename = fp, plot = p_2, width = 6, height = 3, units = "in")
 ```
-
-# Rule-based groups: How much telework?
-
-```{r}
-prep_d_01 <-
-  d %>%
-  select(person_id, 
-         rule_based_primarily_teleworking_working,
-         rule_based_mostly_teleworking_working,
-         rule_based_mostly_reporting_to_job_site_working,
-         rule_based_primarily_reporting_to_job_site_working,
-         rule_based_all_remote,
-         rule_based_telework_onsite_minimum,
-         daily_status_reporting_to_job_site) %>% 
-  pivot_longer(starts_with("rule_based_")) %>% 
-  filter(value == 1) %>% 
-  mutate(
-    name = str_remove(name, "rule_based_"),
-    name = str_remove(name, "_working"),
-    name = str_replace_all(name, "_", " "),
-    name = str_to_sentence(name),
-    name = fct_relevel(
-      name,
-      "Primarily teleworking",
-      "Mostly teleworking",
-      "Mostly reporting to job site",
-      "Primarily reporting to job site",
-      "All remote",
-      "Telework onsite minimum"
-    ),
-    name = fct_relabel(name, ~str_wrap(.,width = 20))
-  ) %>% 
-  arrange(name)
-
-prep_01 <- 
-  prep_d_01 %>% 
-  group_by(name) %>% 
-  summarise(num = mean(daily_status_reporting_to_job_site)) %>% 
-  ungroup()
-
-prep_02 <- 
-  prep_d_01 %>% 
-  group_by(name) %>% 
-  summarise(y = max(density(daily_status_reporting_to_job_site)$y),
-            x = density(daily_status_reporting_to_job_site)$x[density(daily_status_reporting_to_job_site)$y == max(density(daily_status_reporting_to_job_site)$y)]
-  )
-```
-
-```{r}
-p_1 <- 
-  prep_01 %>% 
-  ggplot(
-    aes(x = name, y = num, fill = name)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Mean days of onsite work") +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_2 <- 
-  prep_d_01 %>% 
-  ggplot(
-    aes(x = daily_status_reporting_to_job_site, color = name, fill = name)
-  ) +
-  geom_density(alpha = .5) +
-  # geom_vline(data = prep_01, aes(xintercept = num, color = name)) +
-  geom_text(data=prep_02, aes(x=x, y=y, label=name), size = 3, hjust = "inward") +
-  xlab("Days of onsite work") +
-  ylab("Density") +
-  theme_light() +
-  theme(legend.position = "None")
-
-p_1|p_2
-```
-
-# Onsite Flexible: Rule-based groups
-
-```{r}
-prep_d_01 <- 
-  d %>%
-  filter(position_category_description == "Onsite Flexible") %>% 
-  summarise(across(
-    .cols = starts_with("rule_based"),
-    .fns = ~ sum(., rm.na = T)
-  )) %>%
-  select(-contains("_position_category_")) %>%
-  select(-ends_with("observation")) %>%
-  rownames_to_column() %>%
-  pivot_longer(-rowname) %>%
-  select(-rowname) %>%
-  mutate(
-    name = str_remove(name, "rule_based_"),
-    name = str_remove(name, "_working"),
-    name = str_replace_all(name, "_", " "),
-    name = str_to_sentence(name),
-    name = fct_relevel(
-      name,
-      "Primarily teleworking",
-      "Mostly teleworking",
-      "Mostly reporting to job site",
-      "Primarily reporting to job site",
-      "All remote",
-      "Telework onsite minimum"
-    ),
-    name = fct_relabel(name, ~str_wrap(.,width = 20))
-  ) %>% 
-  arrange(name)
-
-prep_d_02 <- 
-  prep_d_01 %>% 
-  mutate(tot = d %>% count() %>% pull(),
-         prop = value/tot,
-         text = scales::percent(prop, accuracy = .1))
-```
-
-```{r}
-p_1 <- 
-  prep_d_01 %>% 
-  ggplot(
-    aes(x = name, y = value, fill = name)
-  ) +
-  geom_col() +
-  geom_text(data = prep_d_02, aes(x = name, y = .5*value, label = text), color = "white") +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Employees") +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
-```
-
-# CONTINUE FROM HERE
-
-```{r}
-beepr::beep(sound = 5)
-```
-
-```{r}
-
-```

### 2023-09-06 04. Analysis/scripts/02_data_preparation_clusters_employee.R

@@ -14,7 +14,7 @@ library(purrr)
 author <-  "Ben Jaques-Leslie"
 project_number <-  2312
 project_name <-  "Occupancy Patterns"
-google_drive_home <-  "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
+google_drive_home <-  "G:/Shared drives/GSA Evaluation Division/Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
 data_folder_1 <-  "prepared-data"
 data_file_1 <-  "check_in_panel_2023-04-12.rdata"
 unique_identifier_1 <- c("date","person_id")

### 2023-09-06 04. Analysis/scripts/03-01-data-analysis-employee-cluster-identification.R

@@ -14,9 +14,9 @@ library(purrr)
 author <-  "Ben Jaques-Leslie"
 project_number <-  2312
 project_name <-  "Occupancy Patterns"
-google_drive_home <-  "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
+google_drive_home <-  "G:/Shared drives/GSA Evaluation Division/Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
 data_folder_1 <-  "prepared-data"
-data_file_1 <-  "prep_employees_2023-08-09.rdata"
+data_file_1 <-  "prep_employees_2023-09-06.rdata"
 unique_identifier_1 <- c("date","person_id")
 date_cohort_month <-  "2022-03-01"
 observation_window_length_months <-  6

### 2023-09-06 04. Analysis/scripts/03-02-data-analysis-employee-cluster-assessment.R

@@ -14,9 +14,9 @@ library(purrr)
 author <- "Ben Jaques-Leslie"
 project_number <- 2312
 project_name <- "Occupancy Patterns"
-google_drive_home <- "G:/Shared drives/MSG Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
+google_drive_home <-  "G:/Shared drives/GSA Evaluation Division/Projects/1.0 Real Estate Solutions (LQ1)/2312 Work Patterns"
 data_folder_1 <- "prepared-data"
-data_file_1 <- "prep_employees_2023-08-09.rdata"
+data_file_1 <- "prep_employees_2023-09-06.rdata"
 in_number_of_clusters_start <- 1
 in_number_of_clusters_end <- 20
 in_seed <- 27

### 2023-09-07 04. Analysis/scripts/04-03-reporting-slides.Rmd
Create 04-03-reporting-slides.Rmd
New markdown for reporting slides

--- 2023-09-06 04. Analysis/scripts/04-01-reporting-presentation.Rmd
@@
                             "Office visitors" = "2",
-                            "Hybrid workers" = "3",
-                            "In-office workers" = "4",
-                            "Disconnected workers" = "5"),
+                            "In-office workers" = "3",
+                            "Disconnected workers" = "4",
+                            "Hybrid workers" = "5"),
+    .cluster_5 = fct_relevel(.cluster_5,
+                            "Telecommuters",
+                            "Office visitors",
+                            "Hybrid workers",
+                            "In-office workers",
+                            "Disconnected workers"
+                            ),
     .cluster_5 = fct_relabel(.cluster_5, ~str_wrap(.x,width = 10))
@@
 ```
+
+# Clusters and position categories (alluvial)
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(position_category_description) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n))
+
+prep_v_01 <- 
+  prep_d_01 %>% 
+  slice(3) %>% 
+  pull(n)
+
+prep_d_02 <-
+  d %>%
+  mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
+         position_category_description = fct_infreq(position_category_description)) %>%
+  group_by(position_category_description,.cluster_5) %>%
+  count() %>%
+  ungroup() %>%
+  arrange(desc(n)) %>% 
+  rename(num = n) %>% 
+  mutate(
+    position_category_description = fct_relevel(position_category_description, 
+                                               "Offsite",
+                                               "Onsite Flexible",
+                                               "Onsite Required",
+                                               "Other")
+  )
+
+prep_d_03 <- 
+  prep_d_02 %>% 
+  filter(position_category_description != "Other")
+
+prep_d_04 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_05 <- 
+  prep_d_03 %>% 
+  full_join(prep_d_04) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  ) 
+```
+
+```{r}
+p_1 <- 
+  prep_d_05 %>% 
+   mutate(.cluster_5 = fct_relabel(.cluster_5,~str_wrap(.,width = 50))) %>% 
+  ggplot(aes(y = num, axis1 = position_category_description, axis2 = .cluster_5, fill = .cluster_5)) +
+  geom_alluvium(width = 1/12) +
+  geom_stratum(width = 1/12,
+               # alpha = 1,
+               fill = "black",
+               color = "white"
+               ) +
+  geom_label(stat = "stratum", aes(label = after_stat(stratum)),
+             fill = "white",
+             # , alpha = .05,
+              size = 4,
+             hjust = "inward"
+             ) +
+  labs(title = "Linking position categories to work pattern groups") +
+  ylab("Number of employees") +
+  scale_y_continuous(labels = scales::comma) +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_blank())
+```
+
+```{r}
+p_1
+```
+
+# CONTINUE FROM HERE
+
+```{r}
+beepr::beep(sound = 5)
+```
+
+```{r}
+
+```
+
+# Appendix
 
@@
 # Clusters and position categories (alluvial)
-
-```{r}
-is_alluvia_form(prep_d_05)
-```
 

### 2023-09-07 04. Analysis/scripts/04-02-abstract.Rmd
Update 04-02-abstract.Rmd
Adjusting for new observation window and data

@@
 
-```{r include=FALSE}
-d <- d %>% 
-  mutate(
-    .cluster_5 = fct_recode(.cluster_5,
-                            "Telecommuters" = "1",
-                            "Office visitors" = "2",
-                            "Hybrid workers" = "3",
-                            "Disconnected workers" = "4",
-                            "In-office workers" = "5"),
-    .cluster_5 = fct_relabel(.cluster_5, ~str_wrap(.x,width = 10))
-  )
-```
+# Summary
 
@@
   as.data.frame()
+```
+
+# CONTINUE FROM HERE
+
+```{r}
+beepr::beep(sound = 5)
+```
+
+```{r}
+
+```
+
+# Defining work pattern groups
+
+```{r}
+d <- d %>% 
+  mutate(
+    .cluster_5 = fct_recode(.cluster_5,
+                            "Telecommuters" = "1",
+                            "Office visitors" = "2",
+                            "In-office workers" = "3",
+                            "Disconnected workers" = "4",
+                            "Hybrid workers" = "5"),
+    .cluster_5 = fct_relevel(.cluster_5,
+                            "Telecommuters",
+                            "Office visitors",
+                            "Hybrid workers",
+                            "In-office workers",
+                            "Disconnected workers"
+                            ),
+    .cluster_5 = fct_relabel(.cluster_5, ~str_wrap(.x,width = 10))
+  )
 ```
@@
   rollbackward()
+date_cohort_month_start
+date_cohort_month_end
+date_observation_window_month_start
+date_observation_window_month_end
 ```
@@
 
-```{r}
-params$date_cohort_month %m+% months(params$observation_window_length_months)
-```
-
-Second, create a dataframe of all the days of the year.
+Filter to just the days in the observation window.
 
@@
 prep_b <- 
-  tibble(
-  date = seq.Date(from = ymd("2022-01-01"),
-         to = ymd("2022-12-31"),
-         by = "days")
-)
+  prep_a %>% 
+  filter(date >= date_cohort_month_start & date <= date_observation_window_month_end)
+
+prep_b
+```
+
+Count the number of pay periods.
+
+```{r}
+prep_val_01 <- prep_b %>% 
+  summarise(n_distinct(period_number)) %>% 
+  pull()
+
+prep_val_01
+```
+
+Calculate telework and onsite per pay period.
+
+```{r}
+d <- 
+  d %>% 
+  mutate(across(
+    .cols = c(daily_status_reporting_to_job_site,daily_status_teleworking),
+    .fns = ~./prep_val_01,
+    .names = "{col}_ppp"
+  ))
 ```
@@
 ```{r}
-prep_b %>% 
-  skim()
+d %>% 
+  skim(ends_with("_ppp"))
+```
+
+## Calculate averages
+
+```{r}
+d %>% 
+  group_by(.cluster_5) %>% 
+  skim(daily_status_reporting_to_job_site,
+       daily_status_reporting_to_job_site_observation_prop,
+       daily_status_reporting_to_job_site_working_prop,
+       daily_status_reporting_to_job_site_ppp,
+       daily_status_teleworking,
+       daily_status_teleworking_observation_prop,
+       daily_status_teleworking_working_prop,
+       daily_status_teleworking_ppp,
+       days_colocated_1,
+       days_colocated_1_observation_prop,
+       days_colocated_supervisor,
+       days_colocated_supervisor_observation_prop,
+       days_colocated_team,
+       days_colocated_team_observation_prop,
+       days_telework_team,
+       days_telework_team_observation_prop,
+       working_days,
+       team_size_mode)
+```
+
+# Calculating ranges
+
+```{r}
+d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(
+    across(
+      .cols = c(daily_status_reporting_to_job_site_ppp,
+                daily_status_reporting_to_job_site_working_prop,
+                daily_status_teleworking_ppp,
+                daily_status_teleworking_working_prop),
+      .fns = list(q_025 = ~quantile(.,probs = .025),
+                  q_975 = ~quantile(.,probs = .975))
+    )
+  ) %>% 
+  pivot_longer(-.cluster_5) %>% 
+  pivot_wider(values_from = value, names_from = .cluster_5)
+```
+
+# Regional difference.
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(location_state,.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(num = n)
+
+prep_d_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_03 <- 
+  prep_d_01 %>% 
+  full_join(prep_d_02) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  )# %>% 
+  # mutate(
+  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
+  # )
+
+prep_d_03
+```
+
+# Office differences
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(gsa_sso) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n))
+
+prep_v_01 <- 
+  prep_d_01 %>% 
+  slice(2) %>% 
+  pull(n)
+
+prep_d_02 <-
+  d %>%
+  mutate(gsa_sso = fct_lump_min(gsa_sso, min = prep_v_01),
+         gsa_sso = fct_infreq(gsa_sso)) %>%
+  group_by(gsa_sso,.cluster_5) %>%
+  count() %>%
+  ungroup() %>%
+  arrange(desc(n)) %>% 
+  rename(num = n) %>% 
+  mutate(gsa_sso = fct_relevel(gsa_sso,
+                               "PBS",
+                               "FAS",
+                               "OCFO",
+                               "Other"))
+
+prep_d_03 <- 
+  prep_d_02 %>% 
+  filter(gsa_sso != "Other")
+
+prep_d_04 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_05 <- 
+  prep_d_03 %>% 
+  full_join(prep_d_04) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  )
+
+prep_d_05 %>% view()
 ```
@@
 ```
+# Clusters: How much telework?
+
+```{r include=FALSE}
+prep_01 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(num = mean(daily_status_teleworking)) %>% 
+  ungroup()
+
+prep_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(y = max(density(daily_status_teleworking)$y),
+            x = density(daily_status_teleworking)$x[density(daily_status_teleworking)$y == max(density(daily_status_teleworking)$y)]
+  )
+```
+
+```{r}
+p_1 <- 
+  prep_01 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = num, fill = .cluster_5)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::comma) +
+  ylab("Mean days of telework") +
+  theme_light() +
+  oescolorrrs::scale_fill_oes() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_2 <- 
+  d %>% 
+  ggplot(
+    aes(x = daily_status_teleworking, color = .cluster_5, fill = .cluster_5)
+  ) +
+  geom_density(alpha = .5) +
+  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
+  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
+  xlab("Days of telework") +
+  ylab("Density") +
+  theme_light() +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme(legend.position = "None")
+
+p_1|p_2
+```
+
+# Clusters: How much telework? (proportion of working)
+
+```{r include=FALSE}
+prep_01 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(num = mean(daily_status_teleworking_working_prop)) %>% 
+  ungroup()
+
+prep_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(y = max(density(daily_status_teleworking_working_prop)$y),
+            x = density(daily_status_teleworking_working_prop)$x[density(daily_status_teleworking_working_prop)$y == max(density(daily_status_teleworking_working_prop)$y)]
+  )
+```
+
+```{r}
+p_1 <- 
+  prep_01 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = num, fill = .cluster_5)
+  ) +
+  geom_col() +
+  scale_y_continuous(labels = scales::comma) +
+  ylab("Mean days of telework") +
+  theme_light() +
+  oescolorrrs::scale_fill_oes() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_2 <- 
+  d %>% 
+  ggplot(
+    aes(x = daily_status_teleworking_working_prop, color = .cluster_5, fill = .cluster_5)
+  ) +
+  geom_density(alpha = .5) +
+  # geom_vline(data = prep_01, aes(xintercept = num, color = .cluster_5)) +
+  geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
+  xlab("Days of telework") +
+  ylab("Density") +
+  theme_light() +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme(legend.position = "None")
+
+p_1|p_2
+```

### 2023-09-11 04. Analysis/scripts/04-02-abstract.Rmd
Update 04-02-abstract.Rmd
Adding per month metrics and adjusting title placement and size in alluvial chart

@@
 
-# CONTINUE FROM HERE
-
-```{r}
-beepr::beep(sound = 5)
-```
-
-```{r}
-
-```
-
 # Defining work pattern groups
@@
     .cols = c(daily_status_reporting_to_job_site,daily_status_teleworking),
-    .fns = ~./prep_val_01,
-    .names = "{col}_ppp"
+    .fns = list(ppp = ~./prep_val_01,pm = ~./params$observation_window_length_months),
+    .names = "{col}_{fn}"
   ))
@@
 d %>% 
-  skim(ends_with("_ppp"))
+  skim(ends_with("_ppp"),ends_with("_pm"))
 ```
@@
        daily_status_reporting_to_job_site_ppp,
+       daily_status_reporting_to_job_site_pm,
        daily_status_teleworking,
@@
        daily_status_teleworking_ppp,
+       daily_status_teleworking_pm,
        days_colocated_1,
@@
       .cols = c(daily_status_reporting_to_job_site_ppp,
+                daily_status_reporting_to_job_site_pm,
                 daily_status_reporting_to_job_site_working_prop,
                 daily_status_teleworking_ppp,
+                daily_status_teleworking_pm,
                 daily_status_teleworking_working_prop),
@@
     legend.position = "None",
+    plot.title = element_text(hjust = 0.5,
+                              size = 13),
     axis.title.y = element_text(size = 8),
@@
 ```
+
 # Clusters: How much telework?
@@
 ```
+
+# Difference in colocation
+
+```{r}
+d %>% 
+  group_by(.cluster_5) %>% 
+  skim(team_size_mode,starts_with("days_colocated"), starts_with("days_telework"))
+```
+
+# CONTINUE FROM HERE
+
+```{r}
+beepr::beep(sound = 5)
+```
+
+```{r}
+
+```

### 2023-09-25 04. Analysis/scripts/04-02-abstract.Rmd
Update 04-02-abstract.Rmd
Adding some statistics for leave

@@
 
+## Percent of GSA employees by office
+
+```{r}
+prep_d_01 <- 
+  d %>%
+  group_by(gsa_sso) %>% 
+  count() %>% 
+  ungroup()
+
+prep_d_02 <- 
+  prep_d_01 %>% 
+  mutate(tot = d %>% count() %>% pull(),
+         prop = n/tot,
+         text = scales::percent(prop, accuracy = .1))
+
+prep_d_02
+```
+
 ## Days per pay period
@@
   mutate(across(
-    .cols = c(daily_status_reporting_to_job_site,daily_status_teleworking),
+    .cols = c(daily_status_reporting_to_job_site,daily_status_teleworking, daily_status_leave),
     .fns = list(ppp = ~./prep_val_01,pm = ~./params$observation_window_length_months),
@@
        daily_status_teleworking_pm,
+       daily_status_leave,
+       daily_status_leave_pm,
+       daily_status_leave_ppp,
        days_colocated_1,
@@
 
+# Work and leave ppp
+
+```{r}
+prep_d_06 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(
+    across(
+      .cols = ends_with("_ppp"),
+      .fns = mean
+    )
+  ) %>% 
+  pivot_longer(cols = -.cluster_5) %>% 
+  mutate(
+    name = str_remove(name,"daily_status_"),
+    name = str_remove(name,"_ppp"),
+    name = str_replace_all(name,"_", " "),
+    name = str_to_sentence(name),
+    name = str_wrap(name, width = 15)
+  )
+
+prep_d_06
+```
+
+```{r}
+p_3 <- 
+  prep_d_06 %>% 
+  ggplot(aes(x = .cluster_5, y = value, fill = name)) +
+  geom_bar(stat = "identity") +
+  labs(title = "Work and leave per pay period") +
+  ylab("Days per pay period") +
+  scale_y_continuous(labels = scales::comma) +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
+  theme(
+    legend.position = "right",
+    legend.title = element_blank(),
+    plot.title = element_text(hjust = 0.5,
+                              size = 13),
+    axis.title.y = element_text(size = 8),
+    axis.title.x = element_blank()
+    )
+
+p_3
+```
+
+```{r}
+file_name <- "abstract_3.png"
+fp <- file.path(params$google_drive_home,"04. Analysis", "output", "png",file_name)
+```
+
+```{r}
+ggsave(filename = fp, plot = p_3, width = 6, height = 3, units = "in")
+```
+
 # CONTINUE FROM HERE

### 2023-09-27 04. Analysis/scripts/04-04-reporting-summary-slides.Rmd
Create 04-04-reporting-summary-slides.Rmd

--- 2023-09-06 04. Analysis/scripts/04-01-reporting-presentation.Rmd
@@
 ---
-title: "slides for lab"
+title: "GSA Work Patterns"
 author: "Ben Jaques-Leslie"
@@
 
-# What is the GSA priority?
-
--   Telework has become very common
-
--   Much of GSA staff telework
-
--   How employees use telework is not clear
-
--   Defining and describing different work patterns may help to understand organizational health
-
--   By understanding how staff work (remote, hybrid, or onsite), different strategies may be developed to improve productivity and staff engagement
-
-# How did the evaluation work?
-
--   Data:
-
-    -   GSA check-in data, GSA staff roster
-
-    -   March - September 2023
-
--   All GSA staff
-
-    -   Categorized work patterns by remote or onsite
-
-    -   Rules: Mostly remote or onsite, staff category (flexible, onsite, etc), flexible onsite
-
-    -   Clusters: K-means clusters defined using frequency of work location status, collocation with team members, and team remote work
-
-# Position categories
+```{r}
+date_cohort_month_start <- ymd(params$date_cohort_month)
+date_cohort_month_end <- ceiling_date(date_cohort_month_start,unit = "month") %>% rollbackward()
+date_observation_window_month_start <- date_cohort_month_start %m+% months(params$observation_window_length_months)
+date_observation_window_month_end <- 
+  # ceiling_date(date_observation_window_month_start,unit = "month") %>% 
+  date_observation_window_month_start %>% 
+  rollbackward()
+```
+
+```{r}
+prep_a <- 
+  tibble(
+  date = seq.Date(from = ymd("2022-01-01"),
+         to = ymd("2022-12-31"),
+         by = "2 weeks")
+) %>% 
+  rownames_to_column(var = "period_number") 
+```
+
+```{r}
+prep_b <- 
+  prep_a %>% 
+  filter(date >= date_cohort_month_start & date <= date_observation_window_month_end)
+
+```
+
+```{r}
+prep_val_01 <- prep_b %>% 
+  summarise(n_distinct(period_number)) %>% 
+  pull()
+
+```
+
+```{r}
+d <- 
+  d %>% 
+  mutate(across(
+    .cols = c(daily_status_reporting_to_job_site,daily_status_teleworking, daily_status_leave),
+    .fns = list(ppp = ~./prep_val_01,pm = ~./params$observation_window_length_months),
+    .names = "{col}_{fn}"
+  ))
+```
+
+# GSA Work Patterns
+
+**What is the GSA priority?**
+
+Hybrid work has become widespread over the past three years, however, little is known about GSA employee work patterns.
+
+This information can be used to develop and tailor technologies, spaces, and strategies to support hybrid and distributed models of work so that employees are engaged, perform at their best, and remain focused on mission delivery.
+
+# GSA Work Patterns
+
+**What is the GSA priority?**
+
+Existing administrative data offers an opportunity to better understand how and where employees work and make progress in addressing GSA's Learning Agenda priority question:
+
+*What technologies and solutions does the federal workforce need to improve effectiveness in a more responsive remote work setting?*
+
+# GSA Work Patterns
+
+**What did we evaluate?**
+
+This **descriptive study** characterizes the different ways GSA employees work remotely or from the office by investigating frequencies of onsite work and telework.
+
+The **purpose of the study** is to describe these groups in greater detail with recent data to inform strategic decision-making.
+
+# GSA Work Patterns
+
+**How did the evaluation work?**
+
+-   GSA employees are asked daily to report their work status
+
+    -   Telework, reporting to job site, on leave, etc.
+
+-   We combined these daily check-in data with other information about employees
+
+    -   Position categories (onsite required, onsite flexible, offsite), supervisors, staff offices, and other information from the GSA roster.
+
+# GSA Work Patterns
+
+**How did the evaluation work?**
+
+1.  **Data**: March-September 2023
+
+2.  **Preparation**: Calculate:
+
+    1.  Frequencies of work status for the 11,251 GSA employees who worked in March 2023
+
+    2.  Number of days the entire team teleworks or works onsite
+
+3.  **Grouping**: Based on similarities in their frequencies of working remote or onsite
+
+# GSA Work Patterns
+
+**What did we learn?**
+
+GSA employees can be clustered into five work pattern groups:
+
+-   **Telecommuters**: Work more days and almost all telework
+
+-   **Office visitors**: Primarily telework, occasionally onsite, works 10 fewer days than teleworkers
+
+-   **Hybrid workers**: Mostly telework, periodically onsite
+
+-   **In-office workers**: Sometimes work remote, primarily onsite
+
+-   **Disconnected workers**: Work fewer days, likely to exit employment
+
+# GSA Work Patterns
+
+```{r}
+prep_d_01 <- 
+  d %>%
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup()
+
+prep_d_02 <- 
+  prep_d_01 %>% 
+  mutate(tot = d %>% count() %>% pull(),
+         prop = n/tot,
+         text = scales::percent(prop, accuracy = .1))
+```
+
+```{r}
+p_1 <- 
+  prep_d_01 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = n, fill = .cluster_5)
+  ) +
+  geom_col() +
+  geom_text(data = prep_d_02, aes(x = .cluster_5, y = .5*n, label = text), color = "white") +
+  scale_y_continuous(labels = scales::comma) +
+  ylab("Employees") +
+  labs(
+    title = "GSA Employees in work pattern groups"
+  ) +
+  theme_light() +
+  oescolorrrs::scale_fill_oes() +
+  theme(
+    legend.position = "None",
+    plot.title = element_text(hjust = 0.5,
+                              size = 13),
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 8))
+
+p_1
+```
+
+# GSA Work Patterns
+
+```{r}
+prep_d_06 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  summarise(
+    across(
+      .cols = ends_with("_ppp"),
+      .fns = mean
+    )
+  ) %>% 
+  pivot_longer(cols = -.cluster_5) %>% 
+  mutate(
+    name = str_remove(name,"daily_status_"),
+    name = str_remove(name,"_ppp"),
+    name = str_replace_all(name,"_", " "),
+    name = str_to_sentence(name),
+    name = str_wrap(name, width = 15)
+  )
+```
+
+```{r}
+p_3 <- 
+  prep_d_06 %>% 
+  ggplot(aes(x = .cluster_5, y = value, fill = name)) +
+  geom_bar(stat = "identity") +
+  labs(title = "Work and leave per pay period") +
+  ylab("Days per pay period") +
+  scale_y_continuous(labels = scales::comma) +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
+  theme(
+    legend.position = "right",
+    legend.title = element_blank(),
+    plot.title = element_text(hjust = 0.5,
+                              size = 13),
+    axis.title.y = element_text(size = 8),
+    axis.title.x = element_blank()
+    )
+
+p_3
+```
+
+# GSA Work Patterns
+
+**What do we recommend?**
+
+-   Areas of exploration
+
+    -    Why some Offsite classified employees occasionally work in the office?
+
+    -   What drives workers to come in on particular days?
+
+    -   Do work pattern groups have differing levels of employee satisfaction or engagement? Advancement and tenure?
+
+-   Design and target specific interventions for improving organizational health using these work pattern groups
+
+# Appendix
+
+# GSA Work Patterns
+
+```{r}
+prep_01 <-
+  d %>%
+  group_by(.cluster_5) %>%
+  summarise(
+    num = mean(daily_status_reporting_to_job_site_working_prop),
+    l = quantile(daily_status_reporting_to_job_site_working_prop, probs = .25),
+    u = quantile(daily_status_reporting_to_job_site_working_prop, probs = .75)
+  ) %>%
+  ungroup()
+```
+
+```{r}
+# d %>%
+  ggplot(
+  ) +
+  geom_jitter(data = d,
+    aes(
+      x = .cluster_5,
+      y = daily_status_reporting_to_job_site_working_prop,
+      fill = .cluster_5,
+      color = .cluster_5
+    ),
+    position = position_jitter(0.3), color = "darkgray") +
+  geom_pointrange(
+    aes(
+      x = .cluster_5,
+      fill = .cluster_5,
+      color = .cluster_5,
+      y = num,
+      ymin = l,
+      ymax = u
+    ),
+    data = prep_01
+  ) +
+  labs(title = "Percent of days reporting to job site") +
+  ylab("Percent of working days") +
+  scale_y_continuous(labels = scales::percent) +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
+  theme(
+    legend.position = "none",
+    legend.title = element_blank(),
+    plot.title = element_text(hjust = 0.5,
+                              size = 13),
+    axis.title.y = element_text(size = 8),
+    axis.title.x = element_blank()
+    )
+
+```
+
+# GSA Work Patterns
+
+```{r}
+prep_01 <-
+  d %>%
+  group_by(.cluster_5) %>%
+  summarise(
+    num = mean(daily_status_teleworking_working_prop),
+    l = quantile(daily_status_teleworking_working_prop, probs = .25),
+    u = quantile(daily_status_teleworking_working_prop, probs = .75)
+  ) %>%
+  ungroup()
+```
+
+```{r}
+# d %>%
+  ggplot(
+  ) +
+  geom_jitter(data = d,
+    aes(
+      x = .cluster_5,
+      y = daily_status_teleworking_working_prop,
+      fill = .cluster_5,
+      color = .cluster_5
+    ),
+    position = position_jitter(0.3), color = "darkgray") +
+  geom_pointrange(
+    aes(
+      x = .cluster_5,
+      fill = .cluster_5,
+      color = .cluster_5,
+      y = num,
+      ymin = l,
+      ymax = u
+    ),
+    data = prep_01
+  ) +
+  labs(title = "Percent of days teleworking") +
+  ylab("Percent of working days") +
+  scale_y_continuous(labels = scales::percent) +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
+  theme(
+    legend.position = "none",
+    legend.title = element_blank(),
+    plot.title = element_text(hjust = 0.5,
+                              size = 13),
+    axis.title.y = element_text(size = 8),
+    axis.title.x = element_blank()
+    )
+
+```
+
+# GSA Work Patterns
+
+```{r}
+prep_01 <-
+  d %>%
+  group_by(.cluster_5) %>%
+  summarise(
+    num = mean(daily_status_leave),
+    l = quantile(daily_status_leave, probs = .25),
+    u = quantile(daily_status_leave, probs = .75)
+  ) %>%
+  ungroup()
+```
+
+```{r}
+# d %>%
+  ggplot(
+  ) +
+  geom_jitter(data = d,
+    aes(
+      x = .cluster_5,
+      y = daily_status_leave,
+      fill = .cluster_5,
+      color = .cluster_5
+    ),
+    position = position_jitter(0.3), color = "darkgray") +
+  geom_pointrange(
+    aes(
+      x = .cluster_5,
+      fill = .cluster_5,
+      color = .cluster_5,
+      y = num,
+      ymin = l,
+      ymax = u
+    ),
+    data = prep_01
+  ) +
+  labs(title = "Number of days on leave") +
+  ylab("Number of days") +
+  scale_y_continuous(labels = scales::comma) +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
+  theme(
+    legend.position = "none",
+    legend.title = element_blank(),
+    plot.title = element_text(hjust = 0.5,
+                              size = 13),
+    axis.title.y = element_text(size = 8),
+    axis.title.x = element_blank()
+    )
+
+```
+
+# GSA Work Patterns
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(location_state,.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(num = n)
+
+prep_d_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_03 <- 
+  prep_d_01 %>% 
+  full_join(prep_d_02) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  )# %>% 
+  # mutate(
+  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
+  # )
+
+prep_d_04 <- 
+  prep_d_03 %>% 
+  filter(location_state %in% c("MD","PA","VA")
+           )
+```
+
+```{r}
+geom_region <- function(in_data)
+{
+  out <- 
+  in_data %>% 
+  ggplot(
+    aes(x = .cluster_5, y = n, fill = .cluster_5)
+  ) +
+  geom_col() +
+  facet_wrap(facets = vars(location_state), nrow = 1) +
+  labs(title = "Percent of working pattern group by state") +
+  ylab("Percent of working pattern group") +
+  scale_y_continuous(labels = scales::percent) +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
+  theme(
+    legend.position = "none",
+    legend.title = element_blank(),
+    plot.title = element_text(hjust = 0.5,
+                              size = 13),
+    axis.title.y = element_text(size = 8),
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 6)
+    )
+
+return(out)
+}
+
+```
+
+```{r}
+p_1 <- 
+  prep_d_04 %>% 
+  geom_region()
+
+p_1
+```
+
+# GSA Work Patterns
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(location_state,.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(num = n)
+
+prep_d_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_03 <- 
+  prep_d_01 %>% 
+  full_join(prep_d_02) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  )# %>% 
+  # mutate(
+  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
+  # )
+
+prep_d_04 <- 
+  prep_d_03 %>% 
+  filter(location_state %in% c("CA", "IL")
+           )
+```
+
+```{r}
+p_1 <- 
+  prep_d_04 %>% 
+  geom_region()
+
+p_1
+```
+
+# GSA Work Patterns
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(location_state,.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(num = n)
+
+prep_d_02 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_03 <- 
+  prep_d_01 %>% 
+  full_join(prep_d_02) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  )# %>% 
+  # mutate(
+  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
+  # )
+
+prep_d_04 <- 
+  prep_d_03 %>% 
+  filter(location_state %in% c("DC")
+           )
+```
+
+```{r}
+p_1 <- 
+  prep_d_04 %>% 
+  geom_region()
+
+p_1
+```
+
+# GSA Work Patterns
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(gsa_sso) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n))
+
+prep_v_01 <- 
+  prep_d_01 %>% 
+  slice(2) %>% 
+  pull(n)
+
+prep_d_02 <-
+  d %>%
+  mutate(gsa_sso = fct_lump_min(gsa_sso, min = prep_v_01),
+         gsa_sso = fct_infreq(gsa_sso)) %>%
+  group_by(gsa_sso,.cluster_5) %>%
+  count() %>%
+  ungroup() %>%
+  arrange(desc(n)) %>% 
+  rename(num = n) %>% 
+  mutate(gsa_sso = fct_relevel(gsa_sso,
+                               "PBS",
+                               "FAS",
+                               "OCFO",
+                               "Other"))
+
+prep_d_03 <- 
+  prep_d_02 #%>% 
+  # filter(gsa_sso != "Other")
+
+prep_d_04 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_05 <- 
+  prep_d_03 %>% 
+  full_join(prep_d_04) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  ) 
+```
+
+```{r}
+p_1 <- 
+  prep_d_05 %>% 
+  ggplot(
+    aes(x = .cluster_5, y = n, fill = .cluster_5)
+  ) +
+  geom_col() +
+  facet_wrap(facets = vars(gsa_sso), nrow = 1) +
+  labs(title = "Percent of working pattern group by office") +
+  ylab("Percent of working pattern group") +
+  scale_y_continuous(labels = scales::percent) +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
+  theme(
+    legend.position = "none",
+    legend.title = element_blank(),
+    plot.title = element_text(hjust = 0.5,
+                              size = 13),
+    axis.title.y = element_text(size = 8),
+    axis.title.x = element_blank()
+    )
+
+p_1
+```
+
+# GSA Work Patterns
 
@@
          position_category_description = fct_infreq(position_category_description)) %>%
+  group_by(position_category_description,.cluster_5) %>%
+  count() %>%
+  ungroup() %>%
+  arrange(desc(n)) %>% 
+  rename(num = n) %>% 
+  mutate(
+    position_category_description = fct_relevel(position_category_description, 
+                                               "Offsite",
+                                               "Onsite Flexible",
+                                               "Onsite Required",
+                                               "Other")
+  )
+
+prep_d_03 <- 
+  prep_d_02 %>% 
+  filter(position_category_description != "Other")
+
+prep_d_04 <- 
+  d %>% 
+  group_by(.cluster_5) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n)) %>% 
+  rename(tot = n)
+
+prep_d_05 <- 
+  prep_d_03 %>% 
+  full_join(prep_d_04) %>% 
+  mutate(
+    n = num/tot,
+    text = scales::comma(num)
+  ) 
+```
+
+```{r}
+p_1 <- 
+  prep_d_05 %>% 
+   mutate(.cluster_5 = fct_relabel(.cluster_5,~str_wrap(.,width = 50))) %>% 
+  ggplot(aes(y = num, axis1 = position_category_description, axis2 = .cluster_5, fill = .cluster_5)) +
+  geom_alluvium(width = 1/12) +
+  geom_stratum(width = 1/12,
+               # alpha = 1,
+               fill = "black",
+               color = "white"
+               ) +
+  geom_label(stat = "stratum", aes(label = after_stat(stratum)),
+             fill = "white",
+             # , alpha = .05,
+              size = 4,
+             hjust = "inward"
+             ) +
+  labs(title = "Linking position categories to work pattern groups") +
+  ylab("Number of employees") +
+  scale_y_continuous(labels = scales::comma) +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
+  theme(
+    legend.position = "None",
+    axis.title.x = element_blank(),
+    axis.text.x = element_blank(),
+    plot.title = element_text(hjust = 0.5,
+                              size = 10))
+```
+
+```{r}
+p_1
+```
+
+# GSA Work Patterns
+
+```{r}
+prep_d_01 <- 
+  d %>% 
+  group_by(position_category_description) %>% 
+  count() %>% 
+  ungroup() %>% 
+  arrange(desc(n))
+
+prep_v_01 <- 
+  prep_d_01 %>% 
+  slice(3) %>% 
+  pull(n)
+
+prep_d_02 <-
+  d %>%
+  mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
+         position_category_description = fct_infreq(position_category_description)) %>%
   group_by(position_category_description) %>%
@@
   geom_col() +
+  labs(title = "Number of employees by position category") +
+  ylab("Number of employees") +
   scale_y_continuous(labels = scales::comma) +
-  ylab("Employees") +
-  theme_light() +
-  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
   theme(
@@
     axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
+    # axis.text.x = element_blank(),
+    plot.title = element_text(hjust = 0.5,
+                              size = 10))
 
@@
 
-# Rule-based groups
+# GSA Work Patterns
 
@@
   geom_text(data = prep_d_02, aes(x = name, y = .5*value, label = text), color = "white") +
+  labs(title = "Number and percent of employees by rule-based group") +
+  ylab("Number of employees") +
   scale_y_continuous(labels = scales::comma) +
-  ylab("Employees") +
-  theme_light() +
-  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
   theme(
@@
     axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
+    axis.text.x = element_text(size = 8),
+    plot.title = element_text(hjust = 0.5,
+                              size = 10))
 
@@
 
-# Clusters
-
-1.  Telecommuters
-
-2.  Office visitors
-
-3.  Hybrid workers
-
-4.  Onsite workers
-
-5.  Disconnected workers
-
-# Clusters
-
-```{r}
-prep_d_01 <- 
-  d %>%
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup()
-
-prep_d_02 <- 
-  prep_d_01 %>% 
-  mutate(tot = d %>% count() %>% pull(),
-         prop = n/tot,
-         text = scales::percent(prop, accuracy = .1))
-```
-
-```{r}
-p_1 <- 
-  prep_d_01 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = n, fill = .cluster_5)
-  ) +
-  geom_col() +
-  geom_text(data = prep_d_02, aes(x = .cluster_5, y = .5*n, label = text), color = "white") +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Employees") +
-  theme_light() +
-  oescolorrrs::scale_fill_oes() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
-```
-
-# Clusters: How much telework?
+# GSA Work Patterns
 
@@
   scale_y_continuous(labels = scales::comma) +
-  ylab("Mean days of telework") +
+  ylab("Average days of telework") +
   theme_light() +
@@
 
-p_1|p_2
-```
-
-# Clusters: How much telework? (proportion of working)
+(p_1|p_2) +
+  plot_annotation(
+    title = "Average days of telework and distribution by work pattern group",
+    theme = theme(plot.title = element_text(hjust = 0.5,
+                              size = 10))
+  )
+```
+
+# GSA Work Patterns
 
@@
   geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Mean days of telework") +
+  scale_y_continuous(labels = scales::percent) +
+  ylab("Percent of working days teleworking") +
   theme_light() +
@@
 
-p_1|p_2
-```
-
-# Clusters: How much telework? (proportion of working) (rain)
-
-```{r}
-d %>% 
-  ggplot(
-    aes(x = 1, y = daily_status_teleworking_working_prop, fill = .cluster_5)
-  ) +
- geom_rain(alpha = .5,
-           rain.side = "r") +
-  coord_flip()
-```
-
-# Clusters: How much telework? (proportion of working) (rain)
-
-```{r}
-prep_01 <-
-  d %>%
-  group_by(.cluster_5) %>%
-  summarise(
-    num = mean(daily_status_teleworking_working_prop),
-    l = quantile(daily_status_teleworking_working_prop, probs = .25),
-    u = quantile(daily_status_teleworking_working_prop, probs = .75)
-  ) %>%
-  ungroup()
-
-# d %>%
-  ggplot(
-  ) +
-  geom_jitter(data = d,
-    aes(
-      x = .cluster_5,
-      y = daily_status_teleworking_working_prop,
-      fill = .cluster_5,
-      color = .cluster_5
-    ),
-    position = position_jitter(0.2), color = "darkgray") +
-  geom_pointrange(
-    aes(
-      x = .cluster_5,
-      fill = .cluster_5,
-      color = .cluster_5,
-      y = num,
-      ymin = l,
-      ymax = u
-    ),
-    data = prep_01
-  )
-
-# Combine with violin plots
-# d %>% 
-#   ggplot(df, aes(dose, len)) +
-#   geom_violin(color = "darkgray", trim = FALSE) + 
-#   geom_pointrange(aes(ymin = len-sd, ymax = len+sd), data = df.summary)
-```
-
-# Clusters: How much onsite work?
+(p_1|p_2) +
+  plot_annotation(
+    title = "Average telework percent and distribution by work pattern group",
+    theme = theme(plot.title = element_text(hjust = 0.5,
+                              size = 10))
+  )
+```
+
+# GSA Work Patterns
 
@@
   scale_y_continuous(labels = scales::comma) +
-  ylab("Mean days of onsite work") +
+  ylab("Average days of onsite work") +
   theme_light() +
@@
 
-p_1|p_2
-```
-
-# Clusters: Telework and onsite
+(p_1|p_2) +
+  plot_annotation(
+    title = "Average days working onsite and distribution by work pattern group",
+    theme = theme(plot.title = element_text(hjust = 0.5,
+                              size = 10))
+  )
+```
+
+# GSA Work Patterns
 
@@
     # nudge_x           = 100,
-    xlim = c(125),
+    xlim = c(90),
     ylim = c(50,150),
@@
   ylab("Days teleworking") +
+  labs(title = "Days teleworking and working onsite by work pattern group") +
   theme_light() +
@@
   oescolorrrs::scale_color_oes() +
-  theme(legend.position = "None")
+   theme_light() +
+  theme(
+    legend.position = "None",
+    # axis.title.x = element_blank(),
+    # axis.text.x = element_text(size = 8),
+    plot.title = element_text(hjust = 0.5,
+                              size = 10))
 ```
@@
 
-```{r}
-p_2 <- 
-  prep_gg_1 +
-  geom_jitter(# aes(size = working_days),
-    alpha = .5,
-    size = .5) +
-  stat_ellipse(
-    geom = "polygon",
-    alpha = .15,
-    size = .5,
-    level = .99
-  ) +
-  geom_text_repel(
-    data = prep_01,
-    aes(x = daily_status_reporting_to_job_site, y = daily_status_teleworking, 
-        label = .cluster_5,
-        fill = .cluster_5),
-    # fill = "white",
-    # alpha = .15,
-    size = 3,
-    force             = 0.5,
-    # nudge_x           = 100,
-    xlim = c(100, 150),
-    ylim = c(75,150),
-    direction         = "y",
-    hjust             = 0,
-    segment.size      = 0.2,
-    segment.curvature = -0.1,
-    color = "black"
-  ) +
-  xlab("Days reporting to the site") +
-  ylab("Days teleworking") +
-  theme_light() +
-  oescolorrrs::scale_fill_oes() +
-  oescolorrrs::scale_color_oes() +
-  theme(legend.position = "None",
-        axis.title = element_text(size = 8))
-```
-
-```{r}
-p_2
-```
-
-```{r}
-file_name <- "abstract_1.png"
-fp <- file.path(params$google_drive_home,"04. Analysis", "output", "png",file_name)
-```
-
-```{r}
-ggsave(filename = fp, plot = p_2, width = 3, height = 3, units = "in")
-```
-
-# Disconnected workers: Working days
+# GSA Work Patterns
 
@@
   scale_y_continuous(labels = scales::comma) +
-  ylab("Mean working days") +
-  theme_light() +
+  ylab("Average working days") +
+  theme_light() +
+  oescolorrrs::scale_fill_oes() +
   theme(
@@
   ggplot(
-    aes(x = working_days, color = .cluster_5, fill = .cluster_5)
+    aes(x = daily_status_reporting_to_job_site, color = .cluster_5, fill = .cluster_5)
   ) +
@@
   geom_text(data=prep_02, aes(x=x, y=y, label=.cluster_5), size = 3, hjust = "inward") +
-  xlab("Working days") +
+  xlab("Days of onsite work") +
   ylab("Density") +
   theme_light() +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
   theme(legend.position = "None")
 
-p_1|p_2
-```
-
-# Disconnected workers: Exiting employment
+(p_1|p_2) +
+  plot_annotation(
+    title = "Average working days and distribution by work pattern group",
+    theme = theme(plot.title = element_text(hjust = 0.5,
+                              size = 10))
+  )
+```
+
+# GSA Work Patterns
 
@@
   geom_col() +
-  ylab("Percent exiting employment") +
   scale_y_continuous(labels = scales::percent) +
+ xlab("Percent exiting employment") +
+  ylab("Days teleworking") +
+  labs(title = "Percent exiting employment by work pattern group") +
+  theme_light() +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
    theme_light() +
@@
     axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8)
-  )
+    # axis.text.x = element_text(size = 8),
+    plot.title = element_text(hjust = 0.5,
+                              size = 10))
 
@@
 
-# Clusters and position categories
+# GSA Work Patterns
 
@@
   facet_wrap(facets = vars(position_category_description), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
-```
-
-# Clusters and position categories (alluvial)
-
-```{r}
-is_alluvia_form(prep_d_05)
-```
-
-```{r}
-p_1 <- 
-  prep_d_05 %>% 
-  mutate(.cluster_5 = fct_relabel(.cluster_5,~str_wrap(.,width = 50))) %>% 
-  ggplot(aes(y = num, axis1 = .cluster_5, axis2 = position_category_description, fill = .cluster_5)) +
-  geom_alluvium(width = 1/12) +
-  geom_stratum(width = 1/12,
-               # alpha = 1,
-               fill = "black",
-               color = "white"
-               ) +
-  geom_label(stat = "stratum", aes(label = after_stat(stratum)),
-             fill = "white",
-             # , alpha = .05,
-             hjust = "inward"
-             ) +
-  ylab("Number of employees") +
-  scale_y_continuous(labels = scales::comma) +
+  labs(title = "Percent of working pattern group by position category") +
+  ylab("Percent of working pattern group") +
+  scale_y_continuous(labels = scales::percent) +
   oescolorrrs::scale_fill_oes() +
@@
   theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_blank())
-```
-
-```{r}
-p_1
-```
-
-```{r}
-p_2 <- 
-  prep_d_05 %>% 
-  mutate(.cluster_5 = fct_relabel(.cluster_5,~str_wrap(.,width = 50))) %>% 
-  ggplot(aes(y = num, axis1 = .cluster_5, axis2 = position_category_description, fill = .cluster_5)) +
-  geom_alluvium(width = 1/12) +
-  geom_stratum(width = 1/12,
-               # alpha = 1,
-               fill = "black",
-               color = "white"
-               ) +
-  geom_label(stat = "stratum", aes(label = after_stat(stratum)),
-             fill = "white",
-             # , alpha = .05,
-              size = 2,
-             hjust = "inward"
-             ) +
-  ylab("Number of employees") +
-  scale_y_continuous(labels = scales::comma) +
-  oescolorrrs::scale_fill_oes() +
-  oescolorrrs::scale_color_oes() +
-  theme_light() +
-  theme(
-    legend.position = "None",
+    legend.position = "none",
+    legend.title = element_blank(),
+    plot.title = element_text(hjust = 0.5,
+                              size = 13),
     axis.title.y = element_text(size = 8),
     axis.title.x = element_blank(),
-    axis.text.x = element_blank())
-```
-
-```{r}
-p_2
-```
-
-```{r}
-file_name <- "abstract_2.png"
-fp <- file.path(params$google_drive_home,"04. Analysis", "output", "png",file_name)
-```
-
-```{r}
-ggsave(filename = fp, plot = p_2, width = 3, height = 3, units = "in")
-```
-
-# Telecommuters, office visitors, and regions
+    axis.text.x = element_text(size = 6)
+    )
+
+p_1
+```
+
+# GSA Work Patterns
 
@@
   geom_col() +
+  facet_wrap(facets = vars(.cluster_5), nrow = 1) +
+  labs(title = "Percent of working pattern group by GSA region") +
+  ylab("Percent of working pattern group") +
+  xlab("GSA region number") + 
   scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in region") +
-  facet_wrap(facets = vars(.cluster_5), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
+  theme(
+    legend.position = "none",
+    legend.title = element_blank(),
+    plot.title = element_text(hjust = 0.5,
+                              size = 13),
+    axis.title.y = element_text(size = 8),
+    # axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 6)
+    )
 
@@
 
-# Hybrid, onsite, and disconnected workers and regions
+# GSA Work Patterns
 
@@
   filter(.cluster_5 == "Hybrid\nworkers" |
-           .cluster_5 == "Onsite\nworkers" |
+           .cluster_5 == "In-office\nworkers" |
            .cluster_5 == "Disconnected\nworkers")
@@
 
-# States: MD, PA, and VA
-
-```{r}
-prep_d_01 <- 
-  d %>% 
-  group_by(location_state,.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(num = n)
-
-prep_d_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(tot = n)
-
-prep_d_03 <- 
-  prep_d_01 %>% 
-  full_join(prep_d_02) %>% 
-  mutate(
-    n = num/tot,
-    text = scales::comma(num)
-  )# %>% 
-  # mutate(
-  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
-  # )
-
-prep_d_04 <- 
-  prep_d_03 %>% 
-  filter(location_state %in% c("MD","PA","VA")
-           )
-```
-
-```{r}
-p_1 <- 
-  prep_d_04 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = n, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in state") +
-  facet_wrap(facets = vars(location_state), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
-```
-
-# States: CA and IL
-
-```{r}
-prep_d_01 <- 
-  d %>% 
-  group_by(location_state,.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(num = n)
-
-prep_d_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(tot = n)
-
-prep_d_03 <- 
-  prep_d_01 %>% 
-  full_join(prep_d_02) %>% 
-  mutate(
-    n = num/tot,
-    text = scales::comma(num)
-  )# %>% 
-  # mutate(
-  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
-  # )
-
-prep_d_04 <- 
-  prep_d_03 %>% 
-  filter(location_state %in% c("CA", "IL")
-           )
-```
-
-```{r}
-p_1 <- 
-  prep_d_04 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = n, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in state") +
-  facet_wrap(facets = vars(location_state), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
-```
-
-# District of Columbia
-
-```{r}
-prep_d_01 <- 
-  d %>% 
-  group_by(location_state,.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(num = n)
-
-prep_d_02 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(tot = n)
-
-prep_d_03 <- 
-  prep_d_01 %>% 
-  full_join(prep_d_02) %>% 
-  mutate(
-    n = num/tot,
-    text = scales::comma(num)
-  )# %>% 
-  # mutate(
-  #   gsa_region = fct_reorder(gsa_region,as.numeric(gsa_region))
-  # )
-
-prep_d_04 <- 
-  prep_d_03 %>% 
-  filter(location_state %in% c("DC")
-           )
-```
-
-```{r}
-p_1 <- 
-  prep_d_04 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = n, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in state") +
-  facet_wrap(facets = vars(location_state), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
-```
-
-# Clusters and staff offices
-
-```{r}
-prep_d_01 <- 
-  d %>% 
-  group_by(gsa_sso) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n))
-
-prep_v_01 <- 
-  prep_d_01 %>% 
-  slice(2) %>% 
-  pull(n)
-
-prep_d_02 <-
-  d %>%
-  mutate(gsa_sso = fct_lump_min(gsa_sso, min = prep_v_01),
-         gsa_sso = fct_infreq(gsa_sso)) %>%
-  group_by(gsa_sso,.cluster_5) %>%
-  count() %>%
-  ungroup() %>%
-  arrange(desc(n)) %>% 
-  rename(num = n) %>% 
-  mutate(gsa_sso = fct_relevel(gsa_sso,
-                               "PBS",
-                               "FAS",
-                               "OCFO",
-                               "Other"))
-
-prep_d_03 <- 
-  prep_d_02 %>% 
-  filter(gsa_sso != "Other")
-
-prep_d_04 <- 
-  d %>% 
-  group_by(.cluster_5) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n)) %>% 
-  rename(tot = n)
-
-prep_d_05 <- 
-  prep_d_03 %>% 
-  full_join(prep_d_04) %>% 
-  mutate(
-    n = num/tot,
-    text = scales::comma(num)
-  ) 
-```
-
-```{r}
-p_1 <- 
-  prep_d_05 %>% 
-  ggplot(
-    aes(x = .cluster_5, y = n, fill = .cluster_5)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in staff office") +
-  facet_wrap(facets = vars(gsa_sso), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 7))
-
-p_1
-```
-
-# Clusters and series
+# GSA Work Patterns
 
@@
   geom_col() +
+  facet_wrap(facets = vars(occupational_series), nrow = 1) +
+  labs(title = "Percent of working pattern group by occupational series") +
+  ylab("Percent of working pattern group") +
+  xlab("occupational series number") + 
   scale_y_continuous(labels = scales::percent) +
-  ylab("Percent of cluster in series") +
-  facet_wrap(facets = vars(occupational_series), nrow = 1) +
-  theme_light() +
-  theme(
-    legend.position = "None",
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
+  theme(
+    legend.position = "none",
+    legend.title = element_blank(),
+    plot.title = element_text(hjust = 0.5,
+                              size = 13),
+    axis.title.y = element_text(size = 8),
     axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 7))
+    axis.text.x = element_text(size = 6)
+    )
 
@@
 
-# Clusters and series
+# GSA Work Patterns
 
@@
 
-```{r}
-states()
-```
-
-# TIL
-
--   Telework is very common - most GSA employees telework
-
--   Telecommuters and office visitors are very common for those that live in states neighboring DC
-
--   Employees living in DC are more likely to come to the office
-
--   PBS has considerable more onsite work than other offices
-
-# Appendix
-
-# Position Categories: How much telework?
-
-```{r include=FALSE}
-prep_d_01 <- 
-  d %>% 
-  group_by(position_category_description) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n))
-
-prep_v_01 <- 
-  prep_d_01 %>% 
-  slice(3) %>% 
-  pull(n)
-
-prep_01 <- 
-  d %>% 
-   mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
-         position_category_description = fct_infreq(position_category_description)) %>%
-  group_by(position_category_description) %>% 
-  summarise(num = mean(daily_status_teleworking)) %>% 
-  ungroup()
-
-prep_02 <- 
-  d %>% 
-   mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
-         position_category_description = fct_infreq(position_category_description)) %>%
-  group_by(position_category_description) %>% 
-  summarise(y = max(density(daily_status_teleworking)$y),
-            x = density(daily_status_teleworking)$x[density(daily_status_teleworking)$y == max(density(daily_status_teleworking)$y)]
-  )
-```
-
-```{r}
-p_1 <- 
-  prep_01 %>% 
-  ggplot(
-    aes(x = position_category_description, y = num, fill = position_category_description)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Mean days of telework") +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_2 <- 
-  d %>% 
-  mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
-         position_category_description = fct_infreq(position_category_description)) %>%
-  ggplot(
-    aes(x = daily_status_teleworking, color = position_category_description, fill = position_category_description)
-  ) +
-  geom_density(alpha = .5) +
-  # geom_vline(data = prep_01, aes(xintercept = num, color = position_category_description)) +
-  geom_text(data=prep_02, aes(x=x, y=y, label=position_category_description), size = 3, hjust = "inward") +
-  xlab("Days of telework") +
-  ylab("Density") +
-  theme_light() +
-  theme(legend.position = "None")
-
-p_1|p_2
-```
-
-# Position Categories: How much onsite work?
-
-```{r include=FALSE}
-prep_d_01 <- 
-  d %>% 
-  group_by(position_category_description) %>% 
-  count() %>% 
-  ungroup() %>% 
-  arrange(desc(n))
-
-prep_v_01 <- 
-  prep_d_01 %>% 
-  slice(3) %>% 
-  pull(n)
-
-prep_01 <- 
-  d %>% 
-   mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
-         position_category_description = fct_infreq(position_category_description)) %>%
-  group_by(position_category_description) %>% 
-  summarise(num = mean(daily_status_reporting_to_job_site)) %>% 
-  ungroup()
-
-prep_02 <- 
-  d %>% 
-   mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
-         position_category_description = fct_infreq(position_category_description)) %>%
-  group_by(position_category_description) %>% 
-  summarise(y = max(density(daily_status_reporting_to_job_site)$y),
-            x = density(daily_status_reporting_to_job_site)$x[density(daily_status_reporting_to_job_site)$y == max(density(daily_status_reporting_to_job_site)$y)]
-  )
-```
-
-```{r}
-p_1 <- 
-  prep_01 %>% 
-  ggplot(
-    aes(x = position_category_description, y = num, fill = position_category_description)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Mean days of onsite work") +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_2 <- 
-  d %>% 
-  mutate(position_category_description = fct_lump_min(position_category_description, min = prep_v_01),
-         position_category_description = fct_infreq(position_category_description)) %>%
-  ggplot(
-    aes(x = daily_status_reporting_to_job_site, color = position_category_description, fill = position_category_description)
-  ) +
-  geom_density(alpha = .5) +
-  # geom_vline(data = prep_01, aes(xintercept = num, color = position_category_description)) +
-  geom_text(data=prep_02, aes(x=x, y=y, label=position_category_description), size = 3, hjust = "inward") +
-  xlab("Days of onsite work") +
-  ylab("Density") +
-  theme_light() +
-  theme(legend.position = "None")
-
-p_1|p_2
-```
-
-# Rule-based groups: How much telework?
-
-```{r}
-prep_d_01 <-
-  d %>%
-  select(person_id, 
-         rule_based_primarily_teleworking_working,
-         rule_based_mostly_teleworking_working,
-         rule_based_mostly_reporting_to_job_site_working,
-         rule_based_primarily_reporting_to_job_site_working,
-         rule_based_all_remote,
-         rule_based_telework_onsite_minimum,
-         daily_status_teleworking) %>% 
-  pivot_longer(starts_with("rule_based_")) %>% 
-  filter(value == 1) %>% 
-  mutate(
-    name = str_remove(name, "rule_based_"),
-    name = str_remove(name, "_working"),
-    name = str_replace_all(name, "_", " "),
-    name = str_to_sentence(name),
-    name = fct_relevel(
-      name,
-      "Primarily teleworking",
-      "Mostly teleworking",
-      "Mostly reporting to job site",
-      "Primarily reporting to job site",
-      "All remote",
-      "Telework onsite minimum"
-    ),
-    name = fct_relabel(name, ~str_wrap(.,width = 20))
-  ) %>% 
-  arrange(name)
-
-prep_01 <- 
-  prep_d_01 %>% 
-  group_by(name) %>% 
-  summarise(num = mean(daily_status_teleworking)) %>% 
-  ungroup()
-
-prep_02 <- 
-  prep_d_01 %>% 
-  group_by(name) %>% 
-  summarise(y = max(density(daily_status_teleworking)$y),
-            x = density(daily_status_teleworking)$x[density(daily_status_teleworking)$y == max(density(daily_status_teleworking)$y)]
-  )
-```
-
-```{r}
-p_1 <- 
-  prep_01 %>% 
-  ggplot(
-    aes(x = name, y = num, fill = name)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Mean days of telework") +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_2 <- 
-  prep_d_01 %>% 
-  ggplot(
-    aes(x = daily_status_teleworking, color = name, fill = name)
-  ) +
-  geom_density(alpha = .5) +
-  # geom_vline(data = prep_01, aes(xintercept = num, color = name)) +
-  geom_text(data=prep_02, aes(x=x, y=y, label=name), size = 3, hjust = "inward") +
-  xlab("Days of telework") +
-  ylab("Density") +
-  theme_light() +
-  theme(legend.position = "None")
-
-p_1|p_2
-```
-
-# Rule-based groups: How much telework?
-
-```{r}
-prep_d_01 <-
-  d %>%
-  select(person_id, 
-         rule_based_primarily_teleworking_working,
-         rule_based_mostly_teleworking_working,
-         rule_based_mostly_reporting_to_job_site_working,
-         rule_based_primarily_reporting_to_job_site_working,
-         rule_based_all_remote,
-         rule_based_telework_onsite_minimum,
-         daily_status_reporting_to_job_site) %>% 
-  pivot_longer(starts_with("rule_based_")) %>% 
-  filter(value == 1) %>% 
-  mutate(
-    name = str_remove(name, "rule_based_"),
-    name = str_remove(name, "_working"),
-    name = str_replace_all(name, "_", " "),
-    name = str_to_sentence(name),
-    name = fct_relevel(
-      name,
-      "Primarily teleworking",
-      "Mostly teleworking",
-      "Mostly reporting to job site",
-      "Primarily reporting to job site",
-      "All remote",
-      "Telework onsite minimum"
-    ),
-    name = fct_relabel(name, ~str_wrap(.,width = 20))
-  ) %>% 
-  arrange(name)
-
-prep_01 <- 
-  prep_d_01 %>% 
-  group_by(name) %>% 
-  summarise(num = mean(daily_status_reporting_to_job_site)) %>% 
-  ungroup()
-
-prep_02 <- 
-  prep_d_01 %>% 
-  group_by(name) %>% 
-  summarise(y = max(density(daily_status_reporting_to_job_site)$y),
-            x = density(daily_status_reporting_to_job_site)$x[density(daily_status_reporting_to_job_site)$y == max(density(daily_status_reporting_to_job_site)$y)]
-  )
-```
-
-```{r}
-p_1 <- 
-  prep_01 %>% 
-  ggplot(
-    aes(x = name, y = num, fill = name)
-  ) +
-  geom_col() +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Mean days of onsite work") +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_2 <- 
-  prep_d_01 %>% 
-  ggplot(
-    aes(x = daily_status_reporting_to_job_site, color = name, fill = name)
-  ) +
-  geom_density(alpha = .5) +
-  # geom_vline(data = prep_01, aes(xintercept = num, color = name)) +
-  geom_text(data=prep_02, aes(x=x, y=y, label=name), size = 3, hjust = "inward") +
-  xlab("Days of onsite work") +
-  ylab("Density") +
-  theme_light() +
-  theme(legend.position = "None")
-
-p_1|p_2
-```
-
-# Onsite Flexible: Rule-based groups
-
-```{r}
-prep_d_01 <- 
-  d %>%
-  filter(position_category_description == "Onsite Flexible") %>% 
-  summarise(across(
-    .cols = starts_with("rule_based"),
-    .fns = ~ sum(., rm.na = T)
-  )) %>%
-  select(-contains("_position_category_")) %>%
-  select(-ends_with("observation")) %>%
-  rownames_to_column() %>%
-  pivot_longer(-rowname) %>%
-  select(-rowname) %>%
-  mutate(
-    name = str_remove(name, "rule_based_"),
-    name = str_remove(name, "_working"),
-    name = str_replace_all(name, "_", " "),
-    name = str_to_sentence(name),
-    name = fct_relevel(
-      name,
-      "Primarily teleworking",
-      "Mostly teleworking",
-      "Mostly reporting to job site",
-      "Primarily reporting to job site",
-      "All remote",
-      "Telework onsite minimum"
-    ),
-    name = fct_relabel(name, ~str_wrap(.,width = 20))
-  ) %>% 
-  arrange(name)
-
-prep_d_02 <- 
-  prep_d_01 %>% 
-  mutate(tot = d %>% count() %>% pull(),
-         prop = value/tot,
-         text = scales::percent(prop, accuracy = .1))
-```
-
-```{r}
-p_1 <- 
-  prep_d_01 %>% 
-  ggplot(
-    aes(x = name, y = value, fill = name)
-  ) +
-  geom_col() +
-  geom_text(data = prep_d_02, aes(x = name, y = .5*value, label = text), color = "white") +
-  scale_y_continuous(labels = scales::comma) +
-  ylab("Employees") +
-  theme_light() +
-  theme(
-    legend.position = "None",
-    axis.title.x = element_blank(),
-    axis.text.x = element_text(size = 8))
-
-p_1
-```
-
 # CONTINUE FROM HERE

### 2023-09-27 04. Analysis/scripts/04-02-abstract.Rmd
Update 04-02-abstract.Rmd

@@
 
-prep_d_05 %>% view()
+prep_d_05
 ```
@@
 
+## small
+
+```{r}
+p_3 <- 
+  prep_d_06 %>% 
+  ggplot(aes(x = .cluster_5, y = value, fill = name)) +
+  geom_bar(stat = "identity") +
+  labs(title = "Work and leave per pay period") +
+  ylab("Days per pay period") +
+  scale_y_continuous(labels = scales::comma) +
+  oescolorrrs::scale_fill_oes() +
+  oescolorrrs::scale_color_oes() +
+  theme_light() +
+  theme(
+    legend.position = "bottom",
+    legend.title = element_blank(),
+    plot.title = element_text(hjust = 0.5,
+                              size = 10),
+    axis.title.y = element_text(size = 8, vjust = -2),
+    axis.title.x = element_blank(),
+    axis.text = element_text(size = 7),
+    legend.text = element_text(size = 7)
+    )
+
+p_3
+```
+
+```{r}
+file_name <- "abstract_3.png"
+fp <- file.path(params$google_drive_home,"04. Analysis", "output", "png",file_name)
+```
+
+```{r}
+ggsave(filename = fp, plot = p_3, width = 3, height = 3, units = "in")
+```
+
 # CONTINUE FROM HERE

### 2023-09-28 04. Analysis/scripts/04-04-reporting-summary-slides.Rmd
Update 04-04-reporting-summary-slides.Rmd

@@
 
-Hybrid work has become widespread over the past three years, however, little is known about GSA employee work patterns.
-
-This information can be used to develop and tailor technologies, spaces, and strategies to support hybrid and distributed models of work so that employees are engaged, perform at their best, and remain focused on mission delivery.
+-   Hybrid work has become widespread over the past three years, however, little is known about GSA employee work patterns.
+
+-   This information can be used to develop and tailor technologies, spaces, and strategies to support hybrid and distributed models of work so that employees are engaged, perform at their best, and remain focused on mission delivery.
 
@@
 
-*What technologies and solutions does the federal workforce need to improve effectiveness in a more responsive remote work setting?*
+> *What technologies and solutions does the federal workforce need to improve effectiveness in a more responsive remote work setting?*
 
@@
     axis.title.y = element_text(size = 8),
-    axis.title.x = element_blank()
+    axis.title.x = element_blank(),
+    axis.text.x = element_text(size = 6)
     )
